### 2016-06-11 version0.0/appendixa.tex
Initial ShareLaTeX Import

\chapter{Appendix}
\section{SFR from H$\alpha$ plus 24 \um: procedure and result}
\label{app:halpha}

As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the [N II] 6583~\AA\ line.

The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from H$\alpha$ using the scaling factor between fluxes in these two band passes determined by \citet{Azimlu11}. They estimated continuum emission in each H$\alpha$ image, using photometric measurements in both \halpha and R-band images, and determined the scaling factor. These images were observed from a ground-based telescope over two years' time. Consequently, there is a non-negligible sky contribution in the background which must be estimated and removed from each image in both bands. Unfortunately, there is no nearby `blank-sky' image taken with the same instrument available from which to measure the sky contribution, which makes the removal of background emission even harder. The only remaining choice is to subtract the local background for each region. However, subtracting local backgrounds from each image will result in a non-smooth background in the final mosaic image.

\begin{figure*}
\centering
\includegraphics[width=164mm]{../image_paper1/halpha.pdf}
\caption{Mosaic created using the Montage programme from six fields of H$\alpha$ emission images of M31 from \citet{Massey07}. The resulting image from Montage was continuum-subtracted and masked for all point sources. The centre of the galaxy was masked out due to saturation of data in the continuum $R$-band image.}
\label{fig:halpha}
\end{figure*}

To create the final mosaic, first we removed the background from each region in both the \halpha and $R$-band images. The second step was to subtract the continuum from the \halpha images. Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image. At the end, we masked out all the foreground and saturated regions which include a $10\arcmin \times 10\arcmin$ region in the centre of the galaxy. To account for the flux contribution of the [N II] emission we used the flux ratio ${\rm [NII]}/{\rm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map. We created the final mosaic image, Figure~\ref{fig:halpha}, using the Montage program \citep{Berriman08}.

Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}. In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}. The fitting results using SFR(\halpha $+$ 24~\um) are more or less the same as the other two SFR tracers. The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data. Thus we did not include the SFR(\halpha $+$ 24 \um) in our final analysis.

\newpage
\section{More results from the fitting of the extended Schmidt law}
\label{app:es,figs}
Section~\ref{sec: sfl} discusses testing the extended Schmidt law and shows results for one SFR/gas tracer combination. Here we present the plots for the remaining SFR/gas tracer combinations.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_h2.png}
        \caption{Surface density of SFR(TIR) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis) }
        \label{fig:es,all,fir,h2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_hi2.png}
        \caption{Surface density of SFR(TIR) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis) }
        \label{fig:es,all,fir,hi}
    \end{subfigure}
    \hfill
   \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_tot2_f.png}
        \caption{Surface density of SFR(TIR) vs surface density of total gas and surface density of stellar mass ($z$-axis)}
        \label{fig:es,all,fir,tot}
    \end{subfigure}
       \caption{Same as Figure~\ref{fig:es,all,fuv,tot}. Here, from top to bottom plots show the surface density of the SFR(TIR) vs. surface density of H$_2$, surface density of H\,{\sc I}, and the surface density of total gas, respectively. As in Figure~\ref{fig:ks_all}, the analyses use different pixel sizes: each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in the plots with the surface density of H\,{\sc I} or total gas mass represents a region of size $\sim$155~pc. Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
       \label{fig:es,fir}
\end{figure*}

\begin{figure*}
    \centering
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_h22_f.png}
        \caption{Surface density of SFR(FUV+24~$\mu$m) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis)}
        \label{fig:es,all,fuv,h2}
    \end{subfigure}
     \hfill
   \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_hi2.png}
        \caption{Surface density of SFR(FUV+24~$\mu$m) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis)}
        \label{fig:es,all,fuv,hi}
    \end{subfigure}
   \caption{Same as Figure~\ref{fig:es,fir}, but in this figure we used FUV + 24~$\mu$m as a tracer of the SFR. The plot of the surface density of the SFR(FUV+24~$\mu$m) vs the surface density of the total gas is shown in Figure~\ref{fig:es,all,fuv,tot} in the main text.}
\end{figure*}

\begin{figure*}
  \centering
   \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_h22_f.png}
        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis)}
        \label{fig:es,all,halpha,h2}
    \end{subfigure}
     \hfill
      \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_hi2.png}
        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis)}
        \label{fig:es,all,halpha,hi}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_tot2_f.png}
        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs. surface density of total gas and surface density of stellar mass ($z$-axis)}
        \label{fig:es,all,halpha,tot}
    \end{subfigure}
    \caption{Same as Figure~\ref{fig:es,fir}, but in this figure we used H$\alpha$ + 24~$\mu$m as a tracer of the SFR.}
\end{figure*}

\section{Results of training for one-dimensional self-organizing maps}
\label{app: high_Z_1d_soms}
As mentioned in Sec.~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$. In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.

\label{app: 1d}
    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_4.png}
            %\caption{$1\times4$ weight map}
             %\label{fig: 1by4T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_4.png}
             %\caption{$1\times4$ hits map}
             %\label{fig: 1by4Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times4$~grid.}
         \label{fig: 1by4T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_5.png}
            %\caption{$1\times5$ weight map}
             %\label{fig: 1by5T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_5.png}
             %\caption{$1\times5$ hits map}
             %\label{fig: 1by5Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times5$~grid.}
         \label{fig: 1by5T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_6.png}
            %\caption{$1\times6$ weight map}
             %\label{fig: 1by6T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_6.png}
             %\caption{$1\times6$ hits map}
             %\label{fig: 1by6Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times6$~grid.}
         \label{fig: 1by6T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_7.png}
            %\caption{$1\times7$ weight map}
             %\label{fig: 1by7T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_7.png}
             %\caption{$1\times7$ hits map}
             %\label{fig: 1by7Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times7$~grid.}
         \label{fig: 1by7T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_8.png}
            %\caption{$1\times8$ weight map}
             %\label{fig: 1by8T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_8.png}
             %\caption{$1\times8$ hits map}
             %\label{fig: 1by8Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times8$~grid.}
         \label{fig: 1by8T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_9.png}
            %\caption{$1\times9$ weight map}
             %\label{fig: 1by9T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_9.png}
             %\caption{$1\times9$ hits map}
             %\label{fig: 1by9Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times9$~grid.}
         \label{fig: 1by9T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_10.png}
            %\caption{$1\times10$ weight map}
             %\label{fig: 1by10T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_10.png}
             %\caption{$1\times10$ hits map}
             %\label{fig: 1by10Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times10$~grid.}
         \label{fig: 1by10T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_11.png}
            %\caption{$1\times11$ weight map}
             %\label{fig: 1by11T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_11.png}
             %\caption{$1\times11$ hits map}
             %\label{fig: 1by11Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times11$~grid.}
         \label{fig: 1by11T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_12.png}
            %\caption{$1\times12$ weight map}
             %\label{fig: 1by12T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_12.png}
             %\caption{$1\times12$ hits map}
             %\label{fig: 1by12Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times12$~grid.}
         \label{fig: 1by12T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_15.png}
            %\caption{$1\times15$ weight map}
             %\label{fig: 1by15T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_15.png}
             %\caption{$1\times15$ hits map}
             %\label{fig: 1by15Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times15$~grid.}
         \label{fig: 1by15T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_20.png}
            %\caption{$1\times20$ weight map}
             %\label{fig: 1by20T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_20.png}
             %\caption{$1\times20$ hits map}
             %\label{fig: 1by20Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times20$~grid.}
         \label{fig: 1by20T}
    \end{figure}

### 2016-06-11 version0.0/asli.tex
Initial ShareLaTeX Import

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University of Western Ontario Thesis Template
% By: Justin Quinn Veenstra, 2010
% With thanks to Mr. (soon to be Dr.) Will Robertson.

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
%\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
    colorlinks=True,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue,
}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}

\makeatletter
\numberwithin{figure}{chapter}
\newenvironment{acknowledgements}%
{\clearemptydoublepage
 \begin{center}
  \section*{Acknowledgements}
 \end{center}
 \begingroup
}{\newpage\endgroup}

\newenvironment{dedication}%
{\clearemptydoublepage 
 \begin{center}
  \section*{Dedication}
 \end{center}
 \begingroup
}{\newpage\endgroup}

\newenvironment{preliminary}%
{\pagestyle{plain}\pagenumbering{roman}}%
{\pagenumbering{arabic}}

\addtoreflist{chapter}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}

% Default values for title page.

%% To produce output with the desired line spacing, the argument of
%% \spacing should be multiplied by 5/6 = 0.8333, so that 1 1/2 spaced
%% corresponds to \spacing{1.5} and double spaced is \spacing{1.66}.
\def\normalspacing{1.25} % default line spacing

%% Define the "thesis" page style.
\if@twoside % If two-sided printing.
\def\ps@thesis{\let\@mkboth\markboth
   \def\@oddfoot{}
   \let\@evenfoot\@oddfoot
   \def\@oddhead{
      {\sc\rightmark} \hfil \rm\thepage
      }
   \def\@evenhead{
      \rm\thepage \hfil {\sc\leftmark}
      }
   \def\chaptermark##1{\markboth{\ifnum \c@secnumdepth >\m@ne
      Chapter\ \thechapter. \ \fi ##1}{}}
   \def\sectionmark##1{\markright{\ifnum \c@secnumdepth >\z@
      \thesection. \ \fi ##1}}}
\else % If one-sided printing.
\def\ps@thesis{\let\@mkboth\markboth
   \def\@oddfoot{}
   \def\@oddhead{
      {\sc\rightmark} \hfil \rm\thepage
      }
   \def\chaptermark##1{\markright{\ifnum \c@secnumdepth >\m@ne
      Chapter\ \thechapter. \ \fi ##1}}}
\fi

\pagestyle{thesis}
% Set up page layout.
\setlength{\textheight}{9in} % Height of the main body of the text
\setlength{\topmargin}{-.5in} % .5" margin on top of page
\setlength{\headsep}{.5in}  % space between header and top of body
\addtolength{\headsep}{-\headheight} % See The LaTeX Companion, p 85
\setlength{\footskip}{.5in}  % space between footer and bottom of body
\setlength{\textwidth}{6.25in} % width of the body of the text
\setlength{\oddsidemargin}{.25in} % 1.25" margin on the left for odd pages
\setlength{\evensidemargin}{0in} % 1.25"  margin on the right for even pages

% Marginal notes
\setlength{\marginparwidth}{.75in} % width of marginal notes
\setlength{\marginparsep}{.125in} % space between marginal notes and text

% Make each page fill up the entire page. comment this out if you
% prefer. 
\flushbottom

\setcounter{tocdepth}{3} % Number the subsubsections 
\def\normalspacing{1.25} % default line spacing

\newcommand\isco[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \\\underline{Co-Supervisor:}\vspace{0.35in}\\\dots\dots\dots\dots\dots\dots\dots\\{#1}\\
  \fi
}

\newcommand\isjoint[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \\\underline{Joint Supervisor:}\vspace{0.35in}\\\dots\dots\dots\dots\dots\dots\dots\\{#1}\\
  \fi
}

\newcommand\isalt[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \\\underline{Alternate Supervisor:}\vspace{0.35in}\\\dots\dots\dots\dots\dots\dots\dots\\{#1}\\
  \fi
}

\newcommand\isdefinedsig[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \\ \dots\dots\dots\dots\dots\dots\dots\\{#1}\\
  \fi
}
\newcommand\isdefinedspinetitle[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else (Spine title: #1)\\
  \fi
}
\newcommand\coauthor[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Co-Authorship Statement\normalsize\\\indent\\#1\\
  \fi
}

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
%\newcommand{\superj}{Dr. A. Manning} %joint supervisor, if there is one, leave blank if not (lbin)... only one of the three.
\newcommand{\superc}{} %co-supervisor, if there is one, leave blank if not (lbin)
\newcommand{\supera}{} %alternate supervisor, if there is one, leave blank if not (lbin)
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. S. Basu}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. S. Gallagher}
\newcommand{\examth}{Dr. M. Daley}
\newcommand{\examf}{}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{Properties of nearby galaxies from modern statistical methods:Bayesian analysis and Data Mining}
\newcommand{\spinetitle}{Properties of nearby galaxies}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
Thanks to Sophia, Hossein and Els. 
}
\newcommand{\makeacknowlege} {
I would like to thank all my Friends in Western.
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and supports. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

\renewcommand{\maketitle}
{\begin{titlepage}
   \setcounter{page}{1}
   %% Set the line spacing to 1 for the title page.
   %\begin{spacing}{1} 
   \begin{large}
   \begin{center}
      \mbox{}
      \vfill
      {\MakeUppercase{\titl}}\\
      \isdefinedspinetitle{\spinetitle}
      (Thesis format: \thesisformat)\\
      \vfill
      by \\
      \vfill
      {\firstname} \underline{\lastname}\\
      \vfill
      Graduate Program in {\department}\\
      \vfill
		A thesis submitted in partial fulfillment\\
		of the requirements for the degree of\\
		\degree\\
		\vfill
		The School of Graduate and Postdoctoral Studies\\
		The University of Western Ontario\\
		London, Ontario, Canada\\
		\vfill
      {\copyright} {\authorname} {\gyear}  \\
      \vspace*{.2in}
   \end{center}
   \end{large}
%   \end{spacing}
   \end{titlepage}

}%\maketitle

\newcommand{\makecert}{
   \setcounter{page}{2}
\vfill
\begin{center}
\large
THE UNIVERSITY OF WESTERN ONTARIO\\
School of Graduate and Postdoctoral Studies\\
\vfill
\textbf{CERTIFICATE OF EXAMINATION}
\end{center}

\vfill
\begin{table}[ht]
\begin{minipage}[t]{0.5\linewidth} %tabular instead?
\begin{tabular}{l}
\underline{Supervisor:}\vspace{0.35in}
\isdefinedsig{\super}
\isco{\superc}
\isjoint{\superj}
\isalt{\supera}
\underline{Supervisory Committee:}\vspace{0.35in}
\isdefinedsig{\sco}\vspace{0.15in}
\isdefinedsig{\sct}
\end{tabular}
\vfill
\end{minipage}
\hspace{0.5in}
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\underline{Examiners:} \\\vspace{.5cm}
\isdefinedsig{\examo}\\
\isdefinedsig{\examt}\\
\isdefinedsig{\examth}\\
\isdefinedsig{\examf}
\end{tabular}
\vfill
\end{minipage}
\vfill
\end{table}
\vfill
\begin{center}
The thesis by \\ \vfill
\textbf{\firstname{} \middlename{} \underline{\lastname}}\\
\vfill
entitled:\\\vfill
\textbf{\titl}\\\vfill
is accepted in partial fulfillment of the \\
requirements for the degree of\\
\degree\\
\end{center}
\begin{table}[ht]
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\dots\dots\dots\dots\dots\\
Date
\end{tabular}
\end{minipage}
\hspace{0.5in}
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\dots\dots\dots\dots\dots\dots\dots\dots\dots\dots\\
Chair of the Thesis Examination Board
\end{tabular}
\end{minipage}
\end{table}

}

\makeatother
\begin{document}

%% ***   NOTE   ***
%% You should put all of your '\newcommand', '\newenvironment', and
%% '\newtheorem's (in other words, all the global definitions that you
%% will need throughout your thesis) in a separate file and use
%% "\input{filename}" to input it here.

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
\newcommand \sva {SvA}%: Soviet Astronomy

\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}
\defcitealias{Noll09}{N09}

%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}

%% This generates the title page from the information given above.
\maketitle
\addcontentsline{toc}{chapter}{Certificate of Examination}
\makecert
\newpage
\addcontentsline{toc}{chapter}{Co-Authorship Statement}
\coauthor{\makecoauthor}  %comment this out if none
\newpage
\addcontentsline{toc}{chapter}{Acknowledgements}
\acknowlege{\makeacknowlege}	%as above
\newpage
\addcontentsline{toc}{chapter}{Dedication}
\dedications{\makededications}
\newpage
\addcontentsline{toc}{chapter}{Abstract}
\Large\begin{center}\textbf{Abstract}\end{center}\normalsize
%%  ***  Put your Abstract here.   ***
%% (150 words for M.Sc. and 350 words for Ph.D.)

I study properties of galaxies.

\vfill
\textbf{Keywords:} Nearby galaxies: M31, M101, Star formation rate, stellar mass, ISM, data mining
\newpage
\tableofcontents\newpage
\newpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\newpage
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables\newpage
\addcontentsline{toc}{chapter}{List of Appendices}
\listofmyappendices\newpage
%\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
%\large List of Abbreviations, Symbols, and Nomenclature \normalsize
%\newpage
\end{preliminary}
%% End of the preliminary sections: reset page style and numbering.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Put your Chapters here; the easiest way to do this is to keep each %%
%% chapter in a separate file and \include all the files right here.  %%
%% Note that each chapter file should start with the line             %%
%% "\chapter{ChapterName}".  Note that using "\include" instead of    %%
%% "\input" makes each chapter start on a new page.                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\include{intro}
\include{paper1}
\include{paper2}

%% This adds a line for the Bibliography in the Table of Contents.
\addcontentsline{toc}{chapter}{Bibliography}
%% ***   Set the bibliography style.   ***
\bibliographystyle{apj.bst} % (change according to your preference)
%%% ***   Set the bibliography file.   ***
\bibliography{westernthesis}

%Appendices.
\begin{appendices}
\include{appendixa}
\end{appendices}

%CV only relevant stuff... not full CV.
% \addcontentsline{toc}{chapter}{Curriculum Vitae}
% \chapter*{Curriculum Vitae}
% \begin{table}[ht]
% \begin{tabular}{ll}
% \textbf{Name:} & \firstname{} \lastname\\\\
% \textbf{Post-Secondary} & La La School\\
% \textbf{Education and}& La La Land\\
% \textbf{Degrees:}& 1996 - 2000 M.A.\\\\
% & University of Western Ontario\\
% & London, ON\\
% & 2008 - 2012 Ph.D.\\\\
% \textbf{Honours and}& NSERC PGS M\\
% \textbf{Awards:}& 2006-2007\\\\
% \textbf{Related Work}& Teaching Assistant\\
% \textbf{Experience:}& The University of Western Ontario\\
% & 2008 - 2012\\
% \end{tabular}
% \end{table}
% \subsubsection*{Publications:}
% La La
\end{document}

### 2016-06-11 version0.0/intro.tex
Initial ShareLaTeX Import

\chapter{Introduction}
\label{chap:intro}

\section{Overview}

Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe. Stars are also central to the formation of planetary systems and are where the ingredients for life were formed. The energy provided by stars is necessary to maintain the life on planets. The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System. This is one of the main reasons that the study of stellar structure and evolution has been a central topic in astronomy and astrophysics for decades.

In order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation of stars is necessary. Star formation determines the structure and evolution of galaxies, by transforming gas into stars. Moreover, the knowledge of star formation is essential to understanding the origin of planetary systems. The physical process of star formation is naturally complex. Therefore, the basis for a theory of star formation requires a strong foundation of empirical data or observations.

In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the interstellar medium (ISM) which is due to gravitational instabilities. The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution. Numerical simulations have shown that magnetic fields in the cores become supercritical and collapse\citep{Basu97}. In the process of  collapsing, an accretion disk is formed and significant magnetic flux is lost while the star also gradually loses its angular momentum. Powerful winds are magnetocentrifugally driven from the surface of the disk and turn into a jet-like flow due to magnetic hoops stresses \citep{Shu94}. This wind flows from the protostellar core and sweeps up gas into a massive molecular outflow. Massive stars form from massive cores, which are highly energised. These stars are highly luminous, therefore, they ionize their surrounding gas into HII regions. GMCs lose much of their original mass due to photo-evaporation. Most of the mass lost returns to the diffuse interstellar medium and completes the cycle of star formation, which then starts a new cycle (see \cite{McKee07} for more detail).

The study of star formation has been an ongoing process and extends into the present era. The physical processes of star formation can be studied by direct observation. For more than 50 years, the numerical simulations, the empirical and theoretical laws, which describe the star formation rate have been investigated; nevertheless, their results have never been precise. Formation of stars is a complicated process. Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc. Thus to fully understand this intricate process, many theories have been proposed and numerical simulations are carried out.

Despite the complex physical properties, fortunately there are empirical scaling laws to relate the star formation to other properties of galaxies. The most well-known of these scaling laws is the relation between the surface density of the star formation rate (SFR) and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law \citep{Schmidt59, Kennicutt98a}. Similar to KS law, another scaling relation was derived which is a linear scaling between the total SFR and the mass of molecular gas (refer to the review by \cite{Elmgrenn11}). More recently, \cite{Shi11} derived another scaling relation, which relates the surface density of the SFR of galaxies to both gas surface density and the stellar mass.

In this paper, we present the observational review of measuring the star formation rate and other properties that affect measuring and scaling the SFR in nearby galaxies. In $\S2$ we discuss measuring the star formation rate. A discussion of the ISM is presented in $\S3$, followed by a discussion of the measurement of the stellar mass in $\S4$. In $\S5$ the KS law and the models for scaling the star formation rate are introduced. The current issues about KS law and the present project are discussed in $\S6$.

%-----------------------------------------------------
% Chapter: SFR
%-----------------------------------------------------
\section{Star Formation Rate}
\label{chap:sfr}

Understanding formation of stars leads to understanding galaxy formations. Characterisation of the star formation processes, such as the total SFR and the initial mass function of a galaxy, is necessary in examining its structure formation \citep{McKee07}. The main problem is that measuring the SFR is not trivial and depends on the galaxy morphology, metallicity, IMF, the spatial resolution of a target system, etc. There is a large number of review papers in the literature on how stars form and how their formation is traced. From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by \citep{McKee07}. From an observational standpoint, star formation is discussed by \cite{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.

Many groups have been trying to define a technique to calibrate emission from the newly-born, hot and massive ``€œO"€ and ``€œB"€ stars to the rate at which stars are being formed. Emission from the young massive stars are normally used as a tracer of the current SFR. Using luminosity of massive stars makes sense if one considers that star formation rate has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. The number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region. To do so, the stellar IMF must be known. However, knowing the Stellar IMF is not enough. To have a reliable SFR indicator, the stellar IMF must be fully sampled, which means that in the highest-mass bin at least one star is formed and all other mass bins have one or more stars (see section ~\ref{sec: imf}).

The ``O"€™ and ``€œB"€ stars can be observed by both using direct and indirect emission from stars; thus the SFR indicators are categorized based on these methods of observation. In the direct method, the SFR indicators can be probed by the ultraviolet (UV), optical, and near-infrared (NIR) emissions, while for probing the stellar light obscured by dust, mid/far-infrared emission is used. The ionizing photons are used in the indirect method. They are emitted by massive stars and traced by the ionized gas \citep[e.g.,][]{Calzetti04, Calzetti07}. In principle, the SFR is traced by the UV emission, the optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-millimetre range by using the Bremsstrahlung emission. Moreover, high mass binaries, massive stars and supernova explosions produce X-ray emissions which can be used as a tracer of star formation. Each of these tracers has some systematic errors, and one should decide which of these methods are more precise for a given system. for example using dust IR emission as an indicator is not precise in dwarf galaxies with small amounts of the gas, although still errors from dust extinction and attenuation must be considered (see section ~\ref{sec: ism}).

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
One of the most fundamental and difficult questions that a complete theory of star formation must answer is the initial mass function. In order to determine the SFR from calibrated photometry data, it is necessary to know the IMF. Most problems in modern astrophysical studies regarding the origin and evolution of stars and galaxies can be solved by varying an IMF \citep{Bastin10}. \cite{Salpeter55} empirically derived the IMF from the observed stellar luminosity function of the Solar neighbourhood \citep{Shu87}. He introduced a power-law IMF of the form:

\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where M is the mass of a star, $\gamma$ is the power index, and N is the number of stars in some logarithmic mass range $\log M + d\log M$.

In the late 70s, it was recognised that using the single power-law IMF over all stellar masses is not a correct assumption \citep{Kroupa93, Bastin10}. Since then, many groups have studied the IMF and found different power laws for it (Fig.{~\ref{fig: imf}} ). Most SFR calibrations have the same assumption that the IMF is constant across all environments which is adopted from the standard IMF of \cite{Kroupa01}:

\begin{align}
\chi (M) = dN/dM = A M^{-1.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           = 0.5 A M^{-2.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{align}
where $\chi(M)$ is the number of stars between masses $M$ and $M+dM$. Although the Salpeter IMF produces more low-mass stars then the Krupa IMF, they produce almost the same number of the high mass stars. Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration's constant by 1.6 \citep{Calzetti13}. \cite{Bastin10} reviewed  the IMF  by using many observational results and showed that the IMF is constant and universal, although there are uncertainties in different mass bins especially at the high mass end.

\begin{figure}[h]
\label{fig: imf}
\centering
\includegraphics[width=16cm]{../image_intro/imf}
\small
\caption{Comparing the IMFs by plotting the mass fraction per dex versus mass that is normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120 M$_\odot$. Adopted from \cite{Baldry03}}
\end{figure}

The careful measurement of the IMF is a key to understanding the SFR. In distant galaxies, only massive stars can be detected; therefore, the IMF must be measured to include all stellar mass ranges in the SFR calibrations. To show the impact of the different IMF assumptions on the SFR calibrations, \cite{Calzetti13} used two different IMFs and derived the SFR calibrations with these new assumptions. Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors ranging from 1.4 to 5.6 for different SFR indicators (Table {~\ref{table1}}).

\subsection{SFR Indicators}

One of the main issues to study distanced galaxies is the calibration of SFR indicators \citep[e.g.,][]{Lee10}. Calibration of SFR indicators can be affected by differences in star formation history (SFH), metallicity, distribution of stellar population and dust between different galaxies \citep{Calzetti13}. Depending on spatial resolution of the system one can divide star formation indicators into two categories: resolved and unresolved star formation indicators.

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects \citep{Kennicutt12}. These objects mostly have certain ages and usually are referred to as young stellar objects (YSOs). Counting YSOs is a method used for calculating star formation in molecular clouds within $0.5- 1$ kpc of the Solar System. The number of YSOs can be converted to SFR using:

\begin{equation}
SFR(YSO) = N_{yso} <M> \ \tau 
\end{equation}
where N$_{yso}$ is the number of YSOs, $<$M$>$ is the mean mass of YSO which depends on the stellar initial mass function (IMF; see section~\ref{sec: imf}), and $\tau$ is the lifetime of the YSO considering some uncertainly $\tau \sim 2$Myr \citep{Evans09}. The SFR(YSO) is in the unit of M$_{\odot}$yr$^{-1}$. Due to observational difficulties, this method can only be applied to the Milky Way and the Solar neighbourhood.

In theory, for any system with high enough spatial resolution ($\sim 0.5- 1$ kpc), counting YSOs can be used as a tracer of the star formation. However, considering the limited capabilities of the present instrumentations, YSOs in most regions beyond the Magellanic clouds can not be resolved. Therefore, most studies use the emission from the ``O" and ``B" stars as tracer of the SFR. Another method to measure the SFR is by looking at the colour-magnitude diagram (CMD) of star-forming regions. \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to reproduce the spatially and age-resolved maps of star formation in nearby galaxies. More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to \citep{Kennicutt12}.

\subsubsection{Unresolved Star Formation Indicators}
 In star-forming regions farther away than the Magellanic clouds, spatial resolution is not high enough to find all the YSOs. In unresolved systems, luminosity, which is either single band or integrated over some wavelength range, is used as an SFR indicator. This method is used to find continuum or line emission at some wavelengths that are sensitive to the young massive stars \citep[e.g.,][]{Kennicutt98b, Calzetti13}. \cite{Kennicutt98b} reviewed calibrations of star formation tracers. He calibrated luminosity for measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.,][]{Bruzual93}.

In unresolved systems, the SFR indicators can be divided into local and global SFR indicators. The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. While local calibration is used for regions within a galaxy, on a scale of sub-galaxy \citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}. The limitations in the spatial resolution of the data on the one hand, and the broader applicability of distant galaxy populations on the other, have brought more attention to the calibrations of global SFR compared with the local SFR calibrations that had been done in the past. Yet, because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important \cite{Calzetti13}.

The following subsections describe some SFR indicators in more detail. In this paper, we categorise the SFR indicators into tracers based on single-band emission and those that are based on the multi-band emission. For each category, we discuss if a calibration can be used as local or global and also describe their differences.

\subsubsection*{SFR Indicators Based on the Single-Band Emission}

In order to derive the conversion between the luminosity in specific wavelengths and the SFR, synthesis models are used \citep{Kennicutt98b}. General form of a SFR calibration using single-band emission is: 
\begin{equation}
\label{equ: sfrsingle}
SFR(\lambda)= CL(\lambda)
\end{equation}
where SFR is in units of M${_\odot}$yr$^{-1}$, $L(\lambda)$ is luminosity in erg/s at the wavelength $\lambda$, and C is the constant derived from stellar population models (Starburst99, \cite{Leitherer99}). The constant, C, can vary for different emission, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation needs to remain constant. Table~\ref{table1} from \cite{Calzetti13}, summarises the changes in the constant of the calibration.

\begin{table}[ht]
\caption{Luminosity-to-SFR calibrations adapted from \cite{Calzetti13}\label{table1}}
\centering
\begin{tabular}{ c c c }
\hline\hline
Luminosity\footnotemark{} & C\footnotemark{} & Assumptions\footnotemark{}\\
\hline
L(UV) & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
L(UV) & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
L(UV) & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
L(UV) & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
\hline
\end{tabular}
\end{table}
\footnotetext[1]{Luminosities are in erg/s and are given as $\nu L_{\nu}$.}
\footnotetext[2]{The constant C appears in equation~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$.}
\footnotetext[3]{Assumptions for mass range of the stellar IMF, which we adopt to have the expression derived by \cite{Kroupa01} (see section{~\ref{sec: imf}}), and for the timescale $\tau$.}

One of the most common single-band wavelengths, which are used as an SFR indicator, is UV emission. UV emission can be an excellent tracer for the SFR due to the fact that the peak of emission for both ``O" and ``B" stars are in the UV part of the spectrum. Using spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming \cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as \citep{Leitherer99}
\begin{equation}
SFR(UV) = 3.0 \times 10^{-47}\lambda L(\lambda)
\end{equation}
where SFR(UV) is in M$_{\odot}$yr$^{-1}$, $\lambda$ is in $\AA$, and $L(\lambda)$ is in erg/s, while $\lambda$ is in the range of $(0.0912\mu$m $< \lambda < 0.3\mu$m). As shown in table ~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few percent. However, the calibration constant's changes for shorter timescales, are more significant \citep{Calzetti13}. The accuracy of the calibration constant is $\pm 15\%$ which can vary as a function of $\lambda$. The UV light can easily be absorbed or scattered by interstellar dust. Therefore, using the UV emission as a tracer might lead to underestimating of the SFR, if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section ~\ref{sec: ism}).

Another single-band SFR indicator is the emission from hydrogen recombination lines. Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators \citep{Kennicutt98a}.  The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived quantum mechanically. To have such results, the nebula must be optically thick to ionizing photons \citep{Osterbrock06}. Being optically thick makes almost all transitions more energetic than Ly${\alpha}$ to be absorbed and re-emited via Ly${\alpha}$ and longer wavelengths. This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the H$\alpha$ emission line and the ionizing photon rate is \citep[e.g.,][]{Osterbrock06, Kennicutt98b}:

\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(H$\alpha$) is in M$_{\odot}$ yr$^{-1}$, L(H$\alpha$) is in erg/s, and Q(H$^{\circ}$) which is the ionizing photon rate is in units of s$^{-1}$. The constant at the right-hand side of equation~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_e=10000$K and density N$_e=100$ cm$^{-3}$ which is the normal case in the interstellar medium. All SFR indicators that use the ionization of hydrogen to trace the formation of massive stars are sensitive to the effects of dust. Dust extinction (Section ~\ref{sec: ism}) is the most important systematic error for calculating the SFR from hydrogen recombination line.The effects of dust must be measured and H$\alpha$ observations must be corrected or this could lead to underestimating the SFR \citep{Kennicutt98b}.

Another nebular line, which is used as a tracer of the SFR is [OII]$\lambda$3727$\AA$. Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has correlation with the H$\alpha$ emission. As a result, [OII] luminosity can be used as a tracer of the SFR through H$\alpha$ luminosity. \cite{Gallagher89} calibrated the SFR based on the [OII] luminosity by using a sample of 75 galaxies. Another calibration for this luminosity was derived by \cite{Kennicutt92}, which has a different calibration factor. In his review on the SFR, \citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR(O[II]) = 1.4 \times 10^{-41} L(O[II])
\end{equation}  
where SFR(O[II]) is in M$_{\odot}$ yr$^{-1}$, L(H$\alpha$) is in erg/s. Although SFR (O[II]) is not as precise as the SFR(H$\alpha$), it is one of major SFR indicators in high redshift galaxies. In high redshift galaxies, H$\alpha$ emission line is out of optical bands, as a consequence, calibration of the strongest emission feature in the blue light (O[II]) as a SFR indicator is really useful \citep{Kennicutt98b}.

Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the IR emission can be used to trace the SFR. The IR luminosity of a system depends not only on the amount of the embedded dust, but also on the heating rate provided by the stars. Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order the shape of the thermal IR SED depends on the starlight SED \citep{Helou86}. The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60  \mu$m) in comparison with the dust heated by old or low-mass stars.€“ Therefore, the IR wavelength is able to detect the emission from the young stellar population and be used as an SFR indicator.

24 $\mu$m and 70 $\mu$m bands are two empirical single-band IR SFR calibrators. The use of these two bands depends on the type of the galaxy studied or the physical environment in different regions within the galaxy. Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) and a local indicator. That is because the global case includes the Hubble time integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as: HII regions, large star-forming complexes, etc. \cite{Calzetti13}. Table ~\ref{table2} shows the constant C from equation~\ref{equ: sfrsingle} for 24 $\mu$m and 70 $\mu$m luminosities and for local (spatial scale $\sim500$ pc for 24$\mu$m band and spatial resolution less than $\sim 1$ kpc for 70 $\mu$m one) and global cases.

\begin{table}[ht]

\caption{IR Luminosity to SFR calibrations \label{table2}}
\centering
\begin{tabular}{ c c c c }
\hline\hline
Luminosity\footnotemark{} & C & Assumptions & references\\
\hline
L(24)$^{0.885}_{local}$ & $1.31 \times 10^{(-38)}$ &$(1.10^{40} \le L(24) \le 3.10^{44})$& Calzetti et al. (2007)  \\
L(24)$_{global}$ & $2.04 \times 10^{(-43)}$ &$ (4.10^{42} \le L(24)  \le 5.10^{43})$& Calzetti et al. (2007) \\
L(70)$_{local}$ & $9.4 \times 10^{(-44)} $ &$(5.10^{40} \le  L(70) \le 5.10^{43})$& \cite{Li12} \\
L(70) $_{global}$& $5.9 \times 10^{(-44)}$ &$(L(70) \ge 1.4 \times 10^{42} $& \cite{Li10}\\
\hline
\end{tabular}
\end{table}  
 \footnotetext{Luminosities are in form of L($\lambda$) = $\lambda L(\lambda)$ in erg s$^{-1}$}
 %The SFR(70) calibration constant thus increases when going from whole galaxies to 1 kpc regions, i.e., for decreasing region sizes. According to the Li et al. (2012) this constant can be interpreted in terms of star formation timescale within each region (Fig.{~\ref{sfr70}}).
%\begin{figure}
%\label{sfr70}
%\centering
%\includegraphics[width=8cm]{sfr70}
%\caption{The calibration constant, C$_70$, between SFR and the 70$\mu $m luminosity, from equation~\ref{equ: sfrsingle}, as a function of the physical size of the regions used to derive the calibration. The filled red triangles are observed values from Li et al. (2010, 2012) and Calzetti et al. (2010), using both $Spitzer$ and $Herschel$ data. The black stars are from stellar population synthesis models, for constant star formation and a Kroupa (2001) IMF, in the stellar mass range of 0.1-100 M$_\odot$; the mean age of the population that best approximates the observed C70 values is shown. This figure is adapted from \cite{Calzetti13}.}
%\end{figure}

\subsubsection*{SFR Indicators Based on the Multi-Band Emission}

Despite the usefulness of having single-band SFR tracers, in many cases, one should be careful about the corrections due to dust effects, luminosity ranges, etc. Nowadays, thanks to large surveys, enormous data is available at different wavelengths for galaxies. This allows for combining the emission from different bands and finding new calibrations. Conversion between SFR and luminosities at different bands mostly helps avoiding problems regarding dust extinction or attenuation (see~\ref{sec: ism}).

The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically proved \citep{Kennicutt12}. There are studies that use a higher order polynomial relation to combine luminosities \citep[e.g.,][]{Buat05}; however, this discussion is out of the scope of this paper.

Integrating over the full wavelength range of the IR part of spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator. As mentioned earlier, dust absorbs stellar radiation at all wavelengths; however, we only discuss radiation emitted from UV luminous stars. It must be noted that since there is no one-to-one mapping between IR and UV emission \citep{Calzetti13}, it is better to use the TIR emission as a tracer of the SFR instead of the IR single-band emission.

\cite{Draine07} modelled $Spitzer$ \citep{Wener04} data and found a calibration for the total infrared luminosity from photometry images instead of using IR SED. \cite{Boquien10} tested this calibration and found the modified version of calibration to estimate total infrared luminosity: 
\begin{equation}
L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m)
\end{equation}
where $L = \nu L_{\nu}$ and $L_{\nu}$ is the luminosity  in erg/s at frequency $\nu$. \cite{Calzetti07} indicated that star formation rate calibration for a stellar population undergoing constant star formation over $\tau=100Myr$ is:
\begin{equation}
\label{sfr_tot_IR}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
\end{equation}
where SFR(TIR) is in M${\odot}$yr$^{-1}$, and L(TIR) is in erg/s. To do this calculation, it is assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(\rm bol)=L(\rm TIR)$.

The most common use of combining luminosities to trace the SFR is calibration of the SFR by combination of TIR measurements with both far and near UV observations, with the latter being more commonly used. This combination helps to avoid uncertainties from dust attenuation in FUV observations.
\begin{equation}
L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR}
\end{equation}
where the luminosities are $L = \nu L_{\nu}$ in erg/s, and the coefficient $\alpha$ depends on the bandpasses that are chosen for the UV and IR measurements. $\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies is from dust heated by older population stars \citep{Kennicutt12}. The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (e.g., \cite{Hao11}.

Another common method for using the multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the $24\mu$m emission. This combination gives a more accurate dust-corrected estimate of the SFR \citep{Kennicutt09}:

\begin{equation} 
\label{equ: halphaplus24}
SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24)]
\end{equation}
where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg/s. L(24) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.

\begin{table}[ht]
\caption{Multi-wavelength dust-corrected luminosities, adopted from \cite{Kennicutt12} \label{table3}}
\centering
\begin{tabular}{ c c}
\hline\hline
Combined luminosities\footnotemark{} & references\\
\hline
L(FUV)$_{corr}$=L(FUV)$_{obs}$ + 0.46L(TIR)& Hao et al. (2011)\\
L(FUV)$_{corr}$=L(FUV)$_{obs}$ + 3.89L(24$\mu$m)& Hao et al. (2011)\\
L(NUV)$_{corr}$=L(NUV)$_{obs}$ + 0.27L(TIR)& Hao et al. (2011)\\
L(NUV)$_{corr}$=L(NUV)$_{obs}$ + 2.26L(24$\mu$m)& Hao et al. (2011)\\
L(H$\alpha$)$_{corr}$=L(H$\alpha$)$_{obs}$ + 0.0024L(TIR)& Kennicutt et al. (2009)\\
L(H$\alpha$)$_{corr}$=L(H$\alpha$)$_{obs}$ + 0.020L(24$\mu$m)& Kennicutt et al. (2009)\\
\hline
\end{tabular}
\end{table}  
\footnotetext{Luminosities are in the form of L($\lambda$) = $\lambda L(\lambda)$ in erg s$^{-1}$}

Other combinations of luminosities that are used as tracers of the SFR are listed in table ~\ref{table3}. These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer \citep{Kennicutt09}.

As mentioned in section ~\ref{sec: imf}, using different IMFs leads to having different SFR calibrations. From table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. This effect is more than four times larger than UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV radiations; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$. Furthermore, reaching an asymptotic value takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR calibration constants are fairly close to each other. On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than $10\%$ difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$. As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars \citep{Calzetti13}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter: ISM
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interstellar Medium}

Interstellar medium (ISM) is referred to the space between stars in a galaxy, which is full of a thin hydrogen and helium gas and small amounts of heavier elements called metals. These elements can have neutral, ionized, or molecular forms and can be in gas phase or solid state. The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. The ISM has a huge impact on the formation and evolution of stars. Since stars are born in the ISM and release their material into the ISM when they reach the end of their evolution, studying the ISM is essential in the understanding of the formation and evolution of stars.

Considering the effects of the ISM on studying the SFR is important for two main reasons. First, stars are born from the gas; therefore, for scaling the star-formation rate in a galaxy, knowledge on the amount of gas is necessary. The other impact is that gas and dust in the ISM absorb the UV or optical emission from stars and re-emit it in the IR, or scatter the stellar light. Thus for tracing the star-forming region, the effect of dust must be taken into account, otherwise the SFR might be underestimated.

\subsection{Map of the ISM}
\label{sec: ismmap}

A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer. Neutral and molecular hydrogen are the most common elements in the ISM. Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He. Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.

\subsubsection{Direct Measurement of the Gas}

The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen. This method can be promising provided that the spatial resolution of observational data is high enough; nonetheless, due to technical limitations, attaining enough spatial resolutions to resolve clouds is almost impossible. This problem shows itself for distant galaxies more than nearby galaxies. As a result, using this method is limited and has a lot of uncertainties.

\subsubsection*{Molecular Clouds}

 The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect. H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas. The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but the molecular gas also contains heavier elements such as carbon and oxygen which are combined to form CO \citep{Bolato13}.

CO has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy. Given its low energy and critical density, CO can easily be excited even in cold molecular clouds. Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}. Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.

\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is :
\begin{equation}
L_{CO} = D^2 \int I_{CO} d\Omega 
\end{equation}
where D is the distance to the cloud. $I_{CO}$ is the CO brightness temperature integrated over the line profile. It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the linewidth. For a uniform cloud with a radius $R$, the CO luminosity is given by

 \begin{equation}
L_{CO} = \pi R^2 T_{CO} \Delta V
\end{equation}

Galactic molecular clouds are self-gravitating systems. Thus, using the Virial theorem would lead to calculating the mass of the cloud.

 \begin{equation}
 \label{equ: vir}
 M_{cloud} = L_{CO} \sqrt{\frac{4\rho}{3\pi G T_{CO}}}
 \end{equation}
 where $\sqrt{\frac{4\rho}{3\pi G T_{CO}}}$ is called the conversion factor. Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related \citep{Young91}. The relation between CO emission and H$_2$ cloud mass is shown as

\begin{equation}
N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
\end{equation}
where X$_{CO}$ is the conversion factor (also known as the X-factor). The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in metallicity, etc. Though assuming constant conversion factor cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with low metallicity there are uncertainties. Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}.

In order to empirically determine the relation between H$_2$ masses to CO luminosities, many observational attempts have been made in both galactic and extragalactic scales. One of the most significant studies in this regard was \cite{Solomon87} who studied this relation on more than 273 clouds inside the Milky Way and found the strong correlation between Virial mass of clouds and CO luminosity. In the Local Group galaxies, several groups measured the sizes, line widths, and CO luminosities of molecular clouds to investigate the relation between Virial mass and CO luminosity in other environment than the Milky Way. However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud.

Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32 \citep[e.g.,][]{Wilson89, Wilson90}. Figure {~\ref{fig: mco}} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10. The extragalactic molecular clouds are similar to those in the Milky Way. The conversion between the CO luminosity and H$_2$ masses is still a controversial topic \citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}. Problems regarding metallicity are not solved yet and it is still not clear whether the conversion factor is global or local.

\begin{figure}[h]
\label{fig: mco}
\centering
\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds. The Virial masses measured from selected high spatial resolution CO observations are shown. The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from \cite{Young91}}
\end{figure}

\subsubsection*{Neutral Gas}

Neutral hydrogen clouds are traced by 21-cm emission. The 21-cm emission comes from the fact that most of hydrogen in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state. The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. proton's spin is up and electron's spin is down or vice versa).

The energy state of anti-parallel mode is slightly less than parallel mode. Hence, electrons in the parallel mode have a tendency to flip to the anti-parallel mode (atoms always want to be in the state with lowest energy possible). Since the energy difference between these two states is small, eventually it takes millions of years before this transition happens. There are large amounts of atomic hydrogen in the ISM. Therefore, at any given time, there are enough hydrogen atoms that are emitting the 21-cm radiation, even though the transition is really rare.

The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission. Atomic hydrogens, that are along the line-of-sight contribute to the energy received. These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (HI is detectable in most spiral galaxies and some elliptical galaxies). Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick \citep{Braun09}.

\subsubsection{Dust Emission as a Tracer of Gas}

Studying the gas cloud in the ISM of distant galaxies by using direct methods is almost impossible and not practical. \cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-millimetre continuum emission from the dust; continuum dust emission is generally optically thin. The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission.

 One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore. The other important advantage is that this method solves the newly-found problem of the "dark gas"€™ in the galaxies. Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}. So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.

There are many disadvantages regarding the use of the gas to dust ratio in the ISM. In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived. \cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps \citep{Hildebran83}. Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1 \citep{Ealas12}. Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately \citep{Corbelli11}.

In addition to all the disadvantages mentioned before, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate \citep{Ealas12}. The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas \citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.

Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems. Unfortunately, at present, given the available devices and technologies, we cannot reach a high-resolution that is sufficient to detect the gas cloud directly. Therefore, so far this method is the best available solution for measuring the total gas in distant galaxies.

\subsection{Extinction and Attenuation}
\label{sec: ism}
In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed. More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by \citep{Calzetti01}.

Extinction happens when there is a combination of both absorption and scattering of radiation by dust. The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source (left panel of Fig.{~\ref{fig:duste}}).

Attenuation refers to the effect of dust with embedded light sources distributed throughout. The dust itself can be clumpy or smooth\citep{Calzetti13}. In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions (right panel of Fig.{~\ref{fig:duste}}). Dust scattering's effect depends on whether it is in or out of the line of sight. When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer. This is the typical situation that comes across when studying galaxies or extended regions within galaxies.

\begin{figure}[h]
\label{fig:duste}
\centering
\includegraphics[width=16cm]{../image_intro/dustextinction}
\caption{The cartoon of: a) a point source behind a screen of dust, a typical situation to have an extinction; and b) the distribution of stars and clumps of dust, typical system, when attenuation effect is observed. Adopted from \cite{Calzetti13}}
\end{figure}

In order to describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used. At UV/optical/near-IR wavelengths, the radiative transfer equation is:

\begin{equation}
\frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
\end{equation}
where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth, a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. $\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in \citep{Draine03}. The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m is neglected in the equation above. This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, it causes underestimation of the SFR.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter :stellar mass
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass}
\label{starmass}
One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. It was pointed out that stellar mass is linked with the structure and star formation history of disc galaxies \citep{Gavvazi96} and all morphologies \citep{Scodeggio02}. In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass \citep{Bell00}. \cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey \citep[SDSS;][]{York00}. They also showed that these results are applied for all morphological types.

Measuring the mass of the stellar population is indirect and subject to significant uncertainties. In principle there are two ways to measure stellar mass in galaxies. First is measuring the dynamical mass of galaxies using kinematics \citep{Cappellari06} or lensing \citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass. This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies \citep{Zaritsky94},  and can easily cause uncertainties as high as the order of the measurement.

The second method is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations. This method has uncertainties too, and one must also model the uncertainties. Uncertainties come from uncertainties in the stellar initial mass function (see section{~\ref{sec: imf}}), the stellar evolution models, especially the stage where they have most luminosity in their evolution, and the evolutionary state of galaxy \citep[see,][]{Dalcanton12}, and star formation histories.

In order to translate between photometry and dynamics the stellar mass to light ratio (M/L) is needed. Measuring the accurate M/L can easily lead us to stellar mass surface density.  To do that, the M/L by can be measured using scale relation between them, from different colours and then multiply it by the surface brightness to calculate the local surface stellar mass density. The M/L scale relations make a connection between two methods of measuring stellar mass \citep{Bell03}. These relations are indirect methods for measuring the stellar masses and have high uncertainties in specific cases, but they help to study the stellar mass in large samples. This is one of the solution to the problem of the measuring the stellar mass within galaxies. As a result it is important to check the accuracy of total stellar mass estimations and provide methods, which measure and produce a map of the stellar mass surface density distribution in galaxies. This method gives more accurate result than measuring the stellar mass surface density distribution from single-band images rescaled by uniform mass to light ratio \cite{Zibetti09}.

Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences. Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. Comparing the results from measuring stellar mass within galaxies shows that the deferences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}. In the following we address the approaches of measuring stellar mass in galaxies in more detail.

\subsection{Dynamical Mass}
The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and HI lines. Thanks to the current generation of detectors, the H$\alpha$ and CO lines have very high-resolution spectra over most of the optical disk, and cover most regions in the sky. Integrated line widths only yield an estimate of a total mass within some (uncertain) isophotal radius.

Resolved rotation curves produced from H$\alpha$, HI and CO lines are proportional to optical emission lines within the optical disk of galaxies, \citep{Courteau13} which helps us to measure the rotational curves. The simplest way to estimate the mass of a galaxy is assuming that the physics of the galaxy is the simple Newtonian physics. Therefore, the Mass within a potential $\phi$ and the circular velocity in the spherical system is given by:
\begin{equation}
\label{eq: simpmass}
V^2_{circ}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r}
\end{equation}
where $M(r)$ is the mass within a sphere of radius $r$. For a flattened disk which is the case in most spiral galaxies, the right hand side of equation {~\ref{eq: simpmass}}  must  be replaced by the more exact expression derived by \cite{Freeman70}. He assumed in case of no dark matter or bulge, the rotation curve of a self-gravitating disk is:
\begin{equation}
V^2_{circ}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)]
\end{equation}
where $G$ is the gravitational constant, $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, $4y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kind of modified Bessel functions.

Describing more about calculating dynamical masses in galaxies is beyond the scope of this paper. Just note that methods mentioned above is the first order of approximation. For more accurate result one should consider that the rotational velocity is not circular and the fact that galaxies contain millions of stars plus interstellar objects therefore simple two object Newtonian physics is not the case here. There are lots of different profiles to fit the rotation curve for galaxies. A detailed review of dynamical mass of galaxies can be found in Courteau et al review paper (2013).

\subsection{Stellar Population Method}
Galaxies can be observed because of their stellar emission and stars radiate the energy produced from nuclear reactions in their cores. Given the star's initial mass, the theory of stellar evolution can describe the amount of energy released. Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distribution of galaxies. However, there is a fraction of mass of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants.

As mentioned before, stellar population synthesis models is used to reproduce the SED of a stellar population using many physical parameters. These parameters, which control the time evolution of the stellar population are:
the age, $t$, of the population, measured in years, also referred to the time passed since the star formation was began;
the star formation history (SFH), often parametrized with SFR $\propto e^{-1/\tau}$; the IM; The metallicity, which is calculated as the ratio of abundance Z of elements heavier than He to abundance of H ([Z/H]), or as ratio of abundance of iron ([Fe/H]); 
and the chemical composition ratios, or the fraction of all key elements in galaxies and those values measured in the Sun. The stellar evolutionary tracks, the stellar spectral libraries, the parametrization for the mass-loss which affects several late stages of evolution are necessary for stars placing at specific evolutionary phases \citep{Courteau13}.

%\subsubsection{Calibration light of stars} 
The basic idea behind the finding the suitable calibration between flux/luminosity of the stars in different wavelengths and stellar mass is that one can use the SFHs recovered from synthesizing the stellar optical CMs in different regions in the galaxies. The calculated stellar mass can be used  to calibrate the fluxes from the stars as the easily measurable parameters of stars. Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies \citep[e.g.,][]{Elmgreen84}.  Using $B-V$ colours \citep{Bell01} and $Spitzer$ 3.6- and 4.5-$\mu$m, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.

\cite{Zibetti08} suggested for reaching the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel study \citep{Conti03}. They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density. To do so the surface density of stellar mass is derived by 
\begin{equation}
\label{equ: massphot}
\Sigma M_\star (\alpha, \delta) = \Sigma \lambda(\alpha, \delta) \gamma_{\lambda}(\alpha, \delta)
\end{equation}
where $\Sigma \lambda(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L in an effective wavelength $\lambda$. In equation~\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy. Equation~\ref{equ: massphot} can be used for each position in a galaxy.

\cite{Eskew12} related easily observable quantities to the stellar mass. They used 3.6$\mu$m and 4.5$\mu$m fluxes  for calibration of the stellar mass, because these two bandpasses are almost insensitive to the emission from young stellar population, dust absorption and emission. Also thanks to $Spitzer$ and WISE \citep{Wright10} telescopes, great amount of data from many regions in the sky is available, in these bands, which help to test them on more regions and have a more accurate calibration. They also test the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and find the empirical relation between mass of the stars and the luminosities of stars as below:

\begin{equation}
\label{equ:eskew}
M = 31.84 \times 10^{5.65} L_{3.6}^{2.85} L_{4.5}^{-1.85}
\end{equation}

where M$_{\star}$ is the stellar mass and $L = \nu L_{\nu}[\lambda]$ is the luminosity in erg/s/$\AA$.

\cite{Zhu10} used the SDSS and the $Spitzer$ Wide-area Infrared Extragalactic Survey \citep[SWIRE;][] {Lonsdale03} to find the calibration between luminosity of the galaxies and stellar masses. Using the M/L of galaxies, they found the correlation between $K_s$ band, $3.6 \mu$m and $4.5 \mu$m band luminosities and stellar masses and formulate these correlations as:
\begin{align}
\label{equ: zhu1}
\log M_{\star} = (-1.60 ) + (1.12)\times \log \nu L_{\nu}[K_s]\\
\log M_{\star} = (-0.79) + (1.19)\times \log \nu L_{\nu}[3.6\mu \rm m]\\
\label{equ: zhu3}
\log M_{\star} = (-0.25) + (1.15)\times \log \nu L_{\nu}[4.5\mu \rm m] 
\end{align}
where M$_{\star}$ is the stellar mass and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg/s in specified wavelength.

Measuring the stellar mass from equation~\ref{equ:eskew} is limited to the nearby galaxies, and might break down for high star forming regions, moreover, this equation have not tested on regions with different metallicity. Thus there is no calibration regarding variation in  metallicity \citep{Eskew12}. On the other hand equations~\ref{equ: zhu1} -~\ref{equ: zhu3} have been derived from a large sample of galaxies, and was tested on different type of regions and galaxies. Beside they can be used for more distanced galaxy as well as nearby galaxies \citep{Zhu10}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter: KS law
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Scaling the SFR Using Schmidt-Kennicut Law}

The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas. \cite{Schmidt59} assumed the constant IMF of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way. He scaled SFR with a power {\it n} of the gas mass, $M_{gas}$. Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$. A power law relation between surface densities of star formation and gas is known as the Schmidt law and is written as:
\begin{equation}
\Sigma_{SFR} \propto \Sigma_{gas}^n
\end{equation}
where $\Sigma_{SFR}$ is surface density of star formation, $\Sigma_{gas}$ is the surface density of gas in a galaxy and, {\it n} is the power index.

Following \cite{Schmidt59}, many groups worked on the scaling relation between the surface density of star formation, and the surface density of gas. \cite{Buat89} assumed the constant H$_2$/CO ratio and a \cite{Scalo86} initial mass function for the Milky Way. They measured SFR from the UV flux corrected and included molecular and atomic gas to derive the correlation between the star formation rate and the gas surface density. Another major work in that year was \cite{Kennicutt89}. By using H$\alpha$ emission for star formation, and HI and CO as a tracer of gas with constant H$_2$/CO, for more than 15 galaxies, he determined the average H$\alpha$ flux can be scaled with the average gas surface density to a power between 1 and 2.  To get better results he calculated star formation rate both as a function of galactocentric radius and averaged over whole galaxy disks. He also showed that the correlation is more accurate with using only HI as a tracer of gas.

A decade later, \cite{Kennicutt98a} examined another group of galaxies. He used H$\alpha$, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$. Using this power index, the Schmidt law can be rewritten as:

\begin{equation}
\Sigma_{SFR} \propto \Sigma_{gas}^{1.4\pm0.15}
\end{equation}
which is often referred to as the Kennicutt-Schmidt (KS) law.

In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution. For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$. He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$. He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
It should be noted that the KS law can not be applied for the whole range of gas densities. In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g. in regions far outside the optical disk \citep[e.g.,][]{Martin01, Bigiel08}

The Schmidt-Kennicutt scaling relation for star formation is valid for different types of galaxies both in the local universe \citep[e.g.,][]{Kennicutt98a, Bigiel08} and at high-Z \citep[e.g.,][]{Genzel10}, but it is strange that they only consider the effect of gas component while in reality various ISM and stellar objects affect the processes of formation of stars. Current proposed Schmidt relations, do not include the effects of metallicity \citep{Gnedin10}, dust grains, radiation shielding of H$_2$ regions \citep[for a review, see][]{Hollenbach99}, and stellar gravitational effects, as they only invoke the gas component.  Existing stars which form over the whole galaxy's life time are the reason for many of the processes mentioned above. As an example the gas angular momentum can be removed or nuclear SFRs can be increased by the gravitational effects of stellar bars in normal galaxies \citep[e.g.,][]{Sersic67}.

\cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density. Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges. \cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying on a large sample of galaxies. They showed this relation as a power law relation and referred to it as the extended Schmidt law:

\begin{equation}
\Sigma_{SFR} \propto \Sigma_{gas}^{\alpha} \Sigma_{star}^{\beta}
\end{equation}
where $\Sigma_{SFR}$ is SFR surface density, $\Sigma_{gas}$ and $\Sigma_{star}$ are gas mass and stellar surface density. $\alpha$ and $\beta$ are the power law indexes.  They showed that this relation not only predicts SFR as well as the KS law for galaxies and spatially resolved regions ($\sim$1 kpc sizes) where the KS law works, but also is acceptable for low surface brightness galaxies and regions where the KS law fails.

\begin{figure}[h]
\label{fig:duste}
\centering
\includegraphics[width=16cm]{../image_intro/schmidtvsextended}
\caption{Comparing The extended Schmidt law (a) and the Kennicutt-Schmidt relationship (b) for predicting the SFR. The solid and dotted lines are the best fit and observed 1-$\sigma$ scatter, respectively. The fit to the KS law (right panel) is done excluding LSB and early type galaxies. Adapted from \cite{Shi11}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%chapter: current work
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Current issues and the Present Project}
\label{chap:mp}
Studying formation of stars helps us understand the formation and evolution of the universe. Since forming stars contains many complex physical processes, theoretical studies cannot yet give a complete picture of star formation. Therefore empirical studies are used to find scaling laws indicating, which parameters have effects on star formation. Between different scaling relations for star formation, the KS law is the most tested empirical star formation law. Since 1959, many studies have tested KS law on regions inside the Milky Way, nearby galaxies and high redshift galaxies. Not only observational studies, but also  simulations both apply and investigate KS law. Despite all these studies, there are still many unsolved questions about the KS law; Is it really a good correlation? What is the slope, and is it unique?, Does SFR surface density only scale with gas density? does the scatter affect by a second parameter(s)? What is the limit for applying the KS law? Is the SFR surface density correlation with total gas density stranger than with the H$_2$ surface density alone?

Many groups are studying the KS law from different approaches to answer the questions listed in above. The extended Schmidt law is a newer version of the KS law, which by considering the effect of old stellar population on the SFR provides stronger correlation for the SFR than the other scaling laws. Although in original paper this law is tested on large sample of various types of galaxies, but further studies are necessary, due to the fact that this law is tested on the total SFR and not on different regions on galaxies to determine effect of environment on the SFR. In this project, the extended version of the Schmidt law will be tested on the Andromeda galaxy using both pixel by pixel relation and radial average along the disk. To due so star formation rate will be measured using equations~\ref{equ: halphaplus24} and ~\ref{sfr_tot_IR}. In order to find the gas surface density, direct method to map the ISM is chosen. Stellar surface density will be calculated by calibrations from both \cite{Eskew12} and \cite{Zhu10}.

The Andromeda galaxy is chosen for this project due to its similarity in the structure to the MW. Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "€œglobal"€ picture, whereas, studies of the MW are limited by our location within the Galaxy.  The Andromeda is closest spiral galaxy to the MW, therefore, we can have higher resolution images of it than we have of any other spiral galaxy. Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law. The KS law has been tested on the Andromeda galaxy many times but the results have been controversial. The range of slope of KS law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10, Ford13}. Testing extended Schmidt law on the Andromeda galaxy would help us recognise parameters that affect the star formation in the Andromeda galaxy and leads us to model and simulate star formation more accurately. Also it helps us answer questions about in what types of the regions (e.g. in case of different surface brightness, metallicity, distance from the disk, etc.) effect of the stellar mass is more important.

### 2016-06-11 version0.0/paper1.tex
Initial ShareLaTeX Import

\chapter[Star formation laws in M31]{Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}

\section{Introduction}
\label{sec: intro_sfl}
%P1: Star formation laws and why they are important (introducing K-S law and E-S law)

Understanding the underlying processes of formation of stars is a necessary step for explaining the formation and evolution of galaxies from the early universe to the current epoch, as well as the origin of planetary systems. Stars form when molecular cloud cores collapse; however, a complete picture explaining the physical processes involved in the formation of stars is yet to emerge. Various phenomena trigger the collapse of molecular clouds and star formation including the environment of the star-forming region, gas accretion and cooling, H$_2$ formation, the initial mass distribution and chemical compositions of the gas,  existence of dust, and other quantities in a galaxy. The physical processes leading to the formation of stars are naturally complex. Therefore, the basis for a theory of star formation requires a strong foundation of empirical data and/or observations.

The first attempt at scaling the star formation rate was to find a relation between the total star formation rate (SFR) and the mass of interstellar gas. \citet{Schmidt59} proposed a power-law relation between SFR and the gas mass ($M_{\rm gas}$) with {\it N} as the power law exponent. Since then, for more than 50 years empirical star formation laws (relations) have been investigated using both observational data and numerical simulations. Later, \citet{Kennicutt98a} examined H$\alpha$, H\,{\sc I}, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies. He showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with a power-law exponent of $1.4 \pm 0.15$. Using this power-law index, the Schmidt law can be rewritten as:

\begin{equation}
\label{equ:ks_org}
\eqsigmasfr \propto \eqsigmagas^{1.4\pm0.15},
\end{equation}
\noindent which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is the surface density of star formation, and \sigmagas is the surface density of gas in a galaxy. Moreover, \citet{Kennicutt07} investigated the K-S law in spatially resolved regions (0.5--2~kpc across) in the spiral galaxy M51. To calculate the SFR, they used a combination of 24~$\mu$m and H${\alpha}$ emission, and for the gas surface density, a constant conversion factor for CO to H$_2$ was applied. They showed that the K-S law also holds locally in this galaxy, and found {\it N} to be $1.56 \pm 0.04$.

The K-S law was applied to different types of both local and high-redshift galaxies \citep[e.g.][]{Boissier07,Kennicutt07, Bigiel08, Freundlich13}, but the results were never precise. Low gas density regions ($ < 1-10$~M$_{\odot}$~pc$^{-2}$), such as regions outside disks of galaxies, are an example of the regions for which the K-S law fails. The calculated SFR for these regions is much lower than the value predicted by the K-S law \citep[e.g.][]{Martin01, Bigiel08}. Using different instability models, \citet{Hunter98} showed that in low surface brightness galaxies, the current star formation activity correlates with stellar mass density. Furthermore, a correlation between the star formation rate and the stellar mass density was measured in many studies using both observational data and numerical simulations \citep[e.g.][]{Hunter04,Leroy08,Krumholz09,Shi11,Kim11,Kim13}. 
Studying a large sample of galaxies, \citet{Shi11} found a close relationship between stellar mass surface density, SFR and gas surface density.  They showed this relation as a power law and referred to it as the extended Schmidt law:
\footnote{\citet{Shi11} introduced the extended Schmidt law as a power-law relation between the star formation efficiency (surface density of SFR per surface density of gas, SFE) and $\eqsigmastar$, but to be consistent with equation~\ref{equ:ks_org}, we are using equation~\ref{equ:es_org}, which is equation 5 in their paper.}

\begin{equation}
\label{equ:es_org}
\eqsigmasfr \propto \eqsigmagas^{\eqnprime} \eqsigmastar^{\beta},
\end{equation}
\noindent where \sigmasfr is the SFR surface density while \sigmagas and \sigmastar are the gas mass and stellar mass surface densities,  $\eqnprime$ and $\beta$ are the indices found by \citet{Shi11} to be $1.13 \pm 0.05$ and $0.36\pm0.04$, respectively, in the global case. By testing this relation in sub-kiloparsec resolution regions in 12 spiral galaxies, they showed that the extended Schmidt law works just as well as the K-S law in spatially resolved regions ($\sim$1 kpc). Furthermore, they found the power-law indices for the local regions to be $\eqnprime = 0.80 \pm 0.01$ and $\beta = 0.63\pm0.01$, and concluded that this law is acceptable for low surface brightness galaxies and regions where the K-S law fails.

%P5: How to measure it
A galaxy's metallicity is another physical quantity that likely plays a role in the rate of star formation. However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications. There are many studies on correlation of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Lilly13}. These studies suggest that metallicity has a critical role in the formation of H$_2$ gas. Thus there should be a correlation between metallicity and the SFR. \citet{Krumholz09} introduced a theoretical SFR law which suggests that the SFR and metallicity of galaxies have a power-law correlation, but the power-law index changes with the amount of total gas. 
 Using results obtained from both observations and analytical models, \citet{Mannucci10} and \citet{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a 'fundamental metallicity relation'. They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation. It should be noted that the above two correlations are only valid in the global case. However, \citet{Leroy08} showed that the SFR as measured by combining far-UV and 24$\mu$m emission does not change with changing metallicity. \citet{Roychowdhury15} argued that in nearby spiral galaxies effect of metallicity on the SFR calculation is smaller than the calibration errors and can be ignored. On the other side, \citet{Boissier03} showed that metallicity has an inverse correlation with CO-H$_2$ conversion factor. Therefore, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas mass, and in low metallicity it leads to an underestimation.

%P2: SFR, measuring, scaling, ...
In order to investigate star formation laws, the first step is to calculate the SFR. Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}. \citet{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.][]{Bruzual93}. Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands. \citet{Kennicutt09} and \citet{Hao11} introduced new SFR calibrations using a combination of \halpha or far-ultraviolet (FUV) and far-infrared (FIR) emission. In addition to using suitable calibrations for each region, considering the differences between the global and the local ($\sim 0.5-1$~\kpc) cases is important. In $\S$~\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.

%P3: Gas cloud, variety, observing etc
Calculating the surface density of gas is the next step in testing star formation laws.
Considering the effect of the interstellar medium (ISM) is essential in understanding star formation laws since stars are born from gas and also release their material into the ISM when they reach the end of their evolution. 
A map of the total gas in the ISM is produced by direct observations of the gas or by using interstellar dust as a tracer. Neutral and molecular hydrogen are the most common elements in the ISM. Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements. 
Calculations of the gas surface density for the Andromeda galaxy are shown in $\S$~\ref{sec:ISM}.

%P4: Stellar mass and how to measure it
Additionally, for testing the Extended Schmidt law, measuring the stellar mass density is necessary. Measuring the mass of stellar populations is indirect and subject to significant uncertainties. One method to calculate the stellar mass within a galaxy is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09}. These models are used to connect stellar mass to an observable quantity such as luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
Having various methods to measure stellar mass helps to compare the results and determine whether there are any systematic differences. 
\citep{McLaughlin05} found differences between methods to be on the order of a few tens of percent and concluded that one should be careful to model subtleties.
Section $\S$~\ref{sec:starmass} describes our calculations of stellar mass in the Andromeda galaxy.

%P6(2*): What we did and why Andromeda
In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31). Additionally, we applied these two laws on three different regions in M31 to determine whether there is any dependence on distance from the centre of the galaxy. Since M31 is the nearest spiral galaxy to our own, high resolution images of this galaxy are available, providing data from various regions with different physical properties (e.g. metallicity, surface brightness, gas density). This inside look helps us test star formation laws in diverse physical conditions. Thus M31 is a suitable testbed for studying scaling laws.

Furthermore, the range of power-law indices calculated for the Andromeda galaxy using the K-S law is between 0.5 and 2 \citep[e.g.][]{Tabatabaei10,Ford13}. The use of different methods and data results in measuring different values for the power-law index. In a recent study of the K-S law in M31, \citet{Ford13} tested this law on six annular regions using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus H\,{\sc I}, and total gas calculated from dust emission). The measured power-law indices for each map and region vary between 0.6 to 2.03. The origin of these variations in the results is still an open question. It is unclear whether it depends on galactocentric distance, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law not working in M31. In order to examine the dependence of the results on the fitting method, we also applied a new statistical method, instead of the Ordinary Least Squares (OLS) fitting which is more commonly used in the literature to test the K-S law ($\S$~\ref{sec:fitting}).

%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
\section{Data}
\label{sec: data_sfl}
Being the closest large galaxy to the Milky Way, M31 has extensively been studied using both ground- and space-based telescopes. Therefore, large datasets on M31 exist spanning from gamma-ray to radio wavelengths, allowing us to measure all the required parameters to test star formation laws in this galaxy. Table~\ref{table:data} lists the data we used in this paper. Each dataset comes with a different angular resolution and pixel size. In order to match the images at different wavelengths, we smoothed the maps to the same FWHM using the kernel library and convolution code of \citet{Aniano11}. Our final results have two different angular resolutions depending on which gas tracer we use in studying the SFR laws. For studying the correlations between the SFR and molecular gas, our maps have the same resolution and pixel size as the $^{12}$CO(J:$1\rightarrow0$) data, while for investigating the relationships between the SFR and atomic gas (or total gas), we smoothed and re-gridded our maps to the resolution and pixel size of the atomic gas map.

\begin{table*}
\centering
\caption{Data used in this study.}
\label{table:data}
\begin{tabular}{@{}lcccc}
\hline\hline
Wavelength & FWHM & Coverage area &Telescope
& Ref. \\
\hline
%500 \um & 36\arcsec & $Herschel$ & \citet{Fritz12} \\
%250 \um & 18\arcsec.2 & $Herschel$ & \citet{Fritz12} \\
1550~\AA & 4\arcsec.5 & 5\degr $\times$ 5\degr &GALEX & \citet{Martin05}\\  
2250~\AA & 6\arcsec & 5\degr $\times$ 5\degr &GALEX & \citet{Martin05}\\
6570~\AA  & 1\arcsec & 2\degr.2 $\times$ 0\degr.6 &KPNO& \citet{Massey07}\\
3.6~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \citet{Barmby06} \\ 
8~\um & 1\arcsec.9 & 3\degr $\times$ 1\degr &\Spitzer & \citet{Barmby06} \\ 
24~\um & 6\arcsec & 3\degr $\times$ 1\degr &\Spitzer & \citet{Gordon06} \\ 
70~\um & 18\arcsec & 3\degr $\times$ 1\degr &\Spitzer & \citet{Gordon06} \\
160~\um & 12\arcsec & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \citet{Fritz12} \\
350~\um & 24\arcsec.9 & 3\degr $\times$ 1\degr &\Herschel & \citet{Groves12} \\
2.6~mm & 23\arcsec & 2\degr $\times$ 0\degr.5 &IRAM 30-m & \citet{Nieten06}\\
21~cm & 60\arcsec $\times$ 90\arcsec & 5\degr.2 $\times$ 1\degr.5 &DRAO & \citet{Chemin09}\\
\hline
\end{tabular}
\end{table*}

Several different observational datasets are used to compute properties of M31 for testing star formation laws.
One method for calculating the SFR uses FUV emission as a tracer of the star-forming regions: for this we
use the FUV image of M31 as observed by the Galaxy Evolution Explorer \citep[GALEX;][]{Martin05}. 
A second method to calculate the SFR involved using a combination of \halpha and 24~$\mu$m emission. \citet{Massey06, Massey07} mapped M31 in broad and narrow bands, including \halpha, as part of the Nearby Galaxies Survey using the KPNO 4-m telescope. A detailed description of how our \halpha map was made can be found in Appendix~\ref{app:halpha}.

%\subsection{IR and sub mm Data}
Calculations of the SFR using the total infrared emission requires observations at 8, 24, 70, and 160~\um, made
with the {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes. 
Observations with the Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8~\um); IRAC observations of M31 were obtained by \citet{Barmby06}, covering a region $3\degr.7 \times 1\degr.6$. 
The Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 70, and 160 \um and covered a region $\sim 3\degr \times 1\degr$ \citep{Gordon06}. {\em Herschel} observations of M31 were made with with PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10}  at 100 and 160~\um and SPIRE  \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} 
at 250, 350, and 500~\um, covering a region  $\sim 5\degr.5 \times 2\degr.5$ \citep{Fritz12}.
The IRAC 8, MIPS 24, MIPS 70, and PACS 160 images were used to calculate M31's total infrared emission. 
The IRAC 3.6~\um band image was used to calculate the stellar mass.

%\subsection{Radio Emission}
Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium. This map covers a $2\degr \times 0\degr.5$ region with an angular resolution of $23\arcsec$ and has the smallest coverage of the galaxy among the maps we used in this paper. In this study, we also used a 21-cm emission map of the atomic gas (H\,{\sc I}) in M31 from \citet{Chemin09}. This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a $5\degr.1 \times 1\degr.5$ region with an angular resolution of $60\arcsec \times 90\arcsec$.

\section{Measuring the components of Star Formation Laws}
Before studying the star formation laws, we need to calculate the components of these laws. We used different data and calibrations to produce the SFR maps, the stellar mass surface density and the gas mass surface density. In this section we describe how we measured each ingredient using available data, and calibrations. To use these calibrations, we assumed the M31 distance to be 0.78~Mpc~\citep{McConnachie05}. The ``total'' values recorded in this paper are integrated out to a distance of~25~kpc from the centre of the galaxy along the major axis.

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
Stellar population synthesis models make different assumptions about the IMF, often either \citet{Salpeter55},
$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or 
\citet{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$ for higher mass.
For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars. Different predictions of the number of stars between various IMFs are one of the main uncertainty sources in the calculation of the stellar mass \citep{Eskew12,Brewer12}. \citet{Eskew12} showed that the total mass of low-mass stars can change by a factor of 2.5 depending on the IMF.
\citet{Calzetti13} showed the impact of different IMF assumptions on SFR calibrations. Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators. Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\sun$.

In this project we used values based on the Kroupa IMF as is standard in the field, although discussion continues on whether the IMF is universal \citep{Bastin10}. Where necessary we converted from calibration values based on the Salpeter IMF by multiplying by 0.67  \citep{Madau14}.

%----------------------------------------------------------------------------------------
%STAR FORMATION RATE
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\subsection{Star Formation Rate}
\label{sec:sfr}
\subsubsection{FUV plus 24~$\mu$m Star Formation Rate}

Our first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \citet{Hao11}. Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}. The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}. However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction. On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars. This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}. The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the \citet{Kroupa03} IMF as:
\begin{equation}
\label{equ: fuvplus24}
SFR =4.46\times10^{-44}[L(FUV)_{\rm obs}+3.89L(24\mu m)],
\end{equation}
\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\rm obs}$ are in erg~s$^{-1}$. L(FUV)$_{\rm obs}$ is the luminosity of the galaxy in the FUV. The subscript "obs" indicates that the FUV emission is not corrected for extinction. Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \citet{Leroy08}. We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission. This process results in masking about 3\% of the pixels within a 25 kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR. 
Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map. We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$. The reported uncertainty for the total SFR only considers the values we measured and does not include uncertainties related to the masked pixels.

\begin{figure*}
    \centering
       \includegraphics[width=164mm]{../image_paper1/sfr_fir.eps}
    \caption {SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}). The SFR map here has an angular resolution of 18\arcsec and pixel size of 9.85\arcsec, the same as the MIPS 70 $\mu$m map.}
    \label{fig:sfrs}
\end{figure*}

\subsubsection{\halpha plus 24 \um Star Formation Rate}
\label{sec:sfr_halpha}

The SFR can also be calculated using a combination of \halpha and \Spitzer  24 \um maps. \halpha emission of galaxies is dominated by light emitted from young and massive stars. Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}. Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}. However, \halpha emission is very sensitive to dust extinction. Therefore, the combination of the \halpha and 24\um of considered a better choice for calculating the SFR. We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
\begin{equation}
\label{equ: halphaplus24_g}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24\mu m)],
\end{equation}
\noindent where L(H${\alpha}$)$_{\rm obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$. It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.

\citet{Calzetti07} introduced a new calibration using the same bandpasses for the case of local regions:
\begin{equation}
\label{equ: halphaplus24_l}
SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)],
\end{equation}
\noindent where the units here are the same as in equation~\ref{equ: halphaplus24_g}. Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc and is what we used for testing the SFR laws in local regions. The total M31 SFR calculated from summing pixel values and applying equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\sun$~yr$^{-1}$, which is in good agreement with previous studies.

\subsubsection{Total Infrared Star Formation Rate}
\label{sec:sfr_fir}
The total infrared emission of a system can also be used as a tracer of the SFR. Dust absorbs radiation from hot and young stars and re-emits it at infrared wavelengths; however, there is no one-to-one mapping between IR and UV emission. Therefore, integrating over the full wavelength range of the IR part and calculating the TIR luminosity is a better tracer of the SFR compared to IR single-band emission \citep{Calzetti13}. \citet{Calzetti13} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$, and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over 100 Myr:
\begin{equation}
\label{equ:sfr_fir}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR),
\end{equation}
\noindent where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$, respectively. Part of the dust emission in galaxies (specially in M31) comes from dust heated by the cosmic background radiation \citep[e.g.][]{Dole06, Calzetti13, Mattsson14}, hence, using equation~\ref{equ:sfr_fir} slightly overestimates the SFR in M31.

Total infrared luminosity can be measured from the integration of the infrared part of a galaxy's spectral energy distribution or by combining photometric data at different IR wavelengths. As an example of the second approach, \citet{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity. \citet{Boquien10} tested and modified this calibration as:
\begin{equation}
 \label{equ: TIR}
L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160),
\end{equation}
\noindent where L(8), L(24), L(70), and L(160) are the luminosities of the galaxy at 8 $\mu$m, 24~$\mu$m, 70~$\mu$m, and 160~\um in units of erg~s$^{-1}$. We used results from equation~\ref{equ: TIR} in the equation~\ref{equ:sfr_fir} to calculate our final map of the M31 SFR (Figure~\ref{fig:sfrs}). Using this method, we calculated the total SFR by adding all the pixels to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$. Table~\ref{table:sfr} compares recent measurements of the total SFR of M31 from the literature and the present work.

\begin{table*}
\begin{minipage}{100mm}
\caption{Comparison of the total star formation rate of M31}
\label{table:sfr}
\begin{tabular}{@{}lcc}
\hline\hline
Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
\hline
Current work&FUV and 24~$\mu$m&0.31 \\
Current work&\halpha and 24~$\mu$m&0.35 \\
Current work&TIR luminosity&0.4\\
\citet{Ford13}&FUV and 24~$\mu$m&0.25\\
\citet{Ford13}&TIR luminosity&0.48-0.52\\
\citet{Azimlu11}& \halpha and 24~$\mu$m&0.34\\
\citet{Azimlu11}&Extinction-corrected \halpha&0.44\\
\citet{Tabatabaei10}&Extinction-corrected \halpha&0.27--0.38\\
\citet{Barmby06}&Infrared 8\um luminosity& 0.4\\
\hline
\end{tabular}
\end{minipage}
\end{table*}

%----------------------------------------------------------------------------------------
%ISM
%----------------------------------------------------------------------------------------

\subsection{Gas Surface Density}
\label{sec:ISM}

The molecular form of hydrogen is very difficult to detect. Therefore, CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][]{Sanders84}. Higher rotational transitions of CO can be used as tracers as well; however, they are not as common as $J(1\rightarrow 0)$. Equation~\ref{equ:conversion} shows the relation between CO emission and H$_2$ column density:
\begin{equation}
\label{equ:conversion}
\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/[{\rm K km s^{-1}}],
\end{equation}
\noindent where X$_{CO}$ is the conversion factor (also known as the X-factor), I$_{CO}$ is the CO intensity in  K~km~s$^{-1}$ and N$_{H_2}$ is the molecular hydrogen column density. The X-factor could be different in regions within a galaxy due to varying metallicity \citep{Wilson95, Bosselli02, Bolato13}. In the case of M31, different values of X-factor in the range of ($1-5.6 \times 10^{20}$) were adopted in previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant difference in X-factor leads to horizontal changes in a plot of log(SFR) versus log($\Sigma_{\rm {gas}}$) and does not affect our power-law indices for molecular gas, we chose $X_{\rm {CO}}= 2 \times 10^{20}$. This is the same value that is adopted in many other works \citep[e.g.][]{Ford13, Smith12}. Since H\,{\sc I} mass dominates over the H$_2$ mass in M31, the constant X-factor has a negligible effect on the total gas mass.

To calculate the mass of H$_2$ from the molecular hydrogen column density, we estimated the volume and volume density of H$_2$ in each pixel. Then, using M$_{H_2} = \mu_{H_2}m_H\rho_{H_2}$ where $ \mu_{H_2}$ is the mean molecular mass of H$_2$, m$_H$ is the mass of one hydrogen atom and $\rho_{H_2}$ is the volume density, we calculated M$_{H_2}$.

The total gas mass was calculated from:
\begin{equation}
\label{equ:total_gas}
\rm M_{\rm \bld {total \, gas}} = 1.36[M_{\rm H I}+M_{H_2}],
\end{equation}
\noindent where the factor of 1.36 is a constant that takes into account the contribution of He and other heavier elements to the total gas mass, M$_{\rm H\,{\sc I}}$ is the mass of neutral hydrogen that was obtained from 21 cm observations (the map, which we got from \citet{Chemin09}, has units of number density which we used to calculate mass density of H\,{\sc I}), and M$_{H_2}$ was calculated from equation~\ref{equ:conversion} in units of M$_{\sun}$/pc$^2$. We assumed a gas mass of zero for regions where data for  either M$_{\rm H\,{\sc I}}$ or M$_{H_2}$ was not available, due to differences in coverage or bad pixels, etc. In this case the above equation gives a lower limit for the total gas; this applies to regions beyond 18~kpc from the galaxy centre.

%----------------------------------------------------------------------------------------
%STELLAR MASS
%----------------------------------------------------------------------------------------
\subsection{Stellar Mass}
\label{sec:starmass}
\begin{figure*}
\centering
\includegraphics[width=164mm]{../image_paper1/star.eps}.
\caption{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
\label{fig:stellarmass}
\end{figure*}

Emission in near-infrared bands, such as 3.6~$\mu$m, 4.5~\um and $K$-band, is almost insensitive to emission from young stellar populations, dust absorption and emission, which makes these bands good tracers of the mass of older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.We calculated the stellar mass within M31 using a calibration of the 3.6 \um flux by \citet{Eskew12}. They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
\begin{equation}
\label{equ:eskew}
M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
\end{equation}
\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is the 3.6~\um flux in Jy, and $D$ is the distance to the galaxy in Mpc. This calibration is based on the \citet{Salpeter55} IMF. Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf}). We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission. We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $F_{3.6 \mu m}$ and $F_{4.5 \mu m}$, though this was not mentioned in the aforementioned paper. 
Figure~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image. Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$. The replaced pixels include less than 8\% of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1\%.
Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6\%. This result is in fairly good agreement with the results of \citet{Tamm12}. They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56\% of which is in the disk with the rest in the bulge of the galaxy. In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.

%----------------------------------------------------------------------------------------
%Metallicity
%----------------------------------------------------------------------------------------
\subsection{Metallicity}
\label{sec:metal}

The metallicity of a galaxy can be estimated by measuring abundances of heavier elements in its ISM. 
It is common to use  gas phase oxygen abundance, $[{\rm O/H}]$, as a gauge to determine metallicity \citep[e.g.][]{McGaugh91, Zaritsky94}. 
Results from modelling dust in the Milky Way and nearby galaxies showed that the dust to gas mass ratio depends on $[{\rm O/H}]$ and, consequently, on metallicity \citet{Draine07}. \citet{Draine14} assumed that depletion of gas elements from the gas to the diffuse ISM in M31 is similar to the Milky Way, and proposed that: 
 \begin{equation}
 \label{equ: metal}
\frac{M_d}{M_H}=0.0091 \frac{Z}{Z_{\odot}},
 \end{equation} 
\noindent where M$_d$ and M$_H$ are the total masses of dust and hydrogen, $Z$ is the metallicity of M31 and $Z_{\odot}$ is solar metallicity.

\citet{Draine14} produced two dust maps of M31 using MIPS-160 resolution (FWHM  39\arcsec; 18\arcsec $\times$ 18\arcsec pixels) and SPIRE 350 resolution (FWHM 24\arcsec.9; 10\arcsec $\times$ 10\arcsec pixels), which are publicly available. 
We used the dust map with SPIRE 350 resolution, convolved and re-gridded  to have the same resolution and pixel size for the H\,{\sc I} map, then divided this dust mass by the mass of hydrogen in M31. 
However, in a private correspondence with the author, Draine pointed out that based on the Planck observations of Milky Way dust \citet{Tauber10}, the dust mass surface density map estimated for M31 by \citet{Draine14} may be systematically high by a factor of 2. We divided our dust map by 2 to account for this correction. 
We then generated a metallicity map of M31 by using the dust map in combination with equation~\ref{equ: metal}. \citet{Draine14} showed that with increasing distance from the centre of M31, the dust to H mass ratio declines monotonically and concluded that metallicity also behaves in the same way. 
Their fitting results showed that M31 can be divided into three regions ($R< 8~\kpc$, $8~\kpc < R < 18~\kpc$, and $18~\kpc < R \la 25~\kpc$) where the dust to H mass ratio (or metallicity) has a different correlation with galactocentric distance.

%----------------------------------------------------------------------------------------
%SFR LAWS
%----------------------------------------------------------------------------------------
\section{Scaling the star formation rate}
\subsection{Fitting method}
\label{sec:fitting}

%=164mm, height=218mm
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../image_paper1/ks_all_density.pdf}
\caption{Results from fitting the Kennicutt-Schmidt law to data from the whole galaxy using the pixel-by-pixel method. The colour represents the density of the pixels, increasing from blue to red. The number of points among the three columns is different due to the different angular resolution of the H\,{\sc I} and H$_2$ maps. Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\sc I} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of $60\arcsec \times 90\arcsec$). Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
\label{fig:ks_all}
\end{figure*}

Producing the SFR, gas mass, stellar mass, and metallicity maps provides enough data to examine and compare the K-S law and the extended Schmidt law. To create surface density maps, we divided the value of each pixel by its area in pc$^2$. We investigated the K-S law and the extended Schmidt law using the pixel-by-pixel method in two ways. In one approach we used all the available pixels over the galaxy; in  the other approach we compare the laws in three elliptical regions at different distances from the centre of the galaxy as described in Section~\ref{sec:metal}, assuming a position angle of 38\degr and inclination of 77\degr\ for M31.
As mentioned in Section~\ref{sec: data_sfl}, since the H$_2$ gas mass map has higher angular resolution and smaller pixel size than the H\,{\sc I} gas mass map, our final results have two sets of different  angular resolutions and pixel sizes.

Equations~\ref{equ:ks_org}~and~\ref{equ:es_org} can be re-written in logarithmic form to obtain two linear equations:
\begin{subequations}
\begin{equation}
\label{eq:sfr_law_ks_log}
\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A,
\end{equation}
\begin{equation}
\label{eq:sfr_law_es_log}
\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime,
\end{equation}
\end{subequations}
\noindent where, {\it N}, $\eqnprime$, $\beta$, A, and A$^\prime$ are free fitting parameters. The units in the above equations are the same as those in equations~\ref{equ:ks_org} and ~\ref{equ:es_org}.

We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \citet{Shetty13}. Shetty and colleagues used a Bayesian linear regression approach in a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
We used the same technique as \citet{Shetty13} to estimate the K-S law parameters. For the extended Schmidt law, we extended the code such that instead of using  simple hierarchical Bayesian linear regression, which is used for the K-S law, it uses multiple hierarchical Bayesian linear regression. In this case, we were able to examine the effect of stellar mass on the SFR as shown in equation~\ref{eq:sfr_law_es_log}.

Uncertainties in the SFR and stellar mass maps  were measured following the method described in \citet{Kennicutt07}. We used the quadratic sum of the variance of the local background for each luminosity map from the original pixel size images, Poisson noise of images, and calibration uncertainties. Note that this method measures the lower limit of the uncertainties for these variables. Uncertainties in H$_2$ mass were measured using the mean rms values of the  CO intensity, reported in \cite{Nieten06}. Uncertainties of the total gas map are calculated as the quadrature sum of the uncertainties in  H$_2$ and H\,{\sc I} masses.

We also tested each law on three different regions which were chosen in the same manner as explained in Section~\ref{sec:metal}. Applying the SFR laws in these regions provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws such as metallicity, gas mass, stellar mass gradients and changing the ratio of H$_2$ to H\,{\sc I}.

\subsection{Star formation laws}
\label{sec: sfl}

We made three SFR maps, three gas mass density maps and a stellar mass density map of the whole galaxy. We applied both laws on the whole galaxy using each combination of SFR and gas mass density tracer, along with applying the laws on three different regions. \citet{Kennicutt12} reviewed star formation in the Milky Way and nearby galaxies and described that there might be a breakdown of SFR laws for small size regions. Therefore, we re-gridded all the maps to have a pixel size equivalent to 750~pc, and repeated all of our processes on these new maps (Table~\ref{table:res750}). Additionally, we used these results to see if there is any correlation between the SFR laws and metallicity, as will be described in Section~\ref{sec:fittingmetal}.

\begin{figure*}

\includegraphics[width=168mm , height=230mm]{../image_paper1/Results_all_3_regs_after_err_co.pdf}
\caption{Same as figure~\ref{fig:ks_all}, but in this figure we separated pixels from different regions in the galaxy by their colours. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}%%
\label{fig:ks,regs}
\end{figure*}

Figure~\ref{fig:ks_all} shows the pixel-by-pixel fitting of the K-S law on the whole galaxy. The first row of plots are the surface density of the SFR(TIR), which is calculated using the TIR emission from Section~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$), only atomic gas (H\,{\sc I}), and total gas from right to left, respectively. 
The only difference between the upper and the other rows is that in the lower rows the SFR indicator is FUV plus 24~$\mu$m (second row), and \halpha plus 24~$\mu$m emission (third row). Figure~\ref{fig:ks,regs} shows the same data as Figure~\ref{fig:ks_all}. However, in this figure we separated pixels from different regions in the galaxy by their colours. 
 There is a deviation in the middle panel plots of Figure~\ref{fig:ks_all} which shows a set of points with with high star formation rate and low H\,{\sc I} gas.
As can be clearly seen in middle panel of Figure~\ref{fig:ks,regs}, this deviation is due to regions within 8~kpc of the centre of the galaxy (red points).
 \cite{Braun09} saw a similar feature in their studies of the K-S law in M31. 
The H\,{\sc I} surface density profile of M31 \citep[see figure 16 in][]{Chemin09} shows several local minima from the centre of M31 out to 30~kpc distance which could be a result of the H\,{\sc I} wrap. The H\,{\sc I} surface density map shows a lower density in the central regions compared to the ring area; on the other hand, the SFR maps show high densities in the central regions. The combination of the relatively low gas and high SFR causes the deviation. However,~~\cite{Braun09} argued that the high 24~$\mu$m fluxes in the centre of the galaxy are due to other processes such as shock heating rather than a large amount of star formation.
Since the total gas mass is calculated by adding H\,{\sc I} and H$_2$ gas mass, we can see this deviation in the right panel of Figure~\ref{fig:ks_all} as well. However, since we have H$_2$ emission in those regions these deviations are less prominent than the ones in the middle panel.

We took a similar approach for the extended Schmidt law. Figures~\ref{fig:es,all,fuv,tot}-~\ref{fig:es,regs,fuv,tot} and Figures~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} show the results of the pixel-by-pixel fitting of the extended Schmidt law. For the extended Schmidt law, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly. In this series of plots, the $x$-axis is the gas mass surface density, either molecular gas (H$_2$), atomic gas (H\,{\sc I}), or total gas, the $y$-axis is the SFR(TIR), SFR(FUV + 24~$\mu$m) or SFR(H$\alpha$ + 24~$\mu$m), and the $z$-axis is the stellar mass surface density. The shadows of the data on each surface are also plotted, to have a more clear picture of correlations between components. The shadows on the $x-y$ surface are the same as in Figure~\ref{fig:ks_all}.

\begin{figure*}
        \centering
        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_tot2_f.png}
        \caption{The result from fitting the extended Schmidt law on the surface density of SFR(FUV + 24~$\mu$m), the surface density of total gas and the surface density of stellar mass ($z$-axis) from the whole galaxy. Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method. Equivalent plots for the other SFR and gas tracers are in Figures~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the appendix.}
        \label{fig:es,all,fuv,tot}
    \end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../image_paper1/color_3d_fuv_tot.png}
\caption{Fitting result for SFR(FUV + 24~$\mu$m) vs total gas. Same as Figure~\ref{fig:es,all,fuv,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
\label{fig:es,regs,fuv,tot}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../image_paper1/color_3d_tir_tot.png}
\caption{Same as Figure~\ref{fig:es,regs,fuv,tot}, but in this figure we use total infrared emission as a tracer of the SFR.}
\label{fig:es,regs,fir,tot}
\end{figure*}

\begin{table*}
\caption{ K-S law and Extended Schmidt law fitting results}
\label{table:res}
\begin{tabular}{ccccccccc}
\hline\hline
\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer & Gas Tracer & {\it N}    & A      & \nprime & $\beta$ & A$^\prime$ \\
\hline\hline
\multicolumn{1}{c}{\multirow{9}{*}{Whole Galaxy}} &TIR & H$_2$ only & 0.57 - 0.58 & -8.88 - -8.87  & 0.51 - 0.53  &  0.31 - 0.33 & -9.42 - -9.39  \\
& TIR               & HI only    & 1.13 - 1.19 & -9.71 - -9.69   & 0.76 - 0.79 & 0.74 - 0.75 & -10.58 - -10.56 \\
& TIR               & Total gas  & 0.73 - 0.75 & -9.85 - -9.84   & 0.46 - 0.48 & 0.53 - 0.55 & -10.40 - -10.38 \\
& FUV + 24\um       & H$_2$ only & 0.61 - 0.63 & -9.24 - -9.23   & 0.57 - 0.59 & 0.20 - 0.22 & -9.60 - -9.57   \\
& FUV + 24\um       & HI only    & 1.16 - 1.19 & -9.97 - -9.95   & 0.78 - 0.81 & 0.59 - 0.60 & -10.64 - -10.62 \\
& FUV + 24\um       & Total gas  & 0.67 - 0.70 & -10.10 - -10.09 & 0.42 - 0.44 & 0.43 - 0.45 & -10.51 - -10.49 \\
& H$\alpha$ + 24\um & H$_2$ only & 0.60 - 0.62 & -9.14 - -9.13   & 0.54 - 0.56  & 0.33 - 0.35  & -9.72 - -9.70 \\
& H$\alpha$ + 24\um & HI only    & 0.46 - 0.54 & -9.64 - 9.61    & 0.48 - 0.53 & 0.72 - 0.76 & -10.75 - -10.69 \\
& H$\alpha$ + 24\um & Total gas  & 0.48 - 0.51 & -9.85 - 9.82    & 0.32 - 0.35 & 0.54 - 0.58 & -10.59 - 10.54    \\
\hline
\multicolumn{1}{c}{\multirow{9}{*}{R$< 8\kpc$}} & TIR & H$_2$ only & 0.30 - 0.33  & -8.84 - -8.83 & 0.31 - 0.33 & 0.67 - 0.70 & -10.28 - -10.23  \\
 & TIR               & HI only    & 0.02 - 0.16  & -9.09 - -9.06 & 0.74 - 0.83 & 0.84 - 0.89 & -10.83 - -10.73 \\
 & TIR               & Total gas  & 0.20 - 0.24  & -9.22 - -9.18 & 0.28 - 0.30 & 0.70 - 0.73 & -10.70 - -10.63 \\
 & FUV + 24\um       & H$_2$ only & 0.37 - 0.41  & -9.22 - -9.21 & 0.26 - 0.32 & 0.43 - 0.46 & -10.01 - -9.96  \\
 & FUV + 24\um       & HI only    & -0.13 - 0.01 & -9.44 - -9.42 & 0.67 - 0.76 & 0.81 - 0.86 & -10.64 - -10.62 \\
 & FUV + 24\um       & Total gas  & 0.13 - 0.18  & -9.55 - -9.51 & 0.24 - 0.26 & 0.68 - 0.73 & -11.03 - -10.94 \\
 & H$\alpha$ + 24\um & H$_2$ only & 0.29 - 0.32  & -9.14 - -9.13 & 0.38 - 0.41 & 0.50 - 0.53 & -10.33 - -10.26  \\
 & H$\alpha$ + 24\um & HI only    & 0.00 - 0.10  & -9.26 - 9.24  & 0.48 - 0.53 & 0.61 - 0.64 & -10.51 - -10.44 \\
 & H$\alpha$ + 24\um & Total gas  & 0.13 - 0.16  & -9.34 - 9.32  & 0.18 - 0.19 & 0.50 - 0.53 & -10.41 - -10.35     \\
\hline
\multicolumn{1}{c}{\multirow{9}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 0.63 - 0.65 & -8.80 - -8.79   & 0.47 - 0.49 & 0.68 - 0.70 & -9.97 - -9.93   \\
 & TIR               & HI only    & 1.90 - 1.99 & -10.03 - -10.00 & 1.33 - 1.39 & 0.92 - 0.96 & -11.08 - -11.03 \\
 & TIR               & Total gas  & 0.76 - 0.79 & -9.89 - -9.87   & 0.55 - 0.58 & 0.53 - 0.58 & -10.70 - -10.63 \\
 & FUV + 24\um       & H$_2$ only & 0.66 - 0.68 & -9.16 - -9.15   & 0.54 - 0.56 & 0.54 - 0.57 & -10.12 - -10.08 \\
 & FUV + 24\um       & HI only    & 1.52 - 1.59 & -10.12 - -10.09 & 1.12 - 1.17 & 0.60 - 0.63 & -10.64 - -10.62 \\
 & FUV + 24\um       & Total gas  & 0.60 - 0.61 & -10.01 - -10.00 & 0.48 - 0.50 & 0.29 - 0.34 & -10.36 - -10.31 \\
 & H$\alpha$ + 24\um & H$_2$ only & 0.69 - 0.70 & -9.09 - -9.08   & 0.53 - 0.55 & 0.70 - 0.73 & -10.30 - 10.25  \\
 & H$\alpha$ + 24\um & HI only    & 1.28 - 1.35 & -10.00 - -9.95  & 0.64 - 0.76 & 1.17 - 1.26 & -10.51 - -10.44 \\
 & H$\alpha$ + 24\um & Total gas  & 0.62 - 0.65 & -10.04 - -10.01 & 0.39 - 0.43 & 0.75 - 0.85 & -11.04 - -10.91  \\
\hline
\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $\la 25\kpc$}} & TIR & H$_2$ only &  N/A$^a$ & N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$ \\
 & TIR               & H\,{\sc I} only    & 0.44 - 0.54 & -9.96 - -9.94  & 0.33 - 0.41    & 0.31 - 0.36    & -10.22 - -10.18     \\
 & TIR               & Total gas  & 0.44 - 0.54 &  -10.00 - -9.98  & 0.33 - 0.41  & 0.31 - 0.36    & -10.25 -10.21     \\
 & FUV + 24~$\mu$m       & H$_2$ only & N/A$^a$ & N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$    \\
 & FUV + 24~$\mu$m       & H\,{\sc I} only    & 0.65 - 0.72 & -10.18 - -10.16  & 0.59 - 0.67    & 0.17 - 0.22    & -10.33 - -10.29     \\
 & FUV + 24~$\mu$m       & Total gas  & 0.64 - 0.72 & -10.22 - -10.21  &  0.59 - 0.67   & 0.16 - 0.22    & -10.37 - -10.33     \\
 & H$\alpha$ + 24~$\mu$m & H$_2$ only &  N/A$^a$ & N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$     \\
 & H$\alpha$ + 24~$\mu$m & H\,{\sc I} only    & 0.48 - 0.97 &  -9.97 - -9.88  & 0.61 - 1.12    & -0.36 - -0.12    & -9.82 - -9.59     \\
 & H$\alpha$ + 24~$\mu$m & Total gas  & 0.40 - 0.90 & -10.01 - -9.95  &  0.53 - 1.03    & -0.35 - -0.11    & -9.82 - -9.59     \\
 \hline
\end{tabular}
\begin{tablenotes}
 \item $^a$  Since there are very few pixels which we can use for the fitting in this region we cannot provide a meaningful result.
\item Each entry shows the 95\% confidence range for the fitting parameter.
\item Fitting parameters of SF laws from applying the Bayesian method.  {\it N} is the power-law index of the K-S law; A is the intercept of the K-S law; \nprime is the gas power-law index in the extended Schmidt law;
 $\beta$ is the power-law index of the stellar component in the extended Schmidt law; and A$^\prime$ is the intercept of the extended Schmidt law.
\end{tablenotes}
\end{table*}

\begin{table*}
\caption{K-S law and Extended Schmidt Law fits for larger pixels}
\label{table:res750}
\begin{tabular}{cccccccc}
\hline\hline
\multicolumn{1}{c}{\multirow{1}{*}{Region}}  & Gas Tracer & {\it N} & A  & \nprime & $\beta$ & A$^\prime$ \\
\hline\hline
\multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
 & H$_2$ only & 0.26 - 0.31 & -10.00 - -9.91  & 0.21 - 0.26  & 0.26 - 0.40    & -10.51 - -10.30  \\
 & H\,{\sc I} only    & 1.08 - 1.24 & -11.60 - -11.36  & 0.73 - 0.85  & 0.58 - 0.64    & -11.74 - -11.60     \\
 & Total gas  & 0.66 - 0.73 & -10.11 - -10.06 & 0.39 - 0.46    & 0.41 - 0.49    & -11.56 - -10.47     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
 & H$_2$ only & 0.14 - 0.27 & -9.82 - -9.59  & 0.14 - 0.21   & 0.48 - 0.66   & -11.04 - -10.66      \\
 & H\,{\sc I} only    & 1.42 - 1.68 & -12.35 - -11.92 & 0.51 - 0.92    & 0.72 - 0.97    & -12.52 - -11.61     \\
 & Total gas  & 0.07 - 0.31 & -9.63 - -9.45  & 0.22 - 0.32    & 0.63 - 0.78    & -11.17 - -10.84      \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
 & H$_2$ only & 0.27 - 0.32 & -9.98 - -9.86  & 0.17 - 0.24    &  0.38 - 0.73   & -10.89 - -10.44       \\
 & H\,{\sc I} only    & 0.88 - 1.38 & -11.80 - -11.06 & 1.00 - 1.22    & 0.53 - 0.69    & -12.41 - -12.09     \\
 & Total gas  & 0.55 - 0.64 & -10.03 - -9.96 & 0.40 - 0.51    & 0.27 - 0.49    & -10.53 - -10.29     \\
\hline
\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $\la 25\kpc$}} 
 & H$_2$ only & N/A$^a$& N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$    \\
 & H\,{\sc I} only    & 0.46 - 0.81 & -11.21 - -10.80  & 0.44 - 0.76    & 0.13 - 0.36    & -11.35 -10.94     \\
 & Total gas  & 0.47 - 0.82 & -10.25 - -10.18 & 0.44 - 0.78    & 0.12 - 0.36    & -10.49 - -10.30     \\
 \hline
\end{tabular}
\begin{tablenotes}
\item Similar to Table~\ref{table:res} but here the fitting is performed on regions with a size of 750~pc, and we only show the results from SFR(FUV+24$\mu$m).
\end{tablenotes}
\end{table*}

%----------------------------------------------------------------------------------------
%
%----------------------------------------------------------------------------------------
\section{Discussion}

Table~\ref{table:res} shows the results of the hierarchical Bayesian fitting for the whole galaxy and all three regions. Considering the data and uncertainties for each parameter, we are 95\% confident that our fitting parameter is in the ranges given in Table~\ref{table:res}.
Our results suggest that changing the gas tracer has a more significant impact on the determination of the power law index than changing the SFR tracers. Therefore, we only discuss the results from SFR(FUV+24$\mu$m), and in Table~\ref{table:res750} we only show results from this SFR map.

\subsection{The K-S law in M31}

As mentioned before, the K-S law in M31 has been tested by many groups. In one of the most recent works on M31, \citet{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares fitting method. 
To make a meaningful comparison between our results and the results reported in \citet{Ford13}, we averaged the power-law indices in \citet{Ford13} with a certain annuli and compared to the results with the same annuli in ours. We calculated power-law indices to be in the case of the H$_{2}$-only gas $N \sim 0.35, 0.58, 0.68$ and in case of total gas, $N \sim 1.37, 2.05, 1.60$ for $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$, respectively.
\citet{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have some differences with results from \citet{Ford13}. \citet{Ford13} argued that the main reason for these differences is the cut-off they used to fit the data.

The whole-galaxy fit of the K-S law shows that using total gas or H$_{2}$-only gas gives a sub-linear relation between \sigmasfr and \sigmatotalgas. When using  H\,{\sc I}-only gas we find a nearly super-linear relation. These results are different from the power-law index estimated by \citet{Ford13}  in the case of total gas, $N=2.03\pm0.04$, but similar to their value of $N=0.6\pm0.01$ in the case of H$_{2}$-only gas. 
\citet{Tabatabaei10} estimated the K-S law power index as $N=1.30\pm0.05$ using total gas and $N=0.96\pm0.03$ using H$_{2}$-only gas. The reason behind these differences is mostly because of the statistical method we chose. The OLS fitting using H$_{2}$-only gas gives us a power-law index of $N=0.54\pm0.003$ which is close to the \citet{Ford13} results but still different fro \citet{Tabatabaei10}, perhaps for the same reason \citet{Ford13} suggested for the discrepancy between their results and results from \citet{Tabatabaei10}. We also noticed that different methods of measuring the uncertainties affect the power-law indexes, as well. The OLS fitting with \sigmatotalgas gives $N=0.74\pm0.003$, which is still lower than values in both  \citet{Tabatabaei10} and  \citet{Ford13}. Different methods in making the total gas map and using different criteria to choose outliers are the main reasons for this difference.

 \citet{Bigiel08} argued that there is no universal relationship between the surface density of the total gas and the SFR. They also showed that the SFR and the molecular hydrogen have a linear relationship. \citet{Shetty13} used the same data as \citet{Bigiel08} and argued that using the hierarchical Bayesian fitting leads to significant galaxy-by-galaxy variation between power-law indices with all of them being lower than those of \citet{Bigiel08}. Although some of our results in Table~\ref{table:res} showed a nearly linear correlation, we did not find any specific trend between power-law indices in the different regions.

The sub-linear power-law index in the case of the total gas or molecular gas surface density suggests that the star formation efficiency is decreasing as the total gas increases. Consequently, the depletion time increases. On the contrary, the super-linear relation suggests that the depletion time is decreasing with an increasing amount of H\,{\sc I} gas. The latter conclusion is more similar to the initial suggestion of the K-S law. If we assume that stars form in the molecular clouds, decreasing SFE with increasing total gas is justifiable.

The hierarchical Bayesian fitting on the $8<R<18$~kpc region gives similar values as the fitting to the whole galaxy data. This region contains the 10~kpc ring, which is where most of the star formation is happening, so it dominates the results from the whole galaxy.  For the other two regions, the K-S law fitting gives a sub-linear relation between the SFR and the gas surface density. A sub-linear relationship between \sigmasfr and  $\Sigma_{H_2}$ indicates that there are some CO-bright regions which do not associate with star forming regions.
 \citet{Krumholz09} showed that for regions with \sigmagas~$\leq 100$~M$_{\odot}$~pc$^{-2}$, \sigmasfr and $\Sigma_{H_2}$ have a nearly linear correlation. They also conclude that, at intermediate total gas column density, (\sigmagas~$\leq 100$~M$_{\odot}$~pc$^{-2}$), \sigmasfr and \sigmagas have a linear or slightly sub-linear correlation. The latter conclusion agrees with our results.

The K-S law power-law index varies with the distance to the centre of the galaxy. Similar to results from \citet{Ford13}, the power-law index considering molecular gas only increases with increasing distance from the centre of the galaxy. The power-law index using total gas or atomic gas does not show any particular correlation with distance. The increase of the power-law index while using molecular cloud only may be an effect of the decreasing metallicity across the galaxy or other physical properties of the galaxy such as stellar mass (see Section~\ref{sec:es_res}).

\subsection{The extended Schmidt law in M31}
\label{sec:es_res}
The extended Schmidt law has been a recently proposed law \citep{Shi11}, which shows a tight correlation between the SFR and the total gas surface density and the surface density of the stellar mass. Our results from fitting the whole galaxy shows a sub-linear relation between \sigmasfr and \sigmastar.
Using only atomic gas, $\beta$ is in good agreement with the original suggestion of the extended Schmidt law, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$. However, $\beta$ is much smaller in other two gas tracers. Using total gas mass, we find $\eqnprime$ to be very close to $\beta$. This relation suggests that, although increasing the total gas causes a decrease to the SFE, the existing stars will increase the SFE.

The fitting result on the $8<R<18$~kpc region (see Table~\ref{table:res}) is similar to that from fitting the whole galaxy together.  Taking the average $\beta$ from the atomic gas only fits gives us $\eqnprime \sim 0.79$ which is in good agreement with \citet{Shi11}, but $\beta = 0.53$  which is smaller than the original suggestion of the extended Schmidt law. However, the final indices reported by \citet{Shi11} for  the extended Schmidt law are an average over 12 different spiral galaxies, and some of their individual galaxies (e.g. NGC 4736, NGC 4726) have similar values as for M31.
Similar to the K-S law, the extended Schmidt law results are sensitive to the fitting method. Using the OLS fitting, one only will consider the SFR and stellar mass surface density errors, nevertheless, the hierarchical Bayesian regression fitting considers uncertainties on all the parameters.

Thus we can conclude that the SFR is higher in regions with higher stellar mass surface density than those with less stellar mass surface density.
In most cases this effect is almost as strong as the effect of gas surface density on the SFR.
\citet{Kim13}, using 3D numerical hydrodynamic simulations, showed that in the outer disk regions of a galaxy where the total gas is dominated by H\,{\sc I} gas, the SFR correlates with $\rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk plus dark matter. This is because in the outer regions of the disk, the gravity from stars dominates. 
We calculated the power index related to the stellar mass surface density to be 0.36 for these regions (Table~\ref{table:res750}) which is slightly different from their suggestion. Since we do not have enough H$_2$ data for regions within $18\kpc < R \la 25\kpc$, our results are limited to ones from the extended Schmidt law for H\,{\sc I} gas only. Therefore, we could neither confirm nor refuse this prediction.

\subsection{Metallicity}
\label{sec:fittingmetal}
It is well established that the metallicity of M31 is higher in the centre than it is in the outer disk  \citep[e.g.][]{Draine14}. The inverse correlation between metallicity and the X-factor, which was described in Section~\ref{sec: intro_sfl}, leads to an underestimation of the power-law indices from fitting the K-S law in the case of the molecular gas only and total gas. 
Thus a corrected power-law index of the K-S law is higher than shown in Table~\ref{table:res}. Another correlation between components of the SFR laws and metallicity was introduced by \citet{Krumholz09}. 
They found a new SFR law based on a correlation between SFR and metallicity, and suggested that this correlation strongly depends on the amount of total gas in galaxies. They also showed the SFR has a dependence on metallicity which we saw a weak correlation (Figure~\ref{fig:metal}).
 We estimated the SFR using \citet{Krumholz09} SFR laws for regions with size of $\sim$750~pc.
Using the mid value of metallicity, 1.65, and clumping factor of 1.2, We found that the SFR calculated using the Krumholz law is, on average, different by 45\% from the measured SFR(FUV + 24~$\mu$m) in this work.

In more recent studies, \citet{Mannucci10} and \citet{Lilly13} assumed the K-S law holds for their sample of local and high-redshift galaxies and obtained a correlation between metallicity and the stellar mass, the gas mass and the SFR. 
They found that increasing both the SFR and the stellar mass increases metallicity, but increasing the gas mass decreases metallicity (equation 9 in \citep{Mannucci10}). 
However, by considering results from \citet{wong13} regarding the dependence of the rate of H\,{\sc I}-H$_2$ conversion to metallicity, \citet{Roychowdhury15} showed that the K-S law is independent of metallicity in galaxies with H\,{\sc I} as a dominant gas.

In Figure~\ref{fig:metal}, we plot dust to gas mass ratio versus the SFR(FUV + 24~$\mu$m) and the stellar mass, and could not find any correlation over the scale of the whole galaxy.
We calculated the Pearson correlation coefficients between metallicity and SFR, and between metallicity and the stellar mass, and found them to be 0.08 and 0.04, respectively. 
However, in Figure~\ref{fig:metal}, we can see a correlation between metallicity and both SFR and stellar mass for regions within $R< 18\kpc$. These are weak correlations with Pearson correlation coefficients of $-0.58$ and $-0.46$ for the SFR case and the stellar mass case, respectively.
We cannot see any correlation in the data from $18\kpc < R \la 25\kpc$. The average metallicity uncertainty in this region is almost 10 times higher than the average uncertainty for the rest of the galaxy. This higher uncertainty obscures any tentative correlation between metallicity and SFR or stellar mass for from $18\kpc < R \la 25\kpc$.   
This analysis confirms that there is a correlation between metallicity and both the SFR/the stellar mass. Although we could not find any strong correlation between the SFR and metallicity, especially in outer disk regions, we should note that the effect of the metallicity on SF laws is ambiguous and more high resolution data is needed to solve this puzzle.

\begin{figure*}
\centering
\includegraphics[width=180mm]{../image_paper1/metal_with_errors.png}
    \caption{Left: the SFR(FUV + 24~$\mu$m) surface density versus gas/dust mass ratio surface density and right: Stellar mass versus gas/dust mass ratio surface density  shows the stellar mass. Each point shows a region with size of $\sim$750~pc. Typical uncertainties of the x-axes within 18~kpc are shown in upper right side of the plots. The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
    \label{fig:metal}
\end{figure*}

%----------------------------------------------------------------------------------------
%SUMMERY
%----------------------------------------------------------------------------------------
\section{Summary}
 We investigated the K-S law, the extended Schmidt law and the Krumholz law at both global and local scales in M31. We have determined the surface density of star formation rate, gas mass and stellar mass of this galaxy. Our three SFR maps in M31 use a combination of the FUV and 24~\um emission, a combination of the H$\alpha$ and 24~\um emission, and total infrared luminosity. We noticed that the H$_\alpha$ data available for M31 is not suitable for SFR studies (see appendix ~\ref{app:halpha}). We calculated the total SFR from FUV and 24 \um emission as 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$. We also produced the ISM map, using molecular gas only, atomic gas only and the total gas. Our main results are as follows:
\newline
1) The power-law index of the K-S law is mostly depended on which gas is used as a tracer of the gas mass in galaxy. Power-law indices are mostly independent of the SFR tracer.
\newline
2) Using different fitting methods gives different results. This dependence mostly comes from the way each fitting method handles the uncertainty on the star formation law parameters.
\newline
3) Although there is a correlation between \sigmasfr and \sigmagas, it is not the same in all regions in M31. The star formation laws predict more accurate results on regions with relatively higher star formation. 
\newline
4) We confirmed the suggestions of \citet{Shi11} that the surface density of stars has an impact on the SFR, and in regions with low gas surface brightness this impact is even more important. 
\newline
5) We performed statistical tests and found no correlation between the SFR, the stellar mass surface density and metallicity in the case of the whole galaxy. However there is a weak correlation between these quantities within 18~kpc of the centre of the galaxy.
\newline 
Obtaining images with higher resolution and maps with better coverage of this galaxy will enable continuation of these studies in finer detail.

### 2016-06-11 version0.0/paper2.tex
Initial ShareLaTeX Import

\chapter[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction}
\label{sec: intro}
%General information about SEDs
Nearly all information we can obtain from a galaxy is encapsulated in the light it emits; every observable phenomenon in a galaxy leaves a footprint on its spectral energy distribution (SED).
We can determine some physical property of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical or spiral.
Each group has its own characteristic features and can in turn be divided into many sub-branches.

%%Creating templates and NIR_UV templates
Several attempts have been made to create a complete set of templates for categorizing the spectral type of galaxies using data from nearby galaxies~(e.g.~\citealt{Kinney93}, \citealt[][hereafter \citetalias{Kinney96}]{Kinney96}, \citealt{Bershady00}, \citealt{Mannucci01}). 
Based on their usage, these templates are restricted to certain wavelengths.
In near-infrared (NIR) to ultraviolet (UV) wavelengths (the region where energy output of stars peaks), the SED contains information about the main physical properties of galaxies, e.g., age, star formation rate (SFR), stellar mass, metallicity, and interstellar medium.

% categorizing galaxies based on their SED

Advances in techniques and detectors have resulted in more detailed observations of SEDs and also made classification of galaxies more complex.
Since no two galaxies, even with the same morphology, have exactly the same properties, classifying SEDs of galaxies using templates is very challenging.
To overcome this challenge, many fitting methods have been developed and used to find template matches for SEDs, with $\chi^2$ minimization being the most commonly used. 
Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.

%ANNs
Artificial neural networks (ANNs), which are inspired by the way neurons in a human brain route and process data, are very powerful tools that are used in data processing and pattern recognition problems.
An ANN contains many interconnected units (nodes or neurons) which process data and work together to solve problems.
It uses a set of training methods to learn about nonlinear and complex relations between input and output data, and how to apply these relations to new sets of data~\citep[e.g.][]{Hossein14,Hossein16,Ellison16a, Ellison16b}.
Studies have shown that ANNs outperform chi-square minimizing techniques and can be used as an alternative choice for fitting data~\citep[e.g.][]{Marquez91}.
Specifically, ANNs perform faster in large databases~\citep[][]{Gulati97}.

%Training methods for networks
Neural networks can be trained using two methods: supervised and unsupervised.
In supervised method, a neural network would be trained using input data based on a desired outcome.
This method is very useful for classification of data with specific target values.
On the other hand, in unsupervised method there is no prediction of output.
This method classifies data based on their underlying structures and hidden patterns.
The unsupervised method is very helpful to obtain knowledge from the data, or when the underlying structure of data is not well established.

%SOM
A Kohonen self-organizing map (also called self-organizing map, or SOM) is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data introduced by~\citet{Kohonen82}.
It shows simple geometrical relationships in non-linear high dimensional data on a map \citep{Kohonen98}.
%SOM in Astronomy
The utilization of the SOM in astronomy dates back to the 1990s, with \citet[][]{Odewahn92}, \citet[][]{Hernandez94}, and \citet[][]{Murtagh95} among the first to use SOMs in their studies.
\citet{Geach12} used COSMOS data to demonstrate two of the main applications of SOMs: object classification and clustering, and photometric redshift estimation. The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.

%SOM in Astronomy continued.
Large spectroscopic surveys have made available integrated spectra of millions of galaxies.
These integrated spectra combine the light of billions of individual stars and nebulae within a galaxy, and
finding patterns and common characteristics between galaxies can be a complex task.
\citet{In12} introduced a new clustering tool based on the SOM method for analyzing these large datasets.
They used $\sim 60000$ spectra from the Sloan Digital Sky Survey \citep[SDSS;][]{Abazajian09} to test their tool, and created very large SOMs to analyze the type of spectra/objects.
They also generated SOMs from quasars' spectra in order to find unusual types of spectra. 
Later, \citet{Meusinger16} used these SOMs and updated data from SDSS and other surveys to find a new class of quasars.
The other application of SOMs is to find outliers or errors in the data.
\citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline. This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.

%What \citetalias{Hossein12} did
~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
With the supervised method, they could only classify SED of 105 out of the 142 galaxies.
The SED of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
%This procedure showed that, not a single type of galaxies in \citetalias{Kinney96} template could describe the SED of any of those 37 galaxies. %PB20160603: repeats previous sentence
\citetalias{Hossein12} also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.

%What we did
In this paper, we compare supervised and unsupervised methods of galaxy spectral classification directly, using exactly the same data as \citetalias{Hossein12}.  
Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to this data 
to find the best SED class for the 37 galaxies that could not be classified by the supervised method.
First, we train self-organizing maps using the \citetalias{Kinney96} spectral templates and compare our classification with the \citetalias{Kinney96} classification.
Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
In Section $\S$~\ref{sec: data_highZ}, we present the data that we use to train and test our networks. 
We describe the SOM methods in Section $\S$~\ref{sec: method}. 
The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{Data}
\label{sec: data_highZ}
We use SED templates from \citetalias{Kinney96} to train neural networks.
To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12}.
Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare supervised and unsupervised methods.

 \subsection{Kinney spectral model}
     \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../image_paper2/k96.jpg}
        \caption{\citetalias{Kinney96} spectra template for 12 types of galaxies from \citetalias{Hossein12} paper (Fig. 1 in \citetalias{Hossein12}). The type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belong to the early types galaxies. Starburst galaxies spectra are indicated with SB 1 to 6. Higher numbers represent more intrinsic colour extinction.}
        \label{fig: k96}
    \end{figure}

    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
    These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
    \citetalias{Kinney96} stated that these templates can also be used to classify the SED of high-redshift galaxies.

    The 12 templates are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
    The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
    The bulge group represents galaxies similar to M31 and M81, whose UV and optical spectra are dominated by their bulge stellar populations.
    The starburst galaxies are divided into six groups (SB1 to SB6) based on their intrinsic extinctions ($E(B-V)$). 
    As Fig.~\ref{fig: k96} shows, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies. 
    In the early type (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
    SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the early types and show strong emission lines.
    For more details on each spectral type, we encourage readers to see \citetalias{Kinney96} and references therein. 
   The \citetalias{Kinney96} spectra span from $\sim1200$~\AA~to $10000$~\AA~with a resolution of $\sim 10$~\AA.
    However, in this work we only use $\sim1200< \lambda < 8000$~\AA~to train our networks; 
    this wavelength range was chosen due to availability of flux information in those wavelengths for all 12 templates.

 \subsection{SED and properties of the sample galaxies} 
    \citetalias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field~\citep{Vanzella05, Vanzella06, Vanzella08}.
    The 142 galaxies were selected based on the availability of photometry from HST/ACS, VLA/ISAAC, and {\it Spitzer}/MIPS and IRAC (10--13 filters with $\sim 0.4<\lambda<24~\mu$m in the observed frame).
   Data from these instruments was necessary in order to have a complete picture of stellar population and star formation rate. 
    For each galaxy, a robust spectroscopic redshift and photometric measurements from the GOODS-MUSIC catalogue \citep{Santini09} was available.
   \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
   % as well as some of the physical properties of the galaxies.
% PB 20160603: commented out following 3 lines as I don't think this fit well here. Could maybe go somewhere else.    
%    {\em CIGALE} is a valuable tool to investigate the properties of galaxies using ultraviolet to infrared wavebands.
%    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei optical spectral templates to model the SEDs of galaxies.
%    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by \citetalias{Noll09}.
    \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
    Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
    Some of these properties are shown in Tab.~\ref{tab: props}.
    In Sec.~\ref{sec: 1D}, we study these properties for each category.
    More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.

\begin{table}
\caption{Description of the properties of \citetalias{Hossein12} galaxies; the output result of {\em CIGALE}}     
\label{tab: props}
\centering
\begin{tabular}{l l l}
\hline\hline
\noalign{\smallskip}
Par. & Unit & Description\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
$t_{\,\mathrm{oSP}}$ & Gyr & age of old SP model \\
$t_{\,\mathrm{ySP}}$ & Gyr & age of young SP model \\
$f_\mathrm{burst}$ & --- & mass fraction of \\
& & young single population (SP) model \\
\noalign{\smallskip}
$t_{\,\mathrm{D4000}}$ & Gyr & D4000-related age \\
\noalign{\smallskip}
$M_\mathrm{star}$ & M$_\odot$ & total stellar mass  \\
SFR & M$_\odot$/yr & instantaneous SFR  \\
$A_\mathrm{FUV}$ & mag & attenuation at 1500\,\AA{} \\
\noalign{\smallskip}
\hline
\end{tabular}
\end{table}

    For testing the created networks, we use SEDs that were produced by \citetalias{Hossein12}. 
    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength in a wide range of wavelengths.
    Since we have used the \citetalias{Hossein12} SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} templates.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{Method}
\label{sec: method}
 \subsection{Self Organizing Maps}
 \label{sec: som}

 The self-organizing map is a clustering method which reduces the dimension of the data, usually to one or two dimensions (1D or 2D), while preserving topological features of the original dataset.
 The result of an SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
 Each node may contain one or more samples from the input data.
 The distance between the nodes represents similarity or dissimilarity of the underlying samples, i.e., similar data are closer together in the array and the distance between two nodes is related to the dissimilarity of their samples.
 A weight vector ``\boldit{W}" with the same dimension as the input data is associated with each node and will be varied during the training process.
 This vector is the key factor in determining the position of the nodes in a map.
 \cite{Geach12} presented the application of the SOM and discussed its algorithm in detail.
 In this section we briefly discuss the algorithm of SOM, how we create our maps and a present a  test model which will help interpretation of our results.

 \subsubsection{Algorithm of SOM} 
 \label{sec: algorithm}
     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on the map's topology provided by the user.
     In the case of 1D maps, since each neuron has two immediate neighbours, the topology of the map does not have any effect on the final result and any topology can be chosen.
     However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
     Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
     The process of creating SOM happens over a series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration, the SOM code:
     \begin{enumerate}
        \item chooses a random vector from the dataset ($V_i$).
        \item calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$"). This neuron is the winner node and is called the Best Matching Unit (BMU). 
        \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. The radius of the neighbourhood is arbitrary and can be set to be as high as half of the SOM size. It then decays exponentially over each iteration as
        \begin{equation}
            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
        \end{equation}
        where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively. 
        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
        \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
        \end{equation}
        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
     \end{enumerate}
     These steps are then repeated $N$ times.

\subsection{Creating self-organizing maps}
\label{sec: create_som}
     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     %%Sr160611: Last time I got the following note from the MNRAS editor:
     %"Please note that computer software/programming lan- guages must be styled in SMALL CAPITAL LETTERS, according to journal style. Please check and correct this paper accordingly."
     % PB20160603: right, but I think the right way to do this is {\sc newsom}, not {\tiny NEWSOM} -- the distinction being that {\sc.. } will scale up or down with the global font size but {\tiny} will not.
     SOM in {\sc nnt} can be created by {\sc newsom} or {\sc selforgmap} library, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
     The first phase is called the ``ordering phase" and
     starts with maximum neighbourhood distance and an initial high learning factor (usually 0.9) is provided by the user. 
     The ordering phase continues for a requested number of iterations.
     During the iterations, the learning factor decreases to the tuning phase learning factor and the neighbourhood distance reaches that of the tuning phase as well.
     Both the learning factor and the neighbourhood of the tuning phase are set by the user. 
     The amount by which these two factors change in each iteration depends on the number of iterations.

     In the second, or ``tuning'' phase,
     the neighbourhood distance is kept at the user-defined minimum.
     The learning factor, however, decreases gradually.
     The gradual change in the leaning factor helps to fine-tune the topology results, leading to a more stable SOM. 
     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase. %cite kohenen book?!
     We chose the number of epochs in the tuning phase to be 3 times the number of epochs in the ordering phase.

     To present our results, we use {\sc nnt}'s built-in plotting tool.
%     This tool is designed to show the distance between each cluster more clearly.
     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
     In the maps, the purple hexagonal shapes represent the neurons. 
     The distances in a distance map are shown by the grey cycle colours:
     the darker the colour, the larger the distance between neurons.
     In the hit maps, neurons with zero hits are left empty.

    The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.

\subsection{Mock sample}

         \begin{figure}
            \begin{subfigure}[b]{0.5\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../image_paper2/sample/sample2_dist.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{../image_paper2/sample/sample2_hits.png}
            \end{subfigure}
            \caption{SOM of the mock sample. In both plots, the axes show the position of the neurons. Hexagonal shapes represent the neurons. The top plot is a distance map. The grey cycle colours show the differences between the weights of each neuron with white being the minimum difference and black being the maximum one. The lower plot is a ``hits plot". It represents the number of samples in each neuron, where empty means zero hits. In this sample, the 27 galaxies are clustered in 4 groups, containing 8, 7, 6 and 6 galaxies respectively.}
            \label{fig: sample}
        \end{figure}

 To illustrate how self-organizing maps work, we create a mock sample of 27 galaxies.
% We create a mock sample of 27 galaxies to show how this method works, illustrate the results of SOMs, and how they can be analysed.(<- I don't like this sentence)
 The mock sample contains two attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). 
 We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Sec.~\ref{sec: create_som}.

 Fig. ~\ref{fig: sample} shows the SOM of this mock sample. 
 The upper panel is the distance map. 
 The axes show the position of the neurons in the $10 \times 10$ network.
 The lower panel in Fig.~\ref{fig: sample} shows the hit map.
 On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
 The number on the purple neurons shows the number of galaxies in that neuron.
 Colour coverage of neurons depends on the number of the hits on the sample.
 The neuron with the maximum number of hits is dark-coloured while the empty neurons are left uncoloured (white).

Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
The upper panel in the Fig.~\ref{fig: sample} clearly shows this division.
In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to low star forming galaxies.
The left half of the plot is where type 1 galaxies belong, and type 2 galaxies reside in the right side.
Different shades of gray show the border between regions.
The lower panel in Fig.~\ref{fig: sample} shows that only 4 neurons (out of 100) are occupied. 
8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
%Since the input data are chosen to not to be complex, each entry only could get either 0 or 1 as a type of galaxy and 0 or 0.5 as an indicator of  high or low SFR, only four of the neurons were filled.
We can conclude that although each galaxy had  the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributes, they remained only in four groups.
This network is considered a training network and can be used to cluster any new dataset with similar entries.

As we show in the following sections, with data from real galaxies there are more than two dimensions and two galaxies never have exactly the same information. 
If the network has enough neurons, the input data points would eventually separate from each other and cluster into smaller groups. 
However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
Therefore, it is up to the users to decide the similarity or dissimilarity between the input data based on number of neurons.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\include{sections_highz/}{results.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Results and discussion}
\label{sec: result}

    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra.
    Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
    The trained networks can then be used to categorize other galaxies.
    %In following we show how we trained data and used galaxies from \citetalias{Hossein12} to show how the clustering using trained networks works.

    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
   Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.
    We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
    We generate 2D networks (Sec.~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.

    \subsection{One-dimensional self-organizing maps}
    \label{sec: 1D}
        \subsubsection{Training the networks}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided into only two general types; quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
            As mentioned in Sec.~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citetalias{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.
            In the lower part of Fig.~\ref{fig: 1by2T}, we see that the templates are divided into two groups of 5 and 7.
            Although we know from \citetalias{Kinney96} and \citetalias{Hossein12} that 6 of the templates are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorize in a maximum 3 groups. 
            %If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty(this sentence does not make much sense. I kind of think I know what you're trying to say (because once I translate this sentence to farsi word by word, it kind of comes together) but please phrase it more carefully.).
            %[suggested sentence: 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst templates are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are very similar; both groups are starbursting and have strong emission lines.
            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the SED to become flatter at shorter wavelengths. 
            The flatter UV SED makes these two templates more similar to quiescent galaxies than to other starbursts.
            Therefore, in the networks, SB5 and SB6 types are to be grouped close to the early type galaxy templates.

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid. In this network again, 5 of the \citetalias{Kinney96} templates are categorized as quiescent and 7 as starbursts. However, this time 2  templates (SB5 and SB6) are separated from the starburst groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the  algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../image_paper2/1d/dist_1_by_22.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_22.png}
            \end{subfigure}
            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*}

            In Fig.~\ref{fig: 1by22T}, we can see twelve different groups:
            5 groups in the left-side neurons are separated from 7 groups on the right side of the map with two dark-grey colours between them.
            This shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
            The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
            This template has the most extinction and its SED has more similarity to early type galaxies than other starburst types.

            The fact that the templates need to have at least 22 different neurons to be divided into 12 groups shows that the differences between SB1 and SB2, and B and E, templates are very small.
            Because of their similarities, they tend to stay in the same group until the network becomes big enough to make attention to the smallest particularity.

        \subsubsection{Classifying the galaxy sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Sec.~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
            %The lower panels show the average SED of the galaxies in each node. 
            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy SEDs from \citetalias{Hossein12} using the $1\times2$~networks trained from the \citetalias{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies. Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's SED predominantly decides which group the galaxy belongs to.
            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as early type.
            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.

            Fig.~\ref{fig: 1by3V} presents the result of classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to the early type group, and 47 belong to the starburst group. 
            However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the early type galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
           As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_22_n.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the average SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones. The 4000\AA~ break weakens from left to right and the emission line strengths increase.}
                \label{fig: 1by22V}
            \end{figure*}
            The lower panels present the average SED of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.

            Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
            Otherwise, we can conclude that the SEDs of galaxies in the cluster are similar to two of the \citetalias{Kinney96} templates.
            For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with SEDs similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            18 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SEDs similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and the SEDs of the 14 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with SED comparable to types SB1 and SB2.

            In general, 56 galaxies correspond exactly to \citetalias{Kinney96} templates and the other 86 are placed between the initial 12 suggestions.
            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies.
            In this small sample, it is quite possible that the best SEDs do not match any model perfectly and the original classifications have high uncertainties.

            %PB20160604: is this paragraph really necessary?
            %%Sr: I think it clears the point of having regions in middle neurons
            With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of SEDs is limited to models and the results are always reported with uncertainties.
            However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.

        \subsubsection{Properties of the clustered galaxies}

        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.

        \begin{figure}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/props5.png}
            \caption{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
            \label{fig: props}
        \end{figure}

        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.%, and vertical axis is one of the aforementioned properties.
%        
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst. 
       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
        %Considering the results from Fig.~\ref{fig: props}, we can clearly see that s
        Separating galaxies based on SED types also leads to a separation in properties that derived (via {\sc CIGALE}) from the SEDs, as expected since the SED types are also based on {\sc CIGALE} fitting.

        %Sr07062016: Is it better?
        {\sc CIGALE} has various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\sc CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.

               \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/1d/f6.png}
        \end{subfigure}
        \caption{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values. colours shows the type of the galaxies in the new classification. The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies. The other colours depend on how much they are close to red or blue show that the galaxies are early type or starburst.}
        \label{fig: props_vs_props}
    \end{figure}

        In order to compare our classifications with previous works, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
        The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
        The redder the colour, the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        The purple point in the middle of the blue points in  Fig.~\ref{fig: props_vs_props} corresponds to galaxies with SEDs similar to type Sc: the shape of their SED indicates that they are old galaxies with high sSFR.

        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with tighter correlation than those two, in all three plots.
        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
        From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
        %for more details discussion on these correlations, we encourage readers to read \citetalias{Noll09} and \citetalias{Hossein12}.

        \citetalias{Noll09} studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
        The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
        They found that for early type galaxies (E, S0 and S0/a ), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
       Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing sSFR in the S0 and Sa types.
        The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
        Whether this dependence is real or not, our results here show that using self-organizing maps can separate SEDs of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.

    \subsection{Two-dimensional self-organizing maps}
    \label{sec: 2D}
    The one-dimensional networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies with category.
    However, each neuron in these networks is limited to be connected to one other neuron in each direction.
    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each SED type.
    As described in Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
    This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
    At first, as in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 templates in Fig.~\ref{fig: k96}.
    In this case, we can categorize SEDs of other galaxies based on those 12 types.
   In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
    This approach can be used to trace and recognize the outliers.
    To execute the second approach, we used the {\tiny selforgmap} library in {\tiny MATLAB}.
    Using the {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
%    The latter case, can be used to identify outliers.

    To get the best result from both methods, we should have SOMs with ``enough"  neurons to give any new types of galaxies a chance to find their places in the map.
    ``Enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
    Since the training dataset (the \citetalias{Kinney96} templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
    We then increased the size of the SOM to find the highest size suitable for the training sample.
    We noticed that very few changes occurred after the SOMs were grown to a size greater than $12\times12$, so we used this as the maximum size.

    \begin{figure*}
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/2d/dist_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/2d/dist_12_by_self_org_res12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/2d/hit_v_12_by_12.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{../image_paper2/2d/hit_v_12_by_self_org_res12.png}
        \end{subfigure}
        \caption{$12\times12$~2D SOM results. Upper pabel: SOMs trained using the \citetalias{Kinney96} templates. For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right). Lower panel: classifying the galaxies from \citetalias{Hossein12}, using the trained networks shown in the upper panels. From the lower right panel, we can see that there are no outliers in the galaxies from \citetalias{Hossein12}, and we can use the map in the lower left panel as a final clustering result for the \citetalias{Hossein12} galaxies.}
        \label{fig: 12by12}
    \end{figure*}

    The upper left panel in Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
    Since we considered that SEDs of all galaxies can be categorized using the \citetalias{Kinney96} templates, the galaxies were placed all over the map.
    Using this network to categorize any set of SEDs forced the SEDs to be either in the same neurons as the \citetalias{Kinney96} templates or in the neurons between them.
    In the map shown in the upper right panel in Fig.~\ref{fig: 12by12}, the \citetalias{Kinney96} templates are in a small region. This provides enough freedom for the SEDs of galaxies to be placed everywhere in the map, even far away from the templates.

    In the upper left part of the map in Fig.~\ref{fig: 12by12}, although galaxies have more ways to be separated, they were separated in two main groups.
    There is a distinguishable strip of grey, dark grey and in some cases black colour in the map:
    this strip separates early type galaxies from starburst ones.
    The lower map shows that 5 of the neurons on the left side of the strip are full. 
    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (early type galaxies),
    the only difference being that in this map they have more space to be separated from each other.
    When we use this network to categorize the SED of galaxies, any galaxy placed on the left hand side of the strip is an early type galaxy and any one placed on the right side of the strip is a starburst one.
    The decision about what sub-type of early type or starburst galaxy is based upon its relative position to each type in the SOM.

    As in the other map, in the upper right panel of Fig.~\ref{fig: 12by12}, galaxies are generally divided into two main groups.
    The border between the early type galaxies and the starburst ones is the black strips in the middle of the map,  ending with the bright grey colour at the bottom of the map in the fifth neuron.
    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the starburst ones. 
    When categorizing a new set of SEDs, if the new SEDs are similar to the \citetalias{Kinney96} template all of them will be placed in the bottom of the map, but if there are different type of galaxies, they would sit in any other neurons in the map.
    In large datasets, one can easily use this network to figure out whether there is any of new type of SEDs (or any outliers) in the datasets. 
    Since the networks are already available, this procedure should be quick and easy for big datasets.

    We used both 2D networks to categorize the \citetalias{Hossein12} galaxies and the results are shown in the lower panels of Fig.~\ref{fig: 12by12}.
    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the \citetalias{Hossein12} sample there are no outliers or SEDs very different from  the \citetalias{Kinney96} templates.
    The lower left map of Fig.~\ref{fig: 12by12} shows the \citetalias{Hossein12} galaxies categorized based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
    Comparing this categorization with the 1D one from Fig.~\ref{fig: 1by22V}, we can see that only 23 galaxies correspond exactly to \citetalias{Kinney96} types.
    Using 2D maps results in categorizing galaxies into more intermediate type than in 1D maps.
    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the early type side of the SOM, which was predictable from the results in Sec.\ref{sec: 1Dv}. This does not imply that in general there are more early type galaxies at higher red-shifts but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.

    Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy SED classification should use 2D networks first. These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Summary and future applications}
\label{sec: summary}

Self-organizing maps can be used to classify celestial objects (e.g. stars, quasars, spectra of galaxies, light curves, etc.)
Galaxy spectra can be classified in various networks with different sizes/dimensions based on the information needed from the data. 
If a broad and general classification is required, networks can have one dimension with a few neurons.
If one needs more detailed classifications, a higher number of neurons should be used.
Since self-organizing maps do not include the uncertainty of input parameters, sometimes too much attention to detail can cause problems in classifications. 
%Some small differences could easily be the result of atmosphere fluctuation or other instrumental or observational problems. 
When using the SOM method, one should consider whether small differences between objects are physically meaningful when separating two groups from each other.

We used SOMs to classify the template spectra of \citetalias{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
By varying the size of the networks, we found the relative similarity between the \citetalias{Kinney96} template classes.
A one-dimensional network with 22 neurons was needed in order to
separate all 12 \citetalias{Kinney96} spectra; we concluded that \citetalias{Kinney96} types B and E, and types SB1 and SB2, are very similar to each other.
We also showed that networks generated with the SOM method can be used to easily identify new types of spectra in large surveys.

A sample of 142 high red-shift galaxies from \citetalias{Hossein12} was used to test the trained networks.
%One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
The test results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.% but not exactly the same as one of them.
The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} SED templates and classify the same sample of 142 galaxy spectra;
however, they could not classify 37 out of 142 spectra.
The unsupervised method used in this project was able to classify  all 142 spectra in the sample
as belonging to one of the morphological types introduced by \citetalias{Kinney96} or a class in between those types.

The properties of the galaxies in the test sample using the new
classification were found to more tightly correlate in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies. 
The properties of the galaxies in each group are in good agreement with their morphological types.

### 2016-07-06 image_paper3/text_files/image_texts/col3byall.tex
adding prelude to into. section

\begin{figure*}
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
        \label{fig: col3and11_dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
        \label{fig: col3and12_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
        \label{fig: col3and13_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
        \label{fig: col3and14_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
        \label{fig: col3and15_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
        \label{fig: col3and16_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
        \label{fig: col3and17_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
        \label{fig: col3and18_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
        \label{fig: col3and19_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
        \label{fig: col3and20_dist}
    \end{subfigure}        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
        \label{fig: col3and21_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
        \label{fig: col3and22_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
        \label{fig: col3and23_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
        \label{fig: col3and24_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
        \label{fig: col3and25_dist}
    \end{subfigure}
    \caption{Results from increasing dimension of input data from 11 to 25}
    \label{fig: inc_D_col3s}
\end{figure*}

### 2016-07-06 image_paper3/text_files/image_texts/subset9.tex
adding prelude to into. section

\begin{figure}
 \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/image_subsets/subset9_dist_with_hits_t.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{../../images0.01/M31/2D/image_subsets/subset9_dist_with_hits_v.png}
    \end{subfigure}
    \caption{Results from subset 9}
    \label{fig: subset9}
\end{figure}

### 2016-07-06 version0.0/appendixa.tex
adding prelude to into. section

@@
     \end{figure}
+
+\section{2D SOMs of subsets}
+\label{sec: app_2d_soms_SOMN}
+
+        We removed IRAC 5.7 $\mu$m; [\sii] continuum and [\oiii] continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, [~\oiii] continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
+        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}.
+        IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
+        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
+        For subset sample 7 (Table~\ref{tab: subset7}) we removed [\sii] flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
+        The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
+        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
+        \import{../image_paper3/text_files/tables/}{subset2.tex}
+        \import{../image_paper3/text_files/image_texts/}{subset2.tex}
+
+        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
+        Since region 4 and 5 have a similar [~\oiii] and [~\sii] continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
+        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
+        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
+        moreover, similar to regions 4 and 5, [~\oiii] and [~\sii] continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions.
+Therefore, they moved further from each other.
+        \import{../image_paper3/text_files/tables/}{subset3.tex}
+        \import{../image_paper3/text_files/image_texts/}{subset3.tex}
+
+        In the results from the subset 4 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
+        These two regions have distinct metallicity, removing metallicity from input data caused these two stay in a closer neurons. 
+        Since regions 1 and 2 have similar metallicity and total PAHs, and their total stellar mass are comparable, removing these values from input data made the position of the regions 1 and 2 moved further from each other.
+        \import{../image_paper3/text_files/tables/}{subset4.tex}
+        \import{../image_paper3/text_files/image_texts/}{subset4.tex}
+
+        The positions of the region 8 and 5 are moved closer in Fig.~\ref{fig: subset7}.
+        Both of these regions are around the inner ring inside the galaxy.
+        Therefore, both of them have similar values in most of the input parameters.
+        However, they have very different fluxes in IRAC 5.7 $\mu$m and [~\sii] continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
+        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
+        In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
+        \import{../image_paper3/text_files/tables/}{subset7.tex}
+        \import{../image_paper3/text_files/image_texts/}{subset7.tex}

### 2016-07-06 version0.0/asli.tex
adding prelude to into. section

@@
 \usepackage[byname]{smartref}
-%\usepackage{hyperref} %comment out for hardcopy
+\usepackage{hyperref} %comment out for hardcopy
 \usepackage{txfonts}
@@
 \usepackage{amsmath}
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=True,
-    linkcolor=black,
-    filecolor=magenta,      
-    urlcolor=cyan,
-    citecolor=blue,
-}
 \usepackage{graphicx}
@@
 \usepackage{pdflscape}	% Landscape pages
-%\usepackage{booktabs,fixltx2e}
 \usepackage[flushleft]{threeparttable}
 \usepackage{pgffor}
+\usepackage{chapterbib}
+\usepackage{mwe}    % loads »blindtext« and »graphicx«
+\usepackage{subfig}
 
@@
 \newcommand{\super}{Dr. P. M. Barmby} %supervisor
-%\newcommand{\superj}{Dr. A. Manning} %joint supervisor, if there is one, leave blank if not (lbin)... only one of the three.
-\newcommand{\superc}{} %co-supervisor, if there is one, leave blank if not (lbin)
-\newcommand{\supera}{} %alternate supervisor, if there is one, leave blank if not (lbin)
 \newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
 \newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
-\newcommand{\examo}{Dr. S. Basu}  %examining committee (up to four, if less leave blank)
-\newcommand{\examt}{Dr. S. Gallagher}
-\newcommand{\examth}{Dr. M. Daley}
-\newcommand{\examf}{}
+\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
+\newcommand{\examt}{Dr. M. Daley}
+\newcommand{\examth}{Dr. S. C. Gallagher}
+\newcommand{\examf}{Dr. P. Wiegert}
 \newcommand{\department}{Physics and Astronomy}
@@
 \newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
-\newcommand{\titl}{Properties of nearby galaxies from modern statistical methods:Bayesian analysis and Data Mining}
-\newcommand{\spinetitle}{Properties of nearby galaxies}%only if the above is more than 60 characters
+\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
+\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
 \newcommand{\thesisformat}{Integrated Article} %or Integrated Article
@@
 I would like to thank all my Friends in Western.
+Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad,
 }
 \newcommand{\makededications} {
-To my parents, my sisters, and Matin, for their unconditional love and supports. 
+To my parents, my sisters, and Matin, for their unconditional love and support. 
 }
@@
 \newcommand \Herschel {{\it Herschel }}
+\newcommand \sii {S~{\textsc II}} 
+\newcommand \oiii {O~{\textsc III}} 
+\newcommand \hi {H~{\textsc I}\ }
+\newcommand \hii {H~{\textsc II}\ }
+\newcommand \oii {O~{\textsc II}}
+
 \newcommand \aaj {A\&A}
@@
 \newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
+\newcommand \afz {Afz}%: Astrofizika
+\newcommand \aj {AJ}%: Astronomical Journal (the)
+\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
+\newcommand \apj {ApJ}
+\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
+\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
 \newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
+\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
+\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
 \newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
+\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
+\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
+%\newcommand {Nature}%(do not abbreviate)
+\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
+\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
+\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
 \newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
+%\newcommand {Science }%}%(do not abbreviate)
 \newcommand \sva {SvA}%: Soviet Astronomy
+\newcommand \aap {APP} %:American Academy of Pediatrics
+\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
 
+%% This sets the page style and numbering for preliminary sections.
+\begin{preliminary}
 \defcitealias{Hossein12}{T12}
@@
 \defcitealias{Noll09}{N09}
-
-%% This sets the page style and numbering for preliminary sections.
-\begin{preliminary}
 
@@
 %% (150 words for M.Sc. and 350 words for Ph.D.)
+Understanding the process of star formation is one of the key steps in understanding the formation and evolution of galaxies.
+In this thesis, I address the empirical star formation laws, and study the properties of galaxies that can affect the star formation rate.
 
-I study properties of galaxies.
+The Andromeda galaxy (M31) is the nearest large spiral galaxy, and Therefore, high resolution images of this galaxy are available.
+These images provide data from various regions with different physical properties.
+Star formation rate and gas mass surface densities of M31have been measured using three different methods, and have been used to compare different star formation laws over the whole galaxy and in spatially-resolved regions.
+Using hierarchical Bayesian regression analysis, I conclude that there is a correlation between surface density of star formation and the stellar mass surface density.
+A weak correlation between star formation rate, stellar mass and metallicity is also found.
+
+To study the effect of other properties a galaxy on the star formation rate, I utilize an unsupervised data mining method (specifically the self-organizing map) on measurements of both nearby and high-redshift galaxies.
+Both observed data and derived quantities (e.g. star formation rate, stellar mass) of star-forming regions in M31 and the nearby spiral galaxy M101 are used as inputs to the self-organizing map.
+Clustering the M31 regions in the feature space reveals some (anti)-correlations between the properties the galaxy, which are not apparent when considering data from all regions in the galaxy. 
+The self-organizing map can be used to predict star formation rates for spatially-resolved regions in galaxies using other properties of those regions.
+
+I also apply the self-organizing map method to spectral energy distributions of high-redshift galaxies.
+Template spectra made from galaxies with known morphological type are used to train self-organizing maps.
+The trained maps are used to classify a sample of galaxy spectral energy distributions derived from fitting models to photometry data of 142 high-redshift galaxies.
+The grouped properties of the classified galaxies are found to be more tightly correlated in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
 
@@
 
-\include{intro}
-\include{paper1}
-\include{paper2}
+\include{intro0.0}
+%\include{paper1}
+%\include{paper3}
+%\include{paper2}
 
 %% This adds a line for the Bibliography in the Table of Contents.
-\addcontentsline{toc}{chapter}{Bibliography}
+%\addcontentsline{toc}{chapter}{Bibliography}
 %% ***   Set the bibliography style.   ***
-\bibliographystyle{apj.bst} % (change according to your preference)
+%\bibliographystyle{apj.bst} % (change according to your preference)
 %%% ***   Set the bibliography file.   ***
-\bibliography{westernthesis}
+%\bibliography{westernthesis}
 

### 2016-07-06 version0.0/comprehensive_exam.tex
adding prelude to into. section

--- 2016-06-11 version0.0/intro.tex
@@
 \section{Overview}
-
 Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe.
@@
 Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution.
-Numerical simulations have shown that magnetic fields in the cores become supercritical and collapse\citep{Basu97}.
+Numerical simulations have shown that magnetic fields in the cores become super-critical and collapse\citep{Basu97}.
 In the process of  collapsing, an accretion disk is formed and significant magnetic flux is lost while the star also gradually loses its angular momentum.
@@
 Massive stars form from massive cores, which are highly energised.
-These stars are highly luminous, therefore, they ionize their surrounding gas into HII regions.
+These stars are highly luminous, therefore, they ionize their surrounding gas into \hii regions.
 GMCs lose much of their original mass due to photo-evaporation.
-Most of the mass lost returns to the diffuse interstellar medium and completes the cycle of star formation, which then starts a new cycle (see \cite{McKee07} for more detail).
+Most of the mass lost returns to the diffuse interstellar medium and completes the cycle of star formation, which then starts a new cycle (see~\cite{McKee07} for more detail).
 
@@
 
-In this paper, we present the observational review of measuring the star formation rate and other properties that affect measuring and scaling the SFR in nearby galaxies.
-In $\S2$ we discuss measuring the star formation rate.
-A discussion of the ISM is presented in $\S3$, followed by a discussion of the measurement of the stellar mass in $\S4$.
-In $\S5$ the KS law and the models for scaling the star formation rate are introduced.
-The current issues about KS law and the present project are discussed in $\S6$.
+In this chapter, we present the observational review of measuring the star formation rate and other properties that affect measuring and scaling the SFR in nearby galaxies.
+In $\S$~\ref{chap:sfr} we discuss measuring the star formation rate.
+A discussion of the ISM is presented in $\S$~\ref{chap:ISM}, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{chap:starrmass}.
+In $\S$~\ref{chap:metal} we talk about effect of metallicity on SFR.
+The current issues about studying star formation and its relation to other properties of a galaxy and the present project are discussed in $\S$~\ref{chap:cipp}.
 
@@
 
-Many groups have been trying to define a technique to calibrate emission from the newly-born, hot and massive ``€œO"€ and ``€œB"€ stars to the rate at which stars are being formed.
+Many groups have been trying to define a technique to calibrate emission from the newly-born, hot and massive ``O'' and ``B'' stars to the rate at which stars are being formed.
 Emission from the young massive stars are normally used as a tracer of the current SFR.
@@
 
-The ``O"€™ and ``€œB"€ stars can be observed by both using direct and indirect emission from stars; thus the SFR indicators are categorized based on these methods of observation.
+The ``O'' and ``B'' stars can be observed by both using direct and indirect emission from stars; thus the SFR indicators are categorized based on these methods of observation.
 In the direct method, the SFR indicators can be probed by the ultraviolet (UV), optical, and near-infrared (NIR) emissions, while for probing the stellar light obscured by dust, mid/far-infrared emission is used.
@@
 In theory, for any system with high enough spatial resolution ($\sim 0.5- 1$ kpc), counting YSOs can be used as a tracer of the star formation.
-However, considering the limited capabilities of the present instrumentations, YSOs in most regions beyond the Magellanic clouds can not be resolved.
+However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic clouds can not be resolved.
 Therefore, most studies use the emission from the ``O" and ``B" stars as tracer of the SFR.
@@
 Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order the shape of the thermal IR SED depends on the starlight SED \citep{Helou86}.
-The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60  \mu$m) in comparison with the dust heated by old or low-mass stars.€“ Therefore, the IR wavelength is able to detect the emission from the young stellar population and be used as an SFR indicator.
+The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60  \mu$m) in comparison with the dust heated by old or low-mass stars.
+Therefore, the IR wavelength is able to detect the emission from the young stellar population and be used as an SFR indicator.
 
@@
 \section{Interstellar Medium}
+\label{chap:ism}
 
@@
 Thus for tracing the star-forming region, the effect of dust must be taken into account, otherwise the SFR might be underestimated.
+\subsection{Molecular clouds}
+\subsection{Ionized regions}
+\subsection{Dust}
 
@@
  One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore.
-The other important advantage is that this method solves the newly-found problem of the "dark gas"€™ in the galaxies.
+The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies.
 Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}.
@@
 \section{Stellar Mass}
-\label{starmass}
+\label{chap:starmass}
 One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass.
@@
 
-\section{Scaling the SFR Using Schmidt-Kennicut Law}
+% \section{Scaling the SFR Using Schmidt-Kennicut Law}
 
-The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas.
+% The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas.
 \cite{Schmidt59} assumed the constant IMF of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way.
@@
 A power law relation between surface densities of star formation and gas is known as the Schmidt law and is written as:
-\begin{equation}
-\Sigma_{SFR} \propto \Sigma_{gas}^n
-\end{equation}
-where $\Sigma_{SFR}$ is surface density of star formation, $\Sigma_{gas}$ is the surface density of gas in a galaxy and, {\it n} is the power index.
+% \begin{equation}
+% \Sigma_{SFR} \propto \Sigma_{gas}^n
+% \end{equation}
+% where $\Sigma_{SFR}$ is surface density of star formation, $\Sigma_{gas}$ is the surface density of gas in a galaxy and, {\it n} is the power index.
 
-Following \cite{Schmidt59}, many groups worked on the scaling relation between the surface density of star formation, and the surface density of gas.
+% Following \cite{Schmidt59}, many groups worked on the scaling relation between the surface density of star formation, and the surface density of gas.
 \cite{Buat89} assumed the constant H$_2$/CO ratio and a \cite{Scalo86} initial mass function for the Milky Way.
@@
 
-A decade later, \cite{Kennicutt98a} examined another group of galaxies.
+% A decade later, \cite{Kennicutt98a} examined another group of galaxies.
 He used H$\alpha$, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$.
@@
 
-\begin{equation}
-\Sigma_{SFR} \propto \Sigma_{gas}^{1.4\pm0.15}
-\end{equation}
-which is often referred to as the Kennicutt-Schmidt (KS) law.
+% \begin{equation}
+% \Sigma_{SFR} \propto \Sigma_{gas}^{1.4\pm0.15}
+% \end{equation}
+% which is often referred to as the Kennicutt-Schmidt (KS) law.
 
-In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution.
+% In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution.
 For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$.
@@
 He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
-It should be noted that the KS law can not be applied for the whole range of gas densities.
+% It should be noted that the KS law can not be applied for the whole range of gas densities.
 In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g.
@@
 
-The Schmidt-Kennicutt scaling relation for star formation is valid for different types of galaxies both in the local universe \citep[e.g.,][]{Kennicutt98a, Bigiel08} and at high-Z \citep[e.g.,][]{Genzel10}, but it is strange that they only consider the effect of gas component while in reality various ISM and stellar objects affect the processes of formation of stars.
+% The Schmidt-Kennicutt scaling relation for star formation is valid for different types of galaxies both in the local universe \citep[e.g.,][]{Kennicutt98a, Bigiel08} and at high-Z \citep[e.g.,][]{Genzel10}, but it is strange that they only consider the effect of gas component while in reality various ISM and stellar objects affect the processes of formation of stars.
 Current proposed Schmidt relations, do not include the effects of metallicity \citep{Gnedin10}, dust grains, radiation shielding of H$_2$ regions \citep[for a review, see][]{Hollenbach99}, and stellar gravitational effects, as they only invoke the gas component.
@@
 
-\cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density.
+% \cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density.
 Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges.
@@
 
-\begin{equation}
-\Sigma_{SFR} \propto \Sigma_{gas}^{\alpha} \Sigma_{star}^{\beta}
-\end{equation}
-where $\Sigma_{SFR}$ is SFR surface density, $\Sigma_{gas}$ and $\Sigma_{star}$ are gas mass and stellar surface density.
+% \begin{equation}
+% \Sigma_{SFR} \propto \Sigma_{gas}^{\alpha} \Sigma_{star}^{\beta}
+% \end{equation}
+% where $\Sigma_{SFR}$ is SFR surface density, $\Sigma_{gas}$ and $\Sigma_{star}$ are gas mass and stellar surface density.
 $\alpha$ and $\beta$ are the power law indexes.
@@
 
-\begin{figure}[h]
-\label{fig:duste}
-\centering
-\includegraphics[width=16cm]{../image_intro/schmidtvsextended}
-\caption{Comparing The extended Schmidt law (a) and the Kennicutt-Schmidt relationship (b) for predicting the SFR.
+% \begin{figure}[h]
+% \label{fig:duste}
+% \centering
+% \includegraphics[width=16cm]{../image_intro/schmidtvsextended}
+% \caption{Comparing The extended Schmidt law (a) and the Kennicutt-Schmidt relationship (b) for predicting the SFR.
 The solid and dotted lines are the best fit and observed 1-$\sigma$ scatter, respectively.
@@
 Adapted from \cite{Shi11}.}
-\end{figure}
+% \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%chapter: current work
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %chapter: current work
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Current issues and the Present Project}
-\label{chap:mp}
+ \label{chap:cipp}
  Studying formation of stars helps us understand the formation and evolution of the universe.
@@
 The Andromeda galaxy is chosen for this project due to its similarity in the structure to the MW.
-Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "€œglobal"€ picture, whereas, studies of the MW are limited by our location within the Galaxy.
+Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "global" picture, whereas, studies of the MW are limited by our location within the Galaxy.
 The Andromeda is closest spiral galaxy to the MW, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.

### 2016-07-06 version0.0/intro0.0.tex
adding prelude to into. section

--- 2016-07-06 version0.0/comprehensive_exam.tex
@@
 \label{chap:intro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%Overview%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Overview}
-Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe.
-Stars are also central to the formation of planetary systems and are where the ingredients for life were formed.
-The energy provided by stars is necessary to maintain the life on planets.
+\section{Prelude}
+\label{sec: overview}
+%what do we have inside galaxies:
+% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
+Inside every galaxy, there are millions of stars, planets, black holes, and high amount of dust and gas which all affect each others' formation, evolution and extinction.
+There are also dark matter inside every galaxy, which to the best our knowledge only has gravitational effect on the galaxies.%add ref.s
+All the information we can obtain from galaxies other than our owns are implanted in their light. % now we can detect gravitational wave which is not part of the SEDs, right?
+Light emitted from young and evolved stars, and dust and gas in the space between stars have the most contribution on spectral energy distributions (SEDs) of galaxies.
+We cannot detect any contribution from planets and black holes on SEDs due to their low intensity or the limitation of our detectors.
+Therefore, with properly modeling observed features in SEDs we can extract information about evolution of stars, dust and gas inside galaxies.
+
+%stars
+Arguably, stars are the main component of normal galaxies.
+They control the chemical composition and structure of galaxies by transforming gas into new born stars and by transforming death stars to the gas.
+They are also central to the formation and evolution of planetary systems.
+The energy provided by stars is necessary to create and maintain the life on planets. 
 The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System.
-This is one of the main reasons that the study of stellar structure and evolution has been a central topic in astronomy and astrophysics for decades.
+Furthermore, in order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
+As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.
 
-In order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation of stars is necessary.
-Star formation determines the structure and evolution of galaxies, by transforming gas into stars.
-Moreover, the knowledge of star formation is essential to understanding the origin of planetary systems.
-The physical process of star formation is naturally complex.
-Therefore, the basis for a theory of star formation requires a strong foundation of empirical data or observations.
+%ISM 1)Gas 2)dust
+There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas.
+Gas and dust in galaxies can be found in the space between stars that is called interstellar medium (ISM) which is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
+The gas and dust in ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
+Effect of ISM in stellar formation is undeniable; ISM provides raw material for formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
+Studying ISM is not only essential for understanding of the formation of stars but also it is necessary for interpretation of stellar evolution in that stars release their material into ISM when they reach at the end of their evolution.
 
-In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the interstellar medium (ISM) which is due to gravitational instabilities.
+% Metallicity
+Metallicity, which is defined as the ratio of abundance of metal to the abundance of hydrogen atom, affects formation and evolution of stars indisputably.
+In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in ISM which is due to gravitational instabilities. 
 The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
-Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution.
-Numerical simulations have shown that magnetic fields in the cores become super-critical and collapse\citep{Basu97}.
-In the process of  collapsing, an accretion disk is formed and significant magnetic flux is lost while the star also gradually loses its angular momentum.
-Powerful winds are magnetocentrifugally driven from the surface of the disk and turn into a jet-like flow due to magnetic hoops stresses \citep{Shu94}.
-This wind flows from the protostellar core and sweeps up gas into a massive molecular outflow.
-Massive stars form from massive cores, which are highly energised.
-These stars are highly luminous, therefore, they ionize their surrounding gas into \hii regions.
-GMCs lose much of their original mass due to photo-evaporation.
-Most of the mass lost returns to the diffuse interstellar medium and completes the cycle of star formation, which then starts a new cycle (see~\cite{McKee07} for more detail).
+Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution (see~\cite{McKee07} for more detail).
+\cite{Walch11} showed that in case of the large scale turbulence the amount of metallicity on star formation is negligible, but if turbulence is decaying  metallicity has high impact and stabilizing self-gravitating cores.
+Metals also play an important role on heating, cooling and ionizing processes in ISM. %%ADD ref.
+Since cooling is one of the main reason of condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed.
+%Sahar: should I talk about metallicity in stars and their relation with age?
 
-The study of star formation has been an ongoing process and extends into the present era.
-The physical processes of star formation can be studied by direct observation.
+%what does SED look like?
+Our primary source of information for galaxies, specifically unresolved ones, is their SEDs.
+Broadly speaking, young and hot stars emit most of their light in Ultraviolet (UV) wavelengths, evolved stellar population show themselves in optical and near-Infrared (NIR) emission and gas and dust heated by stellar emission are bright in Mid-IR (MIR) or far-IR (FIR) wavelengths.
+Therefore, UV-to-IR SEDs contains valuable information about stellar evolution and their ISM. 
+Other wavelengths regimes in SEDs (i.e. X-ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shock, are beyond the scope of this thesis.
+general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rate (SFR), emit bulk of their energy in UV, while light of quiescent galaxies are dominated by optical and IR emission
+Detail information about age of stellar populations and other properties of galaxies can be determine by properly modelling of galaxy SEDs.
+
+ %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass
+Stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, is widely utilized from 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
+A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grains emission such as polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}, to fit the observed SEDs.
+Many groups modelled SEDs for different type of galaxies and created templates of SEDs. (for more information see review of \cite{Walcher11} on fitting of SEDs and references therein).
+Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs using the templates.
+Code Investigating GALaxy Emission ({\em CIGALE})~\citep{Noll09} is one example of codes that find best SED fittings.
+It combines some of the SED models to find best SED fitting for given observed data in the rest-frame of UV-to-IR and find physical properties of galaxies such as SFR, Stellar mass and dust attenuation.
+
+Formation of stars is a complicated process and directly affect on galaxies evolution. 
+Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc.
 For more than 50 years, the numerical simulations, the empirical and theoretical laws, which describe the star formation rate have been investigated; nevertheless, their results have never been precise.
-Formation of stars is a complicated process.
-Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc.
-Thus to fully understand this intricate process, many theories have been proposed and numerical simulations are carried out.
+There are empirical scaling laws to relate the star formation to other properties of galaxies. 
+The most well-known of these scaling laws is the relation between the surface density of the star formation rate (SFR) and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}.
+Similar to KS law, another scaling relation was derived which is a linear scaling between the total SFR and the mass of molecular gas (refer to reviews~\cite{Elmgrenn11, Kennicutt12}).
 
-Despite the complex physical properties, fortunately there are empirical scaling laws to relate the star formation to other properties of galaxies.
-The most well-known of these scaling laws is the relation between the surface density of the star formation rate (SFR) and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law \citep{Schmidt59, Kennicutt98a}.
-Similar to KS law, another scaling relation was derived which is a linear scaling between the total SFR and the mass of molecular gas (refer to the review by \cite{Elmgrenn11}).
-More recently, \cite{Shi11} derived another scaling relation, which relates the surface density of the SFR of galaxies to both gas surface density and the stellar mass.
+In this chapter, we present a review of observational method of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
+A discussion of the ISM, its role on star formation is presented in $\S$~\ref{sec: ism_intro}, In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}.
+The current issues about studying star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
 
-In this chapter, we present the observational review of measuring the star formation rate and other properties that affect measuring and scaling the SFR in nearby galaxies.
-In $\S$~\ref{chap:sfr} we discuss measuring the star formation rate.
-A discussion of the ISM is presented in $\S$~\ref{chap:ISM}, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{chap:starrmass}.
-In $\S$~\ref{chap:metal} we talk about effect of metallicity on SFR.
-The current issues about studying star formation and its relation to other properties of a galaxy and the present project are discussed in $\S$~\ref{chap:cipp}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%ISM%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%-----------------------------------------------------
-% Chapter: SFR
-%-----------------------------------------------------
-\section{Star Formation Rate}
-\label{chap:sfr}
+\section{Interstellar Medium}
+\label{sec: ism_intro}
+%how do we observe it
+%what the observation tell us
+% how do we measure the dust and gas
+ISM in galaxies is a complex system with wide range of structures, but this structures can be divided into two main components: Gas and Dust.
+Gas in ISM of galaxies is mostly made of hydrogen and helium with 1 per cent of heavier elements (metals), and can be in the forms of clouds or diffuse regions.
+Gas clouds contains molecular clouds, cold neutral hydrogen (\hi~) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud mediums.
+Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
+%Among these regions in ISM, molecular clouds, \hii~regions and dust clouds have important role in understanding star formation in galaxies. 
+Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observing signatures of the gas in the ISM of galaxies.
+Dust can be observed directly through FIR and sub-mm observation or indirectly through their extinction and attenuation effect (see Sec.~\ref{sec: extinction}).
 
+%%observing \hii region
+%what do we observe
+%how the line is created
+%why it is important for star formation
+
+%%observing molecular clouds
+%what do we observe
+%how the line is created
+%why it is important for star formation
+
+%%observing molecular clouds
+%what do we observe
+%how the line is created
+%why it is important for star formation
+
+%%observingdust
+%what do we observe
+%how the line is created
+%why it is important for star formation
+
+\hii~regions are generally associate with star formation 
+%\subsection{Ionized regions}
+
+%\subsection{Molecular clouds}
+Molecular clouds in ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$)~\cite{Bolato08}.
+These clouds are cold and dense enough to form simple molecules; hence the name, but they are surrounded by cloud of atomic gas~\cite{Kennicutt12}.
+The area, where the hydrogen is in a molecular form but the carbon is in atomic state, is called the transition region, dark gas, photo-dissociation regions or photon-dominated regions~\citep[e.g.][]{van88,Hollenbach99}.
+
+%\subsection{Dust}
+
+\subsection{Map of the ISM}
+\label{sec: ismmap}
+A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer. 
+Neutral and molecular hydrogen are the most common elements in the ISM.
+Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
+Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.
+
+\subsubsection{Direct Measurement of the Gas}
+
+The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
+This method can be promising provided that the spatial resolution of observational data is high enough; nonetheless, due to technical limitations, attaining enough spatial resolutions to resolve clouds is almost impossible.
+This problem shows itself for distant galaxies more than nearby galaxies.
+As a result, using this method is limited and has a lot of uncertainties.
+
+\subsubsection*{Molecular Clouds}
+
+ The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
+H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
+The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but the molecular gas also contains heavier elements such as carbon and oxygen which are combined to form CO \citep{Bolato13}.
+
+CO has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy.
+Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
+Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
+Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.
+
+\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is :
+\begin{equation}
+L_{CO} = D^2 \int I_{CO} d\Omega 
+\end{equation}
+where D is the distance to the cloud.
+$I_{CO}$ is the CO brightness temperature integrated over the line profile.
+It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the linewidth.
+For a uniform cloud with a radius $R$, the CO luminosity is given by
+
+ \begin{equation}
+L_{CO} = \pi R^2 T_{CO} \Delta V
+\end{equation}
+
+Galactic molecular clouds are self-gravitating systems. Thus, using the Virial theorem would lead to calculating the mass of the cloud.
+
+ \begin{equation}
+ \label{equ: vir}
+ M_{cloud} = L_{CO} \sqrt{\frac{4\rho}{3\pi G T_{CO}}}
+ \end{equation}
+ where $\sqrt{\frac{4\rho}{3\pi G T_{CO}}}$ is called the conversion factor.
+Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related \citep{Young91}.
+The relation between CO emission and H$_2$ cloud mass is shown as
+
+\begin{equation}
+N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
+\end{equation}
+where X$_{CO}$ is the conversion factor (also known as the X-factor).
+The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in metallicity, etc.
+Though assuming constant conversion factor cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with low metallicity there are uncertainties.
+Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}.
+
+In order to empirically determine the relation between H$_2$ masses to CO luminosities, many observational attempts have been made in both galactic and extragalactic scales.
+One of the most significant studies in this regard was \cite{Solomon87} who studied this relation on more than 273 clouds inside the Milky Way and found the strong correlation between Virial mass of clouds and CO luminosity.
+In the Local Group galaxies, several groups measured the sizes, line widths, and CO luminosities of molecular clouds to investigate the relation between Virial mass and CO luminosity in other environment than the Milky Way.
+However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes.
+To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud.
+
+Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32 \citep[e.g.,][]{Wilson89, Wilson90}.
+Figure {~\ref{fig: mco}} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10.
+The extragalactic molecular clouds are similar to those in the Milky Way.
+The conversion between the CO luminosity and H$_2$ masses is still a controversial topic \citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
+Problems regarding metallicity are not solved yet and it is still not clear whether the conversion factor is global or local.
+
+\begin{figure}
+\label{fig: mco}
+\centering
+\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
+\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds.
+The Virial masses measured from selected high spatial resolution CO observations are shown.
+The extragalactic molecular clouds are very similar to those in the Milky Way.
+Adapted from \cite{Young91}}
+\end{figure}
+
+\subsubsection*{Neutral Gas}
+
+Neutral hydrogen clouds are traced by 21-cm emission.
+The 21-cm emission comes from the fact that most of hydrogen in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state.
+The electron and proton spins in the ground state can be parallel (i.e.
+both spin up) or anti-parallel (i.e.
+proton's spin is up and electron's spin is down or vice versa).
+
+The energy state of anti-parallel mode is slightly less than parallel mode.
+Hence, electrons in the parallel mode have a tendency to flip to the anti-parallel mode (atoms always want to be in the state with lowest energy possible).
+Since the energy difference between these two states is small, eventually it takes millions of years before this transition happens.
+There are large amounts of atomic hydrogen in the ISM.
+Therefore, at any given time, there are enough hydrogen atoms that are emitting the 21-cm radiation, even though the transition is really rare.
+
+The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission.
+Atomic hydrogens, that are along the line-of-sight contribute to the energy received.
+These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (HI is detectable in most spiral galaxies and some elliptical galaxies).
+Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick \citep{Braun09}.
+
+\subsubsection{Dust Emission as a Tracer of Gas}
+
+Studying the gas cloud in the ISM of distant galaxies by using direct methods is almost impossible and not practical.
+\cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-millimetre continuum emission from the dust; continuum dust emission is generally optically thin.
+The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}.
+This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission.
+
+ One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore.
+The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies.
+Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}.
+So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
+
+There are many disadvantages regarding the use of the gas to dust ratio in the ISM.
+In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
+\cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains.
+Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps \citep{Hildebran83}.
+Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1 \citep{Ealas12}.
+Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately \citep{Corbelli11}.
+
+In addition to all the disadvantages mentioned before, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary.
+To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate \citep{Ealas12}.
+The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas \citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
+
+Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems.
+Unfortunately, at present, given the available devices and technologies, we cannot reach a high-resolution that is sufficient to detect the gas cloud directly.
+Therefore, so far this method is the best available solution for measuring the total gas in distant galaxies.
+
+\subsection{Extinction and Attenuation}
+\label{sec: extinction}
+In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed.
+More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by \citep{Calzetti01}.
+
+Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
+The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source.
+
+Attenuation refers to the effect of dust with embedded light sources distributed throughout.
+The dust itself can be clumpy or smooth\citep{Calzetti13}.
+In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions.
+Dust scattering's effect depends on whether it is in or out of the line of sight.
+When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer.
+This is the typical situation that comes across when studying galaxies or extended regions within galaxies.
+
+In order to describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
+At UV/optical/near-IR wavelengths, the radiative transfer equation is:
+
+\begin{equation}
+\frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
+\end{equation}
+where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth, a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients.
+$\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight.
+Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in \citep{Draine03}.
+The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m is neglected in the equation above.
+This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, it causes underestimation of the SFR.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%SFR%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{SFR}
+\label{sec: sfr_intro}
+%beside the normal ones; add SFR based on PAHs, add SFR from SED
 Understanding formation of stars leads to understanding galaxy formations.
@@
 As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars \citep{Calzetti13}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%Stellar Mass%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%chapter: ISM
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Interstellar Medium}
-\label{chap:ism}
-
-Interstellar medium (ISM) is referred to the space between stars in a galaxy, which is full of a thin hydrogen and helium gas and small amounts of heavier elements called metals.
-These elements can have neutral, ionized, or molecular forms and can be in gas phase or solid state.
-The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions.
-The ISM has a huge impact on the formation and evolution of stars.
-Since stars are born in the ISM and release their material into the ISM when they reach the end of their evolution, studying the ISM is essential in the understanding of the formation and evolution of stars.
-
-Considering the effects of the ISM on studying the SFR is important for two main reasons.
-First, stars are born from the gas; therefore, for scaling the star-formation rate in a galaxy, knowledge on the amount of gas is necessary.
-The other impact is that gas and dust in the ISM absorb the UV or optical emission from stars and re-emit it in the IR, or scatter the stellar light.
-Thus for tracing the star-forming region, the effect of dust must be taken into account, otherwise the SFR might be underestimated.
-\subsection{Molecular clouds}
-\subsection{Ionized regions}
-\subsection{Dust}
-
-\subsection{Map of the ISM}
-\label{sec: ismmap}
-
-A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer.
-Neutral and molecular hydrogen are the most common elements in the ISM.
-Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.
-
-\subsubsection{Direct Measurement of the Gas}
-
-The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
-This method can be promising provided that the spatial resolution of observational data is high enough; nonetheless, due to technical limitations, attaining enough spatial resolutions to resolve clouds is almost impossible.
-This problem shows itself for distant galaxies more than nearby galaxies.
-As a result, using this method is limited and has a lot of uncertainties.
-
-\subsubsection*{Molecular Clouds}
-
- The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
-H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
-The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but the molecular gas also contains heavier elements such as carbon and oxygen which are combined to form CO \citep{Bolato13}.
-
-CO has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy.
-Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
-Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
-Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.
-
-\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is :
-\begin{equation}
-L_{CO} = D^2 \int I_{CO} d\Omega 
-\end{equation}
-where D is the distance to the cloud.
-$I_{CO}$ is the CO brightness temperature integrated over the line profile.
-It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the linewidth.
-For a uniform cloud with a radius $R$, the CO luminosity is given by
-
- \begin{equation}
-L_{CO} = \pi R^2 T_{CO} \Delta V
-\end{equation}
-
-Galactic molecular clouds are self-gravitating systems. Thus, using the Virial theorem would lead to calculating the mass of the cloud.
-
- \begin{equation}
- \label{equ: vir}
- M_{cloud} = L_{CO} \sqrt{\frac{4\rho}{3\pi G T_{CO}}}
- \end{equation}
- where $\sqrt{\frac{4\rho}{3\pi G T_{CO}}}$ is called the conversion factor.
-Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related \citep{Young91}.
-The relation between CO emission and H$_2$ cloud mass is shown as
-
-\begin{equation}
-N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
-\end{equation}
-where X$_{CO}$ is the conversion factor (also known as the X-factor).
-The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in metallicity, etc.
-Though assuming constant conversion factor cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with low metallicity there are uncertainties.
-Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}.
-
-In order to empirically determine the relation between H$_2$ masses to CO luminosities, many observational attempts have been made in both galactic and extragalactic scales.
-One of the most significant studies in this regard was \cite{Solomon87} who studied this relation on more than 273 clouds inside the Milky Way and found the strong correlation between Virial mass of clouds and CO luminosity.
-In the Local Group galaxies, several groups measured the sizes, line widths, and CO luminosities of molecular clouds to investigate the relation between Virial mass and CO luminosity in other environment than the Milky Way.
-However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes.
-To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud.
-
-Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32 \citep[e.g.,][]{Wilson89, Wilson90}.
-Figure {~\ref{fig: mco}} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10.
-The extragalactic molecular clouds are similar to those in the Milky Way.
-The conversion between the CO luminosity and H$_2$ masses is still a controversial topic \citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
-Problems regarding metallicity are not solved yet and it is still not clear whether the conversion factor is global or local.
-
-\begin{figure}[h]
-\label{fig: mco}
-\centering
-\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
-\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds.
-The Virial masses measured from selected high spatial resolution CO observations are shown.
-The extragalactic molecular clouds are very similar to those in the Milky Way.
-Adapted from \cite{Young91}}
-\end{figure}
-
-\subsubsection*{Neutral Gas}
-
-Neutral hydrogen clouds are traced by 21-cm emission.
-The 21-cm emission comes from the fact that most of hydrogen in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state.
-The electron and proton spins in the ground state can be parallel (i.e.
-both spin up) or anti-parallel (i.e.
-proton's spin is up and electron's spin is down or vice versa).
-
-The energy state of anti-parallel mode is slightly less than parallel mode.
-Hence, electrons in the parallel mode have a tendency to flip to the anti-parallel mode (atoms always want to be in the state with lowest energy possible).
-Since the energy difference between these two states is small, eventually it takes millions of years before this transition happens.
-There are large amounts of atomic hydrogen in the ISM.
-Therefore, at any given time, there are enough hydrogen atoms that are emitting the 21-cm radiation, even though the transition is really rare.
-
-The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission.
-Atomic hydrogens, that are along the line-of-sight contribute to the energy received.
-These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (HI is detectable in most spiral galaxies and some elliptical galaxies).
-Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick \citep{Braun09}.
-
-\subsubsection{Dust Emission as a Tracer of Gas}
-
-Studying the gas cloud in the ISM of distant galaxies by using direct methods is almost impossible and not practical.
-\cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-millimetre continuum emission from the dust; continuum dust emission is generally optically thin.
-The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}.
-This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission.
-
- One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore.
-The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies.
-Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}.
-So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
-
-There are many disadvantages regarding the use of the gas to dust ratio in the ISM.
-In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
-\cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains.
-Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps \citep{Hildebran83}.
-Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1 \citep{Ealas12}.
-Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately \citep{Corbelli11}.
-
-In addition to all the disadvantages mentioned before, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary.
-To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate \citep{Ealas12}.
-The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas \citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-
-Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems.
-Unfortunately, at present, given the available devices and technologies, we cannot reach a high-resolution that is sufficient to detect the gas cloud directly.
-Therefore, so far this method is the best available solution for measuring the total gas in distant galaxies.
-
-\subsection{Extinction and Attenuation}
-\label{sec: ism}
-In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed.
-More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by \citep{Calzetti01}.
-
-Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
-The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source (left panel of Fig.{~\ref{fig:duste}}).
-
-Attenuation refers to the effect of dust with embedded light sources distributed throughout.
-The dust itself can be clumpy or smooth\citep{Calzetti13}.
-In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions (right panel of Fig.{~\ref{fig:duste}}).
-Dust scattering's effect depends on whether it is in or out of the line of sight.
-When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer.
-This is the typical situation that comes across when studying galaxies or extended regions within galaxies.
-
-\begin{figure}[h]
-\label{fig:duste}
-\centering
-\includegraphics[width=16cm]{../image_intro/dustextinction}
-\caption{The cartoon of: a) a point source behind a screen of dust, a typical situation to have an extinction; and b) the distribution of stars and clumps of dust, typical system, when attenuation effect is observed.
-Adopted from \cite{Calzetti13}}
-\end{figure}
-
-In order to describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
-At UV/optical/near-IR wavelengths, the radiative transfer equation is:
-
-\begin{equation}
-\frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
-\end{equation}
-where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth, a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients.
-$\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight.
-Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in \citep{Draine03}.
-The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m is neglected in the equation above.
-This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, it causes underestimation of the SFR.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%chapter :stellar mass
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Stellar Mass}
-\label{chap:starmass}
+\section{Stellar mass}
+\label{sec: starmass_intro}
 One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass.
@@
 Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference.
-Comparing the results from measuring stellar mass within galaxies shows that the deferences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
+Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
 In the following we address the approaches of measuring stellar mass in galaxies in more detail.
@@
 Beside they can be used for more distanced galaxy as well as nearby galaxies \citep{Zhu10}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%Preview%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%chapter: KS law
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Preview}
+\label{sec: pre_intro}
+%Thesis questions.
 
-% \section{Scaling the SFR Using Schmidt-Kennicut Law}
-
-% The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas.
-\cite{Schmidt59} assumed the constant IMF of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way.
-He scaled SFR with a power {\it n} of the gas mass, $M_{gas}$.
-Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$.
-A power law relation between surface densities of star formation and gas is known as the Schmidt law and is written as:
-% \begin{equation}
-% \Sigma_{SFR} \propto \Sigma_{gas}^n
-% \end{equation}
-% where $\Sigma_{SFR}$ is surface density of star formation, $\Sigma_{gas}$ is the surface density of gas in a galaxy and, {\it n} is the power index.
-
-% Following \cite{Schmidt59}, many groups worked on the scaling relation between the surface density of star formation, and the surface density of gas.
-\cite{Buat89} assumed the constant H$_2$/CO ratio and a \cite{Scalo86} initial mass function for the Milky Way.
-They measured SFR from the UV flux corrected and included molecular and atomic gas to derive the correlation between the star formation rate and the gas surface density.
-Another major work in that year was \cite{Kennicutt89}.
-By using H$\alpha$ emission for star formation, and HI and CO as a tracer of gas with constant H$_2$/CO, for more than 15 galaxies, he determined the average H$\alpha$ flux can be scaled with the average gas surface density to a power between 1 and 2.
-To get better results he calculated star formation rate both as a function of galactocentric radius and averaged over whole galaxy disks.
-He also showed that the correlation is more accurate with using only HI as a tracer of gas.
-
-% A decade later, \cite{Kennicutt98a} examined another group of galaxies.
-He used H$\alpha$, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$.
-Using this power index, the Schmidt law can be rewritten as:
-
-% \begin{equation}
-% \Sigma_{SFR} \propto \Sigma_{gas}^{1.4\pm0.15}
-% \end{equation}
-% which is often referred to as the Kennicutt-Schmidt (KS) law.
-
-% In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution.
-For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$.
-He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$.
-He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
-% It should be noted that the KS law can not be applied for the whole range of gas densities.
-In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g.
-in regions far outside the optical disk \citep[e.g.,][]{Martin01, Bigiel08}
-
-% The Schmidt-Kennicutt scaling relation for star formation is valid for different types of galaxies both in the local universe \citep[e.g.,][]{Kennicutt98a, Bigiel08} and at high-Z \citep[e.g.,][]{Genzel10}, but it is strange that they only consider the effect of gas component while in reality various ISM and stellar objects affect the processes of formation of stars.
-Current proposed Schmidt relations, do not include the effects of metallicity \citep{Gnedin10}, dust grains, radiation shielding of H$_2$ regions \citep[for a review, see][]{Hollenbach99}, and stellar gravitational effects, as they only invoke the gas component.
-Existing stars which form over the whole galaxy's life time are the reason for many of the processes mentioned above.
-As an example the gas angular momentum can be removed or nuclear SFRs can be increased by the gravitational effects of stellar bars in normal galaxies \citep[e.g.,][]{Sersic67}.
-
-% \cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density.
-Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges.
-\cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying on a large sample of galaxies.
-They showed this relation as a power law relation and referred to it as the extended Schmidt law:
-
-% \begin{equation}
-% \Sigma_{SFR} \propto \Sigma_{gas}^{\alpha} \Sigma_{star}^{\beta}
-% \end{equation}
-% where $\Sigma_{SFR}$ is SFR surface density, $\Sigma_{gas}$ and $\Sigma_{star}$ are gas mass and stellar surface density.
-$\alpha$ and $\beta$ are the power law indexes.
-They showed that this relation not only predicts SFR as well as the KS law for galaxies and spatially resolved regions ($\sim$1 kpc sizes) where the KS law works, but also is acceptable for low surface brightness galaxies and regions where the KS law fails.
-
-% \begin{figure}[h]
-% \label{fig:duste}
-% \centering
-% \includegraphics[width=16cm]{../image_intro/schmidtvsextended}
-% \caption{Comparing The extended Schmidt law (a) and the Kennicutt-Schmidt relationship (b) for predicting the SFR.
-The solid and dotted lines are the best fit and observed 1-$\sigma$ scatter, respectively.
-The fit to the KS law (right panel) is done excluding LSB and early type galaxies.
-Adapted from \cite{Shi11}.}
-% \end{figure}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %chapter: current work
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Current issues and the Present Project}
- \label{chap:cipp}
- Studying formation of stars helps us understand the formation and evolution of the universe.
-Since forming stars contains many complex physical processes, theoretical studies cannot yet give a complete picture of star formation.
-Therefore empirical studies are used to find scaling laws indicating, which parameters have effects on star formation.
-Between different scaling relations for star formation, the KS law is the most tested empirical star formation law.
-Since 1959, many studies have tested KS law on regions inside the Milky Way, nearby galaxies and high redshift galaxies.
-Not only observational studies, but also  simulations both apply and investigate KS law.
-Despite all these studies, there are still many unsolved questions about the KS law; Is it really a good correlation?
-What is the slope, and is it unique?, Does SFR surface density only scale with gas density?
-does the scatter affect by a second parameter(s)?
-What is the limit for applying the KS law?
-Is the SFR surface density correlation with total gas density stranger than with the H$_2$ surface density alone?
-
-Many groups are studying the KS law from different approaches to answer the questions listed in above.
-The extended Schmidt law is a newer version of the KS law, which by considering the effect of old stellar population on the SFR provides stronger correlation for the SFR than the other scaling laws.
-Although in original paper this law is tested on large sample of various types of galaxies, but further studies are necessary, due to the fact that this law is tested on the total SFR and not on different regions on galaxies to determine effect of environment on the SFR.
-In this project, the extended version of the Schmidt law will be tested on the Andromeda galaxy using both pixel by pixel relation and radial average along the disk.
-To due so star formation rate will be measured using equations~\ref{equ: halphaplus24} and ~\ref{sfr_tot_IR}.
-In order to find the gas surface density, direct method to map the ISM is chosen.
-Stellar surface density will be calculated by calibrations from both \cite{Eskew12} and \cite{Zhu10}.
-
-The Andromeda galaxy is chosen for this project due to its similarity in the structure to the MW.
-Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "global" picture, whereas, studies of the MW are limited by our location within the Galaxy.
-The Andromeda is closest spiral galaxy to the MW, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
-Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g.
-metallicity, surface brightness and etc.).
-All these parameters make the Andromeda a suitable test bed for studying the scaling law.
-The KS law has been tested on the Andromeda galaxy many times but the results have been controversial.
-The range of slope of KS law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10, Ford13}.
-Testing extended Schmidt law on the Andromeda galaxy would help us recognise parameters that affect the star formation in the Andromeda galaxy and leads us to model and simulate star formation more accurately.
-Also it helps us answer questions about in what types of the regions (e.g.
-in case of different surface brightness, metallicity, distance from the disk, etc.) effect of the stellar mass is more important.
+\addcontentsline{toc}{section}{Bibliography}
+\bibliographystyle{apj.bst} 
+\bibliography{ref_intro}

### 2016-07-06 version0.0/paper2.tex
adding prelude to into. section

@@
 \chapter[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
+\defcitealias{Hossein12}{T12}
+\defcitealias{Kinney96}{K96}
+\defcitealias{Noll09}{N09}
+
 %----------------------------------------------------------------------------------------
@@
         \includegraphics[width=\textwidth]{../image_paper2/k96.jpg}
-        \caption{\citetalias{Kinney96} spectra template for 12 types of galaxies from \citetalias{Hossein12} paper (Fig.
-1 in \citetalias{Hossein12}).
+        \caption{\citet{Kinney96} spectra template for 12 types of galaxies from \citet{Hossein12} paper (Fig.
+1 in \citet{Hossein12}).
 The type of each template is shown in each frame.
@@
 \begin{table}
-\caption{Description of the properties of \citetalias{Hossein12} galaxies; the output result of {\em CIGALE}}     
+\caption{Description of the properties of \citet{Hossein12} galaxies; the output result of {\em CIGALE}}     
 \label{tab: props}
@@
 As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map.
-In this network, 5 of the templates from \citetalias{Kinney96} are categorized as quiescent galaxies and the rest are starbursts.
+In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts.
 Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
@@
                 \caption{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid.
-In this network again, 5 of the \citetalias{Kinney96} templates are categorized as quiescent and 7 as starbursts.
+In this network again, 5 of the \citet{Kinney96} templates are categorized as quiescent and 7 as starbursts.
 However, this time 2  templates (SB5 and SB6) are separated from the starburst groups.}
@@
                 \end{subfigure}
-                \caption{Classification of fitted galaxy SEDs from \citetalias{Hossein12} using the $1\times2$~networks trained from the \citetalias{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
+                \caption{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~networks trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
 Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
@@
         \caption{$12\times12$~2D SOM results.
-Upper pabel: SOMs trained using the \citetalias{Kinney96} templates.
+Upper pabel: SOMs trained using the \citet{Kinney96} templates.
 For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right).
@@
 The properties of the galaxies in each group are in good agreement with their morphological types.
+
+\addcontentsline{toc}{section}{Bibliography}
+\bibliographystyle{apj.bst}
+\bibliography{ref_paper2.bib}

### 2016-07-06 version0.0/paper3.tex
adding prelude to into. section

\chapter{Data Mining in Nearby Galaxies}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} %%( I am not really happy with this introduction but it is the best I can have for now:/ )
%General information about galaxies %(Maybe it is too generic?!!)
Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
Galaxies are an active and complicated systems, that are constantly changing.
There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.

% Nearby galaxies and their importance 
Nearby galaxies play an important role in learning about galaxies' formation and evolution.
These galaxies are close enough to be able to observe various regions inside them in details.
As a result, many studies are devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole%(Some more references here)
, and many others use these results in analyzing data from high-redshift galaxies. %(Some more references here)
The amount of data that is acquired from nearby galaxies is increasing daily.
Advances in technology helps to both observe and store enormous amount of data from sky.%The sky?! 
Telescopes and surveys gather data from nearby galaxies in variuse wavelengths and from these data we can measure physical properties of galaxies (e.g. stellar mass, star formation rate (SFR), dust mass, gas mass)~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), with a distance of $\sim$0.78~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
Images of this galaxy provide us a detail view of inside of a spiral galaxy from distance.
M31 data was a target of many telescopes (e.g. {\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.

\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
Using the mid-IR data from Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of the dust in M31.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data of the galaxy to study PAHs and other line emissions in the ISM.

Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of undergoing processes in the galaxy.
The amount of the observed data and measured quantities of M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
Knowledge discovery and data mining methods are designed to extract hidden information from data and are tested in many astronomical studies.
However, to the best of our knowledge, this study is the first study that uses a data mining method on data from nearby galaxies. %%% ehh

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usages in astronomy.
A data mining algorithm learns about data from sets of trainings, which can be supervised or unsupervised.
The supervised trainings refer to methods, that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
On the contrary, the unsupervised methods train without any prior knowledge of output results. 
They solely work based on the underlying structure of input data.   
The unsupervised methods are very useful tools in knowledge discovery studies on input data, which we do not have any insight of them (or when we want to make sure that we did not miss any valuable information in our previous studies). %%% ehh to after or part.

%SOM
One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein12, Hossein14,Hossein16,Ellison16a}.
ANNs are designed to work in the same way that the neurons work in a human mind.
They are networks of interconnected neurons (nodes), which all of the connections are weighted.
These networks are used to study about nonlinear and complex relations between input and output data.
%These relations can be applied to the new sets of data with similar feature

One of the most well-known unsupervised neural network in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
SOMs map and visualize a complex and nonlinear high dimension data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
Since 1990s, many studies utilized SOMs for object classification and clustering (e.g. classifying quasars' spectra, star/galaxy classifications, gamma-ray bursts clustering and classification of light curves), and photometric redshift estimations~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper

% other Unsupervised methods
The purpose of this project is to have a new insight into nearby galaxies using M31 data with focusing on relations between PAHs and other properties of the galaxy.
To fulfill this purpose, an unsupervised data mining method is the most suitable choice. %%eh  
K-means algorithm, SOMs, and hierarchical clustering are main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more

For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of the clusters.
In the hierarchical clustering method, the user must define dissimilarity between the groups, and the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure. 
Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method miss-classifies the data~\citep[][and references therein]{Mangiameli96}.
We chose SOM method over K-means due to the fact that SOMs not only clusters data, but also shows similarity and dissimilarity between each cluster.
Therefore, we can cluster our sample data and study the underlying structure of data, simultaneously.

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply SOM algorithm on M31 data, and trained 1D and 2D networks.
Using smaller size networks we study the properties of the clusters and investigate relations between PAHs features with other features in M31.
We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM, which leads to prediction of the unmeasured quantities in a galaxy.
Assuming that all the spiral nearby galaxies have similar properties, we apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is another spiral nearby galaxy. 
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101, that we use in this study. 
We describe the SOM method in Section $\S$~\ref{sec: method}. 
The results of the 1D SOM networks and studying PAHs in M31 is presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the result of 2D SOM networks and how we use them to extract information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{Sample of study}
\label{Sec: data_SOMN}

We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}) as inputs for SOMs.
We chose those specific regions due to availability of the PAHs data for them.
Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
Table~\ref{tab: data} shows the full list of the data and their unit for both M31 and M101.
We divided each values by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
Since the resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match the resolutions causes loosing all the information in some of the input data (e.g. the spectroscopic data).
On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve it~\citep{Aniano12}.
Therefore, we did not perform any resolution matching in this paper and used data in their original resolutions.

\import{../image_paper3/text_files/tables/}{tab_data.tex}

  \begin{figure*}
    \subfloat[MIPS 24~$\mu$m image of M31 from~\cite{Gordon06}, with position of 10 regions \label{fig: regions in m31}]{
      \includegraphics[width=\textwidth]{../image_paper3/images0.0/M31/M31.png}
    }
    \hfill
    \subfloat[IRAC 3.6~$\mu$m image of M101~\cite{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
      \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}}
    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
    \label{fig:dummy}
  \end{figure*}

%M31 data 
%%%%% Sahar: More detail, right?
    \subsection{M31 data}
     \label{Sec: data_M31_SOMN}

     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations. 
     They used {\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
     \cite{Dim15} also measured metallicity and of radiation hardness index (RHI) for these 10 regions.
     We used the measured fluxes for PAHs featured, metallicity and RHI of each region as an input for SOMs.

     We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] narrow badn and [\oiii] narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAHs fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, mass of molecular clouds, mass of atomic gas (H\,{\sc I}), total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm dust}$ and mass data from \cite{Draine14}.

    \subsection{M101 data}
    \label{Sec: data_M101_SOMN} 
     For M101 galaxy, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
     We also added their measurement of metallicity and RHI for these regions to our sample.
     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101. 
     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
     The Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in \cite{Rahmani16}.

      Some of the correlations between some wavelengths and properties of galaxies are well-known.
     For example, \citep{Rahmani16} used IRAC1 band emission to calculate the stellar mass, or FUV, NUV and MIPS24 emission to measure the SFR values. 
     To make sure that we wouldn't use some of the observed data as an input data in various forms, we removed all the observed data, that were used to calculate these properties from the input sample.
     We used these sample as the main input for creating SOMs.
     Fig.~\ref{fig: cor_all} shows Pearson correlation coefficients with a confidence level of $95\%$ for the input data.

      \begin{figure}
                \centering
                \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
            \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all the in the subset 0. The colours show the Pearson correlation coefficients where 1 means highly correlated and -1 is highly anti-correlated quantities. The non-significant correlations were left empty.}
            \label{fig: cor_all}
        \end{figure}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Method
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\section{METHOD}
\label{sec: method}
 \subsection{Self Organizing Maps}
 \label{sec: som}
 The SOM is a clustering method which reduces the dimension of data to lower dimensions, while preserving topological features of the original data~\citep{Kohonen98}. 
 The results of the SOM are shown with a map of neurons.
 Each neuron has a fixed position in the map, and may contain one or more samples from input data, \boldit{V} $\in \Re^n$.
 A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data is associated with each node and will be varied during the training process.
 The process of creating SOM, happens over series of $N$ iterations.
 In each iteration, the algorithm calculates the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with ``$D_{j_{min}}$". 
 This neuron is the winner node and is calling Best Matching Unit (BMU). 
 The weight vectors in the neighbourhood of BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
  \begin{equation}
            \label{equ: weight adj}
            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
 \end{equation}
where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
Values for number of neurons, L(t) and R(t) are arbitrary. 
~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more details.

     In order to create SOM, we used {\sc MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     An SOM in {\sc NNT} can be created by {\sc newsom} library which works in two phases; ``ordering phase" and ``tuning phase" . 
     Phase one is the ``ordering phase". 
     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.

     The second phase is the ``tuning phase".
     In this phase the neighbourhood distance is at its minimum, but learning factor decreases very slowly.
     This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. 
     We chose number of epochs the tuning phase be 3 times more than number of epochs in the ordering phase.

     To present our results, we use {\sc nnt}'s built-in plotting tool.
     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
     In the maps, the purple hexagonal shapes shows the neurons. 
     The distances are shown by the grey cycle colours: the darker the colour, the larger the distance between neurons.
     Neurons with zero hits are left empty.
     In Section~\ref{sec: mock_sample} we used {\sc newsom} to create SOMs from a mock sample to illustrate how this method works and how we can interpret the results.

     One feature of the SOM method is that there is no rule and restriction on number of clusters.
     Users must decide the size of networks based on their data set and their usages of the results .
     There has been few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
     We varied size of SOMs from $1\times2$ to $50\times50$ to choose the most suitable size for our maps, and found that based on the size of our sample, the 2D SOMs to be 10$\times$10. 
     We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively. 
     %Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
     %Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
     %All the other parameters are default values in {\sc newsom} library and cannot be changed by the users.

\subsection{Mock sample}
\label{sec: mock_sample}

         \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/mock_sample.png}
            \caption{SOM of the mock sample. The axes show the position of the neurons. Hexagonal shapes represent the neurons. The grey cycle colours show the differences between weight of each neuron where white is the minimum differences and black has the maximum one.}
            \label{fig: sample}
        \end{figure}

To show how self-organizing maps work, we created a mock sample, which contains a few regions.
We gave two information to each sample; amount of dust and the SFR.
 Therefore, we have a simple input data with low dimension; each entry only can get either 0 or 1 as high or low SFR, and 0 or 0.5 to show high or low amount of dust for the mock regions.
 We generated an SOM with the size of $10 \times 10$ from the sample, using the method that described in Sec.~\ref{sec: som}.
 Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
 The axes show the position of the neurons in a $10 \times 10$ network and the hexagonal shapes are the neurons.

Using this method, as expected, we are able to divide the mock sample into 4 distinct groups: regions with high SFR and high amount of dust, regions with low SFR and high amount of dust, regions with high SFR and low amount of dust, and regions low SFR and low amount of dust. 
The plot in the Fig.~\ref{fig: sample}, clearly shows these divisions.
In that plot, the upper part belongs to regions with low amount of dust, while the lower part belongs to the high amount of dust.
The left part of the plot, is where regions with low SFR belong to and the right side is for high SFR regions.
Grey to black colours show the border between regions.
This network is considered as a trained network, and can used to cluster any new data set with similar entries.

Having two regions with exactly the same values in all their quantities in the real world is almost impossible. 
Therefore, one can find a network with high amount of the neurons, which separates the input data completely, and clusters them into separate groups.
However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
Therefore, it is up to the user to decide the similarity or dissimilarity between the input data based on the number of neurons.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One dimensional Self-organizing maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of the exploring M31 data with 1D maps is to monitor the general behaviour of data. 
    1D SOMs can have from the minimum number of clusters, $1\times2$, to the highest number of cluster possible.
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without the clustering the data.
    On the other hand, higher grid 1D SOMs are a helpful tool to get quick insight into data.
%    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
%Clustering
 %   \subsection{Clustering M31 data}

        In order to monitor how the data behaves, we created SOMs with two to fourteen neurons (Fig.~\ref{fig: M31_nets_1d}).
        The $1\times2$ network (Fig.~\ref{fig: M31_net_1by2}) shows how the M31 data can be divided into two broad categories.
        While the $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network that all the regions in M31 are completely separated.
        Since in the higher network sizes, regions have more space to be separated based on their differences, we can see that from $1\times2$ to $1\times14$ network the M31 regions separated from each other increasingly, until they are completely separated.

        In Fig.~\ref{fig: M31_net_1by2}, it is clear that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
        The medium grey colour between two neurons indicates that there are some similarity between two groups, but they are not very similar. 
        By increasing the size of the neurones to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that the region 2 separates itself from the other regions and occupies the middle neuron.
        The white colour between two left neurons suggests that regions, which occupy these neurons are very similar to each other, while the black colour between two right neurons expresses otherwise.

        %%%Talking about four right regions
        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAHs flux intensity compare to other regions (Fig. 5 in \cite{Dim15} paper). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensity in the SPIRE bands and have high dust luminosity.
        The higher values in the intensity of the PAHs, SPIRE bands and the dust luminosity could be the reason that these 4 regions become separated from the others, in $1\times2$ network.
        Besides, Regions 1, and 9 are in the 10~Kpc ring, region 2 is slightly out of the 10~Kpc ring and the region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason of regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        The similarity in the other input values with the other regions causes regions 1, 2, and 9 gradually move towards other regions, and have more distance with region 10, in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

        %%% Repeated from the other paragraphs
        %%%Talking about 6 left regions
        %In both Figs.~\ref{fig: M31_net_1by2} and~\ref{fig: M31_net_1by3} the most left neuron is occupied with regions 3 to 8. 
        %These regions all are located outside the inner or 10~kpc rings (See fig.~\ref{fig: regions in m31}).
        %Since the locations of these regions have similar physical properties, they occupy a same neurons in a smaller SOMs.
        %As it can be seen in the $1\times3$ SOM (Fig.~\ref{fig: M31_net_1by3}), the region 2 is moved to the middle neurons.
       % The fact that this region is slightly out of the 10~kpc ring makes region 2 to be the first region to move towards the neurons that occupied with regions 3 to 8. 
       % In the $1\times14$ SOM (Fig.~\ref{fig: M31_net_1by14}), although all the regions were separated, but the colour between regions 10 to the other regions become completely dark.
       % This dark colour indicates that region 10 is absolutely different, which considering the fact that it is the only regions in the bulge of the galaxy, we expected to see such a distance between this regions and the others.

        \begin{figure}
            \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
             \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by2_all.png}
             }
            \hfill
            \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
            \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by3_all.png}
             }
             \hfill
            \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
             \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by14_all.png}
             }%%% What should I do with this one! It doesn't look good visually
            \caption{SOM of the M31 data from $1\times2$~, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple Hexagonal shapes represent the neurons. The grey cycle colours show the differences between weight of each neuron with white is the minimum differences and black has the maximum one. The numbers in the plot show the regions that are located in each neuron.}
            \label{fig: M31_nets_1d}
        \end{figure}

        %%Network 1by14
        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network, that has no neuron to be occupied with more than one region.
        In a higher grid SOM, network pays more attention to smaller details and differences in the input data.
        Therefore, since at least 14 neurons are needed to separate all the 10 regions in M31, we can conclude that some of the regions have very small differences.
        Regions that are located in similar area in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely show more similarity to each other.
        In Fig.~\ref{fig: M31_net_1by14}, the most right neuron is occupied by region 10.
        Two black colour between this region and the others indicates the high differences between this neuron and the other ones.
        The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences with region 10.

    \subsection{Inside of the 2 neurons network}%%% I will find better title for this subsection
        %What is going on in this section
        \label{sec: inside_the_2_neurons}
        Using SOMs, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other, for a reason.
        This reason can vary from having higher values in some specific wavelengths, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data, that cannot be seen in other groups or in a Galaxy's data as a whole.
        To investigate the later, we showed the Pearson correlation coefficients for the inputs from regions 3 to 8 in Fig.~\ref{fig: cor_cluster1}, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left side of the Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure}

        %%% what regions' version shows and how it compares with the other one:
        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAHs features highly correlate with each other. 
        Also, there are very strong correlations between all the PAHs features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
        However, in Fig.~\ref{fig: cor_cluster1}, 12.0 and 12.7~$\mu$m~PAHs fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most of the other quantities.
        The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between 12 and 12.7~$\mu$m PAH fluxes.
        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient become insignificant.
        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAHs fluxes and the other quantities show themselves.

        For the rest of the PAHs fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity, neither.
        They have correlations with SPIRE emission, but they are weaker than the ones with data from all regions.
        Correlations between PAHs features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
        Many groups used PAHs features as a tracer of SFR by finding correlations between 
        PAHs emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
        These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
        Further analyses show that the absence of correlations between PAHs features and SFR, is because of one outlier in data. 
        When we disregard the outlier data, high correlations between 6.2 to 11.3~$\mu$m~PAHs features and SFR (and L$_{\rm TIR}$) reappear.
        Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAHs features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.
     %   In Fig.~\ref{fig: cor_cluster1}, 6.2, 7.7, 8.3, 8.6, and 11.3~$\mu$m~PAHs features show strong anti-correlations with RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission.

        Anti-correlations between PAHs features and the \halpha, \sii, and \oiii~emission could be the result of one the followings. 
        First, the optical data are not corrected for dust extinction.
        The PAHs features correlate with dust, and \halpha emission is sensitive to dust extinction.
        Therefore, more PAHs features, means more dust and less \halpha~emission (The same for \sii~and \oiii~emission).
        Second, it is the effect of observing apertures.
        If the regions are located in the edge of the H {\sc II} regions we would expect too see more PAHs and less \halpha~emission. %%% reference?
        The anti-correlations between 6.2 to 11.3~$\mu$m~PAHs features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
        \cite{Wu06} discussed these ant-correlations could be the result of destruction of the PAHs due to the high amount of the harder radiation (thus higher RHI).
        On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
        The PAHs features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAHs features underlying continuum emission is from the H {\sc II} regions.
        Therefore, the lower flux of the PAHs features could be the result of the smaller size of PDRs.
        The later reason, which could also describe the anti-correlation between PAHs features and \halpha~emission, seems to be the more probable one. 
        %%% The anti correlation with stellar mass?!! with IRAC3?!!

       Despite the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meanings, we have to mention that, we only used 6 regions to calculate these correlation coefficients.
       Having 6 data points as a sample of the study is not high enough to have a strong conclusion about the PAHs in M31.%%% it doesn't sound right:((
        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differs from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, which their properties are different than the others. %%Again eh!

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
 \section{Two dimensional self-organizing maps}
 \label{sec: 2d_cluster}
    Although 1D networks are great to have a general idea about the data, neurons in 1D maps have maximum two neighbours, which causes some limitation in the results.
    In 2D networks, each neuron has two to six neighbours, which allowed them to to capture a whole picture of the complicated relations in the input data.
    Therefore, we created $10\times10$ 2D networks to study the data in details.
    As mentioned in previous sections, the size of SOMs are arbitrary and users must decide about it based on what their goals of using SOMs are.
    In this section we chose $10\times10$ size despite that we knew, from the size of our input data, that most of the neurons would be empty.
    Using 2D networks, we are mostly interested in the ability of the SOMs in showing underlying structure of the data rather than its clustering features.
    \import{../image_paper3/text_files/image_texts/}{all.tex}
    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of M31 data.
    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions completely separated from each other in Fig.~\ref{fig: all_derived_ones}.

    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with very bright colour between their neurons, which presents that these two regions are very similar.
    Considering the position of these two regions in M31 (Both of these regions are right on the edge of the star forming rings in the galaxy), similarity of these two regions were predictable.
    Position of region 3 on the SOM is close to the position of regions 4 and 7, but with darker colour between the nodes. 
    In Fig.~\ref{fig: regions in m31} it is clear that, this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
    Regions 5 and 6 are in their second neighbourhood on the SOM, with a medium gray colour between them.
    These two regions are around the inner ring of the galaxy.
    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star forming activities, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.

    Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
    However, region 1 is in an area of the galaxy with lesser diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
    Region 2 is more distant from other regions in the galaxy, and placed in the star forming ring.
    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffused \halpha~emission.
    Therefore, place of region 2 in the SOM is more favoured towards regions 1 and 4. 
    Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.

    In order to analyse effects of any input data on the final SOM, in the following we created SOMs from various subsets of data.
    We compare results of the subsets with one another and with SOM created from all data in Fig.~\ref{fig: all_derived_ones}.

    \subsection{Subsets}
    \label{sec: subsets}
            For analysing subsets, we creating SOMs by using only PAHs data, as well as using all data except PAHs ones (Fig.~\ref{fig: PAHS_or_not_PAHs}).
             \import{../image_paper3/text_files/image_texts/}{PAHS_or_not_PAHs.tex}
            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, showed that the general position of regions in those networks are the same. 
            The region 10 is in one corner of the all three networks.
            However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
            Regions 9 and 10 are totally isolated in SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
            In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
            This indicates that there are more similarity between PAHs features from all 10 regions then the other input data.

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data), gradually, by adding data from other quantities of galaxies to the input data. 
            The order of adding data is the same as order of data in Fig.~\ref{fig: cor_all}, i.e. SOM in Fig~\ref{fig: inc_D_col3s}a was created from PAHs data and H$\alpha$ emission as input data, SOM in Fig~\ref{fig: inc_D_col3s}b created from PAHs, H$\alpha$ emission and [\sii] continuum as input data, and so on. 
            \import{../image_paper3/text_files/image_texts/}{col3byall.tex}

            SOM algorithm assigns random weight to each network, that causes the overall position of regions in networks (even with the same input data) changes in each run of the algorithm.
            However, the position of each region regarding to other regions changes dramatically only because of the new sets of input data is given to the algorithm (assuming all the initial values for the run are intact).
            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: inc_D_col3s}a,~\ref{fig: inc_D_col3s}d,~\ref{fig: inc_D_col3s}g,~\ref{fig: inc_D_col3s}k, and ~\ref{fig: inc_D_col3s}l, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data in the network.

            Comparing Figs.~\ref{fig: inc_D_col3s}a to ~\ref{fig: inc_D_col3s}o shows that adding \halpha~emission data to PAHs features causes regions 9 and 10 become isolated. 
            Increasing dimension of the input data makes region 10 more isolated.
            The relative position of regions 4 and 7 stays the same with increasing the input data. 
            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ do not have any adequate effect on the networks.
            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.

            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to study effects of the input data on SOMs, further.
            Subset 1, that are listed in Tab.~\ref{tab: subset1}, includes all the inputs data except data from stellar mass.
            Tab.~\ref{tab: subset5} is the list of data that were used in a subset 2, which includes all data except the fact that instead of the individual PAH fluxes we added them all together and have total PAH flux. 
            For subset 3 ( in Tab.~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m from subset 2.
            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs that are created by data from subsets 1 to 3, respectively.
            The rest of the subsets are discussed in the Appendix.~\ref{sec: app_2d_soms_SOMN}.

            The results from Table~\ref{tab: subset1} is shown in Fig.~\ref{fig: subset1}. 
            In this SOM compare with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
            Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
            Since the differences in the amount of the stellar mass were one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of the region 10.
            Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.

            \import{../image_paper3/text_files/tables/}{subset1.tex}
            \import{../image_paper3/text_files/image_texts/}{subset1.tex}

            Changing from separate values for each PAH features to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compare to the one in Fig.~\ref{fig: all_derived_ones}. 
            Distance between the relative position of regions 6 and 8 increased significantly, while the position of region 2 moved closer to the positions of regions 4 and 7.
            The winner neurons for regions 3 and 5 moved towards each other, but the colours between them became much more darker.

            \import{../image_paper3/text_files/tables/}{subset5.tex}
            \import{../image_paper3/text_files/image_texts/}{subset5.tex}

            Fig.~\ref{fig: subset6} shows the SOM generated from data that are listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except SPIRE 250 and 500~$\mu$m emission.
            Although for most of the regions we see the changes in their positions, the colours between neurons changed, too. 
            %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
            The distance between the positions of the regions 4 and 2 are increased.
            The same happened for distances between regions 7, 3 and 6.
            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from input data moved the positions of the regions further from each other. 
            \import{../image_paper3/text_files/tables/}{subset6.tex}
            \import{../image_paper3/text_files/image_texts/}{subset6.tex}

            %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.
            \subsubsection{Prediction observing data using M31}

                On SOMs we can see relations between the input data from each region regarding to the other regions.
                These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
                Therefore, we have the probability distribution of quantities of each values given data from other regions.
                We can use these probability distribution to estimate missing data for regions.

                To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
                Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
                \import{../image_paper3/text_files/image_texts/}{sim_subset1.tex}
                We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
                Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
                In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.

                We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
                \begin{equation}
                \label{equ: prob1}
                    P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
                \end{equation}
                Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
                We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
                This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.

    \subsection{Validating networks using M101 data}
    Another application of SOM for nearby galaxies is that to apply the trained networks on the data from other galaxies in order to prediction properties of the regions in them. %%eh
    As an example of this application, we generated an SOM using data from M31 that held in common with M101 data (Fig.~\ref{fig: subset9}a). 
    In this SOM, the same as the others, region 10 is separated from other regions in M31.
    Regions 7 and 4 are close to each other with very light colours between their neurons, and the same as the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
    \import{../image_paper3/text_files/image_texts/}{subset9.tex}

    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
    Region 6 in M31 and region 2 in M101 both occupied the same neuron in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these two regions have similar properties. 
    Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
    Region 6 in M31 is located near the inner ring of the galaxy (see Fig.~\ref{fig: regions in m31}).
    Both regions have relatively low amount of PAHs emission and medium amount of the SFR regarding the other regions in the galaxy, which makes them very similar regions.

    Region 7 in M101 is located in the nucleus of the galaxy and have relatively higher quantities than the other regions.
    This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
    Since the bulge of a spiral galaxy has different environment from its nucleus, region 7 in M101 and region 10 in M31 are not occupied the same neuron in the SOM, and have a medium grey colour between their neurons.

    Region 1 in M101 is located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities than the ones in region 7.
    The lower values for fluxes of the PAH features, and relatively moderate amount of the SFR caused this region places between region 4 and 5 of M31 in the network. 
    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated itself from other regions and located between region 9 and 10 in M31.
    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high amount of fluxes of PAH features. 
    This region also shows a high amount of the SFR and the stellar mass, which describes why the location of region 4 from M101 in the SOM is close to regions 9 and 10 from M31.

    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
    We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
    Increasing dimension of the data and the number of regions would help to have more reliable networks.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}
\label{sec: summary}
Self-organizing maps can be used to explore hidden subgroups and underlying structure of the data.
In this project we investigated applications of the Self-organizing maps in data from nearby galaxies.
We utilized the SOM method to study data from two well-studied galaxies; M31 and M101.
Data from nearby galaxies can be clustered in various networks with different sizes/dimensions based on the information needed from the data. 
A network with one dimension and a few neurons, can be used for general classification, while for more detailed clustering, a higher number of neurons should be used.

Using smaller-sized self-organizing maps, the M31 data were clustered in 2 major groups; we found correlations that could not have otherwise been seen without clustering.
For example in Sec.~\ref{sec: inside_the_2_neurons}, we found that six of the regions in M31 create a subgroup of data, that have lower amount of PAHs flux.
Flux from the PAHs features in these regions highly anti-correlated with \halpha~emission despite that considering Flux from the PAHs features in all regions highly correlates with SFR.
Our analyses of smaller-sized networks showed that using this method we can find hidden subgroups in data to extend our knowledge of inside the galaxies.

In the maps with larger sizes, networks can be used to illustrate the relative relations of the regions with one another.
We found the relative similarity between M31 regions, by varying the size of networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; we concluded that some of the region in M31 (e.g. regions 4 and 7) are very similar.
A two-dimensional networks provide us a more complete picture of the data.
Using these networks, we show a relative relations between regions in M31.

We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
We also applied the SOMs from M31 data to M101 data and found regions with similar properties in both galaxies placed in close regions in the SOMs.
We show that using this ability of the SOM, we can predict properties of regions in other nearby galaxies very fast.

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%------------------

\addcontentsline{toc}{section}{Bibliography}
\bibliographystyle{apj.bst}
\bibliography{ref_paper3.bib}

### 2016-07-09 version0.0/asli.tex
finishing intro

@@
 }
-\newcommand{\makeacknowlege} {
-I would like to thank all my Friends in Western.
-Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad,
+\newcommand{\makeacknowlege} { 1) Pauline
+2) Els, Sophia, Hossein,
+3)I would like to thank all my Friends in Western.
+Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
+4) bacheha
+5) western ppl; Jodi, Brian, Henry, Phin,...
+6) Mohad, shahin, pejman, pouria, masood,babak
+7) fako famil
 }
@@
 \newcommand \kpc {\,{\rm kpc}}
-\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
-\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
-\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
-\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
-\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
-\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
-\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
+\newcommand \sigmagas {$\Sigma_{\mathrm {gas }} $\ }
+\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
+\newcommand \eqsigmagas {\Sigma_{\mathrm {gas }}}
+\newcommand \sigmasfr {$\Sigma_{\mathrm {SFR }} $\ }
+\newcommand \eqsigmasfr {\Sigma_{\mathrm {SFR }}}
+\newcommand \sigmastar {$\Sigma_{\mathrm {star }} $\ }
+\newcommand \eqsigmastar {\Sigma_{\mathrm {star }}}
 \newcommand \halpha {H$\alpha $\ }
@@
 \newcommand \Herschel {{\it Herschel }}
-\newcommand \sii {S~{\textsc II}} 
-\newcommand \oiii {O~{\textsc III}} 
-\newcommand \hi {H~{\textsc I}\ }
-\newcommand \hii {H~{\textsc II}\ }
-\newcommand \oii {O~{\textsc II}}
+\newcommand \sii {[S~{\textsc II}]} 
+\newcommand \oiii {[O~{\textsc III}]} 
+\newcommand \hi {H~{\textsc I}}
+\newcommand \hii {H~{\textsc II}}
+\newcommand \oii {[O~{\textsc II}]}
+\newcommand \nii {[N~{\textsc II}]}
 

### 2016-07-09 version0.0/intro0.0.tex
finishing intro

@@
 Gas in ISM of galaxies is mostly made of hydrogen and helium with 1 per cent of heavier elements (metals), and can be in the forms of clouds or diffuse regions.
-Gas clouds contains molecular clouds, cold neutral hydrogen (\hi~) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud mediums.
+Gas clouds contains molecular clouds, cold atomic neutral hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud mediums.
 Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
@@
 
-%%observing \hii region
-%what do we observe
-%how the line is created
-%why it is important for star formation
+Molecular clouds in ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$), masses in molecular clouds range from few to million solar masses. %~\citep{Bolato08}.
+Density in the molecular clouds is not uniform; dense and colds clumps.
+Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
+However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them really hard to detect in visible light.
+The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
+CO molecules take a third place in case of abundance in the molecular clouds.
+In fact, most of our knowledge from extragalactic molecular clouds comes from observing emission line of CO molecules, which due to their heavy weight, they have very low rotational state and can be excited in the temperature of molecular clouds.
+Other heavier molecules have emission lines which are detectable in spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study properties of molecular clouds i.e.
+their mass (see Sec.~\ref{sec: ismmap} for more details).
 
-%%observing molecular clouds
-%what do we observe
-%how the line is created
-%why it is important for star formation
+The molecular clouds are surrounded by cloud of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
+Hydrogen atoms in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state. 
+The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. proton's spin is up and electron's spin is down or vice versa). 
+The energy state of anti-parallel mode is slightly less than parallel mode.
+Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
+However, difference between these two states are very small and it takes millions of years before the transition happens.
+The large amount of hydrogen atoms, on the other hand, compensate the rareness of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
+The observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of ISM, which leads to understanding star formation process in ISM~\citep{Walter08}.
 
-%%observing molecular clouds
-%what do we observe
-%how the line is created
-%why it is important for star formation
+\hii~regions are hot and low density regions that are mostly located in the disk of spiral galaxies.
+Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as star formation tracers~\citep[e.g.][]{Kennicutt98b,Calzetti13}. 
+High energy UV photon emitted by massive new born stars have sufficient amount of energy to ionize their surrounding gas.
+~\halpha emission is main observational feature\hii~regions.
+Temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, \sii, \oii, \oiii, and \nii from \hii~regions.
+Studying \hii~regions provide valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
 
-%%observingdust
-%what do we observe
-%how the line is created
-%why it is important for star formation
+Dust has insignificant effect on mass of ISM, but it plays crucial roles in evolution of ISM.
+The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
+In spiral galaxies dust are in cold regions $\sim 30$~K and has power low distribution of size.
+Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
+MIR emission from dust grains are manly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed types``A" and ``B'' stars~\cite{Peeters04}.
+Large grains that are either heated by light from star forming regions or by interstellar radiation field from total stellar population emit most of their light in FIR~\citep[e.g.][]{Calapa14, lu14}
+Dust are main source of extinction and reddening of star lights (See Sec.\ref{sec: extinction} for more information).
 
-\hii~regions are generally associate with star formation 
-%\subsection{Ionized regions}
-
-%\subsection{Molecular clouds}
-Molecular clouds in ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$)~\cite{Bolato08}.
-These clouds are cold and dense enough to form simple molecules; hence the name, but they are surrounded by cloud of atomic gas~\cite{Kennicutt12}.
-The area, where the hydrogen is in a molecular form but the carbon is in atomic state, is called the transition region, dark gas, photo-dissociation regions or photon-dominated regions~\citep[e.g.][]{van88,Hollenbach99}.
-
-%\subsection{Dust}
-
-\subsection{Map of the ISM}
+\subsection{Map of ISM}
 \label{sec: ismmap}
-A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer. 
-Neutral and molecular hydrogen are the most common elements in the ISM.
-Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.
+Measuring mass of gas in galaxies is a necessary step to now how much row material is available for forming stars.
+A map of total gas mass in ISM is produced by direct observations of gas or using interstellar dust as a tracer. 
+Neutral and molecular hydrogen are the most common elements in ISM. 
+Therefore, for producing the total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
+Another way to do the mapping is assuming that the ratio of total gas and dust is constant across the galaxy, and convert dust observations to the map of total gas mass.
 
@@
 
-\subsubsection*{Molecular Clouds}
+%\subsubsection{Molecular Clouds}
 
- The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
-H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
-The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but the molecular gas also contains heavier elements such as carbon and oxygen which are combined to form CO \citep{Bolato13}.
-
-CO has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy.
+CO molecule has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy. 
 Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
-Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
-Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.
+Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen~\citep[e.g.][] {Sanders84}.
+Higher rotational transition of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.
 
@@
 $I_{CO}$ is the CO brightness temperature integrated over the line profile.
-It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the linewidth.
+It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the line-width. 
 For a uniform cloud with a radius $R$, the CO luminosity is given by
@@
 
-Galactic molecular clouds are self-gravitating systems. Thus, using the Virial theorem would lead to calculating the mass of the cloud.
+Galactic molecular clouds are self-gravitating systems.
+Thus, using the Virial theorem would lead to calculating the mass of the cloud.
 
@@
  where $\sqrt{\frac{4\rho}{3\pi G T_{CO}}}$ is called the conversion factor. 
-Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related \citep{Young91}.
+ Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related~\citep{Young91}. 
  The relation between CO emission and H$_2$ cloud mass is shown as
@@
 where X$_{CO}$ is the conversion factor (also known as the X-factor).
-The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in metallicity, etc.
-Though assuming constant conversion factor cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with low metallicity there are uncertainties.
-Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}.
+The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties of regions such as metallicity. 
+Though assuming constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties. 
+Various groups are working on observation from different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.
 
-In order to empirically determine the relation between H$_2$ masses to CO luminosities, many observational attempts have been made in both galactic and extragalactic scales.
-One of the most significant studies in this regard was \cite{Solomon87} who studied this relation on more than 273 clouds inside the Milky Way and found the strong correlation between Virial mass of clouds and CO luminosity.
-In the Local Group galaxies, several groups measured the sizes, line widths, and CO luminosities of molecular clouds to investigate the relation between Virial mass and CO luminosity in other environment than the Milky Way.
+In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made in both galactic and extragalactic scales. 
+One of the most significant studies in this regard had been done by~\cite{Solomon87}, who studied this relation on more than 273 clouds inside the Milky Way and found a strong correlation between Virial mass of molecular clouds and CO luminosity.
+In the Local Group galaxies, several groups measured size, line width, and CO luminosity of molecular clouds and investigate the relation between  their Virial masses and CO emission in environment other than the Milky Way.
 However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes.
-To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud.
+To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Bolato13}.
 
-Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32 \citep[e.g.,][]{Wilson89, Wilson90}.
-Figure {~\ref{fig: mco}} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10.
+Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
+Fig.~\ref{fig: mco} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10. 
 The extragalactic molecular clouds are similar to those in the Milky Way. 
-The conversion between the CO luminosity and H$_2$ masses is still a controversial topic \citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
+The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
 Problems regarding metallicity are not solved yet and it is still not clear whether the conversion factor is global or local.
@@
 The extragalactic molecular clouds are very similar to those in the Milky Way.
-Adapted from \cite{Young91}}
+Adapted from~\cite{Young91}}
 \end{figure}
 
-\subsubsection*{Neutral Gas}
-
-Neutral hydrogen clouds are traced by 21-cm emission.
-The 21-cm emission comes from the fact that most of hydrogen in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state.
-The electron and proton spins in the ground state can be parallel (i.e.
-both spin up) or anti-parallel (i.e.
-proton's spin is up and electron's spin is down or vice versa).
-
-The energy state of anti-parallel mode is slightly less than parallel mode.
-Hence, electrons in the parallel mode have a tendency to flip to the anti-parallel mode (atoms always want to be in the state with lowest energy possible).
-Since the energy difference between these two states is small, eventually it takes millions of years before this transition happens.
-There are large amounts of atomic hydrogen in the ISM.
-Therefore, at any given time, there are enough hydrogen atoms that are emitting the 21-cm radiation, even though the transition is really rare.
-
+%\subsubsection{Neutral Gas}
 The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission. 
 Atomic hydrogens, that are along the line-of-sight contribute to the energy received. 
-These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (HI is detectable in most spiral galaxies and some elliptical galaxies).
-Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick \citep{Braun09}.
+These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
+Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.
 
@@
 Studying the gas cloud in the ISM of distant galaxies by using direct methods is almost impossible and not practical. 
-\cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-millimetre continuum emission from the dust; continuum dust emission is generally optically thin.
+\cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
 The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
@@
 The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies. 
-Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission \citep{Abdo10}.
+Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
 So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
@@
 \cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains.
-Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps \citep{Hildebran83}.
-Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1 \citep{Ealas12}.
-Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately \citep{Corbelli11}.
+Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps~\citep{Hildebran83}. 
+Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1~\citep{Ealas12}. 
+Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately~\citep{Corbelli11}.
 
 In addition to all the disadvantages mentioned before, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
-To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate \citep{Ealas12}.
-The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas \citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-
+To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
+The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
 Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems. 
@@
 In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed.
-More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by \citep{Calzetti01}.
-
+More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by~\citep{Calzetti01}. 
 Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
@@
 At UV/optical/near-IR wavelengths, the radiative transfer equation is:
-
 \begin{equation}
@@
 \end{equation}
-where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth, a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients.
+where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth.
+a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
 $\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. 
-Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in \citep{Draine03}.
+Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
 The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m is neglected in the equation above. 
@@
 \label{sec: sfr_intro}
-%beside the normal ones; add SFR based on PAHs, add SFR from SED
-Understanding formation of stars leads to understanding galaxy formations.
-Characterisation of the star formation processes, such as the total SFR and the initial mass function of a galaxy, is necessary in examining its structure formation \citep{McKee07}.
-The main problem is that measuring the SFR is not trivial and depends on the galaxy morphology, metallicity, IMF, the spatial resolution of a target system, etc.
+Understanding formation of stars leads to understanding galaxies formation and evolution. 
+Characterisation of the star formation processes such as SFR and IMF is necessary in examining galaxies structure formation~\citep{McKee07}. 
+Measuring the SFR is not trivial and depends on galaxy's morphology, metallicity, IMF, spatial resolution of a target system, and other propertied of galaxies. 
 There is a large number of review papers in the literature on how stars form and how their formation is traced. 
-From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by \citep{McKee07}.
-From an observational standpoint, star formation is discussed by \cite{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
+From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
+From an observational standpoint, star formation is discussed by \cite[][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.
 
-Many groups have been trying to define a technique to calibrate emission from the newly-born, hot and massive ``O'' and ``B'' stars to the rate at which stars are being formed.
-Emission from the young massive stars are normally used as a tracer of the current SFR.
-Using luminosity of massive stars makes sense if one considers that star formation rate has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer.
-The number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region.
-To do so, the stellar IMF must be known.
-However, knowing the Stellar IMF is not enough.
-To have a reliable SFR indicator, the stellar IMF must be fully sampled, which means that in the highest-mass bin at least one star is formed and all other mass bins have one or more stars (see section ~\ref{sec: imf}).
-
-The ``O'' and ``B'' stars can be observed by both using direct and indirect emission from stars; thus the SFR indicators are categorized based on these methods of observation.
-In the direct method, the SFR indicators can be probed by the ultraviolet (UV), optical, and near-infrared (NIR) emissions, while for probing the stellar light obscured by dust, mid/far-infrared emission is used.
-The ionizing photons are used in the indirect method.
-They are emitted by massive stars and traced by the ionized gas \citep[e.g.,][]{Calzetti04, Calzetti07}.
-In principle, the SFR is traced by the UV emission, the optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-millimetre range by using the Bremsstrahlung emission.
-Moreover, high mass binaries, massive stars and supernova explosions produce X-ray emissions which can be used as a tracer of star formation.
-Each of these tracers has some systematic errors, and one should decide which of these methods are more precise for a given system.
-for example using dust IR emission as an indicator is not precise in dwarf galaxies with small amounts of the gas, although still errors from dust extinction and attenuation must be considered (see section ~\ref{sec: ism}).
+In principle, emission from new stars can be traced by UV emission, optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission.
+Some of these emission are directly from stars, e.g UV emission, and some are from ISM components around stars that absorb and re-emit light of young stars, e.g FIR emission.
+Techniques to calibrate emission from the newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed were subjects of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
+Emission from the young massive type ``O'' or ``B'' stars are normally used as a tracer of the current SFR.
+One of the main assumptions for using luminosity of massive stars is that SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
+By knowing IMF, the number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region.
+To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
+In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.
 
@@
 \label{sec: imf}
-One of the most fundamental and difficult questions that a complete theory of star formation must answer is the initial mass function.
-In order to determine the SFR from calibrated photometry data, it is necessary to know the IMF.
-Most problems in modern astrophysical studies regarding the origin and evolution of stars and galaxies can be solved by varying an IMF \citep{Bastin10}.
-\cite{Salpeter55} empirically derived the IMF from the observed stellar luminosity function of the Solar neighbourhood \citep{Shu87}.
-He introduced a power-law IMF of the form:
+One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar (or cores) initial mass distribution of star forming region. 
+Since, most of SFR calibrations use emission from specific mass range stars, it is necessary to know the stellar IMF to determine a more accurate SFR from calibrated photometry data. 
+Most problems in modern astrophysical studies regarding the origin and evolution of stars and galaxies can be solved by sampling an IMF ~\citep{Bastin10}. 
+\cite{Salpeter55} empirically derived stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
+He introduced a power-law IMF in the form of:
 
@@
 \end{equation} 
-where M is the mass of a star, $\gamma$ is the power index, and N is the number of stars in some logarithmic mass range $\log M + d\log M$.
+where M is the stellar mass, $\gamma$ is the power index, and $N$ is the number of stars in logarithmic mass range of $\log M + d\log M$.
 
-In the late 70s, it was recognised that using the single power-law IMF over all stellar masses is not a correct assumption \citep{Kroupa93, Bastin10}.
-Since then, many groups have studied the IMF and found different power laws for it (Fig.{~\ref{fig: imf}} ).
-Most SFR calibrations have the same assumption that the IMF is constant across all environments which is adopted from the standard IMF of \cite{Kroupa01}:
-
+In the late 70s, it was recognised that using the single power-law IMF over all stellar masses is not a correct assumption and might overestimate number of low-mass stars~\citep{Kroupa93, Bastin10}. 
+Since then, many groups have studied the stellar IMFs and found different power-law relations for them (Fig.~\ref{fig: imf} ). 
+Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
 \begin{align}
@@
 where $\chi(M)$ is the number of stars between masses $M$ and $M+dM$. 
-Although the Salpeter IMF produces more low-mass stars then the Krupa IMF, they produce almost the same number of the high mass stars.
-Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration's constant by 1.6 \citep{Calzetti13}.
-\cite{Bastin10} reviewed  the IMF  by using many observational results and showed that the IMF is constant and universal, although there are uncertainties in different mass bins especially at the high mass end.
+Although the Salpeter IMF produces more low-mass stars than the Krupa IMF, they produce almost the same number of the high-mass stars. 
+Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration's constant by 1.6~\citep{Calzetti13}.
+In more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMF overestimate amount of stars in all masses.
+\cite{Bastin10} reviewed the stellar IMF by using many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high mass end.
 
-\begin{figure}[h]
+\begin{figure}
 \label{fig: imf}
@@
 The mass ranges from 0.1 to 120 M$_\odot$.
-Adopted from \cite{Baldry03}}
+Adopted from~\cite{Baldry03}}
 \end{figure}
 
-The careful measurement of the IMF is a key to understanding the SFR.
+The careful measurement of the stellar IMF is a key factor in understanding the SFR. 
 In distant galaxies, only massive stars can be detected; therefore, the IMF must be measured to include all stellar mass ranges in the SFR calibrations. 
-To show the impact of the different IMF assumptions on the SFR calibrations, \cite{Calzetti13} used two different IMFs and derived the SFR calibrations with these new assumptions.
-Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors ranging from 1.4 to 5.6 for different SFR indicators (Table {~\ref{table1}}).
+To show the impact of the different stellar IMF assumptions on the SFR calibrations, \cite{Calzetti13} used two different stellar IMFs and derived the SFR calibrations with these new assumptions.
+Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes SFR calibrations' constants by factors ranging from 1.4 to 5.6 for different SFR indicators (Tab.~\ref{table1}).
 
@@
 
-One of the main issues to study distanced galaxies is the calibration of SFR indicators \citep[e.g.,][]{Lee10}.
-Calibration of SFR indicators can be affected by differences in star formation history (SFH), metallicity, distribution of stellar population and dust between different galaxies \citep{Calzetti13}.
-Depending on spatial resolution of the system one can divide star formation indicators into two categories: resolved and unresolved star formation indicators.
+One of the main issues to study star formation in distant galaxies is calibration of SFR indicators~\citep[e.g.,][]{Lee10}. 
+Calibration of SFR indicators can be affected by differences in star formation history (SFH), metallicity, distribution of stellar population and dust in galaxies~\citep{Calzetti13}. 
+Based on the spatial resolution of a system one can divide star formation indicators into two categories: resolved and unresolved star formation indicators.
 
 \subsubsection{Resolved Star Formation Indicators}
-The most direct way to measure the SFR and trace recent star formation is counting individual objects \citep{Kennicutt12}.
+The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
 These objects mostly have certain ages and usually are referred to as young stellar objects (YSOs). 
-Counting YSOs is a method used for calculating star formation in molecular clouds within $0.5- 1$ kpc of the Solar System.
+Counting YSOs is a method that used for calculating star formation in molecular clouds within $0.5- 1$ kpc of the Solar System. 
 The number of YSOs can be converted to SFR using: 
-
 \begin{equation}
-SFR(YSO) = N_{yso} <M> \ \tau 
+SFR(YSO) = N_{yso} <M>/\tau 
 \end{equation}
-where N$_{yso}$ is the number of YSOs, $<$M$>$ is the mean mass of YSO which depends on the stellar initial mass function (IMF; see section~\ref{sec: imf}), and $\tau$ is the lifetime of the YSO considering some uncertainly $\tau \sim 2$Myr \citep{Evans09}.
-The SFR(YSO) is in the unit of M$_{\odot}$yr$^{-1}$.
-Due to observational difficulties, this method can only be applied to the Milky Way and the Solar neighbourhood.
+where N$_{yso}$ is the number of YSOs, $<$M$>$ is the mean mass of YSO which depends on the IMF. 
+$\tau$ is the lifetime of the YSO considering some uncertainly $\tau \sim 2$Myr~\citep{Evans09},and the SFR(YSO) is in the unit of M$_{\odot}$yr$^{-1}$. 
+Due to observational difficulties, this method can only be applied to the Solar neighbourhood and the Milky Way.
 
@@
 However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic clouds can not be resolved. 
-Therefore, most studies use the emission from the ``O" and ``B" stars as tracer of the SFR.
+Therefore, most studies use the emission from the energetic ``O" and ``B" stars as a tracer of the SFR. 
 Another method to measure the SFR is by looking at the colour-magnitude diagram (CMD) of star-forming regions. 
 \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to reproduce the spatially and age-resolved maps of star formation in nearby galaxies. 
-More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to \citep{Kennicutt12}.
+More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}.
 
 \subsubsection{Unresolved Star Formation Indicators}
+
  In star-forming regions farther away than the Magellanic clouds, spatial resolution is not high enough to find all the YSOs. 
-In unresolved systems, luminosity, which is either single band or integrated over some wavelength range, is used as an SFR indicator.
-This method is used to find continuum or line emission at some wavelengths that are sensitive to the young massive stars \citep[e.g.,][]{Kennicutt98b, Calzetti13}.
-\cite{Kennicutt98b} reviewed calibrations of star formation tracers.
-He calibrated luminosity for measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.,][]{Bruzual93}.
+ In unresolved systems, calibrating continuum or line emission at wavelengths that are sensitive to the young massive stars are primary method of measuring SFR.~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
+\cite{Kennicutt98b} calibrated luminosities of galaxies in specific wavelengths for measuring the SFR using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by synthesis models~\citep[e.g.,][]{Bruzual93}.
 
-In unresolved systems, the SFR indicators can be divided into local and global SFR indicators.
+In unresolved systems, the SFR indicators can be divided into local and global ones. 
 The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
-While local calibration is used for regions within a galaxy, on a scale of sub-galaxy \citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+While local calibration is used for regions within a galaxy, on a scale of sub-galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
 The limitations in the spatial resolution of the data on the one hand, and the broader applicability of distant galaxy populations on the other, have brought more attention to the calibrations of global SFR compared with the local SFR calibrations that had been done in the past.
-Yet, because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important \cite{Calzetti13}.
-
-The following subsections describe some SFR indicators in more detail.
-In this paper, we categorise the SFR indicators into tracers based on single-band emission and those that are based on the multi-band emission.
-For each category, we discuss if a calibration can be used as local or global and also describe their differences.
+Yet, because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.
 
@@
 
-In order to derive the conversion between the luminosity in specific wavelengths and the SFR, synthesis models are used \citep{Kennicutt98b}.
+In order to derive the conversion between the luminosity in specific wavelengths and the SFR, synthesis models are used~\citep{Kennicutt98b}. 
 General form of a SFR calibration using single-band emission is: 
@@
 \end{equation}
-where SFR is in units of M${_\odot}$yr$^{-1}$, $L(\lambda)$ is luminosity in erg/s at the wavelength $\lambda$, and C is the constant derived from stellar population models (Starburst99, \cite{Leitherer99}).
+where SFR is in units of M${_\odot}$yr$^{-1}$, $L(\lambda)$ is luminosity in erg s$^{-1}$ at the wavelength $\lambda$, and C is the constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}).
 The constant, C, can vary for different emission, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation needs to remain constant. 
@@
 
-\begin{table}[ht]
-\caption{Luminosity-to-SFR calibrations adapted from \cite{Calzetti13}\label{table1}}
+\begin{table}
 \centering
+\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
+\label{table1}
 \begin{tabular}{ c c c }
 \hline\hline
-Luminosity\footnotemark{} & C\footnotemark{} & Assumptions\footnotemark{}\\
+Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
 \hline
@@
 \end{tabular}
+\begin{tablenotes}
+\item $^1$ Luminosities are in erg s$^{-1}$ and are given as $\nu L_{\nu}$.
+\item $^2$ The constant C appears in equation~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$.
+\item $^3$ Assumptions for mass range of the stellar IMF, which we adopt to have the expression derived by \cite{Kroupa01} (see Sec.~\ref{sec: imf}), and for the timescale $\tau$.
+\end{tablenotes}
 \end{table}
-\footnotetext[1]{Luminosities are in erg/s and are given as $\nu L_{\nu}$.}
-\footnotetext[2]{The constant C appears in equation~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$.}
-\footnotetext[3]{Assumptions for mass range of the stellar IMF, which we adopt to have the expression derived by \cite{Kroupa01} (see section{~\ref{sec: imf}}), and for the timescale $\tau$.}
 
-One of the most common single-band wavelengths, which are used as an SFR indicator, is UV emission.
-UV emission can be an excellent tracer for the SFR due to the fact that the peak of emission for both ``O" and ``B" stars are in the UV part of the spectrum.
-Using spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming \cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as \citep{Leitherer99}
+The most common single-band wavelengths that are used as an SFR indicator, is UV emission.
+UV emission is an excellent tracer for the SFR due to the fact that the peak of emission for young  ``O" and ``B" stars are in the UV part of the spectrum.
+Using spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}
 \begin{equation}
@@
 \end{equation}
-where SFR(UV) is in M$_{\odot}$yr$^{-1}$, $\lambda$ is in $\AA$, and $L(\lambda)$ is in erg/s, while $\lambda$ is in the range of $(0.0912\mu$m $< \lambda < 0.3\mu$m).
-As shown in table ~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few percent.
-However, the calibration constant's changes for shorter timescales, are more significant \citep{Calzetti13}.
+where SFR(UV) is in M$_{\odot}$yr$^{-1}$, $\lambda$ in the range of $(912< \lambda < 3000~\AA$), and $L(\lambda)$ is in erg s$^{-1}$. 
+As shown in table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
+However, the calibration constants' changes for shorter timescales are more significant~\citep{Calzetti13}. 
 The accuracy of the calibration constant is $\pm 15\%$ which can vary as a function of $\lambda$. 
 The UV light can easily be absorbed or scattered by interstellar dust. 
-Therefore, using the UV emission as a tracer might lead to underestimating of the SFR, if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section ~\ref{sec: ism}).
+Therefore, using the UV emission as a tracer might lead to underestimating of the SFR, if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
 
@@
 Ionizing photons emitted from young massive stars ionize the surrounding gas.
-Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators \citep{Kennicutt98a}.
+Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}.
 The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived quantum mechanically. 
-To have such results, the nebula must be optically thick to ionizing photons \citep{Osterbrock06}.
+To have such results, the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}. 
 Being optically thick makes almost all transitions more energetic than Ly${\alpha}$ to be absorbed and re-emited via Ly${\alpha}$ and longer wavelengths.
 This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
-The relation between the SFR, the luminosity of the H$\alpha$ emission line and the ionizing photon rate is \citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
+The relation between the SFR, the luminosity of the \halpha emission line and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
 
@@
 \end{align}
-where SFR(H$\alpha$) is in M$_{\odot}$ yr$^{-1}$, L(H$\alpha$) is in erg/s, and Q(H$^{\circ}$) which is the ionizing photon rate is in units of s$^{-1}$.
-The constant at the right-hand side of equation~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_e=10000$K and density N$_e=100$ cm$^{-3}$ which is the normal case in the interstellar medium.
+where SFR(\halpha) is in M$_{\odot}$ yr$^{-1}$, L(\halpha) is in erg s$^{-1}$, and Q(H$^{\circ}$) which is the ionizing photon rate is in units of s$^{-1}$.
+The constant at the right-hand side of equation~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is the normal case in the interstellar medium.
 All SFR indicators that use the ionization of hydrogen to trace the formation of massive stars are sensitive to the effects of dust.
-Dust extinction (Section ~\ref{sec: ism}) is the most important systematic error for calculating the SFR from hydrogen recombination line.The effects of dust must be measured and H$\alpha$ observations must be corrected or this could lead to underestimating the SFR \citep{Kennicutt98b}.
+Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important systematic error for calculating the SFR from hydrogen recombination line.
+The effects of dust must be measured and \halpha observations must be corrected or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
 
-Another nebular line, which is used as a tracer of the SFR is [OII]$\lambda$3727$\AA$.
-Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has correlation with the H$\alpha$ emission.
-As a result, [OII] luminosity can be used as a tracer of the SFR through H$\alpha$ luminosity.
-\cite{Gallagher89} calibrated the SFR based on the [OII] luminosity by using a sample of 75 galaxies.
+Another nebular line, which is used as a tracer of the SFR is \oii~$\lambda$3727$\AA$.
+Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has correlation with the \halpha emission. 
+As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity.
+\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
 Another calibration for this luminosity was derived by \cite{Kennicutt92}, which has a different calibration factor. 
-In his review on the SFR, \citep{Kennicutt98b} averaged these calibrations and derived the following relation:
+In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
 \begin{equation}
-SFR(O[II]) = 1.4 \times 10^{-41} L(O[II])
+SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
 \end{equation}  
-where SFR(O[II]) is in M$_{\odot}$ yr$^{-1}$, L(H$\alpha$) is in erg/s.
-Although SFR (O[II]) is not as precise as the SFR(H$\alpha$), it is one of major SFR indicators in high redshift galaxies.
-In high redshift galaxies, H$\alpha$ emission line is out of optical bands, as a consequence, calibration of the strongest emission feature in the blue light (O[II]) as a SFR indicator is really useful \citep{Kennicutt98b}.
+where SFR(\oii) is in M$_{\odot}$ yr$^{-1}$, L(\halpha) is in erg s$^{-1}$. 
+Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high redshift galaxies.
+In high redshift galaxies, \halpha emission line is out of optical bands, as a consequence, calibration of the strongest emission feature in the blue light (\oii) as a SFR indicator is really useful~\citep{Kennicutt98b}.
 
@@
 The IR luminosity of a system depends not only on the amount of the embedded dust, but also on the heating rate provided by the stars. 
-Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order the shape of the thermal IR SED depends on the starlight SED \citep{Helou86}.
-The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60  \mu$m) in comparison with the dust heated by old or low-mass stars.
+Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
+The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with the dust heated by old or low-mass stars.
 Therefore, the IR wavelength is able to detect the emission from the young stellar population and be used as an SFR indicator.
 
-24 $\mu$m and 70 $\mu$m bands are two empirical single-band IR SFR calibrators.
+24~$\mu$m and 70~$\mu$m bands are two empirical single-band IR SFR calibrators. 
 The use of these two bands depends on the type of the galaxy studied or the physical environment in different regions within the galaxy. 
 Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) and a local indicator.
-That is because the global case includes the Hubble time integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as: HII regions, large star-forming complexes, etc.
-\cite{Calzetti13}.
-Table ~\ref{table2} shows the constant C from equation~\ref{equ: sfrsingle} for 24 $\mu$m and 70 $\mu$m luminosities and for local (spatial scale $\sim500$ pc for 24$\mu$m band and spatial resolution less than $\sim 1$ kpc for 70 $\mu$m one) and global cases.
+That is because the global case includes the Hubble time integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as: \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
+Table~\ref{table2} shows the constant C from equation~\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities and for local (spatial scale $\sim500$~pc for 24~$\mu$m band and spatial resolution less than $\sim 1$ kpc for 70~$\mu$m one) and global cases.
 
-\begin{table}[ht]
-
-\caption{IR Luminosity to SFR calibrations \label{table2}}
+\begin{table}
 \centering
+\caption{IR Luminosity to SFR calibrations}
+\label{table2}
 \begin{tabular}{ c c c c }
 \hline\hline
-Luminosity\footnotemark{} & C & Assumptions & references\\
+Luminosity$^1$ & C & Assumptions & references\\
 \hline
@@
 \end{tabular}
+\begin{tablenotes}
+\item $^1$ Luminosities are in form of L($\lambda$) = $\lambda$ L($\lambda$) in erg s$^{-1}$
+\end{tablenotes}
 \end{table}
- \footnotetext{Luminosities are in form of L($\lambda$) = $\lambda L(\lambda)$ in erg s$^{-1}$}
- %The SFR(70) calibration constant thus increases when going from whole galaxies to 1 kpc regions, i.e., for decreasing region sizes.
-According to the Li et al.
-(2012) this constant can be interpreted in terms of star formation timescale within each region (Fig.{~\ref{sfr70}}).
-%\begin{figure}
-%\label{sfr70}
-%\centering
-%\includegraphics[width=8cm]{sfr70}
-%\caption{The calibration constant, C$_70$, between SFR and the 70$\mu $m luminosity, from equation~\ref{equ: sfrsingle}, as a function of the physical size of the regions used to derive the calibration.
-The filled red triangles are observed values from Li et al.
-(2010, 2012) and Calzetti et al.
-(2010), using both $Spitzer$ and $Herschel$ data.
-The black stars are from stellar population synthesis models, for constant star formation and a Kroupa (2001) IMF, in the stellar mass range of 0.1-100 M$_\odot$; the mean age of the population that best approximates the observed C70 values is shown.
-This figure is adapted from \cite{Calzetti13}.}
-%\end{figure}
 
@@
 
-Despite the usefulness of having single-band SFR tracers, in many cases, one should be careful about the corrections due to dust effects, luminosity ranges, etc.
-Nowadays, thanks to large surveys, enormous data is available at different wavelengths for galaxies.
-This allows for combining the emission from different bands and finding new calibrations.
-Conversion between SFR and luminosities at different bands mostly helps avoiding problems regarding dust extinction or attenuation (see~\ref{sec: ism}).
-
-The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically proved \citep{Kennicutt12}.
-There are studies that use a higher order polynomial relation to combine luminosities \citep[e.g.,][]{Buat05}; however, this discussion is out of the scope of this paper.
+%%add PAHs here
+Despite the usefulness of having single-band SFR tracers, in many cases the corrections due to dust effects and luminosity ranges increases the uncertainty in measurements.
+Nowadays, thanks to large surveys, enormous data is available at different wavelengths for galaxies, which allows for combining the emission from different bands and finding new calibrations.
+Conversion between SFR and luminosities at different bands mostly helps avoiding problems regarding dust extinction or attenuation (see~\ref{sec: ism_intro}). 
+The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically proved~\citep{Kennicutt12}.
+%There are studies that use a higher order polynomial relation to combine luminosities~\citep[e.g.,][]{Buat05}; however, this discussion is out of the scope of this paper.
 
 Integrating over the full wavelength range of the IR part of spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator. 
-As mentioned earlier, dust absorbs stellar radiation at all wavelengths; however, we only discuss radiation emitted from UV luminous stars.
-It must be noted that since there is no one-to-one mapping between IR and UV emission \citep{Calzetti13}, it is better to use the TIR emission as a tracer of the SFR instead of the IR single-band emission.
+As mentioned earlier, dust absorbs stellar radiation at all wavelengths; however, here we are only interested in radiation emitted from UV luminous stars. 
+It must be noted that since there is no one-to-one mapping between IR and UV emission~\citep{Calzetti13}, it is better to use the TIR emission as a tracer of the SFR instead of single-band IR emission.
 
-\cite{Draine07} modelled $Spitzer$ \citep{Wener04} data and found a calibration for the total infrared luminosity from photometry images instead of using IR SED.
+\cite{Draine07} modelled observations from \Spitzer telescope and found a calibration for TIR luminosity from photometry images instead of using IR SED. 
 \cite{Boquien10} tested this calibration and found the modified version of calibration to estimate total infrared luminosity: 
@@
 \end{equation}
-where $L = \nu L_{\nu}$ and $L_{\nu}$ is the luminosity  in erg/s at frequency $\nu$.
+where $L = \nu L_{\nu}$ and $L_{\nu}$ is the luminosity  in erg s$^{-1}$ at frequency $\nu$. 
 \cite{Calzetti07} indicated that star formation rate calibration for a stellar population undergoing constant star formation over $\tau=100Myr$ is:
@@
 \end{equation}
-where SFR(TIR) is in M${\odot}$yr$^{-1}$, and L(TIR) is in erg/s.
-To do this calculation, it is assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(\rm bol)=L(\rm TIR)$.
+where SFR(TIR) is in M${\odot}$yr$^{-1}$, and L(TIR) is in erg s$^{-1}$. 
+To do this calculation, it is assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{\mathrm{star}}({\rm bol})=L(\rm TIR)$.
+
+As mentioned before emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
+Most of studies used MIR emission, which contains PAHs emission, to calibrate SFR~\citep[e.g.][]{Calzetti07}.
+\cite{Shipley16} calibrated SFR using observation from 105 star framing galaxies with $z < 0.4$ as:
+
+\begin{equation}
+log SFR = A + B log L_{\mathrm{PAH}, \lambda}
+\end{equation}
+where $L_{\mathrm{PAH}, \lambda}$ is luminosity of PAH features at 6.2, 7.7, 11.3~$\mu$m PAHs features and any combination thereof in erg s$^{-1}$.
+Tab.~\ref{table_PAH} shows the constants for each $L_{\mathrm{PAH}, \lambda}$.
+These calibration underestimates SFR for low-redshift galaxies with IR luminosity more than $10^12$erg s$^{-1}$.
+\cite{Shipley16} showed that adding 7.7~$\mu$m features in calibrations reduces the scatter and concluded that this wavelengths provides the most robust SFR tracer.
+
+\begin{table}
+\centering
+\caption{SFR calibrations from PAHs luminosities; adopted from~\cite{Shipley16}}
+\label{table_PAH}
+\begin{tabular}{ l c c}
+\hline\hline
+PAH Feature(s) & A & B\\
+\hline
+6.2 + 7.7 + 11.3 & -42.56 $\pm$ 0.03 & 1.00 $\pm$ 0.03 \\ 
+6.2 & -40.06 $\pm$ 0.09 & 0.96 $\pm$ 0.04 \\ 
+7.7 & -42.38 $\pm$ 0.06 & 1.00 $\pm$ 0.03 \\ 
+11.3 & -44.14 $\pm$ 0.08 & 1.06 $\pm$ 0.03 \\ 
+6.2 + 7.7 & -42.05 $\pm$ 0.04 & 0.99 $\pm$ 0.03 \\ 
+6.2 + 11.3 & -42.52 $\pm$ 0.05 & 1.01 $\pm$ 0.03 \\ 
+7.7 + 11.3 & -42.85 $\pm$ 0.04 & 1.01 $\pm$ 0.03 \\ 
+\hline
+\end{tabular}
+\end{table}
 
@@
 \end{equation}
-where the luminosities are $L = \nu L_{\nu}$ in erg/s, and the coefficient $\alpha$ depends on the bandpasses that are chosen for the UV and IR measurements.
-$\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies is from dust heated by older population stars \citep{Kennicutt12}.
-The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (e.g., \cite{Hao11}.
+where the luminosities are $L = \nu L_{\nu}$ in erg s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses that are chosen for the UV and IR measurements.
+$\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies is from dust heated by older population stars~\citep{Kennicutt12}.
+The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.p][]{Hao11, Leroy08}.
 
-Another common method for using the multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the $24\mu$m emission.
-This combination gives a more accurate dust-corrected estimate of the SFR \citep{Kennicutt09}:
-
+Another common method for using the multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
+This combination gives a more accurate dust-corrected estimate of the SFR~\citep{Kennicutt09}:
 \begin{equation} 
@@
 \end{equation}
-where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg/s.
-L(24) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
+where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg s$^{-1}$. 
+L(24) is the 24~$\mu$m IR luminosity in erg s$^{-1}$, and SFR is in M$_{\odot}$yr$^{-1}$.
 
-\begin{table}[ht]
-\caption{Multi-wavelength dust-corrected luminosities, adopted from \cite{Kennicutt12} \label{table3}}
+\begin{table}
 \centering
+\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
+\label{table3}
 \begin{tabular}{ c c}
 \hline\hline
-Combined luminosities\footnotemark{} & references\\
+Combined luminosities$^1$ & references\\
 \hline
 L(FUV)$_{corr}$=L(FUV)$_{obs}$ + 0.46L(TIR)& Hao et al. (2011)\\
-L(FUV)$_{corr}$=L(FUV)$_{obs}$ + 3.89L(24$\mu$m)& Hao et al. (2011)\\
+L(FUV)$_{corr}$=L(FUV)$_{obs}$ + 3.89L(24~$\mu$m)& Hao et al. (2011)\\
 L(NUV)$_{corr}$=L(NUV)$_{obs}$ + 0.27L(TIR)& Hao et al. (2011)\\
-L(NUV)$_{corr}$=L(NUV)$_{obs}$ + 2.26L(24$\mu$m)& Hao et al. (2011)\\
-L(H$\alpha$)$_{corr}$=L(H$\alpha$)$_{obs}$ + 0.0024L(TIR)& Kennicutt et al. (2009)\\
-L(H$\alpha$)$_{corr}$=L(H$\alpha$)$_{obs}$ + 0.020L(24$\mu$m)& Kennicutt et al. (2009)\\
+L(NUV)$_{corr}$=L(NUV)$_{obs}$ + 2.26L(24~$\mu$m)& Hao et al. (2011)\\
+L(\halpha)$_{corr}$=L(\halpha)$_{obs}$ + 0.0024L(TIR)& Kennicutt et al. (2009)\\
+L(\halpha)$_{corr}$=L(\halpha)$_{obs}$ + 0.020L(24~$\mu$m)& Kennicutt et al. (2009)\\
 \hline
 \end{tabular}
+\begin{tablenotes}
+\item $^1$ Luminosities are in form of L($\lambda$) = $\lambda$ L($\lambda$) in erg s$^{-1}$
+\end{tablenotes}
 \end{table}
-\footnotetext{Luminosities are in the form of L($\lambda$) = $\lambda L(\lambda)$ in erg s$^{-1}$}
 
-Other combinations of luminosities that are used as tracers of the SFR are listed in table ~\ref{table3}.
+Other combinations of luminosities that are used as tracers of the SFR are listed in table~\ref{table3}. 
 These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
-Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer \citep{Kennicutt09}.
+Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.
 
-As mentioned in section ~\ref{sec: imf}, using different IMFs leads to having different SFR calibrations.
+As mentioned in section~\ref{sec: imf}, using different IMFs results in having different SFR calibrations' constant. 
 From table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
@@
 On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than $10\%$ difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
-As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars \citep{Calzetti13}.
+As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. 
-It was pointed out that stellar mass is linked with the structure and star formation history of disc galaxies \citep{Gavvazi96} and all morphologies \citep{Scodeggio02}.
-In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass \citep{Bell00}.
-\cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey \citep[SDSS;][]{York00}.
+Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and all morphologies~\citep{Scodeggio02}. 
+In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass~\citep{Bell00}. 
+\cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey~\citep[SDSS;][]{York00}. 
 They also showed that these results are applied for all morphological types.
@@
 In principle there are two ways to measure stellar mass in galaxies. 
-First is measuring the dynamical mass of galaxies using kinematics \citep{Cappellari06} or lensing \citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
-This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies \citep{Zaritsky94},  and can easily cause uncertainties as high as the order of the measurement.
+First is measuring the dynamical mass of galaxies using kinematics~\citep{Cappellari06} or lensing~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
+This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies~\citep{Zaritsky94}, and can easily cause uncertainties as high as the order of the measurement.
 
-The second method is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
+The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
 This method has uncertainties too, and one must also model the uncertainties. 
-Uncertainties come from uncertainties in the stellar initial mass function (see section{~\ref{sec: imf}}), the stellar evolution models, especially the stage where they have most luminosity in their evolution, and the evolutionary state of galaxy \citep[see,][]{Dalcanton12}, and star formation histories.
+Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where they have most luminosity in their evolution, and the evolutionary state of galaxy~\citep[see,][]{Dalcanton12}, and star formation histories.
 
@@
 To do that, the M/L by can be measured using scale relation between them, from different colours and then multiply it by the surface brightness to calculate the local surface stellar mass density. 
-The M/L scale relations make a connection between two methods of measuring stellar mass \citep{Bell03}.
+The M/L scale relations make a connection between two methods of measuring stellar mass~\citep{Bell03}. 
 These relations are indirect methods for measuring the stellar masses and have high uncertainties in specific cases, but they help to study the stellar mass in large samples. 
@@
 As a result it is important to check the accuracy of total stellar mass estimations and provide methods, which measure and produce a map of the stellar mass surface density distribution in galaxies. 
-This method gives more accurate result than measuring the stellar mass surface density distribution from single-band images rescaled by uniform mass to light ratio \cite{Zibetti09}.
+This method gives more accurate result than measuring the stellar mass surface density distribution from single-band images rescaled by uniform mass to light ratio~\citep{Zibetti09}.
 
@@
 Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. 
-Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
-In the following we address the approaches of measuring stellar mass in galaxies in more detail.
+Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 per cent, so one should be more careful to model subtleties~\citep{McLaughlin05}.
 
 \subsection{Dynamical Mass}
-The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and HI lines.
-Thanks to the current generation of detectors, the H$\alpha$ and CO lines have very high-resolution spectra over most of the optical disk, and cover most regions in the sky.
+The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi lines. 
+Thanks to the current generation of detectors, the \halpha and CO lines have very high-resolution spectra over most of the optical disk, and cover most regions in the sky. 
 Integrated line widths only yield an estimate of a total mass within some (uncertain) isophotal radius.
 
-Resolved rotation curves produced from H$\alpha$, HI and CO lines are proportional to optical emission lines within the optical disk of galaxies, \citep{Courteau13} which helps us to measure the rotational curves.
+Resolved rotation curves produced from \halpha, \hi and CO lines are proportional to optical emission lines within the optical disk of galaxies,~\citep{Courteau13} which helps us to measure the rotational curves.
 The simplest way to estimate the mass of a galaxy is assuming that the physics of the galaxy is the simple Newtonian physics. 
@@
 where $M(r)$ is the mass within a sphere of radius $r$. 
-For a flattened disk which is the case in most spiral galaxies, the right hand side of equation {~\ref{eq: simpmass}}  must  be replaced by the more exact expression derived by \cite{Freeman70}.
+For a flattened disk which is the case in most spiral galaxies, the right hand side of equation~\ref{eq: simpmass} must be replaced by the more exact expression derived by~\cite{Freeman70}. 
 He assumed in case of no dark matter or bulge, the rotation curve of a self-gravitating disk is:
@@
 the age, $t$, of the population, measured in years, also referred to the time passed since the star formation was began;
-the star formation history (SFH), often parametrized with SFR $\propto e^{-1/\tau}$; the IM; The metallicity, which is calculated as the ratio of abundance Z of elements heavier than He to abundance of H ([Z/H]), or as ratio of abundance of iron ([Fe/H]);
-and the chemical composition ratios, or the fraction of all key elements in galaxies and those values measured in the Sun.
-The stellar evolutionary tracks, the stellar spectral libraries, the parametrization for the mass-loss which affects several late stages of evolution are necessary for stars placing at specific evolutionary phases \citep{Courteau13}.
+the star formation history (SFH), often parametrized with SFR $\propto e^{-1/\tau}$; the IM; The metallicity; and the chemical composition ratios, or the fraction of all key elements in galaxies and those values measured in the Sun.
+The stellar evolutionary tracks, the stellar spectral libraries, the parametrization for the mass-loss which affects several late stages of evolution are necessary for stars placing at specific evolutionary phases~\citep{Courteau13}.
 
@@
 The calculated stellar mass can be used to calibrate the fluxes from the stars as the easily measurable parameters of stars. 
-Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies \citep[e.g.,][]{Elmgreen84}.
-Using $B-V$ colours \citep{Bell01} and $Spitzer$ 3.6- and 4.5-$\mu$m, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
+Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies~\citep[e.g.,][]{Elmgreen84}.
+Using $B-V$ colours~\citep{Bell01} and $Spitzer$ 3.6- and 4.5-$\mu$m, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
 
-\cite{Zibetti08} suggested for reaching the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel study \citep{Conti03}.
+\cite{Zibetti08} suggested for reaching the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel study~\citep{Conti03}. 
 They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density. 
@@
 \cite{Eskew12} related easily observable quantities to the stellar mass. 
-They used 3.6$\mu$m and 4.5$\mu$m fluxes  for calibration of the stellar mass, because these two bandpasses are almost insensitive to the emission from young stellar population, dust absorption and emission.
-Also thanks to $Spitzer$ and WISE \citep{Wright10} telescopes, great amount of data from many regions in the sky is available, in these bands, which help to test them on more regions and have a more accurate calibration.
+They used 3.6 and 4.5$\mu$m fluxes for calibration of the stellar mass, because these two bandpasses are almost insensitive to the emission from young stellar population, dust absorption and emission.
+Also thanks to \Spitzer~\citep{Wener04} data and WISE~\citep{Wright10} telescopes, great amount of data from many regions in the sky is available, in these bands, which help to test them on more regions and have a more accurate calibration.
 They also test the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and find the empirical relation between mass of the stars and the luminosities of stars as below:
@@
 \end{equation}
+where M$_{\star}$ is the stellar mass and $L = \nu L_{\nu}[\lambda]$ is luminosity in erg s$^{-1}$/$\AA$.
 
-where M$_{\star}$ is the stellar mass and $L = \nu L_{\nu}[\lambda]$ is the luminosity in erg/s/$\AA$.
-
-\cite{Zhu10} used the SDSS and the $Spitzer$ Wide-area Infrared Extragalactic Survey \citep[SWIRE;][] {Lonsdale03} to find the calibration between luminosity of the galaxies and stellar masses.
-Using the M/L of galaxies, they found the correlation between $K_s$ band, $3.6 \mu$m and $4.5 \mu$m band luminosities and stellar masses and formulate these correlations as:
+\cite{Zhu10} used the SDSS and the $Spitzer$ Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find the calibration between luminosity of the galaxies and stellar masses. 
+Using the M/L of galaxies, they found the correlation between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulate these correlations as:
 \begin{align}
@@
 \end{align}
-where M$_{\star}$ is the stellar mass and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg/s in specified wavelength.
-
+where M$_{\star}$ is the stellar mass and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg s$^{-1}$ in specified wavelength. 
 Measuring the stellar mass from equation~\ref{equ:eskew} is limited to the nearby galaxies, and might break down for high star forming regions, moreover, this equation have not tested on regions with different metallicity.
-Thus there is no calibration regarding variation in  metallicity \citep{Eskew12}.
+Thus there is no calibration regarding variation in  metallicity~\citep{Eskew12}. 
 On the other hand equations~\ref{equ: zhu1} -~\ref{equ: zhu3} have been derived from a large sample of galaxies, and was tested on different type of regions and galaxies. 
-Beside they can be used for more distanced galaxy as well as nearby galaxies \citep{Zhu10}.
+Beside they can be used for more distanced galaxy as well as nearby galaxies~\citep{Zhu10}. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec: pre_intro}
-%Thesis questions.
+
+ Studying formation of stars helps us understand the formation and evolution of the universe. 
+ Since forming stars contains many complex physical and chemical processes, theoretical studies cannot yet give a complete picture of star formation.
+ Therefore empirical studies are used to find laws that indicate the relations between physical properties of galaxies and star formation.
+ Between different scaling relations for star formation, the the Kennicutt-Schmidt (KS) law \citep{Schmidt59, Kennicutt98a} is the most tested empirical star formation law. 
+ Since 1959, many studies have tested KS law on regions inside the Milky Way, nearby galaxies and high redshift galaxies.
+ Not only observational studies, but also  simulations both apply and investigate KS law. 
+ Despite all these studies, there are still many unsolved questions about the KS law; Is it really a good correlation?
+What is the slope, and is it unique?, Does SFR surface density only scale with gas density?
+does the scatter affect by a second parameter(s)?
+What is the limit for applying the KS law?
+Is the SFR surface density correlation with total gas density stranger than with the H$_2$ surface density alone?
+
+Many groups are studying the KS law from different approaches to answer the questions listed in above.
+The extended Schmidt law is a newer version of the KS law, which by considering the effect of old stellar population on the SFR provides stronger correlation for the SFR than the other scaling laws.
+Although in original paper this law is tested on large sample of various types of galaxies, but further studies are necessary, due to the fact that this law is tested on the total SFR and not on different regions on galaxies to determine effect of environment on the SFR.
+In this project, the extended version of the Schmidt law will be tested on the Andromeda galaxy using both pixel by pixel relation and radial average along the disk.
+To due so star formation rate will be measured using equations~\ref{equ: halphaplus24} and ~\ref{sfr_tot_IR}.
+In order to find the gas surface density, direct method to map the ISM is chosen.
+Stellar surface density will be calculated by calibrations from both \cite{Eskew12} and \cite{Zhu10}.
+
+The Andromeda galaxy is chosen for this project due to its similarity in the structure to the MW.
+Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "global" picture, whereas, studies of the MW are limited by our location within the Galaxy.
+The Andromeda is closest spiral galaxy to the MW, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
+Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g.
+metallicity, surface brightness and etc.).
+All these parameters make the Andromeda a suitable test bed for studying the scaling law.
+The KS law has been tested on the Andromeda galaxy many times but the results have been controversial.
+The range of slope of KS law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10, Ford13}.
+Testing extended Schmidt law on the Andromeda galaxy would help us recognise parameters that affect the star formation in the Andromeda galaxy and leads us to model and simulate star formation more accurately.
+Also it helps us answer questions about in what types of the regions (e.g.
+in case of different surface brightness, metallicity, distance from the disk, etc.) effect of the stellar mass is more important.
+
+This thesis focuses on effect of quantities of galaxies on SFR in nearby and high redshift galaxies.
 

### 2016-07-10 version0.0/intro0.0.tex
finishing intro0.0

@@
 Inside every galaxy, there are millions of stars, planets, black holes, and high amount of dust and gas which all affect each others' formation, evolution and extinction.
-There are also dark matter inside every galaxy, which to the best our knowledge only has gravitational effect on the galaxies.%add ref.s
+There are also dark matter inside every galaxy, which to the best our knowledge only has gravitational effect on the galaxies.
 All the information we can obtain from galaxies other than our owns are implanted in their light. % now we can detect gravitational wave which is not part of the SEDs, right?
@@
 It combines some of the SED models to find best SED fitting for given observed data in the rest-frame of UV-to-IR and find physical properties of galaxies such as SFR, Stellar mass and dust attenuation.
-
-Formation of stars is a complicated process and directly affect on galaxies evolution. 
-Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc.
-For more than 50 years, the numerical simulations, the empirical and theoretical laws, which describe the star formation rate have been investigated; nevertheless, their results have never been precise.
-There are empirical scaling laws to relate the star formation to other properties of galaxies. 
-The most well-known of these scaling laws is the relation between the surface density of the star formation rate (SFR) and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}.
-Similar to KS law, another scaling relation was derived which is a linear scaling between the total SFR and the mass of molecular gas (refer to reviews~\cite{Elmgrenn11, Kennicutt12}).
 
@@
 
- Studying formation of stars helps us understand the formation and evolution of the universe. 
- Since forming stars contains many complex physical and chemical processes, theoretical studies cannot yet give a complete picture of star formation.
- Therefore empirical studies are used to find laws that indicate the relations between physical properties of galaxies and star formation.
- Between different scaling relations for star formation, the the Kennicutt-Schmidt (KS) law \citep{Schmidt59, Kennicutt98a} is the most tested empirical star formation law. 
- Since 1959, many studies have tested KS law on regions inside the Milky Way, nearby galaxies and high redshift galaxies.
- Not only observational studies, but also  simulations both apply and investigate KS law. 
- Despite all these studies, there are still many unsolved questions about the KS law; Is it really a good correlation?
-What is the slope, and is it unique?, Does SFR surface density only scale with gas density?
-does the scatter affect by a second parameter(s)?
-What is the limit for applying the KS law?
-Is the SFR surface density correlation with total gas density stranger than with the H$_2$ surface density alone?
+Complete picture of galaxies are formed and evolved are tied to unfolding the mystery of formation of stars.
+ Various phenomena affect the collapse of molecular clouds and star formation which include environment of the star-forming region, chemical compositions of the region, initial mass distribution of gas, mass of sounding stars and other physical properties of galaxies
+ For decades, Observational, theoretical and numerical studies have investigated star formation; nevertheless, their results have never been precise. 
+ Empirical studies are used alongside of theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
 
-Many groups are studying the KS law from different approaches to answer the questions listed in above.
-The extended Schmidt law is a newer version of the KS law, which by considering the effect of old stellar population on the SFR provides stronger correlation for the SFR than the other scaling laws.
-Although in original paper this law is tested on large sample of various types of galaxies, but further studies are necessary, due to the fact that this law is tested on the total SFR and not on different regions on galaxies to determine effect of environment on the SFR.
-In this project, the extended version of the Schmidt law will be tested on the Andromeda galaxy using both pixel by pixel relation and radial average along the disk.
-To due so star formation rate will be measured using equations~\ref{equ: halphaplus24} and ~\ref{sfr_tot_IR}.
-In order to find the gas surface density, direct method to map the ISM is chosen.
-Stellar surface density will be calculated by calibrations from both \cite{Eskew12} and \cite{Zhu10}.
+The most well-known scaling law is the relation between the surface density of FR and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
+The K-S law and similar empirical laws were tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
+Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are yet undetermined and there is no definitive answer on whether there is any universal star formation laws.
+Their dependence on physical properties of galaxies is nontrivial and sometimes differs by type of star forming regions.
+Although relation between stars and gas are well established, the detail of this relation is not clear.
+Not only different types of gas change SFR in different ways, but also variations in metallicity for each type alter it.
+There is no fully sampled and universal IMF.
+In fact there are many debates on weather IMF is universal or not.
+Influence of evolved stars and distance of star forming regions from centre of galaxies on SFR is mentioned in studies but not fully investigated.
+Besides studying the impact of mentioned properties of galaxies on SFR, searching for other properties of galaxies/star forming regions is continuing.
 
-The Andromeda galaxy is chosen for this project due to its similarity in the structure to the MW.
-Also it is the nearest spiral galaxy and provides a clear image of a galaxy like our own with the advantage that we get a "global" picture, whereas, studies of the MW are limited by our location within the Galaxy.
-The Andromeda is closest spiral galaxy to the MW, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
-Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g.
-metallicity, surface brightness and etc.).
-All these parameters make the Andromeda a suitable test bed for studying the scaling law.
-The KS law has been tested on the Andromeda galaxy many times but the results have been controversial.
-The range of slope of KS law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10, Ford13}.
-Testing extended Schmidt law on the Andromeda galaxy would help us recognise parameters that affect the star formation in the Andromeda galaxy and leads us to model and simulate star formation more accurately.
-Also it helps us answer questions about in what types of the regions (e.g.
-in case of different surface brightness, metallicity, distance from the disk, etc.) effect of the stellar mass is more important.
+Advances in observing facilities, image qualities, and methodology expands our knowledge of formation of stars.
+Besides these advances, in the past few decades,using advanced statistical methods grew in astronomical studies.
+Applying modern statistical methods on star formation studies can shed a light on unsolved problems in this field. 
+Studies show that using different statistical methods changes our perspective on star formation laws. 
+For example,~\cite{Shetty13} used Bayesian methods to show the K-S law is not universal. 
+On the other hand, since astronomy is a data driven science, data mining methods are quiet useful to get new insight on properties of star forming regions.
 
-This thesis focuses on effect of quantities of galaxies on SFR in nearby and high redshift galaxies.
+In this thesis, we present three projects that study effects of quantities of galaxies on SFR.
+We use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties and using modern statistical methods study their impact on SFR.
+Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxies (M31) in both local and global scales using hierarchical Bayesian analysis.
+Additional to the K-S law, we study the extended Schmidt law~\citep{Shi11} and and the metallicity/star formation correlation~\citep{Krumholz09}.
+We also show the effect of using different SFR and ISM gas tracers on star formation laws.
+In Chapter~\ref{ch: paper3}, we explore nearby galaxies using an unsupervised data mining method (self organizing map, SOM).
+We cluster observational data and derived quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
+We find hidden structures in high dimensional data space during this process.
+In Chapter~\ref{ch: paper2}, we move to higher redshift and apply SOM algorithm on SED of high-redshift galaxies.
+We train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
+Then, we study the grouped properties of classified galaxies.
+For each chapter, we also describe the methodology and data used in that chapter.
+We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}
 

### 2016-07-10 version0.0/summary.tex
finishing intro0.0

\chapter{Summary and feature works}
\label{ch: summary}

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to prelude sub-section

@@
 % stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
-Inside every galaxy, there are millions of stars, planets, black holes, and high amount of dust and gas which all affect each others' formation, evolution and extinction.
-There are also dark matter inside every galaxy, which to the best our knowledge only has gravitational effect on the galaxies.
-All the information we can obtain from galaxies other than our owns are implanted in their light. % now we can detect gravitational wave which is not part of the SEDs, right?
-Light emitted from young and evolved stars, and dust and gas in the space between stars have the most contribution on spectral energy distributions (SEDs) of galaxies.
-We cannot detect any contribution from planets and black holes on SEDs due to their low intensity or the limitation of our detectors.
-Therefore, with properly modeling observed features in SEDs we can extract information about evolution of stars, dust and gas inside galaxies.
+Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
+There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
+Nearly all the information we can obtain from galaxies other than our own comes from their light. % now we can detect gravitational wave which is not part of the SEDs, right? % PB: right.
+Young and evolved stars and dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
+%PB: explain what you mean by spectral energy distribution
+We cannot detect any contribution from planets and black holes to SEDs due to their low intensity compared to these other components.
+%or the limitation of our detectors.
+% PB: need to rephase a bit  to mention AGN!
+Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.
 
@@
 Arguably, stars are the main component of normal galaxies.
-They control the chemical composition and structure of galaxies by transforming gas into new born stars and by transforming death stars to the gas.
+They control the chemical composition and structure of galaxies by transforming gas into new stars and by transforming dead stars back into gas.
 They are also central to the formation and evolution of planetary systems.
 The energy provided by stars is necessary to create and maintain the life on planets. 
-The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System.
+The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
 Furthermore, in order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
@@
 %ISM 1)Gas 2)dust
-There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas.
-Gas and dust in galaxies can be found in the space between stars that is called interstellar medium (ISM) which is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
-The gas and dust in ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
-Effect of ISM in stellar formation is undeniable; ISM provides raw material for formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
-Studying ISM is not only essential for understanding of the formation of stars but also it is necessary for interpretation of stellar evolution in that stars release their material into ISM when they reach at the end of their evolution.
+There could be a galaxy without stars (i.e.
+dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas.
+%PB: this is a very strong statement.
+Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now).
+So qualify this a bit.
+Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM).
+The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
+The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
+The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
+Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.
 
-% Metallicity
-Metallicity, which is defined as the ratio of abundance of metal to the abundance of hydrogen atom, affects formation and evolution of stars indisputably.
-In a galaxy like our own, star formation begins with condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in ISM which is due to gravitational instabilities. 
-The interplay of turbulence and magnetic field with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
-Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic field play central roles in defining this distribution (see~\cite{McKee07} for more detail).
-\cite{Walch11} showed that in case of the large scale turbulence the amount of metallicity on star formation is negligible, but if turbulence is decaying  metallicity has high impact and stabilizing self-gravitating cores.
-Metals also play an important role on heating, cooling and ionizing processes in ISM. %%ADD ref.
-Since cooling is one of the main reason of condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed.
+% Metallicity %PB: you start talking about metallicity but then switch over to SF. Overview the SF process first, then talk about how metallicity affects it.
+Metallicity, which is defined as the ratio of abundance of metals to the abundance of hydrogen, affects formation and evolution of stars indisputably. %PB: define what "metals" means here
+In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
+The interplay of turbulence and magnetic fields with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
+Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic fields play central roles in defining this distribution (see~\cite{McKee07} for more detail).
+%PB: this sentence has a lot of concepts in it: going to be hard for non-astronomer to understand
+\cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores.
+%PB: please check edits to prev sentence
+Metals also play an important role in heating, cooling and ionizing processes in the ISM. %%ADD ref.
+Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed.
 %Sahar: should I talk about metallicity in stars and their relation with age?
+%PB: yes.
+Need to introduce the general idea of chemical evolution - you hint at this above, but can state it explicitly.
 
 %what does SED look like?
-Our primary source of information for galaxies, specifically unresolved ones, is their SEDs.
-Broadly speaking, young and hot stars emit most of their light in Ultraviolet (UV) wavelengths, evolved stellar population show themselves in optical and near-Infrared (NIR) emission and gas and dust heated by stellar emission are bright in Mid-IR (MIR) or far-IR (FIR) wavelengths.
-Therefore, UV-to-IR SEDs contains valuable information about stellar evolution and their ISM. 
-Other wavelengths regimes in SEDs (i.e. X-ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shock, are beyond the scope of this thesis.
-general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rate (SFR), emit bulk of their energy in UV, while light of quiescent galaxies are dominated by optical and IR emission
-Detail information about age of stellar populations and other properties of galaxies can be determine by properly modelling of galaxy SEDs.
+Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. %PB: since SED is a really important concept, I took out the acronym here.
+Broadly speaking, young and hot stars emit most of their light in iltraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
+Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
+Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
+The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission.
+Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.
 
- %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass
-Stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, is widely utilized from 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
-A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grains emission such as polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}, to fit the observed SEDs.
-Many groups modelled SEDs for different type of galaxies and created templates of SEDs. (for more information see review of \cite{Walcher11} on fitting of SEDs and references therein).
+ %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass %PB: Need more detail here - how do SED models include SFR, Mstar, etc?
+The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
+A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.%, to fit the observed SEDs.
+Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
 Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs using the templates.
-Code Investigating GALaxy Emission ({\em CIGALE})~\citep{Noll09} is one example of codes that find best SED fittings.
-It combines some of the SED models to find best SED fitting for given observed data in the rest-frame of UV-to-IR and find physical properties of galaxies such as SFR, Stellar mass and dust attenuation.
+One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
+It combines SED models to find the best-fit SED for observed data in the rest-frame UV-to-IR and finds physical properties of galaxies such as SFR, stellar mass and dust attenuation.
 
-In this chapter, we present a review of observational method of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
-A discussion of the ISM, its role on star formation is presented in $\S$~\ref{sec: ism_intro}, In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}.
-The current issues about studying star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
+%PB: I think you need a one-or-two sentence intro to the overall thesis goals here, so that the reader can see why you are talking about all of this stuff.
+In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
+A discussion of the ISM and its role in star formation is presented in $\S$~\ref{sec: ism_intro}.
+In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}.
+Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
 

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to "Interstellar Medium" before first subsection

@@
 
-\section{Interstellar Medium}
+\section{Interstellar Medium} %PB: suggest "Components of the Interstellar Medium in Galaxies" or "The Interstellar Medium in Galaxies"
 \label{sec: ism_intro}
@@
 % how do we measure the dust and gas
-ISM in galaxies is a complex system with wide range of structures, but this structures can be divided into two main components: Gas and Dust.
-Gas in ISM of galaxies is mostly made of hydrogen and helium with 1 per cent of heavier elements (metals), and can be in the forms of clouds or diffuse regions.
-Gas clouds contains molecular clouds, cold atomic neutral hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud mediums.
+The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
+%PB: in general, don't start a sentence with an acronym.
+The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
+Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud medium.
 Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
 %Among these regions in ISM, molecular clouds, \hii~regions and dust clouds have important role in understanding star formation in galaxies. 
-Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observing signatures of the gas in the ISM of galaxies.
-Dust can be observed directly through FIR and sub-mm observation or indirectly through their extinction and attenuation effect (see Sec.~\ref{sec: extinction}).
+Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
+Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).
 
-Molecular clouds in ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$), masses in molecular clouds range from few to million solar masses. %~\citep{Bolato08}.
-Density in the molecular clouds is not uniform; dense and colds clumps.
+Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses. %~\citep{Bolato08}. %PB: why no citation?
+Density in the molecular clouds is not uniform; dense and colds clumps. %PB: I don't get this sentence.
 Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
-However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them really hard to detect in visible light.
+However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect in visible light.
+%PB: just visible light, or all wavelengths?
 The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
-CO molecules take a third place in case of abundance in the molecular clouds.
-In fact, most of our knowledge from extragalactic molecular clouds comes from observing emission line of CO molecules, which due to their heavy weight, they have very low rotational state and can be excited in the temperature of molecular clouds.
-Other heavier molecules have emission lines which are detectable in spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study properties of molecular clouds i.e.
+Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
+In fact, most of our knowledge from extragalactic molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds.
+%PB just extragalactic, or Galactic too?
+Phrase marked with \bf needs clarification
+Other heavier molecules have emission lines which are also detectable in the spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.
 their mass (see Sec.~\ref{sec: ismmap} for more details).
 
-The molecular clouds are surrounded by cloud of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
-Hydrogen atoms in the ISM (excluding the regions close to type ``O" and ``B" stars) are in their ground state. 
-The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. proton's spin is up and electron's spin is down or vice versa). 
-The energy state of anti-parallel mode is slightly less than parallel mode.
+The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
+Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
+The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
+The energy state of the anti-parallel mode is slightly less than the parallel mode.
 Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
-However, difference between these two states are very small and it takes millions of years before the transition happens.
-The large amount of hydrogen atoms, on the other hand, compensate the rareness of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
-The observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of ISM, which leads to understanding star formation process in ISM~\citep{Walter08}.
+However, the difference between these two states is very small and it takes millions of years before the transition happens.
+The large amount of hydrogen atoms compensates for the rareness of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
+Observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.
 
-\hii~regions are hot and low density regions that are mostly located in the disk of spiral galaxies.
-Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as star formation tracers~\citep[e.g.][]{Kennicutt98b,Calzetti13}. 
-High energy UV photon emitted by massive new born stars have sufficient amount of energy to ionize their surrounding gas.
-~\halpha emission is main observational feature\hii~regions.
-Temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, \sii, \oii, \oiii, and \nii from \hii~regions.
-Studying \hii~regions provide valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
+\hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
+High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
+~\halpha emission is the main observational feature of \hii~regions.
+The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, \sii, \oii, \oiii, and \nii. 
+Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
+%PB: moved this sentence.
+Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
 
-Dust has insignificant effect on mass of ISM, but it plays crucial roles in evolution of ISM.
+%PB: it is difficult to see how the sentences in this paragraph fit together. Right now it reads like a collection of barely-related facts.
+Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
 The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
-In spiral galaxies dust are in cold regions $\sim 30$~K and has power low distribution of size.
+In spiral galaxies dust grains are located in cold regions ($\sim 30$~K) and have a power-law distribution of size.
 Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
-MIR emission from dust grains are manly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed types``A" and ``B'' stars~\cite{Peeters04}.
-Large grains that are either heated by light from star forming regions or by interstellar radiation field from total stellar population emit most of their light in FIR~\citep[e.g.][]{Calapa14, lu14}
-Dust are main source of extinction and reddening of star lights (See Sec.\ref{sec: extinction} for more information).
+Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed type ``A" and ``B'' stars~\cite{Peeters04}.
+%PB: A and B or O and B?
+Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
+Dust is the main source of extinction and reddening of starlight (See Sec.\ref{sec: extinction} for more information).
 

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to "Map of ISM" subsection

@@
 
-\subsection{Map of ISM}
+\subsection{Map of ISM} %PB: suggest "Mapping the Interstellar Medium"
 \label{sec: ismmap}
-Measuring mass of gas in galaxies is a necessary step to now how much row material is available for forming stars.
-A map of total gas mass in ISM is produced by direct observations of gas or using interstellar dust as a tracer. 
-Neutral and molecular hydrogen are the most common elements in ISM. 
-Therefore, for producing the total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-Another way to do the mapping is assuming that the ratio of total gas and dust is constant across the galaxy, and convert dust observations to the map of total gas mass.
+Measuring the mass of gas in galaxies is a necessary step to know how much raw material is available for forming stars.
+A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
+Neutral atomic and molecular hydrogen are the most common components of the ISM. %PB: same element
+Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
+%PB: point out that He can't be observed directly
+Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.
 
@@
 The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
-This method can be promising provided that the spatial resolution of observational data is high enough; nonetheless, due to technical limitations, attaining enough spatial resolutions to resolve clouds is almost impossible.
+This method can be promising provided that the spatial resolution of observational data is high enough, although due to technical limitations, attaining enough spatial resolution to resolve clouds is almost impossible.
 This problem shows itself for distant galaxies more than nearby galaxies.
-As a result, using this method is limited and has a lot of uncertainties.
+As a result, using this method is limited and has a lot of uncertainties. % PB last 3 sentences are vague. What exactly ar the limitations and uncertainties?
 
 %\subsubsection{Molecular Clouds}
+%PB: some repetition from earlier subsection here. 
+The carbon monoxide molecule has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy. 
+Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
+Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][] {Sanders84}.
+Higher rotational transitions of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.
 
-CO molecule has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy. 
-Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
-Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen~\citep[e.g.][] {Sanders84}.
-Higher rotational transition of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.
-
-\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is :
+\cite{Young91} described the relationship between the CO luminosity of a cloud and its mass. The CO luminosity of a cloud is:
 \begin{equation}
-L_{CO} = D^2 \int I_{CO} d\Omega 
+L_{CO} = D^2 \int I_{\rm CO} d\Omega 
 \end{equation}
-where D is the distance to the cloud. 
-$I_{CO}$ is the CO brightness temperature integrated over the line profile.
-It shows in the form of ${\int T_{co} dV}$ where $T_{CO}$ is the peak brightness temperature in CO line and $V$ is the line-width. 
-For a uniform cloud with a radius $R$, the CO luminosity is given by
-
+where $D$ is the distance to the cloud and 
+$I_{\rm CO}$ is the CO brightness temperature integrated over the line profile.
+It can be written as ${\int T_{\rm CO} dV}$ where $T_{\rm CO}$ is the peak brightness temperature in the CO line and $V$ is the line-width. %PB units for these quantities?
+For a uniform cloud with a radius $R$, the CO luminosity is given by:
  \begin{equation}
-L_{CO} = \pi R^2 T_{CO} \Delta V
+L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V
 \end{equation}
 
-Galactic molecular clouds are self-gravitating systems.
-Thus, using the Virial theorem would lead to calculating the mass of the cloud.
-
+Galactic molecular clouds are self-gravitating systems. %PB: ref?
+Thus, using the virial theorem leads to calculating the mass of the cloud: %(PB note: "Virial" is not a name, no capital needed)
  \begin{equation}
  \label{equ: vir}
- M_{cloud} = L_{CO} \sqrt{\frac{4\rho}{3\pi G T_{CO}}}
+ M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}
  \end{equation}
- where $\sqrt{\frac{4\rho}{3\pi G T_{CO}}}$ is called the conversion factor. 
+ where $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor. %PB: what is \rho here?
  Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related~\citep{Young91}.
+% PB: you refer to individual clouds above, then you jump to totals for the galaxy.
+Is this OK to do?
+(what assumption about optical depth is being made?)
  The relation between CO emission and H$_2$ cloud mass is shown as
+%PB: no paragaph break between the text and the beginning of the equation
+\begin{equation}
+N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1}
+\end{equation}
+where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
+The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
+Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties.
+%PB: need references here
+Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.
 
-\begin{equation}
-N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
-\end{equation}
-where X$_{CO}$ is the conversion factor (also known as the X-factor).
-The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties of regions such as metallicity. 
-Though assuming constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties. 
-Various groups are working on observation from different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.
-
-In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made in both galactic and extragalactic scales. 
-One of the most significant studies in this regard had been done by~\cite{Solomon87}, who studied this relation on more than 273 clouds inside the Milky Way and found a strong correlation between Virial mass of molecular clouds and CO luminosity.
-In the Local Group galaxies, several groups measured size, line width, and CO luminosity of molecular clouds and investigate the relation between  their Virial masses and CO emission in environment other than the Milky Way.
+In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
+One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity.
+In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environment other than the Milky Way.
 However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes.
 To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Bolato13}.
-
+%PB: put these last 2 sentences at end of paragraph
+%PB no new paragraph here
 Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
-Fig.~\ref{fig: mco} shows the CO luminosity verses Virial masses of molecular clouds in the Milky Way, M31, M33, and IC10. 
+Fig.~\ref{fig: mco} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
 The extragalactic molecular clouds are similar to those in the Milky Way. 
 The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
-Problems regarding metallicity are not solved yet and it is still not clear whether the conversion factor is global or local.
+Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local.
 
@@
 \includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
-\caption{Relation between The Virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), m31 (triangles), and IC 10 (squares) clouds.
-The Virial masses measured from selected high spatial resolution CO observations are shown.
+\caption{Relation between the virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), M31 (triangles), and IC~10 (squares) clouds.
+Virial masses are measured from selected high spatial resolution CO observations.
 The extragalactic molecular clouds are very similar to those in the Milky Way.
-Adapted from~\cite{Young91}}
+Adapted from~\cite{Young91}.}
 \end{figure}
 
-%\subsubsection{Neutral Gas}
+%\subsubsection{Neutral Gas} %PB: paragraph needs a topic sentence
 The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission.
-Atomic hydrogens, that are along the line-of-sight contribute to the energy received. 
-These properties make the 21-cm a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
+%PB: reverse: intensity of 21cm is proportional to density.
+Is this optically thin/thick ?
+Atomic hydrogen along the line-of-sight contributes to the energy received. %PB does this sentence add something to the previous one?
+These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
 Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.
+%PB: do you want to give the equation for converting between intensity and mass for HI, the way you did for CO?
 
@@
 
-Studying the gas cloud in the ISM of distant galaxies by using direct methods is almost impossible and not practical. 
-\cite{Hildebran83} was the first person to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
+Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical. %PB: why?
+\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
 The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
 This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
+%PB: join these 2 paragraphs
+One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. %PB: why?
+The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
+Dark gas is a significant fraction of gas in galaxies which is traced by neither 21-cm emission nor CO emission~\citep{Abdo10}. 
+As such it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
 
-One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, the high spatial resolution is not necessary anymore. 
-The other important advantage is that this method solves the newly-found problem of the ``dark gas" in the galaxies. 
-Dark gas is a significant fraction of the gas in the galaxy which is traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
-So it is really hard to detect them by telescopes, but accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
-
-There are many disadvantages regarding the use of the gas to dust ratio in the ISM.
+There are many disadvantages of the use of the gas to dust ratio to trace gas in the ISM.
 In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
 \cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains.
-Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps~\citep{Hildebran83}. 
-Also by using current telescopes, it is difficult to detect dust emission from galaxies at z $>$ 0.1~\citep{Ealas12}. 
-Besides, in some cases such as the Virgo cluster, dust mass is more tightly correlated with the total gas mass than to the masses of molecular or atomic gas separately~\citep{Corbelli11}.
+Also, methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps~\citep{Hildebran83}. 
+Using current telescopes, it is difficult to detect dust emission from galaxies at $z > 0.1$~\citep{Ealas12}. %PB: this doesn't seem correct to me - what about submm galaxies?
+In some cases such as Virgo cluster galaxies, dust mass is more tightly correlated with the total gas mass than with the masses of molecular or atomic gas separately~\citep{Corbelli11}.
+%PB: so why is this a problem?
 
-In addition to all the disadvantages mentioned before, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
-To solve this problem, measurement of the continuum emission at far-infrared wavelengths enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
+In addition to all the disadvantages mentioned above, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
+To solve this problem, measurement of the continuum emission at far-infrared wavelengths long enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
 The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems. 
-Unfortunately, at present, given the available devices and technologies, we cannot reach a high-resolution that is sufficient to detect the gas cloud directly.
+%Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems. PB: sentence doesn't add anything
+Unfortunately, at present, given the available devices and technologies, we cannot reach the spatial resolution that is sufficient to detect the gas clouds directly.
+%PB why do we need high spatial resolution?
+Or is it sensitivity that is the problem?
 Therefore, so far this method is the best available solution for measuring the total gas in distant galaxies.

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to extinction and attenuation subsection

@@
 
-\subsection{Extinction and Attenuation}
+\subsection{Extinction and Attenuation} %PB: suggest "The ISM and starlight: extinction and attenuation" or something like that, to make clear why we care about this.
 \label{sec: extinction}
 In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed.
-More advanced and detailed discussions on this topic is out of the scope of this paper; and for more information one can refer to the review by~\citep{Calzetti01}. 
+%PB: explain why we care (because stars and dust are spatially mixed in galaxies, and dust affects emitted SED).
+A  sentence like that is more useful than "in this section we will discuss X".
+More advanced and detailed discussion on this topic can be found in the review by~\citep{Calzetti01}. 
 Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
 The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source.
+%PB: source is *considered* to be a background point source (but what if it isn't a point source?)
+% PB: join paragraphs
+Attenuation refers to the effects of dust with embedded light sources distributed throughout. 
+The dust itself can be clumpy or smooth \citep{Calzetti13}. 
+In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions.
+Dust scattering's effect depends on whether the dust is in or out of the line of sight. 
+When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer. %PB: bluer? really?
+This is the typical situation that occurs when studying galaxies or extended regions within galaxies.
 
-Attenuation refers to the effect of dust with embedded light sources distributed throughout. 
-The dust itself can be clumpy or smooth\citep{Calzetti13}. 
-In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions.
-Dust scattering's effect depends on whether it is in or out of the line of sight. 
-When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer. 
-This is the typical situation that comes across when studying galaxies or extended regions within galaxies.
-
-In order to describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
-At UV/optical/near-IR wavelengths, the radiative transfer equation is:
+To describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
+% PB: "beam" is jargon, change to something else.
+Simplify this sentence.
+At UV/optical/near-IR wavelengths, the radiative transfer equation is: %PB: why does this eqn only apply at UV/opt/NIR? 
 \begin{equation}
@@
 \end{equation}
-where I$_{\nu}$ is the intensity of radiation, $\tau$ is the dust's optical depth.
-a$_{\nu}$ is the dust albedo, which refers to the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
-$\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. 
-Both a$_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
-The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m is neglected in the equation above. 
-This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, it causes underestimation of the SFR.
+where I$_{\nu}$ is the intensity of radiation and $\tau$ is the dust's optical depth.
+$a_{\nu}$ is the dust albedo,  the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
+$\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. %PB: what is \phi? Need to explain at least a little
+Both $a_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
+The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m, is neglected in the equation above.
+%PB: why no dust emission at short wavelengths?
+(temperature)
+This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, there will be an underestimation of the star formation rate.
+%PB: what do you mean by "different emission" in this sentence?
 

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to first part of SFR section

@@
 \label{sec: sfr_intro}
-Understanding formation of stars leads to understanding galaxies formation and evolution. 
-Characterisation of the star formation processes such as SFR and IMF is necessary in examining galaxies structure formation~\citep{McKee07}. 
-Measuring the SFR is not trivial and depends on galaxy's morphology, metallicity, IMF, spatial resolution of a target system, and other propertied of galaxies. 
-There is a large number of review papers in the literature on how stars form and how their formation is traced. 
+Understanding the formation of stars leads to better understanding of galaxies' formation and evolution. 
+Characterisation of the star formation processes such as star formation rate (SFR) and the stellar initial mass function (IMF) is necessary in examining galaxies' structure formation~\citep{McKee07}. 
+Measuring the SFR is not trivial and depends on a galaxy's morphology, metallicity, IMF, observational spatial resolution, and other properties. 
+There is a large number of review papers on how stars form and how their formation is traced. 
 From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
@@
 
-In principle, emission from new stars can be traced by UV emission, optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission.
-Some of these emission are directly from stars, e.g UV emission, and some are from ISM components around stars that absorb and re-emit light of young stars, e.g FIR emission.
-Techniques to calibrate emission from the newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed were subjects of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
-Emission from the young massive type ``O'' or ``B'' stars are normally used as a tracer of the current SFR.
-One of the main assumptions for using luminosity of massive stars is that SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
-By knowing IMF, the number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region.
+In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission.
+Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
+Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
+Emission from young, massive, type ``O'' or ``B'' stars is normally used as a tracer of the current SFR. %PB: why?
+One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer.
+By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
 To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to IMF subsection

@@
 \label{sec: imf}
-One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar (or cores) initial mass distribution of star forming region. 
-Since, most of SFR calibrations use emission from specific mass range stars, it is necessary to know the stellar IMF to determine a more accurate SFR from calibrated photometry data. 
+One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar (or cores) initial mass distribution of a star forming region.
+% PB: leave out the cores part.
+Explain why we care about the mass distribution (because mass determines the important properties of a star like luminosity, lifetime, etc)
+Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
 Most problems in modern astrophysical studies regarding the origin and evolution of stars and galaxies can be solved by sampling an IMF ~\citep{Bastin10}.
-\cite{Salpeter55} empirically derived stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
-He introduced a power-law IMF in the form of:
-
+%PB: this sentence doesn't really add anything
+\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
+He introduced a power-law IMF in the form:
 \begin{equation}
@@
 \end{equation} 
-where M is the stellar mass, $\gamma$ is the power index, and $N$ is the number of stars in logarithmic mass range of $\log M + d\log M$.
+where $M$ is the stellar mass, $\gamma$ is a power index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.
+%PB: what is \Phi ??
+Could write "introduced a power-law IMF $\Phi$ in the form"
 
-In the late 70s, it was recognised that using the single power-law IMF over all stellar masses is not a correct assumption and might overestimate number of low-mass stars~\citep{Kroupa93, Bastin10}. 
-Since then, many groups have studied the stellar IMFs and found different power-law relations for them (Fig.~\ref{fig: imf} ). 
+In the late 70s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}.
+Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
 Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
@@
 \end{align}
-where $\chi(M)$ is the number of stars between masses $M$ and $M+dM$. 
-Although the Salpeter IMF produces more low-mass stars than the Krupa IMF, they produce almost the same number of the high-mass stars. 
-Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration's constant by 1.6~\citep{Calzetti13}.
-In more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMF overestimate amount of stars in all masses.
-\cite{Bastin10} reviewed the stellar IMF by using many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high mass end.
+where $\chi(M)$ is the number of stars between masses $M$ and $M+dM$. %PB: what is $A$? 
+Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
+Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration constant by 1.6~\citep{Calzetti13}.
+%PB: clarify this: multiply calibration based on Kroupa by 1.6 to get calibration based on Salpeter?
+Or the other way around?
+In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars at all masses.%PB: doesn't quite make sense.
+Does't an overestimate at all masses just mean an incorrect normalization?
+\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.
+%PB: check that you are using "high-mass" vs "high mass" (same for low) consistently
 
@@
 \small
-\caption{Comparing the IMFs by plotting the mass fraction per dex versus mass that is normalized so that the integral under each curve is unity.
-The mass ranges from 0.1 to 120 M$_\odot$.
-Adopted from~\cite{Baldry03}}
+\caption{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex versus mass, normalized so that the integral under each curve is unity.
+The mass ranges from 0.1 to 120~M$_\odot$.
+Adopted from~\cite{Baldry03}.} %PB: note that "dex" is astro-jargon.
 \end{figure}
 
-The careful measurement of the stellar IMF is a key factor in understanding the SFR. 
+Careful measurement of the stellar initial mass function is a key factor in understanding the star formation rate. 
 In distant galaxies, only massive stars can be detected; therefore, the IMF must be measured to include all stellar mass ranges in the SFR calibrations.
+%PB: but how can you measure the IMF if you only detect the massive stars?
 To show the impact of the different stellar IMF assumptions on the SFR calibrations, \cite{Calzetti13} used two different stellar IMFs and derived the SFR calibrations with these new assumptions.
-Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes SFR calibrations' constants by factors ranging from 1.4 to 5.6 for different SFR indicators (Tab.~\ref{table1}).
+Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30~M$_{\odot}$ instead of 100~M$_{\odot}$, changes the SFR calibration constants by factors ranging from 1.4 to 5.6 for different SFR indicators (Tab.~\ref{table1}).
 

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to SFR indicators subsection  up to but not including multi-band emission; suggest new title for SFR section

@@
 
-\section{SFR}
+\section{SFR} %PB: suggest "Measuring the star formation rate in galaxies"
 \label{sec: sfr_intro}
@@
 
-One of the main issues to study star formation in distant galaxies is calibration of SFR indicators~\citep[e.g.,][]{Lee10}. 
+One of the main issues in studying star formation in distant galaxies is the calibration of star formation rate indicators~\citep[e.g.,][]{Lee10}. 
 Calibration of SFR indicators can be affected by differences in star formation history (SFH), metallicity, distribution of stellar population and dust in galaxies~\citep{Calzetti13}. 
-Based on the spatial resolution of a system one can divide star formation indicators into two categories: resolved and unresolved star formation indicators.
+Based on the spatial resolution of a system, one can divide star formation indicators into two categories: resolved and unresolved star formation indicators.
 
@@
 The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
-These objects mostly have certain ages and usually are referred to as young stellar objects (YSOs). 
-Counting YSOs is a method that used for calculating star formation in molecular clouds within $0.5- 1$ kpc of the Solar System. 
+These objects mostly have certain ages and usually are referred to as young stellar objects (YSOs). %PB: "mostly have certain ages" ??
+Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
 The number of YSOs can be converted to SFR using: 
@@
 \end{equation}
-where N$_{yso}$ is the number of YSOs, $<$M$>$ is the mean mass of YSO which depends on the IMF. 
-$\tau$ is the lifetime of the YSO considering some uncertainly $\tau \sim 2$Myr~\citep{Evans09},and the SFR(YSO) is in the unit of M$_{\odot}$yr$^{-1}$. 
+where N$_{yso}$ is the number of YSOs, $<$M$>$ is the mean mass of YSO which depends on the IMF, 
+$\tau$ is the lifetime of the YSO considering some uncertainly $\tau \sim 2$Myr~\citep{Evans09}, and the SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$. 
 Due to observational difficulties, this method can only be applied to the Solar neighbourhood and the Milky Way.
+%PB: "observational difficulties" is vague.
+What is the issue?
+Actually, it's covered in the following 2 sentences so just drop this one.
 
 In theory, for any system with high enough spatial resolution ($\sim 0.5- 1$ kpc), counting YSOs can be used as a tracer of the star formation.
-However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic clouds can not be resolved. 
+%PB: I think you need higher than 0.5 kpc resolution to count YSOs - need to see individual stars, right?
+However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds can not be resolved.
+%PB: explain what the MCs are (& how far away), for the non-astronomer
 Therefore, most studies use the emission from the energetic ``O" and ``B" stars as a tracer of the SFR.
-Another method to measure the SFR is by looking at the colour-magnitude diagram (CMD) of star-forming regions. 
-\cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to reproduce the spatially and age-resolved maps of star formation in nearby galaxies. 
-More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}.
+%PB: O and B is astro-jargon.
+Leave it out or explain what is important about this class of stars?
+Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
+\cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to produce spatially and age-resolved maps of star formation in nearby galaxies. 
+More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}. %PB: I think you should give a one-sentence summary of the method here.
 
@@
 
- In star-forming regions farther away than the Magellanic clouds, spatial resolution is not high enough to find all the YSOs. 
- In unresolved systems, calibrating continuum or line emission at wavelengths that are sensitive to the young massive stars are primary method of measuring SFR.~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
-\cite{Kennicutt98b} calibrated luminosities of galaxies in specific wavelengths for measuring the SFR using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by synthesis models~\citep[e.g.,][]{Bruzual93}.
+ In star-forming regions farther away than the Magellanic Clouds, the spatial resolution of currently-available observations is not high enough to find all the young stellar objects. 
+ In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to the young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
+\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar populations synthesis models~\citep[e.g.,][]{Bruzual93}.
 
-In unresolved systems, the SFR indicators can be divided into local and global ones. 
+In unresolved systems, SFR indicators can be divided into local and global indicators. 
 The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
-While local calibration is used for regions within a galaxy, on a scale of sub-galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
-The limitations in the spatial resolution of the data on the one hand, and the broader applicability of distant galaxy populations on the other, have brought more attention to the calibrations of global SFR compared with the local SFR calibrations that had been done in the past.
-Yet, because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.
+Local calibration is used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+Limitations in the spatial resolution of observational data on the one hand, and the broader applicability to distant galaxy populations on the other, have in the past brought more attention to the calibrations of global SFR compared to local SFR.
+Because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.
 
-\subsubsection*{SFR Indicators Based on the Single-Band Emission}
+\subsubsection*{SFR Indicators Based on Single-Band Emission}
 
-In order to derive the conversion between the luminosity in specific wavelengths and the SFR, synthesis models are used~\citep{Kennicutt98b}. 
-General form of a SFR calibration using single-band emission is: 
+In order to derive conversions between the luminosity in specific wavelengths and the SFR, stellar population synthesis models are used~\citep{Kennicutt98b}. 
+The general form of a SFR calibration using single-band emission is: 
 \begin{equation}
 \label{equ: sfrsingle}
-SFR(\lambda)= CL(\lambda)
+{\rm SFR}(\lambda)= CL(\lambda)
 \end{equation}
-where SFR is in units of M${_\odot}$yr$^{-1}$, $L(\lambda)$ is luminosity in erg s$^{-1}$ at the wavelength $\lambda$, and C is the constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}).
-The constant, C, can vary for different emission, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation needs to remain constant. 
-Table~\ref{table1} from \cite{Calzetti13}, summarises the changes in the constant of the calibration.
+where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}).
+The constant $C$ varies for different wavelengths, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation is assumed to remain constant. 
+Table~\ref{table1}, from \cite{Calzetti13}, summarises some values of $C$ and their changes with assumption about the IMF.
 
@@
 \begin{tablenotes}
-\item $^1$ Luminosities are in erg s$^{-1}$ and are given as $\nu L_{\nu}$.
-\item $^2$ The constant C appears in equation~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$.
-\item $^3$ Assumptions for mass range of the stellar IMF, which we adopt to have the expression derived by \cite{Kroupa01} (see Sec.~\ref{sec: imf}), and for the timescale $\tau$.
+\item $^1$ Luminosities are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
+\item $^2$ The constant $C$ appears in equation~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$. %PB: why?
+\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Sec.~\ref{sec: imf}), and for the timescale $\tau$.
 \end{tablenotes}
@@
 
-The most common single-band wavelengths that are used as an SFR indicator, is UV emission.
-UV emission is an excellent tracer for the SFR due to the fact that the peak of emission for young  ``O" and ``B" stars are in the UV part of the spectrum.
-Using spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}
+The most common single-band tracer of star formation rate is the ultraviolet.
+UV emission is an excellent tracer for the SFR due to the fact that the peak of emission for young  ``O" and ``B" stars is in the UV part of the spectrum.
+%PB only young O and B stars?
+what about old ones?
+Using a spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
 \begin{equation}
@@
 \end{equation}
-where SFR(UV) is in M$_{\odot}$yr$^{-1}$, $\lambda$ in the range of $(912< \lambda < 3000~\AA$), and $L(\lambda)$ is in erg s$^{-1}$. 
-As shown in table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
+where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ in the range of $(912< \lambda < 3000~\AA$), and $L(\lambda)$ is in erg s$^{-1}$.
+%PB: so L is the integrated luminosity from 912-3000A?
+or something else?
+As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
 However, the calibration constants' changes for shorter timescales are more significant~\citep{Calzetti13}. 
-The accuracy of the calibration constant is $\pm 15\%$ which can vary as a function of $\lambda$. 
-The UV light can easily be absorbed or scattered by interstellar dust. 
-Therefore, using the UV emission as a tracer might lead to underestimating of the SFR, if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
+The accuracy of the calibration constant is $\pm 15\%$ which can vary as a function of $\lambda$.  %PB: ref?
+Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
+Therefore, using the UV emission as a tracer might lead to underestimating of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
 
@@
 Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}.
-The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived quantum mechanically. 
-To have such results, the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}. 
-Being optically thick makes almost all transitions more energetic than Ly${\alpha}$ to be absorbed and re-emited via Ly${\alpha}$ and longer wavelengths.
+The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived from quantum mechanics. 
+To have such results, the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}. %PB: "The assumption is" rather than "To have such results" ?
+Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emited via Ly${\alpha}$ and longer wavelengths.
 This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
 The relation between the SFR, the luminosity of the \halpha emission line and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
-
+%PB: no new paragraph here
 \begin{align}
@@
 \end{align}
-where SFR(\halpha) is in M$_{\odot}$ yr$^{-1}$, L(\halpha) is in erg s$^{-1}$, and Q(H$^{\circ}$) which is the ionizing photon rate is in units of s$^{-1}$.
-The constant at the right-hand side of equation~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is the normal case in the interstellar medium.
-All SFR indicators that use the ionization of hydrogen to trace the formation of massive stars are sensitive to the effects of dust.
-Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important systematic error for calculating the SFR from hydrogen recombination line.
+where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
+The constant on the right-hand side of equation~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the interstellar medium.
+%PB: typical in the ISM, or typical in HII regions?
+All SFR indicators that use the ionization of hydrogen to trace the formation of massive stars are sensitive to the effects of dust. %PB think you can drop this sentence.
+Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
 The effects of dust must be measured and \halpha observations must be corrected or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
+%PB: are you going to explain how correction is done?
 
-Another nebular line, which is used as a tracer of the SFR is \oii~$\lambda$3727$\AA$.
-Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has correlation with the \halpha emission. 
-As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity.
+Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. %PB: explain what a forbidden line is..
+Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
+As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. %PB: are you sure about the explanation in the 2 prev sentences? Please check.
 \cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
-Another calibration for this luminosity was derived by \cite{Kennicutt92}, which has a different calibration factor. 
+Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
 In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
@@
 \end{equation}  
-where SFR(\oii) is in M$_{\odot}$ yr$^{-1}$, L(\halpha) is in erg s$^{-1}$. 
+where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\halpha) is in erg~s$^{-1}$. %PB: do you mean  L([O\ II]) instead of L(\halpha)?
 Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high redshift galaxies.
-In high redshift galaxies, \halpha emission line is out of optical bands, as a consequence, calibration of the strongest emission feature in the blue light (\oii) as a SFR indicator is really useful~\citep{Kennicutt98b}.
+In these galaxies, the \halpha emission line is redshifted out of the optical band; as a consequence, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is really useful~\citep{Kennicutt98b}.
 
-Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the IR emission can be used to trace the SFR.
-The IR luminosity of a system depends not only on the amount of the embedded dust, but also on the heating rate provided by the stars. 
-Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
-The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED has peaked at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with the dust heated by old or low-mass stars.
-Therefore, the IR wavelength is able to detect the emission from the young stellar population and be used as an SFR indicator.
+Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the infrared emission can be used to trace the SFR.
+The IR luminosity of a system depends not only on the amount of embedded dust, but also on the heating rate provided by the stars. 
+Since young stars heat the dust to higher mean temperatures than old stellar populations, to first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
+The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
+Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.
 
-24~$\mu$m and 70~$\mu$m bands are two empirical single-band IR SFR calibrators. 
-The use of these two bands depends on the type of the galaxy studied or the physical environment in different regions within the galaxy. 
-Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) and a local indicator.
-That is because the global case includes the Hubble time integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as: \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
-Table~\ref{table2} shows the constant C from equation~\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities and for local (spatial scale $\sim500$~pc for 24~$\mu$m band and spatial resolution less than $\sim 1$ kpc for 70~$\mu$m one) and global cases.
+Two empirical single-band infrared star formation rate indicators are the 24~$\mu$m and 70~$\mu$m bands.  
+The use of these two bands depends on the type of galaxy studied or the physical environment in different regions within the galaxy. 
+Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) or a local indicator.
+That is because the global case includes the Hubble time integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
+%PB: "Hubble time" is astro-jargon..
+Table~\ref{table2} shows the constant $C$ from equation~\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities, for local (spatial scale $\sim500$~pc for 24~$\mu$m and $\lesssim 1$ kpc for 70~$\mu$m) and global cases.
 
@@
 \centering
-\caption{IR Luminosity to SFR calibrations}
+\caption{Infrared Luminosity to star formation rate calibrations}
 \label{table2}
@@
 \hline\hline
-Luminosity$^1$ & C & Assumptions & references\\
+Luminosity$^1$ & $C$ & Assumptions & references\\ %PB: please check the edits I made here.
 \hline
-L(24)$^{0.885}_{local}$ & $1.31 \times 10^{(-38)}$ &$(1.10^{40} \le L(24) \le 3.10^{44})$& Calzetti et al. (2007)  \\
-L(24)$_{global}$ & $2.04 \times 10^{(-43)}$ &$ (4.10^{42} \le L(24)  \le 5.10^{43})$& Calzetti et al. (2007) \\
-L(70)$_{local}$ & $9.4 \times 10^{(-44)} $ &$(5.10^{40} \le  L(70) \le 5.10^{43})$& \cite{Li12} \\
-L(70) $_{global}$& $5.9 \times 10^{(-44)}$ &$(L(70) \ge 1.4 \times 10^{42} $& \cite{Li10}\\
+L(24)$^{0.885}_{local}$ & $1.31 \times 10^{-38}$ &$1.10\times 10^{40} \le L(24) \le 3.10\times 10^{44}$& Calzetti et al. (2007)  \\ %PB: use \cite
+L(24)$_{global}$ & $2.04 \times 10^{-43}$ &$ 4.10\times 10^{42} \le L(24)  \le 5.10\times 10^{43}$& Calzetti et al. (2007) \\
+L(70)$_{local}$ & $9.4 \times 10^{-44} $ &$5.10\times 10^{40} \le  L(70) \le 5.10\times 10^{43}$& \cite{Li12} \\
+L(70)$_{global}$& $5.9 \times 10^{-44}$ &$L(70) \ge 1.4 \times 10^{42} $& \cite{Li10}\\
 \hline
@@
 \begin{tablenotes}
-\item $^1$ Luminosities are in form of L($\lambda$) = $\lambda$ L($\lambda$) in erg s$^{-1}$
+\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L($\lambda$) in erg s$^{-1}$ %PB: this doesn't make sense: L = \lambda L ?? Or is this missing a _{\lambda} or _{\nu} ?
 \end{tablenotes}
@@
 
-\subsubsection*{SFR Indicators Based on the Multi-Band Emission}
+\subsubsection*{SFR Indicators Based on Multi-Band Emission}
 

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to multiband SFR indicators subsection

@@
 %%add PAHs here
-Despite the usefulness of having single-band SFR tracers, in many cases the corrections due to dust effects and luminosity ranges increases the uncertainty in measurements.
-Nowadays, thanks to large surveys, enormous data is available at different wavelengths for galaxies, which allows for combining the emission from different bands and finding new calibrations.
-Conversion between SFR and luminosities at different bands mostly helps avoiding problems regarding dust extinction or attenuation (see~\ref{sec: ism_intro}). 
-The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically proved~\citep{Kennicutt12}.
+Despite the usefulness of having single-band SFR tracers, in many cases the corrections due to dust effects and luminosity ranges increase the uncertainty in measurements.
+Nowadays, thanks to large surveys, enormous amounts of data are available at different wavelengths for galaxies, which allows for combining the emission from different bands and finding new calibrations.
+The conversion between SFR and luminosities in multiple bands mostly helps to avoid problems regarding dust extinction or attenuation (see~\ref{sec: ism_intro}). 
+The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically derived~\citep{Kennicutt12}.
 %There are studies that use a higher order polynomial relation to combine luminosities~\citep[e.g.,][]{Buat05}; however, this discussion is out of the scope of this paper.
 
-Integrating over the full wavelength range of the IR part of spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator. 
+Integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator. 
 As mentioned earlier, dust absorbs stellar radiation at all wavelengths; however, here we are only interested in radiation emitted from UV luminous stars.
-It must be noted that since there is no one-to-one mapping between IR and UV emission~\citep{Calzetti13}, it is better to use the TIR emission as a tracer of the SFR instead of single-band IR emission.
+% PB: not obvious how this sentence relates to ones before and after it
+Since there is no one-to-one mapping between IR and UV emission~\citep{Calzetti13}, it is better to use the TIR emission as a tracer of the SFR instead of single-band IR emission.
 
-\cite{Draine07} modelled observations from \Spitzer telescope and found a calibration for TIR luminosity from photometry images instead of using IR SED. 
-\cite{Boquien10} tested this calibration and found the modified version of calibration to estimate total infrared luminosity: 
+\cite{Draine07} modelled observations from the \Spitzer Space Telescope and found a calibration for TIR luminosity from spatially-resolved infrared photometry instead of the integrated infrared SED.
+%PB: please check that edits OK.
+Also, this sentence doesn't flow well from the previous text.
+\cite{Boquien10} tested this calibration and found a modified version to estimate the total infrared luminosity: 
 \begin{equation}
@@
 \end{equation}
-where $L = \nu L_{\nu}$ and $L_{\nu}$ is the luminosity  in erg s$^{-1}$ at frequency $\nu$. 
-\cite{Calzetti07} indicated that star formation rate calibration for a stellar population undergoing constant star formation over $\tau=100Myr$ is:
+where $L = \nu L_{\nu}$ and $L_{\nu}$ is the luminosity  in erg~s$^{-1}$ at frequency $\nu$. 
+\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=100$~Myr is:
 \begin{equation}
@@
 \end{equation}
-where SFR(TIR) is in M${\odot}$yr$^{-1}$, and L(TIR) is in erg s$^{-1}$. 
+where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$. 
 To do this calculation, it is assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{\mathrm{star}}({\rm bol})=L(\rm TIR)$.
+%PB: is this a reasonable assumption.
 
-As mentioned before emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
-Most of studies used MIR emission, which contains PAHs emission, to calibrate SFR~\citep[e.g.][]{Calzetti07}.
-\cite{Shipley16} calibrated SFR using observation from 105 star framing galaxies with $z < 0.4$ as:
-
+As mentioned before emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}. %PB: give section ref instead of "before"
+Most studies used infrared emission, which contains PAHs emission, to calibrate SFR~\citep[e.g.][]{Calzetti07}.
+%PB: are you saying that previous studies use broad bands which contain PAHs, but here you're dealing with the PAH features only?
+\cite{Shipley16} calibrated SFR using observation from 105 star-forming galaxies with $z < 0.4$ as:
 \begin{equation}
-log SFR = A + B log L_{\mathrm{PAH}, \lambda}
+\log SFR = A + B \log L_{\mathrm{PAH}, \lambda}
 \end{equation}
-where $L_{\mathrm{PAH}, \lambda}$ is luminosity of PAH features at 6.2, 7.7, 11.3~$\mu$m PAHs features and any combination thereof in erg s$^{-1}$.
+where $L_{\mathrm{PAH}, \lambda}$ is the luminosity of the PAH features at 6.2, 7.7, 11.3~$\mu$m or combinations thereof, in erg~s$^{-1}$.
 Tab.~\ref{table_PAH} shows the constants for each $L_{\mathrm{PAH}, \lambda}$.
-These calibration underestimates SFR for low-redshift galaxies with IR luminosity more than $10^12$erg s$^{-1}$.
-\cite{Shipley16} showed that adding 7.7~$\mu$m features in calibrations reduces the scatter and concluded that this wavelengths provides the most robust SFR tracer.
+These calibrations underestimate the SFR for low-redshift galaxies with IR luminosity more than $10^12$~erg~s$^{-1}$.
+\cite{Shipley16} showed that using the 7.7~$\mu$m feature in the calibration reduces the scatter and concluded that this wavelength provides the most robust SFR tracer.
 
@@
 \centering
-\caption{SFR calibrations from PAHs luminosities; adopted from~\cite{Shipley16}}
+\caption{SFR calibrations from PAH luminosities; adopted from~\cite{Shipley16}}
 \label{table_PAH}
@@
 \hline
-6.2 + 7.7 + 11.3 & -42.56 $\pm$ 0.03 & 1.00 $\pm$ 0.03 \\ 
+6.2 + 7.7 + 11.3 & -42.56 $\pm$ 0.03 & 1.00 $\pm$ 0.03 \\ %PB: change from x $\pm$ y to $x\pm y$
 6.2 & -40.06 $\pm$ 0.09 & 0.96 $\pm$ 0.04 \\ 
@@
 
-The most common use of combining luminosities to trace the SFR is calibration of the SFR by combination of TIR measurements with both far and near UV observations, with the latter being more commonly used.
-This combination helps to avoid uncertainties from dust attenuation in FUV observations.
+The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used.
+This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations. The calibration is: %PB: need ref
 \begin{equation}
@@
 \end{equation}
-where the luminosities are $L = \nu L_{\nu}$ in erg s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses that are chosen for the UV and IR measurements.
-$\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies is from dust heated by older population stars~\citep{Kennicutt12}.
+where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements.
+$\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}.
 The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.p][]{Hao11, Leroy08}.
@@
 \label{equ: halphaplus24}
-SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24)]
+SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24)]
 \end{equation}
-where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg s$^{-1}$. 
-L(24) is the 24~$\mu$m IR luminosity in erg s$^{-1}$, and SFR is in M$_{\odot}$yr$^{-1}$.
+where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. 
+L(24) is the 24~$\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$~yr$^{-1}$.
 
@@
 \hline
-L(FUV)$_{corr}$=L(FUV)$_{obs}$ + 0.46L(TIR)& Hao et al. (2011)\\
-L(FUV)$_{corr}$=L(FUV)$_{obs}$ + 3.89L(24~$\mu$m)& Hao et al. (2011)\\
-L(NUV)$_{corr}$=L(NUV)$_{obs}$ + 0.27L(TIR)& Hao et al. (2011)\\
-L(NUV)$_{corr}$=L(NUV)$_{obs}$ + 2.26L(24~$\mu$m)& Hao et al. (2011)\\
-L(\halpha)$_{corr}$=L(\halpha)$_{obs}$ + 0.0024L(TIR)& Kennicutt et al. (2009)\\
-L(\halpha)$_{corr}$=L(\halpha)$_{obs}$ + 0.020L(24~$\mu$m)& Kennicutt et al. (2009)\\
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& Hao et al. (2011)\\ % use \cite
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& Hao et al. (2011)\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& Hao et al. (2011)\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& Hao et al. (2011)\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& Kennicutt et al. (2009)\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& Kennicutt et al. (2009)\\
 \hline
@@
 \begin{tablenotes}
-\item $^1$ Luminosities are in form of L($\lambda$) = $\lambda$ L($\lambda$) in erg s$^{-1}$
+\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L($\lambda$) in erg~s$^{-1}$ %PB see comments above on this.
 \end{tablenotes}
@@
 
-Other combinations of luminosities that are used as tracers of the SFR are listed in table~\ref{table3}. 
+Other combinations of luminosities that are used as tracers of the SFR are listed in Table~\ref{table3}.
+%PB: are these corrected values used with the SFR calibrations in table 1?
+Or do they need different calibrations?
 These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
@@
 
-As mentioned in section~\ref{sec: imf}, using different IMFs results in having different SFR calibrations' constant. 
-From table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
-This effect is more than four times larger than UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV radiations; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
-Furthermore, reaching an asymptotic value takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
-Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR calibration constants are fairly close to each other.
-On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than $10\%$ difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
+%PB: would it make sense to put this paragraph closer to where you first discuss Table 1?
+As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
+From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
+This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
+% PB: "more strongly" than what?
+Furthermore, reaching an asymptotic value takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). % PB: "asymptotic value" of what?
+Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR the calibration constants are fairly close to each other.
+On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a $10\%$ difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
 As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.
+
+% PB: SFR section is pretty long, might help to have a short summary here, perhaps when you would use different indicators.
+Expanding the "Other combinations" paragraph a bit would be a way to do this.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to stellar mass section up to but not including dynamical mass

@@
 \label{sec: starmass_intro}
-One of the most fundamental physical parameters which describes the present state of the galaxies is stellar mass. 
+One of the most fundamental physical parameters which describes the present state of a galaxy is its stellar mass. 
 Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and all morphologies~\citep{Scodeggio02}. 
-In order to determine stellar population in spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass~\citep{Bell00}. 
-\cite{Kauffmann03} tested that on more than 100,000 galaxies observed by Sloan Digital Sky Survey~\citep[SDSS;][]{York00}. 
-They also showed that these results are applied for all morphological types.
+In order to determine the stellar populations of spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass~\citep{Bell00}. 
+\cite{Kauffmann03} tested that on more than 100,000 galaxies observed by the Sloan Digital Sky Survey~\citep[SDSS;][]{York00}. %PB: what is "that"?
+They also showed that these results applied to all morphological types. %PB: what are "these results" ?
 
-Measuring the mass of the stellar population is indirect and subject to significant uncertainties. 
+Measuring the mass of a stellar population is indirect and subject to significant uncertainties. 
 In principle there are two ways to measure stellar mass in galaxies. 
-First is measuring the dynamical mass of galaxies using kinematics~\citep{Cappellari06} or lensing~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
+The first is measuring the dynamical mass of a galaxy using kinematics~\citep{Cappellari06} or lensing~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
+%PB: "kinematics" and "lensing" are astro-jargon: please explain a bit more
 This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies~\citep{Zaritsky94}, and can easily cause uncertainties as high as the order of the measurement.
+%PB: but is it successful in measuring the stellar mass?
 
-The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
-This method has uncertainties too, and one must also model the uncertainties. 
-Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where they have most luminosity in their evolution, and the evolutionary state of galaxy~\citep[see,][]{Dalcanton12}, and star formation histories.
+The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution.
+This method has uncertainties too, and one must also model the uncertainties. %PB: sentence not useful.
+Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][]{Dalcanton12}, and star formation histories.
 
-In order to translate between photometry and dynamics the stellar mass to light ratio (M/L) is needed. 
-Measuring the accurate M/L can easily lead us to stellar mass surface density.  
-To do that, the M/L by can be measured using scale relation between them, from different colours and then multiply it by the surface brightness to calculate the local surface stellar mass density. 
-The M/L scale relations make a connection between two methods of measuring stellar mass~\citep{Bell03}. 
-These relations are indirect methods for measuring the stellar masses and have high uncertainties in specific cases, but they help to study the stellar mass in large samples. 
-This is one of the solution to the problem of the measuring the stellar mass within galaxies. 
-As a result it is important to check the accuracy of total stellar mass estimations and provide methods, which measure and produce a map of the stellar mass surface density distribution in galaxies. 
-This method gives more accurate result than measuring the stellar mass surface density distribution from single-band images rescaled by uniform mass to light ratio~\citep{Zibetti09}.
+%PB: this paragraph was very difficult to understand and I did a lot of rewriting. Please check.
+In order to translate between photometry and dynamics the stellar mass-to-light ratio ($M/L$) is needed. %PB: is this the first method or the second one? It's not really about dynamics.
+The use of $M/L$ is one way to measure stellar mass surface density. It is an indirect method and has high uncertainties in specific cases, but can help to study the stellar mass in large samples. 
+For integrated galaxy light, the $M/L$ is estimated using scaling relations between $M/L$ and broadband colours \citep[e.g.]{Bell03} and then multiplied by luminosity to estimate a mass.
+For resolved galaxies, one can produce a map of the stellar mass surface density distribution in galaxies using resolved colour to measure spatial variations in $M/L$.
+This method gives more accurate results than measuring the stellar mass surface density distribution from single-band images rescaled by a uniform mass to light ratio~\citep{Zibetti09}.
 
-Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences. 
-Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. 
-Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 per cent, so one should be more careful to model subtleties~\citep{McLaughlin05}.
+Having two independent methods to measure stellar mass helps to check whether there are any systematic differences. 
+Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. %PB: ref?
+Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 per cent, so one should be careful to model subtleties~\citep{McLaughlin05}.
 
@@
 The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi lines. 
-Thanks to the current generation of detectors, the \halpha and CO lines have very high-resolution spectra over most of the optical disk, and cover most regions in the sky. 
+Thanks to the current generation of detectors, it is possible to obtain  very high-resolution spectra in the \halpha and CO lines  over most of the optical disks of galaxies.
+% and cover most regions in the sky.
+PB: not sure about "most regions of sky"
 Integrated line widths only yield an estimate of a total mass within some (uncertain) isophotal radius.

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to stellar population method subsection

@@
 The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution.
+%PB: need a one-sentence description of what these models do.
 This method has uncertainties too, and one must also model the uncertainties. %PB: sentence not useful.
@@
 
-\subsection{Dynamical Mass}
+\subsection{Dynamical Mass} %PB: suggest "galaxy masses from dynamics"
+% PB: should following paragraph go after the second paragraph?
 The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi lines. 
@@
 PB: not sure about "most regions of sky"
-Integrated line widths only yield an estimate of a total mass within some (uncertain) isophotal radius.
+Integrated line widths only yield an estimate of total mass within some (uncertain) isophotal radius.
 
 Resolved rotation curves produced from \halpha, \hi and CO lines are proportional to optical emission lines within the optical disk of galaxies,~\citep{Courteau13} which helps us to measure the rotational curves.
-The simplest way to estimate the mass of a galaxy is assuming that the physics of the galaxy is the simple Newtonian physics. 
-Therefore, the Mass within a potential $\phi$ and the circular velocity in the spherical system is given by:
+%PB: don't get the purpose of this sentence
+The simplest way to estimate the mass of a galaxy is assuming that the physics of the galaxy is simple Newtonian physics.
+%PB should be clear that this is what nearly everyone does (almost no one assumes that physics isn't Newtonian)
+Therefore, the circular velocity $v{\rm circ}(r)$ of an orbit within a spherical system of gravitational potential $\phi$ and mass $M$ is given by:
 \begin{equation}
 \label{eq: simpmass}
-V^2_{circ}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r}
+v^2_{\rm circ}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r}
 \end{equation}
-where $M(r)$ is the mass within a sphere of radius $r$. 
-For a flattened disk which is the case in most spiral galaxies, the right hand side of equation~\ref{eq: simpmass} must be replaced by the more exact expression derived by~\cite{Freeman70}. 
-He assumed in case of no dark matter or bulge, the rotation curve of a self-gravitating disk is:
+where where $G$ is the gravitational constant and $M(r)$ is the mass within a sphere of radius $r$. 
+For a flattened disk, which is the case in most spiral galaxies, the right hand side of equation~\ref{eq: simpmass} must be replaced by the more exact expression derived by~\cite{Freeman70}. 
+For the case of no dark matter or bulge, \cite{Freeman70} showed that the rotation curve of a self-gravitating disk is:
 \begin{equation}
-V^2_{circ}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)]
+v^2_{circ}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)]
 \end{equation}
-where $G$ is the gravitational constant, $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, $4y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kind of modified Bessel functions.
+where $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, $4y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kinds  modified Bessel functions.
+%PB what is y?
+Also need to define scale length.
 
-Describing more about calculating dynamical masses in galaxies is beyond the scope of this paper. 
-Just note that methods mentioned above is the first order of approximation. 
-For more accurate result one should consider that the rotational velocity is not circular and the fact that galaxies contain millions of stars plus interstellar objects therefore simple two object Newtonian physics is not the case here.
-There are lots of different profiles to fit the rotation curve for galaxies.
-A detailed review of dynamical mass of galaxies can be found in Courteau et al review paper (2013).
+A detailed description of calculating dynamical masses in galaxies is beyond the scope of this work. 
+The methods mentioned represent the first order of approximation. 
+For more accurate results, one should consider non-circular rotational velocities and the fact that galaxies contain millions of stars plus interstellar objects; therefore simple two-object Newtonian physics is not the case here.
+%There are many different profiles to fit the rotation curve for galaxies. PB: not useful.
+A detailed review of dynamical masses of galaxies can be found in \citet{Courteau13}.
 
-\subsection{Stellar Population Method}
-Galaxies can be observed because of their stellar emission and stars radiate the energy produced from nuclear reactions in their cores. 
-Given the star's initial mass, the theory of stellar evolution can describe the amount of energy released. 
-Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distribution of galaxies. 
-However, there is a fraction of mass of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants.
+\subsection{Stellar Population Method} %PB: suggest  "galaxy masses from stellar population modelling"
+Galaxies can be observed because of their stellar emission; stars radiate the energy produced from nuclear reactions in their cores. 
+Given a star's initial mass, the theory of stellar evolution can describe the amount of energy released. 
+Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distributions of galaxies. 
+However, some fraction of the mass of galaxies consists of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants. %PB: so what do we do about this?
 
-As mentioned before, stellar population synthesis models is used to reproduce the SED of a stellar population using many physical parameters. 
-These parameters, which control the time evolution of the stellar population are:
-the age, $t$, of the population, measured in years, also referred to the time passed since the star formation was began;
-the star formation history (SFH), often parametrized with SFR $\propto e^{-1/\tau}$; the IM; The metallicity; and the chemical composition ratios, or the fraction of all key elements in galaxies and those values measured in the Sun.
-The stellar evolutionary tracks, the stellar spectral libraries, the parametrization for the mass-loss which affects several late stages of evolution are necessary for stars placing at specific evolutionary phases~\citep{Courteau13}.
+Stellar population synthesis models are used to predict the SED of a stellar population using many physical parameters. 
+These parameters, which control the time evolution of the stellar population, are:
+the age, $t$, of the population, measured in years, also referred to as the time passed since the star formation began;
+the star formation history (SFH), often parametrized with SFR $\propto e^{-1/\tau}$; the IMF; the metallicity; and the chemical composition ratios, usually measured relative to values measured in the Sun.
+Stellar evolutionary tracks, the stellar spectral libraries, and the parametrization for mass-loss which affects several late stages of evolution are necessary for stars placing at specific evolutionary phases~\citep{Courteau13}.
+%PB: this sentence has a lot of astro-jargon
 
+%PB: please think about how info in following few paragraphs should logically go together into paragraphs.
 %\subsubsection{Calibration light of stars} 
-The basic idea behind the finding the suitable calibration between flux/luminosity of the stars in different wavelengths and stellar mass is that one can use the SFHs recovered from synthesizing the stellar optical CMs in different regions in the galaxies.
-The calculated stellar mass can be used to calibrate the fluxes from the stars as the easily measurable parameters of stars. 
-Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies~\citep[e.g.,][]{Elmgreen84}.
-Using $B-V$ colours~\citep{Bell01} and $Spitzer$ 3.6- and 4.5-$\mu$m, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
+The basic idea behind finding a suitable calibration between flux/luminosity of the stars in different wavelengths and stellar mass is that one can use the SFHs recovered from synthesizing the stellar optical colour-magnitude diagrams in different regions of a galaxy.
+The calculated stellar mass can be used to calibrate the fluxes from the stars as the easily measurable parameters of stars. %PB: don't understand what "as the easily.." means here.
+Using NIR bands, different groups tried to make a map of stellar mass distribution within galaxies~\citep[e.g.,][]{Elmgreen84}.
+Using $B-V$ colours~\citep{Bell01} and {\em Spitzer} 3.6- and 4.5-$\mu$m, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
+%PB: unclear how this  sentence relates to other text.
 
-\cite{Zibetti08} suggested for reaching the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel study~\citep{Conti03}. 
-They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density. 
+\cite{Zibetti08} suggested that to reach the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel basis~\citep{Conti03}. 
+They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density. %PB: join paragraphs. 
 To do so the surface density of stellar mass is derived by 
@@
 \end{equation}
-where $\Sigma \lambda(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L in an effective wavelength $\lambda$. 
+where $\Sigma \lambda(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L at an effective wavelength $\lambda$.
+% PB what are \alpha, \delta ?
 In equation~\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy. 
@@
 \cite{Eskew12} related easily observable quantities to the stellar mass. 
-They used 3.6 and 4.5$\mu$m fluxes for calibration of the stellar mass, because these two bandpasses are almost insensitive to the emission from young stellar population, dust absorption and emission.
-Also thanks to \Spitzer~\citep{Wener04} data and WISE~\citep{Wright10} telescopes, great amount of data from many regions in the sky is available, in these bands, which help to test them on more regions and have a more accurate calibration.
-They also test the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and find the empirical relation between mass of the stars and the luminosities of stars as below:
-
+They used 3.6 and 4.5$\mu$m fluxes for calibration of the stellar mass, because these two bandpasses are almost insensitive to the emission from young stellar population or to dust absorption and emission.
+Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} telescopes, a large amount of data in these bands from many regions in the sky is available, which helps thave a more accurate calibration.
+\cite{Eskew12} tested the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and found an empirical relation between mass of the stars and the luminosities of stars as:
 \begin{equation}
@@
 \end{equation}
-where M$_{\star}$ is the stellar mass and $L = \nu L_{\nu}[\lambda]$ is luminosity in erg s$^{-1}$/$\AA$.
+where M$_{\star}$ is the stellar mass and $L = \nu L_{\nu}[\lambda]$ is luminosity in erg~s$^{-1}$/$\AA$. %PB: units of stellar mass?
 
-\cite{Zhu10} used the SDSS and the $Spitzer$ Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find the calibration between luminosity of the galaxies and stellar masses. 
-Using the M/L of galaxies, they found the correlation between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulate these correlations as:
+\cite{Zhu10} used the SDSS and the {\em Spitzer} Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find another calibration between galaxy luminosity and stellar mass. 
+Using the $M/L$ of galaxies, they found correlations between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulated these correlations as:
 \begin{align}
@@
 \end{align}
-where M$_{\star}$ is the stellar mass and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg s$^{-1}$ in specified wavelength. 
-Measuring the stellar mass from equation~\ref{equ:eskew} is limited to the nearby galaxies, and might break down for high star forming regions, moreover, this equation have not tested on regions with different metallicity.
-Thus there is no calibration regarding variation in  metallicity~\citep{Eskew12}. 
-On the other hand equations~\ref{equ: zhu1} -~\ref{equ: zhu3} have been derived from a large sample of galaxies, and was tested on different type of regions and galaxies. 
-Beside they can be used for more distanced galaxy as well as nearby galaxies~\citep{Zhu10}. 
+where M$_{\star}$ is the stellar mass and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg~s$^{-1}$ at the specified wavelength. 
+Measuring the stellar mass from equation~\ref{equ:eskew} is limited to nearby galaxies, and might break down for highly star-forming regions; moreover, this equation has not tested on regions with different metallicity.
+Thus there is no information on the effects of variation in  metallicity~\citep{Eskew12}. 
+On the other hand equations~\ref{equ: zhu1}--~\ref{equ: zhu3} have been derived from a large sample of galaxies, and were tested on different type of regions and galaxies. 
+They can be used for more distant galaxies as well as nearby galaxies~\citep{Zhu10}. %PB: why is Zhu et al good for distant galaxies but Eskew is not?
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Complete picture of galaxies are formed and evolved are tied to unfolding the mystery of formation of stars.
+A complete picture of galaxies are formed and evolved are tied to unfolding the mystery of formation of stars.
  Various phenomena affect the collapse of molecular clouds and star formation which include environment of the star-forming region, chemical compositions of the region, initial mass distribution of gas, mass of sounding stars and other physical properties of galaxies

### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to preview section

@@
 
-A complete picture of galaxies are formed and evolved are tied to unfolding the mystery of formation of stars.
- Various phenomena affect the collapse of molecular clouds and star formation which include environment of the star-forming region, chemical compositions of the region, initial mass distribution of gas, mass of sounding stars and other physical properties of galaxies
- For decades, Observational, theoretical and numerical studies have investigated star formation; nevertheless, their results have never been precise. 
- Empirical studies are used alongside of theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
+A complete picture of how galaxies are formed and evolve is tied to unfolding the mystery of the formation of stars.
+ Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas, the mass of sounding stars and other physical properties of galaxies.
+%PB "sounding stars" ?
+"other physical properties" is vague - either be specific or delete it.
+ For decades, observational, theoretical and numerical studies have investigated star formation; nevertheless, their results have never been precise.
+%PB: not really clear what you mean by "precise" here.
+ Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
 
-The most well-known scaling law is the relation between the surface density of FR and the gas surface density, which is known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
-The K-S law and similar empirical laws were tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
-Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are yet undetermined and there is no definitive answer on whether there is any universal star formation laws.
+The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
+The K-S law and similar empirical laws have been tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
+Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are yet undetermined and there is no definitive answer on whether there is any universal star formation law.
 Their dependence on physical properties of galaxies is nontrivial and sometimes differs by type of star forming regions.
-Although relation between stars and gas are well established, the detail of this relation is not clear.
-Not only different types of gas change SFR in different ways, but also variations in metallicity for each type alter it.
-There is no fully sampled and universal IMF.
-In fact there are many debates on weather IMF is universal or not.
-Influence of evolved stars and distance of star forming regions from centre of galaxies on SFR is mentioned in studies but not fully investigated.
-Besides studying the impact of mentioned properties of galaxies on SFR, searching for other properties of galaxies/star forming regions is continuing.
+Although a relation between star formation and gas is well established, the details of this relation are not clear:
+different types of gas affect SFR in different ways, and variations in metallicity alter the effects.
+There is no fully sampled and universal IMF,
+in fact there are many debates on whether the IMF is universal or not.
+The influence of evolved stars and distance of star forming regions from centre of galaxies on SFR has been mentioned in studies but not fully investigated.
+Besides studying the impact of the above-mentioned properties of galaxies on SFR, searching for other relations between properties of galaxies and their star forming regions continues.
 
-Advances in observing facilities, image qualities, and methodology expands our knowledge of formation of stars.
-Besides these advances, in the past few decades,using advanced statistical methods grew in astronomical studies.
-Applying modern statistical methods on star formation studies can shed a light on unsolved problems in this field. 
-Studies show that using different statistical methods changes our perspective on star formation laws. 
-For example,~\cite{Shetty13} used Bayesian methods to show the K-S law is not universal. 
-On the other hand, since astronomy is a data driven science, data mining methods are quiet useful to get new insight on properties of star forming regions.
+Advances in observing facilities, image quality, and methodology expand our knowledge of star formation. 
+In the past few decades, the use of advanced statistical methods in astronomical studies has also grown.
+Applying modern statistical methods to star formation studies can shed light on unsolved problems in this field. 
+Studies show that using different statistical methods can change our perspective on star formation laws. 
+For example,~\cite{Shetty13} used Bayesian methods to show that the K-S law is not universal. 
+Since astronomy is a data-driven science, data-mining methods should be quite useful to gain new insight on properties of star-forming regions.
+However, these methods have not been widely-applied to studies of nearby galaxies, where the most detailed information about star formation is available.
 
-In this thesis, we present three projects that study effects of quantities of galaxies on SFR.
-We use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties and using modern statistical methods study their impact on SFR.
-Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxies (M31) in both local and global scales using hierarchical Bayesian analysis.
-Additional to the K-S law, we study the extended Schmidt law~\citep{Shi11} and and the metallicity/star formation correlation~\citep{Krumholz09}.
-We also show the effect of using different SFR and ISM gas tracers on star formation laws.
-In Chapter~\ref{ch: paper3}, we explore nearby galaxies using an unsupervised data mining method (self organizing map, SOM).
-We cluster observational data and derived quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
-We find hidden structures in high dimensional data space during this process.
-In Chapter~\ref{ch: paper2}, we move to higher redshift and apply SOM algorithm on SED of high-redshift galaxies.
+%PB not sure, but you might need a little more intro to the papers 2 and 3 stuff here.
+
+In this thesis, we present three projects that study the effects of galaxy properties on star formation.
+We use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
+Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
+In addition to the Kennicutt-Schmidt law, we study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
+We also show the effect on star formation laws of using different SFR and ISM gas tracers.
+In Chapter~\ref{ch: paper3}, we explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
+We cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
+During this process, we find hidden structures in high-dimensional data space.
+In Chapter~\ref{ch: paper2}, we move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
 We train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
-Then, we study the grouped properties of classified galaxies.
-For each chapter, we also describe the methodology and data used in that chapter.
+Then we study the grouped properties of the classified galaxies.
+%For each chapter, we also describe the methodology and data used in that chapter. %PB: not needed.
 We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}

### 2016-07-13 version0.0/intro0.0.tex
finishing edits on intro

@@
 There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
-Nearly all the information we can obtain from galaxies other than our own comes from their light. % now we can detect gravitational wave which is not part of the SEDs, right? % PB: right.
-Young and evolved stars and dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
-%PB: explain what you mean by spectral energy distribution
-We cannot detect any contribution from planets and black holes to SEDs due to their low intensity compared to these other components.
-%or the limitation of our detectors.
-% PB: need to rephase a bit  to mention AGN!
+Nearly all the information we can obtain from galaxies other than our own comes from their light.
+Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
+a plot of brightness/flux density of galaxies as a function of wavelengths, which is called spectral energy distribution (SED), is a useful tool to have a intuition about galaxies. 
+Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
+We cannot detect any contribution from planets and black holes, the ones without accretion disc, to SEDs due to their low intensity compared to these other components.
 Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.
@@
 %ISM 1)Gas 2)dust
-There could be a galaxy without stars (i.e.
+%There could be a galaxy without stars (i.e.
 dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas.
-%PB: this is a very strong statement.
+%: this is a very strong statement.
 Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now).
 So qualify this a bit.
+done
+Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
 Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM).
@@
 
-% Metallicity %PB: you start talking about metallicity but then switch over to SF. Overview the SF process first, then talk about how metallicity affects it.
-Metallicity, which is defined as the ratio of abundance of metals to the abundance of hydrogen, affects formation and evolution of stars indisputably. %PB: define what "metals" means here
 In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
-The interplay of turbulence and magnetic fields with self-gravity is believed to be responsible for the formation of clumps within GMCs. 
-Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF) while turbulence and magnetic fields play central roles in defining this distribution (see~\cite{McKee07} for more detail).
-%PB: this sentence has a lot of concepts in it: going to be hard for non-astronomer to understand
+The denser regions within GMCs collapse under their own gravity, self-gravity, and creates clumps.
+Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
+Then these clumps continue to become denser and transfer to protostars. 
+Since the protostars have higher mass than their surrounding, more gas from GMCs add to protostars.
+This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).
+
+Metallicity, which is defined as the ratio of abundance of metals (any element heavier than hydrogen and helium) to the abundance of hydrogen, affects formation and evolution of stars indisputably.
 \cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores.
-%PB: please check edits to prev sentence
-Metals also play an important role in heating, cooling and ionizing processes in the ISM. %%ADD ref.
+Metals also play an important role in heating, cooling and ionizing processes in the ISM.
 Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
-%Sahar: should I talk about metallicity in stars and their relation with age?
-%PB: yes.
-Need to introduce the general idea of chemical evolution - you hint at this above, but can state it explicitly.
+Amount of metals in stars affect their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
+For example, low metallicity stars tend to be have lower mass loss by stellar wind than that with higher metallicity.
+Since there is lower amount of mass loss in low metallicity stars, hence no loosing angular momentum because of wind, massive low metallicity stars rotate faster.
+Being more massive at the end of evolutionary track, makes massive low metallicity stars lower chance to explode (become a supernova).
 
 %what does SED look like?
-Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. %PB: since SED is a really important concept, I took out the acronym here.
-Broadly speaking, young and hot stars emit most of their light in iltraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
+Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. 
+Broadly speaking, young and hot stars emit most of their light in ultraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
 Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
@@
 
- %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass %PB: Need more detail here - how do SED models include SFR, Mstar, etc?
+ %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
 The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
-A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.%, to fit the observed SEDs.
+A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
 Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
-Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs using the templates.
+Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs, (either by minizing $\chi^2$ or by Bayesian analysis)  using the templates.
 One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
-It combines SED models to find the best-fit SED for observed data in the rest-frame UV-to-IR and finds physical properties of galaxies such as SFR, stellar mass and dust attenuation.
+It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
+Some of the physical properties of galaxies should be assumed as an input data to find best SED, and others will be derived from SED results~\citep[See][for more detail]{Walcher08}.
+For example, the Best fitted SED has information regarding star formation history and stellar mass to light ratio.
+By integrating star formation history over specific time scale, SFR can be derived. 
+knowing the stellar mass to light ratio, one can used observed luminosity to calculate stellar mass in galaxies.
 
-%PB: I think you need a one-or-two sentence intro to the overall thesis goals here, so that the reader can see why you are talking about all of this stuff.
+Formation of stars in galaxies depends on many parameters, gas, stellar mass, metallicity, dust, galaxy's morphology and location of the star forming region inside the galaxy.
+In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.
+Studying star formation and its relation to other quantities in galaxies in an ongoing progress.
 In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
@@
 
-\section{Interstellar Medium} %PB: suggest "Components of the Interstellar Medium in Galaxies" or "The Interstellar Medium in Galaxies"
+\section{Components of the Interstellar Medium} 
 \label{sec: ism_intro}
@@
 The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
-%PB: in general, don't start a sentence with an acronym.
 The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
@@
 Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
-%Among these regions in ISM, molecular clouds, \hii~regions and dust clouds have important role in understanding star formation in galaxies. 
 Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
@@
 
-Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses. %~\citep{Bolato08}. %PB: why no citation?
-Density in the molecular clouds is not uniform; dense and colds clumps. %PB: I don't get this sentence.
+Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
+Density in the molecular clouds is not uniform; There are dense and colds clumps inside these clouds.
 Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
-However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect in visible light.
-%PB: just visible light, or all wavelengths?
+However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect.
 The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
 Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
-In fact, most of our knowledge from extragalactic molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds.
-%PB just extragalactic, or Galactic too?
-Phrase marked with \bf needs clarification
+In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds.
+%PB \bf needs clarification
 Other heavier molecules have emission lines which are also detectable in the spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.
@@
 ~\halpha emission is the main observational feature of \hii~regions.
-The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, \sii, \oii, \oiii, and \nii. 
+The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
+Forbidden lines are not ``forbidden", they only have much lower probability of occurring than the ``allowed" ones.
 Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
-%PB: moved this sentence.
 Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
 
-%PB: it is difficult to see how the sentences in this paragraph fit together. Right now it reads like a collection of barely-related facts.
 Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
-The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
-In spiral galaxies dust grains are located in cold regions ($\sim 30$~K) and have a power-law distribution of size.
+%The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
+In spiral galaxies dust grains are located in cold regions ($\sim$30~K) and have a power-law distribution of size.
 Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
-Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed type ``A" and ``B'' stars~\cite{Peeters04}.
-%PB: A and B or O and B?
+Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate mass young stars~\cite{Peeters04}. 
 Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
@@
 
-\subsection{Map of ISM} %PB: suggest "Mapping the Interstellar Medium"
+\subsection{Mapping the Interstellar Medium} 
 \label{sec: ismmap}
@@
 A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
-Neutral atomic and molecular hydrogen are the most common components of the ISM. %PB: same element
-Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-%PB: point out that He can't be observed directly
+Neutral atomic and molecular hydrogen are the most common components of the ISM. 
+Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly helium, which cannot be observed directly.
 Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.
@@
 The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
-This method can be promising provided that the spatial resolution of observational data is high enough, although due to technical limitations, attaining enough spatial resolution to resolve clouds is almost impossible.
+This method can be promising if observational data with resolved molecular and atomic clouds are available.
+However, given the state of the current technology, having the high resolution images of clouds for most of galaxies are not possible. 
 This problem shows itself for distant galaxies more than nearby galaxies. 
-As a result, using this method is limited and has a lot of uncertainties. % PB last 3 sentences are vague. What exactly ar the limitations and uncertainties?
+As a result, using images of molecular and atomic cloud to measure surface density of gas in ISM is limited to telescopes resolution.
 
@@
 where $D$ is the distance to the cloud and 
-$I_{\rm CO}$ is the CO brightness temperature integrated over the line profile.
-It can be written as ${\int T_{\rm CO} dV}$ where $T_{\rm CO}$ is the peak brightness temperature in the CO line and $V$ is the line-width. %PB units for these quantities?
+$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in KKms$^{-1}$.
+It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(k) is the peak brightness temperature in the CO line and $V$ is the line-width in Kms$^{-1}$.
 For a uniform cloud with a radius $R$, the CO luminosity is given by:
@@
 
-Galactic molecular clouds are self-gravitating systems. %PB: ref?
-Thus, using the virial theorem leads to calculating the mass of the cloud: %(PB note: "Virial" is not a name, no capital needed)
+Giant molecular clouds are self-gravitating systems~\citep[e.g.][]{Efstathiou83,Blitz99}.
+Thus, using the virial theorem leads to calculating the mass of the cloud: 
  \begin{equation}
@@
  \end{equation}
- where $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor. %PB: what is \rho here?
- Equation~\ref{equ: vir} shows that the total mass of molecular clouds and the total CO luminosity of a galaxy are directly related~\citep{Young91}.
-% PB: you refer to individual clouds above, then you jump to totals for the galaxy.
-Is this OK to do?
-(what assumption about optical depth is being made?)
+ where $\rho$ is the mass density of the cloud and $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor.
+ Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
+ Since the dependency of $I_{\mathrm CO}$ to optical depth is negligible~\citep{Krumholz09}, total CO luminosity of the galaxies, can be used to measure the total H$_2$ mass of galaxies.
  The relation between CO emission and H$_2$ cloud mass is shown as
-%PB: no paragaph break between the text and the beginning of the equation
 \begin{equation}
@@
 The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
-Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties.
-%PB: need references here
+Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties~\citep{Bolato13}.
 Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.
 
-In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
-One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity.
-In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environment other than the Milky Way.
-However, extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes.
-To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Bolato13}.
-%PB: put these last 2 sentences at end of paragraph
-%PB no new paragraph here
-Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
-Fig.~\ref{fig: mco} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
-The extragalactic molecular clouds are similar to those in the Milky Way. 
-The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
-Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local.
-
 \begin{figure}
-\label{fig: mco}
+\label{fig: mco_ch}
 \centering
-\includegraphics[width=16cm]{../image_intro/mvirial_lco.eps}
+\includegraphics[width=16cm]{../image_intro/mvirial_lco.pdf}
 \caption{Relation between the virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), M31 (triangles), and IC~10 (squares) clouds.
@@
 
-%\subsubsection{Neutral Gas} %PB: paragraph needs a topic sentence
-The density of the atomic hydrogen along the line-of-sight is proportional to the intensity of the 21-cm emission.
-%PB: reverse: intensity of 21cm is proportional to density.
-Is this optically thin/thick ?
-Atomic hydrogen along the line-of-sight contributes to the energy received. %PB does this sentence add something to the previous one?
+In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
+One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity.
+In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environment other than the Milky Way.
+Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
+Fig.~\ref{fig: mco_ch} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
+The extragalactic molecular clouds are similar to those in the Milky Way. 
+The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
+Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local. 
+Extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
+To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.
+
+Atomic gas in galaxies are dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
+Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
+\begin{equation}
+N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
+\end{equation}
+where $T_{\mathrm B}$ is the temperature brightness in K and dV is in Kms$^{-1}$, with the integral over the line profile. 
 These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
 Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.
-%PB: do you want to give the equation for converting between intensity and mass for HI, the way you did for CO?
 
@@
 
-Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical. %PB: why?
+Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of data.
 \cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
@@
 This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
-%PB: join these 2 paragraphs
-One of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary. %PB: why?
+The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary.
 The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
@@
 
-There are many disadvantages of the use of the gas to dust ratio to trace gas in the ISM.
+There are disadvantages of the use of the gas to dust ratio to trace gas in the ISM.
 In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
-\cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains.
-Also, methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps~\citep{Hildebran83}. 
-Using current telescopes, it is difficult to detect dust emission from galaxies at $z > 0.1$~\citep{Ealas12}. %PB: this doesn't seem correct to me - what about submm galaxies?
-In some cases such as Virgo cluster galaxies, dust mass is more tightly correlated with the total gas mass than with the masses of molecular or atomic gas separately~\citep{Corbelli11}.
-%PB: so why is this a problem?
-
-In addition to all the disadvantages mentioned above, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
+\cite{Draine03} pointed out that the former approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
+Measuring the gas to dust ratio in galaxies are not accurate, neither~\citep{Hildebran83}, which means that there are problems in both steps. 
+In addition, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
 To solve this problem, measurement of the continuum emission at far-infrared wavelengths long enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
 The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-%Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems. PB: sentence doesn't add anything
-Unfortunately, at present, given the available devices and technologies, we cannot reach the spatial resolution that is sufficient to detect the gas clouds directly.
-%PB why do we need high spatial resolution?
-Or is it sensitivity that is the problem?
-Therefore, so far this method is the best available solution for measuring the total gas in distant galaxies.
+This method is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.
 
-\subsection{Extinction and Attenuation} %PB: suggest "The ISM and starlight: extinction and attenuation" or something like that, to make clear why we care about this.
+\subsection{The ISM and starlight: extinction and attenuation}
 \label{sec: extinction}
-In this section, dust ``attenuation" and ``extinction" will be introduced and their effects on measuring the SFR will be briefly discussed.
-%PB: explain why we care (because stars and dust are spatially mixed in galaxies, and dust affects emitted SED).
-A  sentence like that is more useful than "in this section we will discuss X".
-More advanced and detailed discussion on this topic can be found in the review by~\citep{Calzetti01}. 
-Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
-The distribution of the dust that lies between a source and the observer is irrelevant to the total extinction value because the source is a background point source.
-%PB: source is *considered* to be a background point source (but what if it isn't a point source?)
-% PB: join paragraphs
+Dust in ISM affects stellar emission by attenuating, scattering or absorption.
 Attenuation refers to the effects of dust with embedded light sources distributed throughout. 
-The dust itself can be clumpy or smooth \citep{Calzetti13}. 
-In this situation the relative location of the dust and light sources affect the net absorbed and scattered light, and that happens because both the light sources and the dust have extended distributions.
-Dust scattering's effect depends on whether the dust is in or out of the line of sight. 
-When the dust is in the line of sight, attenuation will make the emerging light dimmer and the SED will be bluer. %PB: bluer? really?
+The dust itself can be clumpy or smooth. 
+Effect of dust clouds with embedded light sources on distribution of the light is called attenuation.
+The dust cloud could have any distribution and be clumpy or smooth.
+Since both light source and dust have extended distribution, the relative location of the dust and light source affect the net absorbed and scattered light.
+The other parameters that is important on  the scattering and absorption is the relative position of dust and observer.
+When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
 This is the typical situation that occurs when studying galaxies or extended regions within galaxies.
 
-To describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
+Extinction happens when there is a combination of both absorption and scattering of radiation by dust and varies with the wavelength of emission; UV light passes through dust are more affected than the optical light.
+Extinction can be defined as reduction of the original intensity caused by dust:
+\begin{equation}
+\label{equ: extinction}
+{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)exp[-\tau_{\lambda}]
+\end{equation}
+where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction in $\lambda$.
+The extinction depends also on size of grains and extinction cross section.
+For measuring SFR using varies wavebands, 
+decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR. 
+% By converting Equ.~\ref{equ: extinction} to magnetidue system:
+% \begin{equation}
+%      {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda}  = -2.5\log(\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)})
+% \end{equation}
+% and by substituting $\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)}$ with $exp[-\tau_{\lambda}]$, we have:
+% \begin{equation}
+% \begin{split}
+%     {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = -2.5\log(exp[-\tau_{\lambda}]) \\
+%               & = 1.086\tau_{\lambda}
+% \end{split}
+% \end{equation}
+% By defining ${\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = {\mathrm A}_{\lambda}$  extinction in magnitude is A$_{\lambda} = 1.086\tau_{\lambda}$.
+
+% To describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
 % PB: "beam" is jargon, change to something else.
 Simplify this sentence.
-At UV/optical/near-IR wavelengths, the radiative transfer equation is: %PB: why does this eqn only apply at UV/opt/NIR? 
-\begin{equation}
-\frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
-\end{equation}
-where I$_{\nu}$ is the intensity of radiation and $\tau$ is the dust's optical depth.
-$a_{\nu}$ is the dust albedo,  the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
-$\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. %PB: what is \phi? Need to explain at least a little
-Both $a_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
-The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m, is neglected in the equation above.
+% At UV/optical/near-IR wavelengths, the radiative transfer equation is: %PB: why does this eqn only apply at UV/opt/NIR? 
+% \begin{equation}
+% \frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
+% \end{equation}
+% where I$_{\nu}$ is the intensity of radiation and $\tau$ is the dust's optical depth.
+% $a_{\nu}$ is the dust albedo,  the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
+% $\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. %PB: what is \phi? Need to explain at least a little
+% Both $a_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
+% The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m, is neglected in the equation above.
 %PB: why no dust emission at short wavelengths?
 (temperature)
-This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, there will be an underestimation of the star formation rate.
+% This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, there will be an underestimation of the star formation rate.
 %PB: what do you mean by "different emission" in this sentence?
@@
 
-\section{SFR} %PB: suggest "Measuring the star formation rate in galaxies"
+\section{Measuring the star formation rate in galaxies} 
 \label{sec: sfr_intro}
@@
 Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
-Emission from young, massive, type ``O'' or ``B'' stars is normally used as a tracer of the current SFR. %PB: why?
+Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
 One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer.
@@
 \label{sec: imf}
-One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar (or cores) initial mass distribution of a star forming region.
-% PB: leave out the cores part.
-Explain why we care about the mass distribution (because mass determines the important properties of a star like luminosity, lifetime, etc)
+Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
+One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
 Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
-Most problems in modern astrophysical studies regarding the origin and evolution of stars and galaxies can be solved by sampling an IMF ~\citep{Bastin10}.
-%PB: this sentence doesn't really add anything
 \cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
-He introduced a power-law IMF in the form:
+He introduced a power-law IMF $\Phi$  in the form:
 \begin{equation}
@@
 where $M$ is the stellar mass, $\gamma$ is a power index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.
-%PB: what is \Phi ??
-Could write "introduced a power-law IMF $\Phi$ in the form"
 
@@
 Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
-\begin{align}
-\chi (M) = dN/dM = A M^{-1.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
-           = 0.5 A M^{-2.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
-\end{align}
-where $\chi(M)$ is the number of stars between masses $M$ and $M+dM$. %PB: what is $A$? 
+\begin{equation}
+\begin{split}
+    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
+           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
+\end{split}
+\end{equation}
 Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
-Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted to one another by multiplying the calibration constant by 1.6~\citep{Calzetti13}.
-%PB: clarify this: multiply calibration based on Kroupa by 1.6 to get calibration based on Salpeter?
-Or the other way around?
-In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars at all masses.%PB: doesn't quite make sense.
-Does't an overestimate at all masses just mean an incorrect normalization?
+Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
+In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8~M$_\odot$.
 \cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.
-%PB: check that you are using "high-mass" vs "high mass" (same for low) consistently
 
@@
 \small
-\caption{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex versus mass, normalized so that the integral under each curve is unity.
+\caption{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity.
 The mass ranges from 0.1 to 120~M$_\odot$.
-Adopted from~\cite{Baldry03}.} %PB: note that "dex" is astro-jargon.
+Adopted from~\cite{Baldry03}.}
 \end{figure}
 
-Careful measurement of the stellar initial mass function is a key factor in understanding the star formation rate. 
-In distant galaxies, only massive stars can be detected; therefore, the IMF must be measured to include all stellar mass ranges in the SFR calibrations.
-%PB: but how can you measure the IMF if you only detect the massive stars?
+Since in using SFR calibration for different galaxies, we assume the initial mass function is universal, careful measurement of the IMF is a key factor in understanding the star formation rate. 
+In distant galaxies, only massive stars can be detected; therefore, the IMF must be assumed to include all stellar mass ranges in the SFR calibrations. 
 To show the impact of the different stellar IMF assumptions on the SFR calibrations, \cite{Calzetti13} used two different stellar IMFs and derived the SFR calibrations with these new assumptions.
@@
 The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
-These objects mostly have certain ages and usually are referred to as young stellar objects (YSOs). %PB: "mostly have certain ages" ??
+These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
 Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
@@
 \end{equation}
-where N$_{yso}$ is the number of YSOs, $<$M$>$ is the mean mass of YSO which depends on the IMF, 
-$\tau$ is the lifetime of the YSO considering some uncertainly $\tau \sim 2$Myr~\citep{Evans09}, and the SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$. 
-Due to observational difficulties, this method can only be applied to the Solar neighbourhood and the Milky Way.
-%PB: "observational difficulties" is vague.
-What is the issue?
-Actually, it's covered in the following 2 sentences so just drop this one.
+where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
+$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
+$\tau$ is the lifetime of the YSO  $\tau \sim 2$Myr~\citep{Evans09}. 
+Since our current devises cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
 
-In theory, for any system with high enough spatial resolution ($\sim 0.5- 1$ kpc), counting YSOs can be used as a tracer of the star formation.
-%PB: I think you need higher than 0.5 kpc resolution to count YSOs - need to see individual stars, right?
-However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds can not be resolved.
-%PB: explain what the MCs are (& how far away), for the non-astronomer
-Therefore, most studies use the emission from the energetic ``O" and ``B" stars as a tracer of the SFR.
-%PB: O and B is astro-jargon.
-Leave it out or explain what is important about this class of stars?
-Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
-\cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to produce spatially and age-resolved maps of star formation in nearby galaxies. 
-More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}. %PB: I think you should give a one-sentence summary of the method here.
-
+In theory, for any system with high enough spatial resolution, counting YSOs can be used as a tracer of the star formation. 
+However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky way with distance of 0.05 Mpc) can not be resolved.
+Therefore, most studies use the emission from the energetic young stars as a tracer of the SFR. 
+% Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
+% \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to produce spatially and age-resolved maps of star formation in nearby galaxies. 
+% More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}. %PB: I think you should give a one-sentence summary of the method here. 
+%Sr: I think later whether I want to keep this section or not.
 \subsubsection{Unresolved Star Formation Indicators}
@@
 \hline
-L(UV) & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
-L(UV) & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
-L(UV) & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
-L(UV) & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
+L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
+L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
+L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
+L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
 L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
@@
 \begin{tablenotes}
-\item $^1$ Luminosities are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
-\item $^2$ The constant $C$ appears in equation~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$. %PB: why?
+\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
+\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}.
+For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$ to convert luminosity density to luminosity.
+%or flux density?
 \item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Sec.~\ref{sec: imf}), and for the timescale $\tau$.
@@
 The most common single-band tracer of star formation rate is the ultraviolet.
-UV emission is an excellent tracer for the SFR due to the fact that the peak of emission for young  ``O" and ``B" stars is in the UV part of the spectrum.
-%PB only young O and B stars?
-what about old ones?
+As mentioned before, UV emission is an excellent tracer for the SFR.
 Using a spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
 \begin{equation}
-SFR(UV) = 3.0 \times 10^{-47}\lambda L(\lambda)
+SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
 \end{equation}
-where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ in the range of $(912< \lambda < 3000~\AA$), and $L(\lambda)$ is in erg s$^{-1}$.
-%PB: so L is the integrated luminosity from 912-3000A?
-or something else?
+where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ could be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
 As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
-However, the calibration constants' changes for shorter timescales are more significant~\citep{Calzetti13}. 
-The accuracy of the calibration constant is $\pm 15\%$ which can vary as a function of $\lambda$.  %PB: ref?
+The calibration constants' changes for shorter timescales are more significant and 
+the their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
 Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
@@
 The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived from quantum mechanics. 
-To have such results, the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}. %PB: "The assumption is" rather than "To have such results" ?
+The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
 Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emited via Ly${\alpha}$ and longer wavelengths.
@@
 The relation between the SFR, the luminosity of the \halpha emission line and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
-%PB: no new paragraph here
 \begin{align}
@@
 where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
-The constant on the right-hand side of equation~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the interstellar medium.
-%PB: typical in the ISM, or typical in HII regions?
-All SFR indicators that use the ionization of hydrogen to trace the formation of massive stars are sensitive to the effects of dust. %PB think you can drop this sentence.
+The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
 Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
-The effects of dust must be measured and \halpha observations must be corrected or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
-%PB: are you going to explain how correction is done?
+The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
+by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
 
-Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. %PB: explain what a forbidden line is..
+Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
 Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
-As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. %PB: are you sure about the explanation in the 2 prev sentences? Please check.
+As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
 \cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
@@
 \end{equation}  
-where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\halpha) is in erg~s$^{-1}$. %PB: do you mean  L([O\ II]) instead of L(\halpha)?
-Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high redshift galaxies.
+where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
+Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
 In these galaxies, the \halpha emission line is redshifted out of the optical band; as a consequence, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is really useful~\citep{Kennicutt98b}.
@@
 Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) or a local indicator.
-That is because the global case includes the Hubble time integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
-%PB: "Hubble time" is astro-jargon..
-Table~\ref{table2} shows the constant $C$ from equation~\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities, for local (spatial scale $\sim500$~pc for 24~$\mu$m and $\lesssim 1$ kpc for 70~$\mu$m) and global cases.
+That is because the global case includes the integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
+Table~\ref{table2} shows the constant $C$ from Equ.\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities, for local (spatial scale $\sim500$~pc for 24~$\mu$m and $\lesssim 1$ kpc for 70~$\mu$m) and global cases.
 
@@
 \hline\hline
-Luminosity$^1$ & $C$ & Assumptions & references\\ %PB: please check the edits I made here.
+Luminosity$^1$ & $C$ & Assumptions & references\\ 
 \hline
-L(24)$^{0.885}_{local}$ & $1.31 \times 10^{-38}$ &$1.10\times 10^{40} \le L(24) \le 3.10\times 10^{44}$& Calzetti et al. (2007)  \\ %PB: use \cite
-L(24)$_{global}$ & $2.04 \times 10^{-43}$ &$ 4.10\times 10^{42} \le L(24)  \le 5.10\times 10^{43}$& Calzetti et al. (2007) \\
+L(24)$^{0.885}_{local}$ & $1.31 \times 10^{-38}$ &$1.10\times 10^{40} \le L(24) \le 3.10\times 10^{44}$&  \cite{Calzetti07}   \\ 
+L(24)$_{global}$ & $2.04 \times 10^{-43}$ &$ 4.10\times 10^{42} \le L(24)  \le 5.10\times 10^{43}$& \cite{Calzetti07} \\
 L(70)$_{local}$ & $9.4 \times 10^{-44} $ &$5.10\times 10^{40} \le  L(70) \le 5.10\times 10^{43}$& \cite{Li12} \\
@@
 \begin{tablenotes}
-\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L($\lambda$) in erg s$^{-1}$ %PB: this doesn't make sense: L = \lambda L ?? Or is this missing a _{\lambda} or _{\nu} ?
+\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda$} in erg s$^{-1}$ 
 \end{tablenotes}
@@
 The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically derived~\citep{Kennicutt12}.
-%There are studies that use a higher order polynomial relation to combine luminosities~\citep[e.g.,][]{Buat05}; however, this discussion is out of the scope of this paper.
 
-Integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator. 
-As mentioned earlier, dust absorbs stellar radiation at all wavelengths; however, here we are only interested in radiation emitted from UV luminous stars.
-% PB: not obvious how this sentence relates to ones before and after it
-Since there is no one-to-one mapping between IR and UV emission~\citep{Calzetti13}, it is better to use the TIR emission as a tracer of the SFR instead of single-band IR emission.
+The emission from dust heated by young stars changes by amount of high energy photon emitted to dust and by properties of dust such as grain size.
+Therefore, calibration of SFR varies with each single-band IR emission.
+Assuming that dust heating is dominated by emission from young stars stellar, integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
 
-\cite{Draine07} modelled observations from the \Spitzer Space Telescope and found a calibration for TIR luminosity from spatially-resolved infrared photometry instead of the integrated infrared SED.
-%PB: please check that edits OK.
-Also, this sentence doesn't flow well from the previous text.
-\cite{Boquien10} tested this calibration and found a modified version to estimate the total infrared luminosity: 
+TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
+\cite{Boquien10} modified calibration of the total infrared luminosity as: 
 \begin{equation}
@@
 \end{equation}
-where $L = \nu L_{\nu}$ and $L_{\nu}$ is the luminosity  in erg~s$^{-1}$ at frequency $\nu$. 
-\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=100$~Myr is:
+where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
+\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
 \begin{equation}
@@
 where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.
-To do this calculation, it is assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{\mathrm{star}}({\rm bol})=L(\rm TIR)$.
-%PB: is this a reasonable assumption.
 
-As mentioned before emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}. %PB: give section ref instead of "before"
-Most studies used infrared emission, which contains PAHs emission, to calibrate SFR~\citep[e.g.][]{Calzetti07}.
-%PB: are you saying that previous studies use broad bands which contain PAHs, but here you're dealing with the PAH features only?
+In Sec~\ref{sec: overview} we mentioned that emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
+Most studies used broad bands IR emission, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using the PAH features only.
 \cite{Shipley16} calibrated SFR using observation from 105 star-forming galaxies with $z < 0.4$ as:
@@
 \hline
-6.2 + 7.7 + 11.3 & -42.56 $\pm$ 0.03 & 1.00 $\pm$ 0.03 \\ %PB: change from x $\pm$ y to $x\pm y$
-6.2 & -40.06 $\pm$ 0.09 & 0.96 $\pm$ 0.04 \\ 
-7.7 & -42.38 $\pm$ 0.06 & 1.00 $\pm$ 0.03 \\ 
-11.3 & -44.14 $\pm$ 0.08 & 1.06 $\pm$ 0.03 \\ 
-6.2 + 7.7 & -42.05 $\pm$ 0.04 & 0.99 $\pm$ 0.03 \\ 
-6.2 + 11.3 & -42.52 $\pm$ 0.05 & 1.01 $\pm$ 0.03 \\ 
-7.7 + 11.3 & -42.85 $\pm$ 0.04 & 1.01 $\pm$ 0.03 \\ 
+6.2 + 7.7 + 11.3 & $ -42.56 \pm 0.03 $ &  1.00 \pm 0.03 \\ 
+6.2 & $ -40.06 \pm 0.09 $ &  0.96 \pm 0.04 \\ 
+7.7 & $ -42.38 \pm 0.06 $ &  1.00 \pm 0.03 \\ 
+11.3 & $ -44.14 \pm 0.08 $ &  1.06 \pm 0.03 \\ 
+6.2 + 7.7 & $ -42.05 \pm 0.04 $ &  0.99 \pm 0.03 \\ 
+6.2 + 11.3 & $ -42.52 \pm 0.05 $ &  1.01 \pm 0.03 \\ 
+7.7 + 11.3 & $ -42.85 \pm 0.04 $ &  1.01 \pm 0.03 \\ 
 \hline
@@
 The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used.
-This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations. The calibration is: %PB: need ref
+This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
 \begin{equation}
@@
 
+The IR emission in the other band can be used for correcting dust effect on UV or \halpha~emission (see Tab.~\ref{table3}). 
+The corrected emission then can be used as a SFR tracer.
+These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
+Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.
+
 \begin{table}
@@
 \hline
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& Hao et al. (2011)\\ % use \cite
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& Hao et al. (2011)\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& Hao et al. (2011)\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& Hao et al. (2011)\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& Kennicutt et al. (2009)\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& Kennicutt et al. (2009)\\
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& \cite{Hao11}\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& \cite{Hao11}\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& \cite{Hao11}\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& \cite{Kennicutt09}\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& \cite{Kennicutt09}\\
 \hline
@@
 \begin{tablenotes}
-\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L($\lambda$) in erg~s$^{-1}$ %PB see comments above on this.
+\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L_{$\lambda$} in erg~s$^{-1}$ 
 \end{tablenotes}
@@
 
-Other combinations of luminosities that are used as tracers of the SFR are listed in Table~\ref{table3}.
-%PB: are these corrected values used with the SFR calibrations in table 1?
-Or do they need different calibrations?
-These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
-Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.
-
 %PB: would it make sense to put this paragraph closer to where you first discuss Table 1?
+Sahar: I thought because IMF affect all of the calibration it would be better to have at the end of the section.
 As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
 From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
-This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
-% PB: "more strongly" than what?
-Furthermore, reaching an asymptotic value takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). % PB: "asymptotic value" of what?
+This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than the other part of spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
+Furthermore, reaching an asymptotic value of ionizing photons takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
 Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR the calibration constants are fairly close to each other.
-On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a $10\%$ difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
+On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a 10 per cent difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
 As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.
 
-% PB: SFR section is pretty long, might help to have a short summary here, perhaps when you would use different indicators.
-Expanding the "Other combinations" paragraph a bit would be a way to do this.
+Our understanding of star formation in extragalactic systems depends on the light emitted by those systems.
+While emission from massive and young stars is dominating light of the system, mass of low-mass stars dominates the mass of regions (see Sec.~\ref{sec: imf}).
+Therefore, SFRs are calibrate based on dominant light of the systems and low-mass stars are accounted using initial mass function.
+Emission from star forming regions should be corrected before it can be used in calibrations.
+In their way to the Earth this emission passes through dust and gas clouds which causes extinction or attenuation (See ref.~\ref{sec: extinction}).
+On the other hand, evolved stars emit their light in the whole spectrum as well as UV. 
+Therefore, even though it might have insignificant part in UV emission from galaxies, a correction for emission from evolved stars should be considered~\citep{Leroy08}.
+After measuring the corrected luminosities for star forming regions in galaxies (global or local), using proper calibrations can give the best estimation of SFR in galaxies.
 
@@
 One of the most fundamental physical parameters which describes the present state of a galaxy is its stellar mass. 
-Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and all morphologies~\citep{Scodeggio02}. 
-In order to determine the stellar populations of spiral galaxies, the mean stellar mass density of a galaxy may be a more basic parameter than the total stellar mass~\citep{Bell00}. 
-\cite{Kauffmann03} tested that on more than 100,000 galaxies observed by the Sloan Digital Sky Survey~\citep[SDSS;][]{York00}. %PB: what is "that"?
-They also showed that these results applied to all morphological types. %PB: what are "these results" ?
-
+Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and allmorphologies~\citep{Scodeggio02}. 
 Measuring the mass of a stellar population is indirect and subject to significant uncertainties. 
 In principle there are two ways to measure stellar mass in galaxies. 
-The first is measuring the dynamical mass of a galaxy using kinematics~\citep{Cappellari06} or lensing~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
-%PB: "kinematics" and "lensing" are astro-jargon: please explain a bit more
-This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies~\citep{Zaritsky94}, and can easily cause uncertainties as high as the order of the measurement.
-%PB: but is it successful in measuring the stellar mass?
+The first is measuring the dynamical mass of a galaxy using kinematics (the mostion of stars)~\citep{Cappellari06} or lensing (bending light as the light pass near a galaxy)~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
 
 The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution.
-%PB: need a one-sentence description of what these models do.
-This method has uncertainties too, and one must also model the uncertainties. %PB: sentence not useful.
-Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][]{Dalcanton12}, and star formation histories.
+Stellar population models predict the expected SEDs for stellar populations based on parameters of regions such as star formation history, metallicity, and IMF
+Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][ans references therein]{Dalcanton12}, and star formation histories.
 
-%PB: this paragraph was very difficult to understand and I did a lot of rewriting. Please check.
-In order to translate between photometry and dynamics the stellar mass-to-light ratio ($M/L$) is needed. %PB: is this the first method or the second one? It's not really about dynamics.
+In order to translate between photometry and stellar mass the stellar mass-to-light ratio ($M/L$) is needed.
 The use of $M/L$ is one way to measure stellar mass surface density. It is an indirect method and has high uncertainties in specific cases, but can help to study the stellar mass in large samples. 
@@
 
-Having two independent methods to measure stellar mass helps to check whether there are any systematic differences. 
-Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. %PB: ref?
-Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 per cent, so one should be careful to model subtleties~\citep{McLaughlin05}.
+Comparing results from independent methods to measure stellar mass helps to determine whether there are any systematic differences.
+Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few tens per cent~\citep{McLaughlin05}.
+Therefore, to model subtleties, the advantages and disadvantages of using each method should be carefully considered.
 
-\subsection{Dynamical Mass} %PB: suggest "galaxy masses from dynamics"
-% PB: should following paragraph go after the second paragraph?
-The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi lines. 
-Thanks to the current generation of detectors, it is possible to obtain  very high-resolution spectra in the \halpha and CO lines  over most of the optical disks of galaxies.
-% and cover most regions in the sky.
-PB: not sure about "most regions of sky"
-Integrated line widths only yield an estimate of total mass within some (uncertain) isophotal radius.
+\subsection{galaxy masses from dynamics}
 
-Resolved rotation curves produced from \halpha, \hi and CO lines are proportional to optical emission lines within the optical disk of galaxies,~\citep{Courteau13} which helps us to measure the rotational curves.
-%PB: don't get the purpose of this sentence
-The simplest way to estimate the mass of a galaxy is assuming that the physics of the galaxy is simple Newtonian physics.
-%PB should be clear that this is what nearly everyone does (almost no one assumes that physics isn't Newtonian)
+The simplest and the most common way to estimate the mass of a galaxy is assuming that the physics of the galaxy is simple Newtonian physics.
 Therefore, the circular velocity $v{\rm circ}(r)$ of an orbit within a spherical system of gravitational potential $\phi$ and mass $M$ is given by:
@@
 where where $G$ is the gravitational constant and $M(r)$ is the mass within a sphere of radius $r$. 
-For a flattened disk, which is the case in most spiral galaxies, the right hand side of equation~\ref{eq: simpmass} must be replaced by the more exact expression derived by~\cite{Freeman70}. 
+For a flattened disk, which is the case in most spiral galaxies, the right hand side of Equ.\ref{eq: simpmass} must be replaced by the more exact expression derived by~\cite{Freeman70}. 
 For the case of no dark matter or bulge, \cite{Freeman70} showed that the rotation curve of a self-gravitating disk is:
@@
 \end{equation}
-where $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, $4y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kinds  modified Bessel functions.
-%PB what is y?
-Also need to define scale length.
+where $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, where ratio of the intensity of disk to bulge is $e$ ($\sim$2.71).  
+$y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kind modified Bessel functions.
+
+The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi~lines. 
+Integrated line widths only yield an estimate of total mass within some (uncertain) isophotal radius.
+Thanks to the current generation of detectors, it is possible to obtain very high-resolution spectra in the \halpha and CO lines over most of the optical disks of galaxies.
+The higher resolution data
 
@@
 For more accurate results, one should consider non-circular rotational velocities and the fact that galaxies contain millions of stars plus interstellar objects; therefore simple two-object Newtonian physics is not the case here.
-%There are many different profiles to fit the rotation curve for galaxies. PB: not useful.
 A detailed review of dynamical masses of galaxies can be found in \citet{Courteau13}.
 
-\subsection{Stellar Population Method} %PB: suggest  "galaxy masses from stellar population modelling"
+\subsection{Galaxy masses from stellar population modelling}
+
 Galaxies can be observed because of their stellar emission; stars radiate the energy produced from nuclear reactions in their cores. 
@@
 Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distributions of galaxies. 
-However, some fraction of the mass of galaxies consists of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants. %PB: so what do we do about this?
+However, some fraction of the mass of galaxies consists of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants and should be considered in models.
+Stellar population synthesis models are used to predict the SED of a stellar population using many physical parameters. 
+These parameters, which control the time evolution of the stellar population such as age, $t$, of the population, measured in years, also referred to as the time passed since the star formation began, IMF, and metallicity~\citep{Courteau13}.
 
-Stellar population synthesis models are used to predict the SED of a stellar population using many physical parameters. 
-These parameters, which control the time evolution of the stellar population, are:
-the age, $t$, of the population, measured in years, also referred to as the time passed since the star formation began;
-the star formation history (SFH), often parametrized with SFR $\propto e^{-1/\tau}$; the IMF; the metallicity; and the chemical composition ratios, usually measured relative to values measured in the Sun.
-Stellar evolutionary tracks, the stellar spectral libraries, and the parametrization for mass-loss which affects several late stages of evolution are necessary for stars placing at specific evolutionary phases~\citep{Courteau13}.
-%PB: this sentence has a lot of astro-jargon
-
-%PB: please think about how info in following few paragraphs should logically go together into paragraphs.
-%\subsubsection{Calibration light of stars} 
 The basic idea behind finding a suitable calibration between flux/luminosity of the stars in different wavelengths and stellar mass is that one can use the SFHs recovered from synthesizing the stellar optical colour-magnitude diagrams in different regions of a galaxy.
-The calculated stellar mass can be used to calibrate the fluxes from the stars as the easily measurable parameters of stars. %PB: don't understand what "as the easily.." means here.
-Using NIR bands, different groups tried to make a map of stellar mass distribution within galaxies~\citep[e.g.,][]{Elmgreen84}.
-Using $B-V$ colours~\citep{Bell01} and {\em Spitzer} 3.6- and 4.5-$\mu$m, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
-%PB: unclear how this  sentence relates to other text.
-
-\cite{Zibetti08} suggested that to reach the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel basis~\citep{Conti03}. 
-They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density. %PB: join paragraphs. 
-To do so the surface density of stellar mass is derived by 
+The calculated stellar mass in nearby galaxies can be used to calibrate the fluxes from the stars in other galaxies.
+\cite{Zibetti09} suggested that to reach the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel basis. 
+They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density.
+To do so the surface density of stellar mass at each position is derived by 
 \begin{equation}
 \label{equ: massphot}
-\Sigma M_\star (\alpha, \delta) = \Sigma \lambda(\alpha, \delta) \gamma_{\lambda}(\alpha, \delta)
+\Sigma_{{\mathrm M_\star}} (\alpha, \delta) = \Sigma_{\lambda}(\alpha, \delta) \gamma_{\lambda}(\alpha, \delta)
 \end{equation}
-where $\Sigma \lambda(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L at an effective wavelength $\lambda$.
-% PB what are \alpha, \delta ?
-In equation~\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy. 
-Equation~\ref{equ: massphot} can be used for each position in a galaxy.
+where $\alpha$ and $\delta$ are position, right ascension and declination, respectively.
+$\Sigma_{{\mathrm M_\star}} (\alpha, \delta)$ is the stellar surface density.
+$\Sigma_{\lambda}(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L at an effective wavelength $\lambda$.
+In Equ.\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy.
 
-\cite{Eskew12} related easily observable quantities to the stellar mass. 
-They used 3.6 and 4.5$\mu$m fluxes for calibration of the stellar mass, because these two bandpasses are almost insensitive to the emission from young stellar population or to dust absorption and emission.
-Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} telescopes, a large amount of data in these bands from many regions in the sky is available, which helps thave a more accurate calibration.
+Peak of emission from evolved stars are in NIR part of spectrum.
+Therefore, many studies tried to make a map of stellar mass distribution using this bandpass within galaxies~\citep[e.g.,][]{Elmgreen84}.
+Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps thave a more accurate calibration.
+Fluxes from 3.6 and 4.5$\mu$m are suitable for calibration of the stellar mass, due to fact these two band-passes not only trace evolved stellar population but also they are almost insensitive to the emission from young stellar population or to dust absorption and emission.
+\cite{Zhu10} used the Sloan Digital Sky Survey~\citep[SDSS][]{York00} and the \Spitzer Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find calibration between galaxy luminosity and stellar mass.
+Using the M/L of galaxies, they found correlations between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulated these correlations as:
+\begin{align}
+\label{equ: zhu1}
+\log M_{\star} = -1.60  + 1.12  \log \nu L_{\nu}[K_s]\\
+\log M_{\star} = -0.79 + 1.19 \log \nu L_{\nu}[3.6\mu \rm m]\\
+\label{equ: zhu3}
+\log M_{\star} = -0.25 + 1.15\log \nu L_{\nu}[4.5\mu \rm m] 
+\end{align}
+where M$_{\star}$ is the stellar mass in solar masses and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg~s$^{-1}$ at the specified wavelength.
+
 \cite{Eskew12} tested the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and found an empirical relation between mass of the stars and the luminosities of stars as:
@@
 \label{equ:eskew}
-M = 31.84 \times 10^{5.65} L_{3.6}^{2.85} L_{4.5}^{-1.85}
+  M_{\star} = 31.84 \times 10^{5.65} L_{3.6}^{2.85} L_{4.5}^{-1.85}
+ %\log M_{\star} = 5.6 +2.85\log (F_{3.6})-1.85 \log (F_{4.5})+2\log \left(\frac{D}{0.05}\right)
 \end{equation}
-where M$_{\star}$ is the stellar mass and $L = \nu L_{\nu}[\lambda]$ is luminosity in erg~s$^{-1}$/$\AA$. %PB: units of stellar mass?
+where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$/$\AA$.
+Equ.~\ref{equ: zhu1}--~\ref{equ: zhu3} have been derived from a large sample of galaxies, and were tested on different type of regions and galaxies. 
+on the other hand,~\cite{Eskew12} mentioned that since their calibration is based on data from Magellanic clouds this,
+measuring the stellar mass from Equ.~\ref{equ:eskew} might break down for highly star-forming regions; moreover, this equation has not tested on regions with different metallicity. 
+In more recent work,~\cite{Laura16} measured stellar mass for group of galaxies with ($z < 0.035$) and  showed they are tightly correlate with stellar mass measured from other calibrations.
 
-\cite{Zhu10} used the SDSS and the {\em Spitzer} Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find another calibration between galaxy luminosity and stellar mass. 
-Using the $M/L$ of galaxies, they found correlations between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulated these correlations as:
-\begin{align}
-\label{equ: zhu1}
-\log M_{\star} = (-1.60 ) + (1.12)\times \log \nu L_{\nu}[K_s]\\
-\log M_{\star} = (-0.79) + (1.19)\times \log \nu L_{\nu}[3.6\mu \rm m]\\
-\label{equ: zhu3}
-\log M_{\star} = (-0.25) + (1.15)\times \log \nu L_{\nu}[4.5\mu \rm m] 
-\end{align}
-where M$_{\star}$ is the stellar mass and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg~s$^{-1}$ at the specified wavelength. 
-Measuring the stellar mass from equation~\ref{equ:eskew} is limited to nearby galaxies, and might break down for highly star-forming regions; moreover, this equation has not tested on regions with different metallicity.
-Thus there is no information on the effects of variation in  metallicity~\citep{Eskew12}. 
-On the other hand equations~\ref{equ: zhu1}--~\ref{equ: zhu3} have been derived from a large sample of galaxies, and were tested on different type of regions and galaxies. 
-They can be used for more distant galaxies as well as nearby galaxies~\citep{Zhu10}. %PB: why is Zhu et al good for distant galaxies but Eskew is not?
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 A complete picture of how galaxies are formed and evolve is tied to unfolding the mystery of the formation of stars.
- Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas, the mass of sounding stars and other physical properties of galaxies.
-%PB "sounding stars" ?
-"other physical properties" is vague - either be specific or delete it.
- For decades, observational, theoretical and numerical studies have investigated star formation; nevertheless, their results have never been precise.
-%PB: not really clear what you mean by "precise" here.
+ Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas and the mass of stars in galaxies.
+ For decades, observational, theoretical and numerical studies have investigated star formation; nevertheless, their results are contrary.
  Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
@@
 Then we study the grouped properties of the classified galaxies.
-%For each chapter, we also describe the methodology and data used in that chapter. %PB: not needed.
 We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}

### 2016-07-13 version0.0/paper1.tex
adding prelude to into. section
finishing intro0.0
finishing edits on intro

@@
 \chapter[Star formation laws in M31]{Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}
+\label{ch: paper1}
 
@@
 with the {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes. 
-Observations with the Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8~\um); IRAC observations of M31 were obtained by \citet{Barmby06}, covering a region $3\degr.7 \times 1\degr.6$.
-The Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 70, and 160 \um and covered a region $\sim 3\degr \times 1\degr$ \citep{Gordon06}.
+Observations with the Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8~\um); IRAC observations of M31 were obtained by \citet{Barmby06}, covering a region 3\degr.7$\times $1\degr.6.
+The Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 70, and 160 \um and covered a region $\sim 3$\degr $\times$ 1\degr \citep{Gordon06}.
 {\em Herschel} observations of M31 were made with with PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10}  at 100 and 160~\um and SPIRE  \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10}
-at 250, 350, and 500~\um, covering a region  $\sim 5\degr.5 \times 2\degr.5$ \citep{Fritz12}.
+at 250, 350, and 500~\um, covering a region  $\sim$5\degr.5 $\times$ 2\degr.5~\citep{Fritz12}.
 The IRAC 8, MIPS 24, MIPS 70, and PACS 160 images were used to calculate M31's total infrared emission. 
@@
 Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium.
-This map covers a $2\degr \times 0\degr.5$ region with an angular resolution of $23\arcsec$ and has the smallest coverage of the galaxy among the maps we used in this paper.
+This map covers a 2\degr $\times$ 0\degr.5 region with an angular resolution of 23\arcsec and has the smallest coverage of the galaxy among the maps we used in this paper.
 In this study, we also used a 21-cm emission map of the atomic gas (H\,{\sc I}) in M31 from \citet{Chemin09}.
-This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a $5\degr.1 \times 1\degr.5$ region with an angular resolution of $60\arcsec \times 90\arcsec$.
+This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.
 
@@
 This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}.
-The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the \citet{Kroupa03} IMF as:
+The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
 \begin{equation}
@@
 The number of points among the three columns is different due to the different angular resolution of the H\,{\sc I} and H$_2$ maps.
-Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\sc I} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of $60\arcsec \times 90\arcsec$).
+Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\sc I} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of 60\arcsec $\times$ 90\arcsec).
 Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
@@
 Obtaining images with higher resolution and maps with better coverage of this galaxy will enable continuation of these studies in finer detail.
+
+\addcontentsline{toc}{section}{Bibliography}
+\bibliographystyle{apj.bst}
+\bibliography{ref_paper1.bib}

### 2016-07-14 version0.0/intro0.0.tex
Update intro0.0.tex
edits to prelude. One question about relation between SFR and SFH.

@@
 Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
-a plot of brightness/flux density of galaxies as a function of wavelengths, which is called spectral energy distribution (SED), is a useful tool to have a intuition about galaxies. 
-Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
-We cannot detect any contribution from planets and black holes, the ones without accretion disc, to SEDs due to their low intensity compared to these other components.
+a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
+Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
+We cannot detect any contribution from planets or non-accreting black holes to SEDs, due to their low intensity compared to these other components.
 Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.
@@
 done
-Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
-Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM).
+Among observable objects in galaxies, gas has a crucial role in the formation and evolution of galaxies.
+Gas and dust in galaxies can be found in the space between stars and are together called the interstellar medium (ISM).
 The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
@@
 The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
-Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.
+Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution, in that stars release their material into the ISM when they reach the end of their evolution.
 
-In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
-The denser regions within GMCs collapse under their own gravity, self-gravity, and creates clumps.
+In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$~M$_{\odot})$ in the ISM due to gravitational instabilities. 
+The denser regions within GMCs collapse under their own gravity (self-gravity) and create clumps.
 Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
 Then these clumps continue to become denser and transfer to protostars. 
-Since the protostars have higher mass than their surrounding, more gas from GMCs add to protostars.
-This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).
+Since the protostars have higher mass than their surroundings, more gas from GMCs is added to protostars.
+This procedure continues until hydrogen burning starts in the centre of protostars (see~\cite{McKee07} for more details).
 
@@
 Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
-Amount of metals in stars affect their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
-For example, low metallicity stars tend to be have lower mass loss by stellar wind than that with higher metallicity.
-Since there is lower amount of mass loss in low metallicity stars, hence no loosing angular momentum because of wind, massive low metallicity stars rotate faster.
-Being more massive at the end of evolutionary track, makes massive low metallicity stars lower chance to explode (become a supernova).
+The amount of metals in stars affects their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
+For example, low metallicity stars tend to have lower mass loss by stellar winds than those with higher metallicity.
+Since there is less mass loss in low metallicity stars, hence no loss of angular momentum because of winds, massive low metallicity stars rotate faster.
+Being more massive at the end of their evolutionary track gives massive low metallicity stars a lower chance to explode and become a supernova.
 
@@
 Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
-The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission.
+The general shape of SEDs mirrors the morphological types of galaxies: starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission.
 Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.
@@
  %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
-The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
-A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
+The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
+A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
 Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
@@
 It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
-Some of the physical properties of galaxies should be assumed as an input data to find best SED, and others will be derived from SED results~\citep[See][for more detail]{Walcher08}.
-For example, the Best fitted SED has information regarding star formation history and stellar mass to light ratio.
-By integrating star formation history over specific time scale, SFR can be derived. 
-knowing the stellar mass to light ratio, one can used observed luminosity to calculate stellar mass in galaxies.
+Some of the physical properties of galaxies must be assumed as an input data to find best SED, and others are derived from SED results~\citep[See][for more detail]{Walcher08}.
+For example, the best-fit SED has information regarding a galaxy's star formation history and stellar mass to light ratio.
+By integrating the star formation history over a specific time scale, the SFR can be derived. %PB: backwards? integrate SFR to get SFH?
+Knowing the stellar mass to light ratio, one can use the observed luminosity to calculate stellar mass in galaxies.
 
-Formation of stars in galaxies depends on many parameters, gas, stellar mass, metallicity, dust, galaxy's morphology and location of the star forming region inside the galaxy.
+The formation of stars in galaxies depends on many parameters, including gas, stellar mass, metallicity, dust, the galaxy's morphology and the location of the star forming region inside the galaxy.
 In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.

### 2016-07-14 version0.0/intro0.0.tex
Update intro0.0.tex
edits to ISM section

@@
 The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
-Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud medium.
-Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
+Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or a hot intercloud medium.
+Dust mostly contains silicate and graphite grains, and can be seen in dark clouds or galactic cirrus. %PB: please check changes to this sentence
 Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
@@
 Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
-Density in the molecular clouds is not uniform; There are dense and colds clumps inside these clouds.
-Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
+Density in the molecular clouds is not uniform; there are dense and colds clumps inside these clouds.
+Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars.
 However, H$_2$ molecules, the main component of molecular clouds, have no permanent electric dipole moment which makes them difficult to detect.
@@
 Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
-In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds.
+In fact, most of our knowledge from molecular clouds comes from observing the line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds.
 %PB \bf needs clarification
-Other heavier molecules have emission lines which are also detectable in the spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.
-their mass (see Sec.~\ref{sec: ismmap} for more details).
+Other heavier molecules have emission lines which are also detectable in the spectra of clouds (especially Galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds e.g.\ their mass (see Sec.~\ref{sec: ismmap} for more details).
 
@@
 Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
-However, the difference between these two states is very small and it takes millions of years before the transition happens.
-The large amount of hydrogen atoms compensates for the rareness of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
+However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
+The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
 Observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.
@@
 \hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
-High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
+High energy UV photons emitted by massive newborn stars have sufficient energy to ionize their surrounding gas, and
 ~\halpha emission is the main observational feature of \hii~regions.
 The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
-Forbidden lines are not ``forbidden", they only have much lower probability of occurring than the ``allowed" ones.
-Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
-Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
+Forbidden lines are not strictly ``forbidden"; they only have much lower probability of occurring than the ``allowed" ones.
+Optically bright \halpha emission from \hii~regions correlates with the number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
+Studying \hii~regions provides valuable insight into star forming regions by providing information such as the star formation rate, the initial mass function (IMF) of stars, and the distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
 
@@
 In spiral galaxies dust grains are located in cold regions ($\sim$30~K) and have a power-law distribution of size.
-Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
+The source of dust thermal emission is heating from stars and the shape of the continuum depends on size of the grain.
 Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate mass young stars~\cite{Peeters04}. 
-Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
-Dust is the main source of extinction and reddening of starlight (See Sec.\ref{sec: extinction} for more information).
+Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in the far-infrared~\citep[e.g.][]{Calapa14, lu14}
+Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).
 
@@
 Neutral atomic and molecular hydrogen are the most common components of the ISM. 
-Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly helium, which cannot be observed directly.
+Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements (mostly helium), which cannot be observed directly.
 Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.
@@
 This method can be promising if observational data with resolved molecular and atomic clouds are available.
-However, given the state of the current technology, having the high resolution images of clouds for most of galaxies are not possible. 
+However, given the state of current technology, having high resolution images of clouds for most galaxies is not possible. 
 This problem shows itself for distant galaxies more than nearby galaxies. 
-As a result, using images of molecular and atomic cloud to measure surface density of gas in ISM is limited to telescopes resolution.
+As a result, using images of molecular and atomic clouds to measure surface density of gas in ISM is limited by telescopes' resolution.
 
@@
 where $D$ is the distance to the cloud and 
-$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in KKms$^{-1}$.
-It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(k) is the peak brightness temperature in the CO line and $V$ is the line-width in Kms$^{-1}$.
+$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
+It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
 For a uniform cloud with a radius $R$, the CO luminosity is given by:
@@
  Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
- Since the dependency of $I_{\mathrm CO}$ to optical depth is negligible~\citep{Krumholz09}, total CO luminosity of the galaxies, can be used to measure the total H$_2$ mass of galaxies.
- The relation between CO emission and H$_2$ cloud mass is shown as
+ Since the dependency of $I_{\mathrm CO}$ on optical depth is negligible~\citep{Krumholz09}, the total CO luminosity of a galaxy can be used to measure its total H$_2$ mass.
+ The relation between CO emission and H$_2$ cloud mass is shown as:
 \begin{equation}
@@
 One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity.
-In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environment other than the Milky Way.
+In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environments other than the Milky Way.
 Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
@@
 Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local. 
-Extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
-To measure the clouds in distant galaxies, spatial resolution of maps must be better than 40 pc which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.
+Extragalactic investigations have been limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
+To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40 pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.
 
-Atomic gas in galaxies are dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
+Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
 Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
@@
 \end{equation}
-where $T_{\mathrm B}$ is the temperature brightness in K and dV is in Kms$^{-1}$, with the integral over the line profile. 
+where $T_{\mathrm B}$ is the temperature brightness in K and dV is in km~s$^{-1}$, with the integral over the line profile. 
 These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
@@
 This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
-The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary.
+The observed FIR flux has almost no dependence on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary.
 The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
@@
 The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-This method is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.
+This method is the best alternative for measuring the total gas in galaxies where there are no observations of CO or \hi~emission.
 
@@
 The dust itself can be clumpy or smooth. 
-Effect of dust clouds with embedded light sources on distribution of the light is called attenuation.
+The effect of dust clouds with embedded light sources on the distribution of the light is called attenuation.
 The dust cloud could have any distribution and be clumpy or smooth.
-Since both light source and dust have extended distribution, the relative location of the dust and light source affect the net absorbed and scattered light.
-The other parameters that is important on  the scattering and absorption is the relative position of dust and observer.
+Since both light sources and dust have an extended distribution, the relative locations of the dust and light sources affect the net absorbed and scattered light.
+The other parameter that is important for the scattering and absorption is the relative position of dust and observer.
 When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
@@
 
-Extinction happens when there is a combination of both absorption and scattering of radiation by dust and varies with the wavelength of emission; UV light passes through dust are more affected than the optical light.
-Extinction can be defined as reduction of the original intensity caused by dust:
+Extinction happens when there is a combination of both absorption and scattering of radiation by dust and varies with the wavelength of emission; UV light passing through dust is more affected than visible light.
+Extinction can be defined as a reduction of the original intensity caused by dust:
 \begin{equation}
@@
 \end{equation}
-where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction in $\lambda$.
-The extinction depends also on size of grains and extinction cross section.
-For measuring SFR using varies wavebands, 
-decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR. 
+where I$(\lambda)$ is the observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is the intensity of light before passing through dust, and $\tau_{\lambda}$ is the otpical depth at wavelength $\lambda$.
+The extinction depends also on the size of grains and their extinction cross section.
+For measuring SFR using various wavebands, 
+the decrease in the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR. 
 % By converting Equ.~\ref{equ: extinction} to magnetidue system:

### 2016-07-14 version0.0/intro0.0.tex
Update intro0.0.tex
edits to SFR section

@@
 
-In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission.
+In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using  Bremsstrahlung emission.
 Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
 Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
-Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
+The peak of emission of young, hot, and massive stars is at UV wavelengths, which makes them an ideal tracer of the current SFR.
 One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer.
-By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
+By knowing the IMF, the number of massive stars can be used to extrapolate to the total number of stars formed in a given star-forming region.
 To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
@@
 Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
-One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
+One of the most fundamental and difficult questions that a complete theory of star formation must answer is ``what is the stellar initial mass distribution?'' of a star forming region.
 Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
@@
 
-In the late 70s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}.
+In the late 70s, it was recognised that the assumption of a single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
 Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
@@
 Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
-Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
+Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, can be converted from the Kroupa IMF  to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
 In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8~M$_\odot$.
-\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.
+\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins, especially at the high-mass end.
 
@@
 The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
-These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
+These objects are mostly a few million years old and  are usually referred to as young stellar objects (YSOs). 
 Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
@@
 where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
-$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
+$<$M$>$ is the mean mass of YSO which depends on the IMF; considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
 $\tau$ is the lifetime of the YSO  $\tau \sim 2$Myr~\citep{Evans09}. 
-Since our current devises cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
+Since our current devices cannot resolve individual YSOs in distant galaxies, this method can only be applied to the Milky Way and its neighbourhood.
 
 In theory, for any system with high enough spatial resolution, counting YSOs can be used as a tracer of the star formation. 
-However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky way with distance of 0.05 Mpc) can not be resolved.
-Therefore, most studies use the emission from the energetic young stars as a tracer of the SFR. 
+However, considering the limited capabilities of present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky Way with a distance of 0.05 Mpc) cannot be resolved.
+Therefore, most studies use the emission from energetic young stars as a tracer of the SFR. 
 % Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
@@
  In star-forming regions farther away than the Magellanic Clouds, the spatial resolution of currently-available observations is not high enough to find all the young stellar objects. 
- In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to the young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
-\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar populations synthesis models~\citep[e.g.,][]{Bruzual93}.
+ In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
+\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar population synthesis models~\citep[e.g.,][]{Bruzual93}.
 
@@
 The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
-Local calibration is used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+Local calibrations are used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
 Limitations in the spatial resolution of observational data on the one hand, and the broader applicability to distant galaxy populations on the other, have in the past brought more attention to the calibrations of global SFR compared to local SFR.
@@
 \end{equation}
-where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ could be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
+where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ could be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA. %PB: should be \AA$^{-1}$? please check.
 As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
 The calibration constants' changes for shorter timescales are more significant and 
-the their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
+their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
 Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
-Therefore, using the UV emission as a tracer might lead to underestimating of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
+Therefore, using the UV emission as a tracer might lead to underestimation of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
 
@@
 The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
-Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emited via Ly${\alpha}$ and longer wavelengths.
+Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emitted via Ly${\alpha}$ and longer wavelengths.
 This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
@@
 where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
-The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
+The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in \hii~regions.
 Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
@@
 Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
-As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
+As a result, \oii~luminosity can be used as a tracer of the SFR through the \halpha luminosity. 
 \cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
@@
 where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
-Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
+Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of the major SFR indicators in high-redshift galaxies.
 In these galaxies, the \halpha emission line is redshifted out of the optical band; as a consequence, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is really useful~\citep{Kennicutt98b}.
@@
 Since young stars heat the dust to higher mean temperatures than old stellar populations, to first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
-The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
+The fact that the heating rate provided by the young stellar population is higher than  that of the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
 Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.
@@
 
-The emission from dust heated by young stars changes by amount of high energy photon emitted to dust and by properties of dust such as grain size.
-Therefore, calibration of SFR varies with each single-band IR emission.
-Assuming that dust heating is dominated by emission from young stars stellar, integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
+The emission from dust heated by young stars changes with the amount of high energy photons heating the dust and by properties of dust such as grain size.
+Therefore, the calibration of SFR varies with each infrared band.
+Assuming that dust heating is dominated by emission from young stars, integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
 
 TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
-\cite{Boquien10} modified calibration of the total infrared luminosity as: 
+\cite{Boquien10} modified the calibration of the total infrared luminosity as: 
 \begin{equation}
@@
 
-In Sec~\ref{sec: overview} we mentioned that emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
-Most studies used broad bands IR emission, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using the PAH features only.
+In Sec.~\ref{sec: overview} we mentioned that emission from PAHs in the ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
+Most studies used broad infared bands, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using the PAH features only.
 \cite{Shipley16} calibrated SFR using observation from 105 star-forming galaxies with $z < 0.4$ as:
@@
 $\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}.
-The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.p][]{Hao11, Leroy08}.
+The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.g.][]{Hao11, Leroy08}.
 
-Another common method for using the multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
+Another common multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
 This combination gives a more accurate dust-corrected estimate of the SFR~\citep{Kennicutt09}:
@@
 \end{equation}
-where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. 
+where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the units of erg~s$^{-1}$. 
 L(24) is the 24~$\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$~yr$^{-1}$.
 
-The IR emission in the other band can be used for correcting dust effect on UV or \halpha~emission (see Tab.~\ref{table3}). 
+Infrared emission in other bands can be used for correcting dust effects on UV or \halpha~emission (see Tab.~\ref{table3}). 
 The corrected emission then can be used as a SFR tracer.
@@
 Sahar: I thought because IMF affect all of the calibration it would be better to have at the end of the section.
+%PB: OK.
 As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
 From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
-This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than the other part of spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
+This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than in other parts of the spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
 Furthermore, reaching an asymptotic value of ionizing photons takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
@@
 Our understanding of star formation in extragalactic systems depends on the light emitted by those systems.
-While emission from massive and young stars is dominating light of the system, mass of low-mass stars dominates the mass of regions (see Sec.~\ref{sec: imf}).
-Therefore, SFRs are calibrate based on dominant light of the systems and low-mass stars are accounted using initial mass function.
+While emission from massive and young stars dominates the light of the system, the mass of low-mass stars dominates the mass  (see Sec.~\ref{sec: imf}).
+Therefore, SFRs are calibrated based on the dominant light and low-mass stars are accounted for using the initial mass function.
 Emission from star forming regions should be corrected before it can be used in calibrations.
-In their way to the Earth this emission passes through dust and gas clouds which causes extinction or attenuation (See ref.~\ref{sec: extinction}).
+On its way to the Earth this emission passes through dust and gas clouds which cause extinction or attenuation (see Sec.~\ref{sec: extinction}).
 On the other hand, evolved stars emit their light in the whole spectrum as well as UV. 
-Therefore, even though it might have insignificant part in UV emission from galaxies, a correction for emission from evolved stars should be considered~\citep{Leroy08}.
+Therefore, even though it might have an insignificant part in the UV emission from galaxies, a correction for emission from evolved stars should be considered~\citep{Leroy08}.
 After measuring the corrected luminosities for star forming regions in galaxies (global or local), using proper calibrations can give the best estimation of SFR in galaxies.

### 2016-07-14 version0.0/intro0.0.tex
Updates from ShareLaTeX

--- 2016-07-14 version0.0/intro0.0.tex
@@
 Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
-a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
-Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
-We cannot detect any contribution from planets or non-accreting black holes to SEDs, due to their low intensity compared to these other components.
+a plot of brightness/flux density of galaxies as a function of wavelengths, which is called spectral energy distribution (SED), is a useful tool to have a intuition about galaxies. 
+Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
+We cannot detect any contribution from planets and black holes, the ones without accretion disc, to SEDs due to their low intensity compared to these other components.
 Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.
@@
 done
-Among observable objects in galaxies, gas has a crucial role in the formation and evolution of galaxies.
-Gas and dust in galaxies can be found in the space between stars and are together called the interstellar medium (ISM).
+Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
+Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM).
 The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
@@
 The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
-Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution, in that stars release their material into the ISM when they reach the end of their evolution.
+Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.
 
-In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$~M$_{\odot})$ in the ISM due to gravitational instabilities. 
-The denser regions within GMCs collapse under their own gravity (self-gravity) and create clumps.
+In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
+The denser regions within GMCs collapse under their own gravity, self-gravity, and creates clumps.
 Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
 Then these clumps continue to become denser and transfer to protostars. 
-Since the protostars have higher mass than their surroundings, more gas from GMCs is added to protostars.
-This procedure continues until hydrogen burning starts in the centre of protostars (see~\cite{McKee07} for more details).
+Since the protostars have higher mass than their surrounding, more gas from GMCs add to protostars.
+This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).
 
@@
 Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
-The amount of metals in stars affects their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
-For example, low metallicity stars tend to have lower mass loss by stellar winds than those with higher metallicity.
-Since there is less mass loss in low metallicity stars, hence no loss of angular momentum because of winds, massive low metallicity stars rotate faster.
-Being more massive at the end of their evolutionary track gives massive low metallicity stars a lower chance to explode and become a supernova.
+Amount of metals in stars affect their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
+For example, low metallicity stars tend to be have lower mass loss by stellar wind than that with higher metallicity.
+Since there is lower amount of mass loss in low metallicity stars, hence no loosing angular momentum because of wind, massive low metallicity stars rotate faster.
+Being more massive at the end of evolutionary track, makes massive low metallicity stars lower chance to explode (become a supernova).
 
@@
 Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
-The general shape of SEDs mirrors the morphological types of galaxies: starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission.
+The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission.
 Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.
@@
  %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
-The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
-A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
+The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
+A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
 Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
@@
 It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
-Some of the physical properties of galaxies must be assumed as an input data to find best SED, and others are derived from SED results~\citep[See][for more detail]{Walcher08}.
-For example, the best-fit SED has information regarding a galaxy's star formation history and stellar mass to light ratio.
-By integrating the star formation history over a specific time scale, the SFR can be derived. %PB: backwards? integrate SFR to get SFH?
-Knowing the stellar mass to light ratio, one can use the observed luminosity to calculate stellar mass in galaxies.
+Some of the physical properties of galaxies should be assumed as an input data to find best SED, and others will be derived from SED results~\citep[See][for more detail]{Walcher08}.
+For example, the Best fitted SED has information regarding star formation history and stellar mass to light ratio.
+By integrating star formation history over specific time scale, SFR can be derived. 
+knowing the stellar mass to light ratio, one can used observed luminosity to calculate stellar mass in galaxies.
 
-The formation of stars in galaxies depends on many parameters, including gas, stellar mass, metallicity, dust, the galaxy's morphology and the location of the star forming region inside the galaxy.
+Formation of stars in galaxies depends on many parameters, gas, stellar mass, metallicity, dust, galaxy's morphology and location of the star forming region inside the galaxy.
 In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.
@@
 \label{equ: extinction}
-{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)exp[-\tau_{\lambda}]
+{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}]
 \end{equation}

### 2016-07-14 version0.0/intro0.01.tex

--- 2016-07-14 version0.0/intro0.0.tex
@@
 % stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
-Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
-There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
+Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
+They all affect each others' formation, evolution, and extinction.
+There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
 Nearly all the information we can obtain from galaxies other than our own comes from their light.
-Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
-a plot of brightness/flux density of galaxies as a function of wavelengths, which is called spectral energy distribution (SED), is a useful tool to have a intuition about galaxies. 
-Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
-We cannot detect any contribution from planets and black holes, the ones without accretion disc, to SEDs due to their low intensity compared to these other components.
-Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.
+Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
+a plot of brightness/flux density of galaxies as a function of wavelengths, which is called spectral energy distribution (SED), is a useful tool to gain a information about galaxies. 
+Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the SEDs of galaxies.
+Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
+Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
 
@@
 Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
-Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM).
-The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
+Gas and dust in galaxies can be found in the space between stars.
+This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
 The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
 The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
-Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.
+Studying the interstellar medium is not only essential to understanding the formation of stars, but also it is necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.
 
-In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
+In a galaxy, like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot}$) in the ISM due to gravitational instabilities. 
 The denser regions within GMCs collapse under their own gravity, self-gravity, and creates clumps.
-Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
+Some of these clumps, which have a similar distribution to stellar initial mass function (IMF), develop into self-gravitating cores.
 Then these clumps continue to become denser and transfer to protostars. 
-Since the protostars have higher mass than their surrounding, more gas from GMCs add to protostars.
+Since the protostars have a higher mass than their surroundings, more gas from GMCs add to protostars.
 This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).
@@
 \cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores.
-Metals also play an important role in heating, cooling and ionizing processes in the ISM.
+Metals also play an important role in heating, cooling, and ionizing processes in the ISM.
 Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
-Amount of metals in stars affect their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
-For example, low metallicity stars tend to be have lower mass loss by stellar wind than that with higher metallicity.
-Since there is lower amount of mass loss in low metallicity stars, hence no loosing angular momentum because of wind, massive low metallicity stars rotate faster.
-Being more massive at the end of evolutionary track, makes massive low metallicity stars lower chance to explode (become a supernova).
+The amount of metals in stars also affect their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
+For instance, low metallicity stars tend to be have lower mass loss by stellar wind than that with higher metallicity.
+Observation shows that massive low metallicity stars rotate faster.
+Being more massive at the end of evolutionary track makes massive low metallicity stars have a lower chance to explode and become a supernova.
 
 %what does SED look like?
-Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. 
+Our primary source of information about galaxies, specifically unresolved ones, is their spectral energy distributions. 
 Broadly speaking, young and hot stars emit most of their light in ultraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
 Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
-Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
+Other wavelengths regimes in galaxy SEDs (e.g. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
 The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission.
@@
  %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
-The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
-A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
+The stellar population synthesis method, which sums stellar spectra of a galaxy to produce its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
+A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
 Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
@@
 It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
-Some of the physical properties of galaxies should be assumed as an input data to find best SED, and others will be derived from SED results~\citep[See][for more detail]{Walcher08}.
+Some of the physical properties of gaalxies should be assumed as an input data to find the best SED, and others will be derived from SED results~\citep[See][for more detail]{Walch08}.
 For example, the Best fitted SED has information regarding star formation history and stellar mass to light ratio.
-By integrating star formation history over specific time scale, SFR can be derived. 
-knowing the stellar mass to light ratio, one can used observed luminosity to calculate stellar mass in galaxies.
+By integrating star formation history over a specific time scale, SFR can be derived. 
+knowing the stellar mass to light ratio, one can use the observed luminosity to calculate stellar mass in galaxies.
 
-Formation of stars in galaxies depends on many parameters, gas, stellar mass, metallicity, dust, galaxy's morphology and location of the star forming region inside the galaxy.
+Formation of stars in galaxies depends on many parameters such as gas, stellar mass, metallicity, dust, galaxy's morphology, and location of the star forming region inside the galaxy.
 In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.
-Studying star formation and its relation to other quantities in galaxies in an ongoing progress.
+Studying star formation and its relation to other quantities in galaxies in an ongoing research.
 In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
@@
 Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
+%% We or I?!
 
@@
 The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
-The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
+The gas in the ISM of galaxies is mostly made of hydrogen and helium, with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse (diffused?) regions.
 Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or hot intercloud medium.
-Dust mostly contains silicate, graphite grains can be seen in dark clouds or galactic cirrus.
-Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
+Dust mostly contains silicate, and graphite grains can be seen in dark clouds or galactic cirrus.
+Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds, and 21~cm emission of \hi~are the main observable signatures of gas in the ISM of galaxies.
 Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).
@@
 Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
-Density in the molecular clouds is not uniform; There are dense and colds clumps inside these clouds.
+Density in the molecular clouds is not uniform. There are dense and colds clumps inside these clouds.
 Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars
@@
 Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
-In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds.
-%PB \bf needs clarification
+In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state} and can be excited in the temperature of molecular clouds.%%Sr: I'll add more detail here
 Other heavier molecules have emission lines which are also detectable in the spectrum of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.
@@
 The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
-The energy state of the anti-parallel mode is slightly less than the parallel mode.
+The energy of the anti-parallel mode is slightly less than the parallel mode.
 Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
@@
 High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
-~\halpha emission is the main observational feature of \hii~regions.
+~\halpha emission is the main observable feature of \hii~regions.
 The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
-Forbidden lines are not ``forbidden", they only have much lower probability of occurring than the ``allowed" ones.
-Optically bright \halpha emission from \hii~regions correlates with number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
+Forbidden lines are not called so because there is no chance of them occurring, but merely because their probability is much lower than the normal ``allowed'' transitions.
+Optically bright \halpha emission from \hii~regions is correlated with number of new massive stars in regions, and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
 Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
@@
 %The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
-In spiral galaxies dust grains are located in cold regions ($\sim$30~K) and have a power-law distribution of size.
-Source of dust thermal emission is from stars and shape of the continuum depends on size of the grain.
-Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate mass young stars~\cite{Peeters04}. 
+In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
+The source of thermal emission of dust is from stars, and shape of the continuum depends on size of the grain.
+Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}. 
 Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
@@
 \label{sec: ismmap}
-Measuring the mass of gas in galaxies is a necessary step to know how much raw material is available for forming stars.
+Measuring the mass of gas in galaxies is a necessary step to knowing how much raw material is available for forming stars.
 A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
 Neutral atomic and molecular hydrogen are the most common components of the ISM. 
-Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly helium, which cannot be observed directly.
+Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements, which are mostly helium and cannot be observed directly.
 Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.
@@
 This method can be promising if observational data with resolved molecular and atomic clouds are available.
-However, given the state of the current technology, having the high resolution images of clouds for most of galaxies are not possible. 
+However, given the state of the current technology, having high resolution images of clouds for most galaxies is not possible. 
 This problem shows itself for distant galaxies more than nearby galaxies. 
-As a result, using images of molecular and atomic cloud to measure surface density of gas in ISM is limited to telescopes resolution.
+As a result, using images of molecular and atomic cloud to measure surface density of gas in ISM is limited to the telescopes resolution.
 
@@
 Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
-Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][] {Sanders84}.
+Therefore, CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][] {Sanders84}.
 Higher rotational transitions of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.
@@
 \begin{equation}
-L_{CO} = D^2 \int I_{\rm CO} d\Omega 
+L_{CO} = D^2 \int I_{\rm CO} d\Omega, 
 \end{equation}
-where $D$ is the distance to the cloud and 
-$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in KKms$^{-1}$.
+%NOTE: Equations must be punctuated.%
+where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in KKms$^{-1}$.
 It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(k) is the peak brightness temperature in the CO line and $V$ is the line-width in Kms$^{-1}$.
@@
  \begin{equation}
-L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V
+L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V.
 \end{equation}
@@
  \label{equ: vir}
- M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}
+ M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}},
 \end{equation}
@@
 Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
- Since the dependency of $I_{\mathrm CO}$ to optical depth is negligible~\citep{Krumholz09}, total CO luminosity of the galaxies, can be used to measure the total H$_2$ mass of galaxies.
- The relation between CO emission and H$_2$ cloud mass is shown as
+Since the dependency of $I_{\mathrm CO}$ to optical depth is negligible~\citep{Krumholz09}, total CO luminosity of the galaxies can be used to measure the total H$_2$ mass of galaxies.
+The relation between CO emission and H$_2$ cloud mass is shown to be
 \begin{equation}
-N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1}
+N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1},
 \end{equation}
 where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
-The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
-Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties~\citep{Bolato13}.
+The X-factor is different for each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity.
+Although assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity this assumption leads to uncertainties~\citep{Bolato13}.
 Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.
@@
 \begin{figure}
-\label{fig: mco_ch}
+\label{fig: mco}
 \centering
@@
 Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
-Fig.~\ref{fig: mco_ch} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
+Fig.~\ref{fig: mco} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
 The extragalactic molecular clouds are similar to those in the Milky Way. 
 The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
-Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local. 
+Problems regarding metallicity are not yet resolved and it is still not clear whether the conversion factor is global or local. 
 Extragalactic investigations were limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
@@
 
-Atomic gas in galaxies are dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
-Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
-\begin{equation}
-N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
-\end{equation}
-where $T_{\mathrm B}$ is the temperature brightness in K and dV is in Kms$^{-1}$, with the integral over the line profile. 
-These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
-Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.
-
-\subsubsection{Dust Emission as a Tracer of Gas}
-
-Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of data.
-\cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
-The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
-This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
-The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary.
-The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
-Dark gas is a significant fraction of gas in galaxies which is traced by neither 21-cm emission nor CO emission~\citep{Abdo10}. 
-As such it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
-
-There are disadvantages of the use of the gas to dust ratio to trace gas in the ISM.
-In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
-\cite{Draine03} pointed out that the former approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
-Measuring the gas to dust ratio in galaxies are not accurate, neither~\citep{Hildebran83}, which means that there are problems in both steps. 
-In addition, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
-To solve this problem, measurement of the continuum emission at far-infrared wavelengths long enough to cover the peak of the emission must be very accurate~\citep{Ealas12}. 
-The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-This method is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.
-
-\subsection{The ISM and starlight: extinction and attenuation}
-\label{sec: extinction}
-Dust in ISM affects stellar emission by attenuating, scattering or absorption.
-Attenuation refers to the effects of dust with embedded light sources distributed throughout. 
-The dust itself can be clumpy or smooth. 
-Effect of dust clouds with embedded light sources on distribution of the light is called attenuation.
-The dust cloud could have any distribution and be clumpy or smooth.
-Since both light source and dust have extended distribution, the relative location of the dust and light source affect the net absorbed and scattered light.
-The other parameters that is important on  the scattering and absorption is the relative position of dust and observer.
-When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
-This is the typical situation that occurs when studying galaxies or extended regions within galaxies.
-
-Extinction happens when there is a combination of both absorption and scattering of radiation by dust and varies with the wavelength of emission; UV light passes through dust are more affected than the optical light.
-Extinction can be defined as reduction of the original intensity caused by dust:
-\begin{equation}
-\label{equ: extinction}
-{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}]
-\end{equation}
-where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction in $\lambda$.
-The extinction depends also on size of grains and extinction cross section.
-For measuring SFR using varies wavebands, 
-decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR. 
-% By converting Equ.~\ref{equ: extinction} to magnetidue system:
-% \begin{equation}
-%      {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda}  = -2.5\log(\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)})
-% \end{equation}
-% and by substituting $\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)}$ with $exp[-\tau_{\lambda}]$, we have:
-% \begin{equation}
-% \begin{split}
-%     {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = -2.5\log(exp[-\tau_{\lambda}]) \\
-%               & = 1.086\tau_{\lambda}
-% \end{split}
-% \end{equation}
-% By defining ${\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = {\mathrm A}_{\lambda}$  extinction in magnitude is A$_{\lambda} = 1.086\tau_{\lambda}$.
-
-% To describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
-% PB: "beam" is jargon, change to something else.
-Simplify this sentence.
-% At UV/optical/near-IR wavelengths, the radiative transfer equation is: %PB: why does this eqn only apply at UV/opt/NIR? 
-% \begin{equation}
-% \frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
-% \end{equation}
-% where I$_{\nu}$ is the intensity of radiation and $\tau$ is the dust's optical depth.
-% $a_{\nu}$ is the dust albedo,  the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
-% $\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. %PB: what is \phi? Need to explain at least a little
-% Both $a_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
-% The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m, is neglected in the equation above.
-%PB: why no dust emission at short wavelengths?
-(temperature)
-% This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, there will be an underestimation of the star formation rate.
-%PB: what do you mean by "different emission" in this sentence?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%SFR%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Measuring the star formation rate in galaxies} 
-\label{sec: sfr_intro}
-Understanding the formation of stars leads to better understanding of galaxies' formation and evolution. 
-Characterisation of the star formation processes such as star formation rate (SFR) and the stellar initial mass function (IMF) is necessary in examining galaxies' structure formation~\citep{McKee07}. 
-Measuring the SFR is not trivial and depends on a galaxy's morphology, metallicity, IMF, observational spatial resolution, and other properties. 
-There is a large number of review papers on how stars form and how their formation is traced. 
-From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
-From an observational standpoint, star formation is discussed by \cite[][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.
-
-In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission.
-Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
-Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
-Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
-One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer.
-By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
-To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
-In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.
-
-\subsection{Stellar Initial Mass Function}
-\label{sec: imf}
-Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
-One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
-Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
-\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
-He introduced a power-law IMF $\Phi$  in the form:
-\begin{equation}
-\label{equ: salp}
-\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
-\end{equation} 
-where $M$ is the stellar mass, $\gamma$ is a power index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.
-
-In the late 70s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}.
-Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
-Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
-\begin{equation}
-\begin{split}
-    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
-           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
-\end{split}
-\end{equation}
-Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
-Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
-In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8~M$_\odot$.
-\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.
-
-\begin{figure}
-\label{fig: imf}
-\centering
-\includegraphics[width=16cm]{../image_intro/imf}
-\small
-\caption{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity.
-The mass ranges from 0.1 to 120~M$_\odot$.
-Adopted from~\cite{Baldry03}.}
-\end{figure}
-
-Since in using SFR calibration for different galaxies, we assume the initial mass function is universal, careful measurement of the IMF is a key factor in understanding the star formation rate. 
-In distant galaxies, only massive stars can be detected; therefore, the IMF must be assumed to include all stellar mass ranges in the SFR calibrations. 
-To show the impact of the different stellar IMF assumptions on the SFR calibrations, \cite{Calzetti13} used two different stellar IMFs and derived the SFR calibrations with these new assumptions.
-Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30~M$_{\odot}$ instead of 100~M$_{\odot}$, changes the SFR calibration constants by factors ranging from 1.4 to 5.6 for different SFR indicators (Tab.~\ref{table1}).
-
-\subsection{SFR Indicators}
-
-One of the main issues in studying star formation in distant galaxies is the calibration of star formation rate indicators~\citep[e.g.,][]{Lee10}. 
-Calibration of SFR indicators can be affected by differences in star formation history (SFH), metallicity, distribution of stellar population and dust in galaxies~\citep{Calzetti13}. 
-Based on the spatial resolution of a system, one can divide star formation indicators into two categories: resolved and unresolved star formation indicators.
-
-\subsubsection{Resolved Star Formation Indicators}
-The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
-These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
-Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
-The number of YSOs can be converted to SFR using: 
-\begin{equation}
-SFR(YSO) = N_{yso} <M>/\tau 
-\end{equation}
-where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
-$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
-$\tau$ is the lifetime of the YSO  $\tau \sim 2$Myr~\citep{Evans09}. 
-Since our current devises cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
-
-In theory, for any system with high enough spatial resolution, counting YSOs can be used as a tracer of the star formation. 
-However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky way with distance of 0.05 Mpc) can not be resolved.
-Therefore, most studies use the emission from the energetic young stars as a tracer of the SFR. 
-% Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
-% \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to produce spatially and age-resolved maps of star formation in nearby galaxies. 
-% More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}. %PB: I think you should give a one-sentence summary of the method here. 
-%Sr: I think later whether I want to keep this section or not.
-\subsubsection{Unresolved Star Formation Indicators}
-
- In star-forming regions farther away than the Magellanic Clouds, the spatial resolution of currently-available observations is not high enough to find all the young stellar objects. 
- In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to the young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
-\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar populations synthesis models~\citep[e.g.,][]{Bruzual93}.
-
-In unresolved systems, SFR indicators can be divided into local and global indicators. 
-The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
-Local calibration is used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
-Limitations in the spatial resolution of observational data on the one hand, and the broader applicability to distant galaxy populations on the other, have in the past brought more attention to the calibrations of global SFR compared to local SFR.
-Because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.
-
-\subsubsection*{SFR Indicators Based on Single-Band Emission}
-
-In order to derive conversions between the luminosity in specific wavelengths and the SFR, stellar population synthesis models are used~\citep{Kennicutt98b}. 
-The general form of a SFR calibration using single-band emission is: 
-\begin{equation}
-\label{equ: sfrsingle}
-{\rm SFR}(\lambda)= CL(\lambda)
-\end{equation}
-where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}).
-The constant $C$ varies for different wavelengths, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation is assumed to remain constant. 
-Table~\ref{table1}, from \cite{Calzetti13}, summarises some values of $C$ and their changes with assumption about the IMF.
-
-\begin{table}
-\centering
-\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
-\label{table1}
-\begin{tabular}{ c c c }
-\hline\hline
-Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
-\hline
-L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
-L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
-L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
-L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
-L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
-\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}.
-For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$ to convert luminosity density to luminosity.
-%or flux density?
-\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Sec.~\ref{sec: imf}), and for the timescale $\tau$.
-\end{tablenotes}
-\end{table}
-
-The most common single-band tracer of star formation rate is the ultraviolet.
-As mentioned before, UV emission is an excellent tracer for the SFR.
-Using a spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
-\begin{equation}
-SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
-\end{equation}
-where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ could be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
-As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
-The calibration constants' changes for shorter timescales are more significant and 
-the their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
-Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
-Therefore, using the UV emission as a tracer might lead to underestimating of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
-
-Another single-band SFR indicator is the emission from hydrogen recombination lines. 
-Ionizing photons emitted from young massive stars ionize the surrounding gas.
-Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}.
-The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived from quantum mechanics. 
-The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
-Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emited via Ly${\alpha}$ and longer wavelengths.
-This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
-The relation between the SFR, the luminosity of the \halpha emission line and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
-\begin{align}
-\label{equ: halpha}
-SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
-                     = 7.4 \times 10^{-54}Q(H^{\circ})
-\end{align}
-where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
-The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
-Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
-The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
-by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
-
-Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
-Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
-As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
-\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
-Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
-In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
-\begin{equation}
-SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
-\end{equation}  
-where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
-Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
-In these galaxies, the \halpha emission line is redshifted out of the optical band; as a consequence, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is really useful~\citep{Kennicutt98b}.
-
-Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the infrared emission can be used to trace the SFR.
-The IR luminosity of a system depends not only on the amount of embedded dust, but also on the heating rate provided by the stars. 
-Since young stars heat the dust to higher mean temperatures than old stellar populations, to first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
-The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
-Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.
-
-Two empirical single-band infrared star formation rate indicators are the 24~$\mu$m and 70~$\mu$m bands.  
-The use of these two bands depends on the type of galaxy studied or the physical environment in different regions within the galaxy. 
-Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) or a local indicator.
-That is because the global case includes the integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
-Table~\ref{table2} shows the constant $C$ from Equ.\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities, for local (spatial scale $\sim500$~pc for 24~$\mu$m and $\lesssim 1$ kpc for 70~$\mu$m) and global cases.
-
-\begin{table}
-\centering
-\caption{Infrared Luminosity to star formation rate calibrations}
-\label{table2}
-\begin{tabular}{ c c c c }
-\hline\hline
-Luminosity$^1$ & $C$ & Assumptions & references\\ 
-\hline
-L(24)$^{0.885}_{local}$ & $1.31 \times 10^{-38}$ &$1.10\times 10^{40} \le L(24) \le 3.10\times 10^{44}$&  \cite{Calzetti07}   \\ 
-L(24)$_{global}$ & $2.04 \times 10^{-43}$ &$ 4.10\times 10^{42} \le L(24)  \le 5.10\times 10^{43}$& \cite{Calzetti07} \\
-L(70)$_{local}$ & $9.4 \times 10^{-44} $ &$5.10\times 10^{40} \le  L(70) \le 5.10\times 10^{43}$& \cite{Li12} \\
-L(70)$_{global}$& $5.9 \times 10^{-44}$ &$L(70) \ge 1.4 \times 10^{42} $& \cite{Li10}\\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda$} in erg s$^{-1}$ 
-\end{tablenotes}
-\end{table}
-
-\subsubsection*{SFR Indicators Based on Multi-Band Emission}
-
-%%add PAHs here
-Despite the usefulness of having single-band SFR tracers, in many cases the corrections due to dust effects and luminosity ranges increase the uncertainty in measurements.
-Nowadays, thanks to large surveys, enormous amounts of data are available at different wavelengths for galaxies, which allows for combining the emission from different bands and finding new calibrations.
-The conversion between SFR and luminosities in multiple bands mostly helps to avoid problems regarding dust extinction or attenuation (see~\ref{sec: ism_intro}). 
-The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically derived~\citep{Kennicutt12}.
-
-The emission from dust heated by young stars changes by amount of high energy photon emitted to dust and by properties of dust such as grain size.
-Therefore, calibration of SFR varies with each single-band IR emission.
-Assuming that dust heating is dominated by emission from young stars stellar, integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
-
-TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
-\cite{Boquien10} modified calibration of the total infrared luminosity as: 
-\begin{equation}
-L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m)
-\end{equation}
-where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
-\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
-\begin{equation}
-\label{sfr_tot_IR}
-SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
-\end{equation}
-where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.
-
-In Sec~\ref{sec: overview} we mentioned that emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
-Most studies used broad bands IR emission, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using the PAH features only.
-\cite{Shipley16} calibrated SFR using observation from 105 star-forming galaxies with $z < 0.4$ as:
-\begin{equation}
-\log SFR = A + B \log L_{\mathrm{PAH}, \lambda}
-\end{equation}
-where $L_{\mathrm{PAH}, \lambda}$ is the luminosity of the PAH features at 6.2, 7.7, 11.3~$\mu$m or combinations thereof, in erg~s$^{-1}$.
-Tab.~\ref{table_PAH} shows the constants for each $L_{\mathrm{PAH}, \lambda}$.
-These calibrations underestimate the SFR for low-redshift galaxies with IR luminosity more than $10^12$~erg~s$^{-1}$.
-\cite{Shipley16} showed that using the 7.7~$\mu$m feature in the calibration reduces the scatter and concluded that this wavelength provides the most robust SFR tracer.
-
-\begin{table}
-\centering
-\caption{SFR calibrations from PAH luminosities; adopted from~\cite{Shipley16}}
-\label{table_PAH}
-\begin{tabular}{ l c c}
-\hline\hline
-PAH Feature(s) & A & B\\
-\hline
-6.2 + 7.7 + 11.3 & $ -42.56 \pm 0.03 $ &  1.00 \pm 0.03 \\ 
-6.2 & $ -40.06 \pm 0.09 $ &  0.96 \pm 0.04 \\ 
-7.7 & $ -42.38 \pm 0.06 $ &  1.00 \pm 0.03 \\ 
-11.3 & $ -44.14 \pm 0.08 $ &  1.06 \pm 0.03 \\ 
-6.2 + 7.7 & $ -42.05 \pm 0.04 $ &  0.99 \pm 0.03 \\ 
-6.2 + 11.3 & $ -42.52 \pm 0.05 $ &  1.01 \pm 0.03 \\ 
-7.7 + 11.3 & $ -42.85 \pm 0.04 $ &  1.01 \pm 0.03 \\ 
-\hline
-\end{tabular}
-\end{table}
-
-The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used.
-This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
-\begin{equation}
-L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR}
-\end{equation}
-where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements.
-$\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}.
-The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.p][]{Hao11, Leroy08}.
-
-Another common method for using the multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
-This combination gives a more accurate dust-corrected estimate of the SFR~\citep{Kennicutt09}:
-\begin{equation} 
-\label{equ: halphaplus24}
-SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24)]
-\end{equation}
-where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. 
-L(24) is the 24~$\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$~yr$^{-1}$.
-
-The IR emission in the other band can be used for correcting dust effect on UV or \halpha~emission (see Tab.~\ref{table3}). 
-The corrected emission then can be used as a SFR tracer.
-These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
-Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.
-
-\begin{table}
-\centering
-\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
-\label{table3}
-\begin{tabular}{ c c}
-\hline\hline
-Combined luminosities$^1$ & references\\
-\hline
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& \cite{Hao11}\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& \cite{Hao11}\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& \cite{Hao11}\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& \cite{Kennicutt09}\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& \cite{Kennicutt09}\\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L_{$\lambda$} in erg~s$^{-1}$ 
-\end{tablenotes}
-\end{table}
-
-%PB: would it make sense to put this paragraph closer to where you first discuss Table 1?
-Sahar: I thought because IMF affect all of the calibration it would be better to have at the end of the section.
-As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
-From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
-This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than the other part of spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
-Furthermore, reaching an asymptotic value of ionizing photons takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
-Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR the calibration constants are fairly close to each other.
-On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a 10 per cent difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
-As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.
-
-Our understanding of star formation in extragalactic systems depends on the light emitted by those systems.
-While emission from massive and young stars is dominating light of the system, mass of low-mass stars dominates the mass of regions (see Sec.~\ref{sec: imf}).
-Therefore, SFRs are calibrate based on dominant light of the systems and low-mass stars are accounted using initial mass function.
-Emission from star forming regions should be corrected before it can be used in calibrations.
-In their way to the Earth this emission passes through dust and gas clouds which causes extinction or attenuation (See ref.~\ref{sec: extinction}).
-On the other hand, evolved stars emit their light in the whole spectrum as well as UV. 
-Therefore, even though it might have insignificant part in UV emission from galaxies, a correction for emission from evolved stars should be considered~\citep{Leroy08}.
-After measuring the corrected luminosities for star forming regions in galaxies (global or local), using proper calibrations can give the best estimation of SFR in galaxies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%Stellar Mass%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Stellar mass}
-\label{sec: starmass_intro}
-One of the most fundamental physical parameters which describes the present state of a galaxy is its stellar mass. 
-Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and allmorphologies~\citep{Scodeggio02}. 
-Measuring the mass of a stellar population is indirect and subject to significant uncertainties. 
-In principle there are two ways to measure stellar mass in galaxies. 
-The first is measuring the dynamical mass of a galaxy using kinematics (the mostion of stars)~\citep{Cappellari06} or lensing (bending light as the light pass near a galaxy)~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
-
-The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution.
-Stellar population models predict the expected SEDs for stellar populations based on parameters of regions such as star formation history, metallicity, and IMF
-Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][ans references therein]{Dalcanton12}, and star formation histories.
-
-In order to translate between photometry and stellar mass the stellar mass-to-light ratio ($M/L$) is needed.
-The use of $M/L$ is one way to measure stellar mass surface density. It is an indirect method and has high uncertainties in specific cases, but can help to study the stellar mass in large samples. 
-For integrated galaxy light, the $M/L$ is estimated using scaling relations between $M/L$ and broadband colours \citep[e.g.]{Bell03} and then multiplied by luminosity to estimate a mass.
-For resolved galaxies, one can produce a map of the stellar mass surface density distribution in galaxies using resolved colour to measure spatial variations in $M/L$.
-This method gives more accurate results than measuring the stellar mass surface density distribution from single-band images rescaled by a uniform mass to light ratio~\citep{Zibetti09}.
-
-Comparing results from independent methods to measure stellar mass helps to determine whether there are any systematic differences.
-Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few tens per cent~\citep{McLaughlin05}.
-Therefore, to model subtleties, the advantages and disadvantages of using each method should be carefully considered.
-
-\subsection{galaxy masses from dynamics}
-
-The simplest and the most common way to estimate the mass of a galaxy is assuming that the physics of the galaxy is simple Newtonian physics.
-Therefore, the circular velocity $v{\rm circ}(r)$ of an orbit within a spherical system of gravitational potential $\phi$ and mass $M$ is given by:
-\begin{equation}
-\label{eq: simpmass}
-v^2_{\rm circ}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r}
-\end{equation}
-where where $G$ is the gravitational constant and $M(r)$ is the mass within a sphere of radius $r$. 
-For a flattened disk, which is the case in most spiral galaxies, the right hand side of Equ.\ref{eq: simpmass} must be replaced by the more exact expression derived by~\cite{Freeman70}. 
-For the case of no dark matter or bulge, \cite{Freeman70} showed that the rotation curve of a self-gravitating disk is:
-\begin{equation}
-v^2_{circ}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)]
-\end{equation}
-where $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, where ratio of the intensity of disk to bulge is $e$ ($\sim$2.71).  
-$y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kind modified Bessel functions.
-
-The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi~lines. 
-Integrated line widths only yield an estimate of total mass within some (uncertain) isophotal radius.
-Thanks to the current generation of detectors, it is possible to obtain very high-resolution spectra in the \halpha and CO lines over most of the optical disks of galaxies.
-The higher resolution data
-
-A detailed description of calculating dynamical masses in galaxies is beyond the scope of this work. 
-The methods mentioned represent the first order of approximation. 
-For more accurate results, one should consider non-circular rotational velocities and the fact that galaxies contain millions of stars plus interstellar objects; therefore simple two-object Newtonian physics is not the case here.
-A detailed review of dynamical masses of galaxies can be found in \citet{Courteau13}.
-
-\subsection{Galaxy masses from stellar population modelling}
-
-Galaxies can be observed because of their stellar emission; stars radiate the energy produced from nuclear reactions in their cores. 
-Given a star's initial mass, the theory of stellar evolution can describe the amount of energy released. 
-Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distributions of galaxies. 
-However, some fraction of the mass of galaxies consists of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants and should be considered in models.
-Stellar population synthesis models are used to predict the SED of a stellar population using many physical parameters. 
-These parameters, which control the time evolution of the stellar population such as age, $t$, of the population, measured in years, also referred to as the time passed since the star formation began, IMF, and metallicity~\citep{Courteau13}.
-
-The basic idea behind finding a suitable calibration between flux/luminosity of the stars in different wavelengths and stellar mass is that one can use the SFHs recovered from synthesizing the stellar optical colour-magnitude diagrams in different regions of a galaxy.
-The calculated stellar mass in nearby galaxies can be used to calibrate the fluxes from the stars in other galaxies.
-\cite{Zibetti09} suggested that to reach the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel basis. 
-They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density.
-To do so the surface density of stellar mass at each position is derived by 
-\begin{equation}
-\label{equ: massphot}
-\Sigma_{{\mathrm M_\star}} (\alpha, \delta) = \Sigma_{\lambda}(\alpha, \delta) \gamma_{\lambda}(\alpha, \delta)
-\end{equation}
-where $\alpha$ and $\delta$ are position, right ascension and declination, respectively.
-$\Sigma_{{\mathrm M_\star}} (\alpha, \delta)$ is the stellar surface density.
-$\Sigma_{\lambda}(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L at an effective wavelength $\lambda$.
-In Equ.\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy.
-
-Peak of emission from evolved stars are in NIR part of spectrum.
-Therefore, many studies tried to make a map of stellar mass distribution using this bandpass within galaxies~\citep[e.g.,][]{Elmgreen84}.
-Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps thave a more accurate calibration.
-Fluxes from 3.6 and 4.5$\mu$m are suitable for calibration of the stellar mass, due to fact these two band-passes not only trace evolved stellar population but also they are almost insensitive to the emission from young stellar population or to dust absorption and emission.
-\cite{Zhu10} used the Sloan Digital Sky Survey~\citep[SDSS][]{York00} and the \Spitzer Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find calibration between galaxy luminosity and stellar mass.
-Using the M/L of galaxies, they found correlations between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulated these correlations as:
-\begin{align}
-\label{equ: zhu1}
-\log M_{\star} = -1.60  + 1.12  \log \nu L_{\nu}[K_s]\\
-\log M_{\star} = -0.79 + 1.19 \log \nu L_{\nu}[3.6\mu \rm m]\\
-\label{equ: zhu3}
-\log M_{\star} = -0.25 + 1.15\log \nu L_{\nu}[4.5\mu \rm m] 
-\end{align}
-where M$_{\star}$ is the stellar mass in solar masses and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg~s$^{-1}$ at the specified wavelength.
-
-\cite{Eskew12} tested the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and found an empirical relation between mass of the stars and the luminosities of stars as:
-\begin{equation}
-\label{equ:eskew}
-  M_{\star} = 31.84 \times 10^{5.65} L_{3.6}^{2.85} L_{4.5}^{-1.85}
- %\log M_{\star} = 5.6 +2.85\log (F_{3.6})-1.85 \log (F_{4.5})+2\log \left(\frac{D}{0.05}\right)
-\end{equation}
-where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$/$\AA$.
-Equ.~\ref{equ: zhu1}--~\ref{equ: zhu3} have been derived from a large sample of galaxies, and were tested on different type of regions and galaxies. 
-on the other hand,~\cite{Eskew12} mentioned that since their calibration is based on data from Magellanic clouds this,
-measuring the stellar mass from Equ.~\ref{equ:eskew} might break down for highly star-forming regions; moreover, this equation has not tested on regions with different metallicity. 
-In more recent work,~\cite{Laura16} measured stellar mass for group of galaxies with ($z < 0.035$) and  showed they are tightly correlate with stellar mass measured from other calibrations.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%Preview%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Preview}
-\label{sec: pre_intro}
-
-A complete picture of how galaxies are formed and evolve is tied to unfolding the mystery of the formation of stars.
- Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas and the mass of stars in galaxies.
- For decades, observational, theoretical and numerical studies have investigated star formation; nevertheless, their results are contrary.
- Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
-
-The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
-The K-S law and similar empirical laws have been tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
-Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are yet undetermined and there is no definitive answer on whether there is any universal star formation law.
-Their dependence on physical properties of galaxies is nontrivial and sometimes differs by type of star forming regions.
-Although a relation between star formation and gas is well established, the details of this relation are not clear:
-different types of gas affect SFR in different ways, and variations in metallicity alter the effects.
-There is no fully sampled and universal IMF,
-in fact there are many debates on whether the IMF is universal or not.
-The influence of evolved stars and distance of star forming regions from centre of galaxies on SFR has been mentioned in studies but not fully investigated.
-Besides studying the impact of the above-mentioned properties of galaxies on SFR, searching for other relations between properties of galaxies and their star forming regions continues.
-
-Advances in observing facilities, image quality, and methodology expand our knowledge of star formation. 
-In the past few decades, the use of advanced statistical methods in astronomical studies has also grown.
-Applying modern statistical methods to star formation studies can shed light on unsolved problems in this field. 
-Studies show that using different statistical methods can change our perspective on star formation laws. 
-For example,~\cite{Shetty13} used Bayesian methods to show that the K-S law is not universal. 
-Since astronomy is a data-driven science, data-mining methods should be quite useful to gain new insight on properties of star-forming regions.
-However, these methods have not been widely-applied to studies of nearby galaxies, where the most detailed information about star formation is available.
-
-%PB not sure, but you might need a little more intro to the papers 2 and 3 stuff here.
-
-In this thesis, we present three projects that study the effects of galaxy properties on star formation.
-We use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
-Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
-In addition to the Kennicutt-Schmidt law, we study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
-We also show the effect on star formation laws of using different SFR and ISM gas tracers.
-In Chapter~\ref{ch: paper3}, we explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
-We cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
-During this process, we find hidden structures in high-dimensional data space.
-In Chapter~\ref{ch: paper2}, we move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
-We train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
-Then we study the grouped properties of the classified galaxies.
-We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}
-
-\addcontentsline{toc}{section}{Bibliography}
-\bibliographystyle{apj.bst} 
-\bibliography{ref_intro}
+%%%to be conticued

### 2016-07-14 version0.0/paper1.tex

@@
 \centering
-\includegraphics[width=164mm]{../image_paper1/star.eps}.
+\includegraphics[width=164mm]{../image_paper1/star.eps}
 \caption{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
@@
  \hline
+
 \end{tabular}

### 2016-07-14 version0.0/intro0.01.tex
merged pb changes fo intro0.0.tex with new intro0.01.tex

--- 2016-07-14 version0.0/intro0.0.tex
@@
 % stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
-Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
-There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
+Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
+They all affect each others' formation, evolution, and extinction.
+There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
 Nearly all the information we can obtain from galaxies other than our own comes from their light.
@@
 Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
-We cannot detect any contribution from planets or non-accreting black holes to SEDs, due to their low intensity compared to these other components.
+Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
 Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.
@@
 done
-Among observable objects in galaxies, gas has a crucial role in the formation and evolution of galaxies.
-Gas and dust in galaxies can be found in the space between stars and are together called the interstellar medium (ISM).
-The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
+Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
+Gas and dust in galaxies can be found in the space between stars.
+This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
 The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
 The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
-Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution, in that stars release their material into the ISM when they reach the end of their evolution.
+Studying the interstellar medium is not only essential to understanding the formation of stars, but also it is necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.
 
-In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$~M$_{\odot})$ in the ISM due to gravitational instabilities. 
+In a galaxy, like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot}$) in the ISM due to gravitational instabilities. 
 The denser regions within GMCs collapse under their own gravity (self-gravity) and create clumps.
-Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
-Then these clumps continue to become denser and transfer to protostars. 
-Since the protostars have higher mass than their surroundings, more gas from GMCs is added to protostars.
-This procedure continues until hydrogen burning starts in the centre of protostars (see~\cite{McKee07} for more details).
+Some of these clumps, which have a similar mass distribution to the stellar initial mass function (IMF), develop into self-gravitating cores.
+Then these clumps continue to become denser and turn into protostars. 
+Since the protostars have a higher mass than their surroundings, more gas from GMCs accretes on to protostars.
+This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).
 
@@
 \cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores.
-Metals also play an important role in heating, cooling and ionizing processes in the ISM.
+Metals also play an important role in heating, cooling, and ionizing processes in the ISM.
 Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
 The amount of metals in stars affects their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
-For example, low metallicity stars tend to have lower mass loss by stellar winds than those with higher metallicity.
-Since there is less mass loss in low metallicity stars, hence no loss of angular momentum because of winds, massive low metallicity stars rotate faster.
+For example, low metallicity stars tend to have lower mass loss from stellar winds than those with higher metallicity.
+Observations show that massive low metallicity stars rotate faster.
 Being more massive at the end of their evolutionary track gives massive low metallicity stars a lower chance to explode and become a supernova.
@@
 %what does SED look like?
-Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. 
+Our primary source of information about galaxies, specifically unresolved ones, is their spectral energy distributions. 
 Broadly speaking, young and hot stars emit most of their light in ultraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
@@
 Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
-Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs, (either by minizing $\chi^2$ or by Bayesian analysis)  using the templates.
+Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minizing $\chi^2$ or by Bayesian analysis),  using the templates.
 One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
 It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
-Some of the physical properties of galaxies must be assumed as an input data to find best SED, and others are derived from SED results~\citep[See][for more detail]{Walcher08}.
-For example, the best-fit SED has information regarding a galaxy's star formation history and stellar mass to light ratio.
-By integrating the star formation history over a specific time scale, the SFR can be derived. %PB: backwards? integrate SFR to get SFH?
+Some of the physical properties of gaalxies must be assumed as input data to find the best SED, and others are derived from SED results~\citep[see ][for more detail]{Walch08}.
+For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
+By integrating the star formation history over a specific time scale, SFR can be derived. %PB: please check: integrate SFH to get SFR, or SFR to get SFH?
 Knowing the stellar mass to light ratio, one can use the observed luminosity to calculate stellar mass in galaxies.
@@
 The formation of stars in galaxies depends on many parameters, including gas, stellar mass, metallicity, dust, the galaxy's morphology and the location of the star forming region inside the galaxy.
-In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.
-Studying star formation and its relation to other quantities in galaxies in an ongoing progress.
+In extragalactic astronomy, measuring the rate at which stars form is uncertain and relies upon theoretical models and observational data.
+Studying star formation and its relation to other quantities in galaxies is the subject of ongoing research.
 In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
@@
 Dust mostly contains silicate and graphite grains, and can be seen in dark clouds or galactic cirrus. %PB: please check changes to this sentence
-Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
+Emission lines from atoms or ions (i.e \hii~regions) in hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
 Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).
@@
 Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
-Density in the molecular clouds is not uniform; there are dense and colds clumps inside these clouds.
+Density in the molecular clouds is not uniform. There are dense and colds clumps inside these clouds.
 Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars.
@@
 Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
-In fact, most of our knowledge from molecular clouds comes from observing the line emission of CO molecules, which {\bf due to their heavy weight, they have very low rotational state} and can be excited in the temperature of molecular clouds.
-%PB \bf needs clarification
-Other heavier molecules have emission lines which are also detectable in the spectra of clouds (especially Galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds e.g.\ their mass (see Sec.~\ref{sec: ismmap} for more details).
+In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state} and can be excited in the temperature of molecular clouds.%%Sr: I'll add more detail here
+Other heavier molecules have emission lines which are also detectable in the spectra of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.
+their mass (see Sec.~\ref{sec: ismmap} for more details).
 
@@
 \hii~regions are hot and low density regions that are mostly located in the disks of spiral galaxies.
-High energy UV photons emitted by massive newborn stars have sufficient energy to ionize their surrounding gas, and
-~\halpha emission is the main observational feature of \hii~regions.
+High energy UV photons emitted by massive new born stars have sufficient energy to ionize their surrounding gas, and
+~\halpha emission is the main observable feature of \hii~regions.
 The temperature and density of these regions can be estimated by observing other recombination lines such as H$\beta$, and forbidden lines such as \sii, \oii, \oiii, and \nii. 
-Forbidden lines are not strictly ``forbidden"; they only have much lower probability of occurring than the ``allowed" ones.
-Optically bright \halpha emission from \hii~regions correlates with the number of new massive stars in regions and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
-Studying \hii~regions provides valuable insight into star forming regions by providing information such as the star formation rate, the initial mass function (IMF) of stars, and the distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
+Forbidden lines are not called so because there is no chance of them occurring, but merely because their probability is much lower than the normal ``allowed'' transitions.
+Optically bright \halpha emission from \hii~regions is correlated with number of new massive stars in regions, and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
+Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
 
@@
 %The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
-In spiral galaxies dust grains are located in cold regions ($\sim$30~K) and have a power-law distribution of size.
+In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
 The source of dust thermal emission is heating from stars and the shape of the continuum depends on size of the grain.
-Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate mass young stars~\cite{Peeters04}. 
-Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in the far-infrared~\citep[e.g.][]{Calapa14, lu14}
-Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).
+Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}. 
+Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
+Dust is the main source of extinction and reddening of starlight (See Sec.\ref{sec: extinction} for more information).
 
@@
 \label{sec: ismmap}
-Measuring the mass of gas in galaxies is a necessary step to know how much raw material is available for forming stars.
+Measuring the mass of gas in galaxies is a necessary step to knowing how much raw material is available for forming stars.
 A map of the total gas mass in the ISM can be produced by direct observations of gas or using interstellar dust as a tracer. 
@@
 This problem shows itself for distant galaxies more than nearby galaxies. 
-As a result, using images of molecular and atomic clouds to measure surface density of gas in ISM is limited by telescopes' resolution.
+As a result, using images of molecular and atomic clouds to measure surface density of gas in galaxies' ISM is limited by telescopes' resolution.
 
@@
 \begin{equation}
-L_{CO} = D^2 \int I_{\rm CO} d\Omega 
+L_{CO} = D^2 \int I_{\rm CO} d\Omega, 
 \end{equation}
-where $D$ is the distance to the cloud and 
-$I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
+%NOTE: Equations must be punctuated.%
+where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
 It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
+
 For a uniform cloud with a radius $R$, the CO luminosity is given by:
  \begin{equation}
-L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V
+L_{\rm CO} = \pi R^2 T_{\rm CO} \Delta V.
 \end{equation}
@@
 Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
- Since the dependency of $I_{\mathrm CO}$ on optical depth is negligible~\citep{Krumholz09}, the total CO luminosity of a galaxy can be used to measure its total H$_2$ mass.
- The relation between CO emission and H$_2$ cloud mass is shown as:
+Since the dependence of $I_{\mathrm CO}$ on optical depth is negligible~\citep{Krumholz09}, total CO luminosity can be used to measure the total H$_2$ mass of galaxies.
+The relation between CO emission and H$_2$ cloud mass is shown to be
 \begin{equation}
-N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1}
+N_{\rm H_2}/\rm cm^{-2} = X_{\rm CO} \times I_{\rm CO}/{\rm K km s}^{-1},
 \end{equation}
 where X$_{\rm CO}$ is the conversion factor (also known as the X-factor).
-The X-factor is different in each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity. 
-Though assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity there are uncertainties~\citep{Bolato13}.
+The X-factor is different for each galaxy and sometimes is even different in regions within a galaxy due to differences in properties such as metallicity.
+Although assuming a constant conversion factor for galaxies like M82 and M31 can lead to accurate estimation of global molecular gas mass, in regions with low metallicity this assumption leads to uncertainties~\citep{Bolato13}.
 Various groups are working on observations of different types of galaxies to measure the X-factor for them~\citep{Wilson95, Bosselli02, Bolato13}.
@@
 Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
-Fig.~\ref{fig: mco_ch} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
+Fig.~\ref{fig: mco} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
 The extragalactic molecular clouds are similar to those in the Milky Way. 
 The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
-Problems regarding metallicity are not yet solved and it is still not clear whether the conversion factor is global or local. 
+Problems regarding metallicity are not yet resolved and it is still not clear whether the conversion factor is global or local. 
 Extragalactic investigations have been limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
@@
 
-\addcontentsline{toc}{section}{Bibliography}
-\bibliographystyle{apj.bst} 
-\bibliography{ref_intro}
+%%%to be conticued

### 2016-07-14 version0.0/intro0.01.tex
Update intro0.01.tex
edits to stellar mass section

@@
 \end{equation}
-where I$(\lambda)$ is the observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is the intensity of light before passing through dust, and $\tau_{\lambda}$ is the otpical depth at wavelength $\lambda$.
+where I$(\lambda)$ is the observed intensity at wavelength $\lambda$, I$_0(\lambda)$ is the intensity of light before passing through dust, and $\tau_{\lambda}$ is the optical depth at wavelength $\lambda$.
 The extinction depends also on the size of grains and their extinction cross section.
@@
 One of the most fundamental physical parameters which describes the present state of a galaxy is its stellar mass. 
-Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and allmorphologies~\citep{Scodeggio02}. 
+Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and galaxies of all morphologies~\citep{Scodeggio02}. 
 Measuring the mass of a stellar population is indirect and subject to significant uncertainties. 
 In principle there are two ways to measure stellar mass in galaxies. 
-The first is measuring the dynamical mass of a galaxy using kinematics (the mostion of stars)~\citep{Cappellari06} or lensing (bending light as the light pass near a galaxy)~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
+The first is measuring the dynamical mass of a galaxy using kinematics (the mostion of stars)~\citep{Cappellari06} or gravitational lensing (bending of light as the light passes near a galaxy)~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
 
-The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution.
-Stellar population models predict the expected SEDs for stellar populations based on parameters of regions such as star formation history, metallicity, and IMF
-Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][ans references therein]{Dalcanton12}, and star formation histories.
+The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity at different wavelengths, colours, or spectral energy distribution.
+Stellar population models predict the expected SEDs for stellar populations based on parameters of regions such as star formation history, metallicity, and IMF.
+Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][and references therein]{Dalcanton12}, and star formation histories.
 
 In order to translate between photometry and stellar mass the stellar mass-to-light ratio ($M/L$) is needed.
-The use of $M/L$ is one way to measure stellar mass surface density. It is an indirect method and has high uncertainties in specific cases, but can help to study the stellar mass in large samples. 
+The use of $M/L$ is one way to measure stellar mass surface density. It is an indirect method and has high uncertainties in specific cases, but can help in studying the stellar mass in large samples. 
 For integrated galaxy light, the $M/L$ is estimated using scaling relations between $M/L$ and broadband colours \citep[e.g.]{Bell03} and then multiplied by luminosity to estimate a mass.
@@
 
-\subsection{galaxy masses from dynamics}
+\subsection{Galaxy masses from dynamics}
 
@@
 \end{equation}
-where $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, where ratio of the intensity of disk to bulge is $e$ ($\sim$2.71).  
-$y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kind modified Bessel functions.
+where $\Sigma_0$ is the central surface brightness, and $R_d$ the disk scale length, where the ratio of the intensity of disk to bulge is $e$ ($\sim$2.71).
+%PB: Not quite the right definition of scale length?
+Please check.
+$y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kinds of modified Bessel functions.
 
@@
 Thanks to the current generation of detectors, it is possible to obtain very high-resolution spectra in the \halpha and CO lines over most of the optical disks of galaxies.
-The higher resolution data
+The higher resolution data %PB sentence incomplete.
 
@@
 \subsection{Galaxy masses from stellar population modelling}
-
+%PB: quite a bit of repetition in the following sentences.
 Galaxies can be observed because of their stellar emission; stars radiate the energy produced from nuclear reactions in their cores. 
@@
 Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distributions of galaxies. 
-However, some fraction of the mass of galaxies consists of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants and should be considered in models.
+However, some fraction of the mass of galaxies consists of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants.
+These should be considered in models.
 Stellar population synthesis models are used to predict the SED of a stellar population using many physical parameters. 
@@
 They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density.
-To do so the surface density of stellar mass at each position is derived by 
+To do so, the surface density of stellar mass at each position is derived by: 
 \begin{equation}
@@
 \end{equation}
-where $\alpha$ and $\delta$ are position, right ascension and declination, respectively.
-$\Sigma_{{\mathrm M_\star}} (\alpha, \delta)$ is the stellar surface density.
-$\Sigma_{\lambda}(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L at an effective wavelength $\lambda$.
-In Equ.\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy.
+where $\alpha$ and $\delta$ are sky position (right ascension and declination, respectively),
+$\Sigma_{{\mathrm M_\star}} (\alpha, \delta)$ is the stellar surface density,
+$\Sigma_{\lambda}(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar $M/L$ at an effective wavelength $\lambda$.
+In Equ.\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in the galaxy.
 
-Peak of emission from evolved stars are in NIR part of spectrum.
-Therefore, many studies tried to make a map of stellar mass distribution using this bandpass within galaxies~\citep[e.g.,][]{Elmgreen84}.
-Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps thave a more accurate calibration.
-Fluxes from 3.6 and 4.5$\mu$m are suitable for calibration of the stellar mass, due to fact these two band-passes not only trace evolved stellar population but also they are almost insensitive to the emission from young stellar population or to dust absorption and emission.
-\cite{Zhu10} used the Sloan Digital Sky Survey~\citep[SDSS][]{York00} and the \Spitzer Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find calibration between galaxy luminosity and stellar mass.
-Using the M/L of galaxies, they found correlations between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulated these correlations as:
+The peak of emission from evolved stars is in the near-infrared part of the spectrum.
+Therefore, many studies tried to make a map of stellar mass distribution within galaxies using this bandpass~\citep[e.g.,][]{Elmgreen84}.
+Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps to make a more accurate calibration.
+Fluxes at 3.6 and 4.5$\mu$m are suitable for calibration of the stellar mass, due to fact these two band-passes not only trace evolved stellar population but also they are almost insensitive to the emission from young stellar population or to dust absorption and emission.
+\cite{Zhu10} used the Sloan Digital Sky Survey~\citep[SDSS][]{York00} and the \Spitzer Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find a calibration between galaxy luminosity and stellar mass.
+Using the $M/L$ of galaxies, they found correlations between the $K_s$ (2.2 $\mu$m) band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulated these correlations as:
 \begin{align}
@@
 
-\cite{Eskew12} tested the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and found an empirical relation between mass of the stars and the luminosities of stars as:
+\cite{Eskew12} tested the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and found an empirical relation between stellar mass and luminosities as:
 \begin{equation}
@@
 \end{equation}
-where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$/$\AA$.
-Equ.~\ref{equ: zhu1}--~\ref{equ: zhu3} have been derived from a large sample of galaxies, and were tested on different type of regions and galaxies. 
-on the other hand,~\cite{Eskew12} mentioned that since their calibration is based on data from Magellanic clouds this,
+where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$~\AA$^{-1}$.
+Equ.~\ref{equ: zhu1}--~\ref{equ: zhu3} have been derived from a large sample of galaxies, and were tested on different types of regions and galaxies. 
+On the other hand,~\cite{Eskew12} mentioned that since their calibration is based on observations of the Magellanic Clouds,
 measuring the stellar mass from Equ.~\ref{equ:eskew} might break down for highly star-forming regions; moreover, this equation has not tested on regions with different metallicity. 

### 2016-07-14 version0.0/intro0.01.tex

@@
  Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas and the mass of stars in galaxies.
- For decades, observational, theoretical and numerical studies have investigated star formation; nevertheless, their results are contrary.
+ For decades, observational, theoretical and numerical studies have investigated star formation;  in many cases, their results disagree with each other.
  Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
@@
 Then we study the grouped properties of the classified galaxies.
-We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}
+We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}.
 

### 2016-07-15 main.tex
Adding summary

--- 2016-07-09 version0.0/asli.tex
@@
 \usepackage{tocloft}
-\usepackage{amsmath}
-\usepackage{graphicx}
+\bibliographystyle{apj}
 \usepackage{natbib}
-\bibliographystyle{apj}
 \usepackage{times}
@@
 \usepackage{import}
-\usepackage[T1]{fontenc}
 \usepackage{ae,aecompl}
@@
 \usepackage{pdflscape}	% Landscape pages
+%\usepackage{booktabs,fixltx2e}
 \usepackage[flushleft]{threeparttable}
-\usepackage{pgffor}
-\usepackage{chapterbib}
-\usepackage{mwe}    % loads »blindtext« and »graphicx«
-\usepackage{subfig}
+\usepackage[T1]{fontenc}
 
@@
 %% corresponds to \spacing{1.5} and double spaced is \spacing{1.66}.
-\def\normalspacing{1.25} % default line spacing
+\def\normalspacing{1.5} % default line spacing
 
@@
 \setcounter{tocdepth}{3} % Number the subsubsections 
-\def\normalspacing{1.25} % default line spacing
+\def\normalspacing{1.5} % default line spacing
 
@@
 \newcommand{\firstname}{Sahar}
-\newcommand{\middlename}{}
+%\newcommand{\middlename}{}
 \newcommand{\lastname}{Rahmani}
@@
 \newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
-\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
+\newcommand{\thesisformat}{Integrated Article} %or Integrat
 \newcommand{\gyear}{\number\year}
@@
 %Type information about coauthorship here/
-Thanks to Sophia, Hossein and Els. 
+The work presented in this thesis has greatly benefited from advice by my supervisor Dr.
+Pauline Barmby and collaborators: Dr.
+Sofia Lianue, Dr.
+Hossein Teimoorinia, and Dr.
+Els Peeters.
+Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were greatly helpful.
+
+{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.
+
+{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.
+
+{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society.
 }
@@
 \begin{document}
-
 %% ***   NOTE   ***
@@
 \newcommand \kpc        {\,{\rm kpc}}
-\newcommand \sigmagas {$\Sigma_{\mathrm {gas }} $\ }
+\newcommand \sigmagas    {$\Sigma_{\mathrm{gas }} $\ }
 \newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
-\newcommand \eqsigmagas {\Sigma_{\mathrm {gas }}}
-\newcommand \sigmasfr {$\Sigma_{\mathrm {SFR }} $\ }
-\newcommand \eqsigmasfr {\Sigma_{\mathrm {SFR }}}
-\newcommand \sigmastar {$\Sigma_{\mathrm {star }} $\ }
-\newcommand \eqsigmastar {\Sigma_{\mathrm {star }}}
-\newcommand \halpha {H$\alpha $\ }
-\newcommand \um {$\mu$m\ }
-\newcommand \mice {$\mu$m}
-\newcommand \nprime {N$^\prime$}
-\newcommand \eqnprime {N^\prime}
+\newcommand{\eqsigmagas}    {\Sigma_{\mathrm {gas }}}
+\newcommand{\sigmasfr}   {$\Sigma_{\mathrm {sfr }} $\ }
+\newcommand{\eqsigmasfr}{\Sigma_{\mathrm{sfr }}}
+\newcommand{\sigmastar}    {$\Sigma_{\mathrm {star }} $\ }
+\newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
+\newcommand{\halpha}    {H$\alpha $\ }
+\newcommand{\um}    {$\mu$m\ }
+\newcommand{\mice} {$\mu$m}
+\newcommand{\nprime}{N$^\prime$}
+\newcommand{\eqnprime} {N^\prime}
+\newcommand{\degr} {$^{\circ}$}
+\newcommand{\arcmin} {$^{\prime}$}
+\newcommand {\arcsec} {$^{\prime\prime}$}
 \newcommand \Spitzer {{\it Spitzer }}
-\newcommand \Galex {GALEX }
+\newcommand \Galex {GALEX\ }
 \newcommand \Herschel {{\it Herschel }}
-\newcommand \sii {[S~{\textsc II}]} 
-\newcommand \oiii {[O~{\textsc III}]} 
-\newcommand \hi {H~{\textsc I}}
-\newcommand \hii {H~{\textsc II}}
-\newcommand \oii {[O~{\textsc II}]}
-\newcommand \nii {[N~{\textsc II}]}
+\newcommand \sii {[S~{\textsc ii}]} 
+\newcommand \oiii {[O~{\textsc iii}]} 
+\newcommand \hi {H~{\textsc i}}
+\newcommand \hii {H~{\textsc ii}}
+\newcommand \oii {[O~{\textsc ii}]}
+\newcommand \nii {[N~{\textsc ii}]}
 
@@
 
-%% This sets the page style and numbering for preliminary sections.
-\begin{preliminary}
 \defcitealias{Hossein12}{T12}
@@
 \defcitealias{Noll09}{N09}
+%% This sets the page style and numbering for preliminary sections.
+\begin{preliminary}
 
@@
 \include{intro0.0}
-%\include{paper1}
-%\include{paper3}
-%\include{paper2}
+\include{paper1}
+\include{paper3}
+\include{paper2}
+\include{summary}
 
@@
 \end{document}
+
+ed Article
+\newcommand{\gyear}{\number\year}
+\newcommand{\makecoauthor}{The work presented in this thesis has greatly benefited from advice by my supervisor Dr.
+Pauline Barmby and collaborators: Dr.
+Sofia Lianue, Dr.
+Hossein Teimoorinia, and Dr.
+Els peeters.
+Although I led the projects, performed the analysis and wrote the manuscripts, my worked greatly benefited from their suggestions and feedback on the analyses and manuscripts in chapters 2,3, and 4.\\
+Chapter 2: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.\\
+Chapter 3: Data Mining in Nearby Galaxies, will be submitted in the near future.\\
+Chapter 4: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society
+}
+\newcommand{\makeacknowlege} { 1) Pauline
+2) Els, Sophia, Hossein,
+3)I would like to thank all my Friends in Western.
+Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
+4) bacheha
+5) western ppl; Jodi, Brian, Henry, Phin,...
+6) Mohad, shahin, pejman, pouria, masood,babak
+7) fako famil
+}
+\newcommand{\makededications} {
+To my parents, my sisters, and Matin, for their unconditional love and support. 
+}
+\newcommand{\listappendixname}{List of Appendices}
+\newlistof{myappendices}{app}{\listappendixname}
+\newcommand{\myappendices}[1]{%
+\addcontentsline{app}{myappendices}{#1}\par}
+
+\renewcommand{\maketitle}
+{\begin{titlepage}
+   \setcounter{page}{1}
+   %% Set the line spacing to 1 for the title page.
+   %\begin{spacing}{1} 
+   \begin{large}
+   \begin{center}
+      \mbox{}
+      \vfill
+      {\MakeUppercase{\titl}}\\
+      \isdefinedspinetitle{\spinetitle}
+      (Thesis format: \thesisformat)\\
+      \vfill
+      by \\
+      \vfill
+      {\firstname} \underline{\lastname}\\
+      \vfill
+      Graduate Program in {\department}\\
+      \vfill
+		A thesis submitted in partial fulfillment\\
+		of the requirements for the degree of\\
+		\degree\\
+		\vfill
+		The School of Graduate and Postdoctoral Studies\\
+		The University of Western Ontario\\
+		London, Ontario, Canada\\
+		\vfill
+      {\copyright} {\authorname} {\gyear}  \\
+      \vspace*{.2in}
+   \end{center}
+   \end{large}
+%   \end{spacing}
+   \end{titlepage}
+
+}%\maketitle
+
+\newcommand{\makecert}{
+   \setcounter{page}{2}
+\vfill
+\begin{center}
+\large
+THE UNIVERSITY OF WESTERN ONTARIO\\
+School of Graduate and Postdoctoral Studies\\
+\vfill
+\textbf{CERTIFICATE OF EXAMINATION}
+\end{center}
+
+\vfill
+\begin{table}[ht]
+\begin{minipage}[t]{0.5\linewidth} %tabular instead?
+\begin{tabular}{l}
+\underline{Supervisor:}\vspace{0.35in}
+\isdefinedsig{\super}
+\isco{\superc}
+\isjoint{\superj}
+\isalt{\supera}
+\underline{Supervisory Committee:}\vspace{0.35in}
+\isdefinedsig{\sco}\vspace{0.15in}
+\isdefinedsig{\sct}
+\end{tabular}
+\vfill
+\end{minipage}
+\hspace{0.5in}
+\begin{minipage}[t]{0.5\linewidth}
+\begin{tabular}{l}
+\underline{Examiners:} \\\vspace{.5cm}
+\isdefinedsig{\examo}\\
+\isdefinedsig{\examt}\\
+\isdefinedsig{\examth}\\
+\isdefinedsig{\examf}
+\end{tabular}
+\vfill
+\end{minipage}
+\vfill
+\end{table}
+\vfill
+\begin{center}
+The thesis by \\ \vfill
+\textbf{\firstname{} \middlename{} \underline{\lastname}}\\
+\vfill
+entitled:\\\vfill
+\textbf{\titl}\\\vfill
+is accepted in partial fulfillment of the \\
+requirements for the degree of\\
+\degree\\
+\end{center}
+\begin{table}[ht]
+\begin{minipage}[t]{0.5\linewidth}
+\begin{tabular}{l}
+\dots\dots\dots\dots\dots\\
+Date
+\end{tabular}
+\end{minipage}
+\hspace{0.5in}
+\begin{minipage}[t]{0.5\linewidth}
+\begin{tabular}{l}
+\dots\dots\dots\dots\dots\dots\dots\dots\dots\dots\\
+Chair of the Thesis Examination Board
+\end{tabular}
+\end{minipage}
+\end{table}
+
+}
+
+\makeatother
+\begin{document}
+%% ***   NOTE   ***
+%% You should put all of your '\newcommand', '\newenvironment', and
+%% '\newtheorem's (in other words, all the global definitions that you
+%% will need throughout your thesis) in a separate file and use
+%% "\input{filename}" to input it here.
+
+\newcommand \kpc        {\,{\rm kpc}}
+\newcommand \sigmagas    {$\Sigma_{\mathrm{gas }} $\ }
+\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
+\newcommand{\eqsigmagas}    {\Sigma_{\mathrm {gas }}}
+\newcommand{\sigmasfr}   {$\Sigma_{\mathrm {sfr }} $\ }
+\newcommand{\eqsigmasfr}{\Sigma_{\mathrm{sfr }}}
+\newcommand{\sigmastar}    {$\Sigma_{\mathrm {star }} $\ }
+\newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
+\newcommand{\halpha}    {H$\alpha $\ }
+\newcommand{\um}    {$\mu$m\ }
+\newcommand{\mice} {$\mu$m}
+\newcommand{\nprime}{N$^\prime$}
+\newcommand{\eqnprime} {N^\prime}
+\newcommand{\degr} {$^{\circ}$}
+\newcommand{\arcmin} {$^{\prime}$}
+\newcommand {\arcsec} {$^{\prime\prime}$}
+\newcommand \Spitzer {{\it Spitzer }}
+\newcommand \Galex {GALEX\ }
+\newcommand \Herschel {{\it Herschel }}
+\newcommand \sii {[S~{\textsc ii}]} 
+\newcommand \oiii {[O~{\textsc iii}]} 
+\newcommand \hi {H~{\textsc i}}
+\newcommand \hii {H~{\textsc ii}}
+\newcommand \oii {[O~{\textsc ii}]}
+\newcommand \nii {[N~{\textsc ii}]}
+
+\newcommand \aaj {A\&A}
+\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
+\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
+\newcommand \afz {Afz}%: Astrofizika
+\newcommand \aj {AJ}%: Astronomical Journal (the)
+\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
+\newcommand \apj {ApJ}
+\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
+\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
+\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
+\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
+\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
+\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
+\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
+\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
+%\newcommand {Nature}%(do not abbreviate)
+\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
+\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
+\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
+\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
+%\newcommand {Science }%}%(do not abbreviate)
+\newcommand \sva {SvA}%: Soviet Astronomy
+\newcommand \aap {APP} %:American Academy of Pediatrics
+\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
+
+\defcitealias{Hossein12}{T12}
+\defcitealias{Kinney96}{K96}
+\defcitealias{Noll09}{N09}
+%% This sets the page style and numbering for preliminary sections.
+\begin{preliminary}
+
+%% This generates the title page from the information given above.
+\maketitle
+\addcontentsline{toc}{chapter}{Certificate of Examination}
+\makecert
+\newpage
+\addcontentsline{toc}{chapter}{Co-Authorship Statement}
+\coauthor{\makecoauthor}  %comment this out if none
+\newpage
+\addcontentsline{toc}{chapter}{Acknowledgements}
+\acknowlege{\makeacknowlege}	%as above
+\newpage
+\addcontentsline{toc}{chapter}{Dedication}
+\dedications{\makededications}
+\newpage
+\addcontentsline{toc}{chapter}{Abstract}
+\Large\begin{center}\textbf{Abstract}\end{center}\normalsize
+%%  ***  Put your Abstract here.   ***
+%% (150 words for M.Sc. and 350 words for Ph.D.)
+Understanding the process of star formation is one of the key steps in understanding the formation and evolution of galaxies.
+In this thesis, I address the empirical star formation laws, and study the properties of galaxies that can affect the star formation rate.
+
+The Andromeda galaxy (M31) is the nearest large spiral galaxy, and Therefore, high resolution images of this galaxy are available.
+These images provide data from various regions with different physical properties.
+Star formation rate and gas mass surface densities of M31have been measured using three different methods, and have been used to compare different star formation laws over the whole galaxy and in spatially-resolved regions.
+Using hierarchical Bayesian regression analysis, I conclude that there is a correlation between surface density of star formation and the stellar mass surface density.
+A weak correlation between star formation rate, stellar mass and metallicity is also found.
+
+To study the effect of other properties a galaxy on the star formation rate, I utilize an unsupervised data mining method (specifically the self-organizing map) on measurements of both nearby and high-redshift galaxies.
+Both observed data and derived quantities (e.g. star formation rate, stellar mass) of star-forming regions in M31 and the nearby spiral galaxy M101 are used as inputs to the self-organizing map.
+Clustering the M31 regions in the feature space reveals some (anti)-correlations between the properties the galaxy, which are not apparent when considering data from all regions in the galaxy. 
+The self-organizing map can be used to predict star formation rates for spatially-resolved regions in galaxies using other properties of those regions.
+
+I also apply the self-organizing map method to spectral energy distributions of high-redshift galaxies.
+Template spectra made from galaxies with known morphological type are used to train self-organizing maps.
+The trained maps are used to classify a sample of galaxy spectral energy distributions derived from fitting models to photometry data of 142 high-redshift galaxies.
+The grouped properties of the classified galaxies are found to be more tightly correlated in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
+
+\vfill
+\textbf{Keywords:} Nearby galaxies: M31, M101, Star formation rate, stellar mass, ISM, data mining
+\newpage
+\tableofcontents\newpage
+\newpage
+\addcontentsline{toc}{chapter}{List of Figures}
+\listoffigures
+\newpage
+\addcontentsline{toc}{chapter}{List of Tables}
+\listoftables\newpage
+\addcontentsline{toc}{chapter}{List of Appendices}
+\listofmyappendices\newpage
+%\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
+%\large List of Abbreviations, Symbols, and Nomenclature \normalsize
+%\newpage
+\end{preliminary}
+%% End of the preliminary sections: reset page style and numbering.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                    %%
+%%                    ***   I M P O R T A N T   ***                   %%
+%%                                                                    %%
+%% Put your Chapters here; the easiest way to do this is to keep each %%
+%% chapter in a separate file and \include all the files right here.  %%
+%% Note that each chapter file should start with the line             %%
+%% "\chapter{ChapterName}".  Note that using "\include" instead of    %%
+%% "\input" makes each chapter start on a new page.                   %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ \import{../version0.0/}{intro0.0}
+% \include{paper1}
+% %\include{paper3}
+% \include{paper2}
+% \include{summary}
+
+%% This adds a line for the Bibliography in the Table of Contents.
+%\addcontentsline{toc}{chapter}{Bibliography}
+%% ***   Set the bibliography style.   ***
+%\bibliographystyle{apj.bst} % (change according to your preference)
+%%% ***   Set the bibliography file.   ***
+%\bibliography{westernthesis}
+
+%Appendices.
+\begin{appendices}
+\include{appendixa}
+\end{appendices}
+
+%CV only relevant stuff... not full CV.
+% \addcontentsline{toc}{chapter}{Curriculum Vitae}
+% \chapter*{Curriculum Vitae}
+% \begin{table}[ht]
+% \begin{tabular}{ll}
+% \textbf{Name:} & \firstname{} \lastname\\\\
+% \textbf{Post-Secondary} & La La School\\
+% \textbf{Education and}& La La Land\\
+% \textbf{Degrees:}& 1996 - 2000 M.A.\\\\
+% & University of Western Ontario\\
+% & London, ON\\
+% & 2008 - 2012 Ph.D.\\\\
+% \textbf{Honours and}& NSERC PGS M\\
+% \textbf{Awards:}& 2006-2007\\\\
+% \textbf{Related Work}& Teaching Assistant\\
+% \textbf{Experience:}& The University of Western Ontario\\
+% & 2008 - 2012\\
+% \end{tabular}
+% \end{table}
+% \subsubsection*{Publications:}
+% La La
+\end{document}

### 2016-07-15 version0.0/appendixa.tex
Adding summary

--- 2016-06-11 version0.0/appendixa.tex
@@
-\chapter{Appendix}
-\section{SFR from H$\alpha$ plus 24 \um: procedure and result}
+\chapter{SFR from H$\alpha$ plus 24 \um: procedure and result}
+\pagestyle{plain}
 \label{app:halpha}
-
+\myappendices{
 As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps.
 These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive.
-Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the [N II] 6583~\AA\ line.
+Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.
 
@@
 Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image.
-At the end, we masked out all the foreground and saturated regions which include a $10\arcmin \times 10\arcmin$ region in the centre of the galaxy.
-To account for the flux contribution of the [N II] emission we used the flux ratio ${\rm [NII]}/{\rm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map.
+At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin region in the centre of the galaxy.
+To account for the flux contribution of the [N II] emission we used the flux ratio ${\mathrm \nii}/{\mathrm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map.
 We created the final mosaic image, Figure~\ref{fig:halpha}, using the Montage program \citep{Berriman08}.
@@
 In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
-The fitting results using SFR(\halpha $+$ 24~\um) are more or less the same as the other two SFR tracers.
+The fitting results using SFR(\halpha $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers.
 The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data.
-Thus we did not include the SFR(\halpha $+$ 24 \um) in our final analysis.
+Thus we did not include the SFR(\halpha $+$ 24~$\mu$m) in our final analysis.
 
@@
 
-\section{Results of training for one-dimensional self-organizing maps}
-\label{app: high_Z_1d_soms}
-As mentioned in Sec.~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$.
-In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.
-
-\label{app: 1d}
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_4.png}
-            %\caption{$1\times4$ weight map}
-             %\label{fig: 1by4T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_4.png}
-             %\caption{$1\times4$ hits map}
-             %\label{fig: 1by4Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times4$~grid.}
-         \label{fig: 1by4T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_5.png}
-            %\caption{$1\times5$ weight map}
-             %\label{fig: 1by5T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_5.png}
-             %\caption{$1\times5$ hits map}
-             %\label{fig: 1by5Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times5$~grid.}
-         \label{fig: 1by5T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_6.png}
-            %\caption{$1\times6$ weight map}
-             %\label{fig: 1by6T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_6.png}
-             %\caption{$1\times6$ hits map}
-             %\label{fig: 1by6Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times6$~grid.}
-         \label{fig: 1by6T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_7.png}
-            %\caption{$1\times7$ weight map}
-             %\label{fig: 1by7T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_7.png}
-             %\caption{$1\times7$ hits map}
-             %\label{fig: 1by7Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times7$~grid.}
-         \label{fig: 1by7T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_8.png}
-            %\caption{$1\times8$ weight map}
-             %\label{fig: 1by8T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_8.png}
-             %\caption{$1\times8$ hits map}
-             %\label{fig: 1by8Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times8$~grid.}
-         \label{fig: 1by8T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_9.png}
-            %\caption{$1\times9$ weight map}
-             %\label{fig: 1by9T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_9.png}
-             %\caption{$1\times9$ hits map}
-             %\label{fig: 1by9Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times9$~grid.}
-         \label{fig: 1by9T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_10.png}
-            %\caption{$1\times10$ weight map}
-             %\label{fig: 1by10T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_10.png}
-             %\caption{$1\times10$ hits map}
-             %\label{fig: 1by10Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times10$~grid.}
-         \label{fig: 1by10T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_11.png}
-            %\caption{$1\times11$ weight map}
-             %\label{fig: 1by11T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_11.png}
-             %\caption{$1\times11$ hits map}
-             %\label{fig: 1by11Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times11$~grid.}
-         \label{fig: 1by11T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_12.png}
-            %\caption{$1\times12$ weight map}
-             %\label{fig: 1by12T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_12.png}
-             %\caption{$1\times12$ hits map}
-             %\label{fig: 1by12Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times12$~grid.}
-         \label{fig: 1by12T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_15.png}
-            %\caption{$1\times15$ weight map}
-             %\label{fig: 1by15T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_15.png}
-             %\caption{$1\times15$ hits map}
-             %\label{fig: 1by15Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times15$~grid.}
-         \label{fig: 1by15T}
-    \end{figure}
-
-    \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_20.png}
-            %\caption{$1\times20$ weight map}
-             %\label{fig: 1by20T}
-        \end{subfigure}
-        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
-             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_20.png}
-             %\caption{$1\times20$ hits map}
-             %\label{fig: 1by20Thits}
-        \end{subfigure}
-                \caption{Results of training network in $1\times20$~grid.}
-         \label{fig: 1by20T}
-    \end{figure}
+}

### 2016-07-15 version0.0/appendixb.tex
Adding summary

\chapter{2-Dimensional networks from subsets of M31}
\pagestyle{plain}
\label{sec: app_2d_soms_SOMN}
\newpage
\myappendices{

        We removed IRAC 5.7 $\mu$m; \sii~continuum and \oiii~continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, \oiii~continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}. 
        IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
        For subset sample 7 (Table~\ref{tab: subset7}) we removed \sii~flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
        The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.

        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
        Since region 4 and 5 have a similar \oiii~and \sii~continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
        moreover, similar to regions 4 and 5, \oiii~and \sii~continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions. Therefore, they moved further from each other. 
         \import{../image_paper3/text_files/tables/}{subset2.tex}
        \import{../image_paper3/text_files/image_texts/}{subset2.tex}
        \import{../image_paper3/text_files/tables/}{subset3.tex}
        \import{../image_paper3/text_files/image_texts/}{subset3.tex}

        In the results from the subset 4 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
        These two regions have distinct metallicity, removing metallicity from input data caused these two stay in a closer neurons. 
        Since regions 1 and 2 have similar metallicity and total PAHs, and their total stellar mass are comparable, removing these values from input data made the position of the regions 1 and 2 moved further from each other. 
        \import{../image_paper3/text_files/tables/}{subset4.tex}
        \import{../image_paper3/text_files/image_texts/}{subset4.tex}

        The positions of the region 8 and 5 are moved closer in Fig.~\ref{fig: subset7}.
        Both of these regions are around the inner ring inside the galaxy.
        Therefore, both of them have similar values in most of the input parameters.
        However, they have very different fluxes in IRAC 5.7 $\mu$m and \sii~continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
        In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
        \import{../image_paper3/text_files/tables/}{subset7.tex}
        \import{../image_paper3/text_files/image_texts/}{subset7.tex}
        }

### 2016-07-15 version0.0/appendixc.tex
Adding summary

\chapter[Self-Organizing Map for High-redshift galaxies]{Results of Training High-redshift Galaxies for one-dimensional self-organizing maps}
\pagestyle{plain}
\label{app: high_Z_1d_soms}
\newpage
\myappendices{
As mentioned in Sec.~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$. In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.

\label{app: 1d}
    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_4.png}
            %\caption{$1\times4$ weight map}
             %\label{fig: 1by4T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_4.png}
             %\caption{$1\times4$ hits map}
             %\label{fig: 1by4Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times4$~grid.}
         \label{fig: 1by4T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_5.png}
            %\caption{$1\times5$ weight map}
             %\label{fig: 1by5T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_5.png}
             %\caption{$1\times5$ hits map}
             %\label{fig: 1by5Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times5$~grid.}
         \label{fig: 1by5T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_6.png}
            %\caption{$1\times6$ weight map}
             %\label{fig: 1by6T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_6.png}
             %\caption{$1\times6$ hits map}
             %\label{fig: 1by6Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times6$~grid.}
         \label{fig: 1by6T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_7.png}
            %\caption{$1\times7$ weight map}
             %\label{fig: 1by7T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_7.png}
             %\caption{$1\times7$ hits map}
             %\label{fig: 1by7Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times7$~grid.}
         \label{fig: 1by7T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_8.png}
            %\caption{$1\times8$ weight map}
             %\label{fig: 1by8T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_8.png}
             %\caption{$1\times8$ hits map}
             %\label{fig: 1by8Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times8$~grid.}
         \label{fig: 1by8T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../image_paper2/1d/apps/dist_1_by_9.png}
            %\caption{$1\times9$ weight map}
             %\label{fig: 1by9T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/apps/hit_t_1_by_9.png}
             %\caption{$1\times9$ hits map}
             %\label{fig: 1by9Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times9$~grid.}
         \label{fig: 1by9T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_10.png}
            %\caption{$1\times10$ weight map}
             %\label{fig: 1by10T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_10.png}
             %\caption{$1\times10$ hits map}
             %\label{fig: 1by10Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times10$~grid.}
         \label{fig: 1by10T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_11.png}
            %\caption{$1\times11$ weight map}
             %\label{fig: 1by11T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_11.png}
             %\caption{$1\times11$ hits map}
             %\label{fig: 1by11Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times11$~grid.}
         \label{fig: 1by11T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_12.png}
            %\caption{$1\times12$ weight map}
             %\label{fig: 1by12T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_12.png}
             %\caption{$1\times12$ hits map}
             %\label{fig: 1by12Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times12$~grid.}
         \label{fig: 1by12T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_15.png}
            %\caption{$1\times15$ weight map}
             %\label{fig: 1by15T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_15.png}
             %\caption{$1\times15$ hits map}
             %\label{fig: 1by15Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times15$~grid.}
         \label{fig: 1by15T}
    \end{figure}

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/dist_1_by_20.png}
            %\caption{$1\times20$ weight map}
             %\label{fig: 1by20T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
             \includegraphics[width=\textwidth,height=2.5cm]{../image_paper2/1d/apps/hit_t_1_by_20.png}
             %\caption{$1\times20$ hits map}
             %\label{fig: 1by20Thits}
        \end{subfigure}
                \caption{Results of training network in $1\times20$~grid.}
         \label{fig: 1by20T}
    \end{figure}
    }

### 2016-07-15 version0.0/asli.tex
finishing intro0.0
finishing edits on intro
Adding summary

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% University of Western Ontario Thesis Template
-% By: Justin Quinn Veenstra, 2010
-% With thanks to Mr. (soon to be Dr.) Will Robertson.
-
 \documentclass[12pt,twoside]{report}
@@
 \usepackage{amsmath}
-\usepackage{graphicx}
 \usepackage{natbib}
@@
 \usepackage{chapterbib}
-\usepackage{mwe}    % loads »blindtext« and »graphicx«
-\usepackage{subfig}
-
 \makeatletter
@@
 \newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
-\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
+\newcommand{\spinetitle}{Extragalactic Star Formation}%only if the above is more than 60 characters
 \newcommand{\thesisformat}{Integrated Article} %or Integrated Article
@@
 %Type information about coauthorship here/
-Thanks to Sophia, Hossein and Els. 
+The work presented in this thesis has greatly benefited from advice by my supervisor Dr.
+Pauline Barmby and collaborators: Dr.
+Sofia Lianue, Dr.
+Hossein Teimoorinia, and Dr.
+Els Peeters.
+Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were greatly helpful.
+
+{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.
+
+{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.
+
+{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society.
 }
+
 \newcommand{\makeacknowlege} { 1) Pauline
@@
 3)I would like to thank all my Friends in Western.
-Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
+Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam(s) , Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
 4) bacheha
@@
 \newcommand{\makededications} {
-To my parents, my sisters, and Matin, for their unconditional love and support. 
+
+\emph{To my parents, my sisters,}
+
+\emph{\& Matin,}
+
+\emph{for their unconditional love and support.}
+
 }
@@
 \underline{Supervisor:}\vspace{0.35in}
-\isdefinedsig{\super}
-\isco{\superc}
-\isjoint{\superj}
-\isalt{\supera}
+\isdefinedsig{\super}\\
 \underline{Supervisory Committee:}\vspace{0.35in}
@@
 \include{intro0.0}
-%\include{paper1}
-%\include{paper3}
-%\include{paper2}
+\include{paper1}
+\include{paper3}
+\include{paper2}
+\include{summary}
 
 %% This adds a line for the Bibliography in the Table of Contents.
-%\addcontentsline{toc}{chapter}{Bibliography}
-%% ***   Set the bibliography style.   ***
-%\bibliographystyle{apj.bst} % (change according to your preference)
-%%% ***   Set the bibliography file.   ***
-%\bibliography{westernthesis}
+% \addcontentsline{toc}{chapter}{Bibliography}
+% %% ***   Set the bibliography style.   ***
+% \bibliographystyle{apj.bst} % (change according to your preference)
+% %%% ***   Set the bibliography file.   ***
+% \bibliography{western_bib}
+
+% \addcontentsline{toc}{section}{Bibliography}
+% \bibliographystyle{apj.bst}
+% \bibliography{western_bib.bib}
 
 %Appendices.
+
+% %Appendices.
 \begin{appendices}
 \include{appendixa}
+\include{appendixb}
+\include{appendixc}
 \end{appendices}

### 2016-07-15 version0.0/intro0.01.tex
Adding summary

--- 2016-07-14 version0.0/intro0.01.tex
@@
 Nearly all the information we can obtain from galaxies other than our own comes from their light.
-Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
-a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
-Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
+Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
+a plot of brightness/flux density of galaxies as a function of wavelength, call a spectral energy distribution (SED), is a useful tool to understand galaxies. 
+Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
 Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
-Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.
+Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
 
@@
 Then these clumps continue to become denser and turn into protostars. 
-Since the protostars have a higher mass than their surroundings, more gas from GMCs accretes on to protostars.
+Since the protostars have a higher mass than their surroundings, more gas from GMCs accretes onto protostars.
 This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).
@@
 The amount of metals in stars affects their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
-For example, low metallicity stars tend to have lower mass loss from stellar winds than those with higher metallicity.
+For instance, low metallicity stars tend to have lower mass loss via stellar winds than those with higher metallicity.
 Observations show that massive low metallicity stars rotate faster.
-Being more massive at the end of their evolutionary track gives massive low metallicity stars a lower chance to explode and become a supernova.
+Being more massive at the end of their evolutionary tracks gives massive low metallicity stars have a lower chance to explode and become a supernova.
 
@@
 Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
-Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
+Other wavelengths regimes in galaxy SEDs (e.g. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
 The general shape of SEDs mirrors the morphological types of galaxies: starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission.
@@
 It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
-Some of the physical properties of gaalxies must be assumed as input data to find the best SED, and others are derived from SED results~\citep[see ][for more detail]{Walch08}.
+Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see ][for more detail]{Walch08}.
 For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
-By integrating the star formation history over a specific time scale, SFR can be derived. %PB: please check: integrate SFH to get SFR, or SFR to get SFH?
-Knowing the stellar mass to light ratio, one can use the observed luminosity to calculate stellar mass in galaxies.
+By integrating star formation history over a specific time scale, SFR can be derived. %PB: please check: integrate SFH to get SFR, or integrate SFR to get SFH?
+Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.
 
-The formation of stars in galaxies depends on many parameters, including gas, stellar mass, metallicity, dust, the galaxy's morphology and the location of the star forming region inside the galaxy.
+The formation of stars in galaxies depends on many parameters including gas mass, stellar mass, metallicity, dust, the galaxy's morphology, and the location of the star forming region inside the galaxy.
 In extragalactic astronomy, measuring the rate at which stars form is uncertain and relies upon theoretical models and observational data.
@@
 Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
-%% We or I?!
+%% We or I?! %PB: use I
 
@@
 The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
-The gas in the ISM of galaxies is mostly made of hydrogen and helium with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse regions.
+The gas in the ISM of galaxies is mostly made of hydrogen and helium, with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse (diffused?) regions.
 Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or a hot intercloud medium.
-Dust mostly contains silicate and graphite grains, and can be seen in dark clouds or galactic cirrus. %PB: please check changes to this sentence
-Emission lines from atoms or ions (i.e \hii~regions) in hot gas, lines from molecules in cold clouds and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
+Dust is mostly comprised of silicates, and graphite grains can be seen in dark clouds or galactic cirrus.
+Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds, and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
 Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).
@@
 In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
-The source of dust thermal emission is heating from stars and the shape of the continuum depends on size of the grain.
+The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
 Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}. 
 Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
-Dust is the main source of extinction and reddening of starlight (See Sec.\ref{sec: extinction} for more information).
+Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).
 
@@
 Neutral atomic and molecular hydrogen are the most common components of the ISM. 
-Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements (mostly helium), which cannot be observed directly.
+Therefore, to produce a total gas mass map in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements (mostly helium) which cannot be observed directly.
 Another way to do the mapping is to assume that the ratio of total gas to dust is constant across the galaxy, and convert dust observations to a map of total gas mass.
@@
 This problem shows itself for distant galaxies more than nearby galaxies. 
-As a result, using images of molecular and atomic clouds to measure surface density of gas in galaxies' ISM is limited by telescopes' resolution.
+As a result, using images of molecular and atomic gas clouds to measure surface density of gas in ISM is limited to the telescopes' resolution.
 
@@
 where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
-It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
-
+It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(k) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
 For a uniform cloud with a radius $R$, the CO luminosity is given by:
@@
 Problems regarding metallicity are not yet resolved and it is still not clear whether the conversion factor is global or local. 
-Extragalactic investigations have been limited to nearby galaxies due to technical problems regarding resolution and sensitivity of the telescopes. 
+Extragalactic investigations have been limited to nearby galaxies due to resolution and sensitivity of telescopes. 
 To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40 pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.
 
-Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
+%%%and now
+
+Atomic gas in galaxies are dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
 Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
@@
 \end{equation}
-where $T_{\mathrm B}$ is the temperature brightness in K and dV is in km~s$^{-1}$, with the integral over the line profile. 
+where $T_{\mathrm B}$ is the temperature brightness in Kelvins and dV is in Kms$^{-1}$, with the integral over the line profile. 
 These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
@@
 \cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
-The Herschel Space Telescope \cite{Pilbratt10} measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
+The Herschel Space Telescope \cite{Pilbratt10} has measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
 This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
-The observed FIR flux has almost no dependence on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary.
-The other important advantage is that this method solves the newly-found problem of the ``dark gas" in galaxies. 
-Dark gas is a significant fraction of gas in galaxies which is traced by neither 21-cm emission nor CO emission~\citep{Abdo10}. 
-As such it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
+The observed FIR flux has almost no dependency on distance, thus, one of the advantages of using the dust emission as a tracer of the gas mass is that unlike the direct method, high spatial resolution is not necessary.
+The other important advantage is that this method solves the newly-found problem of ``dark gas" in galaxies. 
+Dark gas is a significant fraction of gas in galaxies which can be traced by neither the 21-cm emission nor the CO emission~\citep{Abdo10}. 
+As such, it is very difficult to detect with telescopes, but an accurate gas to dust ratio can lead to an accurate estimate of dark gas mass in galaxies.
 
-There are disadvantages of the use of the gas to dust ratio to trace gas in the ISM.
+There are disadvantages in using the gas to dust ratio to trace gas in the ISM.
 In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
 \cite{Draine03} pointed out that the former approach is uncertain because of the uncertainly in the radiative efficiency of dust grains. 
-Measuring the gas to dust ratio in galaxies are not accurate, neither~\citep{Hildebran83}, which means that there are problems in both steps. 
+Measuring the gas to dust ratio in galaxies are not accurate either~\citep{Hildebran83}, which means that there are problems in both steps. 
 In addition, the dust method has two major practical problems: firstly, to apply this method, knowing the temperature of the dust is necessary. 
@@
 The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-This method is the best alternative for measuring the total gas in galaxies where there are no observations of CO or \hi~emission.
+This (MH: This method? what does this refer to?) method is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.
 
@@
 Dust in ISM affects stellar emission by attenuating, scattering or absorption.
-Attenuation refers to the effects of dust with embedded light sources distributed throughout. 
+Attenuation refers to the effects of dust with embedded light sources distributed throughout. (MH Very unclear sentence)
 The dust itself can be clumpy or smooth. 
-The effect of dust clouds with embedded light sources on the distribution of the light is called attenuation.
-The dust cloud could have any distribution and be clumpy or smooth.
-Since both light sources and dust have an extended distribution, the relative locations of the dust and light sources affect the net absorbed and scattered light.
-The other parameter that is important for the scattering and absorption is the relative position of dust and observer.
+Effect of dust clouds with embedded light sources on distribution of the light is called attenuation. (MH I though you defined attenuation two sentences ago, albeit unclearly.)
+The dust cloud could have any distribution and be clumpy or smooth. (MH Deja vu)
+Since both light source and dust have extended distribution, the relative location of the dust and light source affect the net absorbed and scattered light.
+The other parameters that are important for the scattering and absorption is the relative position of dust and observer.
 When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
-This is the typical situation that occurs when studying galaxies or extended regions within galaxies.
+This is the typical occurring situation when studying galaxies or extended regions within galaxies.
 
-Extinction happens when there is a combination of both absorption and scattering of radiation by dust and varies with the wavelength of emission; UV light passing through dust is more affected than visible light.
+Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
+This effect grows inversely with the wavelength.
 Extinction can be defined as a reduction of the original intensity caused by dust:
@@
 \label{equ: extinction}
-{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}]
+{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)exp[-\tau_{\lambda}],
 \end{equation}
-where I$(\lambda)$ is the observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is the intensity of light before passing through dust, and $\tau_{\lambda}$ is the otpical depth at wavelength $\lambda$.
-The extinction depends also on the size of grains and their extinction cross section.
-For measuring SFR using various wavebands, 
-the decrease in the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR. 
-% By converting Equ.~\ref{equ: extinction} to magnetidue system:
-% \begin{equation}
-%      {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda}  = -2.5\log(\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)})
-% \end{equation}
-% and by substituting $\frac{{\mathrm I}(\lambda)}{{\mathrm I}_0(\lambda)}$ with $exp[-\tau_{\lambda}]$, we have:
-% \begin{equation}
-% \begin{split}
-%     {\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = -2.5\log(exp[-\tau_{\lambda}]) \\
-%               & = 1.086\tau_{\lambda}
-% \end{split}
-% \end{equation}
-% By defining ${\mathrm m}_{\lambda} - {\mathrm m_0}_{\lambda} & = {\mathrm A}_{\lambda}$  extinction in magnitude is A$_{\lambda} = 1.086\tau_{\lambda}$.
-
-% To describe the decrease in the intensity of the original beam when it passes through a region where dust particles are present while taking into account the radiation added to the beam by scattering into the line of sight, an integro-differential equation of the radiative transfer of light through dust is used.
-% PB: "beam" is jargon, change to something else.
-Simplify this sentence.
-% At UV/optical/near-IR wavelengths, the radiative transfer equation is: %PB: why does this eqn only apply at UV/opt/NIR? 
-% \begin{equation}
-% \frac{dI_{\nu}}{d\tau} = -I_{\nu}  + \frac{a_{\nu}}{\pi} \int I_{\nu}\phi(\nu,\cos \Theta)d\Omega
-% \end{equation}
-% where I$_{\nu}$ is the intensity of radiation and $\tau$ is the dust's optical depth.
-% $a_{\nu}$ is the dust albedo,  the ratio of the scattering coefficient to the sum of the scattering and absorption coefficients. 
-% $\phi(\nu,\cos \Theta)$ is the scattering phase function, and $\Theta$ is the angle between the scattered photon and the line of sight. %PB: what is \phi? Need to explain at least a little
-% Both $a_{\nu}$ and $\phi(\nu,\cos \Theta)$ are described in more detail in~\citep{Draine03}. 
-% The source function, i.e., the dust emission, which usually has small values for wavelengths shorter than a few $\mu$m, is neglected in the equation above.
-%PB: why no dust emission at short wavelengths?
-(temperature)
-% This decrease in the intensity of the stellar radiation must be calculated and corrected for different emission; otherwise, there will be an underestimation of the star formation rate.
-%PB: what do you mean by "different emission" in this sentence?
+where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction in $\lambda$.
+The extinction also depends on size of grains and extinction cross section.
+For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.
 
@@
 
-In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using  Bremsstrahlung emission.
+In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission.
 Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
 Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
-The peak of emission of young, hot, and massive stars is at UV wavelengths, which makes them an ideal tracer of the current SFR.
+Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
 One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer.
-By knowing the IMF, the number of massive stars can be used to extrapolate to the total number of stars formed in a given star-forming region.
+By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
 To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
@@
 Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
-One of the most fundamental and difficult questions that a complete theory of star formation must answer is ``what is the stellar initial mass distribution?'' of a star forming region.
+One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
 Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
@@
 
-In the late 70s, it was recognised that the assumption of a single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
+In the late 70s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}.
 Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
@@
 Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
-Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, can be converted from the Kroupa IMF  to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
-In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8~M$_\odot$.
-\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins, especially at the high-mass end.
+Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
+In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8M$_\odot$.
+\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.
 
@@
 
-Since in using SFR calibration for different galaxies, we assume the initial mass function is universal, careful measurement of the IMF is a key factor in understanding the star formation rate. 
+Since in using SFR calibration for different galaxies, we assume the initial mass function is universal, careful measurement of the IMF is the key factor in understanding the star formation rate. 
 In distant galaxies, only massive stars can be detected; therefore, the IMF must be assumed to include all stellar mass ranges in the SFR calibrations. 
@@
 The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
-These objects are mostly a few million years old and  are usually referred to as young stellar objects (YSOs). 
+These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
 Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
@@
 where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
-$<$M$>$ is the mean mass of YSO which depends on the IMF; considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
+$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
 $\tau$ is the lifetime of the YSO  $\tau \sim 2$Myr~\citep{Evans09}. 
-Since our current devices cannot resolve individual YSOs in distant galaxies, this method can only be applied to the Milky Way and its neighbourhood.
+Since our current devises cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
 
 In theory, for any system with high enough spatial resolution, counting YSOs can be used as a tracer of the star formation. 
-However, considering the limited capabilities of present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky Way with a distance of 0.05 Mpc) cannot be resolved.
-Therefore, most studies use the emission from energetic young stars as a tracer of the SFR. 
-% Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
-% \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to produce spatially and age-resolved maps of star formation in nearby galaxies. 
-% More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}. %PB: I think you should give a one-sentence summary of the method here. 
-%Sr: I think later whether I want to keep this section or not.
-\subsubsection{Unresolved Star Formation Indicators}
+However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky way with distance of 0.05 Mpc) can not be resolved.
+Therefore, most studies use the emission from the energetic young stars as a tracer of the SFR.
 
- In star-forming regions farther away than the Magellanic Clouds, the spatial resolution of currently-available observations is not high enough to find all the young stellar objects. 
- In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
-\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar population synthesis models~\citep[e.g.,][]{Bruzual93}.
-
-In unresolved systems, SFR indicators can be divided into local and global indicators. 
-The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
-Local calibrations are used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
-Limitations in the spatial resolution of observational data on the one hand, and the broader applicability to distant galaxy populations on the other, have in the past brought more attention to the calibrations of global SFR compared to local SFR.
-Because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.
-
-\subsubsection*{SFR Indicators Based on Single-Band Emission}
-
-In order to derive conversions between the luminosity in specific wavelengths and the SFR, stellar population synthesis models are used~\citep{Kennicutt98b}. 
-The general form of a SFR calibration using single-band emission is: 
-\begin{equation}
-\label{equ: sfrsingle}
-{\rm SFR}(\lambda)= CL(\lambda)
-\end{equation}
-where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}).
-The constant $C$ varies for different wavelengths, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation is assumed to remain constant. 
-Table~\ref{table1}, from \cite{Calzetti13}, summarises some values of $C$ and their changes with assumption about the IMF.
-
-\begin{table}
-\centering
-\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
-\label{table1}
-\begin{tabular}{ c c c }
-\hline\hline
-Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
-\hline
-L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
-L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
-L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
-L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
-L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
-\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}.
-For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$ to convert luminosity density to luminosity.
-%or flux density?
-\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Sec.~\ref{sec: imf}), and for the timescale $\tau$.
-\end{tablenotes}
-\end{table}
-
-The most common single-band tracer of star formation rate is the ultraviolet.
-As mentioned before, UV emission is an excellent tracer for the SFR.
-Using a spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
-\begin{equation}
-SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
-\end{equation}
-where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ could be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA. %PB: should be \AA$^{-1}$? please check.
-As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
-The calibration constants' changes for shorter timescales are more significant and 
-their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
-Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
-Therefore, using the UV emission as a tracer might lead to underestimation of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
-
-Another single-band SFR indicator is the emission from hydrogen recombination lines. 
-Ionizing photons emitted from young massive stars ionize the surrounding gas.
-Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}.
-The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived from quantum mechanics. 
-The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
-Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emitted via Ly${\alpha}$ and longer wavelengths.
-This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
-The relation between the SFR, the luminosity of the \halpha emission line and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
-\begin{align}
-\label{equ: halpha}
-SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
-                     = 7.4 \times 10^{-54}Q(H^{\circ})
-\end{align}
-where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
-The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in \hii~regions.
-Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
-The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
-by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
-
-Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
-Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
-As a result, \oii~luminosity can be used as a tracer of the SFR through the \halpha luminosity. 
-\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
-Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
-In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
-\begin{equation}
-SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
-\end{equation}  
-where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
-Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of the major SFR indicators in high-redshift galaxies.
-In these galaxies, the \halpha emission line is redshifted out of the optical band; as a consequence, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is really useful~\citep{Kennicutt98b}.
-
-Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the infrared emission can be used to trace the SFR.
-The IR luminosity of a system depends not only on the amount of embedded dust, but also on the heating rate provided by the stars. 
-Since young stars heat the dust to higher mean temperatures than old stellar populations, to first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
-The fact that the heating rate provided by the young stellar population is higher than  that of the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
-Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.
-
-Two empirical single-band infrared star formation rate indicators are the 24~$\mu$m and 70~$\mu$m bands.  
-The use of these two bands depends on the type of galaxy studied or the physical environment in different regions within the galaxy. 
-Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) or a local indicator.
-That is because the global case includes the integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
-Table~\ref{table2} shows the constant $C$ from Equ.\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities, for local (spatial scale $\sim500$~pc for 24~$\mu$m and $\lesssim 1$ kpc for 70~$\mu$m) and global cases.
-
-\begin{table}
-\centering
-\caption{Infrared Luminosity to star formation rate calibrations}
-\label{table2}
-\begin{tabular}{ c c c c }
-\hline\hline
-Luminosity$^1$ & $C$ & Assumptions & references\\ 
-\hline
-L(24)$^{0.885}_{local}$ & $1.31 \times 10^{-38}$ &$1.10\times 10^{40} \le L(24) \le 3.10\times 10^{44}$&  \cite{Calzetti07}   \\ 
-L(24)$_{global}$ & $2.04 \times 10^{-43}$ &$ 4.10\times 10^{42} \le L(24)  \le 5.10\times 10^{43}$& \cite{Calzetti07} \\
-L(70)$_{local}$ & $9.4 \times 10^{-44} $ &$5.10\times 10^{40} \le  L(70) \le 5.10\times 10^{43}$& \cite{Li12} \\
-L(70)$_{global}$& $5.9 \times 10^{-44}$ &$L(70) \ge 1.4 \times 10^{42} $& \cite{Li10}\\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda$} in erg s$^{-1}$ 
-\end{tablenotes}
-\end{table}
-
-\subsubsection*{SFR Indicators Based on Multi-Band Emission}
-
-%%add PAHs here
-Despite the usefulness of having single-band SFR tracers, in many cases the corrections due to dust effects and luminosity ranges increase the uncertainty in measurements.
-Nowadays, thanks to large surveys, enormous amounts of data are available at different wavelengths for galaxies, which allows for combining the emission from different bands and finding new calibrations.
-The conversion between SFR and luminosities in multiple bands mostly helps to avoid problems regarding dust extinction or attenuation (see~\ref{sec: ism_intro}). 
-The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, whose correlation with the SFR is empirically derived~\citep{Kennicutt12}.
-
-The emission from dust heated by young stars changes with the amount of high energy photons heating the dust and by properties of dust such as grain size.
-Therefore, the calibration of SFR varies with each infrared band.
-Assuming that dust heating is dominated by emission from young stars, integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
-
-TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
-\cite{Boquien10} modified the calibration of the total infrared luminosity as: 
-\begin{equation}
-L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m)
-\end{equation}
-where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
-\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
-\begin{equation}
-\label{sfr_tot_IR}
-SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
-\end{equation}
-where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.
-
-In Sec.~\ref{sec: overview} we mentioned that emission from PAHs in the ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
-Most studies used broad infared bands, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using the PAH features only.
-\cite{Shipley16} calibrated SFR using observation from 105 star-forming galaxies with $z < 0.4$ as:
-\begin{equation}
-\log SFR = A + B \log L_{\mathrm{PAH}, \lambda}
-\end{equation}
-where $L_{\mathrm{PAH}, \lambda}$ is the luminosity of the PAH features at 6.2, 7.7, 11.3~$\mu$m or combinations thereof, in erg~s$^{-1}$.
-Tab.~\ref{table_PAH} shows the constants for each $L_{\mathrm{PAH}, \lambda}$.
-These calibrations underestimate the SFR for low-redshift galaxies with IR luminosity more than $10^12$~erg~s$^{-1}$.
-\cite{Shipley16} showed that using the 7.7~$\mu$m feature in the calibration reduces the scatter and concluded that this wavelength provides the most robust SFR tracer.
-
-\begin{table}
-\centering
-\caption{SFR calibrations from PAH luminosities; adopted from~\cite{Shipley16}}
-\label{table_PAH}
-\begin{tabular}{ l c c}
-\hline\hline
-PAH Feature(s) & A & B\\
-\hline
-6.2 + 7.7 + 11.3 & $ -42.56 \pm 0.03 $ &  1.00 \pm 0.03 \\ 
-6.2 & $ -40.06 \pm 0.09 $ &  0.96 \pm 0.04 \\ 
-7.7 & $ -42.38 \pm 0.06 $ &  1.00 \pm 0.03 \\ 
-11.3 & $ -44.14 \pm 0.08 $ &  1.06 \pm 0.03 \\ 
-6.2 + 7.7 & $ -42.05 \pm 0.04 $ &  0.99 \pm 0.03 \\ 
-6.2 + 11.3 & $ -42.52 \pm 0.05 $ &  1.01 \pm 0.03 \\ 
-7.7 + 11.3 & $ -42.85 \pm 0.04 $ &  1.01 \pm 0.03 \\ 
-\hline
-\end{tabular}
-\end{table}
-
-The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used.
-This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
-\begin{equation}
-L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR}
-\end{equation}
-where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements.
-$\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}.
-The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.g.][]{Hao11, Leroy08}.
-
-Another common multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
-This combination gives a more accurate dust-corrected estimate of the SFR~\citep{Kennicutt09}:
-\begin{equation} 
-\label{equ: halphaplus24}
-SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24)]
-\end{equation}
-where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the units of erg~s$^{-1}$. 
-L(24) is the 24~$\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$~yr$^{-1}$.
-
-Infrared emission in other bands can be used for correcting dust effects on UV or \halpha~emission (see Tab.~\ref{table3}). 
-The corrected emission then can be used as a SFR tracer.
-These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
-Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.
-
-\begin{table}
-\centering
-\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
-\label{table3}
-\begin{tabular}{ c c}
-\hline\hline
-Combined luminosities$^1$ & references\\
-\hline
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& \cite{Hao11}\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& \cite{Hao11}\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& \cite{Hao11}\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& \cite{Kennicutt09}\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& \cite{Kennicutt09}\\
-\hline
-\end{tabular}
-\begin{tablenotes}
-\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L_{$\lambda$} in erg~s$^{-1}$ 
-\end{tablenotes}
-\end{table}
-
-%PB: would it make sense to put this paragraph closer to where you first discuss Table 1?
-Sahar: I thought because IMF affect all of the calibration it would be better to have at the end of the section.
-%PB: OK.
-As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
-From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
-This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than in other parts of the spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
-Furthermore, reaching an asymptotic value of ionizing photons takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
-Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR the calibration constants are fairly close to each other.
-On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a 10 per cent difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
-As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.
-
-Our understanding of star formation in extragalactic systems depends on the light emitted by those systems.
-While emission from massive and young stars dominates the light of the system, the mass of low-mass stars dominates the mass  (see Sec.~\ref{sec: imf}).
-Therefore, SFRs are calibrated based on the dominant light and low-mass stars are accounted for using the initial mass function.
-Emission from star forming regions should be corrected before it can be used in calibrations.
-On its way to the Earth this emission passes through dust and gas clouds which cause extinction or attenuation (see Sec.~\ref{sec: extinction}).
-On the other hand, evolved stars emit their light in the whole spectrum as well as UV. 
-Therefore, even though it might have an insignificant part in the UV emission from galaxies, a correction for emission from evolved stars should be considered~\citep{Leroy08}.
-After measuring the corrected luminosities for star forming regions in galaxies (global or local), using proper calibrations can give the best estimation of SFR in galaxies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%Stellar Mass%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Stellar mass}
-\label{sec: starmass_intro}
-One of the most fundamental physical parameters which describes the present state of a galaxy is its stellar mass. 
-Stellar mass is linked with the structure and star formation history of disc galaxies~\citep{Gavvazi96} and allmorphologies~\citep{Scodeggio02}. 
-Measuring the mass of a stellar population is indirect and subject to significant uncertainties. 
-In principle there are two ways to measure stellar mass in galaxies. 
-The first is measuring the dynamical mass of a galaxy using kinematics (the mostion of stars)~\citep{Cappellari06} or lensing (bending light as the light pass near a galaxy)~\citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
-
-The second method is based on stellar population models~\citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution.
-Stellar population models predict the expected SEDs for stellar populations based on parameters of regions such as star formation history, metallicity, and IMF
-Uncertainties come from uncertainties in the stellar initial mass function (see Sec.~\ref{sec: imf}), the stellar evolution models, especially the stage where stars have the most luminosity in their evolution, the evolutionary state of the galaxy~\citep[see,][ans references therein]{Dalcanton12}, and star formation histories.
-
-In order to translate between photometry and stellar mass the stellar mass-to-light ratio ($M/L$) is needed.
-The use of $M/L$ is one way to measure stellar mass surface density. It is an indirect method and has high uncertainties in specific cases, but can help to study the stellar mass in large samples. 
-For integrated galaxy light, the $M/L$ is estimated using scaling relations between $M/L$ and broadband colours \citep[e.g.]{Bell03} and then multiplied by luminosity to estimate a mass.
-For resolved galaxies, one can produce a map of the stellar mass surface density distribution in galaxies using resolved colour to measure spatial variations in $M/L$.
-This method gives more accurate results than measuring the stellar mass surface density distribution from single-band images rescaled by a uniform mass to light ratio~\citep{Zibetti09}.
-
-Comparing results from independent methods to measure stellar mass helps to determine whether there are any systematic differences.
-Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few tens per cent~\citep{McLaughlin05}.
-Therefore, to model subtleties, the advantages and disadvantages of using each method should be carefully considered.
-
-\subsection{galaxy masses from dynamics}
-
-The simplest and the most common way to estimate the mass of a galaxy is assuming that the physics of the galaxy is simple Newtonian physics.
-Therefore, the circular velocity $v{\rm circ}(r)$ of an orbit within a spherical system of gravitational potential $\phi$ and mass $M$ is given by:
-\begin{equation}
-\label{eq: simpmass}
-v^2_{\rm circ}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r}
-\end{equation}
-where where $G$ is the gravitational constant and $M(r)$ is the mass within a sphere of radius $r$. 
-For a flattened disk, which is the case in most spiral galaxies, the right hand side of Equ.\ref{eq: simpmass} must be replaced by the more exact expression derived by~\cite{Freeman70}. 
-For the case of no dark matter or bulge, \cite{Freeman70} showed that the rotation curve of a self-gravitating disk is:
-\begin{equation}
-v^2_{circ}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)]
-\end{equation}
-where $\Sigma_0$ the central surface brightness, $R_d$ the disk scale length, where ratio of the intensity of disk to bulge is $e$ ($\sim$2.71).  
-$y=\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are the first and second kind modified Bessel functions.
-
-The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, and \hi~lines. 
-Integrated line widths only yield an estimate of total mass within some (uncertain) isophotal radius.
-Thanks to the current generation of detectors, it is possible to obtain very high-resolution spectra in the \halpha and CO lines over most of the optical disks of galaxies.
-The higher resolution data
-
-A detailed description of calculating dynamical masses in galaxies is beyond the scope of this work. 
-The methods mentioned represent the first order of approximation. 
-For more accurate results, one should consider non-circular rotational velocities and the fact that galaxies contain millions of stars plus interstellar objects; therefore simple two-object Newtonian physics is not the case here.
-A detailed review of dynamical masses of galaxies can be found in \citet{Courteau13}.
-
-\subsection{Galaxy masses from stellar population modelling}
-
-Galaxies can be observed because of their stellar emission; stars radiate the energy produced from nuclear reactions in their cores. 
-Given a star's initial mass, the theory of stellar evolution can describe the amount of energy released. 
-Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distributions of galaxies. 
-However, some fraction of the mass of galaxies consists of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants and should be considered in models.
-Stellar population synthesis models are used to predict the SED of a stellar population using many physical parameters. 
-These parameters, which control the time evolution of the stellar population such as age, $t$, of the population, measured in years, also referred to as the time passed since the star formation began, IMF, and metallicity~\citep{Courteau13}.
-
-The basic idea behind finding a suitable calibration between flux/luminosity of the stars in different wavelengths and stellar mass is that one can use the SFHs recovered from synthesizing the stellar optical colour-magnitude diagrams in different regions of a galaxy.
-The calculated stellar mass in nearby galaxies can be used to calibrate the fluxes from the stars in other galaxies.
-\cite{Zibetti09} suggested that to reach the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel basis. 
-They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density.
-To do so the surface density of stellar mass at each position is derived by 
-\begin{equation}
-\label{equ: massphot}
-\Sigma_{{\mathrm M_\star}} (\alpha, \delta) = \Sigma_{\lambda}(\alpha, \delta) \gamma_{\lambda}(\alpha, \delta)
-\end{equation}
-where $\alpha$ and $\delta$ are position, right ascension and declination, respectively.
-$\Sigma_{{\mathrm M_\star}} (\alpha, \delta)$ is the stellar surface density.
-$\Sigma_{\lambda}(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar M/L at an effective wavelength $\lambda$.
-In Equ.\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy.
-
-Peak of emission from evolved stars are in NIR part of spectrum.
-Therefore, many studies tried to make a map of stellar mass distribution using this bandpass within galaxies~\citep[e.g.,][]{Elmgreen84}.
-Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps thave a more accurate calibration.
-Fluxes from 3.6 and 4.5$\mu$m are suitable for calibration of the stellar mass, due to fact these two band-passes not only trace evolved stellar population but also they are almost insensitive to the emission from young stellar population or to dust absorption and emission.
-\cite{Zhu10} used the Sloan Digital Sky Survey~\citep[SDSS][]{York00} and the \Spitzer Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][] {Lonsdale03} to find calibration between galaxy luminosity and stellar mass.
-Using the M/L of galaxies, they found correlations between $K_s$ band, 3.6 and 4.5 $\mu$m band luminosities and stellar masses and formulated these correlations as:
-\begin{align}
-\label{equ: zhu1}
-\log M_{\star} = -1.60  + 1.12  \log \nu L_{\nu}[K_s]\\
-\log M_{\star} = -0.79 + 1.19 \log \nu L_{\nu}[3.6\mu \rm m]\\
-\label{equ: zhu3}
-\log M_{\star} = -0.25 + 1.15\log \nu L_{\nu}[4.5\mu \rm m] 
-\end{align}
-where M$_{\star}$ is the stellar mass in solar masses and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg~s$^{-1}$ at the specified wavelength.
-
-\cite{Eskew12} tested the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and found an empirical relation between mass of the stars and the luminosities of stars as:
-\begin{equation}
-\label{equ:eskew}
-  M_{\star} = 31.84 \times 10^{5.65} L_{3.6}^{2.85} L_{4.5}^{-1.85}
- %\log M_{\star} = 5.6 +2.85\log (F_{3.6})-1.85 \log (F_{4.5})+2\log \left(\frac{D}{0.05}\right)
-\end{equation}
-where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$/$\AA$.
-Equ.~\ref{equ: zhu1}--~\ref{equ: zhu3} have been derived from a large sample of galaxies, and were tested on different type of regions and galaxies. 
-on the other hand,~\cite{Eskew12} mentioned that since their calibration is based on data from Magellanic clouds this,
-measuring the stellar mass from Equ.~\ref{equ:eskew} might break down for highly star-forming regions; moreover, this equation has not tested on regions with different metallicity. 
-In more recent work,~\cite{Laura16} measured stellar mass for group of galaxies with ($z < 0.035$) and  showed they are tightly correlate with stellar mass measured from other calibrations.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%Preview%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Preview}
-\label{sec: pre_intro}
-
-A complete picture of how galaxies are formed and evolve is tied to unfolding the mystery of the formation of stars.
- Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas and the mass of stars in galaxies.
- For decades, observational, theoretical and numerical studies have investigated star formation; nevertheless, their results are contrary.
- Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
-
-The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
-The K-S law and similar empirical laws have been tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
-Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are yet undetermined and there is no definitive answer on whether there is any universal star formation law.
-Their dependence on physical properties of galaxies is nontrivial and sometimes differs by type of star forming regions.
-Although a relation between star formation and gas is well established, the details of this relation are not clear:
-different types of gas affect SFR in different ways, and variations in metallicity alter the effects.
-There is no fully sampled and universal IMF,
-in fact there are many debates on whether the IMF is universal or not.
-The influence of evolved stars and distance of star forming regions from centre of galaxies on SFR has been mentioned in studies but not fully investigated.
-Besides studying the impact of the above-mentioned properties of galaxies on SFR, searching for other relations between properties of galaxies and their star forming regions continues.
-
-Advances in observing facilities, image quality, and methodology expand our knowledge of star formation. 
-In the past few decades, the use of advanced statistical methods in astronomical studies has also grown.
-Applying modern statistical methods to star formation studies can shed light on unsolved problems in this field. 
-Studies show that using different statistical methods can change our perspective on star formation laws. 
-For example,~\cite{Shetty13} used Bayesian methods to show that the K-S law is not universal. 
-Since astronomy is a data-driven science, data-mining methods should be quite useful to gain new insight on properties of star-forming regions.
-However, these methods have not been widely-applied to studies of nearby galaxies, where the most detailed information about star formation is available.
-
-%PB not sure, but you might need a little more intro to the papers 2 and 3 stuff here.
-
-In this thesis, we present three projects that study the effects of galaxy properties on star formation.
-We use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
-Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
-In addition to the Kennicutt-Schmidt law, we study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
-We also show the effect on star formation laws of using different SFR and ISM gas tracers.
-In Chapter~\ref{ch: paper3}, we explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
-We cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
-During this process, we find hidden structures in high-dimensional data space.
-In Chapter~\ref{ch: paper2}, we move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
-We train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
-Then we study the grouped properties of the classified galaxies.
-We summarize our results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}
-
-%%%to be conticued
+%% to be continued

### 2016-07-15 version0.0/paper3.tex
finishing intro0.0
Adding summary

@@
 \chapter{Data Mining in Nearby Galaxies}
+\label{ch: paper3}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\section{Introduction} %%( I am not really happy with this introduction but it is the best I can have for now:/ )
-%General information about galaxies %(Maybe it is too generic?!!)
-Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
-Galaxies are an active and complicated systems, that are constantly changing.
-There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
-These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.
-
+\section{Introduction} 
 % Nearby galaxies and their importance 
-Nearby galaxies play an important role in learning about galaxies' formation and evolution.
-These galaxies are close enough to be able to observe various regions inside them in details.
-As a result, many studies are devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole%(Some more references here)
-, and many others use these results in analyzing data from high-redshift galaxies. %(Some more references here)
-The amount of data that is acquired from nearby galaxies is increasing daily.
-Advances in technology helps to both observe and store enormous amount of data from sky.%The sky?! 
-Telescopes and surveys gather data from nearby galaxies in variuse wavelengths and from these data we can measure physical properties of galaxies (e.g.
-stellar mass, star formation rate (SFR), dust mass, gas mass)~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.
+Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
+Nearby galaxies are defined as those close enough that we are able to observe their structure and composition in detail.
+As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
+%Advances in technology allow us to collect data from the sky. %PB - commented out
+Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.
 
 % A little bit about M31 and previous studies in M31.
-The Andromeda galaxy (M31), with a distance of $\sim$0.78~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
-Images of this galaxy provide us a detail view of inside of a spiral galaxy from distance.
-M31 data was a target of many telescopes (e.g.
-{\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.
+The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc, is the closest spiral galaxy to the Milky Way~\citep{McConnachie05}.
+Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
+M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer and \Herschel space telescope.
+\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
+Using data from the Multiband Imaging Photometer for Spitzer (MIPS) instrument, \cite{Gordon06} studied the morphology of M31's dust.
+\cite{Azimlu11} and \cite{Sanders12} catalogued and studied \hii~regions of M31.
+\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
+Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}.
+\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the spatially-resolved SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.
 
-\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
-Using the mid-IR data from Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of the dust in M31.
-\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
-\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
-Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
-\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data of the galaxy to study PAHs and other line emissions in the ISM.
-
-Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of undergoing processes in the galaxy.
-The amount of the observed data and measured quantities of M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
-Knowledge discovery and data mining methods are designed to extract hidden information from data and are tested in many astronomical studies.
-However, to the best of our knowledge, this study is the first study that uses a data mining method on data from nearby galaxies. %%% ehh
+Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of underlying processes in the galaxy.
+What is the correlation between PAHs and SFR, dust mass, and gas mass in M31? 
+Are PAH features in M31 similar or they can be divided into various groups? If so, what are the properties of each group?
+Does the intensity of PAH emission depend on the underlying structure of their position? %PB: I don't understand what you mean by "underlying structure of their position"
+How do they compare to properties of galaxies? %PB: what is "they"
+The properties of M31 that derived in various studies and observational data of this galaxy can be used for a knowledge discovery and data mining study.
+%The amount of data for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
+The Pinwheel Galaxy (M101), with distance of 6.7~Mpc~\citep{Freedman01}, is another nearby galaxy that has been well-observed and studied~\citep[e.g.
+][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
+M101 is a large spiral galaxy with several \hii~regions and a large metallicity gradient from centre to outskirts~\citep{Kennicutt03}.
+In case of dimensionality data from M101 is a suitable addition to M31 data for a data mining study. %PB: don't understand "In case of dimensionality"
+Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies~\citep[e.g.][and references therein]{Ball10}.
+However, this study is the first to use a data mining method on observations of nearby galaxies.
 
 % data mining and clustering in general; when we have so many data and we want to map them
-\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usages in astronomy.
-A data mining algorithm learns about data from sets of trainings, which can be supervised or unsupervised.
-The supervised trainings refer to methods, that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
-On the contrary, the unsupervised methods train without any prior knowledge of output results. 
-They solely work based on the underlying structure of input data.   
-The unsupervised methods are very useful tools in knowledge discovery studies on input data, which we do not have any insight of them (or when we want to make sure that we did not miss any valuable information in our previous studies).
-%%% ehh to after or part.
+\cite{Ball10} gave an extensive review of data mining and machine learning algorithms and their usage in astronomy.
+A data mining algorithm learns about data from training, which can be supervised or unsupervised.
+Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
+Unsupervised methods train without any prior knowledge of output results: 
+they work solely based on the underlying structure of the input data.   
+The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.
 
-%SOM
-One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein12, Hossein14,Hossein16,Ellison16a}.
-ANNs are designed to work in the same way that the neurons work in a human mind.
-They are networks of interconnected neurons (nodes), which all of the connections are weighted.
-These networks are used to study about nonlinear and complex relations between input and output data.
-%These relations can be applied to the new sets of data with similar feature
-
-One of the most well-known unsupervised neural network in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
-SOMs map and visualize a complex and nonlinear high dimension data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
-The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
-Since 1990s, many studies utilized SOMs for object classification and clustering (e.g.
-classifying quasars' spectra, star/galaxy classifications, gamma-ray bursts clustering and classification of light curves), and photometric redshift estimations~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper
-
-% other Unsupervised methods
-The purpose of this project is to have a new insight into nearby galaxies using M31 data with focusing on relations between PAHs and other properties of the galaxy.
-To fulfill this purpose, an unsupervised data mining method is the most suitable choice. %%eh  
-K-means algorithm, SOMs, and hierarchical clustering are main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
-
-For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of the clusters.
-In the hierarchical clustering method, the user must define dissimilarity between the groups, and the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
-Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method miss-classifies the data~\citep[][and references therein]{Mangiameli96}.
-We chose SOM method over K-means due to the fact that SOMs not only clusters data, but also shows similarity and dissimilarity between each cluster.
-Therefore, we can cluster our sample data and study the underlying structure of data, simultaneously.
+The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
+There are very few studies on relations between properties of M31 with its PAH features. %generate?!
+\cite{Cesarsky98} studied PAH spectra observed by ISOCAM spectro-imaging in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6$~$\mu$m emission with enhanced 11.2~$\mu$m emission.
+However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citep[IRS;][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
+Those authors re-evaluated the ISOCAM data to compare them to IRS data and found that the earlier results were likely due to incorrect background subtraction.
+%(PB), but the results were inconclusive.
+%%%%% !!!!!%%%%
+Using IRAC imaging observations,~\cite{Barmby06} found good agreement between the M31 SFR derived using observed 8~$\mu$m luminosity with other 
+star formation indicators such as \halpha and far infrared luminosity.
+\cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
+With data mining techniques we address the question of whether,
+compared to other galaxies, PAH features in M31 are unique as~\cite{Cesarsky98} claimed, or  are normal as ~\cite{Dim15} and \cite{Draine14} concluded.
 
 %this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
-In this project we apply SOM algorithm on M31 data, and trained 1D and 2D networks.
-Using smaller size networks we study the properties of the clusters and investigate relations between PAHs features with other features in M31.
-We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM, which leads to prediction of the unmeasured quantities in a galaxy.
-Assuming that all the spiral nearby galaxies have similar properties, we apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is another spiral nearby galaxy. 
+In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
+Using networks with fewer neurons, we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
+We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input on the position of the clusters in the SOM.
+We apply the 2D trained networks to the M101 data to check whether it has similar properties.
 If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
 
-In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101, that we use in this study. 
-We describe the SOM method in Section $\S$~\ref{sec: method}. 
-The results of the 1D SOM networks and studying PAHs in M31 is presented in Section $\S$~\ref{Sec: 1d_cluster}.
-In Section $\S$~\ref{sec: 2d_cluster}, we present the result of 2D SOM networks and how we use them to extract information about other galaxies.
+We describe the SOM method in Section $\S$~\ref{sec: method}. %PB: I think you use either "Section" or $\S$, not both.
+In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
+The results of the 1D SOM networks and the study of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
+In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
 In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
-
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%DATA
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-
-\section{Sample of study}
-\label{Sec: data_SOMN}
-
-We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}) as inputs for SOMs.
-We chose those specific regions due to availability of the PAHs data for them.
-Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
-Table~\ref{tab: data} shows the full list of the data and their unit for both M31 and M101.
-We divided each values by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
-Since the resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match the resolutions causes loosing all the information in some of the input data (e.g.
-the spectroscopic data).
-On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve it~\citep{Aniano12}.
-Therefore, we did not perform any resolution matching in this paper and used data in their original resolutions.
-
-\import{../image_paper3/text_files/tables/}{tab_data.tex}
-
-  \begin{figure*}
-    \subfloat[MIPS 24~$\mu$m image of M31 from~\cite{Gordon06}, with position of 10 regions \label{fig: regions in m31}]{
-      \includegraphics[width=\textwidth]{../image_paper3/images0.0/M31/M31.png}
-    }
-    \hfill
-    \subfloat[IRAC 3.6~$\mu$m image of M101~\cite{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
-      \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}}
-    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
-    \label{fig:dummy}
-  \end{figure*}
-
-%M31 data 
-%%%%% Sahar: More detail, right?
-    \subsection{M31 data}
-     \label{Sec: data_M31_SOMN}
-
-     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
-     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations. 
-     They used {\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
-     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
-     \cite{Dim15} also measured metallicity and of radiation hardness index (RHI) for these 10 regions.
-     We used the measured fluxes for PAHs featured, metallicity and RHI of each region as an input for SOMs.
-
-     We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] narrow badn and [\oiii] narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
-     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAHs fluxes.
-     $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from~\cite{Chemin09} were added to the input data. 
-     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, mass of molecular clouds, mass of atomic gas (H\,{\sc I}), total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm dust}$ and mass data from \cite{Draine14}.
-
-    \subsection{M101 data}
-    \label{Sec: data_M101_SOMN} 
-     For M101 galaxy, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
-     We also added their measurement of metallicity and RHI for these regions to our sample.
-     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101.
-     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
-     The Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
-     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in \cite{Rahmani16}.
-
-      Some of the correlations between some wavelengths and properties of galaxies are well-known.
-     For example, \citep{Rahmani16} used IRAC1 band emission to calculate the stellar mass, or FUV, NUV and MIPS24 emission to measure the SFR values. 
-     To make sure that we wouldn't use some of the observed data as an input data in various forms, we removed all the observed data, that were used to calculate these properties from the input sample.
-     We used these sample as the main input for creating SOMs.
-     Fig.~\ref{fig: cor_all} shows Pearson correlation coefficients with a confidence level of $95\%$ for the input data.
-
-      \begin{figure}
-                \centering
-                \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
-            \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all the in the subset 0.
-The colours show the Pearson correlation coefficients where 1 means highly correlated and -1 is highly anti-correlated quantities.
-The non-significant correlations were left empty.}
-            \label{fig: cor_all}
-        \end{figure}
 
@@
 \label{sec: method}
+\subsection{Choosing an Algorithm}
+
+Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein14,Hossein16}.
+ANNs are designed to work in the same way that the neurons work in a human brain.
+These are networks of interconnected neurons (nodes), in which all of the connections are weighted.
+These networks are used to study nonlinear and complex relations between input and output data.
+One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
+SOMs visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
+The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
+Since the 1990s, many studies have utilized SOMs for object classification and clustering (e.g.
+classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b}.
+%%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g.
+Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not
+
+The K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
+For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into the desired number of clusters.
+In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
+Comparing the SOMs, K-means and hierarchical clustering methods shows that in some cases the hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
+We chose the SOM method over the K-means method due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
+Therefore, we can cluster our sample data and study the underlying structure simultaneously.
+
  \subsection{Self Organizing Maps}
  \label{sec: som}
- The SOM is a clustering method which reduces the dimension of data to lower dimensions, while preserving topological features of the original data~\citep{Kohonen98}. 
- The results of the SOM are shown with a map of neurons.
- Each neuron has a fixed position in the map, and may contain one or more samples from input data, \boldit{V} $\in \Re^n$.
- A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data is associated with each node and will be varied during the training process.
- The process of creating SOM, happens over series of $N$ iterations.
- In each iteration, the algorithm calculates the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with ``$D_{j_{min}}$". 
+ The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features~\citep{Kohonen98}. 
+ The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
+ Each neuron has a fixed position in the map and may contain one or more samples from the input data,~\boldit{V} $\in \Re^n$.
+% Els said the simbols should be describe?!
+I think it is pretty obvious!
+%PB: most are pretty obvious, but mention what $n$ is here
+ A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
+ The process of creating an SOM happens over a series of $N$ iterations.
+ In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,{\mathrm min}}$. 
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
- The weight vectors in the neighbourhood of BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+ The weight vectors in the neighbourhood of the BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
   \begin{equation}
             \label{equ: weight adj}
-            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
+            W(t+1)=W(t)+L(t) \times R(t) \times(V(t)-W(t))
  \end{equation}
-where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
-Values for number of neurons, L(t) and R(t) are arbitrary. 
-~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more details.
+where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
+%PB: mention what L_0, \tau, r are
+Values for the number of neurons, $L(t)$ and $R(t)$ are arbitrary. 
+~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
 
-     In order to create SOM, we used {\sc MATLAB} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     An SOM in {\sc NNT} can be created by {\sc newsom} library which works in two phases; ``ordering phase" and ``tuning phase" . 
+     In order to create self-organizing maps, we used the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library, which works in two phases, the ``ordering phase" and ``tuning phase" . 
      Phase one is the ``ordering phase". 
-     This phase starts with maximum neighbourhood distance, and initial high learning factor usually 0.9 which is provided by user. 
-     The ordering phase continues for requested number of iterations and it continues till the learning factor reduces to tuning phase leaning factor and the neighbourhood distance reaches to the number set by the user.
+     This phase starts with maximum neighbourhood distance, and an initial high learning factor, usually 0.9, which is provided by the user. 
+     The ordering phase continues for the requested number of iterations.
+     At the end of the iterations, the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user. 
+     The second phase is the ``tuning phase".
+     In this phase the neighbourhood distance is at its minimum, but the learning factor decreases very slowly.
+     This minimum neighbourhood distance and slowly decreasing learning factor helps to fine tune the topology results and causes a more stable SOM. 
+     The number of iterations in this tuning phase must be much greater than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
+     We chose the number of epochs in the tuning phase to be 3 times more than the number of epochs in the ordering phase.
 
-     The second phase is the ``tuning phase".
-     In this phase the neighbourhood distance is at its minimum, but learning factor decreases very slowly.
-     This minimum neighbourhood distance and slowly decreasing the leaning factor helps to fine tune the topology results and causes the more stable SOM. 
-     The number of iterations in this tuning phase most be much more than the number iterations in ordering phase, to allow the tuning happens slowly. 
-     We chose number of epochs the tuning phase be 3 times more than number of epochs in the ordering phase.
+     To present our results, we use \textsc{nnt}'s built-in plotting tool.
+     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
+     In the maps, the purple hexagonal shapes show the neurons. 
+     The distances are shown by the grey-scale colours: the darker the colour, the larger the distance between neurons.
+     Neurons with zero hits are left empty.
+     In Section~\ref{sec: mock_sample} we used \textsc{newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
 
-     To present our results, we use {\sc nnt}'s built-in plotting tool.
-     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
-     In the maps, the purple hexagonal shapes shows the neurons. 
-     The distances are shown by the grey cycle colours: the darker the colour, the larger the distance between neurons.
-     Neurons with zero hits are left empty.
-     In Section~\ref{sec: mock_sample} we used {\sc newsom} to create SOMs from a mock sample to illustrate how this method works and how we can interpret the results.
-
-     One feature of the SOM method is that there is no rule and restriction on number of clusters.
-     Users must decide the size of networks based on their data set and their usages of the results .
-     There has been few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
-     We varied size of SOMs from $1\times2$ to $50\times50$ to choose the most suitable size for our maps, and found that based on the size of our sample, the 2D SOMs to be 10$\times$10. 
-     We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
+     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
+     Users must decide the size of the network based on their data set and their usage of the results.
+     There has been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
+     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$.
+     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
      %Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
      %Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
-     %All the other parameters are default values in {\sc newsom} library and cannot be changed by the users.
+     %All the other parameters are default values in \textsc{ newsom} library and cannot be changed by the users.
 
@@
 Hexagonal shapes represent the neurons.
-The grey cycle colours show the differences between weight of each neuron where white is the minimum differences and black has the maximum one.}
+The grey-scale colours show the differences between neuron weights, where white is the minimum difference and black is the maximum one.}
             \label{fig: sample}
@@
 
-To show how self-organizing maps work, we created a mock sample, which contains a few regions.
-We gave two information to each sample; amount of dust and the SFR.
- Therefore, we have a simple input data with low dimension; each entry only can get either 0 or 1 as high or low SFR, and 0 or 0.5 to show high or low amount of dust for the mock regions.
- We generated an SOM with the size of $10 \times 10$ from the sample, using the method that described in Sec.~\ref{sec: som}.
+To show how self-organizing maps work, we created a mock sample containing only a few regions.
+Each sample had two properties: the amount of dust and the star formation rate, where the possible values were
+either 0 or 1 for low or high SFR, and 0 or 0.5 for a low or high amount of dust. 
+ We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Sec.~\ref{sec: som}.
  Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
@@
 
-Using this method, as expected, we are able to divide the mock sample into 4 distinct groups: regions with high SFR and high amount of dust, regions with low SFR and high amount of dust, regions with high SFR and low amount of dust, and regions low SFR and low amount of dust.
-The plot in the Fig.~\ref{fig: sample}, clearly shows these divisions.
-In that plot, the upper part belongs to regions with low amount of dust, while the lower part belongs to the high amount of dust.
-The left part of the plot, is where regions with low SFR belong to and the right side is for high SFR regions.
+Using this method, as expected, we are able to divide the mock sample into 4 distinct groups.
+Their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
+%The plot in the Fig.~\ref{fig: sample} clearly shows these divisions.%PB: commented out.
+In Fig.~\ref{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
+The left part of the plot is where regions with low SFR belong and the right side is for high SFR regions.
 Grey to black colours show the border between regions.
-This network is considered as a trained network, and can used to cluster any new data set with similar entries.
+This network is considered to be a trained network, and can be used to cluster any new data set with similar entries.
 
-Having two regions with exactly the same values in all their quantities in the real world is almost impossible. 
-Therefore, one can find a network with high amount of the neurons, which separates the input data completely, and clusters them into separate groups.
-However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
-Therefore, it is up to the user to decide the similarity or dissimilarity between the input data based on the number of neurons.
+Having two regions with exactly the same values in all their quantities with real data is extremely unlikely. 
+If, in an input data set, there are two entries with similar (but not identical) values in all dimensions, one can find a network that separates these two entries in two groups.  
+However, in case of multiple similar entries in a dataset, the number of neurons must be much higher than the number of entries for complete separation.
+Therefore, the user learns about similarity or dissimilarity of members of the input dataset based on the ratio of the number of entries in the dataset and  the number of neurons.
+
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%DATA
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+
+\section{Study sample} %%or sample study?! %PB: study sample is OK
+\label{Sec: data_SOMN}
+
+Our study includes 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}). 
+These specific regions were chosen for the availability of \Spitzer/IRS 5--15$\mu$m  spectroscopy covering the PAH emission bands.
+Besides PAH band strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+Table~\ref{tab: data} shows the full list of data for both M31 and M101.
+All data were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
+Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
+the spectroscopic data).
+In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
+Therefore, we did not perform any resolution matching and used data at their original resolution. %PB: Need to discuss these last few sentences; not sure I understand what you're saying.
+
+\import{../image_paper3/text_files/tables/}{tab_data.tex}
+
+\begin{figure}
+  \begin{subfigure}[b]{0.5\textwidth}
+        \centering
+    %\centering
+        \includegraphics[width=0.97\textwidth]{../image_paper3/images0.01/M31/M31.png}
+        \caption{MIPS~24 $\mu$m image of M31, with positions of 10 regions studied.}
+        \label{fig: regions in m31}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}
+        \caption{IRAC 3.6 $\mu$m image of M101, with positions of  8 regions studied.}
+    \label{fig: regions in m101}
+    \end{subfigure}
+    \caption{Position of the data in M31 (up) and M101 (down).}
+\end{figure}
+
+%   \begin{figure}
+%     \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
+%       \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/M31.png}
+%     }
+%     \hfill
+%     \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
+%       \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M101/M101.png}}
+%     \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
+%     \label{fig:dummy}
+%   \end{figure}
+
+    \subsection{M31 observations}
+     \label{Sec: data_M31_SOMN}
+
+     \cite{Dim15} used {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31 (Fig.~\ref{fig: regions in m31}). 
+     Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
+     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
+     We used the measured PAH feature fluxes, metallicity and RHI of each region as the input for self-organizing maps.
+
+    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
+     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
+     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
+     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from~\cite{Rahmani16}, and L$_{\mathrm dust}$ and dust mass from~\cite{Draine14}.
+
+    \subsection{M101 observations}
+    \label{Sec: data_M101_SOMN}
+
+     \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions (Fig.~\ref{fig: regions in m101}).
+     Metallicities of 6 of the 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
+     We used the NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including
+      \GALEX FUV and NUV~\citep{depaz07}, IRAC 3.6 -- 8.0~$\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
+     As with M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (\hi) 21~cm emission images from \cite{Walter08}.
+     We calculated SFR(FUV + 24$\mu$m), stellar and total gas mass maps using the same methods as for M31.
+
+       \subsection{Preparing data for data mining}
+
+     Correlations between some of single-wavelength emission and galaxy properties are well-known.
+     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g.][]{Smith07a,Leitherer99} and it can be used to calculate the stellar mass~\citep{Eskew12}.
+     FUV, \halpha, and TIR emission are indicators of star forming regions.
+     In this project, we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24~$\mu$m emission.
+     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibrations using using 8, 24, 70, and 160~$\mu$m emission~\citep{Boquien10}.
+
+    %To guarantee that we do not use the observed data as an input for SOM in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
+    We removed all the observed data that were used to calculate galaxy properties from the input sample, to guarantee that they have not been used in multiple forms.
+   % We used this new sample of observational and derived data as the main input for creating SOMs.
+    To have prior knowledge of the M31 data set, %or to have an insight into the data set!
+    we computed the Pearson correlation coefficients between input measurements.
+    Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients with a confidence level of 95 per cent. 
+    All the PAHs correlate with one another very well.
+    They are also highly correlated with the SPIRE and PACS emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR and metallicity.
+    The fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show a weak anti-correlation with RHI.
+    In general, PAHs in our data set are highly correlated with most of the other quantities.
+
+      \begin{figure*}
+                \centering
+                \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
+            \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
+The colours and circle sizes show the Pearson correlation coefficients where large blue circles are 1, which means highly correlated, and large red circles are $-1$, which means highly anti-correlated quantities.
+The boxes with non-significant correlations were left empty.}
+            \label{fig: cor_all}
+        \end{figure*}
 
@@
 %----------------------------------------------------------------------------------------
-\section{One dimensional Self-organizing maps}
+\section{One dimensional self-organizing maps}
     \label{Sec: 1d_cluster}
 %Why 1D maps are useful
-    The purpose of the exploring M31 data with 1D maps is to monitor the general behaviour of data. 
-    1D SOMs can have from the minimum number of clusters, $1\times2$, to the highest number of cluster possible.
-    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without the clustering the data.
-    On the other hand, higher grid 1D SOMs are a helpful tool to get quick insight into data.
-%    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
-%Clustering
- %   \subsection{Clustering M31 data}
+    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
+    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity).
+    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
+    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.
 
-        In order to monitor how the data behaves, we created SOMs with two to fourteen neurons (Fig.~\ref{fig: M31_nets_1d}).
+    \subsection{Clustering M31 data}%I am not sure about it
+
+        In order to monitor how the data behave, we created SOMs with two to fourteen neurons (Fig.~\ref{fig: M31_nets_1d}).
         The $1\times2$ network (Fig.~\ref{fig: M31_net_1by2}) shows how the M31 data can be divided into two broad categories.
-        While the $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network that all the regions in M31 are completely separated.
-        Since in the higher network sizes, regions have more space to be separated based on their differences, we can see that from $1\times2$ to $1\times14$ network the M31 regions separated from each other increasingly, until they are completely separated.
+        The $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network in which all the regions in M31 are completely separated.
+        Since in the higher network sizes, regions have more space to be separated based on their differences, in going from the $1\times2$ to the $1\times14$ network the distance between M31 regions increases, until they are completely separated.
 
-        In Fig.~\ref{fig: M31_net_1by2}, it is clear that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 occupy one neuron and the other regions occupy the other one.
-        The medium grey colour between two neurons indicates that there are some similarity between two groups, but they are not very similar. 
-        By increasing the size of the neurones to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that the region 2 separates itself from the other regions and occupies the middle neuron.
-        The white colour between two left neurons suggests that regions, which occupy these neurons are very similar to each other, while the black colour between two right neurons expresses otherwise.
+      Fig.~\ref{fig: M31_net_1by2} shows that by forcing the regions in the M31 to be divided into two groups, regions 1, 2, 9 and 10 (shown in Fig.~\ref{fig: regions in m31}) occupy one neuron and the other regions occupy the other one.
+        The medium grey colour between two neurons indicates that there are some similarities between two groups, but they are not very similar. 
+        By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
+        The white colour between two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between the two right neurons indicates otherwise.
 
         %%%Talking about four right regions
-        \cite{Dim15} showed that the regions 1, 2, 9, and 10 have higher PAHs flux intensity compare to other regions (Fig. 5 in \cite{Dim15} paper). 
+        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
         %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
-        These regions also have relatively high intensity in the SPIRE bands and have high dust luminosity.
-        The higher values in the intensity of the PAHs, SPIRE bands and the dust luminosity could be the reason that these 4 regions become separated from the others, in $1\times2$ network.
-        Besides, Regions 1, and 9 are in the 10~Kpc ring, region 2 is slightly out of the 10~Kpc ring and the region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).
-        The differences in their positions might be the reason of regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
-        The similarity in the other input values with the other regions causes regions 1, 2, and 9 gradually move towards other regions, and have more distance with region 10, in the higher grid SOMs.
+        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
+        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
+        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).
+        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
+        Similarities with regions 3 to 8 in the other input values (e.g. SFR) causes regions 1, 2, and 9 to gradually move towards other the regions and away from region 10 in the higher grid SOMs.
        % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.
@@
     \begin{figure}
-            \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
+    \begin{subfigure}[b]{0.5\textwidth}
+        \centering
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by2_all.png}
-             }
+        \caption{$1\times2$~network}
+    \label{fig: M31_net_1by2}
+    \end{subfigure}
     \hfill
-            \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
+    \begin{subfigure}[b]{0.5\textwidth}
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by3_all.png}
-             }
+         \caption{$1\times3$~network}
+        \label{fig: M31_net_1by3}
+    \end{subfigure}
     \hfill
-            \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
+    \begin{subfigure}[b]{0.5\textwidth}
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by14_all.png}
-             }%%% What should I do with this one! It doesn't look good visually
-            \caption{SOM of the M31 data from $1\times2$~, $1\times3$~and $1\times14$~grids.
+        \caption{$1\times14$~network}
+        \label{fig: M31_net_1by14}
+    \end{subfigure}
+   \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
 The axes show the position of the neurons.
-The purple Hexagonal shapes represent the neurons.
-The grey cycle colours show the differences between weight of each neuron with white is the minimum differences and black has the maximum one.
-The numbers in the plot show the regions that are located in each neuron.}
+The purple hexagonal shapes represent the neurons.
+The grey scale colours show the differences between the weights of the neurons, with white as the minimum difference and black as the maximum.
+The numbers in the plot show the M31 regions located in each neuron.}
    \label{fig: M31_nets_1d}
@@
 
+% \end{figure}
+%         \begin{figure}
+%             \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
+%              \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by2_all.png}
+%              }
+%             \hfill
+%             \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
+%             \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by3_all.png}
+%              }
+%              \hfill
+%             \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
+%              \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by14_all.png}
+%              }
+%              %%% What should I do with this one! It doesn't look good visually
+%             \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
+The axes show the position of the neurons.
+The purple hexagonal shapes represent the neurons.
+The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum.
+The numbers in the plot show the M31 regions located in each neuron.}
+%             \label{fig: M31_nets_1d}
+%         \end{figure}
+
         %%Network 1by14
-        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network, that has no neuron to be occupied with more than one region.
-        In a higher grid SOM, network pays more attention to smaller details and differences in the input data.
-        Therefore, since at least 14 neurons are needed to separate all the 10 regions in M31, we can conclude that some of the regions have very small differences.
-        Regions that are located in similar area in M31, like region 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely show more similarity to each other.
-        In Fig.~\ref{fig: M31_net_1by14}, the most right neuron is occupied by region 10.
-        Two black colour between this region and the others indicates the high differences between this neuron and the other ones.
-        The region 10 is located in the bulge of M31, and its separation from other regions, which are mostly located around the inner or outer rings, is due to the fact that most of the input values for this region is much higher than the other regions.
-        The region 8 occupies the most right neurons in this network, that suggests that this region has the most differences with region 10.
+        The network with 14 neurons, in Fig.~\ref{fig: M31_net_1by14}, is the first network that has no neuron occupied by more than one M31 region.
+        In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
+        Since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
+        Regions that are located in similar areas in M31, like regions 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities to each other.
+%%present?
+show?
+represent?
+have?
+        In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
+        Two black colours between this region and the others indicate the large differences between this neuron and the others.
+       Region 10 is located in the bulge of M31, and is separated from other regions, which are mostly located around the inner or outer rings.
+       The SOM shows that this region has completely different input values than the others.
+       Most of the input values for region 10 are much higher than the other regions, which is the main reason for its isolation.
+        Region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.
 
-    \subsection{Inside of the 2 neurons network}%%% I will find better title for this subsection
-        %What is going on in this section
+    \subsection{Inside the 2 neuron network}
+
         \label{sec: inside_the_2_neurons}
-        Using SOMs, we can identify hidden subgroups in our samples. 
-        Each of these subgroups were separated from each other, for a reason.
-        This reason can vary from having higher values in some specific wavelengths, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data, that cannot be seen in other groups or in a Galaxy's data as a whole.
-        To investigate the later, we showed the Pearson correlation coefficients for the inputs from regions 3 to 8 in Fig.~\ref{fig: cor_cluster1}, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
+        Using self-organizing maps, we can identify hidden subgroups in our samples. 
+        Each of these subgroups were separated from each other for a reason.
+        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
+        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
 
-        \begin{figure}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
-        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left side of the Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
+        \begin{figure*}
+        \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
+        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
           \label{fig: cor_cluster1}
-        \end{figure}
+        \end{figure*}
 
         %%% what regions' version shows and how it compares with the other one:
-        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAHs features highly correlate with each other. 
-        Also, there are very strong correlations between all the PAHs features and PACS~100~$\mu$m~, SPIRE 250 to 500~$\mu$m~emission, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, and metallicity.
-        However, in Fig.~\ref{fig: cor_cluster1}, 12.0 and 12.7~$\mu$m~PAHs fluxes do not show any significant or strong correlation with PAH fluxes in other wavelengths or most of the other quantities.
-        The only exceptions are the strong correlation between PAH flux at 12~$\mu$m and L$_{\rm dust}$, and between 12 and 12.7~$\mu$m PAH fluxes.
-        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient become insignificant.
-        By removing the outlier, the correlations between 12.0 and 12.7~$\mu$m~PAHs fluxes and the other quantities show themselves.
+        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features are highly correlated with each other. 
+        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m, SPIRE 250 to 500~$\mu$m~emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, and metallicity.
+        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes at other wavelengths, or with most of the other quantities.
+        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\mathrm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
+        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
+        If we ignore the outlier values, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities reappear. 
+        For example, region 8 breaks correlations between 12.0~$\mu$m and 6.2, 7.7, and 8.3~$\mu$m.
+        This region could be part of scatter for these correlations, but with 6 regions in the dataset it is hard to have a firm conclusion.
 
-        For the rest of the PAHs fluxes in Fig.~\ref{fig: cor_cluster1}, there are not any significant correlations with PACS~100~$\mu$m, L$_{\rm dust}$, L$_{\rm TIR}$, SFR, or metallicity, neither.
-        They have correlations with SPIRE emission, but they are weaker than the ones with data from all regions.
-        Correlations between PAHs features and SFR, and L$_{\rm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
-        Many groups used PAHs features as a tracer of SFR by finding correlations between 
-        PAHs emission and SFR derived from extinction corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
+        For the PAH fluxes except 12.0 and 12.7~$\mu$m in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, or metallicity.
+        These PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.
+        Correlations between PAH features and SFR, and L$_{\mathrm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
+        Many groups have used PAH features as a tracer of SFR by finding correlations between 
+        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
         These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
-        Further analyses show that the absence of correlations between PAHs features and SFR, is because of one outlier in data. 
-        When we disregard the outlier data, high correlations between 6.2 to 11.3~$\mu$m~PAHs features and SFR (and L$_{\rm TIR}$) reappear.
-        Strong ant-correlation between 6.2 to 11.3~$\mu$m~PAHs features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} had not be seen in Fig.~\ref{fig: cor_all}.
-     %   In Fig.~\ref{fig: cor_cluster1}, 6.2, 7.7, 8.3, 8.6, and 11.3~$\mu$m~PAHs features show strong anti-correlations with RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission.
+        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: Region 6. 
+        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\mathrm TIR}$) reappear.
 
-        Anti-correlations between PAHs features and the \halpha, \sii, and \oiii~emission could be the result of one the followings. 
+        Strong anti-correlations between 6.2 to 11.3~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.
+        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
         First, the optical data are not corrected for dust extinction.
-        The PAHs features correlate with dust, and \halpha emission is sensitive to dust extinction.
-        Therefore, more PAHs features, means more dust and less \halpha~emission (The same for \sii~and \oiii~emission).
-        Second, it is the effect of observing apertures.
-        If the regions are located in the edge of the H {\sc II} regions we would expect too see more PAHs and less \halpha~emission. %%% reference?
-        The anti-correlations between 6.2 to 11.3~$\mu$m~PAHs features and RHI have been seen in other studies, too~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
-        \cite{Wu06} discussed these ant-correlations could be the result of destruction of the PAHs due to the high amount of the harder radiation (thus higher RHI).
+        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with amount of dust due to extinction \citep{Calzetti94}.
+        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same for \sii~and \oiii~emission.
+        Second, is the possible effect of observing apertures.
+        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
+        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
+        \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
         On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
-        The PAHs features are mostly coming from the PDRs that are surrounded by H {\sc II} regions, and the PAHs features underlying continuum emission is from the H {\sc II} regions.
-        Therefore, the lower flux of the PAHs features could be the result of the smaller size of PDRs.
-        The later reason, which could also describe the anti-correlation between PAHs features and \halpha~emission, seems to be the more probable one. 
-        %%% The anti correlation with stellar mass?!! with IRAC3?!!
+        The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
+        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
+        The later reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.
 
-       Despite the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meanings, we have to mention that, we only used 6 regions to calculate these correlation coefficients.
-       Having 6 data points as a sample of the study is not high enough to have a strong conclusion about the PAHs in M31.%%% it doesn't sound right:((
-        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differs from correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), SOM separated a hidden cluster of the data, which their properties are different than the others.
-%%Again eh!
+        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g.][]{Jones15,Lu14,Calapa14,Bendo08,Haas02}, a higher stellar mass decreases PAH emission.
+        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, and concluded that the PAH emission traces the old stellar population.
+        In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
+        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in clustered data or in all 10 regions.
+      %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
+      %It is possible that all the 10 regions in M31 simply aligned with the scatter of the correlation.
+Further analysis on M31 data is required to see weather the anti-correlation in this regions is extended to whole galaxy or it is only for these 6 regions.
+
+        Some studies have indicated that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}.
+        To test whether anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
+        The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for either the clustered data or all 10 regions.
+        Therefore, we conclude that in our sample,  stellar mass does not cause the destruction of PAHs.
+
+        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
+        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
+        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an \hii~region, which could be the reason of low PAHs for these regions.
+        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
+        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
+        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!
+
+       % On the other hand, if we divide SFR by stellar mass, which give us specific star formation rate (sSFR), we see strong correlation between sSFR and 6.2 to 11.3~$\mu$m fluxes for clustered regions,
+
+       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to mention that we only used 6 regions to calculate these correlation coefficients.
+       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.
+        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties.
 
@@
  \label{sec: 2d_cluster}
-    Although 1D networks are great to have a general idea about the data, neurons in 1D maps have maximum two neighbours, which causes some limitation in the results.
-    In 2D networks, each neuron has two to six neighbours, which allowed them to to capture a whole picture of the complicated relations in the input data.
-    Therefore, we created $10\times10$ 2D networks to study the data in details.
-    As mentioned in previous sections, the size of SOMs are arbitrary and users must decide about it based on what their goals of using SOMs are.
-    In this section we chose $10\times10$ size despite that we knew, from the size of our input data, that most of the neurons would be empty.
-    Using 2D networks, we are mostly interested in the ability of the SOMs in showing underlying structure of the data rather than its clustering features.
+    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
+    In 2D networks, each neuron has two to six neighbours, which allows them to capture a complete picture of the complicated relations in the input data.
+    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
+    As mentioned in previous sections, the size of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
+
+    In this section we chose $10\times10$ size despite knowing, from the size of our input data, that most of the neurons would be empty.
+    Using 2D networks, we are mostly interested in the ability of the SOMs to show the underlying structure of the data rather than its clustering features.
+    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of the M31 data.
+    Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
     \import{../image_paper3/text_files/image_texts/}{all.tex}
-    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of M31 data.
-    Similar to the Fig.~\ref{fig: M31_net_1by14}, all the 10 regions completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
 
-    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with very bright colour between their neurons, which presents that these two regions are very similar.
-    Considering the position of these two regions in M31 (Both of these regions are right on the edge of the star forming rings in the galaxy), similarity of these two regions were predictable.
-    Position of region 3 on the SOM is close to the position of regions 4 and 7, but with darker colour between the nodes. 
-    In Fig.~\ref{fig: regions in m31} it is clear that, this region in M31 is closer to regions 4 and 7 than any other region, but it is on the outer side of the star forming ring.
-    Regions 5 and 6 are in their second neighbourhood on the SOM, with a medium gray colour between them.
-    These two regions are around the inner ring of the galaxy.
-    Regions 8 and 6 are both in the inner ring of M31, but region 6 is in the region with more star forming activities, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.
+    Regions 4 and 7 are in the top left of Fig.~\ref{fig: all_derived_ones} with a very bright colour between their neurons, indicating that these two regions are very similar.
+    Considering the position of these two regions in M31 (both right on the edge of the star forming rings in the galaxy), similarity of these two regions was predictable.
+    The position of region 3 on the SOM is close to the position of regions 4 and 7, but with a darker colour between the nodes. 
+    In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
+    Regions 5 and 6 are in the second neighbourhood on the SOM, with a medium gray colour between them.
+    These two regions are physically located around the inner ring of the galaxy.
+    Regions 8 and 6 are both in the inner ring of M31, but region 6's location has more star formation, which could be the main reason for their relative distance in the SOM in Fig.~\ref{fig: all_derived_ones}.
 
     Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
-    However, region 1 is in an area of the galaxy with lesser diffuse \halpha~emission than region 9, that might be the reason for their distances in SOM.
-    Region 2 is more distant from other regions in the galaxy, and placed in the star forming ring.
-    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffused \halpha~emission.
-    Therefore, place of region 2 in the SOM is more favoured towards regions 1 and 4. 
-    Region 10 is placed in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.
+    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in SOM.
+    Region 2 is more distant from other regions in the galaxy and placed in the star forming ring.
+    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
+    Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
+    Region 10 is in the bulge of the galaxy, and its position on the SOM is isolated from all the other regions by a strip of a dark colours.
 
-    In order to analyse effects of any input data on the final SOM, in the following we created SOMs from various subsets of data.
-    We compare results of the subsets with one another and with SOM created from all data in Fig.~\ref{fig: all_derived_ones}.
+    In order to analyse effects of any input data on the final SOM, in the following we create SOMs from various subsets of data.
+    We compare results of the subsets with one another and with the SOM created from all data in Fig.~\ref{fig: all_derived_ones}.
 
@@
     \label{sec: subsets}
-            For analysing subsets, we creating SOMs by using only PAHs data, as well as using all data except PAHs ones (Fig.~\ref{fig: PAHS_or_not_PAHs}).
+            For analysing subsets, we created SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
              \import{../image_paper3/text_files/image_texts/}{PAHS_or_not_PAHs.tex}
-            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, showed that the general position of regions in those networks are the same.
-            The region 10 is in one corner of the all three networks.
+            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of regions in those networks are the same.
+            Region 10 is in one corner of all three networks.
             However, in Fig.~\ref{fig: all_derived_ones} and Fig.~\ref{fig: wt_pahs}, region 10 is isolated from the other regions, while in Fig.~\ref{fig: only_pahs}, region 10 is much less isolated and only shows complete dissimilarity with region 8.
-            Regions 9 and 10 are totally isolated in SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
+            Regions 9 and 10 are totally isolated in the SOMs in Fig.~\ref{fig: wt_pahs}, but in Fig.~\ref{fig: only_pahs}, they are more similar to other regions.
             In both SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs}, there are dissimilarities between regions in M31 but in Fig.~\ref{fig: wt_pahs}, the colours are much darker than the ones in Fig.~\ref{fig: only_pahs}.
-            This indicates that there are more similarity between PAHs features from all 10 regions then the other input data.
+            This indicates that there is more similarity between the PAH features over all 10 regions than between the other input data.
 
-            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data), gradually, by adding data from other quantities of galaxies to the input data. 
-            The order of adding data is the same as order of data in Fig.~\ref{fig: cor_all}, i.e.
-SOM in Fig~\ref{fig: inc_D_col3s}a was created from PAHs data and H$\alpha$ emission as input data, SOM in Fig~\ref{fig: inc_D_col3s}b created from PAHs, H$\alpha$ emission and [\sii] continuum as input data, and so on.
+            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data) gradually, by adding other quantities to the input data. 
+            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
+the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, H$\alpha$ emission and \sii~ continuum, and so on.
             \import{../image_paper3/text_files/image_texts/}{col3byall.tex}
 
-            SOM algorithm assigns random weight to each network, that causes the overall position of regions in networks (even with the same input data) changes in each run of the algorithm.
-            However, the position of each region regarding to other regions changes dramatically only because of the new sets of input data is given to the algorithm (assuming all the initial values for the run are intact).
-            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: inc_D_col3s}a,~\ref{fig: inc_D_col3s}d,~\ref{fig: inc_D_col3s}g,~\ref{fig: inc_D_col3s}k, and ~\ref{fig: inc_D_col3s}l, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
-            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data in the network.
+            The SOM algorithm assigns a random weight to each network that causes the overall position of regions in networks (even with the same input data) to change in each run of the algorithm.
+            However, the position of each region relative to other regions changes dramatically only when the new sets of input data are given to the algorithm (assuming all the initial values for the run are unchanged).
+            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: col3and11_dist},~\ref{fig: col3and14_dist},~\ref{fig: col3and17_dist},~\ref{fig: col3and21_dist}, and ~\ref{fig: col3and22_dist}, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
+            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data.
 
-            Comparing Figs.~\ref{fig: inc_D_col3s}a to ~\ref{fig: inc_D_col3s}o shows that adding \halpha~emission data to PAHs features causes regions 9 and 10 become isolated. 
-            Increasing dimension of the input data makes region 10 more isolated.
-            The relative position of regions 4 and 7 stays the same with increasing the input data. 
-            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ do not have any adequate effect on the networks.
+            Comparing Figs.~\ref{fig: col3and11_dist} to ~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
+            Increasing the dimension of the input data makes region 10 more isolated.
+            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
+            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
             Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.
 
-            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to study effects of the input data on SOMs, further.
-            Subset 1, that are listed in Tab.~\ref{tab: subset1}, includes all the inputs data except data from stellar mass.
-            Tab.~\ref{tab: subset5} is the list of data that were used in a subset 2, which includes all data except the fact that instead of the individual PAH fluxes we added them all together and have total PAH flux.
-            For subset 3 ( in Tab.~\ref{tab: subset6}), we removed SPIRE 250 and 500~$\mu$m from subset 2.
-            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs that are created by data from subsets 1 to 3, respectively.
-            The rest of the subsets are discussed in the Appendix.~\ref{sec: app_2d_soms_SOMN}.
+            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to further study the effects of the input data on SOMs.
+            Subset 1, listed in Tab.~\ref{tab: subset1}, includes all the input data except stellar mass.
+            Tab.~\ref{tab: subset5} lists data used in subset 2, which includes all data except that the PAH fluxes are combined into a total PAH flux. 
+            For subset 3 ( in Tab.~\ref{tab: subset6}), SPIRE 250 and 500~$\mu$m were removed from subset 2.
+            Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs created by data from subsets 1 to 3, respectively.
+            The remaining subsets are discussed in Appendix.~\ref{sec: app_2d_soms_SOMN}.
 
-            The results from Table~\ref{tab: subset1} is shown in Fig.~\ref{fig: subset1}. 
-            In this SOM compare with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
+            The results from Table~\ref{tab: subset1} are shown in Fig.~\ref{fig: subset1}. 
+            In this SOM, compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
             Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
-            Since the differences in the amount of the stellar mass were one of the most distinct differences between these three regions, removing stellar mass from input data reduced the distance between these regions.
-            Regions 5, 6 and 8 are in the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they all are closer to the position of the region 10.
-            Distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
+            Since the differences in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from the input data reduced the distance between these regions.
+            Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they  are all closer to the position of region 10.
+            The distance between regions 2 and 3 is reduced but in the meantime the colour between them became darker.
 
@@
 
-            Changing from separate values for each PAH features to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compare to the one in Fig.~\ref{fig: all_derived_ones}.
-            Distance between the relative position of regions 6 and 8 increased significantly, while the position of region 2 moved closer to the positions of regions 4 and 7.
-            The winner neurons for regions 3 and 5 moved towards each other, but the colours between them became much more darker.
+            Changing from separate values for each PAH feature to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compared to the one in Fig.~\ref{fig: all_derived_ones}.
+            The distance between the positions of regions 6 and 8 increased significantly, while the position of region 2 moved closer to the positions of regions 4 and 7.
+            The winner neurons for regions 3 and 5 moved towards each other, but the colours between them became much darker.
 
@@
 
-            Fig.~\ref{fig: subset6} shows the SOM generated from data that are listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except SPIRE 250 and 500~$\mu$m emission.
-            Although for most of the regions we see the changes in their positions, the colours between neurons changed, too. 
+            Fig.~\ref{fig: subset6} shows the SOM generated from data listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except for  the SPIRE 250 and 500~$\mu$m emission.
+            Although for most of the regions we see the changes in their positions, the colours between neurons changes as well. 
             %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
-            The distance between the positions of the regions 4 and 2 are increased.
-            The same happened for distances between regions 7, 3 and 6.
-            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from input data moved the positions of the regions further from each other.
+            The distance between the positions of the regions 4 and 2 is increased as are the
+            distances between regions 7, 3 and 6.
+            In both cases, SPIRE 250 and 500~$\mu$m emission of these regions are similar to one another, and removing these two parameters from the input data moved the positions of the regions further from each other.
             \import{../image_paper3/text_files/tables/}{subset6.tex}
@@
             %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.
-            \subsubsection{Prediction observing data using M31}
 
-                On SOMs we can see relations between the input data from each region regarding to the other regions.
-                These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
-                Therefore, we have the probability distribution of quantities of each values given data from other regions.
-                We can use these probability distribution to estimate missing data for regions.
+            % \subsubsection{Prediction observing data using M31}
 
-                To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
-                Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
-                \import{../image_paper3/text_files/image_texts/}{sim_subset1.tex}
-                We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
-                Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
-                In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.
+            %     On SOMs we can see relations between the input data from each region regarding to the other regions.
+            %     These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
+            %     Therefore, we have the probability distribution of quantities of each values given data from other regions.
+            %     We can use these probability distribution to estimate missing data for regions.
 
-                We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
-                \begin{equation}
-                \label{equ: prob1}
-                    P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
-                \end{equation}
-                Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
-                We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
-                This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.
+            %     To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
+            %     Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
+            %     \import{../image_paper3/text_files/image_texts/}{sim_subset1.tex}
+            %     We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
+            %     Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
+            %     In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.
 
-    \subsection{Validating networks using M101 data}
-    Another application of SOM for nearby galaxies is that to apply the trained networks on the data from other galaxies in order to prediction properties of the regions in them. %%eh
-    As an example of this application, we generated an SOM using data from M31 that held in common with M101 data (Fig.~\ref{fig: subset9}a). 
-    In this SOM, the same as the others, region 10 is separated from other regions in M31.
-    Regions 7 and 4 are close to each other with very light colours between their neurons, and the same as the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
+            %     We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
+            %     \begin{equation}
+            %     \label{equ: prob1}
+            %         P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
+            %     \end{equation}
+            %     Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
+            %     We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
+            %     This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.
+
+    \subsection{Testing networks using M101 observations}
+    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions. %%eh
+    To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
+    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs in these two galaxies (for more detail see \cite{Dim15} and \cite{Gordon08}).
+    In this SOM, as in the others, region 10 is separated from other regions in M31.
+    Regions 7 and 4 are close to each other with very light colours between their neurons, and as in the other SOMs regions 6, 8, and 5 are close to each other, but with a medium dark colour between them.
     \import{../image_paper3/text_files/image_texts/}{subset9.tex}
 
-    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a on M101 data (Fig.~\ref{fig: subset9}b).
-    Region 6 in M31 and region 2 in M101 both occupied the same neuron in the network in Fig.~\ref{fig: subset9}, which immediately suggest that these two regions have similar properties. 
-    Region 2 in M101 is a bright H {\sc II} region that is located at the end of the one of the M101 spiral arm (see Fig.~\ref{fig: regions in m101}). 
-    Region 6 in M31 is located near the inner ring of the galaxy (see Fig.~\ref{fig: regions in m31}).
-    Both regions have relatively low amount of PAHs emission and medium amount of the SFR regarding the other regions in the galaxy, which makes them very similar regions.
+    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
+    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties.
+    Region 2 in M101 is a bright H {\sc II} region located at the end of the one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
+    region 6 in M31 is located near the inner star-forming ring (see Fig.~\ref{fig: regions in m31}).
+    Both regions have relatively low PAH emission and a median amount of  SFR compared to other regions in the galaxy, making them very similar.
 
-    Region 7 in M101 is located in the nucleus of the galaxy and have relatively higher quantities than the other regions.
-    This region is located in the top right side of the network in Fig.~\ref{fig: subset9}, which is close to location of region 10 in the network.
-    Since the bulge of a spiral galaxy has different environment from its nucleus, region 7 in M101 and region 10 in M31 are not occupied the same neuron in the SOM, and have a medium grey colour between their neurons.
+    Region 5 in M31 is in the inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region, while
+    region 8 in M101 is in a spiral arm of the galaxy.
+    Relatively low stellar mass, SFR and SPIRE band emission caused these two regions to be nearby in the map.
+    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties; in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
+    These regions all have medium or low PAH emission, dust and SFR compared to the remaining regions.
 
-    Region 1 in M101 is located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities than the ones in region 7.
-    The lower values for fluxes of the PAH features, and relatively moderate amount of the SFR caused this region places between region 4 and 5 of M31 in the network. 
-    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated itself from other regions and located between region 9 and 10 in M31.
-    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high amount of fluxes of PAH features. 
-    This region also shows a high amount of the SFR and the stellar mass, which describes why the location of region 4 from M101 in the SOM is close to regions 9 and 10 from M31.
+    Region 7 in M101 is located in the nucleus of the galaxy and has relatively higher values of the quantities than the other regions.
+    This region is located in the top right side of the network in Fig.~\ref{fig: subset9},  close to the location of M31 region 10 in the network.
+    Since the bulge of a spiral galaxy has a different environment from its nucleus, region 7 in M101 and region 10 in M31 do not occupy the same neuron in the SOM, and have a medium grey colour between their neurons.
 
+    Region 1 in M101 is also located near the nucleus of M101 (see Fig.~\ref{fig: regions in m101}), but has considerably lower values in all the quantities compared to region 7.
+    The lower values for fluxes of the PAH features and moderate amount of the SFR caused this region to be placed between M31 regions 4 and 5 in the network. 
+    Fig.~\ref{fig: subset9}b shows that region 4 in M101 is separated from other regions and located between M31 regions 9 and 10.
+    \cite{Gordon08} showed that this region is a diffuse nebula in M101, with high PAH emission. 
+    This region also shows a high SFR and stellar mass, explaining why the location of M101 region 4 in the SOM is close to that of M31 regions 9 and 10.
+
+    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, we can have ideas about data entry from other regions/galaxies.
     In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
-    We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
-    Increasing dimension of the data and the number of regions would help to have more reliable networks.
+    We should note that, since we normalized data before using them in the networks, we only see relative properties of the regions.
+    Therefore, we need data from few regions in the galaxy to use this network and cannot use these networks to learn about properties of a single region in other galaxies.
 
@@
 \label{sec: summary}
-Self-organizing maps can be used to explore hidden subgroups and underlying structure of the data.
-In this project we investigated applications of the Self-organizing maps in data from nearby galaxies.
-We utilized the SOM method to study data from two well-studied galaxies; M31 and M101.
-Data from nearby galaxies can be clustered in various networks with different sizes/dimensions based on the information needed from the data. 
-A network with one dimension and a few neurons, can be used for general classification, while for more detailed clustering, a higher number of neurons should be used.
 
-Using smaller-sized self-organizing maps, the M31 data were clustered in 2 major groups; we found correlations that could not have otherwise been seen without clustering.
-For example in Sec.~\ref{sec: inside_the_2_neurons}, we found that six of the regions in M31 create a subgroup of data, that have lower amount of PAHs flux.
-Flux from the PAHs features in these regions highly anti-correlated with \halpha~emission despite that considering Flux from the PAHs features in all regions highly correlates with SFR.
-Our analyses of smaller-sized networks showed that using this method we can find hidden subgroups in data to extend our knowledge of inside the galaxies.
+We present results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
+Self-organizing maps both cluster data and show relative distance between the clusters. 
+We utilized the method to find hidden subgroups in the data as well as finding relations between those groups.
 
-In the maps with larger sizes, networks can be used to illustrate the relative relations of the regions with one another.
-We found the relative similarity between M31 regions, by varying the size of networks.
+Using smaller-sized self-organizing maps, we found that the M31 data are clustered into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
+Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
+PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
+These anti-correlations are insignificant when the full dataset is considered.
+The most probable reason for PAHs to anti-correlate with optical emission lines and RHI is a harder radiation field.
+This makes the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.
+
+PAHs in clustered data also show an anti-correlation with stellar mass.
+We discussed the possibility that higher stellar mass might destroy PAHs;
+however, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
+Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
+This result shows that PAHs in the clustered regions in M31 are not heated by the old stellar populations.
+
+In self-organizing maps with larger sizes, networks can be used to illustrate the relations of the regions with one another.
+We found the relative similarity between M31 regions by varying the size of the networks.
 A one-dimensional network with 14 neurons was needed in order to
-separate all 10 regions; we concluded that some of the region in M31 (e.g. regions 4 and 7) are very similar.
-A two-dimensional networks provide us a more complete picture of the data.
-Using these networks, we show a relative relations between regions in M31.
+separate all 10 regions; some of the regions in M31 (e.g. regions 4 and 7) have very similar properties.
+Two-dimensional networks provide us with a more complete picture of the data.
+We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
+Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
+In that network region 10 blends more with other regions and only shows differences with the data from region 8.
+These results suggest that the PAHs in all 10 regions have almost the same properties.
 
-We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
-By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
-We also applied the SOMs from M31 data to M101 data and found regions with similar properties in both galaxies placed in close regions in the SOMs.
-We show that using this ability of the SOM, we can predict properties of regions in other nearby galaxies very fast.
+Applying the SOMs from M31 to observations of M101, we found regions with similar properties in both galaxies placed in close regions in the SOMs.
+Using this ability of the SOM, we can predict properties of regions in other nearby galaxies very quickly.
+The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
+Increasing the dimension of the data and the number of regions would yield more reliable networks.
+In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83) and learn about the properties of regions in those galaxies.
 

### 2016-07-15 version0.0/summary.tex
Adding summary

@@
-\chapter{Summary and feature works}
+\chapter{Conclusion \& Feature Works}
 \label{ch: summary}
+ %General
+Formation of stars is one of the fundamental factors in formation and evolution of galaxies.
+Star formation rate and its variations during time help us to learn about how a galaxy forms and evolves.
+Many efforts have been made to find a universal law for rate of which stars form. %of or on?
+In order to find a universal law, finding a method to measure SFR accurately is the first step.
+Then correlations between SFR and other properties of galaxies must be investigated, to find SFR law.
+Afterward, each law have to be tested on various environments to confirm its universality.
+Therefore, we need high quality data and good statistical methods to test the laws.
+
+It has been well established that to form stars, gas m is the main ingredient.
+However, the relation between SFR and different tracers of gas mass (atomic, molecular, or total gas) changes in different type of galaxies.
+Relations between stellar mass and metallicity with SFR is not clear and there are fewer studies on them than the relation between SFR and gas mass.
+Dependency of SFR on other properties of galaxies such as morphology and dust mass were tested as well, but there is no SFR law that consider all of the mentioned quantities together.
+% Are these correlations holds for all the regions in galaxies? local and global? nearby and high-redshift?
+% The limitation of these relations should be considered  whether all these relations hold in all types of galaxies, both in nearby and high-redshift galaxies, and 
+Kennicutt-Schmidt law was the first empirical star formation law, which suggest that SFR and molecular gas have a logarithmic correlation with each other~\citep{Schmidt59, Kennicutt98b}. %cite? again?
+However, after many years and studies, it is still ongoing question whether it is a universal law or not.
+\citet{Shetty13} showed besides the physical and environmental, fitting methods also changes our perspective of the K-S law.
+Extended version of K-S law were introduced by adding  affect of stars (extended Schmidt law; introduced by ~\citealt{Shi11}) or by adding effect of metallicity (Krumholz law; introduced by ~\citealt{Krumholz09}).
+Compare to K-S law, the extended Schmidt law and Krumholz law are are relatively recently introduced and yet need to be tested with divers statistical methods in different scales (local and global), various morphological types and in both nearby and high-redshift galaxies.
+
+%Chapter 2
+The spatially resolved images of the Andromeda galaxy (M31) cover different types of environment in galaxies; high or low stellar surface density, gas mass, and metallicity.
+These images helps to examine star formation laws in various environments, in detail.
+In Chapter~\ref{ch: paper1}, we investigated three star formation laws in M31 in both local and global scale in order to determine which one of these laws can be fitted to M31 data more accurately.
+To achieve this goal, We have produced maps of surface density of SFR, gas mass, stellar mass and metallicity of the galaxy.
+We created SFR map using three tracers, a combination of the FUV and 24 \um emission, a combination of the \halpha and 24 \um emission, and TIR luminosity. 
+Using a combination of the FUV and 24 \um emission, we determined the total SFR for M31 is $0.31\pm 0.04$ M$_\odot$ yr$^{−1}$.
+We measured ISM gas mass using molecular gas only, atomic gas only and the total gas.
+we confirmed that the extended Schmidt law works on M31 in local regions and effect of stellar mass in regions with low gas density is even more pronounced 
+By applying both K-S law and the extended Schmidt law on all SFR maps and gas maps, we concluded that changes in SFR tracer does not affect these laws as much as changes in gas tracer does.
+Our fitting results shows that, in regions with higher star formation, power lows are more precise.
+In order to examine Shetty's suggestion on effect of fitting methods on results of fitting SFR laws, we used hierarchical Bayesian regression fitting and normal regression fitting to fit SFR laws.
+The results from two different methods are contrary, which is mostly because of the way these two methods handles the errors.
+We could not re-produced the measured SFR, using Krumholz law and also could not find any high correlation between metallicity and SFR.
+
+%Chapter 3 
+for the reminder of chapter we used machine learning method to have a fresh look on star formation and its relation to other properties of galaxies.
+we chose SOM method to apply data mining method because of its ability to classifying results and showing the morphology of data
+amount of observation in M31 makes it a good target for machine learning studies, therefore Chapter~\ref{ch: paper3} we apply a SOM method on data from M31.
+We used observational data and derived quantities of 10 regions in M31, which were chosen due to availability of IRS data for those regions.
+Therefore, we were able to focus on relations between SFR and dust, specifically PAHs.
+Using a network with 2 neurons, we divided data into two major groups.
+comparing data for clustered regions we found correlations between groups that otherwise cannot be seen.
+In one of the clustered data flux from PAHs showed strong anti-correlation with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
+what anti correlation tell us (after finishing the corrections on the chapter 3)
+Since for 10 regions in M31 we need at least 14 neurons to separate all 10 regions from each other, we conclude that some of these 10 regions have very similar properties.
+using subsets of data we generated various two dimensional networks.
+These subsets showed that except for PAHs only subset, region 10, which is located in the bulge of M31, become isolated.
+Therefore, we can conclude that despite differences in underlying structure of regions, PAHs are very similar together in M31.
+We created network using M31 data that are similar to M101 data.
+We applied these network on M101 data and showed that regions with relative similarity place in the same neurons.
+therefore, we can use these networks to predict properties of other galaxies.
+and whatever after correction of paper I will add
+
+%chapter 4
+In Chapter~\ref{ch: paper2}, we used SOM algorithm on data from high-redshift galaxies.
+We classified the template spectra of \citet{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
+similar to results from Chapter~\ref{ch: paper3}, since we need at least 22 neurons to separate 12 spectra types, we conclude that some of the spectra types have very similar features (\citet{Kinney96} types B and E, and types SB1 and SB2).
+We showed that network generated by SOM methods, can be used to identify new types of spectra in large surveys.
+Using trained networks, we classify a sample of 142 galaxies.
+the classification by SOM allow us to identify galaxies with SEDs similar to two or more morphological types.
+comparing our results with classifications from trained networks, shows this unsupervised method can classify all 142 spectra while, the supervised one failed to classify 37 out 142 galaxies. 
+properties of 142 galaxies shows better correlations in ..... compare to the other methods.
+these correlations are in agreement with morphological type of galaxies.
+
+%future work
+We can compare SFR tracers in many galaxies using SOM!
+In future work, we can use SOM on other galaxies, 
+we can show that SOM is a good tool to predict properties of galaxies and estimate values of unobserved quantities.
+better data with more coverage specially for PAHs.
+improving SOM by adding the uncertainty to analysis.
+
+\addcontentsline{toc}{section}{Bibliography}
+\bibliographystyle{apj.bst}
+\bibliography{western_bib.bib}

### 2016-07-17 image_paper3/text_files/image_texts/PAHS_or_not_PAHs.tex
fig.s and table corrections

\begin{figure}
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols11and26.png}
    \caption{Without PAHs}
    \label{fig: wt_pahs}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.8\textwidth}
    \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and10.png}
    \caption{Only PAHs}
    \label{fig: only_pahs}
    \end{subfigure}
    \caption[Two dimensional self-organizing map of M31 for no PAHs and only PAHs subsets]{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result of a) SOM from data excluding PAHs; b) SOM from PAHs data.}
    \label{fig: PAHS_or_not_PAHs}
\end{figure}

### 2016-07-17 image_paper3/text_files/image_texts/all.tex
fig.s and table corrections

\begin{figure}
        \centering
        \includegraphics[width=0.8\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and26.png}
    \caption[Two dimensional self-organizing map of M31 data]{Two dimensional SOM of M31 using $10\times10$ grid. Similar to Figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, the hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
    \label{fig: all_derived_ones}
\end{figure}

### 2016-07-17 image_paper3/text_files/image_texts/col3byall.tex
fig.s and table corrections

@@
-\begin{figure*}
+\begin{figure}
     \begin{subfigure}[b]{0.25\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: only_pahs} and \halpha} 
         \label{fig: col3and11_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and11_dist} and \oiii} 
         \label{fig: col3and12_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and12_dist} and \sii} 
         \label{fig: col3and13_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and13_dist} and IRAC~5.7~$\mu$m emission} 
         \label{fig: col3and14_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and14_dist} and PACS~100~$\mu$m emission} 
         \label{fig: col3and15_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and15_dist} and SPIRE~250~$\mu$m emission} 
         \label{fig: col3and16_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and16_dist} and SPIRE~350~$\mu$m emission} 
         \label{fig: col3and17_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and17_dist} and SPIRE~500~$\mu$m emission} 
         \label{fig: col3and18_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
+         \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and18_dist} and L$_{\mathrm{ Dust}}$} 
         \label{fig: col3and19_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
+          \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{\mathrm{ Dust}}$} 
         \label{fig: col3and20_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and20_dist} and SFR(FUV\ +\ 24\ $\mu$m)} 
         \label{fig: col3and21_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and21_dist} and M$_{\mathrm{ Stars}}$} 
         \label{fig: col3and22_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and22_dist} and L$_{\mathrm{ TIR}}$} 
         \label{fig: col3and23_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
+        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and23_dist} and M$_{\mathrm{ Total\ gas}}$.} 
         \label{fig: col3and24_dist}
@@
         \centering
-        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
+        \includegraphics[width=52mm, height=32mm ]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
+        \captionsetup{font=tiny}
+        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and RHI.} 
         \label{fig: col3and25_dist}
     \end{subfigure}
-    \caption{Results from increasing dimension of input data from 11 to 25}
+    \caption[Increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually]{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually.
+The order of input data is the same as the order of data in Fig.~\ref{fig: cor_cluster1}.}
     \label{fig: inc_D_col3s}
-\end{figure*}
+\end{figure}

### 2016-07-17 version0.0/appendixa_2.tex
fig.s and table corrections

--- 2016-07-15 version0.0/appendixa.tex
@@
-\chapter{SFR from H$\alpha$ plus 24 \um: procedure and result}
+\chapter{More results from the fitting of the extended Schmidt law}
 \pagestyle{plain}
-\label{app:halpha}
+\label{app:es,figs}
 \myappendices{
-As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps.
-These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive.
-Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.
-
-The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from H$\alpha$ using the scaling factor between fluxes in these two band passes determined by \citet{Azimlu11}.
-They estimated continuum emission in each H$\alpha$ image, using photometric measurements in both \halpha and R-band images, and determined the scaling factor.
-These images were observed from a ground-based telescope over two years' time.
-Consequently, there is a non-negligible sky contribution in the background which must be estimated and removed from each image in both bands.
-Unfortunately, there is no nearby `blank-sky' image taken with the same instrument available from which to measure the sky contribution, which makes the removal of background emission even harder.
-The only remaining choice is to subtract the local background for each region.
-However, subtracting local backgrounds from each image will result in a non-smooth background in the final mosaic image.
-
-\begin{figure*}
-\centering
-\includegraphics[width=164mm]{../image_paper1/halpha.pdf}
-\caption{Mosaic created using the Montage programme from six fields of H$\alpha$ emission images of M31 from \citet{Massey07}.
-The resulting image from Montage was continuum-subtracted and masked for all point sources.
-The centre of the galaxy was masked out due to saturation of data in the continuum $R$-band image.}
-\label{fig:halpha}
-\end{figure*}
-
-To create the final mosaic, first we removed the background from each region in both the \halpha and $R$-band images.
-The second step was to subtract the continuum from the \halpha images.
-Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image.
-At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin region in the centre of the galaxy.
-To account for the flux contribution of the [N II] emission we used the flux ratio ${\mathrm \nii}/{\mathrm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map.
-We created the final mosaic image, Figure~\ref{fig:halpha}, using the Montage program \citep{Berriman08}.
-
-Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}.
-In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
-The fitting results using SFR(\halpha $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers.
-The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data.
-Thus we did not include the SFR(\halpha $+$ 24~$\mu$m) in our final analysis.
-
-\newpage
-\section{More results from the fitting of the extended Schmidt law}
-\label{app:es,figs}
 Section~\ref{sec: sfl} discusses testing the extended Schmidt law and shows results for one SFR/gas tracer combination. Here we present the plots for the remaining SFR/gas tracer combinations.

### 2016-07-17 version0.0/asli.tex
fig.s and table corrections

@@
 \usepackage[byname]{smartref}
-\usepackage{hyperref} %comment out for hardcopy
+\usepackage{hyperref}%comment out for hardcopy
 \usepackage{txfonts}
@@
 %\usepackage{caption}
+\usepackage[font=small,labelfont=bf]{caption}
+\DeclareCaptionFont{tiny}{\tiny}
 \usepackage{subcaption}
@@
 \usepackage{chapterbib}
+\usepackage{adjustbox}
+
 \makeatletter
@@
 Pauline Barmby and collaborators: Dr.
-Sofia Lianue, Dr.
+Sofia Lianou, Dr.
 Hossein Teimoorinia, and Dr.
 Els Peeters.
-Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were greatly helpful.
+Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were priceless.
 
-{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.
+{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in {\em Monthly Notices of the Royal Astronomical Society}, Volume 456, Issue 4, 2016.
 
-{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.
+{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future. %TBD: change this if you change the title
 
-{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society.
+{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to {\em Monthly Notices of the Royal Astronomical Society}.
 }
@@
 
-\emph{To my parents, my sisters,}
-
-\emph{\& Matin,}
-
-\emph{for their unconditional love and support.}
+To my parents, my sisters, \& Matin, for their unconditional love and support.
 
@@
 
-\include{intro0.0}
+% \include{intro0.01}
  \include{paper1}
-\include{paper3}
-\include{paper2}
-\include{summary}
+%\include{paper3}
+%\include{paper2}
+% \include{summary}
 
@@
 % %Appendices.
-\begin{appendices}
-\include{appendixa}
-\include{appendixb}
-\include{appendixc}
-\end{appendices}
+% \begin{appendices}
+% \include{appendixa}
+% \include{appendixa_2}
+% \include{appendixb}
+% \include{appendixc}
+% \end{appendices}
 

### 2016-07-17 version0.0/intro0.0.tex
fig.s and table corrections

@@
 
-The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
+The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98b}. 
 The K-S law and similar empirical laws have been tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.

### 2016-07-17 version0.0/intro0.01.tex
fig.s and table corrections

@@
 \label{sec: overview}
-%what do we have inside galaxies:
-% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
+%what doIhave inside galaxies:
+% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
 Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
@@
 Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
-a plot of brightness/flux density of galaxies as a function of wavelength, call a spectral energy distribution (SED), is a useful tool to understand galaxies. 
+a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
 Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
@@
 Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
+%PB: changed "I" to "we" here - you are talking about the field as a whole, not you in particular
 
@@
 The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
-Studying the interstellar medium is not only essential to understanding the formation of stars, but also it is necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.
+Studying the interstellar medium is not only essential to understanding the formation of stars, but is also  necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.
 
-In a galaxy, like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot}$) in the ISM due to gravitational instabilities. 
+In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot}$) in the ISM due to gravitational instabilities. 
 The denser regions within GMCs collapse under their own gravity (self-gravity) and create clumps.
@@
 Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
-Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minizing $\chi^2$ or by Bayesian analysis), using the templates.
+Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
 One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
@@
 For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
-By integrating star formation history over a specific time scale, SFR can be derived. %PB: please check: integrate SFH to get SFR, or integrate SFR to get SFH?
+By integrating star formation history over a specific time scale, SFR can be derived.
 Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.
@@
 Studying star formation and its relation to other quantities in galaxies is the subject of ongoing research.
-In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
+In this chapter, I present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR.
 A discussion of the ISM and its role in star formation is presented in $\S$~\ref{sec: ism_intro}.
-In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}.
+In $\S$~\ref{sec: sfr_intro} I discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}.
 Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
-%% We or I?! %PB: use I
 
@@
 \label{sec: ism_intro}
-%how do we observe it
+%how do I observe it
 %what the observation tell us
-% how do we measure the dust and gas
+% how do I measure the dust and gas
 The interstellar medium in galaxies is a complex system with a wide range of structures, but these structures can be divided into two main components: gas and dust.
-The gas in the ISM of galaxies is mostly made of hydrogen and helium, with 1 per cent heavier elements (metals), and can be in the form of clouds or diffuse (diffused?) regions.
+The gas in the ISM of galaxies is mostly made of hydrogen and helium, with 1 per cent heavier elements (metals), and can be in the form of clouds or diffused regions.
 Gas clouds include molecular clouds, cold neutral atomic hydrogen (\hi) or hot \hi~clouds, and diffuse gas can be either \hii~(ionized hydrogen) regions or a hot intercloud medium.
@@
 Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds, and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
-Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Sec.~\ref{sec: extinction}).
+Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Section~\ref{sec: extinction}).
 
-Molecular clouds in the ISM are cold ($\sim10$ K) and dense ($ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
-Density in the molecular clouds is not uniform. There are dense and colds clumps inside these clouds.
+Molecular clouds in the ISM are cold ($T \sim10$ K) and dense (particle number density $ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
+Density in molecular clouds is not uniform. There are dense and colds clumps inside these clouds.
 Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars.
@@
 The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but these clouds also contain heavier elements such as carbon monoxide, hydrogen cyanide, water, ammonia and more than tens of others.
-Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds.
-In fact, most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state} and can be excited in the temperature of molecular clouds.%%Sr: I'll add more detail here
-Other heavier molecules have emission lines which are also detectable in the spectra of clouds (specially galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.
-their mass (see Sec.~\ref{sec: ismmap} for more details).
+Carbon monoxide (CO) molecules are the third-most abundant constituent of molecular clouds, and are easily observable.
+Other heavier molecules have emission lines which are also detectable in the spectra of clouds (especially Galactic ones), but observing CO emission is the most common way to study the properties of molecular clouds i.e.\ their mass (see Section~\ref{sec: ismmap} for more details).
 
@@
 Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}.
-Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
+%%SR: it is B stars not O ones!
+Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
 Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).
@@
 
-%\subsubsection{Molecular Clouds}
-%PB: some repetition from earlier subsection here. 
-The carbon monoxide molecule has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy. 
+Most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state}(the state of angular momentum, J) and can be excited in the temperature of molecular clouds.
+%PB: need to fix text in {\bf} earlier in this sentence.
 Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
-Therefore, CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][] {Sanders84}.
+Therefore, $^{12}$CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][]{Sanders84}.
 Higher rotational transitions of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.
@@
 where $D$ is the distance to the cloud and $I_{\mathrm CO}$ is the CO brightness temperature integrated over the line profile in K~km~s$^{-1}$.
-It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(k) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
+It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
 For a uniform cloud with a radius $R$, the CO luminosity is given by:
@@
 \centering
-\includegraphics[width=16cm]{../image_intro/mvirial_lco.pdf}
-\caption{Relation between the virial mass and CO luminosity for the Milky Way (dots), M33 (open circles), M31 (triangles), and IC~10 (squares) clouds.
-Virial masses are measured from selected high spatial resolution CO observations.
-The extragalactic molecular clouds are very similar to those in the Milky Way.
-Adapted from~\cite{Young91}.}
+\includegraphics[width=\textwidth]{../image_intro/mvirial_lco.png}
+\caption[Relation between the virial mass and CO luminosity]{Relation between the virial mass (M$_{\mathrm{vir}}$) and CO luminosity (L$_{\mathrm{CO}}$) for the Milky Way and extragalactic GMCs.
+The Milky Way data are shown by dots measured by~\cite{Solomon87}.
+Black and white symbols correspond to measurements based on $^{12}$CO~($J(2\rightarrow 1)$) and $^{12}$CO~($J(1\rightarrow 0)$), respectively.
+The black dashed line represents the Galactic mass-luminosity relation (M$_{\mathrm{vir}} \approx 39{\mathrm L}^{0.81}_{\mathrm{CO}}$) with gray region illustrating the Galactic 1$\sigma$ dispersion around the line.
+The dot-dashed and blue dashed lines show the fits for dwarf sample and all extragalactic GMCs, respectively.
+The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from~\cite{Bolato08}.}
 \end{figure}
@@
 Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
-Fig.~\ref{fig: mco} shows the CO luminosity verses virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
+Fig.~\ref{fig: mco} shows the CO luminosity versus virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
 The extragalactic molecular clouds are similar to those in the Milky Way. 
@@
 Problems regarding metallicity are not yet resolved and it is still not clear whether the conversion factor is global or local. 
-Extragalactic investigations have been limited to nearby galaxies due to resolution and sensitivity of telescopes. 
-To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40 pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and refrences therein]{Young91,Bolato13}.
+Extragalactic investigations have been limited to nearby galaxies due to telescope resolution and sensitivity. 
+To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40 pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and references therein]{Young91,Bolato13}.
 
-%%%and now
-
-Atomic gas in galaxies are dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
+Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
 Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
+%PB: should that be cm$^{-2}$ ?
 \begin{equation}
@@
 \end{equation}
-where $T_{\mathrm B}$ is the temperature brightness in Kelvins and dV is in Kms$^{-1}$, with the integral over the line profile. 
+where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
 These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
@@
 
-Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of data.
+Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of available observational data.
 \cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
@@
 The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-This (MH: This method? what does this refer to?) method is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.
+Using dust emission as a tracer of gas is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.
 
@@
 Dust in ISM affects stellar emission by attenuating, scattering or absorption.
-Attenuation refers to the effects of dust with embedded light sources distributed throughout. (MH Very unclear sentence)
-The dust itself can be clumpy or smooth. 
-Effect of dust clouds with embedded light sources on distribution of the light is called attenuation. (MH I though you defined attenuation two sentences ago, albeit unclearly.)
-The dust cloud could have any distribution and be clumpy or smooth. (MH Deja vu)
-Since both light source and dust have extended distribution, the relative location of the dust and light source affect the net absorbed and scattered light.
-The other parameters that are important for the scattering and absorption is the relative position of dust and observer.
+Effect of dust clouds with embedded light sources on distribution of the light is called attenuation. 
+The dust cloud could have any distribution and be clumpy or smooth. 
+Since both light source and dust have extended distributions, the relative locations of the dust and light source affect the net absorbed and scattered light.
+The other parameter that is important for the scattering and absorption is the relative position of dust and observer.
 When the dust is in the line of sight, attenuation will make the emerging light dimmer~\citep[e.g.][and references therein]{Calzetti13}.
-This is the typical occurring situation when studying galaxies or extended regions within galaxies.
+This is the typically occurring situation when studying galaxies or extended regions within galaxies.
 
@@
 \label{equ: extinction}
-{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)exp[-\tau_{\lambda}],
+{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}],
 \end{equation}
-where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction in $\lambda$.
-The extinction also depends on size of grains and extinction cross section.
+where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction at wavelength $\lambda$.
+%PB: extinction or optical depth?
+The extinction also depends on the grain size and extinction cross section.
 For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.
@@
 By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
-To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
+To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Section~\ref{sec: imf}).
 In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.
@@
 \end{equation} 
-where $M$ is the stellar mass, $\gamma$ is a power index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.
+where $M$ is the stellar mass, $\gamma$ is a power-law index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.
+%PB should that be $\log $M to $\log M + d\log M$ ?
+Please check mass range.
 
-In the late 70s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}.
+In the late 1970s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}.
 Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
@@
 \centering
-\includegraphics[width=16cm]{../image_intro/imf}
+\includegraphics[width=16cm]{../image_intro/imf.png}
 \small
-\caption{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity.
+\caption[Comparing stellar initial mass functions]{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity.
 The mass ranges from 0.1 to 120~M$_\odot$.
@@
 
-Since in using SFR calibration for different galaxies, we assume the initial mass function is universal, careful measurement of the IMF is the key factor in understanding the star formation rate. 
+Since in using SFR calibration for different galaxies, I assume the initial mass function is universal, careful measurement of the IMF is the key factor in understanding the star formation rate. 
 In distant galaxies, only massive stars can be detected; therefore, the IMF must be assumed to include all stellar mass ranges in the SFR calibrations. 
 To show the impact of the different stellar IMF assumptions on the SFR calibrations, \cite{Calzetti13} used two different stellar IMFs and derived the SFR calibrations with these new assumptions.
-Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30~M$_{\odot}$ instead of 100~M$_{\odot}$, changes the SFR calibration constants by factors ranging from 1.4 to 5.6 for different SFR indicators (Tab.~\ref{table1}).
+Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30~M$_{\odot}$ instead of 100~M$_{\odot}$, changes the SFR calibration constants by factors ranging from 1.4 to 5.6 for different SFR indicators (Table~\ref{table1}).
 
@@
 These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
-Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
+Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$~kpc of the Solar System. 
 The number of YSOs can be converted to SFR using: 
@@
 $<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
-$\tau$ is the lifetime of the YSO  $\tau \sim 2$Myr~\citep{Evans09}. 
-Since our current devises cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
+$\tau$ is the lifetime of the YSO  $\tau \sim 2$~Myr~\citep{Evans09}. 
+Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
 
 In theory, for any system with high enough spatial resolution, counting YSOs can be used as a tracer of the star formation. 
-However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky way with distance of 0.05 Mpc) can not be resolved.
+However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky Way at a distance of 0.05 Mpc) cannot be resolved.
 Therefore, most studies use the emission from the energetic young stars as a tracer of the SFR.
 
-%% to be continued
+%% and the continuation
+
+\subsubsection{Unresolved Star Formation Indicators}
+
+In star-forming regions farther away than the Magellanic Clouds, the spatial resolution of currently-available observations is not high enough to find all the young stellar objects. 
+In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to the young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}.
+\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar populations synthesis models~\citep[e.g.,][]{Bruzual93}.
+
+In unresolved systems, SFR indicators can be divided into local and global indicators. 
+The global SFR indicators are defined for the entire galaxy; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
+Local calibration is used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+Limitations in the spatial resolution of observational data on the one hand, and the broader applicability to distant galaxy populations on the other, have in the past brought more attention to the calibrations of global SFR compared to local SFR.
+Because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.
+
+\subsubsection*{SFR Indicators Based on Single-Band Emission}
+
+In order to derive conversions between the luminosity in specific wavelengths and the SFR, stellar population synthesis models are used~\citep{Kennicutt98b}. 
+The general form of a SFR calibration using single-band emission is: 
+\begin{equation}
+\label{equ: sfrsingle}
+{\rm SFR}(\lambda)= CL(\lambda),
+\end{equation}
+where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}).
+The constant $C$ varies for different wavelengths, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation is assumed to remain constant. 
+Table~\ref{table1}, from \cite{Calzetti13}, summarises some values of $C$ and their changes according to different assumptions about the IMF.
+
+\begin{center}
+\begin{table}
+\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
+\label{table1}
+\begin{tabular}{ c c c }
+\hline\hline
+Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
+\hline
+L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
+L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
+L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
+L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
+L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
+L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
+L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
+L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
+L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
+L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
+L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
+\hline
+\end{tabular}
+\begin{tablenotes}
+\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
+\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}.
+For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$ to convert luminosity density to luminosity.
+%or flux density?
+\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Section~\ref{sec: imf}), and for the timescale $\tau$.
+\end{tablenotes}
+\end{table}
+\end{center}
+
+The most common single-band tracer of star formation rate is the ultraviolet.
+As mentioned before, UV emission is an excellent tracer for the SFR.
+Using a spectral energy distribution (SED) from Starburst99, with solar metallicity, and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
+\begin{equation}
+SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
+\end{equation}
+where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ can be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
+As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
+The calibration constants' changes for shorter timescales are more significant and 
+the their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
+Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
+Therefore, using the UV emission as a tracer might lead to underestimation of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).
+
+Another single-band SFR indicator is the emission from hydrogen recombination lines. 
+Ionizing photons emitted from young massive stars ionize the surrounding gas.
+Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ ($0.6563 \mu$m) and H${\beta}$ ($0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}.
+The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived using quantum mechanics. 
+The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
+Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorb and re-emit via Ly${\alpha}$ and longer wavelengths.
+This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
+The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
+\begin{align}
+\label{equ: halpha}
+SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
+                     = 7.4 \times 10^{-54}Q(H^{\circ})
+\end{align}
+where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
+The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
+%PB: big $N$ (column density) or small $n$ (number density) ?
+Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
+The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
+by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
+
+Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
+Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
+As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
+\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
+Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
+In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
+\begin{equation}
+SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
+\end{equation}  
+where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
+Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
+In these galaxies, the \halpha emission line is redshifted out of the optical band.
+Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.
+
+Since interstellar dust absorbs approximately half of the starlight and re-emits in the infrared, the infrared emission can be used to trace the SFR.
+The IR luminosity of a system depends not only on the amount of embedded dust, but also on the heating rate provided by the stars. 
+Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order, the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
+The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
+Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.
+
+Two empirical single-band infrared star formation rate indicators are the 24~$\mu$m and 70~$\mu$m bands.  
+The use of these two bands depends on the type of the galaxy under study or the physical environment in different regions within the galaxy. 
+Since the luminosity of a stellar population with constant star formation increases with time, the IR emission, which is used as a tracer of the emission of the stellar population, has different calibration constants in the case of a global (the entire galaxy SFR indicator) or a local indicator.
+That is because the global case includes the integrated stellar population of a galaxy, while the other is calculated from regions with short star formation timescales such as \hii~regions, large star-forming complexes, etc.~\cite{Calzetti13}.
+Table~\ref{table2} shows the constant $C$ from Equ.\ref{equ: sfrsingle} for 24~$\mu$m and 70~$\mu$m luminosities, for local (spatial scale $\sim500$~pc for 24~$\mu$m and $\lesssim 1$ kpc for 70~$\mu$m) and global cases.
+\begin{center}
+\begin{table}
+\caption{Infrared luminosity to star formation rate calibrations}
+\label{table2}
+\begin{tabular}{ c c c c }
+\hline\hline
+Luminosity$^1$ & $C$ & Assumptions & References\\ 
+\hline
+L(24)$^{0.885}_{local}$ & $1.31 \times 10^{-38}$ &$1.10\times 10^{40} \le L(24) \le 3.10\times 10^{44}$&  \cite{Calzetti07}   \\ 
+L(24)$_{global}$ & $2.04 \times 10^{-43}$ &$ 4.10\times 10^{42} \le L(24)  \le 5.10\times 10^{43}$& \cite{Calzetti07} \\
+L(70)$_{local}$ & $9.4 \times 10^{-44} $ &$5.10\times 10^{40} \le  L(70) \le 5.10\times 10^{43}$& \cite{Li12} \\
+L(70)$_{global}$& $5.9 \times 10^{-44}$ &$L(70) \ge 1.4 \times 10^{42} $& \cite{Li10}\\
+\hline
+\end{tabular}
+\begin{tablenotes}
+\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda}$ in erg s$^{-1}$.
+\end{tablenotes}
+\end{table}  
+\end{center}
+
+\subsubsection*{SFR Indicators Based on Multi-Band Emission}
+
+%%add PAHs here
+Despite the usefulness of having single-band SFR tracers, in many cases the corrections due to dust effects and luminosity ranges increase the uncertainty in measurements.
+Nowadays, thanks to large surveys, enormous amounts of data are available at different wavelengths for galaxies, which allows for combining the emission from different bands and finding new calibrations.
+The conversion between SFR and luminosities in multiple bands mostly helps to avoid problems regarding dust extinction or attenuation (see~\ref{sec: ism_intro}). 
+The simplest possible way to combine luminosities at different bands in order to convert them to SFR is through a linear relation, for which the correlation with the SFR is empirically derived~\citep{Kennicutt12}.
+
+The emission from dust heated by young stars changes by the amount of high energy photon emitted toward the dust and by the properties of the dust such as the grain size.
+Therefore, calibration of SFR varies for each of the single-band IR emissions.
+Assuming that dust heating is dominated by emission from young stars stellar, integrating over the full wavelength range of the infrared part of the spectrum reveals the total infrared (TIR) emission of the system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
+
+TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
+\cite{Boquien10} modified calibration of the total infrared luminosity as: 
+\begin{equation}
+L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m),
+\end{equation}
+where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
+\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
+\begin{equation}
+\label{sfr_tot_IR}
+SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR),
+\end{equation}
+where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.
+
+In Sec~\ref{sec: overview} I mentioned that emission from PAHs in ISM can be used as an SFR indicator~\citep[e.g.][]{Peeters04}.
+Most studies used emission in broad infrared bands, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using only the PAH features.
+\cite{Shipley16} calibrated SFR using observations from 105 star-forming galaxies with $z < 0.4$ as:
+\begin{equation}
+\log SFR = A + B \log L_{\mathrm{PAH}, \lambda},
+\end{equation}
+where $L_{\mathrm{PAH}, \lambda}$ is the luminosity of the PAH features at 6.2, 7.7, 11.3~$\mu$m or combinations thereof, in erg~s$^{-1}$.
+Table~\ref{table_PAH} shows the constants for each $L_{\mathrm{PAH}, \lambda}$.
+These calibrations underestimate the SFR for low-redshift galaxies with IR luminosity more than $10^{12}$~erg~s$^{-1}$.
+\cite{Shipley16} showed that using the 7.7~$\mu$m feature in the calibration reduces the scatter and concluded that this wavelength provides the most robust SFR tracer.
+
+\begin{center}
+\begin{table}
+\caption{SFR calibrations from PAH luminosities; adopted from~\cite{Shipley16}}
+\label{table_PAH}
+\begin{tabular}{ l c c}
+\hline\hline
+PAH Feature(s) & A & B\\
+\hline
+6.2 + 7.7 + 11.3 & $ -42.56 \pm 0.03 $ &  $1.00 \pm 0.03$ \\ 
+6.2 & $ -40.06 \pm 0.09 $ &  $0.96 \pm 0.04$ \\ 
+7.7 & $ -42.38 \pm 0.06 $ &  $1.00 \pm 0.03$ \\ 
+11.3 & $ -44.14 \pm 0.08 $ &  $1.06 \pm 0.03$ \\ 
+6.2 + 7.7 & $ -42.05 \pm 0.04 $ &  $0.99 \pm 0.03$ \\ 
+6.2 + 11.3 & $ -42.52 \pm 0.05 $ &  $1.01 \pm 0.03$ \\ 
+7.7 + 11.3 & $ -42.85 \pm 0.04 $ &  $1.01 \pm 0.03$ \\ 
+\hline
+\end{tabular}
+\end{table}  
+\end{center}
+
+The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used.
+This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
+\begin{equation}
+L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR},
+\end{equation}
+where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements.
+$\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}.
+The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.p][]{Hao11, Leroy08}.
+
+Another common method for using the multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
+This combination gives a more accurate dust-corrected estimate of the SFR~\citep{Kennicutt09}:
+\begin{equation} 
+\label{equ: halphaplus24}
+SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24)]
+\end{equation}
+where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. 
+L(24) is the 24~$\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$~yr$^{-1}$.
+
+The IR emission in the other band can be used for correcting dust effect on UV or \halpha~emission (see Table~\ref{table3}). 
+The corrected emission then can be used as a SFR tracer.
+These composite SFR indicators also have systematic uncertainties; yet, it seems that there is a good correlation between multi-band tracers and single-band tracers. 
+Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.
+
+\begin{center}
+\begin{table}
+\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
+\label{table3}
+\begin{tabular}{ c c}
+\hline\hline
+Combined luminosities$^1$ & references\\
+\hline
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\ % use \cite
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& \cite{Hao11}\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& \cite{Hao11}\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& \cite{Hao11}\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& \cite{Kennicutt09}\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& \cite{Kennicutt09}\\
+\hline
+\end{tabular}
+\begin{tablenotes}
+\item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda}$ in erg~s$^{-1}$ 
+\end{tablenotes}
+\end{table}  
+\end{center}
+
+As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
+From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
+This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than any other part of the spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
+Furthermore, reaching an asymptotic value of ionizing photons takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
+Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR the calibration constants are fairly close to each other.
+On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a 10\% difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$.
+As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.
+
+Our understanding of star formation in extragalactic systems depends on the light emitted by those systems.
+While emissions from massive and young stars are the dominating light of the system, mass of low-mass stars dominates the mass of the regions (see Section~\ref{sec: imf}).
+Therefore, SFRs are calibrated based on the dominant light of the systems and low-mass stars are accounted for using the initial mass function.
+Emission from star forming regions should be corrected before it can be used in calibrations.
+On its way to the Earth this emission passes through dust and gas clouds which cause extinction or attenuation (see ref.~\ref{sec: extinction}).
+On the other hand, evolved stars emit their light in the whole spectrum as well as the  UV. 
+Therefore, even though it might have an insignificant part in UV emission from galaxies, a correction for emission from evolved stars should be considered~\citep{Leroy08}.
+After measuring the corrected luminosities for star forming regions in galaxies (global or local), using proper calibrations can give the best estimation of SFR in galaxies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%Stellar Mass%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Stellar mass}
+\label{sec: starmass_intro}
+One of the most fundamental physical parameters that describes the present state of a galaxy is its stellar mass. 
+Stellar mass is linked to the structure and star formation history of disc galaxies~\citep{Gavvazi96} and  galaxies of all morphologies~\citep{Scodeggio02}. 
+Measuring the mass of a stellar population is indirect and subject to significant uncertainties. 
+In principle there are two ways to measure stellar mass in galaxies. 
+The first is measuring the dynamical mass of a galaxy using kinematics (the motion of stars)~\citep{Cappellari06} or gravitational lensing (the bending of light as it passes near a galaxy)~\citep{Auger09}, and then modeling the mass of the dark matter and subtracting it from the measured mass.
+The second method is based on stellar population models~\citep[e.g.][]{Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, such as luminosity in different wavelengths, colours, or spectral energy distribution.
+Stellar population models predict the expected SEDs for stellar populations based on the parameters of the regions such as star formation history, metallicity, and IMF.
+Uncertainties come from the uncertainties in the stellar initial mass function (see Section~\ref{sec: imf}), the stellar evolution models (especially the stage where stars have the most luminosity in their evolution), the evolutionary state of the galaxy~\citep[see][and references therein]{Dalcanton12}, and star formation histories.
+
+In order to translate between photometry and stellar mass, the stellar mass-to-light ratio ($M/L$) is needed.
+The use of $M/L$ is one way to measure the stellar mass surface density. 
+It is an indirect method and has high uncertainties in specific cases, but can help in studying the stellar mass in large samples. 
+For integrated galaxy light, the $M/L$ is estimated using scaling relations between $M/L$ and broadband colours \citep[e.g.][]{Bell03}, and then multiplying this ratio by luminosity to estimate the mass.
+For resolved galaxies, one can produce a map of the stellar mass surface density distribution in galaxies using resolved colours to measure spatial variations in $M/L$.
+This method gives more accurate results than measuring the stellar mass surface density distribution from single-band images that are rescaled by a uniform mass to light ratio~\citep{Zibetti09}.
+
+Comparing results from independent methods to measure stellar mass helps to determine whether there are any systematic differences.
+Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few tens per cent~\citep{McLaughlin05}.
+Therefore, to model subtleties, the advantages and disadvantages of using each method should be carefully considered.
+
+\subsection{Galaxy masses from dynamics}
+
+The simplest and the most common way to estimate the mass of a galaxy is to assume that the dynamics of the galaxy are governed by simple Newtonian classical physics.
+In this model, the circular velocity $v_{\rm circ}(r)$ of an orbit with radius $r$ within a spherical system of gravitational potential $\phi$ and mass $M$ is given by:
+\begin{equation}
+\label{eq: simpmass}
+v^2_{\rm circ}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r},
+\end{equation}
+where $G$ is the gravitational constant and $M(r)$ is the total mass within a sphere of radius $r$. 
+For a flattened disk, which is the case in most spiral galaxies, the right hand side of Equ.\ref{eq: simpmass} is replaced by the more exact expression derived by~\cite{Freeman70}. 
+For the case of no dark matter or bulge, \cite{Freeman70} showed that the rotation curve of a self-gravitating disk is:
+\begin{equation}
+v^2_{circ}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)],
+\end{equation}
+where $\Sigma_0$ the central surface brightness, $R_d$ is the disk scale length where the ratio of the intensity of disk to bulge is equal to $e$.% ($\sim$2.71).
+%PB: don't need to define e, but do need to define $R$ !!
+$y$ is equal to $\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are  modified Bessel functions of the first and second kinds.
+
+The mass distribution in disk galaxies is usually calculated from rotation curves or integrated line profiles from emission lines such as H${\alpha}$, CO, or \hi. 
+Integrated line widths only yield an estimate of total mass within some (uncertain) isophotal radius.
+Thanks to the current generation of detectors, it is now possible to obtain very high-resolution spectra in the \halpha and CO lines over the most of the optical disks of galaxies.
+
+A detailed description of calculating dynamical masses in galaxies is beyond the scope of this work. 
+The methods mentioned here represent the first order of approximation. 
+For more accurate results, one should consider non-circular rotational velocities and the fact that galaxies contain millions of stars plus interstellar objects; therefore simple two-object Newtonian physics is not sufficient.
+A detailed review of dynamical masses of galaxies can be found in \citet{Courteau13}.
+
+\subsection{Galaxy masses from stellar population modelling}
+
+Galaxies can be observed because of their stellar emission; stars radiate the energy produced from nuclear reactions in their cores. 
+Given a star's initial mass, the theory of stellar evolution can describe the amount of released energy. 
+Hence, stellar mass that is responsible for radiation of stars can be derived by modelling the spectral energy distributions of galaxies. 
+However, some fraction of the mass of galaxies consist of evolved stars which no longer emit radiation yet still contribute to the galaxy mass as stellar remnants and should be considered in the models.
+Stellar population synthesis models are used to predict the SED of a stellar population using many physical parameters. 
+Some of these parameters, which control the time evolution of the stellar population, are age ($t$) of the population measured in years (also referred to as the time passed since the star formation began), IMF, and metallicity~\citep{Courteau13}.
+
+The basic idea behind finding a suitable calibration between flux/luminosity of the stars in different wavelengths and stellar mass is that one can use the SFHs recovered from synthesizing the stellar optical colour-magnitude diagrams in different regions of a galaxy.
+The calculated stellar mass in nearby galaxies can be used to calibrate the fluxes from the stars in other galaxies.
+\cite{Zibetti09} suggested that to reach the maximum spatial resolution one can recombine the photometric information on a pixel-by-pixel basis. 
+They used this method to study the stellar mass distribution in galaxies as well as the dependence of the SED on stellar mass density.
+To do so the surface density of stellar mass at each position is derived by 
+\begin{equation}
+\label{equ: massphot}
+\Sigma_{{\mathrm M_\star}} (\alpha, \delta) = \Sigma_{\lambda}(\alpha, \delta) \gamma_{\lambda}(\alpha, \delta),
+\end{equation}
+where $\alpha$ and $\delta$ are sky position (right ascension and declination, respectively).
+$\Sigma_{{\mathrm M_\star}} (\alpha, \delta)$ is the stellar surface density.
+$\Sigma_{\lambda}(\alpha, \delta)$ is the surface brightness and $\gamma_{\lambda}(\alpha, \delta)$ is the effective stellar $M/L$ at an effective wavelength $\lambda$.
+In Equ.\ref{equ: massphot},  $\gamma_{\lambda}$ can be described as a function of one or more colours as observed at the specified location in galaxy.
+
+The peak of emission from evolved stars is in the near-infrared part of the spectrum.
+Therefore, many studies have tried to make a map of stellar mass distribution using this bandpass within galaxies~\citep[e.g.,][]{Elmgreen84}.
+Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps to have a more accurate calibration.
+Fluxes from 3.6 and 4.5~$\mu$m are suitable for calibration of the stellar mass, due to fact that these two band-passes not only trace evolved stellar population but are also almost insensitive to the emission from young stellar population and to dust absorption and emission.
+\cite{Zhu10} used the Sloan Digital Sky Survey~\citep[SDSS][]{York00} and the \Spitzer Wide-area Infrared Extragalactic Survey~\citep[SWIRE;][]{Lonsdale03} to find a calibration between galaxy luminosity and stellar mass.
+Using the $M/L$ of galaxies, they found correlations between $K_s$ band (2.2~$\mu$m), 3.6 and 4.5~$\mu$m band luminosities and stellar masses and formulated these correlations as:
+\begin{align} %PB: does this need a \begin{equation} ??
+\label{equ: zhu1}
+\log M_{\star} = -1.60  + 1.12  \log \nu L_{\nu}[K_s]\\
+\log M_{\star} = -0.79 + 1.19 \log \nu L_{\nu}[3.6\mu \rm m]\\
+\label{equ: zhu3}
+\log M_{\star} = -0.25 + 1.15\log \nu L_{\nu}[4.5\mu \rm m], 
+\end{align}
+where M$_{\star}$ is the stellar mass in solar masses and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg~s$^{-1}$ at a specified wavelength.
+
+\cite{Eskew12} tested the 3.6- and 4.5 $\mu$m fluxes as proxies for stellar mass in the Large Magellanic Cloud and found an empirical relation between mass of the stars and the luminosities of stars as:
+\begin{equation}
+\label{equ:eskew}
+  M_{\star} = 31.84 \times 10^{5.65} L_{3.6}^{2.85} L_{4.5}^{-1.85},
+ %\log M_{\star} = 5.6 +2.85\log (F_{3.6})-1.85 \log (F_{4.5})+2\log \left(\frac{D}{0.05}\right)
+\end{equation}
+where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$~$\AA^{-1}$.
+Equ.~\ref{equ: zhu1}--~\ref{equ: zhu3} were derived from a large sample of galaxies and tested on different types of regions and galaxies.
+On the other hand,~\cite{Eskew12} mentioned that since their calibration is based on data from the Magellanic Clouds,
+measuring the stellar mass from Equ.~\ref{equ:eskew} might break down for highly star-forming regions; moreover, this equation has not been tested on regions with different metallicities. 
+In more recent work,~\cite{Laura16} measured stellar mass for a group of galaxies with ($z < 0.035$) and showed they are tightly correlated with stellar mass measured from other calibrations.
+%PB: how measured?
+What is "they" ?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%Preview%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Preview}
+\label{sec: pre_intro}
+
+A complete picture of how galaxies are formed and evolve is tied to unfolding the mystery of the formation of stars.
+Various phenomena affect the collapse of molecular clouds and star formation, including the environment of the star-forming region, chemical composition of the region, the initial density distribution of the gas and the mass of stars in galaxies.
+For decades, observational, theoretical, and numerical studies have investigated star formation; nevertheless, their results are not in agreement.
+Empirical studies are used alongside theoretical ones to find laws that indicate the relations between physical properties of galaxies and star formation.
+
+The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (K-S) law~\citep{Schmidt59, Kennicutt98a}. 
+The K-S law and similar empirical laws have been tested on local and high-redshift galaxies with various morphological types, local and global scales and different ISM types~\citep[e.g.][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
+Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are still undetermined and there is no definitive answer to whether or not there is a universal star formation law.
+Their dependence on physical properties of galaxies is nontrivial, and sometimes differs by the type of star forming region.
+Although a relation between star formation and gas is well established, the details of this relation are not clear:
+different types of gas affect SFR in different ways, and variations in metallicity alter the effects.
+There is no fully sampled and universal IMF, in fact there is an ongoing debate on whether the IMF is universal or not.
+The influence of evolved stars and distance of star forming regions from the centre of galaxies on SFR has been mentioned in studies but not fully investigated.
+Besides studying the impact of the aforementioned properties of galaxies on SFR, searching for other relations between properties of galaxies and their star forming regions continues.
+
+Advances in observing facilities, image quality, and methodology expand our knowledge of star formation. 
+In the past few decades, the use of advanced statistical methods in astronomical studies has also grown.
+Applying modern statistical methods to star formation studies can shed light on unsolved problems in this field. 
+Studies show that using different statistical methods can change our perspective on star formation laws. 
+For example,~\cite{Shetty13} used Bayesian methods to show that the K-S law is not universal. 
+Since astronomy is a data-driven science, data-mining methods can be quite useful to gain new insights on properties of star-forming regions. 
+However, these methods have not been widely-applied to studies of nearby galaxies, where the most detailed information about star formation is available.
+
+In this thesis, I present three projects that study the effects of galaxy properties on star formation.
+I use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
+Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
+In addition to the Kennicutt-Schmidt law, I study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
+I also show the effect on star formation laws by using different SFR and ISM gas tracers.
+In Chapter~\ref{ch: paper3}, I explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
+I cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
+During this process, I find hidden structures in high-dimensional data space.
+In Chapter~\ref{ch: paper2}, I move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
+I train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
+Then I study the grouped properties of the classified galaxies.
+I summarize these results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}
+
+\addcontentsline{toc}{section}{Bibliography}
+\bibliographystyle{apj.bst} 
+\bibliography{ref_intro}

### 2016-07-17 version0.0/paper1.tex
fig.s and table corrections

--- 2016-07-13 version0.0/paper1.tex
@@
 The first attempt at scaling the star formation rate was to find a relation between the total star formation rate (SFR) and the mass of interstellar gas.
-\citet{Schmidt59} proposed a power-law relation between SFR and the gas mass ($M_{\rm gas}$) with {\it N} as the power law exponent.
+\citet{Schmidt59} proposed a power-law relation between SFR and the gas mass ($M_{\mathrm gas}$) with {\it N} as the power law exponent.
 Since then, for more than 50 years empirical star formation laws (relations) have been investigated using both observational data and numerical simulations.
-Later, \citet{Kennicutt98a} examined H$\alpha$, H\,{\sc I}, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies.
+Later, \citet{Kennicutt98a} examined H$\alpha$, H\,{\textsc i}, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies.
 He showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with a power-law exponent of $1.4 \pm 0.15$.
@@
 The use of different methods and data results in measuring different values for the power-law index.
-In a recent study of the K-S law in M31, \citet{Ford13} tested this law on six annular regions using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus H\,{\sc I}, and total gas calculated from dust emission).
+In a recent study of the K-S law in M31, \citet{Ford13} tested this law on six annular regions using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus H\,{\textsc i}, and total gas calculated from dust emission).
 The measured power-law indices for each map and region vary between 0.6 to 2.03.
@@
 This map covers a 2\degr $\times$ 0\degr.5 region with an angular resolution of 23\arcsec and has the smallest coverage of the galaxy among the maps we used in this paper.
-In this study, we also used a 21-cm emission map of the atomic gas (H\,{\sc I}) in M31 from \citet{Chemin09}.
+In this study, we also used a 21-cm emission map of the atomic gas (H\,{\textsc i}) in M31 from \citet{Chemin09}.
 This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.
@@
 Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators.
-Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\sun$.
+Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.
 
 In this project we used values based on the Kroupa IMF as is standard in the field, although discussion continues on whether the IMF is universal \citep{Bastin10}.
-Where necessary we converted from calibration values based on the Salpeter IMF by multiplying by 0.67  \citep{Madau14}.
+Where necessary we converted from calibration values based on the Salpeter IMF by multiplying by 0.67~\citep{Madau14}.
 
@@
 On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars.
-This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}.
+This emission is sensitive to the star formation timescale of $<10$ Myr \citep{Calzetti07}.
 The FUV band of \Galex and the 24 \um band of \Spitzer were used to measure the SFR for stars with ages $<100$~Myr calibrated by \citet{Hao11}  using nearby galaxies and the~\citet{Kroupa03} IMF as:
@@
 \label{equ: fuvplus24}
-SFR =4.46\times10^{-44}[L(FUV)_{\rm obs}+3.89L(24\mu m)],
+SFR =4.46\times10^{-44}[L(FUV)_{\mathrm obs}+3.89L(24\mu m)],
 \end{equation}
-\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\rm obs}$ are in erg~s$^{-1}$.
-L(FUV)$_{\rm obs}$ is the luminosity of the galaxy in the FUV.
+\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$.
+L(FUV)$_{\mathrm obs}$ is the luminosity of the galaxy in the FUV.
 The subscript "obs" indicates that the FUV emission is not corrected for extinction.
@@
 We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission.
-This process results in masking about 3\% of the pixels within a 25 kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR.
+This process results in masking about 3 per cent of the pixels within a 25~kpc radius from the centre in the FUV$_{obs}$ map, which leads to a slight underestimate of the total SFR.
 Then we smoothed the FUV$_{obs}$  map to have the same angular resolution and pixel size as the MIPS 24~$\mu$m, and masked the same regions in the 24 \um map as in the FUV$_{obs}$  map.
@@
 
-\begin{figure*}
+\begin{figure}
     \centering
-       \includegraphics[width=164mm]{../image_paper1/sfr_fir.eps}
+       \includegraphics[width=\textwidth]{../image_paper1/sfr_fir.eps}
     \caption {SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}).
@@
     \label{fig:sfrs}
-\end{figure*}
+\end{figure}
 
@@
 \label{equ: halphaplus24_g}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24\mu m)],
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{\mathrm obs} + 0.020L(24\mu m)],
 \end{equation}
-\noindent where L(H${\alpha}$)$_{\rm obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
+\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
 L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$.
@@
 Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc and is what we used for testing the SFR laws in local regions.
-The total M31 SFR calculated from summing pixel values and applying equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\sun$~yr$^{-1}$, which is in good agreement with previous studies.
+The total M31 SFR calculated from summing pixel values and applying equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\odot$~yr$^{-1}$, which is in good agreement with previous studies.
 
@@
 \noindent where L(8), L(24), L(70), and L(160) are the luminosities of the galaxy at 8 $\mu$m, 24~$\mu$m, 70~$\mu$m, and 160~\um in units of erg~s$^{-1}$.
-We used results from equation~\ref{equ: TIR} in the equation~\ref{equ:sfr_fir} to calculate our final map of the M31 SFR (Figure~\ref{fig:sfrs}).
+We used results from equation~\ref{equ: TIR} in the equation~\ref{equ:sfr_fir} to calculate our final map of the M31 SFR (Fig.~\ref{fig:sfrs}).
 Using this method, we calculated the total SFR by adding all the pixels to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$.
@@
 
-\begin{table*}
+\begin{table}
 \begin{minipage}{100mm}
@@
 \end{minipage}
-\end{table*}
+\end{table}
 
@@
 \label{equ:conversion}
-\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/[{\rm K km s^{-1}}],
+\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/[{\mathrm K km s^{-1}}],
 \end{equation}
@@
 The X-factor could be different in regions within a galaxy due to varying metallicity \citep{Wilson95, Bosselli02, Bolato13}.
-In the case of M31, different values of X-factor in the range of ($1-5.6 \times 10^{20}$) were adopted in previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant difference in X-factor leads to horizontal changes in a plot of log(SFR) versus log($\Sigma_{\rm {gas}}$) and does not affect our power-law indices for molecular gas, we chose $X_{\rm {CO}}= 2 \times 10^{20}$.
+In the case of M31, different values of X-factor in the range of ($1-5.6 \times 10^{20}$) were adopted in previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant difference in X-factor leads to horizontal changes in a plot of log(SFR) versus log($\Sigma_{\mathrm {gas}}$) and does not affect our power-law indices for molecular gas, we chose $X_{\mathrm {CO}}= 2 \times 10^{20}$.
 This is the same value that is adopted in many other works \citep[e.g.][]{Ford13, Smith12}.
-Since H\,{\sc I} mass dominates over the H$_2$ mass in M31, the constant X-factor has a negligible effect on the total gas mass.
+Since H\,{\textsc i} mass dominates over the H$_2$ mass in M31, the constant X-factor has a negligible effect on the total gas mass.
 
@@
 \label{equ:total_gas}
-\rm M_{\rm \bld {total \, gas}} = 1.36[M_{\rm H I}+M_{H_2}],
+\rm M_{\mathrm{total \, gas}} = 1.36[M_{\mathrm H I}+M_{H_2}],
 \end{equation}
-\noindent where the factor of 1.36 is a constant that takes into account the contribution of He and other heavier elements to the total gas mass, M$_{\rm H\,{\sc I}}$ is the mass of neutral hydrogen that was obtained from 21 cm observations (the map, which we got from \citet{Chemin09}, has units of number density which we used to calculate mass density of H\,{\sc I}), and M$_{H_2}$ was calculated from equation~\ref{equ:conversion} in units of M$_{\sun}$/pc$^2$.
-We assumed a gas mass of zero for regions where data for  either M$_{\rm H\,{\sc I}}$ or M$_{H_2}$ was not available, due to differences in coverage or bad pixels, etc.
+\noindent where the factor of 1.36 is a constant that takes into account the contribution of He and other heavier elements to the total gas mass, M$_{\mathrm H\,{\textsc i}}$ is the mass of neutral hydrogen that was obtained from 21 cm observations (the map, which we got from \citet{Chemin09}, has units of number density which we used to calculate mass density of H\,{\textsc i}), and M$_{H_2}$ was calculated from equation~\ref{equ:conversion} in units of M$_{\odot}$pc$^{-2}$.
+We assumed a gas mass of zero for regions where data for  either M$_{\mathrm H\,{\textsc i}}$ or M$_{H_2}$ was not available, due to differences in coverage or bad pixels, etc.
 In this case the above equation gives a lower limit for the total gas; this applies to regions beyond 18~kpc from the galaxy centre.
@@
 \label{sec:starmass}
-\begin{figure*}
+
+\begin{figure}
 \centering
-\includegraphics[width=164mm]{../image_paper1/star.eps}.
+\includegraphics[width=\textwidth]{../image_paper1/star.eps}
 \caption{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
 \label{fig:stellarmass}
-\end{figure*}
+\end{figure}
 
@@
 We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $F_{3.6 \mu m}$ and $F_{4.5 \mu m}$, though this was not mentioned in the aforementioned paper.
-Figure~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image.
+Fig.~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image.
 Using the coverage map of the IRAC 3.6~\um data, we used only pixels with coverage of more than 2 images per sky position, and replaced the rest with zero M$_{\odot}$.
-The replaced pixels include less than 8\% of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1\%.
-Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6\%.
+The replaced pixels include less than 8 per cent of the data;  since these pixels are mainly  in regions with low surface brightness, their effect on the final total mass is less than 1 per cent.
+Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6 per cent.
 This result is in fairly good agreement with the results of \citet{Tamm12}.
-They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56\% of which is in the disk with the rest in the bulge of the galaxy.
+They calculate the stellar mass of M31 to be $(10-15) \times 10^{10}$M$_{\odot}$, 56 per cent of which is in the disk with the rest in the bulge of the galaxy.
 In their recent work on the stellar mass of M31, \cite{Viaene14} measured the total stellar mass using the integrated fluxes to be $5.49 \times 10^{10}$M$_{\odot}$, which is in good agreement with our result.
@@
 The metallicity of a galaxy can be estimated by measuring abundances of heavier elements in its ISM. 
-It is common to use  gas phase oxygen abundance, $[{\rm O/H}]$, as a gauge to determine metallicity \citep[e.g.][]{McGaugh91, Zaritsky94}. 
-Results from modelling dust in the Milky Way and nearby galaxies showed that the dust to gas mass ratio depends on $[{\rm O/H}]$ and, consequently, on metallicity \citet{Draine07}.
+It is common to use  gas phase oxygen abundance, $[{\mathrm O/H}]$, as a gauge to determine metallicity \citep[e.g.][]{McGaugh91, Zaritsky94}. 
+Results from modelling dust in the Milky Way and nearby galaxies showed that the dust to gas mass ratio depends on $[{\mathrm O/H}]$ and, consequently, on metallicity \citet{Draine07}.
 \citet{Draine14} assumed that depletion of gas elements from the gas to the diffuse ISM in M31 is similar to the Milky Way, and proposed that:
@@
 \citet{Draine14} produced two dust maps of M31 using MIPS-160 resolution (FWHM  39\arcsec; 18\arcsec $\times$ 18\arcsec pixels) and SPIRE 350 resolution (FWHM 24\arcsec.9; 10\arcsec $\times$ 10\arcsec pixels), which are publicly available.
-We used the dust map with SPIRE 350 resolution, convolved and re-gridded  to have the same resolution and pixel size for the H\,{\sc I} map, then divided this dust mass by the mass of hydrogen in M31.
+We used the dust map with SPIRE 350 resolution, convolved and re-gridded  to have the same resolution and pixel size for the H\,{\textsc i} map, then divided this dust mass by the mass of hydrogen in M31.
 However, in a private correspondence with the author, Draine pointed out that based on the Planck observations of Milky Way dust \citet{Tauber10}, the dust mass surface density map estimated for M31 by \citet{Draine14} may be systematically high by a factor of 2.
@@
 \citet{Draine14} showed that with increasing distance from the centre of M31, the dust to H mass ratio declines monotonically and concluded that metallicity also behaves in the same way.
-Their fitting results showed that M31 can be divided into three regions ($R< 8~\kpc$, $8~\kpc < R < 18~\kpc$, and $18~\kpc < R \la 25~\kpc$) where the dust to H mass ratio (or metallicity) has a different correlation with galactocentric distance.
+Their fitting results showed that M31 can be divided into three regions ($R< 8~\kpc$, $8~\kpc < R < 18~\kpc$, and $18~\kpc < R < 25~\kpc$) where the dust to H mass ratio (or metallicity) has a different correlation with galactocentric distance.
 
@@
 %=164mm, height=218mm
-\begin{figure*}
+\begin{figure}
 \centering
@@
 The colour represents the density of the pixels, increasing from blue to red.
-The number of points among the three columns is different due to the different angular resolution of the H\,{\sc I} and H$_2$ maps.
-Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\sc I} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of 60\arcsec $\times$ 90\arcsec).
+The number of points among the three columns is different due to the different angular resolution of the H\,{\textsc i} and H$_2$ maps.
+Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc (for maps with resolution of 23\arcsec) while each point for which the surface density of H\,{\textsc i} or total gas mass is a tracer represents a region of size $\sim$155~pc (for maps with resolution of 60\arcsec $\times$ 90\arcsec).
 Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
 \label{fig:ks_all}
-\end{figure*}
+\end{figure}
 
@@
 In one approach we used all the available pixels over the galaxy; in  the other approach we compare the laws in three elliptical regions at different distances from the centre of the galaxy as described in Section~\ref{sec:metal}, assuming a position angle of 38\degr and inclination of 77\degr\ for M31.
-As mentioned in Section~\ref{sec: data_sfl}, since the H$_2$ gas mass map has higher angular resolution and smaller pixel size than the H\,{\sc I} gas mass map, our final results have two sets of different  angular resolutions and pixel sizes.
+As mentioned in Section~\ref{sec: data_sfl}, since the H$_2$ gas mass map has higher angular resolution and smaller pixel size than the H\,{\textsc i} gas mass map, our final results have two sets of different  angular resolutions and pixel sizes.
 
@@
 Uncertainties in H$_2$ mass were measured using the mean rms values of the  CO intensity, reported in \cite{Nieten06}.
-Uncertainties of the total gas map are calculated as the quadrature sum of the uncertainties in  H$_2$ and H\,{\sc I} masses.
+Uncertainties of the total gas map are calculated as the quadrature sum of the uncertainties in  H$_2$ and H\,{\textsc i} masses.
 
 We also tested each law on three different regions which were chosen in the same manner as explained in Section~\ref{sec:metal}.
-Applying the SFR laws in these regions provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws such as metallicity, gas mass, stellar mass gradients and changing the ratio of H$_2$ to H\,{\sc I}.
+Applying the SFR laws in these regions provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws such as metallicity, gas mass, stellar mass gradients and changing the ratio of H$_2$ to H\,{\textsc i}.
 
@@
 
-\begin{figure*}
+\begin{figure}
 
-\includegraphics[width=168mm , height=230mm]{../image_paper1/Results_all_3_regs_after_err_co.pdf}
-\caption{Same as figure~\ref{fig:ks_all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
-The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}%%
+\includegraphics[width=\textwidth]{../image_paper1/Results_all_3_regs_after_err_co.pdf}
+\caption{Same as Fig.~\ref{fig:ks_all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}%%
 \label{fig:ks,regs}
-\end{figure*}
+\end{figure}
 
-Figure~\ref{fig:ks_all} shows the pixel-by-pixel fitting of the K-S law on the whole galaxy.
-The first row of plots are the surface density of the SFR(TIR), which is calculated using the TIR emission from Section~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$), only atomic gas (H\,{\sc I}), and total gas from right to left, respectively.
+Fig.~\ref{fig:ks_all} shows the pixel-by-pixel fitting of the K-S law on the whole galaxy.
+The first row of plots are the surface density of the SFR(TIR), which is calculated using the TIR emission from Section~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$), only atomic gas (H\,{\textsc i}), and total gas from right to left, respectively.
 The only difference between the upper and the other rows is that in the lower rows the SFR indicator is FUV plus 24~$\mu$m (second row), and \halpha plus 24~$\mu$m emission (third row).
-Figure~\ref{fig:ks,regs} shows the same data as Figure~\ref{fig:ks_all}.
+Fig.~\ref{fig:ks,regs} shows the same data as Fig.~\ref{fig:ks_all}.
 However, in this figure we separated pixels from different regions in the galaxy by their colours.
- There is a deviation in the middle panel plots of Figure~\ref{fig:ks_all} which shows a set of points with with high star formation rate and low H\,{\sc I} gas.
-As can be clearly seen in middle panel of Figure~\ref{fig:ks,regs}, this deviation is due to regions within 8~kpc of the centre of the galaxy (red points).
+ There is a deviation in the middle panel plots of Fig.~\ref{fig:ks_all} which shows a set of points with with high star formation rate and low H\,{\textsc i} gas.
+As can be clearly seen in middle panel of Fig.~\ref{fig:ks,regs}, this deviation is due to regions within 8~kpc of the centre of the galaxy (red points).
  \cite{Braun09} saw a similar feature in their studies of the K-S law in M31. 
-The H\,{\sc I} surface density profile of M31 \citep[see figure 16 in][]{Chemin09} shows several local minima from the centre of M31 out to 30~kpc distance which could be a result of the H\,{\sc I} wrap.
-The H\,{\sc I} surface density map shows a lower density in the central regions compared to the ring area; on the other hand, the SFR maps show high densities in the central regions.
+The H\,{\textsc i} surface density profile of M31 \citep[see figure 16 in][]{Chemin09} shows several local minima from the centre of M31 out to 30~kpc distance which could be a result of the H\,{\textsc i} wrap.
+The H\,{\textsc i} surface density map shows a lower density in the central regions compared to the ring area; on the other hand, the SFR maps show high densities in the central regions.
 The combination of the relatively low gas and high SFR causes the deviation.
 However,~~\cite{Braun09} argued that the high 24~$\mu$m fluxes in the centre of the galaxy are due to other processes such as shock heating rather than a large amount of star formation.
-Since the total gas mass is calculated by adding H\,{\sc I} and H$_2$ gas mass, we can see this deviation in the right panel of Figure~\ref{fig:ks_all} as well.
+Since the total gas mass is calculated by adding H\,{\textsc i} and H$_2$ gas mass, we can see this deviation in the right panel of Fig.~\ref{fig:ks_all} as well.
 However, since we have H$_2$ emission in those regions these deviations are less prominent than the ones in the middle panel.
@@
 We took a similar approach for the extended Schmidt law.
-Figures~\ref{fig:es,all,fuv,tot}-~\ref{fig:es,regs,fuv,tot} and Figures~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} show the results of the pixel-by-pixel fitting of the extended Schmidt law.
+Fig.s~\ref{fig:es,all,fuv,tot}-~\ref{fig:es,regs,fuv,tot} and Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} show the results of the pixel-by-pixel fitting of the extended Schmidt law.
 For the extended Schmidt law, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly.
-In this series of plots, the $x$-axis is the gas mass surface density, either molecular gas (H$_2$), atomic gas (H\,{\sc I}), or total gas, the $y$-axis is the SFR(TIR), SFR(FUV + 24~$\mu$m) or SFR(H$\alpha$ + 24~$\mu$m), and the $z$-axis is the stellar mass surface density.
+In this series of plots, the $x$-axis is the gas mass surface density, either molecular gas (H$_2$), atomic gas (H\,{\textsc i}), or total gas, the $y$-axis is the SFR(TIR), SFR(FUV + 24~$\mu$m) or SFR(H$\alpha$ + 24~$\mu$m), and the $z$-axis is the stellar mass surface density.
 The shadows of the data on each surface are also plotted, to have a more clear picture of correlations between components.
-The shadows on the $x-y$ surface are the same as in Figure~\ref{fig:ks_all}.
+The shadows on the $x-y$ surface are the same as in Fig.~\ref{fig:ks_all}.
 
-\begin{figure*}
+\begin{figure}
         \centering
@@
 Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method.
-Equivalent plots for the other SFR and gas tracers are in Figures~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the appendix.}
+Equivalent plots for the other SFR and gas tracers are in Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the appendix.}
         \label{fig:es,all,fuv,tot}
-    \end{figure*}
+    \end{figure}
 
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \caption{Fitting result for SFR(FUV + 24~$\mu$m) vs total gas.
-Same as Figure~\ref{fig:es,all,fuv,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours.
-The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
+Same as Fig.~\ref{fig:es,all,fuv,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours.
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}
 \label{fig:es,regs,fuv,tot}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{../image_paper1/color_3d_tir_tot.png}
-\caption{Same as Figure~\ref{fig:es,regs,fuv,tot}, but in this figure we use total infrared emission as a tracer of the SFR.}
+\caption{Same as Fig.~\ref{fig:es,regs,fuv,tot}, but in this figure we use total infrared emission as a tracer of the SFR.}
 \label{fig:es,regs,fir,tot}
-\end{figure*}
+\end{figure}
 
-\begin{table*}
+\begin{table}
 \caption{ K-S law and Extended Schmidt law fitting results}
 \label{table:res}
+\begin{adjustbox}{width=\textwidth}
 \begin{tabular}{ccccccccc}
@@
 \hline
-\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $\la 25\kpc$}} & TIR & H$_2$ only &  N/A$^a$ & N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$ \\
- & TIR               & H\,{\sc I} only    & 0.44 - 0.54 & -9.96 - -9.94  & 0.33 - 0.41    & 0.31 - 0.36    & -10.22 - -10.18     \\
+\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $< 25\kpc$}} & TIR & H$_2$ only &  N/A$^a$ & N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$ \\
+ & TIR               & H\,{\textsc i} only    & 0.44 - 0.54 & -9.96 - -9.94  & 0.33 - 0.41    & 0.31 - 0.36    & -10.22 - -10.18     \\
  & TIR               & Total gas  & 0.44 - 0.54 &  -10.00 - -9.98  & 0.33 - 0.41  & 0.31 - 0.36    & -10.25 -10.21     \\
  & FUV + 24~$\mu$m       & H$_2$ only & N/A$^a$ & N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$    \\
- & FUV + 24~$\mu$m       & H\,{\sc I} only    & 0.65 - 0.72 & -10.18 - -10.16  & 0.59 - 0.67    & 0.17 - 0.22    & -10.33 - -10.29     \\
+ & FUV + 24~$\mu$m       & H I only    & 0.65 - 0.72 & -10.18 - -10.16  & 0.59 - 0.67    & 0.17 - 0.22    & -10.33 - -10.29     \\
  & FUV + 24~$\mu$m       & Total gas  & 0.64 - 0.72 & -10.22 - -10.21  &  0.59 - 0.67   & 0.16 - 0.22    & -10.37 - -10.33     \\
  & H$\alpha$ + 24~$\mu$m & H$_2$ only &  N/A$^a$ & N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$     \\
- & H$\alpha$ + 24~$\mu$m & H\,{\sc I} only    & 0.48 - 0.97 &  -9.97 - -9.88  & 0.61 - 1.12    & -0.36 - -0.12    & -9.82 - -9.59     \\
+ & H$\alpha$ + 24~$\mu$m & H I only    & 0.48 - 0.97 &  -9.97 - -9.88  & 0.61 - 1.12    & -0.36 - -0.12    & -9.82 - -9.59     \\
  & H$\alpha$ + 24~$\mu$m & Total gas  & 0.40 - 0.90 & -10.01 - -9.95  &  0.53 - 1.03    & -0.35 - -0.11    & -9.82 - -9.59     \\
@@
 \end{tabular}
+\end{adjustbox}
 \begin{tablenotes}
  \item $^a$  Since there are very few pixels which we can use for the fitting in this region we cannot provide a meaningful result.
-\item Each entry shows the 95\% confidence range for the fitting parameter.
+\item Each entry shows the 95 per cent confidence range for the fitting parameter.
 \item Fitting parameters of SF laws from applying the Bayesian method.
@@
 \end{tablenotes}
-\end{table*}
 
-\begin{table*}
+\end{table}
+
+\begin{table}
 \caption{K-S law and Extended Schmidt Law fits for larger pixels}
 \label{table:res750}
+\begin{adjustbox}{width=\textwidth}
 \begin{tabular}{cccccccc}
@@
  & H$_2$ only & 0.26 - 0.31 & -10.00 - -9.91  & 0.21 - 0.26  & 0.26 - 0.40    & -10.51 - -10.30  \\
- & H\,{\sc I} only    & 1.08 - 1.24 & -11.60 - -11.36  & 0.73 - 0.85  & 0.58 - 0.64    & -11.74 - -11.60     \\
+ & H\,{\textsc i} only    & 1.08 - 1.24 & -11.60 - -11.36  & 0.73 - 0.85  & 0.58 - 0.64    & -11.74 - -11.60     \\
  & Total gas  & 0.66 - 0.73 & -10.11 - -10.06 & 0.39 - 0.46    & 0.41 - 0.49    & -11.56 - -10.47     \\
@@
  & H$_2$ only & 0.14 - 0.27 & -9.82 - -9.59  & 0.14 - 0.21   & 0.48 - 0.66   & -11.04 - -10.66      \\
- & H\,{\sc I} only    & 1.42 - 1.68 & -12.35 - -11.92 & 0.51 - 0.92    & 0.72 - 0.97    & -12.52 - -11.61     \\
+ & H\,{\textsc i} only    & 1.42 - 1.68 & -12.35 - -11.92 & 0.51 - 0.92    & 0.72 - 0.97    & -12.52 - -11.61     \\
  & Total gas  & 0.07 - 0.31 & -9.63 - -9.45  & 0.22 - 0.32    & 0.63 - 0.78    & -11.17 - -10.84      \\
@@
  & H$_2$ only & 0.27 - 0.32 & -9.98 - -9.86  & 0.17 - 0.24    &  0.38 - 0.73   & -10.89 - -10.44       \\
- & H\,{\sc I} only    & 0.88 - 1.38 & -11.80 - -11.06 & 1.00 - 1.22    & 0.53 - 0.69    & -12.41 - -12.09     \\
+ & H\,{\textsc i} only    & 0.88 - 1.38 & -11.80 - -11.06 & 1.00 - 1.22    & 0.53 - 0.69    & -12.41 - -12.09     \\
  & Total gas  & 0.55 - 0.64 & -10.03 - -9.96 & 0.40 - 0.51    & 0.27 - 0.49    & -10.53 - -10.29     \\
 \hline
-\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $\la 25\kpc$}} 
+\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $< 25\kpc$}} 
  & H$_2$ only & N/A$^a$& N/A$^a$ & N/A$^a$ &N/A$^a$ & N/A$^a$    \\
- & H\,{\sc I} only    & 0.46 - 0.81 & -11.21 - -10.80  & 0.44 - 0.76    & 0.13 - 0.36    & -11.35 -10.94     \\
+ & H\,{\textsc i} only    & 0.46 - 0.81 & -11.21 - -10.80  & 0.44 - 0.76    & 0.13 - 0.36    & -11.35 -10.94     \\
  & Total gas  & 0.47 - 0.82 & -10.25 - -10.18 & 0.44 - 0.78    & 0.12 - 0.36    & -10.49 - -10.30     \\
@@
 \end{tabular}
+\end{adjustbox}
 \begin{tablenotes}
@@
 \end{tablenotes}
-\end{table*}
+\end{table}
 
@@
 Table~\ref{table:res} shows the results of the hierarchical Bayesian fitting for the whole galaxy and all three regions.
-Considering the data and uncertainties for each parameter, we are 95\% confident that our fitting parameter is in the ranges given in Table~\ref{table:res}.
+Considering the data and uncertainties for each parameter, we are 95 per cent confident that our fitting parameter is in the ranges given in Table~\ref{table:res}.
 Our results suggest that changing the gas tracer has a more significant impact on the determination of the power law index than changing the SFR tracers.
@@
 To make a meaningful comparison between our results and the results reported in \citet{Ford13}, we averaged the power-law indices in \citet{Ford13} with a certain annuli and compared to the results with the same annuli in ours.
-We calculated power-law indices to be in the case of the H$_{2}$-only gas $N \sim 0.35, 0.58, 0.68$ and in case of total gas, $N \sim 1.37, 2.05, 1.60$ for $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$, respectively.
+We calculated power-law indices to be in the case of the H$_{2}$-only gas $N \sim 0.35, 0.58, 0.68$ and in case of total gas, $N \sim 1.37, 2.05, 1.60$ for $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$, respectively.
 \citet{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have some differences with results from \citet{Ford13}.
@@
 The whole-galaxy fit of the K-S law shows that using total gas or H$_{2}$-only gas gives a sub-linear relation between \sigmasfr and \sigmatotalgas.
-When using  H\,{\sc I}-only gas we find a nearly super-linear relation.
+When using  H\,{\textsc i}-only gas we find a nearly super-linear relation.
 These results are different from the power-law index estimated by \citet{Ford13}  in the case of total gas, $N=2.03\pm0.04$, but similar to their value of $N=0.6\pm0.01$ in the case of H$_{2}$-only gas.
@@
 Consequently, the depletion time increases.
-On the contrary, the super-linear relation suggests that the depletion time is decreasing with an increasing amount of H\,{\sc I} gas.
+On the contrary, the super-linear relation suggests that the depletion time is decreasing with an increasing amount of H\,{\textsc i} gas.
 The latter conclusion is more similar to the initial suggestion of the K-S law.
@@
 In most cases this effect is almost as strong as the effect of gas surface density on the SFR.
-\citet{Kim13}, using 3D numerical hydrodynamic simulations, showed that in the outer disk regions of a galaxy where the total gas is dominated by H\,{\sc I} gas, the SFR correlates with $\rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk plus dark matter.
+\citet{Kim13}, using 3D numerical hydrodynamic simulations, showed that in the outer disk regions of a galaxy where the total gas is dominated by H\,{\textsc i} gas, the SFR correlates with $\rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk plus dark matter.
 This is because in the outer regions of the disk, the gravity from stars dominates.
 We calculated the power index related to the stellar mass surface density to be 0.36 for these regions (Table~\ref{table:res750}) which is slightly different from their suggestion.
-Since we do not have enough H$_2$ data for regions within $18\kpc < R \la 25\kpc$, our results are limited to ones from the extended Schmidt law for H\,{\sc I} gas only.
+Since we do not have enough H$_2$ data for regions within $18\kpc < R < 25\kpc$, our results are limited to ones from the extended Schmidt law for H\,{\textsc i} gas only.
 Therefore, we could neither confirm nor refuse this prediction.
@@
 They found a new SFR law based on a correlation between SFR and metallicity, and suggested that this correlation strongly depends on the amount of total gas in galaxies.
-They also showed the SFR has a dependence on metallicity which we saw a weak correlation (Figure~\ref{fig:metal}).
+They also showed the SFR has a dependence on metallicity which we saw a weak correlation (Fig.~\ref{fig:metal}).
  We estimated the SFR using \citet{Krumholz09} SFR laws for regions with size of $\sim$750~pc.
-Using the mid value of metallicity, 1.65, and clumping factor of 1.2, We found that the SFR calculated using the Krumholz law is, on average, different by 45\% from the measured SFR(FUV + 24~$\mu$m) in this work.
+Using the mid value of metallicity, 1.65, and clumping factor of 1.2, We found that the SFR calculated using the Krumholz law is, on average, different by 45 per cent from the measured SFR(FUV + 24~$\mu$m) in this work.
 
@@
 They found that increasing both the SFR and the stellar mass increases metallicity, but increasing the gas mass decreases metallicity (equation 9 in \citep{Mannucci10}). 
-However, by considering results from \citet{wong13} regarding the dependence of the rate of H\,{\sc I}-H$_2$ conversion to metallicity, \citet{Roychowdhury15} showed that the K-S law is independent of metallicity in galaxies with H\,{\sc I} as a dominant gas.
+However, by considering results from \citet{wong13} regarding the dependence of the rate of H\,{\textsc i}-H$_2$ conversion to metallicity, \citet{Roychowdhury15} showed that the K-S law is independent of metallicity in galaxies with H\,{\textsc i} as a dominant gas.
 
-In Figure~\ref{fig:metal}, we plot dust to gas mass ratio versus the SFR(FUV + 24~$\mu$m) and the stellar mass, and could not find any correlation over the scale of the whole galaxy.
+In Fig.~\ref{fig:metal}, we plot dust to gas mass ratio versus the SFR(FUV + 24~$\mu$m) and the stellar mass, and could not find any correlation over the scale of the whole galaxy.
 We calculated the Pearson correlation coefficients between metallicity and SFR, and between metallicity and the stellar mass, and found them to be 0.08 and 0.04, respectively. 
-However, in Figure~\ref{fig:metal}, we can see a correlation between metallicity and both SFR and stellar mass for regions within $R< 18\kpc$.
+However, in Fig.~\ref{fig:metal}, we can see a correlation between metallicity and both SFR and stellar mass for regions within $R< 18\kpc$.
 These are weak correlations with Pearson correlation coefficients of $-0.58$ and $-0.46$ for the SFR case and the stellar mass case, respectively.
-We cannot see any correlation in the data from $18\kpc < R \la 25\kpc$.
+We cannot see any correlation in the data from $18\kpc < R < 25\kpc$.
 The average metallicity uncertainty in this region is almost 10 times higher than the average uncertainty for the rest of the galaxy.
-This higher uncertainty obscures any tentative correlation between metallicity and SFR or stellar mass for from $18\kpc < R \la 25\kpc$.
+This higher uncertainty obscures any tentative correlation between metallicity and SFR or stellar mass for from $18\kpc < R < 25\kpc$.
 This analysis confirms that there is a correlation between metallicity and both the SFR/the stellar mass.
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=180mm]{../image_paper1/metal_with_errors.png}
+\includegraphics[width=\textwidth]{../image_paper1/metal_with_errors.png}
     \caption{Left: the SFR(FUV + 24~$\mu$m) surface density versus gas/dust mass ratio surface density and right: Stellar mass versus gas/dust mass ratio surface density  shows the stellar mass.
@@
 Typical uncertainties of the x-axes within 18~kpc are shown in upper right side of the plots.
-The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}
     \label{fig:metal}
-\end{figure*}
+\end{figure}
 

### 2016-07-17 version0.0/paper2.tex
finishing intro0.0
fig.s and table corrections

@@
 \chapter[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
+\label{ch: paper2}
 \defcitealias{Hossein12}{T12}
@@
         \includegraphics[width=\textwidth]{../image_paper2/k96.jpg}
-        \caption{\citet{Kinney96} spectra template for 12 types of galaxies from \citet{Hossein12} paper (Fig.
+        \caption[\citet{Kinney96} spectra template for 12 types of galaxies]{\citet{Kinney96} spectra template for 12 types of galaxies from \citet{Hossein12} paper (Fig.
 1 in \citet{Hossein12}).
@@
     Assuming decreasing SFR and visual attenuation ($\tau$) model, Salpeter initial mass function~\citep{Salpeter55}, and old stellar population with age of $\sim 10$~Gyr, they derived physical properties of the galaxies such as age and stellar mass.
-    Some of these properties are shown in Tab.~\ref{tab: props}.
-    In Sec.~\ref{sec: 1D}, we study these properties for each category.
+    Some of these properties are shown in Table~\ref{tab: props}.
+    In Section~\ref{sec: 1D}, we study these properties for each category.
     More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.
@@
 \begin{table}
-\caption{Description of the properties of \citet{Hossein12} galaxies; the output result of {\em CIGALE}}     
+\caption[Description of the properties of \citet{Hossein12} galaxies]{Description of the properties of \citet{Hossein12} galaxies; the output result of {\em CIGALE}}     
 \label{tab: props}
@@
      In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     %%Sr160611: Last time I got the following note from the MNRAS editor:
-     %"Please note that computer software/programming lan- guages must be styled in SMALL CAPITAL LETTERS, according to journal style. Please check and correct this paper accordingly."
-     % PB20160603: right, but I think the right way to do this is {\sc newsom}, not {\tiny NEWSOM} -- the distinction being that {\sc..
-} will scale up or down with the global font size but {\tiny} will not.
+
      SOM in {\sc nnt} can be created by {\sc newsom} or {\sc selforgmap} library, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
@@
      The gradual change in the leaning factor helps to fine-tune the topology results, leading to a more stable SOM. 
-     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase. %cite kohenen book?!
+     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase.
      We chose the number of epochs in the tuning phase to be 3 times the number of epochs in the ordering phase.
@@
      To present our results, we use {\sc nnt}'s built-in plotting tool.
-%     This tool is designed to show the distance between each cluster more clearly.
      Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
@@
             \end{subfigure}
-            \caption{SOM of the mock sample.
+            \caption[Self-organizing map of the mock sample]{SOM of the mock sample.
 In both plots, the axes show the position of the neurons.
@@
  To illustrate how self-organizing maps work, we create a mock sample of 27 galaxies.
-% We create a mock sample of 27 galaxies to show how this method works, illustrate the results of SOMs, and how they can be analysed.(<- I don't like this sentence)
  The mock sample contains two attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). 
- We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Sec.~\ref{sec: create_som}.
+ We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Section~\ref{sec: create_som}.
 
@@
 8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
-%Since the input data are chosen to not to be complex, each entry only could get either 0 or 1 as a type of galaxy and 0 or 0.5 as an indicator of  high or low SFR, only four of the neurons were filled.
 We can conclude that although each galaxy had  the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributes, they remained only in four groups.
@@
     The trained networks can then be used to categorize other galaxies.
-    %In following we show how we trained data and used galaxies from \citetalias{Hossein12} to show how the clustering using trained networks works.
 
@@
     We started our analysis by creating 1D SOMs. 
-    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Sec.~\ref{sec: 1D}).
-    We generate 2D networks (Sec.~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
+    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D}).
+    We generate 2D networks (Section~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
     For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
@@
             Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
-            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances, $D_j$.
-            As mentioned in Sec.~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
+            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
+            As mentioned in Section~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
             The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
             \begin{figure}
-                \begin{subfigure}[b]{0.5\textwidth}
+                \begin{subfigure}[b]{\textwidth}
                     \centering
@@
                 \hfill
-                \begin{subfigure}[b]{0.5\textwidth}
+                \begin{subfigure}[b]{\textwidth}
                      \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                 \end{subfigure}
-                \caption{Results of training network in $1\times2$~grid.
+                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid.
 As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map.
@@
             In these plots we force the galaxies to be categorize in a maximum 3 groups. 
-            %If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty(this sentence does not make much sense.
-I kind of think I know what you're trying to say (because once I translate this sentence to farsi word by word, it kind of comes together) but please phrase it more carefully.).
-            %[suggested sentence: 
             If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
@@
             \begin{figure}
-                \begin{subfigure}[b]{0.5\textwidth}
+                \begin{subfigure}[b]{\textwidth}
                     \centering
@@
                 \hfill
-                \begin{subfigure}[b]{0.5\textwidth}
+                \begin{subfigure}[b]{\textwidth}
                      \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_3.png}
                 \end{subfigure}
-                \caption{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid.
+                \caption[Results of training network in $1\times3$~grid]{The same as Fig.~\ref{fig: 1by2T} but showing the results of training network in $1\times3$~grid.
 In this network again, 5 of the \citet{Kinney96} templates are categorized as quiescent and 7 as starbursts.
@@
             The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
-        \begin{figure*}
+        \begin{figure}
             \begin{subfigure}[b]{\textwidth}
@@
             \end{subfigure}
-            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
+            \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
             \label{fig: 1by22T}
-        \end{figure*}
+        \end{figure}
 
@@
          \label{sec: 1Dv}
-            After training the networks as discussed in Sec.~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
+            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the fitted SEDs of the sample of 142 galaxies from \citetalias{Hossein12}.
             The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
             Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
-            %The lower panels show the average SED of the galaxies in each node. 
             The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
@@
                 \hfill
-                \begin{subfigure}[b]{0.5\textwidth}
+                \begin{subfigure}[b]{\textwidth}
                      \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2.png}
@@
                 \end{subfigure}
-                \caption{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~networks trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
+                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~networks]{Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}).
 Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
@@
             \begin{figure}
-                \begin{subfigure}[b]{0.5\textwidth}
+                \begin{subfigure}[b]{\textwidth}
                     \centering
                     \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_3.png}
-                    %\caption{$1\times2$ weight map}
-                     %\label{fig: 1by3T}
                 \end{subfigure}
                 \hfill
-                \begin{subfigure}[b]{0.5\textwidth}
+                \begin{subfigure}[b]{\textwidth}
                      \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by3.png}
-                     %\caption{$1\times2$ hits map}
-                     %\label{fig: 1by3Thits}
                 \end{subfigure}
-                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
+                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times3$~networks]{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times3$ (Fig.~\ref{fig: 1by3T}) to classify the sample galaxies.}
                 \label{fig: 1by3V}
@@
             In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
-            As mentioned in Sec.~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
+            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
            As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
-            \begin{figure*}
-                \begin{subfigure}[b]{0.9\textwidth}
+
+            \begin{figure}
+                \begin{subfigure}[b]{\textwidth}
+                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_22_n.png}
                     \centering
-                    \includegraphics[width=\textwidth]{../image_paper2/1d/hit_v_1_by_22_n.png}
-                    %\caption{$1\times2$ weight map}
-                     %\label{fig: 1by3T}
                 \end{subfigure}
                 \hfill
-                \begin{subfigure}[b]{0.9\textwidth}
+                \begin{subfigure}[b]{\textwidth}
+                \centering
                      \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by22.png}
-                     %\caption{$1\times2$ hits map}
-                     %\label{fig: 1by3Thits}
                 \end{subfigure}
-                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
+                \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times22$~networks]{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
 In the average SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones.
@@
                 \label{fig: 1by22V}
-            \end{figure*}
+            \end{figure}
+
             The lower panels present the average SED of the galaxies in each neuron.
@@
 
-            %PB20160604: is this paragraph really necessary?
-            %%Sr: I think it clears the point of having regions in middle neurons
             With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of SEDs is limited to models and the results are always reported with uncertainties.
@@
 
-        In order to check whether our conclusions in Sec.~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.
+        In order to check whether our conclusions in Section~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.
 
@@
             \includegraphics[width=\textwidth]{../image_paper2/1d/props5.png}
-            \caption{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
+            \caption[The median of four properties of galaxies in three networks]{Comparing the median of four properties of galaxies in each node in $1\times2$ (black circles), $1\times4$ (blue diamonds), and $1\times8$ (red triangles) networks.}
             \label{fig: props}
@@
         \begin{figure}
-        \begin{subfigure}[b]{0.5\textwidth}
+        \begin{subfigure}[b]{0.3\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/f1.png}
@@
         \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
+        \begin{subfigure}[b]{0.3\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/f2.png}
@@
         \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
+        \begin{subfigure}[b]{0.3\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/f3.png}
@@
         \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
+        \begin{subfigure}[b]{0.3\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/f4.png}
@@
         \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
+        \begin{subfigure}[b]{0.3\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/f5.png}
@@
        \hfill
-        \begin{subfigure}[b]{0.5\textwidth}
+        \begin{subfigure}[b]{0.3\textwidth}
             \includegraphics[width=\textwidth]{../image_paper2/1d/f6.png}
         \end{subfigure}
-        \caption{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
+        \caption[Relations between properties of the clustered galaxies]{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass.
 Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values.
@@
     In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each SED type.
-    As described in Sec.~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
+    As described in Section~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
     This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
@@
     To get the best result from both methods, we should have SOMs with ``enough"  neurons to give any new types of galaxies a chance to find their places in the map.
-    ``Enough  neurons" is a vague statement, but as mentioned in the Sec.~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
+    ``Enough  neurons" is a vague statement, but as mentioned in the Section~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
     Since the training dataset (the \citetalias{Kinney96} templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
@@
         \end{subfigure}
-        \caption{$12\times12$~2D SOM results.
+        \caption[$12\times12$ two-dimensional self-organizing map results.]{$12\times12$~2D SOM results.
 Upper pabel: SOMs trained using the \citet{Kinney96} templates.

### 2016-07-17 version0.0/paper3.tex
fig.s and table corrections

@@
 As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
-%Advances in technology allow us to collect data from the sky. %PB - commented out
 Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.
@@
 Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
-M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer and \Herschel space telescope.
+M31 has been observed by many telescopes including the {\textit {Hubble}}, \Spitzer and \Herschel space telescopes. %Els: Use the correct names for telescopes?
 \cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
@@
 Are PAH features in M31 similar or they can be divided into various groups? If so, what are the properties of each group?
-Does the intensity of PAH emission depend on the underlying structure of their position? %PB: I don't understand what you mean by "underlying structure of their position"
-How do they compare to properties of galaxies? %PB: what is "they"
+Does the intensity of PAH emission depend on location or global galaxy properties? 
 The properties of M31 that derived in various studies and observational data of this galaxy can be used for a knowledge discovery and data mining study.
-%The amount of data for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
 The Pinwheel Galaxy (M101), with distance of 6.7~Mpc~\citep{Freedman01}, is another nearby galaxy that has been well-observed and studied~\citep[e.g.
@@
 M101 is a large spiral galaxy with several \hii~regions and a large metallicity gradient from centre to outskirts~\citep{Kennicutt03}.
-In case of dimensionality data from M101 is a suitable addition to M31 data for a data mining study. %PB: don't understand "In case of dimensionality"
+Since the observational data from M31 and M101 are similar, M101 is a suitable addition to M31 data for a data mining study. 
 Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies~\citep[e.g.][and references therein]{Ball10}.
@@
 
-The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
-There are very few studies on relations between properties of M31 with its PAH features. %generate?!
+The purpose of the present work is to use M31 observations to provide new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy,
+as there are few studies on relations between properties of M31 with its PAH features. %generate?!
 \cite{Cesarsky98} studied PAH spectra observed by ISOCAM spectro-imaging in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6$~$\mu$m emission with enhanced 11.2~$\mu$m emission.
@@
 %(PB), but the results were inconclusive.
-%%%%% !!!!!%%%%
+$$Sr:?
 Using IRAC imaging observations,~\cite{Barmby06} found good agreement between the M31 SFR derived using observed 8~$\mu$m luminosity with other 
@@
 Using networks with fewer neurons, we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
-We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input on the position of the clusters in the SOM.
-We apply the 2D trained networks to the M101 data to check whether it has similar properties.
+We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect on each input on the position of the clusters in the SOM.
+We apply the 2D trained networks to the M101 data to study whether they have similar properties to M31 ones.
 If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
 
-We describe the SOM method in Section $\S$~\ref{sec: method}. %PB: I think you use either "Section" or $\S$, not both.
-In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
-The results of the 1D SOM networks and the study of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
-In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
-In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
-
+We describe the SOM method in $\S$~\ref{sec: method}. 
+In $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
+The results of the 1D SOM networks and the study of PAHs in M31 are presented in $\S$~\ref{Sec: 1d_cluster}.
+In $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
+In $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
 %----------------------------------------------------------------------------------------
@@
 
-\section{METHOD}
+\section{Method}
 \label{sec: method}
@@
 classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b}.
-%%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g.
-Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not
 
-The K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
+The K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}.
 For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into the desired number of clusters.
@@
  The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
- Each neuron has a fixed position in the map and may contain one or more samples from the input data,~\boldit{V} $\in \Re^n$.
-% Els said the simbols should be describe?!
-I think it is pretty obvious!
-%PB: most are pretty obvious, but mention what $n$ is here
+ Each neuron has a fixed position in the map and may contain one or more samples from the input data in a n-dimensional space,~\boldit{V} $\in \Re^n$.
  A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
@@
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
- The weight vectors in the neighbourhood of the BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+ In each iteration (t),The weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
   \begin{equation}
@@
  \end{equation}
-where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
-%PB: mention what L_0, \tau, r are
-Values for the number of neurons, $L(t)$ and $R(t)$ are arbitrary. 
+where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor with $L_0$ is the initial value of learning, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
+$\tau$ is the number of total iterations.
+Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
 ~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
@@
      We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
-     %Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
-     %Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
-     %All the other parameters are default values in \textsc{ newsom} library and cannot be changed by the users.
 
@@
                 \centering
-                \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/mock_sample.png}
-            \caption{SOM of the mock sample.
+                \includegraphics[width=\textwidth]{../image_paper3/images0.01/mock_sample.png}
+            \caption[Self-organizing map of the mock sample]{SOM of the mock sample.
 The axes show the position of the neurons.
@@
 either 0 or 1 for low or high SFR, and 0 or 0.5 for a low or high amount of dust. 
- We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Sec.~\ref{sec: som}.
- Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
- The axes show the position of the neurons in a $10 \times 10$ network and the hexagonal shapes are the neurons.
+ We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Section~\ref{sec: som}.
+ Fig.~\ref{fig: sample} shows the SOM of the mock sample. 
+ The axes show the position of the neurons in a $10 \times 10$ network and the hexagonal shapes (depicted by purple hexagons) are the neurons.
 
@@
 Their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
-%The plot in the Fig.~\ref{fig: sample} clearly shows these divisions.%PB: commented out.
 In Fig.~\ref{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
@@
 
-\section{Study sample} %%or sample study?! %PB: study sample is OK
+\section{Study Sample}
 \label{Sec: data_SOMN}
@@
 These specific regions were chosen for the availability of \Spitzer/IRS 5--15$\mu$m  spectroscopy covering the PAH emission bands.
-Besides PAH band strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
+Besides PAH band strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$), dust mass, metallicity, and gas mass.
 Table~\ref{tab: data} shows the full list of data for both M31 and M101.
 All data were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
-Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
+Since the spatial resolution of the observations varies from as small as $<1$\arcsec to as high as 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g.
 the spectroscopic data).
 In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
-Therefore, we did not perform any resolution matching and used data at their original resolution. %PB: Need to discuss these last few sentences; not sure I understand what you're saying.
+Therefore, we did not perform any resolution matching and used data at their original resolution.
 
@@
 \begin{figure}
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{\textwidth}
         \centering
-    %\centering
         \includegraphics[width=0.97\textwidth]{../image_paper3/images0.01/M31/M31.png}
@@
     \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}
@@
     \end{subfigure}
-    \caption{Position of the data in M31 (up) and M101 (down).}
+    \caption{Position of the data in M31 (a) and M101 (b).}
 \end{figure}
-
-%   \begin{figure}
-%     \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
-%       \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/M31.png}
-%     }
-%     \hfill
-%     \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
-%       \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M101/M101.png}}
-%     \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
-%     \label{fig:dummy}
-%   \end{figure}
 
@@
 
-    %To guarantee that we do not use the observed data as an input for SOM in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
     We removed all the observed data that were used to calculate galaxy properties from the input sample, to guarantee that they have not been used in multiple forms.
-   % We used this new sample of observational and derived data as the main input for creating SOMs.
-    To have prior knowledge of the M31 data set, %or to have an insight into the data set!
+    To have prior knowledge of the M31 data set, 
     we computed the Pearson correlation coefficients between input measurements.
     Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients with a confidence level of 95 per cent. 
+    If the significant level of correlation becomes smaller than 0.05 (5 per cent), the correlation is marked as insignificant. 
     All the PAHs correlate with one another very well.
@@
 
-      \begin{figure*}
+      \begin{figure}
         \centering
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
-            \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
+        \caption[Pearson correlation coefficients for data from 10 regions in M31]{Pearson correlation coefficients with a confidence level of 95 per cent for all data from M31.
 The colours and circle sizes show the Pearson correlation coefficients where large blue circles are 1, which means highly correlated, and large red circles are $-1$, which means highly anti-correlated quantities.
@@
         \label{fig: cor_all}
-        \end{figure*}
+    \end{figure}
 
@@
 %----------------------------------------------------------------------------------------
-\section{One dimensional self-organizing maps}
+\section{One-Dimensional Self-Organizing Maps}
     \label{Sec: 1d_cluster}
@@
     The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
-    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity).
+    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible (infinity). %Els asked what is maximum possible #
     In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
@@
 
-    \subsection{Clustering M31 data}%I am not sure about it
+    \subsection{Clustering M31 Data}%I am not sure about it
 
@@
         The $1\times14$ network (Fig.~\ref{fig: M31_net_1by14}) is the first network in which all the regions in M31 are completely separated.
-        Since in the higher network sizes, regions have more space to be separated based on their differences, in going from the $1\times2$ to the $1\times14$ network the distance between M31 regions increases, until they are completely separated.
+        In the higher network sizes, regions have more space to be separated based on their differences.
+In going from the $1\times2$ to the $1\times14$ network the distance between M31 regions increases, until they are completely separated.
 
@@
         By increasing the size of the neurons to three, in Fig.~\ref{fig: M31_net_1by3}, we can see that region 2 separates itself from the other regions and occupies the middle neuron.
-        The white colour between two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between the two right neurons indicates otherwise.
+        The white colour between the two left neurons suggests that the regions which occupy these neurons are very similar to each other, while the black colour between the two right neurons indicates otherwise.
 
         %%%Talking about four right regions
-        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
+        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to the other regions (fig. 5 in \citealt{Dim15}). 
         %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
         These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
-        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
+        The higher values for these quantities could be the reason that these four regions become separated from the others in the $1\times2$ network.
         Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).
-        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
-        Similarities with regions 3 to 8 in the other input values (e.g. SFR) causes regions 1, 2, and 9 to gradually move towards other the regions and away from region 10 in the higher grid SOMs.
-       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.
-
-        %%% Repeated from the other paragraphs
-        %%%Talking about 6 left regions
-        %In both Figs.~\ref{fig: M31_net_1by2} and~\ref{fig: M31_net_1by3} the most left neuron is occupied with regions 3 to 8. 
-        %These regions all are located outside the inner or 10~kpc rings (See fig.~\ref{fig: regions in m31}).
-        %Since the locations of these regions have similar physical properties, they occupy a same neurons in a smaller SOMs.
-        %As it can be seen in the $1\times3$ SOM (Fig.~\ref{fig: M31_net_1by3}), the region 2 is moved to the middle neurons.
-       % The fact that this region is slightly out of the 10~kpc ring makes region 2 to be the first region to move towards the neurons that occupied with regions 3 to 8. 
-       % In the $1\times14$ SOM (Fig.~\ref{fig: M31_net_1by14}), although all the regions were separated, but the colour between regions 10 to the other regions become completely dark.
-       % This dark colour indicates that region 10 is absolutely different, which considering the fact that it is the only regions in the bulge of the galaxy, we expected to see such a distance between this regions and the others.
+        The differences in their positions account for their difference in input parameters.
+        Since region 10 is located in the bulge of M31 and has high surface brightness for most of the input values, regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
+       % Similarities with regions 3 to 8 in the other input values (e.g. SFR) causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
 
     \begin{figure}
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \centering
@@
     \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by3_all.png}
@@
     \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by14_all.png}
@@
     \end{subfigure}
-   \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
+   \caption[One-dimensional self-organizing map of M31 data]{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
 The axes show the position of the neurons.
 The purple hexagonal shapes represent the neurons.
-The grey scale colours show the differences between the weights of the neurons, with white as the minimum difference and black as the maximum.
+The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum.
 The numbers in the plot show the M31 regions located in each neuron.}
@@
 
-% \end{figure}
-%         \begin{figure}
-%             \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
-%              \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by2_all.png}
-%              }
-%             \hfill
-%             \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
-%             \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by3_all.png}
-%              }
-%              \hfill
-%             \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
-%              \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/1D/combine_1D_1by14_all.png}
-%              }
-%              %%% What should I do with this one! It doesn't look good visually
-%             \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids.
-The axes show the position of the neurons.
-The purple hexagonal shapes represent the neurons.
-The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum.
-The numbers in the plot show the M31 regions located in each neuron.}
-%             \label{fig: M31_nets_1d}
-%         \end{figure}
-
         %%Network 1by14
@@
         In a larger-grid SOM, the network pays more attention to smaller details and differences in the input data.
-        Since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
-        Regions that are located in similar areas in M31, like regions 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities to each other.
-%%present?
-show?
-represent?
-have?
+        Therefore, since at least 14 neurons are needed to separate all 10 regions in M31, we can conclude that some of the regions have very small differences.
+        Regions that are located in similar areas (e.g.
+spiral arms, bulge, and 10 kpc ring) in M31, like regions 7 and 4 (see Fig.~\ref{fig: regions in m31}), are most likely to have more similarities with each other.
         In Fig.~\ref{fig: M31_net_1by14}, the right-most neuron is occupied by region 10.
-        Two black colours between this region and the others indicate the large differences between this neuron and the others.
-       Region 10 is located in the bulge of M31, and is separated from other regions, which are mostly located around the inner or outer rings.
-       The SOM shows that this region has completely different input values than the others.
-       Most of the input values for region 10 are much higher than the other regions, which is the main reason for its isolation.
+        Two black colours between this region and the others indicate the large differences between this neuron and the other ones.
+        Region 10 is located in the bulge of M31, and is physically separated from the other regions, which are mostly located around the inner or outer rings.
+        The SOM shows that this region has completely different input values from the others: most of the values for region 10 are much higher than for the other regions, which is the main reason for its isolation.
         Region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.
@@
         Using self-organizing maps, we can identify hidden subgroups in our samples. 
-        Each of these subgroups were separated from each other for a reason.
-        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
+        Each of these subgroups separates for a reason.
+        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
         To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).
@@
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
-        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
+        \caption[Pearson correlation coefficients for data from clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.
+}
           \label{fig: cor_cluster1}
@@
 
-        %%% what regions' version shows and how it compares with the other one:
-        In Fig.~\ref{fig: cor_all}, which shows the Pearson correlation coefficients from data in all 10 regions, all the PAH features are highly correlated with each other. 
-        Also, there are very strong correlations between all the PAH features and PACS~100~$\mu$m, SPIRE 250 to 500~$\mu$m~emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, and metallicity.
-        However, in Fig.~\ref{fig: cor_cluster1}, the 12.0 and 12.7~$\mu$m~PAH fluxes do not show any significant or strong correlation with PAH fluxes at other wavelengths, or with most of the other quantities.
-        The only exceptions are the strong correlations between PAH flux at 12~$\mu$m and L$_{\mathrm dust}$, and between the 12 and 12.7~$\mu$m PAH fluxes.
-        Since there are only 6 regions in this cluster, even one outlier in the data may cause the correlation coefficient to become insignificant.
-        If we ignore the outlier values, the correlations between 12.0 and 12.7~$\mu$m~PAH fluxes and the other quantities reappear. 
-        For example, region 8 breaks correlations between 12.0~$\mu$m and 6.2, 7.7, and 8.3~$\mu$m.
-        This region could be part of scatter for these correlations, but with 6 regions in the dataset it is hard to have a firm conclusion.
+        Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
+        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
+        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, or metallicity.
+        The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.
 
-        For the PAH fluxes except 12.0 and 12.7~$\mu$m in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, or metallicity.
-        These PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.
-        Correlations between PAH features and SFR, and L$_{\mathrm TIR}$ are well-studied~\citep[e.g.][]{Tielens08,Peeters04}. 
+        \cite{Calzetti10} mentioned that with increasing RHI in regions, metallicity and PAH equivalent widths decrease. 
+        \cite{Dim15} investigated the correlation between PAHs features and both metallicity and RHI using the equivalent width of the 8~$\mu$m (combination of 7.7, 8.3, and 8.6~$\mu$m components) and the 7.7 and 11.2~$\mu$m features.
+        They did not see any relations between PAHs and metallicity or RHI for 10 regions in M31.
+        In Fig.~\ref{fig: cor_all}, we show that all the PAH fluxes correlate with metallicity, and PAH fluxes in the 7.7, 8.3 and 17.0~$\mu$m bands weakly anti-correlate with RHI.
+        However, in Fig.~\ref{fig: cor_cluster1}, there is no correlation between the PAH fluxes and metallicity, but all of them strongly anti-correlate with RHI.
+        \cite{Dim15} argued that the absence of (anti)-correlation between the PAH features and metallicity and RHI was related to a lack of data in low-metallicity regions.
+        Although data from more regions would improve the results, our analysis shows that clustering data would show the missing (anti)-correlations.
+        For example, for both clusters in Fig.~\ref{fig: M31_net_1by2},
+        we can see anti-correlations between PAHs and RHI, but each of them has a different slope which removes the anti-correlation over all 10 regions.
+
+        Correlations between PAH features and SFR, and L$_{\mathrm TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
         Many groups have used PAH features as a tracer of SFR by finding correlations between 
-        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Shipley16,Khramtsova13,Calzetti07}.
+        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
         These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
-        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: Region 6. 
-        When we disregard this region, high correlations between 6.2 to 11.3~$\mu$m~PAHs and SFR (and L$_{\mathrm TIR}$) reappear.
+        Note that, since there are only 6 regions in the clustered data, even one outlier in the data may cause the correlation coefficient to become insignificant.
+        Further analyses show that the absence of correlations between PAH fluxes and SFR is because of one outlier: region 6.
+Region 6 is located in a FUV-bright region, which breaks the correlations.
+        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_{\mathrm TIR}$) reappear.
 
-        Strong anti-correlations between 6.2 to 11.3~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all}.
+        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
         Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
         First, the optical data are not corrected for dust extinction.
-        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with amount of dust due to extinction \citep{Calzetti94}.
-        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same for \sii~and \oiii~emission.
-        Second, is the possible effect of observing apertures.
-        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. %%% reference? PB: I will try to find one.
-        The anti-correlations between 6.2 to 11.3~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Dim15, Gordon08, Wu06}.
+        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
+        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
+        Second is the possible effect of the structure of the observed regions.
+        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. 
+        The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
         \cite{Wu06} suggested these anti-correlations could be the result of PAH destruction due to a high amount of harder radiation (thus higher RHI).
-        On the other hand, \cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
+        On the other hand,~\cite{Gordon08} argued that the harder radiation could make the photodissociation regions (PDRs) smaller.
         The PAH features are mostly coming from the PDRs that are surrounded by \hii~regions, and the PAH features' underlying continuum emission is from the \hii~regions.
-        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.
-        The later reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.
+        Therefore, the lower flux of the PAH features could be the result of the smaller size of PDRs.%Els: If you have an harder radiation field, you destroy your smaller PAHs.
+Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible.
+        The latter reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.
 
-        The strong anti-correlation between PAHs and stellar mass suggests that, despite the general assumption that one of the main source of heating PAHs is stellar emission~\citep[e.g.][]{Jones15,Lu14,Calapa14,Bendo08,Haas02}, a higher stellar mass decreases PAH emission.
-        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, and concluded that the PAH emission traces the old stellar population.
+        The strong anti-correlation between PAHs and stellar mass suggests that, a higher stellar mass decreases PAH emission. 
+        In observations of M33,~\cite{Calapa14} showed that the 8/250~$\mu$m luminosity ratio correlates with 3.6~$\mu$m emission, which translates to stellar mass, %Els: I'm unfamiliar with the details of this translation.
+But if you look at individual HII regions or starforming complexes, I would think that the 3.6um flux is not dominated by the stellar light as the stars are too hot to have a large fraction of emission at these wavelengths?
+        and conclude that the PAH emission traces the old stellar population.
         In Fig.~\ref{fig: cor_cluster1}, we see a weak anti-correlation between SPIRE 250~$\mu$m emission and the stellar mass.
-        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in clustered data or in all 10 regions.
-      %  The results from~\cite{Calapa14} were based on data from the whole galaxy and has a relatively high scatter.
-      %It is possible that all the 10 regions in M31 simply aligned with the scatter of the correlation.
-Further analysis on M31 data is required to see weather the anti-correlation in this regions is extended to whole galaxy or it is only for these 6 regions.
-
-        Some studies have indicated that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}.
-        To test whether anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
+        We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in the clustered data or in all 10 regions.
+       % Some studies have indicated that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}. %%% These are all UV emission
+        To test that whether the anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
         The ratio of 8/24~$\mu$m emission, which can be considered as a proxy for PAH abundances~\citep[e.g.][]{Sandstrom10,Khramtsova13}, does not anti-correlate with stellar mass for either the clustered data or all 10 regions.
@@
 
-        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
-        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
-        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an \hii~region, which could be the reason of low PAHs for these regions.
+        The anti-correlation between stellar mass and PAHs could be result of the position of the regions within M31.
+        Regions 5, 6, and 8 are located in the stellar disk of the galaxy and have relatively high stellar mass and faint PAH emission. 
+        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in thesample that do not include an \hii~region, which could be the reason for the faint PAH emission for these regions.
         Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
         Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
-        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!
-
-       % On the other hand, if we divide SFR by stellar mass, which give us specific star formation rate (sSFR), we see strong correlation between sSFR and 6.2 to 11.3~$\mu$m fluxes for clustered regions,
 
@@
        The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.
-        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties.
+       However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from all 10 regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties.
 
@@
 %----------------------------------------------------------------------------------------
- \section{Two dimensional self-organizing maps}
+ \section{Two dimensional self-Organizing Maps}
  \label{sec: 2d_cluster}
@@
     Accordingly, we created $10\times10$ 2D networks to study the data in detail.
-    As mentioned in previous sections, the size of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
+    As mentioned in previous sections, the sizes of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
 
@@
     In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
-    Regions 5 and 6 are in the second neighbourhood on the SOM, with a medium gray colour between them.
+    Regions 5 and 6 are in the second neighbourhood (there are two neurons between them) of the SOM, with a medium gray colour between them.
     These two regions are physically located around the inner ring of the galaxy.
@@
 
-    Regions 1 and 9 are close to each other, and in the same side of the star forming ring. 
-    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in SOM.
-    Region 2 is more distant from other regions in the galaxy and placed in the star forming ring.
+    Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
+    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in the SOM.
+    Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
     However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
@@
 
-    In order to analyse effects of any input data on the final SOM, in the following we create SOMs from various subsets of data.
+    In order to analyse effects of any input data on the final SOM, in the following we created SOMs from various subsets of data.
     We compare results of the subsets with one another and with the SOM created from all data in Fig.~\ref{fig: all_derived_ones}.
@@
     \label{sec: subsets}
-            For analysing subsets, we created SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
+
+            For analysing subsets, we create SOMs by using only PAH data, as well as using all data except the PAHs (Fig.~\ref{fig: PAHS_or_not_PAHs}).
              \import{../image_paper3/text_files/image_texts/}{PAHS_or_not_PAHs.tex}
@@
 
-            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data) gradually, by adding other quantities to the input data. 
+            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH-only data) gradually, by adding other quantities to the input data. 
             The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
@@
 
-            The SOM algorithm assigns a random weight to each network that causes the overall position of regions in networks (even with the same input data) to change in each run of the algorithm.
+            At the beginning of each run, the SOM algorithm assigns a random weight to neurons that causes the overall position of regions in networks (even with the same input data) changes in each run of the algorithm.
             However, the position of each region relative to other regions changes dramatically only when the new sets of input data are given to the algorithm (assuming all the initial values for the run are unchanged).
-            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: col3and11_dist},~\ref{fig: col3and14_dist},~\ref{fig: col3and17_dist},~\ref{fig: col3and21_dist}, and ~\ref{fig: col3and22_dist}, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
+            In all SOMs in Fig.~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs.~\ref{fig: col3and11_dist},~\ref{fig: col3and14_dist},~\ref{fig: col3and17_dist},~\ref{fig: col3and21_dist}, and ~\ref{fig: col3and22_dist}, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
             In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data.
 
-            Comparing Figs.~\ref{fig: col3and11_dist} to ~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
+            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
             Increasing the dimension of the input data makes region 10 more isolated.
@@
             Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
-            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.
+            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revokes those changes.
 
-            We generated other subsets of the data based on the results in Figs~\ref{fig: inc_D_col3s} to further study the effects of the input data on SOMs.
-            Subset 1, listed in Tab.~\ref{tab: subset1}, includes all the input data except stellar mass.
-            Tab.~\ref{tab: subset5} lists data used in subset 2, which includes all data except that the PAH fluxes are combined into a total PAH flux. 
-            For subset 3 ( in Tab.~\ref{tab: subset6}), SPIRE 250 and 500~$\mu$m were removed from subset 2.
+            We generated other subsets of the data based on the results in Fig~\ref{fig: inc_D_col3s} to further study the effects of the input data on SOMs.
+            Subset 1, listed in Table~\ref{tab: subset1}, includes all the input data except stellar mass.
+            Table~\ref{tab: subset5} lists data used in subset 2, which includes all data except that the PAH fluxes are combined into a total PAH flux. 
+            For subset 3 (in Table~\ref{tab: subset6}), SPIRE 250 and 500~$\mu$m were removed from subset 2.
             Figs.~\ref{fig: subset1} --~\ref{fig: subset6} show SOMs created by data from subsets 1 to 3, respectively.
-            The remaining subsets are discussed in Appendix.~\ref{sec: app_2d_soms_SOMN}.
+            The remaining subsets are discussed in Appendix~\ref{sec: app_2d_soms_SOMN}.
 
-            The results from Table~\ref{tab: subset1} are shown in Fig.~\ref{fig: subset1}. 
+            The results from Table~\ref{tab: subset1} are used to create the network in Fig.~\ref{fig: subset1}. 
             In this SOM, compared with the SOM from all the data in Fig.~\ref{fig: all_derived_ones}, regions 1 and 9 are closer to region 10. 
             Regions 1 and 9 are the ones with lowest stellar mass values, and region 10 has the highest stellar mass value among those 10 regions. 
-            Since the differences in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from the input data reduced the distance between these regions.
+            Since the difference in the amount of stellar mass was one of the most distinct differences between these three regions, removing stellar mass from the input data reduced the distance between these regions.
             Regions 5, 6 and 8 have the same relative distance from each other as in Fig.~\ref{fig: all_derived_ones}, but they are all closer to the position of region 10.
@@
 
-            Changing from separate values for each PAH feature to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compared to the one in Fig.~\ref{fig: all_derived_ones}.
+            Changing from separate values for each PAH features to a single value for the total PAHs caused small changes to the SOM map in Fig.~\ref{fig: subset5} compared to the one in Fig.~\ref{fig: all_derived_ones}.
             The distance between the positions of regions 6 and 8 increased significantly, while the position of region 2 moved closer to the positions of regions 4 and 7.
@@
 
-            Fig.~\ref{fig: subset6} shows the SOM generated from data listed in Tab.~\ref{tab: subset6}, which includes all the data from Tab.~\ref{tab: subset5} except for  the SPIRE 250 and 500~$\mu$m emission.
-            Although for most of the regions we see the changes in their positions, the colours between neurons changes as well. 
-            %Therefore, we can conclude that these changes caused by the differences in the initial assigned weights.
+            Fig.~\ref{fig: subset6} shows the SOM generated from data listed in Table~\ref{tab: subset6}, which includes all the data from Table~\ref{tab: subset5} except for  the SPIRE 250 and 500~$\mu$m emission.
+            Although for most of the regions we see the changes in their positions, the colours between neurons change as well. 
             The distance between the positions of the regions 4 and 2 is increased as are the
@@
 
-            %Subsets, that some of them  are studied in this section, can be used to learn about the effect of each input on the map as well as they can be used to predict unobserved quantities in the galaxy.
-
-            % \subsubsection{Prediction observing data using M31}
-
-            %     On SOMs we can see relations between the input data from each region regarding to the other regions.
-            %     These relations are shown by colour in SOMs, when white is 100 per cent similarity and black is 0 per cent similarity.
-            %     Therefore, we have the probability distribution of quantities of each values given data from other regions.
-            %     We can use these probability distribution to estimate missing data for regions.
-
-            %     To demonstrate this conclusion, we assumed the stellar mass value for region 1 is unknown.
-            %     Therefore, we need a SOM that are generated from all the inputs data for all regions except stellar mass (e.g subset 1 in Fig.~\ref{fig: subset1}).
-            %     \import{../image_paper3/text_files/image_texts/}{sim_subset1.tex}
-            %     We found the shortest path between region 1 and the other regions and measure their relative similarity ($p_j$).
-            %     Assuming the maximum similarity is 100 per cent between two neurons (white colour), we multiply the similarity values along the shortest path between two regions to find $p_j$ between region 1 and the other regions (Fig.~\ref{fig: sim_subset1}).
-            %     In both Figs.~\ref{fig: subset1} and ~\ref{fig: sim_subset1} are clear that region 1 shows more similarity to regions 2 and 9 than the others and the most dissimilarity to region 8.
-
-            %     We measured probability of stellar mass given other quantities of the region 1 ($P(m_1\mid \forall_1)$) using Equation~\ref{equ: prob1}.
-            %     \begin{equation}
-            %     \label{equ: prob1}
-            %         P(m_1\mid \forall_1) = \sum_{j=2}^{10}p_j*m_j
-            %     \end{equation}
-            %     Where $m_1$ is the stellar mass of region 1 and $m_j$ is the stellar mass of region j (any other region).
-            %     We estimated the stellar mass to be $\sim1377$~M$\odot$ which is 10 per cent less than the observed values.
-            %     This type of the prediction from SOM networks can be used to predict observation values in observational proposals or can be used in pre-phase studies of the big missions such as the James Webb Space Telescope (JWST) and LLST.
+            Subsets, as studied in this section, can be used to learn about the effect of each input on the SOM and tell us about variation in the input data.
+            Comparing Fig.~\ref{fig: only_pahs} with other networks show us that PAH features are less variable than other input data.
+            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius. %PB: part of sentence missing?
+            Additional evidence for the PAH features varying significantly less than other parameters is that changing from the PAH single band emission to total PAHs does not affect the networks.
+            In contrary, PACS~100~$\mu$m, stellar mass, total gas mass and RHI
+            are the data with the most variance; adding them to input data increases the dark colours between neurons significantly.
+            Although with changing input parameters for each network the  distances between neurons and positions of the regions change, the general positions of the regions  relative to one another does not change dramatically.
+%PB: changed "data" to "regions" in this sentence - please check.
+            Therefore, the networks created by subsets can be used to predict the properties of unobserved quantities in other regions of the galaxy.
+            For example, photometry data, stellar mass, SFR, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, and dust mass are available for most of M31. 
+            The network from Fig.~\ref{fig: wt_pahs} can be applied to 
+            these data from another region in M31.
+            By comparing the position of the new region with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.
 
     \subsection{Testing networks using M101 observations}
-    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions. %%eh
+    Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions.
     To demonstrate this, we generated an SOM using only M31 measurements which were also available for M101 (Fig.~\ref{fig: subset9}a). 
-    \cite{Dim15} compared PAHs in M31 with those from H {\sc II} regions in M101, and showed the similarity between PAHs in these two galaxies (for more detail see \cite{Dim15} and \cite{Gordon08}).
-    In this SOM, as in the others, region 10 is separated from other regions in M31.
-    Regions 7 and 4 are close to each other with very light colours between their neurons, and as in the other SOMs regions 6, 8, and 5 are close to each other, but with a medium dark colour between them.
+    \cite{Dim15} compared PAHs in M31 with those from \hii~regions in M101, and showed the similarity between PAHs in these two galaxies (for more detail see \cite{Dim15} and \cite{Gordon08}).
+    In order to test whether these similarities are limited to PAH features or can be extended to other features in these two galaxies, we applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
+    Since the neurons in the SOM network created by M31 data already have their finalized weights, the algorithm finds the minimum differences between parameters for each region in M101 and the weights of neurons and introduces the winner neuron in one iteration.
+    %This process is time efficient %PB:sentence incomplete?
+
+    In the SOM that is created by M31 data in Fig.~\ref{fig: subset9}a, as in the others, region 10 is separated from other regions in M31.
+    Regions 7 and 4 are close to each other with very light colours between their neurons, and as in the other SOMs regions 6, 8, and 5 are close to each other, but with medium dark colour between them.
+    Given the fact that we know the relative relation between M31 regions from 2D networks, we can analyze properties of M101 regions from their locations in Fig.~\ref{fig: subset9}b.
+    To do so, we compared positions of regions in M31 and M101 in the networks presented in Fig.s~\ref{fig: subset9}a and~\ref{fig: subset9}b, respectively, and based on colours between regions determine their (dis-)similarities.
     \import{../image_paper3/text_files/image_texts/}{subset9.tex}
 
-    We applied the SOM created using M31 data in Fig.~\ref{fig: subset9}a to M101 data (Fig.~\ref{fig: subset9}b).
-    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupied neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties.
-    Region 2 in M101 is a bright H {\sc II} region located at the end of the one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
+    Region 5 in M31 and region 8 in M101 and regions 6 in M31 and region 2 in M101 occupy neurons with a white colour between them in the network in Fig.~\ref{fig: subset9}, which immediately suggests that these regions have similar properties.
+    Region 2 in M101 is a bright \hii~region located at the end of  one of the M101 spiral arms (see Fig.~\ref{fig: regions in m101}) while
     region 6 in M31 is located near the inner star-forming ring (see Fig.~\ref{fig: regions in m31}).
@@
 
-    Region 5 in M31 is in the inner ring of the galaxy and it is one of two regions in M31 that are not an  H {\sc II} region, while
+    Region 5 in M31 is in the inner ring of the galaxy and it is one of two regions in M31 that is not an  \hii~region, while
     region 8 in M101 is in a spiral arm of the galaxy.
     Relatively low stellar mass, SFR and SPIRE band emission caused these two regions to be nearby in the map.
-    In Sec.~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties; in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
+    In Section~\ref{Sec: 1d_cluster} we showed that regions 3 to 8 in M31 have similar properties; in Fig.~\ref{fig: subset9}b we see that regions 1 to 3 and 5 to 8 in M101 are located near regions 3 to 8 in M101.
     These regions all have medium or low PAH emission, dust and SFR compared to the remaining regions.
@@
 
-    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, we can have ideas about data entry from other regions/galaxies.
-    In this section we showed that we can use networks that are created by data from nearby galaxies, to study the properties of other galaxies in a fast way.
+    Knowing the effects of the different input quantities on the networks from Section~\ref{sec: subsets}, can yield ideas about data entry from other regions/galaxies.
+    In this section we showed that we can use networks that are created by data from nearby galaxies to study the properties of other galaxies.
+    If an SOM network is available, applying data from other regions to the network is very time efficient to learn about relative properties of galaxies.
     We should note that, since we normalized data before using them in the networks, we only see relative properties of the regions.
-    Therefore, we need data from few regions in the galaxy to use this network and cannot use these networks to learn about properties of a single region in other galaxies.
+    Therefore, we need data from at least a few regions in the galaxy to use this application of SOMs and cannot use these networks to learn about properties of a single region in other galaxies.
+    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that region 7 and 4 have relatively higher surface brightness than the other regions in M101.
+    Similarly, we can say that regions 6 and 8 in M101 have very faint surface brightness for most of the parameters, and are very different from regions 7 and 4.
 
@@
 
-We present results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
+We present the results of studying spatially resolved regions in nearby galaxies using Kohonen self-organizing maps.
 Self-organizing maps both cluster data and show relative distance between the clusters. 
-We utilized the method to find hidden subgroups in the data as well as finding relations between those groups.
+We utilized the method to find hidden subgroups in the data as well as to find relations between those groups.
 
-Using smaller-sized self-organizing maps, we found that the M31 data are clustered into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
+Using smaller-sized self-organizing maps, we clustered M31 data into two major groups, which led us to correlations that could not have otherwise been seen without clustering.
 Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
@@
 This result shows that PAHs in the clustered regions in M31 are not heated by the old stellar populations.
+The reason behind the observed anti-correlation between PAH features and stellar mass needs further investigation, which requires mid-infrared PAH observations for more regions in M31.
 
@@
 We created various subsets of the input data and generated different networks which helped to show relations between regions in M31 more clearly.
-Region 10 always becomes isolated in the networks, except when we  used only PAH data to create a network. %PB: remind the reader where regions 8 and 10 are
-In that network region 10 blends more with other regions and only shows differences with the data from region 8.
+Region 10, which is located in the bulge of M31, always becomes isolated in the networks, except when we  used only PAH data to create a network.
+In that network region 10 blends more with the other regions and is only differentiated from region 8, which is located inside the inner ring of M31.
 These results suggest that the PAHs in all 10 regions have almost the same properties.
 
+We introduced self-organizing maps as a method that can be used to predict various quantities based on the relative positions of the regions in the networks.
+For regions that lack the observational data for some quantities (e.g. PAH emission), SOMs can be used to extrapolate the unobserved quantities.
 Applying the SOMs from M31 to observations of M101, we found regions with similar properties in both galaxies placed in close regions in the SOMs.
 Using this ability of the SOM, we can predict properties of regions in other nearby galaxies very quickly.
+
 The networks we created used values for 26 quantities from 10 regions in M31, which is not a large sample.
 Increasing the dimension of the data and the number of regions would yield more reliable networks.
-In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83) and learn about the properties of regions in those galaxies.
+Since there is very little spatially-resolved PAH spectroscopy for other galaxies from the \Spitzer Space Telescope, increasing the size of samples will require data from the James Webb Space Telescope.
+The method described in this work can be used to select target regions for PAH observations with that facility. %%Eh % better now?
 

### 2016-07-17 version0.0/summary.tex
fig.s and table corrections

--- 2016-07-10 version0.0/summary.tex
@@
-\chapter{Summary and feature works}
+\chapter{Conclusions \& Future Work}
 \label{ch: summary}
+ %General
+The formation of stars is one of the fundamental factors in the formation and evolution of galaxies.
+Measuring the star formation rate and its variation through time helps us to learn about how a galaxy forms and evolves.
+Many efforts have been made to find a universal law for the rate at which stars form.
+In order to find a universal law, finding a method to measure SFR accurately is the first step.
+Then correlations between SFR and other properties of galaxies must be investigated.
+Afterward, each law has to be tested in various environments to confirm its universality.
+Therefore, we need high quality data and good statistical methods to test the laws.
+
+It has been well established that to form stars, gas is the main ingredient.
+However, the relation between SFR and different tracers of gas mass (atomic, molecular, or total gas) changes in different type of galaxies.
+Relations between stellar mass, metallicity and SFR are not clear and there are fewer studies of these than of the relation between SFR and gas mass.
+The dependence of SFR on other properties of galaxies such as morphology and dust mass have been tested as well, but there is no SFR law that considers all of the above quantities together.
+The Kennicutt-Schmidt law ~\citep{Schmidt59, Kennicutt98b} was the first empirical star formation law, suggesting that SFR and molecular gas have a logarithmic correlation with each other. 
+However, after many years and studies, there is still an ongoing question of whether it is a universal law or not.
+\citet{Shetty13} showed that, besides the physical and environmental effects, fitting methods also change our perspective of the K-S law.
+Extended version of the K-S law were introduced by adding the effect of stars (extended Schmidt law; introduced by ~\citealt{Shi11}) or metallicity (Krumholz law; introduced by ~\citealt{Krumholz09}).
+Compared to the K-S law, the extended Schmidt law and Krumholz law are relatively recently introduced and still need to be tested with diverse statistical methods on different scales (local and global), with various morphological types and in both nearby and high-redshift galaxies.
+
+%Chapter 2
+Spatially resolved images of the Andromeda galaxy (M31) cover different types of environments within a galaxy: high or low stellar surface density, gas mass, and metallicity.
+These images permit us to examine star formation laws in detail, in various environments.
+In Chapter~\ref{ch: paper1}, we investigated three star formation laws in M31 on both local and global scales in order to determine which of these laws describe M31 data more accurately.
+To achieve this goal, we produced maps of surface density of SFR, gas mass, stellar mass and metallicity of the galaxy.
+We created SFR maps using three SFR indicators: a combination of the FUV and 24~\um emission, a combination of the \halpha and 24~\um emission, and TIR luminosity. 
+Using a combination of the FUV and 24~\um emission, we determined the total SFR for M31 to be $0.31\pm 0.04$~M$_\odot$~yr$^{−1}$.
+We measured the ISM gas mass using molecular gas only, atomic gas only and the total gas.
+We confirmed that the extended Schmidt law holds in M31 for local regions and the effect of stellar mass in regions with low gas density is even more pronounced. 
+By applying both the K-S law and the extended Schmidt law on all SFR maps and gas maps, we concluded that changes in SFR tracer do not affect these laws as much as changes in gas tracer.
+Our fitting results show that in regions with higher star formation rate, power laws are more in agreement with other studies.
+In order to examine Shetty's suggestions on the effect of fitting methods on SFR laws, we used hierarchical Bayesian regression fitting and normal regression fitting to fit SFR laws.
+The results from the two different methods are dissimilar, mostly because of the ways these two methods handle the uncertainties.
+The measured SFR by the Krumholz law did not match with the observed data in M31.
+By performing statistical tests, we showed that there is no strong correlation between metallicity and SFR in M31.
+
+%Chapter 3 
+For the remainder of this thesis we used a machine learning method to have a fresh look on star formation and its relation to other properties of galaxies.
+We chose the self-organizing map algorithm as our data mining method because of its ability to classify results and show the morphology of data, simultaneously.
+The amount of observational data and derived quantities for M31 is enough to make this galaxy a good target for machine learning studies.
+Therefore, in Chapter~\ref{ch: paper3} we applied the self-organizing map algorithm on observational data from M31.
+We used observational data and derived quantities of 10 regions in M31, which were chosen due to the availability of mid-infrared spectroscopy for those regions.
+Therefore, we were able to focus on relations between SFR and interstellar medium components, specifically polycyclic aromatic hydrocarbons (PAHs).
+Using a network with 2 neurons, we divided the data into two major groups.
+By comparing data from these groups, we found correlations within groups that otherwise would not have been seen.
+In one of the groups, the flux from PAHs showed strong anti-correlations with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
+We found two reasons for PAHs to anti-correlate with optical emission and RHI.
+First, the harder radiation field could make the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission.
+Second, since optical emission was not corrected for dust extinction, dustier regions would have less observed optical emission.
+Since for 10 regions in M31 we needed at least 14 neurons to separate all 10 regions from each other, we concluded that some of these 10 regions have very similar properties.
+Using subsets of the data we generated various two dimensional networks.
+The networks created by the subsets showed that, except for PAH-only subsets, region 10, which is located in the bulge of M31, becomes isolated.
+The network from the PAH-only data is the only network with no isolated regions, which means that, despite differences in underlying physical conditions in different regions, PAHs in M31 are very similar.
+We created another network using the same set of M31 observations that were available for M101.
+Using subsets of data, we show that the SOMs can be used to predict observations for regions that lack the observational data for some quantities (e.g.\ PAH emission).
+We applied this network to the M101 observations and showed that regions with relative similarity to M31 data were placed in the same neurons.
+Therefore, we can use these networks to predict properties of other galaxies.
+
+%chapter 4
+In Chapter~\ref{ch: paper2}, we used the self-organizing map algorithm on data from high-redshift galaxies.
+We classified the template spectra of~\citet{Kinney96}, made from galaxies with known morphological type, and created networks with different uses.
+Similar to the results of Chapter~\ref{ch: paper3}, since we needed at least 22 neurons to separate 12 spectral types, we concluded that some of the spectral types have very similar features (types B and E, and types SB1 and SB2 from \citealt{Kinney96}).
+We showed that network generated by the self-organizing map method can be used to identify new types of spectra in large surveys.
+Using the trained networks, we classified a sample of 142 galaxies from~\citet{Hossein12}.
+The classification by self-organizing map allowed us to identify galaxies with SEDs similar to two or more morphological types.
+Comparing our results with classifications from trained networks showed that this unsupervised method could classify all 142 spectra while the supervised methods failed to classify 37 out 142 galaxies.
+The properties of the 142 classified galaxies show better correlations in mean values of age, specific star formation rate, stellar mass, and far-UV extinction compared to the other methods.
+These correlations are also in agreement with the galaxies' morphological types.
+
+%future works and add big questions
+To move forward, we would like to test star formation laws in high-redshift galaxies with the hierarchical Bayesian regression fitting method.
+This would allow investigation of both the effects of fitting methods on using global values for galaxies and differences in using this method on nearby galaxies and high-redshift ones.
+We could also use data mining methods to recalibrate the correlations between luminosities from star forming regions and the SFR in both nearby and high redshift galaxies.
+Self-organizing maps can help us to examine our calibrations of the SFR, find their flaws and predict the SFR in distant galaxies.
+Another project to continue after this thesis would be to show that self-organizing maps are good tools to predict properties of galaxies and estimate values of unobserved quantities.
+Continuing the work in Chapter~\ref{ch: paper3}, we would like to obtain mid-infrared spectroscopy with more coverage in M31 and other nearby galaxies to have a higher dimensional sample for creating SOMs as well as to investigate the anti-correlation between stellar mass and PAHs.
+Having these new calibrations for finding properties of galaxies and applying them to observations from recently (or soon to be) operational telescopes such as TMT, ALMA, SKA, and {\it JWST} would help us solve the mystery of how stars form and evolve in time.
+
+\addcontentsline{toc}{section}{Bibliography}
+\bibliographystyle{apj.bst}
+\bibliography{western_bib.bib}

### 2016-07-17 version0.0/intro0.01.tex
Completed intro.

@@
 Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
-%PB: changed "I" to "we" here - you are talking about the field as a whole, not you in particular
 
@@
 It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
-Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see ][for more detail]{Walch08}.
+Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see ][for more detail]{Walcher08}.
 For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
@@
 Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
-%The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
 In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
@@
 Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}.
-%%SR: it is B stars not O ones!
 Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
@@
 
-Most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state}(the state of angular momentum, J) and can be excited in the temperature of molecular clouds.
+%Most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state}(the state of angular momentum, J) and can be excited in the temperature of molecular clouds.
 %PB: need to fix text in {\bf} earlier in this sentence.
+Most of our knowledge of molecular clouds come from observation of line emission of CO molecules, which, die to their large mass, possess a very low energy rotational state (the state of angular momentum, J) and can be excited in the temperature of molecular clouds.
+%Sr should I put the \bf back?
 Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
@@
 \begin{figure}
-\label{fig: mco}
 \centering
@@
 The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from~\cite{Bolato08}.}
+\label{fig: mco}
 \end{figure}
@@
 Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
-Fig.~\ref{fig: mco} shows the CO luminosity versus virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
+Fig.~\ref{fig: mco} shows the CO luminosity versus virial masses of the Galactic and extragalactic molecular clouds. 
 The extragalactic molecular clouds are similar to those in the Milky Way. 
@@
 Extragalactic investigations have been limited to nearby galaxies due to telescope resolution and sensitivity. 
-To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40 pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and references therein]{Young91,Bolato13}.
+To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40~pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and references therein]{Young91,Bolato13}.
 
 Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
-Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight.
-%PB: should that be cm$^{-2}$ ?
+Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-2}$), along the line-of-sight.
 \begin{equation}
@@
 Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
-This effect grows inversely with the wavelength.
-Extinction can be defined as a reduction of the original intensity caused by dust:
+This effect grows inversely with wavelength.
+%Extinction can be defined as a reduction of the original intensity caused by dust:
+Extinction is quantified as the difference in observed and initial magnitudes of an object in a specific wavelength ($\lambda$):
+\begin{equation}
+m_{\lambda} - m_{\lambda}(0) = \mathrm{A}_{\lambda},
+\end{equation}
+where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are observed and initial magnitude, respectively.
+Magnitude is related to intensity (I) as:
+\begin{equation}
+m_{\lambda} = 2.5 \log (I_{\lambda}) + C,
+\end{equation}
+where c is a constant which depends on photometric system that is being used.
+Optical depth, $\tau_{\lambda}$, is defined by ratio of observed and initial intensity of a source as:
 \begin{equation}
@@
 \end{equation}
-where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction at wavelength $\lambda$.
-%PB: extinction or optical depth?
+where I$(\lambda)$ is observed intensity in wavelength $\lambda$ and I$_0(\lambda)$ is intensity of light before passing through dust.
+Therefore, the optical depth and extinction can be converted to one an other by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
 The extinction also depends on the grain size and extinction cross section.
@@
 \end{equation} 
-where $M$ is the stellar mass, $\gamma$ is a power-law index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.
-%PB should that be $\log $M to $\log M + d\log M$ ?
-Please check mass range.
+where $M$ is the stellar mass, $\gamma$ is a power-law index, and $N$ is the number of stars in the logarithmic mass range of $\log M$ to $\log M + d\log M$.
 
@@
 \begin{figure}
-\label{fig: imf}
 \centering
@@
 Adopted from~\cite{Baldry03}.}
+\label{fig: imf}
 \end{figure}
@@
 
-\begin{center}
 \begin{table}
@@
 \label{table1}
+\begin{center}
 \begin{tabular}{ c c c }
@@
 \end{tabular}
+\end{center}
 \begin{tablenotes}
 \item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
-\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}.
-For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$ to convert luminosity density to luminosity.
-%or flux density?
+\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in \AA to convert luminosity density to luminosity. 
 \item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Section~\ref{sec: imf}), and for the timescale $\tau$.
@@
 \end{table}
-\end{center}
 
@@
 \end{equation}
-where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ can be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
+where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ can be in the range of $(912< \lambda < 3000~$\AA), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
 As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
@@
 where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
-The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
-%PB: big $N$ (column density) or small $n$ (number density) ?
+The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density n$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
 Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
 The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
-by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
+by adding L(24~$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
 
-Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
+Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727~\AA. 
 Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
@@
 \label{table_PAH}
+\begin{center}
 \begin{tabular}{ l c c}
@@
 \end{tabular}
+\end{center}
 \end{table}
-\end{center}
 
@@
 $\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}.
-The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.p][]{Hao11, Leroy08}.
+The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs~\citep[e.g.][]{Hao11, Leroy08}.
 
@@
 \label{table3}
+\begin{center}
 \begin{tabular}{ c c}
@@
 \hline
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\ % use \cite
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\
 L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& \cite{Hao11}\\
@@
 \end{tabular}
+\end{center}
 \begin{tablenotes}
@@
 The simplest and the most common way to estimate the mass of a galaxy is to assume that the dynamics of the galaxy are governed by simple Newtonian classical physics.
-In this model, the circular velocity $v_{\rm circ}(r)$ of an orbit with radius $r$ within a spherical system of gravitational potential $\phi$ and mass $M$ is given by:
+In this model, the circular velocity $v_{\mathrm{circ}}(r)$ of an orbit with radius $r$ within a spherical system of gravitational potential $\phi$ and mass $M$ is given by:
 \begin{equation}
 \label{eq: simpmass}
-v^2_{\rm circ}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r},
+v^2_{\mathrm{circ}}(r)=r\frac{d\phi}{dr} = G\frac{M(r)}{r},
 \end{equation}
@@
 \begin{equation}
-v^2_{circ}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)],
+v^2_{\mathrm{circ}}(R)= 4\pi G \Sigma_{0}R_{d} y^2[I_0(y)K_0(y) - I_1(y)K_1(y)],
 \end{equation}
-where $\Sigma_0$ the central surface brightness, $R_d$ is the disk scale length where the ratio of the intensity of disk to bulge is equal to $e$.% ($\sim$2.71).
-%PB: don't need to define e, but do need to define $R$ !!
+where $R$ is the distance from the centre, $\Sigma_0$ the central surface brightness, $R_d$ is the disk scale length where the ratio of the intensity of disk to bulge is equal to $e$.
 $y$ is equal to $\frac{R}{2R_d}$, and $I_i(y)$ and $K_i(y)$ are  modified Bessel functions of the first and second kinds.
@@
 Using the $M/L$ of galaxies, they found correlations between $K_s$ band (2.2~$\mu$m), 3.6 and 4.5~$\mu$m band luminosities and stellar masses and formulated these correlations as:
-\begin{align} %PB: does this need a \begin{equation} ??
+\begin{equation}
+\begin{split}
 \label{equ: zhu1}
-\log M_{\star} = -1.60  + 1.12  \log \nu L_{\nu}[K_s]\\
-\log M_{\star} = -0.79 + 1.19 \log \nu L_{\nu}[3.6\mu \rm m]\\
-\label{equ: zhu3}
-\log M_{\star} = -0.25 + 1.15\log \nu L_{\nu}[4.5\mu \rm m], 
-\end{align}
+\log M_{\star} =& -1.60  + 1.12  \log \nu L_{\nu}[K_s]\\
+\log M_{\star} =& -0.79 + 1.19 \log \nu L_{\nu}[3.6\mu \rm m]\\
+\log M_{\star} =&-0.25 + 1.15\log \nu L_{\nu}[4.5\mu \rm m], 
+\end{split}
+\end{equation}
 where M$_{\star}$ is the stellar mass in solar masses and $ \nu L_{\nu}[\lambda]$ is the luminosity in erg~s$^{-1}$ at a specified wavelength.
@@
   M_{\star} = 31.84 \times 10^{5.65} L_{3.6}^{2.85} L_{4.5}^{-1.85},
- %\log M_{\star} = 5.6 +2.85\log (F_{3.6})-1.85 \log (F_{4.5})+2\log \left(\frac{D}{0.05}\right)
 \end{equation}
-where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$~$\AA^{-1}$.
-Equ.~\ref{equ: zhu1}--~\ref{equ: zhu3} were derived from a large sample of galaxies and tested on different types of regions and galaxies.
+where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$~\AA$^{-1}$.
+Equ.s in~\ref{equ: zhu1} were derived from a large sample of galaxies and tested on different types of regions and galaxies.
 On the other hand,~\cite{Eskew12} mentioned that since their calibration is based on data from the Magellanic Clouds,
 measuring the stellar mass from Equ.~\ref{equ:eskew} might break down for highly star-forming regions; moreover, this equation has not been tested on regions with different metallicities. 
-In more recent work,~\cite{Laura16} measured stellar mass for a group of galaxies with ($z < 0.035$) and showed they are tightly correlated with stellar mass measured from other calibrations.
-%PB: how measured?
-What is "they" ?
-
+%In more recent work,~\cite{Laura16} measured stellar mass for a group of galaxies with ($z < 0.035$) using correlation introduced by~\cite{Eskew12} and showed these stellar masses are tightly correlated with stellar masses measured from other calibrations.
+In more recent work,~\cite{Laura16} measured stellar mass for a group of galaxies with $z < 0.035$, using the correlation that was introduced by~\cite{Eskew12}. 
+The study revealed that measured stellar masses in that study are tightly correlated with stellar masses measured from other calibrations.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-07-18 version0.0/appendixa.tex
Completed intro.
Completed paper1 and 3

@@
-\chapter{SFR from H$\alpha$ plus 24 \um: procedure and result}
+\chapter{SFR from H$\alpha$ Plus 24 \um: Procedure and Result}
 \pagestyle{plain}
 \label{app:halpha}
-\myappendices{
-As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps.
+\myappendices
+As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps.
 These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive.
-Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.
+Making a spatially resolved SFR map of M31 using \halpha emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of \halpha continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.
 
-The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from H$\alpha$ using the scaling factor between fluxes in these two band passes determined by \citet{Azimlu11}.
-They estimated continuum emission in each H$\alpha$ image, using photometric measurements in both \halpha and R-band images, and determined the scaling factor.
+The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from \halpha using the scaling factor between fluxes in these two band passes determined by~\citet{Azimlu11}.
+They estimated continuum emission in each \halpha image, using photometric measurements in both \halpha and $R$-band images, and determined the scaling factor.
 These images were observed from a ground-based telescope over two years' time.
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
 \includegraphics[width=164mm]{../image_paper1/halpha.pdf}
-\caption{Mosaic created using the Montage programme from six fields of H$\alpha$ emission images of M31 from \citet{Massey07}.
+\caption[Mosaic of H$\alpha$ emission images of M31]{Mosaic created using the Montage programme from six fields of \halpha emission images of M31 from \citet{Massey07}.
 The resulting image from Montage was continuum-subtracted and masked for all point sources.
@@
 \label{fig:halpha}
-\end{figure*}
+\end{figure}
 
-To create the final mosaic, first we removed the background from each region in both the \halpha and $R$-band images.
+To create the final mosaic, first we removed the background from each region in both the \halpha\ and $R$-band images.
 The second step was to subtract the continuum from the \halpha images.
 Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image.
-At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin region in the centre of the galaxy.
-To account for the flux contribution of the [N II] emission we used the flux ratio ${\mathrm \nii}/{\mathrm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map.
-We created the final mosaic image, Figure~\ref{fig:halpha}, using the Montage program \citep{Berriman08}.
+At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin\ region in the centre of the galaxy.
+To account for the flux contribution of the \nii\ emission we used the flux ratio $\mathrm{\nii}/\mathrm{H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha\ map.
+We created the final mosaic image, Fig.\ref{fig:halpha}, using the Montage program~\citep{Berriman08}.
 
-Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}.
+Creating the SFR map using \halpha plus 24~$\mu$m was described in Section~\ref{sec:sfr_halpha}.
 In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
@@
 
-\newpage
-\section{More results from the fitting of the extended Schmidt law}
-\label{app:es,figs}
-Section~\ref{sec: sfl} discusses testing the extended Schmidt law and shows results for one SFR/gas tracer combination. Here we present the plots for the remaining SFR/gas tracer combinations.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_h2.png}
-        \caption{Surface density of SFR(TIR) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis) }
-        \label{fig:es,all,fir,h2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_hi2.png}
-        \caption{Surface density of SFR(TIR) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis) }
-        \label{fig:es,all,fir,hi}
-    \end{subfigure}
-    \hfill
-   \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_tot2_f.png}
-        \caption{Surface density of SFR(TIR) vs surface density of total gas and surface density of stellar mass ($z$-axis)}
-        \label{fig:es,all,fir,tot}
-    \end{subfigure}
-       \caption{Same as Figure~\ref{fig:es,all,fuv,tot}.
-Here, from top to bottom plots show the surface density of the SFR(TIR) vs.
-surface density of H$_2$, surface density of H\,{\sc I}, and the surface density of total gas, respectively.
-As in Figure~\ref{fig:ks_all}, the analyses use different pixel sizes: each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in the plots with the surface density of H\,{\sc I} or total gas mass represents a region of size $\sim$155~pc.
-Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
-       \label{fig:es,fir}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-     \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_h22_f.png}
-        \caption{Surface density of SFR(FUV+24~$\mu$m) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis)}
-        \label{fig:es,all,fuv,h2}
-    \end{subfigure}
-     \hfill
-   \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_hi2.png}
-        \caption{Surface density of SFR(FUV+24~$\mu$m) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis)}
-        \label{fig:es,all,fuv,hi}
-    \end{subfigure}
-   \caption{Same as Figure~\ref{fig:es,fir}, but in this figure we used FUV + 24~$\mu$m as a tracer of the SFR.
-The plot of the surface density of the SFR(FUV+24~$\mu$m) vs the surface density of the total gas is shown in Figure~\ref{fig:es,all,fuv,tot} in the main text.}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-   \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_h22_f.png}
-        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis)}
-        \label{fig:es,all,halpha,h2}
-    \end{subfigure}
-     \hfill
-      \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_hi2.png}
-        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis)}
-        \label{fig:es,all,halpha,hi}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_tot2_f.png}
-        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs. surface density of total gas and surface density of stellar mass ($z$-axis)}
-        \label{fig:es,all,halpha,tot}
-    \end{subfigure}
-    \caption{Same as Figure~\ref{fig:es,fir}, but in this figure we used H$\alpha$ + 24~$\mu$m as a tracer of the SFR.}
-\end{figure*}
-
-}
+\bibliographystyle{apj.bst}
+\bibliography{ref_paper1.bib}

### 2016-07-18 version0.0/appendixa_2.tex
Completed paper1 and 3

@@
-\chapter{More results from the fitting of the extended Schmidt law}
+\chapter{More Results from the Fitting of the Extended Schmidt Law in M31}
 \pagestyle{plain}
 \label{app:es,figs}
-\myappendices{
+\myappendices
+
 Section~\ref{sec: sfl} discusses testing the extended Schmidt law and shows results for one SFR/gas tracer combination. Here we present the plots for the remaining SFR/gas tracer combinations.
 
-\begin{figure*}
+\begin{figure}
     \centering
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_h2.png}
+        \includegraphics[width=0.5\textwidth]{../image_paper1/es_tot_fir_vs_h2.png}
+        \captionsetup{font=tiny}
         \caption{Surface density of SFR(TIR) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis) }
@@
     \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_hi2.png}
-        \caption{Surface density of SFR(TIR) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis) }
+        \includegraphics[width=0.5\textwidth]{../image_paper1/es_tot_fir_vs_hi2.png}
+        \captionsetup{font=tiny}
+        \caption{Surface density of SFR(TIR) vs surface density of \hi\ and surface density of stellar mass ($z$-axis) }
         \label{fig:es,all,fir,hi}
@@
     \hfill
-   \begin{subfigure}[b]{0.5\textwidth}
+   \begin{subfigure}[b]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../image_paper1/es_tot_fir_vs_tot2_f.png}
+        \includegraphics[width=0.5\textwidth]{../image_paper1/es_tot_fir_vs_tot2_f.png}
+        \captionsetup{font=tiny}
         \caption{Surface density of SFR(TIR) vs surface density of total gas and surface density of stellar mass ($z$-axis)}
@@
     \end{subfigure}
-       \caption{Same as Figure~\ref{fig:es,all,fuv,tot}.
+       \caption[Same as Fig.~\ref{fig:es,all,fuv,tot}, but here the surface density of the SFR(TIR) versus three gas tracer are used]{Same as Fig.~\ref{fig:es,all,fuv,tot}.
 Here, from top to bottom plots show the surface density of the SFR(TIR) vs.
-surface density of H$_2$, surface density of H\,{\sc I}, and the surface density of total gas, respectively.
-As in Figure~\ref{fig:ks_all}, the analyses use different pixel sizes: each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in the plots with the surface density of H\,{\sc I} or total gas mass represents a region of size $\sim$155~pc.
+surface density of H$_2$, surface density of \hi\, and the surface density of total gas, respectively.
+As in Fig.~\ref{fig:ks_all}, the analyses use different pixel sizes: each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in the plots with the surface density of \hi\ or total gas mass represents a region of size $\sim$155~pc.
 Solid lines show the best fit, using the mean value of the ranges in Table~\ref{table:res}.}
        \label{fig:es,fir}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
     \centering
@@
         \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_h22_f.png}
+        \captionsetup{font=tiny}
         \caption{Surface density of SFR(FUV+24~$\mu$m) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis)}
@@
         \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_hi2.png}
-        \caption{Surface density of SFR(FUV+24~$\mu$m) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis)}
+        \captionsetup{font=tiny}
+        \caption{Surface density of SFR(FUV+24~$\mu$m) vs surface density of \hi\ and surface density of stellar mass ($z$-axis)}
         \label{fig:es,all,fuv,hi}
     \end{subfigure}
-   \caption{Same as Figure~\ref{fig:es,fir}, but in this figure we used FUV + 24~$\mu$m as a tracer of the SFR.
-The plot of the surface density of the SFR(FUV+24~$\mu$m) vs the surface density of the total gas is shown in Figure~\ref{fig:es,all,fuv,tot} in the main text.}
-\end{figure*}
+   \caption[Same as Fig.~\ref{fig:es,fir}, but in this figure we used FUV $+$ 24~$\mu$m as a tracer of the SFR]{Same as Fig.~\ref{fig:es,fir}, but in this figure we used FUV $+$ 24~$\mu$m as a tracer of the SFR.
+The plot of the surface density of the SFR(FUV+24~$\mu$m) vs the surface density of the total gas is shown in Fig.~\ref{fig:es,all,fuv,tot} in the main text.}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
   \centering
@@
         \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_h22_f.png}
+        \captionsetup{font=tiny}
         \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs surface density of H$_2$ and surface density of stellar mass ($z$-axis)}
@@
         \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_hi2.png}
-        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs surface density of H\,{\sc I} and surface density of stellar mass ($z$-axis)}
+        \captionsetup{font=tiny}
+        \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs surface density of \hi\ and surface density of stellar mass ($z$-axis)}
         \label{fig:es,all,halpha,hi}
@@
         \includegraphics[width=\textwidth]{../image_paper1/es_tot_halpha_vs_tot2_f.png}
+        \captionsetup{font=tiny}
         \caption{Surface density of SFR(H$\alpha$+24~$\mu$m) vs. surface density of total gas and surface density of stellar mass ($z$-axis)}
@@
     \end{subfigure}
-    \caption{Same as Figure~\ref{fig:es,fir}, but in this figure we used H$\alpha$ + 24~$\mu$m as a tracer of the SFR.}
-\end{figure*}
-
-}
+    \caption{Same as Fig.~\ref{fig:es,fir}, but in this figure we used H$\alpha$ + 24~$\mu$m as a tracer of the SFR.}
+\end{figure}

### 2016-07-18 version0.0/appendixb.tex
Completed paper1 and 3

@@
-\chapter{2-Dimensional networks from subsets of M31}
+\chapter{Two-Dimensional Networks From Subsets of M31}
 \pagestyle{plain}
@@
 \newpage
-\myappendices{
+\myappendices
 
-        We removed IRAC 5.7 $\mu$m; \sii~continuum and \oiii~continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, \oiii~continuum, stellar mass and metallicity from subset 0, and generated subset samples 2 to 4, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
+        We removed IRAC 5.7 $\mu$m; \sii~continuum and \oiii~continuum; PAH8.3 $\mu$m, PAH12.0 $\mu$m, PAH17.0 $\mu$m, \oiii~continuum, stellar mass and metallicity from data from 10 regions in M31 that were described in Section~\ref{Sec: data_SOMN}, and generated subset samples 4 to 6, respectively (Tables~\ref{tab: subset2} to~\ref{tab: subset4}).
         In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}.
         IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
-        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
-        For subset sample 7 (Table~\ref{tab: subset7}) we removed \sii~flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 2 (~\ref{tab: subset5}).
+        Therefore, removing flux from IRAC 5.7~$\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
+        For subset sample 7 (Table~\ref{tab: subset7}) we removed \sii~flux, SPIRE 250 and 500~$\mu$m and TIR emission from subset 4 (~\ref{tab: subset5}).
         The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
-        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
+        In general by removing IRAC 5.7~$\mu$m flux data from the input data, the colours between regions become much more darker.
 
@@
 
-        In the results from the subset 4 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
+        In the results from the subset 6 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
         These two regions have distinct metallicity, removing metallicity from input data caused these two stay in a closer neurons. 
@@
         Therefore, both of them have similar values in most of the input parameters.
-        However, they have very different fluxes in IRAC 5.7 $\mu$m and \sii~continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
-        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
+        However, they have very different fluxes in IRAC 5.7~$\mu$m and \sii~emission, which removing these two fluxes from the input data moved their position on the SOM closer.
+        TIR luminosity and IRAC 5.7~$\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
         In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
@@
         \import{../image_paper3/text_files/image_texts/}{subset7.tex}
-        }

### 2016-07-18 version0.0/appendixc.tex
fig.s and table corrections
Completed paper1 and 3

@@
-\chapter[Self-Organizing Map for High-redshift galaxies]{Results of Training High-redshift Galaxies for one-dimensional self-organizing maps}
+\chapter[Self-Organizing Map for High-redshift Galaxies]{Results of Training High-redshift Galaxies for One-Dimensional Self-Organizing Maps}
 \pagestyle{plain}
@@
 \myappendices{
-As mentioned in Sec.~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$.
+As mentioned in Section~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$.
 In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.
@@
     }
+
+\bibliographystyle{apj.bst}
+\bibliography{ref_paper2.bib}

### 2016-07-18 version0.0/paper1.tex
Completed paper1 and 3

@@
-\chapter[Star formation laws in M31]{Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}
+\chapter[Star Formation Laws in M31]{Star Formation Laws in the Andromeda Galaxy: Gas, Stars, Metals and the Surface Density of Star Formation}
 \label{ch: paper1}
-
 \section{Introduction}
@@
 
-\begin{table*}
+\begin{table}
 \centering
@@
 \end{tabular}
-\end{table*}
+\end{table}
 
@@
 This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a 5\degr.1 $\times$ 1\degr.5 region with an angular resolution of 60\arcsec $\times$ 90\arcsec.
-
-\section{Measuring the components of Star Formation Laws}
+\section{Measuring the Components of Star Formation Laws}
 Before studying the star formation laws, we need to calculate the components of these laws.
@@
 \label{sec:sfr}
-\subsubsection{FUV plus 24~$\mu$m Star Formation Rate}
+\subsubsection{FUV Plus 24~$\mu$m Star Formation Rate}
 
@@
 However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction.
-On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars.
+On the other hand, 24~$\mu$m emission is dominated by emission from dust heated by UV photons from young and hot stars.
 This emission is sensitive to the star formation timescale of $<10$ Myr \citep{Calzetti07}.
@@
        \includegraphics[width=\textwidth]{../image_paper1/sfr_fir.eps}
-    \caption {SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}).
+    \caption[SFR map calculated from total infrared emission ]{SFR map calculated from total infrared emission (see Section~\ref{sec:sfr_fir}).
 The SFR map here has an angular resolution of 18\arcsec and pixel size of 9.85\arcsec, the same as the MIPS 70 $\mu$m map.}
@@
 %----------------------------------------------------------------------------------------
-
 \subsection{Gas Surface Density}
@@
 \includegraphics[width=\textwidth]{../image_paper1/star.eps}
-\caption{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
+\caption[Stellar mass surface density map produced using IRAC 3.6~$\mu$m data]{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
 \label{fig:stellarmass}
@@
 We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission.
-We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $F_{3.6 \mu m}$ and $F_{4.5 \mu m}$, though this was not mentioned in the aforementioned paper.
+We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $\mathrm{F}_{3.6 \mu \mathrm{m}}$ and $\mathrm{F}_{4.5 \mu \mathrm{m}}$, though this was not mentioned in the aforementioned paper.
 Fig.~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6~\um in the original angular resolution and pixel size of the IRAC 3.6~\um image.
@@
 %----------------------------------------------------------------------------------------
-\section{Scaling the star formation rate}
-\subsection{Fitting method}
+\section{Scaling the Star Formation Rate}
+\subsection{Fitting Method}
 \label{sec:fitting}
@@
 \includegraphics[width=\textwidth]{../image_paper1/ks_all_density.pdf}
-\caption{Results from fitting the Kennicutt-Schmidt law to data from the whole galaxy using the pixel-by-pixel method.
+\caption[Results from fitting the Kennicutt-Schmidt law to M31 data from the whole galaxy]{Results from fitting the Kennicutt-Schmidt law to data from the whole galaxy using the pixel-by-pixel method.
 The colour represents the density of the pixels, increasing from blue to red.
@@
 Applying the SFR laws in these regions provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws such as metallicity, gas mass, stellar mass gradients and changing the ratio of H$_2$ to H\,{\textsc i}.
-
-\subsection{Star formation laws}
+\subsection{Star Formation Laws}
 \label{sec: sfl}
@@
 \includegraphics[width=\textwidth]{../image_paper1/Results_all_3_regs_after_err_co.pdf}
-\caption{Same as Fig.~\ref{fig:ks_all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
+\caption[Results from fitting the Kennicutt-Schmidt law to data from three regions in M31]{Same as Fig.~\ref{fig:ks_all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
 The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$ are shown in red, green and blue, respectively.}%%
@@
         \includegraphics[width=\textwidth]{../image_paper1/es_tot_fuv_vs_tot2_f.png}
-        \caption{The result from fitting the extended Schmidt law on the surface density of SFR(FUV + 24~$\mu$m), the surface density of total gas and the surface density of stellar mass ($z$-axis) from the whole galaxy.
+        \caption[Result from fitting the extended Schmidt law on the M31 data of the whole galaxy]{The result from fitting the extended Schmidt law on the surface density of SFR(FUV + 24~$\mu$m), the surface density of total gas and the surface density of stellar mass ($z$-axis) from the whole galaxy.
 Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method.
@@
 \includegraphics[width=\textwidth]{../image_paper1/color_3d_fuv_tot.png}
-\caption{Fitting result for SFR(FUV + 24~$\mu$m) vs total gas.
+\caption[Result from fitting the extended Schmidt law in three regions in M31]{Fitting result for SFR(FUV + 24~$\mu$m) vs total gas.
 Same as Fig.~\ref{fig:es,all,fuv,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours.
@@
 
-\subsection{The K-S law in M31}
+\subsection{The K-S Law in M31}
 
@@
 
-\subsection{The extended Schmidt law in M31}
+\subsection{The Extended Schmidt Law in M31}
 \label{sec:es_res}
@@
 \includegraphics[width=\textwidth]{../image_paper1/metal_with_errors.png}
-    \caption{Left: the SFR(FUV + 24~$\mu$m) surface density versus gas/dust mass ratio surface density and right: Stellar mass versus gas/dust mass ratio surface density  shows the stellar mass.
+    \caption[The SFR(FUV + 24~$\mu$m) surface density and the stellar mass surface density versus gas/dust mass ratio]{Left: the SFR(FUV + 24~$\mu$m) surface density versus gas/dust mass ratio surface density and right: the stellar mass surface density versus gas/dust mass ratio surface density  shows the stellar mass.
 Each point shows a region with size of $\sim$750~pc.

### 2016-07-18 version0.0/paper3.tex
Completed paper1 and 3

@@
 The purpose of the present work is to use M31 observations to provide new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy,
-as there are few studies on relations between properties of M31 with its PAH features. %generate?!
+as there are few studies on relations between properties of M31 with its PAH features.
 \cite{Cesarsky98} studied PAH spectra observed by ISOCAM spectro-imaging in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6$~$\mu$m emission with enhanced 11.2~$\mu$m emission.
@@
 Those authors re-evaluated the ISOCAM data to compare them to IRS data and found that the earlier results were likely due to incorrect background subtraction.
-%(PB), but the results were inconclusive.
-$$Sr:?
 Using IRAC imaging observations,~\cite{Barmby06} found good agreement between the M31 SFR derived using observed 8~$\mu$m luminosity with other 
@@
 
-We describe the SOM method in $\S$~\ref{sec: method}. 
+We describe the SOM method in $\S$~\ref{sec: method_SOMN}. 
 In $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
@@
 %----------------------------------------------------------------------------------------
-
 \section{Method}
-\label{sec: method}
+\label{sec: method_SOMN}
 \subsection{Choosing an Algorithm}
@@
  The process of creating an SOM happens over a series of $N$ iterations.
- In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,{\mathrm min}}$. 
+ In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,\mathrm{min}}$. 
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
@@
 Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
-~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
+\cite{Geach12} and~\cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
 
@@
 
-\subsection{Mock sample}
+\subsection{Mock Sample}
 \label{sec: mock_sample}
@@
 %----------------------------------------------------------------------------------------
-
 \section{Study Sample}
@@
     \end{subfigure}
-    \caption{Position of the data in M31 (a) and M101 (b).}
+    \caption[Position of the data in M31 and M101]{Position of the data in M31 (a) and M101 (b).}
 \end{figure}
 
-    \subsection{M31 observations}
+    \subsection{M31 Observations}
      \label{Sec: data_M31_SOMN}
@@
      $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
-     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from~\cite{Rahmani16}, and L$_{\mathrm dust}$ and dust mass from~\cite{Draine14}.
+     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_\mathrm{TIR}$) from~\cite{Rahmani16}, and L$_\mathrm{dust}$ and dust mass from~\cite{Draine14}.
 
-    \subsection{M101 observations}
+    \subsection{M101 Observations}
     \label{Sec: data_M101_SOMN}
@@
 
-      \subsection{Preparing data for data mining}
+     \subsection{Preparing Data for Data Mining}
 
@@
     All the PAHs correlate with one another very well.
-    They are also highly correlated with the SPIRE and PACS emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR and metallicity.
+    They are also highly correlated with the SPIRE and PACS emission, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR and metallicity.
     The fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show a weak anti-correlation with RHI.
@@
 
-    \subsection{Clustering M31 Data}%I am not sure about it
+    \subsection{Clustering M31 Data}
 
@@
         %%%Talking about four right regions
-        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to the other regions (fig. 5 in \citealt{Dim15}). 
-        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
+        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH fluxes compared to the other regions (fig.~5 in \citealt{Dim15}). 
         These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
@@
         Since region 10 is located in the bulge of M31 and has high surface brightness for most of the input values, regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
-       % Similarities with regions 3 to 8 in the other input values (e.g. SFR) causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
 
@@
 
-    \subsection{Inside the 2 neuron network}
-
+    \subsection{Inside the Two Neuron Network}
         \label{sec: inside_the_2_neurons}
@@
 
-        \begin{figure*}
+        \begin{figure}
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
-        \caption[Pearson correlation coefficients for data from clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.
+        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.
 }
           \label{fig: cor_cluster1}
-        \end{figure*}
+        \end{figure}
 
@@
         The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
-        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR, or metallicity.
+        Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
         The PAH fluxes correlate with the SPIRE emission, but to a lesser extent than for the data from all regions.
@@
 
-        Correlations between PAH features and SFR, and L$_{\mathrm TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
+        Correlations between PAH features and SFR, and L$_\mathrm{TIR}$ are well-studied~\citep[e.g.][]{Peeters04,Tielens08}. 
         Many groups have used PAH features as a tracer of SFR by finding correlations between 
@@
 Region 6 is located in a FUV-bright region, which breaks the correlations.
-        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_{\mathrm TIR}$) reappear.
+        When we disregard this region, high correlations between 6.2 to 17.0~$\mu$m~PAHs and SFR (and L$_\mathrm{TIR}$) reappear.
 
@@
         We see no correlation between 8/250~$\mu$m luminosity and stellar mass, either in the clustered data or in all 10 regions.
-       % Some studies have indicated that strong stellar emission could lead to destruction of PAHs ~\citep[e.g.][]{Clayton03,Seok14}. %%% These are all UV emission
+
         To test that whether the anti-correlation between stellar mass and PAH emission is the result of the destruction of PAHs in high stellar mass regions, or that high stellar mass obscures PAH emission, we compared PAH abundance with stellar mass for the clustered regions.
@@
 %----------------------------------------------------------------------------------------
- \section{Two dimensional self-Organizing Maps}
+\section{Two-Dimensional Self-Organizing Maps}
  \label{sec: 2d_cluster}
@@
             The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
-the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, H$\alpha$ emission and \sii~ continuum, and so on.
+the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha~emission and \sii~ continuum, and so on.
             \import{../image_paper3/text_files/image_texts/}{col3byall.tex}
@@
             Comparing Fig.~\ref{fig: only_pahs} with other networks show us that PAH features are less variable than other input data.
-            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius. %PB: part of sentence missing?
+            These result is consistent with results from~\cite{Draine14}, who showed that the amount of PAHs in M31 for regions within 20~kpc radius is constant.
             Additional evidence for the PAH features varying significantly less than other parameters is that changing from the PAH single band emission to total PAHs does not affect the networks.
@@
             Although with changing input parameters for each network the distances between neurons and positions of the regions change, the general positions of the regions relative to one another does not change dramatically.
-%PB: changed "data" to "regions" in this sentence - please check.
             Therefore, the networks created by subsets can be used to predict the properties of unobserved quantities in other regions of the galaxy.
-            For example, photometry data, stellar mass, SFR, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, and dust mass are available for most of M31. 
+            For example, photometry data, stellar mass, SFR, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, and dust mass are available for most of M31. 
             The network from Fig.~\ref{fig: wt_pahs} can be applied to 
@@
 
-    \subsection{Testing networks using M101 observations}
+    \subsection{Applying Networks to M101 Observations}
     Another application of self-organizing maps made with data from a single galaxy is to apply its trained networks on data from other galaxies to make predictions.
@@
     Since the neurons in the SOM network created by M31 data already have their finalized weights, the algorithm finds the minimum differences between parameters for each region in M101 and the weights of neurons and introduces the winner neuron in one iteration.
-    %This process is time efficient %PB:sentence incomplete?
 
@@
 %----------------------------------------------------------------------------------------
-\section{SUMMARY}
+\section{Summary}
 \label{sec: summary}
@@
 Since there is very little spatially-resolved PAH spectroscopy for other galaxies from the \Spitzer Space Telescope, increasing the size of samples will require data from the James Webb Space Telescope.
-The method described in this work can be used to select target regions for PAH observations with that facility. %%Eh % better now?
+The method described in this work can be used to select target regions for PAH observations with that facility.
 

### 2016-07-18 version0.0/appendixa.tex
All chapter done

@@
 \myappendices
-As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps.
+As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha\ data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps.
 These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive.
-Making a spatially resolved SFR map of M31 using \halpha emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of \halpha continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.
+Making a spatially resolved SFR map of M31 using \halpha\ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of \halpha\ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha\ filter from the \nii\ 6583~\AA\ line.
 
-The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from \halpha using the scaling factor between fluxes in these two band passes determined by~\citet{Azimlu11}.
-They estimated continuum emission in each \halpha image, using photometric measurements in both \halpha and $R$-band images, and determined the scaling factor.
+The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from \halpha\ using the scaling factor between fluxes in these two band passes determined by~\citet{Azimlu11}.
+They estimated continuum emission in each \halpha\ image, using photometric measurements in both \halpha\ and $R$-band images, and determined the scaling factor.
 These images were observed from a ground-based telescope over two years' time.
@@
 \includegraphics[width=164mm]{../image_paper1/halpha.pdf}
-\caption[Mosaic of H$\alpha$ emission images of M31]{Mosaic created using the Montage programme from six fields of \halpha emission images of M31 from \citet{Massey07}.
+\caption[Mosaic of H$\alpha$ emission images of M31]{Mosaic created using the Montage programme from six fields of \halpha\ emission images of M31 from \citet{Massey07}.
 The resulting image from Montage was continuum-subtracted and masked for all point sources.
@@
 To create the final mosaic, first we removed the background from each region in both the \halpha\ and $R$-band images.
-The second step was to subtract the continuum from the \halpha images.
-Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image.
+The second step was to subtract the continuum from the \halpha\ images.
+Since both \halpha\ and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha\ image.
 At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin\ region in the centre of the galaxy.
@@
 
-Creating the SFR map using \halpha plus 24~$\mu$m was described in Section~\ref{sec:sfr_halpha}.
+Creating the SFR map using \halpha\ plus 24~$\mu$m was described in Section~\ref{sec:sfr_halpha}.
 In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
-The fitting results using SFR(\halpha $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers.
-The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data.
-Thus we did not include the SFR(\halpha $+$ 24~$\mu$m) in our final analysis.
+The fitting results using SFR(\halpha\ $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers.
+The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha\ data.
+Thus we did not include the SFR(\halpha\ $+$ 24~$\mu$m) in our final analysis.
 

### 2016-07-18 version0.0/appendixc.tex
All chapter done

--- 2016-07-15 version0.0/appendixc.tex
@@
-\chapter[Self-Organizing Map for High-redshift galaxies]{Results of Training High-redshift Galaxies for one-dimensional self-organizing maps}
+\chapter[Self-Organizing Map for High-Redshift Galaxies]{Results of Training High-Redshift Galaxies for One-Dimensional Self-Organizing Maps}
 \pagestyle{plain}
@@
 \newpage
-\myappendices{
-As mentioned in Sec.~\ref{sec: 1D}, we changed the size of the SOM from $1\times2$ to $1\times22$.
+\myappendices
+
+As mentioned in Section~\ref{sec: 1D_somz}, we changed the size of the SOM from $1\times2$ to $1\times22$.
 In that section we show some example of the results, here we show the rest of the maps to monitor the changes in the map in various sizes.
@@
     \end{figure}
-    }

### 2016-07-18 version0.0/paper1.tex
All chapter done

@@
 Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands.
-\citet{Kennicutt09} and \citet{Hao11} introduced new SFR calibrations using a combination of \halpha or far-ultraviolet (FUV) and far-infrared (FIR) emission.
+\citet{Kennicutt09} and \citet{Hao11} introduced new SFR calibrations using a combination of \halpha\ or far-ultraviolet (FUV) and far-infrared (FIR) emission.
 In addition to using suitable calibrations for each region, considering the differences between the global and the local ($\sim 0.5-1$~\kpc) cases is important.
@@
 use the FUV image of M31 as observed by the Galaxy Evolution Explorer \citep[GALEX;][]{Martin05}. 
-A second method to calculate the SFR involved using a combination of \halpha and 24~$\mu$m emission.
+A second method to calculate the SFR involved using a combination of \halpha\ and 24~$\mu$m emission.
 \citet{Massey06, Massey07} mapped M31 in broad and narrow bands, including \halpha, as part of the Nearby Galaxies Survey using the KPNO 4-m telescope.
-A detailed description of how our \halpha map was made can be found in Appendix~\ref{app:halpha}.
+A detailed description of how our \halpha\ map was made can be found in Appendix~\ref{app:halpha}.
 
@@
 Adopting a modified \citet{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators.
-Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.
+Changes in the IMF mostly affect the calibration based on \halpha\ luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\odot$.
 
@@
 
-\subsubsection{\halpha plus 24 \um Star Formation Rate}
+\subsubsection{\halpha\ plus 24 \um Star Formation Rate}
 \label{sec:sfr_halpha}
 
-The SFR can also be calculated using a combination of \halpha and \Spitzer  24 \um maps.
-\halpha emission of galaxies is dominated by light emitted from young and massive stars.
+The SFR can also be calculated using a combination of \halpha\ and \Spitzer  24 \um maps.
+\halpha\ emission of galaxies is dominated by light emitted from young and massive stars.
 Star formation timescales traced by this emission are $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}.
-Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}.
-However, \halpha emission is very sensitive to dust extinction.
-Therefore, the combination of the \halpha and 24\um of considered a better choice for calculating the SFR.
+Therefore, \halpha\ alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}.
+However, \halpha\ emission is very sensitive to dust extinction.
+Therefore, the combination of the \halpha\ and 24\um of considered a better choice for calculating the SFR.
 We used a calibration introduced by \citet{Kennicutt09} to measure the SFR:
@@
 \end{equation}
-\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
+\noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha\ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
 L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$.
@@
 Current work&FUV and 24~$\mu$m&0.31 \\
-Current work&\halpha and 24~$\mu$m&0.35 \\
+Current work&\halpha\ and 24~$\mu$m&0.35 \\
 Current work&TIR luminosity&0.4\\
@@
 \citet{Ford13}&TIR luminosity&0.48-0.52\\
-\citet{Azimlu11}& \halpha and 24~$\mu$m&0.34\\
+\citet{Azimlu11}& \halpha\ and 24~$\mu$m&0.34\\
 \citet{Azimlu11}&Extinction-corrected \halpha&0.44\\
@@
 The first row of plots are the surface density of the SFR(TIR), which is calculated using the TIR emission from Section~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$), only atomic gas (H\,{\textsc i}), and total gas from right to left, respectively.
-The only difference between the upper and the other rows is that in the lower rows the SFR indicator is FUV plus 24~$\mu$m (second row), and \halpha plus 24~$\mu$m emission (third row).
+The only difference between the upper and the other rows is that in the lower rows the SFR indicator is FUV plus 24~$\mu$m (second row), and \halpha\ plus 24~$\mu$m emission (third row).
 Fig.~\ref{fig:ks,regs} shows the same data as Fig.~\ref{fig:ks_all}.

### 2016-07-18 version0.0/paper2.tex
Completed paper1 and 3
All chapter done

@@
-\chapter[SOM: classifying high $Z$ galaxies]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
+\chapter[Classifying High-Redshift Galaxies Using Self-Organizing Maps]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
 \label{ch: paper2}
@@
 \section{Introduction}
-\label{sec: intro}
+\label{sec: intro_somz}
 %General information about SEDs
@@
 In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
-%This procedure showed that, not a single type of galaxies in \citetalias{Kinney96} template could describe the SED of any of those 37 galaxies. %PB20160603: repeats previous sentence
 \citetalias{Hossein12} also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.
@@
 In Section $\S$~\ref{sec: data_highZ}, we present the data that we use to train and test our networks. 
-We describe the SOM methods in Section $\S$~\ref{sec: method}. 
+We describe the SOM methods in Section $\S$~\ref{sec: method_somz}. 
 The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
@@
 
- \subsection{Kinney spectral model}
+ \subsection{Kinney Spectral Model}
      \begin{figure}
         \centering
-        \includegraphics[width=\textwidth]{../image_paper2/k96.jpg}
+        \includegraphics[width=0.9\textwidth]{../image_paper2/k96.jpg}
         \caption[\citet{Kinney96} spectra template for 12 types of galaxies]{\citet{Kinney96} spectra template for 12 types of galaxies from \citet{Hossein12} paper (Fig.
@@
 
- \subsection{SED and properties of the sample galaxies} 
+ \subsection{SED and Properties of the Sample Galaxies} 
     \citetalias{Hossein12} selected 142 galaxies from the spectroscopic campaign of the ESO GOODS-South field~\citep{Vanzella05, Vanzella06, Vanzella08}.
@@
    \citetalias{Hossein12} matched the point spread function (PSF) of the photometric data with \citetalias{Kinney96} data and used the photometry as inputs to the Code Investigating GALaxy Emission ({\em CIGALE});~\citep[][hereafter N09]{Noll09} to generate the best-fit SED for each galaxy.
-   % as well as some of the physical properties of the galaxies.
-% PB 20160603: commented out following 3 lines as I don't think this fit well here. Could maybe go somewhere else.    
-%    {\em CIGALE} is a valuable tool to investigate the properties of galaxies using ultraviolet to infrared wavebands.
-%    It uses stellar populations, synthetic attenuation and dust emission models, spectral line templates, and active galactic nuclei optical spectral templates to model the SEDs of galaxies.
-%    This code was successfully tested on data from 39 galaxies selected from the Spitzer Infrared Nearby Galaxy Survey (SINGS;~\citep{Kennicutt03}) by \citetalias{Noll09}.
     \citetalias{Hossein12} produced the best SED match, with wavelength interval of 910~\AA~to $\sim 80$~cm, for each galaxy\footnote{This wavelength interval is the default output of the {\em CIGALE} code}.
@@
     Some of these properties are shown in Table~\ref{tab: props}.
-    In Section~\ref{sec: 1D}, we study these properties for each category.
+    In Section~\ref{sec: 1D_somz}, we study these properties for each category.
     More details on creating SEDs and extracting information about galaxy properties using {\em CIGALE} can be found in \citetalias{Noll09} and \citetalias{Hossein12}.
@@
 %----------------------------------------------------------------------------------------
-
 \section{Method}
-\label{sec: method}
+\label{sec: method_somz}
  \subsection{Self Organizing Maps}
@@
 \subsubsection{Algorithm of SOM} 
- \label{sec: algorithm}
+   \label{sec: algorithm_somz}
+
      Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
@@
 
-\subsection{Creating self-organizing maps}
+\subsection{Creating Self-Organizing Maps}
 \label{sec: create_som}
@@
 
-\subsection{Mock sample}
+\subsection{Mock Sample}
 
@@
 %----------------------------------------------------------------------------------------
-\section{Results and discussion}
+\section{Results and Discussion}
 \label{sec: result}
@@
     We started our analysis by creating 1D SOMs. 
-    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D}).
+    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
     We generate 2D networks (Section~\ref{sec: 2D}),  again starting with the smallest possible number of neurons (4 neurons in a $2\times2$ map), increasing to 144 in a $12\times12$ map.    
@@
 
-    \subsection{One-dimensional self-organizing maps}
-    \label{sec: 1D}
-        \subsubsection{Training the networks}
+    \subsection{One-Dimensional Self-Organizing Maps}
+    \label{sec: 1D_somz}
+        \subsubsection{Training the Networks}
         \label{sec: 1Dt}
@@
             As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
-            As mentioned in Section~\ref{sec: method}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
+            As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
             The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
@@
                     \centering
-                    \includegraphics[width=\textwidth]{../image_paper2/1d/dist_1_by_2.png}
+                    \includegraphics[width=0.8\textwidth]{../image_paper2/1d/dist_1_by_2.png}
                 \end{subfigure}
@@
                 \begin{subfigure}[b]{\textwidth}
-                     \includegraphics[width=\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
+                     \includegraphics[width=0.8\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                 \end{subfigure}
@@
 
-            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
+            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and ~\ref{fig: 1by22T}).
             Since there are more nodes in higher grid SOMs, the  algorithm 
@@
 
-        \subsubsection{Classifying the galaxy sample}
+        \subsubsection{Classifying the Galaxy Sample}
          \label{sec: 1Dv}
@@
 
-        \subsubsection{Properties of the clustered galaxies}
+        \subsubsection{Properties of the Clustered Galaxies}
 
@@
         As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst. 
-       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. 
-        %Considering the results from Fig.~\ref{fig: props}, we can clearly see that s
-        Separating galaxies based on SED types also leads to a separation in properties that derived (via {\sc CIGALE}) from the SEDs, as expected since the SED types are also based on {\sc CIGALE} fitting.
+       Separating galaxies based on SED types also leads to a separation in properties that derived (via {\em CIGALE}) from the SEDs, as expected since the SED types are also based on {\em CIGALE} fitting.
 
-        %Sr07062016: Is it better?
-        {\sc CIGALE} has various models to derive the properties of galaxies.
+        {\em CIGALE} has various models to derive the properties of galaxies.
         Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
@@
         They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
-        Since in the {\sc CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
+        Since in the {\em CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
         They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
@@
 
-    \subsection{Two-dimensional self-organizing maps}
+    \subsection{Two-Dimensional Self-Organizing Maps}
     \label{sec: 2D}
@@
     In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each SED type.
-    As described in Section~\ref{sec: method}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
+    As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
     This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
@@
     Using the {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
-%    The latter case, can be used to identify outliers.
 
     To get the best result from both methods, we should have SOMs with ``enough"  neurons to give any new types of galaxies a chance to find their places in the map.
-    ``Enough  neurons" is a vague statement, but as mentioned in the Section~\ref{sec: method} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
+    ``Enough  neurons" is a vague statement, but as mentioned in the Section~\ref{sec: method_somz} the size of SOMs is arbitrary and depends on the size of the input data and the kind of information needed from the SOMs.
     Since the training dataset (the \citetalias{Kinney96} templates) has 12 members, we assumed a SOM with size of $8\times8$~would be a good start.
@@
 
-    \begin{figure*}
+    \begin{figure}
         \begin{subfigure}[b]{0.45\textwidth}
@@
         \end{subfigure}
-        \caption[$12\times12$ two-dimensional self-organizing map results.]{$12\times12$~2D SOM results.
+        \caption[$12\times12$ two-dimensional self-organizing map results]{$12\times12$~2D SOM results.
 Upper pabel: SOMs trained using the \citet{Kinney96} templates.
@@
         \label{fig: 12by12}
-    \end{figure*}
+    \end{figure}
 
@@
 %----------------------------------------------------------------------------------------
-\section{Summary and future applications}
+\section{Summary and Future Applications}
 \label{sec: summary}

### 2016-07-18 version0.0/asli.tex
Completed intro.
Completed paper1 and 3
All chapter done
Added CV

@@
 \usepackage[byname]{smartref}
-\usepackage{hyperref}%comment out for hardcopy
+\usepackage[draft=false]{hyperref}%comment out for hardcopy
 \usepackage{txfonts}
@@
 \newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
-\newcommand{\halpha}    {H$\alpha $\ }
+\newcommand{\halpha}    {H$\alpha $}
 \newcommand{\um}    {$\mu$m\ }
@@
 \newcommand{\nprime}{N$^\prime$}
+\newcommand \boldit {\textbf{\textit{}}}
 \newcommand{\eqnprime} {N^\prime}
@@
 \newcommand \Galex {GALEX\ }
+\newcommand \GALEX {GALEX\ }
 \newcommand \Herschel {{\it Herschel }}
-\newcommand \sii {[S~{\textsc ii}]} 
-\newcommand \oiii {[O~{\textsc iii}]} 
-\newcommand \hi {H~{\textsc i}}
-\newcommand \hii {H~{\textsc ii}}
-\newcommand \oii {[O~{\textsc ii}]}
-\newcommand \nii {[N~{\textsc ii}]}
+\newcommand \sii {[S~\textsc{ii}]} 
+\newcommand \oiii {[O~\textsc{iii}]} 
+\newcommand \hi {H~\textsc{i}}
+\newcommand \hii {H~\textsc{ii}}
+\newcommand \oii {[O~\textsc{ii}]}
+\newcommand \nii {[N~\textsc{ii}]}
 
@@
 \listoftables\newpage
-\addcontentsline{toc}{chapter}{List of Appendices}
-\listofmyappendices\newpage
+% \addcontentsline{toc}{chapter}{List of Appendices}
+% \listofmyappendices\newpage
 %\addcontentsline{toc}{chapter}{List of Abbreviations, Symbols, and Nomenclature}
@@
 
-% \include{intro0.01}
+\include{intro0.01}
 \include{paper1}
-%\include{paper3}
-%\include{paper2}
-% \include{summary}
+\include{paper3}
+\include{paper2}
+\include{summary}
 
@@
 % %Appendices.
-% \begin{appendices}
-% \include{appendixa}
-% \include{appendixa_2}
-% \include{appendixb}
-% \include{appendixc}
-% \end{appendices}
+ \begin{appendices}
+ \include{appendixa}
+ \include{appendixa_2}
+ \include{appendixb}
+\include{appendixc}
+ \end{appendices}
 
 %CV only relevant stuff... not full CV.
-% \addcontentsline{toc}{chapter}{Curriculum Vitae}
-% \chapter*{Curriculum Vitae}
-% \begin{table}[ht]
-% \begin{tabular}{ll}
-% \textbf{Name:} & \firstname{} \lastname\\\\
-% \textbf{Post-Secondary} & La La School\\
-% \textbf{Education and}& La La Land\\
-% \textbf{Degrees:}& 1996 - 2000 M.A.\\\\
-% & University of Western Ontario\\
-% & London, ON\\
-% & 2008 - 2012 Ph.D.\\\\
-% \textbf{Honours and}& NSERC PGS M\\
-% \textbf{Awards:}& 2006-2007\\\\
-% \textbf{Related Work}& Teaching Assistant\\
-% \textbf{Experience:}& The University of Western Ontario\\
-% & 2008 - 2012\\
-% \end{tabular}
-% \end{table}
-% \subsubsection*{Publications:}
-% La La
+ \addcontentsline{toc}{chapter}{Curriculum Vitae}
+\chapter*{Curriculum Vitae}
+\begin{table}[ht]
+\begin{tabular}{ll}
+\textbf{Name:} & \firstname{} \lastname\\\\
+\textbf{Post-Secondary} & {\sl Doctor of Philosophy,} Astronomy \\
+\textbf{Education and}& Western University\\
+\textbf{Degrees:}& London, ON\\
+& 2012 - 2016\\\\
+&{\sl Master of Science,} Astronomy \\
+& University of Sussex \\
+& Brighton, England\\
+& 2011 - 2012\\\\
+& {\sl Bachelor of Science,} Physics \\
+& Sharif University of Technology \\
+& Tehran, Iran \\
+& 2006 - 2011\\\\
+\textbf{Honours and}& {\sl Western University Graduate Research Scholarship}\\
+\textbf{Awards:}&(2012-2016)\\\\
+& {\sl Travel Grant for Statistical Challenges in Modern Astronomy VI,}\\
+&  Pittsburgh, PA (Spring, 2016)\\\\
+% &{\sl Travel Grant for Canadian Astronomical Society Conference (CASCA),} \\
+% & Winnipeg, MA (Spring, 2016)\\
+&{\sl Scholarship for Utrecht Summer School on Star formation,}\\
+&Utrecht, Netherlands (Summer, 2009)\\\\
+\textbf{Related Work}& Graduate Research \& Teaching Assistant\\
+\textbf{Experience:}& Western University\\
+& 2012 - 2016\\\\
+% & Instructor for Software Carpentry\\
+% & 2015 - 2016\\\\
+&Graduate Research Assistant\\
+& University of Sussex \\
+& 2011 - 2012\\\\
+\end{tabular}
+\end{table}
+
+\subsubsection*{Publications:}
+ \textbf{Rahmani. S}, Lianou. S, Barmby. P, ``{\em Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}'', 2016, MNRAS, 456, 4128\\
+\textbf{Rahmani. S}, Teimoorinia. H, Barmby. P, `` {\em Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}", Submitted to MNRAS, JUNE,2016\\
+
+\subsubsection*{Work in Preparation}
+ \textbf{Rahmani. S}, Teimoorinia. H, Peeters. E, Barmby. P, `` {\em Data Mining in nearby galaxies}", In prep.\\
+
+\subsubsection*{Conferences Talks}
+
+{\sl Canadian Astronomical Society Conference (CASCA), Winnipeg, MA}\hfill(2016)
+\begin{itemize} 
+\item Rahmani, S., Teimoorinia, H., Peeters, E.,  Barmby, P. 2013, ``Data mining in nearby galaxies" 
+\end{itemize}
+
+{\sl International Tusi Conference on Astrophysics, devoted to the Maragha Observatory's 750th year
+anniversary, Maragha, Iran} \hfill(2009)
+\begin{itemize} 
+\item Rahmani, S., Mashhoon, M., Moghaddam , A., ``Challenges of brightness variations of Planets: From Geocentric to Heliocentric" 
+\end{itemize}
+\subsubsection*{Conferences Posters}
+{\sl Statistical challenges in Modern Astronomy {\textsc VI}, Pittsburgh, PA}\hfill(2016)
+\begin{itemize} 
+\item Rahmani, S., Teimoorinia, H., Peeters, E.,  Barmby, P. 2013, ``Data mining in nearby galaxies" 
+\end{itemize}
+
+{\sl From galactic to extra galactic star formation (GESF), Marsseile, France}\hfill (2014)
+\begin{itemize} 
+\item Rahmani, S., Barmby, P. 2013, ``Which Star formation laws in M31?" 
+\end{itemize}
+
+{\sl Canadian Astronomical Society Conference (CASCA), University of British Colombia, BC}\hfill (2013)
+\begin{itemize} 
+\item Rahmani, S., Barmby, P. 2013, ``Effects of Gas Clouds and Existing Stars on Current Star Formation in M31: Testing the Extended Schmidt Law" 
+\end{itemize}
+
 \end{document}

### 2016-07-18 version0.0/paper1.tex
Added CV

@@
 \subsection{Stellar Initial Mass Function}
-\label{sec: imf}
+\label{sec: imf_sfl}
 In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
@@
 \includegraphics[width=\textwidth]{../image_paper1/star.eps}
-\caption[Stellar mass surface density map produced using IRAC 3.6~$\mu$m data]{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ:eskew}.}
+\caption[Stellar mass surface density map produced using IRAC 3.6~$\mu$m data]{The stellar mass surface density map produced using IRAC 3.6~$\mu$m data and the calibration presented in equation~\ref{equ: eskew_sfl}.}
 \label{fig:stellarmass}
@@
 \begin{equation}
-\label{equ:eskew}
+\label{equ: eskew_sfl}
 M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2,
@@
 This calibration is based on the \citet{Salpeter55} IMF.
-Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf}).
-We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ:eskew} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission.
+Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration to the Kroupa IMF (see Section~\ref{sec: imf_sfl}).
+We should note that \citet{Eskew12} gave two calibrations for calculating the stellar mass in their paper: one is equation~\ref{equ: eskew_sfl} which only uses 3.6~\um emission and the other uses both 3.6~\um and 4.5~\um emission.
 We noticed that the second calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass on $\mathrm{F}_{3.6 \mu \mathrm{m}}$ and $\mathrm{F}_{4.5 \mu \mathrm{m}}$, though this was not mentioned in the aforementioned paper.

### 2016-07-18 version0.0/paper2.tex
Added CV

@@
 The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
-In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.
+In Section $\S$~\ref{sec: summary_SOMZ}, we summarize our results and discuss potential future work in this subject.
 %----------------------------------------------------------------------------------------
@@
  \subsection{Self Organizing Maps}
- \label{sec: som}
+ \label{sec: som_SOMZ}
 
@@
      The process of creating SOM happens over a series of $N$ iterations. 
-     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj_SOMZ}). 
       In each iteration, the SOM code:
@@
         \begin{equation}
-            \label{equ: weight adj}
+            \label{equ: weight adj_SOMZ}
             w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
@@
 In this sample, the 27 galaxies are clustered in 4 groups, containing 8, 7, 6 and 6 galaxies respectively.}
-            \label{fig: sample}
+            \label{fig: sample_SOMZ}
         \end{figure}
@@
 
- Fig. ~\ref{fig: sample} shows the SOM of this mock sample. 
+ Fig. ~\ref{fig: sample_SOMZ} shows the SOM of this mock sample. 
  The upper panel is the distance map. 
  The axes show the position of the neurons in the $10 \times 10$ network.
- The lower panel in Fig.~\ref{fig: sample} shows the hit map.
+ The lower panel in Fig.~\ref{fig: sample_SOMZ} shows the hit map.
  On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
@@
 Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
-The upper panel in the Fig.~\ref{fig: sample} clearly shows this division.
+The upper panel in the Fig.~\ref{fig: sample_SOMZ} clearly shows this division.
 In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to low star forming galaxies.
@@
 Different shades of gray show the border between regions.
-The lower panel in Fig.~\ref{fig: sample} shows that only 4 neurons (out of 100) are occupied. 
+The lower panel in Fig.~\ref{fig: sample_SOMZ} shows that only 4 neurons (out of 100) are occupied. 
 8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
@@
             Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
-            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
+            As in to Fig.~\ref{fig: sample_SOMZ}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
             As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
@@
                 \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid.
-As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map.
+As in Fig.~\ref{fig: sample_SOMZ}, the upper panel is a distance map and the lower panel is a hit map.
 In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts.
@@
 \section{Summary and Future Applications}
-\label{sec: summary}
+\label{sec: summary_SOMZ}
 

### 2016-07-18 version0.0/asli.tex
Compeleted

@@
 
-\newcommand{\makeacknowlege} { 1) Pauline
-2) Els, Sophia, Hossein,
-3)I would like to thank all my Friends in Western.
-Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam(s) , Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
-4) bacheha
-5) western ppl; Jodi, Brian, Henry, Phin,...
-6) Mohad, shahin, pejman, pouria, masood,babak
-7) fako famil
+\newcommand{\makeacknowlege} {
+
+This is the first or second page to be read, but the last one written. 
+I will try to thank all the people that helped me to start studying Astronomy, and gave me courage to continuing this process.
+My most gratitude goes to my awesome supervisor, Prof. Pauline Barmby, for all the support, during the last four years.
+The amount I learned from her, her knowledge and superb physical intuition is incalculable.
+She is truly one of the best supervisors in the world.
+
+I also would like to thank you all my collaborators Prof.
+E.
+Peeters, Dr.
+S.
+Lianue, and Dr.
+H.
+Teimoorinia for not only helping me on forwarding my projects, but also thought me how a good scientist works.
+Thank you to Dr. D. Stock and Dr. M. Azimlue for all their helps and comments
+
+I would like to thank all my fellow graduate students in Western University; Aycha, Beth, Boshra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
+You guys are amazing; you helped me whenever I needed, and I had so much fun hanging out with you.
+Thank you Western Physics and Astronomy department staff, especially Clara Buma, Brian Davis, Jodi Guthrie, Henry Leparskas, and Phin Perquin for helping me with problems an international student can have.
+
+I always consider myself a lucky person because of my amazing teachers and friends.
+I am particularly grateful to my astronomy teachers, Shahin, Mohadesseh, Pejman, Pouria, Masoud and Babak, the first group of people who showed me the wonders of the universe
+
+My dearest friend, Nazanin P., my thanks goes to you and your family.
+During our 18 years of friendship you always encouraged me and be there for me If I needed anything. 
+Your help when I was applying for graduate school and when I moved to Canada, was priceless. You are the loveliest family in the world.
+Matin, Sogol, Mercedeh, Alireza, Farhad and Ardeshir thank you for always finding a way to remind me my dreams when I was too busy or too tiered to continue.
+
+Last but not least, I want to thank my family. 
+My father, who thought me to learn from my  mistakes and do not repeat them again.
+My mother, who is always available to talk to me and make me feel better. 
+Setareh, who I hope that she knows that I am here in this stage of my life all because of her believe in me.
+Seti, "aroosakam", my little secret keeper, whom I trust by all my heart.
+Mehdi, the greatest brother (in-law) in the world.
+And Radvin and Ronika for being my main source of happiness during these years.
+Love you.
+I would also like to thank, my grandmother, uncles, aunts and cousins for always having my back.
+
 }

### 2016-07-22 version0.0/appendixa.tex
Submitted version

@@
-\chapter{SFR from H$\alpha$ Plus 24 \um: Procedure and Result}
+\chapter{SFR from H$\alpha$ Plus 24~$\mu$m: Procedure and Result}
 \pagestyle{plain}
@@
 \myappendices
+
 As mentioned in Section~\ref{sec: data_sfl}, we used the \halpha\ data from the Nearby Galaxies Survey~\citep{Massey07} to create one of our SFR maps.

### 2016-07-22 version0.0/asli.tex
Submitted version

--- 2016-07-18 version0.0/asli.tex
@@
 
-\newcommand{\makeacknowlege} { 1) Pauline
-2) Els, Sophia, Hossein,
-3)I would like to thank all my Friends in Western.
-Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam(s) , Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
-4) bacheha
-5) western ppl; Jodi, Brian, Henry, Phin,...
-6) Mohad, shahin, pejman, pouria, masood,babak
-7) fako famil
+\newcommand{\makeacknowlege} { 
+This is the first or second page to be read of this thesis, but the last one written.
+I will try to thank all the people that helped me during studies, and gave me courage to continuing this process.
+My most gratitude goes to my awesome supervisor, Prof. Pauline Barmby, for all the support during the last four years;
+the amount I've learned from her, her knowledge and superb physical intuition is incalculable.
+She is truly one of the best supervisors in the world.
+
+I also would like to thank all my collaborators Prof.
+E.
+Peeters, Dr.
+S.
+Lianue, and Dr.
+H.
+Teimoorinia for not only helping me on moving my projects forward, but also for teaching me how a good scientist work.
+Thank you to Dr. D. Stock and Dr. M. Azimlu for all your useful comments.
+
+I would like to thank all my fellow graduate students in Western University: Alex, Aycha, Beth, Boshra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
+You guys are amazing; you helped me whenever I needed, and I had so much fun hanging out with you.
+Thank you Western Physics and Astronomy department staff, especially Clara Buma, Brian Davis, Jodi Guthrie, Henry Leparskas, and Phin Perquin for helping me with the problems an international student can have.
+
+My dearest friend, Nazanin P., my thanks goes to you and your family.
+During our 18 years of friendship you always encouraged me and was there for me whenever I needed anything.
+Your help when I was applying for graduate school and when I moved to Canada, was priceless. You are the loveliest family in the world.
+Matin, Sogol, Mercedeh, Alireza, Farhad and Ardeshir thank you for always finding a way to remind me my dreams when I was too busy or too tiered to continue.
+
+Last but not least, I want to thank my family.
+My father, who thought me to learn from my mistakes and not to repeat them.
+My mother, who is always available to talk to and make me feel better.
+Setareh, who I hope she knows that I am here in this stage of my life all because of her believing in me.
+Seti, "aroosakam", my little secret-keeper, whom I trust by all my heart.
+Mehdi, the greatest brother (in-law) in the world.
+And Radvin and Ronika for being my main source of happiness during these years.
+Love you.
+
 }
@@
 \vfill
-\textbf{Keywords:} Nearby galaxies: M31, M101, Star formation rate, stellar mass, ISM, data mining
+\textbf{Keywords:} galaxies: individual: M31, M101, galaxies: high-redshift, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, techniques: image processing
 \newpage

### 2016-07-22 version0.0/intro0.01.tex
Submitted version

@@
 It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
-Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see ][for more detail]{Walcher08}.
+Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see][for more detail]{Walcher08}.
 For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
@@
 \begin{center}
-\begin{tabular}{ c c}
+\begin{tabular}{ c}
 \hline\hline
-Combined luminosities$^1$ & references\\
+Combined luminosities$^1$ \\
 \hline
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)& \cite{Hao11}\\
-L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)& \cite{Hao11}\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)& \cite{Hao11}\\
-L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)& \cite{Hao11}\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)& \cite{Kennicutt09}\\
-L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)& \cite{Kennicutt09}\\
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 0.46L(TIR)$^2$\\
+L(FUV)$_{\rm corr}$=L(FUV)$_{\rm obs}$ + 3.89L(24~$\mu$m)$^2$\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 0.27L(TIR)$^2$\\
+L(NUV)$_{\rm corr}$=L(NUV)$_{\rm obs}$ + 2.26L(24~$\mu$m)$^2$\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.0024L(TIR)$^3$\\
+L(\halpha)$_{\rm corr}$=L(\halpha)$_{\rm obs}$ + 0.020L(24~$\mu$m)$^3$\\
 \hline
@@
 \item $^1$ Luminosities are in the form of L($\lambda$) = $\lambda$ L$_{\lambda}$ in erg~s$^{-1}$ 
+\item $^2$ Calibrated by~\cite{Hao11}
+\item $^3$ Calibrated by~\cite{Kennicutt09}
 \end{tablenotes}

### 2016-07-22 version0.0/paper1.tex
Submitted version

@@
 However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications.
-There are many studies on correlation of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Lilly13}.
+There are many studies on correlation of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Dib11b, Lilly13}.
 These studies suggest that metallicity has a critical role in the formation of H$_2$ gas.
@@
 It should be noted that the above two correlations are only valid in the global case.
-However, \citet{Leroy08} showed that the SFR as measured by combining far-UV and 24$\mu$m emission does not change with changing metallicity.
+However, \citet{Leroy08} showed that the SFR as measured by combining far-UV and 24~$\mu$m emission does not change with changing metallicity.
 \citet{Roychowdhury15} argued that in nearby spiral galaxies effect of metallicity on the SFR calculation is smaller than the calibration errors and can be ignored.
@@
 In order to investigate star formation laws, the first step is to calculate the SFR.
-Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11, Kennicutt12, Calzetti13}.
 \citet{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.][]{Bruzual93}.
@@
 \end{equation}
-\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$.
+\noindent where SFR is in M$_{\odot}$~yr$^{-1}$, and L(24~$\mu$m) and L(FUV)$_{\mathrm obs}$ are in erg~s$^{-1}$.
 L(FUV)$_{\mathrm obs}$ is the luminosity of the galaxy in the FUV.
@@
 \noindent where L(H${\alpha}$)$_{\mathrm obs}$ is the observed \halpha\ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
-L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$.
+L(24~$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}~$yr$^{-1}$.
 It was indicated that the formulation above can only be used for the global situation, i.e., the total SFR.
@@
 \begin{tablenotes}
-\item Similar to Table~\ref{table:res} but here the fitting is performed on regions with a size of 750~pc, and we only show the results from SFR(FUV+24$\mu$m).
+\item Similar to Table~\ref{table:res} but here the fitting is performed on regions with a size of 750~pc, and we only show the results from SFR(FUV+24~$\mu$m).
 \end{tablenotes}
@@
 Our results suggest that changing the gas tracer has a more significant impact on the determination of the power law index than changing the SFR tracers.
-Therefore, we only discuss the results from SFR(FUV+24$\mu$m), and in Table~\ref{table:res750} we only show results from this SFR map.
+Therefore, we only discuss the results from SFR(FUV+24~$\mu$m), and in Table~\ref{table:res750} we only show results from this SFR map.
 

### 2016-08-29 version0.0/asli.tex
Applying P.W.'s comments on introduction

@@
 \newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
-\newcommand{\halpha}    {H$\alpha $}
+\newcommand{\halpha}    {H$\alpha\ $}
 \newcommand{\um}    {$\mu$m\ }
@@
 
-The Andromeda galaxy (M31) is the nearest large spiral galaxy, and Therefore, high resolution images of this galaxy are available.
+The Andromeda galaxy (M31) is the nearest large spiral galaxy, and therefore, high resolution images of this galaxy are available.
 These images provide data from various regions with different physical properties.
-Star formation rate and gas mass surface densities of M31have been measured using three different methods, and have been used to compare different star formation laws over the whole galaxy and in spatially-resolved regions.
+Star formation rate and gas mass surface densities of M31 have been measured using three different methods, and have been used to compare different star formation laws over the whole galaxy and in spatially-resolved regions.
 Using hierarchical Bayesian regression analysis, I conclude that there is a correlation between surface density of star formation and the stellar mass surface density.
@@
 
-To study the effect of other properties a galaxy on the star formation rate, I utilize an unsupervised data mining method (specifically the self-organizing map) on measurements of both nearby and high-redshift galaxies.
+To study the effect of other properties of a galaxy on the star formation rate, I utilize an unsupervised data mining method (specifically the self-organizing map) on measurements of both nearby and high-redshift galaxies.
 Both observed data and derived quantities (e.g. star formation rate, stellar mass) of star-forming regions in M31 and the nearby spiral galaxy M101 are used as inputs to the self-organizing map.
@@
 % &{\sl Travel Grant for Canadian Astronomical Society Conference (CASCA),} \\
-% & Winnipeg, MA (Spring, 2016)\\
+% & Winnipeg, MB (Spring, 2016)\\
 &{\sl Scholarship for Utrecht Summer School on Star formation,}\\
@@
 
-{\sl Canadian Astronomical Society Conference (CASCA), Winnipeg, MA}\hfill(2016)
+{\sl Canadian Astronomical Society Conference (CASCA), Winnipeg, MB}\hfill(2016)
 \begin{itemize} 

### 2016-08-29 version0.0/intro0.01.tex
Applying P.W.'s comments on introduction

@@
 Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
-Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
+Therefore, by properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
 
@@
 The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
-Furthermore, in order to completely understand the formation and evolution of galaxies from early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary. 
+Furthermore, in order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary.
 As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.
@@
 This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
-The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
+The gas and dust in the ISM are heated by interstellar radiation field and cooled through a variety of line and continuum processes which usually depend on the local physical conditions. 
 The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
@@
 Molecular clouds in the ISM are cold ($T \sim10$ K) and dense (particle number density $ 50<n<500$ cm$^{-3}$); masses of molecular clouds range from a few to millions of solar masses~\citep{Bolato08}.
-Density in molecular clouds is not uniform. There are dense and colds clumps inside these clouds.
+Density in molecular clouds is not uniform. There are dense and cold clumps inside these clouds.
 Since these clumps are ideal places to form stars, studying molecular clouds has an important role in understanding formation of stars.
@@
 The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
-Observation of the \hi atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.
+Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.
 
@@
 The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
-Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}.
+Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
 Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
@@
 %PB: need to fix text in {\bf} earlier in this sentence.
-Most of our knowledge of molecular clouds come from observation of line emission of CO molecules, which, die to their large mass, possess a very low energy rotational state (the state of angular momentum, J) and can be excited in the temperature of molecular clouds.
+Most of our knowledge of molecular clouds come from observation of line emission of CO molecules, which, due to their large mass, possess a very low energy rotational state (the state of angular momentum, J) and can be excited in the temperature of molecular clouds.
 %Sr should I put the \bf back?
@@
  \label{equ: vir}
- M_{cloud} = L_{\rm CO} \sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}},
+ M_{cloud} = \frac{L_{\rm CO}}{T_{\rm CO}} \sqrt{\frac{4\rho}{3\pi G }},
 \end{equation}
-where $\rho$ is the mass density of the cloud and $\sqrt{\frac{4\rho}{3\pi G T_{\rm CO}}}$ is called the conversion factor.
+where $\rho$ is the mass density of the cloud and $\frac{1}{T_{\rm CO}}\sqrt{\frac{4\rho}{3\pi G}}$ is called the conversion factor.
 Equ.~\ref{equ: vir} shows that the total mass of molecular clouds and the CO luminosity of the cloud are directly related~\citep{Young91}. 
@@
 where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
-These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
+These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi~is detectable in most spiral galaxies and some elliptical galaxies).
 Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.
@@
 \cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
-The Herschel Space Telescope \cite{Pilbratt10} has measured the continuum dust emission from hundreds of galaxies\citep{Eales10, Oliver12}. 
+The Herschel Space Telescope~\citep{Pilbratt10} has measured the continuum dust emission from hundreds of galaxies~\citep{Eales10, Oliver12}. 
 This amount of observational data provides a unique opportunity to study the ISM of galaxies using dust emission. 
@@
 \end{equation}
-where c is a constant which depends on photometric system that is being used.
+where $c$ is a constant which depends on photometric system that is being used.
 Optical depth, $\tau_{\lambda}$, is defined by ratio of observed and initial intensity of a source as:
@@
 There is a large number of review papers on how stars form and how their formation is traced. 
-From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
-From an observational standpoint, star formation is discussed by \cite[][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.
+From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\cite{McKee07}. 
+From an observational standpoint, star formation is discussed by many authers \citep[e.g.][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.
 
@@
 Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
-Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}
+Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}.
 Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
@@
 Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
-Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
+Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\ \cite{Kroupa01}:
 \begin{equation}
@@
 This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
-The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
+The relation between the SFR, the luminosity of the \halpha\ emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
 \begin{align}
@@
 Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
-The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
-by adding L(24~$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
+The effects of dust must be measured and \halpha\ observations must be corrected for extinction (e.g.
+by adding lumincity at 24~$\mu$m (L(24~$\mu$m)) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
 
 Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727~\AA. 
-Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
-As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
-\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
+Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha\ emission. 
+As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha\ luminosity. 
+\cite{Gallagher89} calibrated the SFR based on the \oii~luminosity by using a sample of 75 galaxies. 
 Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
@@
 Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
-In these galaxies, the \halpha emission line is redshifted out of the optical band.
+In these galaxies, the \halpha\ emission line is redshifted out of the optical band.
 Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.
@@
 The IR luminosity of a system depends not only on the amount of embedded dust, but also on the heating rate provided by the stars. 
-Since young stars heat the dust to higher mean temperatures than old stellar populations, to the first order, the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
-The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
+Since young stars heat the dust to higher mean temperatures than old stellar populations, to first order, the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
+The fact that the heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
 Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.
@@
 
-The emission from dust heated by young stars changes by the amount of high energy photon emitted toward the dust and by the properties of the dust such as the grain size.
+The emission from dust heated by young stars changes by the amount of high energy photons emitted toward the dust and by the properties of the dust such as the grain size.
 Therefore, calibration of SFR varies for each of the single-band IR emissions.
-Assuming that dust heating is dominated by emission from young stars stellar, integrating over the full wavelength range of the infrared part of the spectrum reveals the total infrared (TIR) emission of the system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
+Assuming that dust heating is dominated by emission from young stars, integrating over the full wavelength range of the infrared part of the spectrum reveals the total infrared (TIR) emission of the system, which can be used as an SFR indicator~\citep{Kennicutt98b}.
 
@@
 \label{equ: halphaplus24}
-SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24)]
+SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24 \mu m)]
 \end{equation}
@@
 
-The IR emission in the other band can be used for correcting dust effect on UV or \halpha~emission (see Table~\ref{table3}). 
+The IR emission in the other band can be used for correcting dust effect on UV or \halpha emission (see Table~\ref{table3}). 
 The corrected emission then can be used as a SFR tracer.
@@
 Therefore, many studies have tried to make a map of stellar mass distribution using this bandpass within galaxies~\citep[e.g.,][]{Elmgreen84}.
-Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps to have a more accurate calibration.
+Thanks to the \Spitzer~\citep{Wener04} and WISE~\citep{Wright10} space telescopes, a large amount of data in these bands from many regions in the sky is available, which helps to give a more accurate calibration.
 Fluxes from 3.6 and 4.5~$\mu$m are suitable for calibration of the stellar mass, due to fact that these two band-passes not only trace evolved stellar population but are also almost insensitive to the emission from young stellar population and to dust absorption and emission.
@@
 \end{equation}
-where M$_{\star}$ is the stellar mass in solar masses, and $L = \lambda L_{\lambda}$ is luminosity in erg~s$^{-1}$~\AA$^{-1}$.
+where M$_{\star}$ is the stellar mass in solar masses, and $L = \nu L_{\nu}$ is luminosity in erg~s$^{-1}$~\AA$^{-1}$.
 Equ.s in~\ref{equ: zhu1} were derived from a large sample of galaxies and tested on different types of regions and galaxies.

### 2016-08-29 version0.0/paper1.tex
Applying P.W's Comments on chapter2

@@
 We used the dust map with SPIRE 350 resolution, convolved and re-gridded  to have the same resolution and pixel size for the H\,{\textsc i} map, then divided this dust mass by the mass of hydrogen in M31.
-However, in a private correspondence with the author, Draine pointed out that based on the Planck observations of Milky Way dust \citet{Tauber10}, the dust mass surface density map estimated for M31 by \citet{Draine14} may be systematically high by a factor of 2.
+However, in a private correspondence with the author, Draine pointed out that based on the Planck observations of Milky Way dust \citep{Tauber10}, the dust mass surface density map estimated for M31 by \citet{Draine14} may be systematically high by a factor of 2.
 We divided our dust map by 2 to account for this correction.
@@
 In one of the most recent works on M31, \citet{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares fitting method.
-To make a meaningful comparison between our results and the results reported in \citet{Ford13}, we averaged the power-law indices in \citet{Ford13} with a certain annuli and compared to the results with the same annuli in ours.
+To make a meaningful comparison between our results and the results reported in \citet{Ford13}, we averaged the power-law indices in \citet{Ford13} by a certain annuli and compared to the results with the same annuli in ours.
 We calculated power-law indices to be in the case of the H$_{2}$-only gas $N \sim 0.35, 0.58, 0.68$ and in case of total gas, $N \sim 1.37, 2.05, 1.60$ for $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R < 25\kpc$, respectively.

### 2016-08-29 version0.0/paper3.tex
Applying P.W.'s comments on ch. 3

@@
 The K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}.
-For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into the desired number of clusters.
+For K-means algorithms, the user must define the number of clusters and for and SOM algorithms the user defines the number of neurons, and the algorithms decide how to separate the data into clusters.
 In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
@@
  This neuron is the winner node and is calling Best Matching Unit (BMU). 
- In each iteration (t),The weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+ In each iteration (t), the weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
   \begin{equation}
@@
      Users must decide the size of the network based on their data set and their usage of the results.
-     There has been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
+     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
      We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$.
@@
 Their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
-In Fig.~\ref{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
+In Fig.~\refthere ha{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
 The left part of the plot is where regions with low SFR belong and the right side is for high SFR regions.

### 2016-08-29 version0.0/paper2.tex
Submitted version
Applying P.W.'s comments on ch.4

@@
                 \begin{subfigure}[b]{\textwidth}
-                     \includegraphics[width=0.8\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
+                    \centering \includegraphics[width=0.8\textwidth]{../image_paper2/1d/hit_t_1_by_2.png}
                 \end{subfigure}
@@
             Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
-            In these plots we force the galaxies to be categorize in a maximum 3 groups. 
+            In these plots we force the galaxies to be categorized in a maximum 3 groups. 
             If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
@@
             Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
-            The lower left panel shows the average SED of the 80 galaxies that were classified as early type 
+            The lower left panel shows the average SED of the 80 galaxies that were classified as early type. 
             These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
@@
         \caption[$12\times12$ two-dimensional self-organizing map results]{$12\times12$~2D SOM results.
-Upper pabel: SOMs trained using the \citet{Kinney96} templates.
+Upper panel: SOMs trained using the \citet{Kinney96} templates.
 For training 2D SOMs two different approaches were considered: either only 12 types of galaxies exist (left) or not (right).

### 2016-08-29 version0.0/intro0.01.tex
Applying M.D.'s comments on the intro.

@@
 % stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
-Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
+Inside every galaxy, there are billions of stars, planets, and black holes, as well as dust and gas.
 They all affect each others' formation, evolution, and extinction.
 There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
-Nearly all the information we can obtain from galaxies other than our own comes from their light.
+Nearly all the information we can obtain from galaxies other than our own comes from their electromagnetic radiation.
 Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
@@
 Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
-Therefore, by properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
+Therefore, with proper modeling of observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
 
@@
 The energy of the anti-parallel mode is slightly less than the parallel mode.
-Since atoms always want to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
+Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
 However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
@@
 Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
-In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
+In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically proven that they have a power-law size distribution.
 The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
@@
 Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
-\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
+\cite{Salpeter55} empirically described the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
 He introduced a power-law IMF $\Phi$  in the form:
@@
 \begin{equation}
-SFR(YSO) = N_{yso} <M>/\tau 
+\m {SFR}(YSO) = N_{yso} <M>/\tau 
 \end{equation}

### 2016-08-30 version0.0/intro0.01.tex
Applying R.A.'s comments on the intro

@@
 Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
-a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
+a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool for understanding galaxies. 
 Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
 Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
-Therefore, with proper modeling of observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
+Therefore, by properly modeling of observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
 
@@
 The study of the formation and evolution of the Sun, and more generally that of stars, helps us understand more about our origin and the future of our Solar System.
-Furthermore, in order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, the knowledge of the formation and evolution of stars is necessary.
+Furthermore, in order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, knowledge of the formation and evolution of stars is necessary. 
 As a result, the study of stellar formation and evolution has been a central topic in astronomy and astrophysics for decades.
@@
 For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
-By integrating star formation history over a specific time scale, SFR can be derived.
+By integrating instantaneous star formation over a specific time scale, SFR can be derived.
 Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.
@@
 The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
-Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
+Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
 Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}

### 2016-08-30 version0.0/asli.tex
Switching the method sections in ch3 and ch4.

@@
 Both observed data and derived quantities (e.g. star formation rate, stellar mass) of star-forming regions in M31 and the nearby spiral galaxy M101 are used as inputs to the self-organizing map.
-Clustering the M31 regions in the feature space reveals some (anti)-correlations between the properties the galaxy, which are not apparent when considering data from all regions in the galaxy. 
+Clustering the M31 regions in the feature space reveals some (anti)-correlations between the properties of the galaxy, which are not apparent when considering data from all regions in the galaxy. 
 The self-organizing map can be used to predict star formation rates for spatially-resolved regions in galaxies using other properties of those regions.

### 2016-08-30 version0.0/paper2.tex
Switching the method sections in ch3 and ch4.

@@
  \label{sec: som_SOMZ}
+  The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features~\citep{Kohonen98}. 
+ The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
+ Each neuron has a fixed position in the map and may contain one or more samples from the input data in a n-dimensional space,~\boldit{V} $\in \Re^n$.
+ A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
+ The process of creating an SOM happens over a series of $N$ iterations.
+ In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,\mathrm{min}}$. 
+ This neuron is the winner node and is calling Best Matching Unit (BMU). 
+ In each iteration (t), the weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+  \begin{equation}
+            \label{equ: weight adj}
+            W(t+1)=W(t)+L(t) \times R(t) \times(V(t)-W(t))
+ \end{equation}
+where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor with $L_0$ is the initial value of learning, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
+$\tau$ is the number of total iterations.
+Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
+\cite{Geach12} and~\cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
 
- The self-organizing map is a clustering method which reduces the dimension of the data, usually to one or two dimensions (1D or 2D), while preserving topological features of the original dataset.
- The result of an SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
- Each node may contain one or more samples from the input data.
- The distance between the nodes represents similarity or dissimilarity of the underlying samples, i.e., similar data are closer together in the array and the distance between two nodes is related to the dissimilarity of their samples.
- A weight vector ``\boldit{W}" with the same dimension as the input data is associated with each node and will be varied during the training process.
- This vector is the key factor in determining the position of the nodes in a map.
- \cite{Geach12} presented the application of the SOM and discussed its algorithm in detail.
- In this section we briefly discuss the algorithm of SOM, how we create our maps and a present a  test model which will help interpretation of our results.
+     In order to create self-organizing maps, we used the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library, which works in two phases, the ``ordering phase" and ``tuning phase" . 
+     Phase one is the ``ordering phase". 
+     This phase starts with maximum neighbourhood distance, and an initial high learning factor, usually 0.9, which is provided by the user. 
+     The ordering phase continues for the requested number of iterations.
+     At the end of the iterations, the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user. 
+     The second phase is the ``tuning phase".
+     In this phase the neighbourhood distance is at its minimum, but the learning factor decreases very slowly.
+     This minimum neighbourhood distance and slowly decreasing learning factor helps to fine tune the topology results and causes a more stable SOM. 
+     The number of iterations in this tuning phase must be much greater than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
+     We chose the number of epochs in the tuning phase to be 3 times more than the number of epochs in the ordering phase.
 
-\subsubsection{Algorithm of SOM} 
-   \label{sec: algorithm_somz}
+     To present our results, we use \textsc{nnt}'s built-in plotting tool.
+     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
+     In the maps, the purple hexagonal shapes show the neurons. 
+     The distances are shown by the grey-scale colours: the darker the colour, the larger the distance between neurons.
+     Neurons with zero hits are left empty.
+     In Section~\ref{sec: mock_sample} we used \textsc{newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
 
-     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
-     We start by creating S1 $\times$ S2 empty neurons. 
-     The initial arrangement of these neurons depends on the map's topology provided by the user.
-     In the case of 1D maps, since each neuron has two immediate neighbours, the topology of the map does not have any effect on the final result and any topology can be chosen.
-     However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
-     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
-     Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
-     The process of creating SOM happens over a series of $N$ iterations. 
-     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj_SOMZ}). 
-      In each iteration, the SOM code:
-     \begin{enumerate}
-        \item chooses a random vector from the dataset ($V_i$).
-        \item calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
-This neuron is the winner node and is called the Best Matching Unit (BMU).
-        \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius.
-The weight vectors of these nodes will be affected in the next steps.
-The radius of the neighbourhood is arbitrary and can be set to be as high as half of the SOM size.
-It then decays exponentially over each iteration as
-        \begin{equation}
-            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
-        \end{equation}
-        where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$.
-$r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively.
-        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
-        \begin{equation}
-            \label{equ: weight adj_SOMZ}
-            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
-        \end{equation}
-        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
-$R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
-     \end{enumerate}
-     These steps are then repeated $N$ times.
+     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
+     Users must decide the size of the network based on their data set and their usage of the results.
+     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
+     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$.
+     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
 
-\subsection{Creating Self-Organizing Maps}
-\label{sec: create_som}
-     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+% \subsection{Mock Sample}
 
-     SOM in {\sc nnt} can be created by {\sc newsom} or {\sc selforgmap} library, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
-     The first phase is called the ``ordering phase" and
-     starts with maximum neighbourhood distance and an initial high learning factor (usually 0.9) is provided by the user. 
-     The ordering phase continues for a requested number of iterations.
-     During the iterations, the learning factor decreases to the tuning phase learning factor and the neighbourhood distance reaches that of the tuning phase as well.
-     Both the learning factor and the neighbourhood of the tuning phase are set by the user. 
-     The amount by which these two factors change in each iteration depends on the number of iterations.
-
-     In the second, or ``tuning'' phase,
-     the neighbourhood distance is kept at the user-defined minimum.
-     The learning factor, however, decreases gradually.
-     The gradual change in the leaning factor helps to fine-tune the topology results, leading to a more stable SOM. 
-     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase.
-     We chose the number of epochs in the tuning phase to be 3 times the number of epochs in the ordering phase.
-
-     To present our results, we use {\sc nnt}'s built-in plotting tool.
-     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
-     In the maps, the purple hexagonal shapes represent the neurons. 
-     The distances in a distance map are shown by the grey cycle colours:
-     the darker the colour, the larger the distance between neurons.
-     In the hit maps, neurons with zero hits are left empty.
-
-    The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
-    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
-
-\subsection{Mock Sample}
-
-         \begin{figure}
-            \begin{subfigure}[b]{0.5\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{../image_paper2/sample/sample2_dist.png}
-            \end{subfigure}
-            \hfill
-            \begin{subfigure}[b]{0.5\textwidth}
-                \includegraphics[width=\textwidth]{../image_paper2/sample/sample2_hits.png}
-            \end{subfigure}
-            \caption[Self-organizing map of the mock sample]{SOM of the mock sample.
+%          \begin{figure}
+%             \begin{subfigure}[b]{0.5\textwidth}
+%                 \centering
+%                 \includegraphics[width=\textwidth]{../image_paper2/sample/sample2_dist.png}
+%             \end{subfigure}
+%             \hfill
+%             \begin{subfigure}[b]{0.5\textwidth}
+%                 \includegraphics[width=\textwidth]{../image_paper2/sample/sample2_hits.png}
+%             \end{subfigure}
+%             \caption[Self-organizing map of the mock sample]{SOM of the mock sample.
 In both plots, the axes show the position of the neurons.
@@
 In this sample, the 27 galaxies are clustered in 4 groups, containing 8, 7, 6 and 6 galaxies respectively.}
-            \label{fig: sample_SOMZ}
-        \end{figure}
+%             \label{fig: sample_SOMZ}
+%         \end{figure}
 
- To illustrate how self-organizing maps work, we create a mock sample of 27 galaxies.
- The mock sample contains two attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). 
- We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Section~\ref{sec: create_som}.
+%  To illustrate how self-organizing maps work, we create a mock sample of 27 galaxies.
+%  The mock sample contains two attributes for each galaxy: the type (type 1 or type 2), and the star formation rate (high or low). 
+%  We generated a SOM of size $10 \times 10$ using the same initial values mentioned in Section~\ref{sec: create_som}.
 
- Fig. ~\ref{fig: sample_SOMZ} shows the SOM of this mock sample. 
- The upper panel is the distance map. 
- The axes show the position of the neurons in the $10 \times 10$ network.
- The lower panel in Fig.~\ref{fig: sample_SOMZ} shows the hit map.
- On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
- The number on the purple neurons shows the number of galaxies in that neuron.
- Colour coverage of neurons depends on the number of the hits on the sample.
- The neuron with the maximum number of hits is dark-coloured while the empty neurons are left uncoloured (white).
+%  Fig. ~\ref{fig: sample_SOMZ} shows the SOM of this mock sample. 
+%  The upper panel is the distance map. 
+%  The axes show the position of the neurons in the $10 \times 10$ network.
+%  The lower panel in Fig.~\ref{fig: sample_SOMZ} shows the hit map.
+%  On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
+%  The number on the purple neurons shows the number of galaxies in that neuron.
+%  Colour coverage of neurons depends on the number of the hits on the sample.
+%  The neuron with the maximum number of hits is dark-coloured while the empty neurons are left uncoloured (white).
 
-Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
-The upper panel in the Fig.~\ref{fig: sample_SOMZ} clearly shows this division.
-In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to low star forming galaxies.
-The left half of the plot is where type 1 galaxies belong, and type 2 galaxies reside in the right side.
-Different shades of gray show the border between regions.
-The lower panel in Fig.~\ref{fig: sample_SOMZ} shows that only 4 neurons (out of 100) are occupied. 
-8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
-We can conclude that although each galaxy had  the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributes, they remained only in four groups.
-This network is considered a training network and can be used to cluster any new dataset with similar entries.
+% Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
+% The upper panel in the Fig.~\ref{fig: sample_SOMZ} clearly shows this division.
+% In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to low star forming galaxies.
+% The left half of the plot is where type 1 galaxies belong, and type 2 galaxies reside in the right side.
+% Different shades of gray show the border between regions.
+% The lower panel in Fig.~\ref{fig: sample_SOMZ} shows that only 4 neurons (out of 100) are occupied. 
+% 8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
+% We can conclude that although each galaxy had  the chance to occupy any of the neurons in the network, because of the similarity in the values of their attributes, they remained only in four groups.
+% This network is considered a training network and can be used to cluster any new dataset with similar entries.
 
-As we show in the following sections, with data from real galaxies there are more than two dimensions and two galaxies never have exactly the same information. 
-If the network has enough neurons, the input data points would eventually separate from each other and cluster into smaller groups. 
-However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
-Therefore, it is up to the users to decide the similarity or dissimilarity between the input data based on number of neurons.
+% As we show in the following sections, with data from real galaxies there are more than two dimensions and two galaxies never have exactly the same information. 
+% If the network has enough neurons, the input data points would eventually separate from each other and cluster into smaller groups. 
+% However, if the input data has high similarity, the number of neurons must be much higher than the number of input samples to be able to separate the groups from each other. 
+% Therefore, it is up to the users to decide the similarity or dissimilarity between the input data based on number of neurons.
 

### 2016-08-30 version0.0/paper3.tex
Switching the method sections in ch3 and ch4.

@@
 Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein14,Hossein16}.
-ANNs are designed to work in the same way that the neurons work in a human brain.
+ANNs are spiered to work in the same way that the neurons work in a human brain.
 These are networks of interconnected neurons (nodes), in which all of the connections are weighted.
@@
 
- \subsection{Self Organizing Maps}
- \label{sec: som}
- The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features~\citep{Kohonen98}. 
- The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
- Each neuron has a fixed position in the map and may contain one or more samples from the input data in a n-dimensional space,~\boldit{V} $\in \Re^n$.
- A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
- The process of creating an SOM happens over a series of $N$ iterations.
- In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,\mathrm{min}}$. 
- This neuron is the winner node and is calling Best Matching Unit (BMU). 
- In each iteration (t), the weight vectors W(t) in the neighbourhood of the BMU ($r^t_{BMU}$) will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
+    \subsubsection{Algorithm of SOM} 
+   \label{sec: algorithm_somz}
+    The self-organizing map is a clustering method which reduces the dimension of the data, usually to one or two dimensions (1D or 2D), while preserving topological features of the original dataset.
+    The result of an SOM is a set of nodes (neurons) that are arranged in a 1D or 2D arrays \citep{Kohonen98}. 
+    Each node may contain one or more samples from the input data.
+    The distance between the nodes represents similarity or dissimilarity of the underlying samples, i.e., similar data are closer together in the array and the distance between two nodes is related to the dissimilarity of their samples.
+    A weight vector ``\boldit{W}" with the same dimension as the input data is associated with each node and will be varied during the training process.
+    This vector is the key factor in determining the position of the nodes in a map.
+    \cite{Geach12} presented the application of the SOM and discussed its algorithm in detail.
+    In this section we briefly discuss the algorithm of SOM, how we create our maps and a present a  test model which will help interpretation of our results.
+
+     Assume we have a dataset which contains vectors, \boldit{V} $\in \Re^n$, and we want to map them on an S1 by S2 map. 
+     We start by creating S1 $\times$ S2 empty neurons. 
+     The initial arrangement of these neurons depends on the map's topology provided by the user.
+     In the case of 1D maps, since each neuron has two immediate neighbours, the topology of the map does not have any effect on the final result and any topology can be chosen.
+     However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
+     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
+     Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
+     The process of creating SOM happens over a series of $N$ iterations. 
+     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj_SOMZ}). 
+      In each iteration, the SOM code:
+     \begin{enumerate}
+        \item chooses a random vector from the dataset ($V_i$).
+        \item calculates the Euclidean distance for each node, $j$, as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with minimum $D_j$, (``$D_{j_{min}}$").
+This neuron is the winner node and is called the Best Matching Unit (BMU).
+        \item  computes the radius of the neighbourhood of the BMU to find nodes within this radius.
+The weight vectors of these nodes will be affected in the next steps.
+The radius of the neighbourhood is arbitrary and can be set to be as high as half of the SOM size.
+It then decays exponentially over each iteration as
         \begin{equation}
-            \label{equ: weight adj}
-            W(t+1)=W(t)+L(t) \times R(t) \times(V(t)-W(t))
+            r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
         \end{equation}
-where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor with $L_0$ is the initial value of learning, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change.
-$\tau$ is the number of total iterations.
-Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
-\cite{Geach12} and~\cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
+        where $\tau$ is a decay constant and is usually set to be the same as the number of iterations, $N$.
+$r^0_{BMU}$ and $r^t_{BMU}$ are the radii of the neighbourhood at 0th and $t$th iteration, respectively.
+        \item changes the weight vectors of the BMU and all the nodes within $r^t_{BMU}$ as:
+        \begin{equation}
+            \label{equ: weight adj_SOMZ}
+            w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
+        \end{equation}
+        where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate.
+$R(t)$ determines how the weight of each node in the neighbourhood of BMU will change.
+     \end{enumerate}
+     These steps are then repeated $N$ times.
 
-     In order to create self-organizing maps, we used the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library, which works in two phases, the ``ordering phase" and ``tuning phase" . 
-     Phase one is the ``ordering phase". 
-     This phase starts with maximum neighbourhood distance, and an initial high learning factor, usually 0.9, which is provided by the user. 
-     The ordering phase continues for the requested number of iterations.
-     At the end of the iterations, the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user. 
-     The second phase is the ``tuning phase".
-     In this phase the neighbourhood distance is at its minimum, but the learning factor decreases very slowly.
-     This minimum neighbourhood distance and slowly decreasing learning factor helps to fine tune the topology results and causes a more stable SOM. 
-     The number of iterations in this tuning phase must be much greater than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
-     We chose the number of epochs in the tuning phase to be 3 times more than the number of epochs in the ordering phase.
+\subsection{Creating Self-Organizing Maps}
+\label{sec: create_som}
+     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
 
-     To present our results, we use \textsc{nnt}'s built-in plotting tool.
-     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
-     In the maps, the purple hexagonal shapes show the neurons. 
-     The distances are shown by the grey-scale colours: the darker the colour, the larger the distance between neurons.
-     Neurons with zero hits are left empty.
-     In Section~\ref{sec: mock_sample} we used \textsc{newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
+     SOM in {\sc nnt} can be created by {\sc newsom} or {\sc selforgmap} library, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
+     The first phase is called the ``ordering phase" and
+     starts with maximum neighbourhood distance and an initial high learning factor (usually 0.9) is provided by the user. 
+     The ordering phase continues for a requested number of iterations.
+     During the iterations, the learning factor decreases to the tuning phase learning factor and the neighbourhood distance reaches that of the tuning phase as well.
+     Both the learning factor and the neighbourhood of the tuning phase are set by the user. 
+     The amount by which these two factors change in each iteration depends on the number of iterations.
 
-     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
-     Users must decide the size of the network based on their data set and their usage of the results.
-     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
-     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$.
-     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
+     In the second, or ``tuning'' phase,
+     the neighbourhood distance is kept at the user-defined minimum.
+     The learning factor, however, decreases gradually.
+     The gradual change in the leaning factor helps to fine-tune the topology results, leading to a more stable SOM. 
+     To allow the fine tuning, the number of iterations in this phase must be much larger than the that of the ordering phase.
+     We chose the number of epochs in the tuning phase to be 3 times the number of epochs in the ordering phase.
 
+     To present our results, we use {\sc nnt}'s built-in plotting tool.
+     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
+     In the maps, the purple hexagonal shapes represent the neurons. 
+     The distances in a distance map are shown by the grey cycle colours:
+     the darker the colour, the larger the distance between neurons.
+     In the hit maps, neurons with zero hits are left empty.
+
+    The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
+    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
 \subsection{Mock Sample}
@@
 either 0 or 1 for low or high SFR, and 0 or 0.5 for a low or high amount of dust. 
- We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Section~\ref{sec: som}.
+ We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Section~\ref{sec: method_SOMN}.
  Fig.~\ref{fig: sample} shows the SOM of the mock sample. 

### 2016-08-30 version0.0/paper2.tex
Applying R.A's comments on the ch3.

@@
 Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
-\cite{Geach12} and~\cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.
+\cite{Geach12} demonstrate the algorithm of the SOM in more detail.
 
@@
             Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
-            As in to Fig.~\ref{fig: sample_SOMZ}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
+            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
             As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
@@
                 \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid.
-As in Fig.~\ref{fig: sample_SOMZ}, the upper panel is a distance map and the lower panel is a hit map.
+As in Fig.~\ref{fig: sample}, the upper panel is a distance map and the lower panel is a hit map.
 In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts.

### 2016-08-30 version0.0/paper3.tex
Applying R.A's comments on the ch3.

@@
 Since the 1990s, many studies have utilized SOMs for object classification and clustering (e.g.
-classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b}.
+classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16}.
 
@@
      However, in 2D maps, the shape of the neurons specifies the number of immediate neighbours for each neuron and it is up to user to choose the most suitable shape based on the data.
-     In this paper, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
+     In this chapter, we choose hexagonal topology, which gives each neuron six neighbours, and provides more interactions between neurons.
      Initially a random weight vector, \boldit{W} $\in \Re^n$, will be assigned to each node.
@@
 
-     To present our results, we use {\sc nnt}'s built-in plotting tool.
-     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
-     In the maps, the purple hexagonal shapes represent the neurons. 
-     The distances in a distance map are shown by the grey cycle colours:
-     the darker the colour, the larger the distance between neurons.
-     In the hit maps, neurons with zero hits are left empty.
+     To present our results, we use \textsc{nnt}'s built-in plotting tool.
+     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
+     In the maps, the purple hexagonal shapes show the neurons. 
+     The distances are shown by the grey-scale colours: the darker the colour, the larger the distance between neurons.
+     Neurons with zero hits are left empty.
+     In Section~\ref{sec: mock_sample} we used \textsc{newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
 
@@
     \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
+
 \subsection{Mock Sample}
@@
      Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
-     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
+     Metallicity for all regions except regions 5 and 8 were adapted from~\citep{Sanders12} and for regions 5 and 8, \cite{Dim15} estimated metallicity from the radial metallicity profile.
+     \cite{Dim15} also measured radiation hardness index (RHI) using calibration of the ratio of two lines, $\left (\log \frac{[Ne~\textsc{iii}]}{[Ne~\textsc{ii}]} + \left [ 0.71 + 1.58\log\frac{[S~\textsc{iV}]}{[S~\textsc{iii}]} \right ] \right )/2$, for these 10 regions.
      We used the measured PAH feature fluxes, metallicity and RHI of each region as the input for self-organizing maps.
@@
         The SOM shows that this region has completely different input values from the others: most of the values for region 10 are much higher than for the other regions, which is the main reason for its isolation.
-        Region 8 occupies the right-most neuron in this network, suggesting that this region has the most differences from region 10.
+        Region 8 occupies the left-most neuron in this network, suggesting that this region has the most differences from region 10.
 
@@
         \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
-        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.
-}
+        \caption[Pearson correlation coefficients for data from the clustered regions in M31]{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}.}
           \label{fig: cor_cluster1}
@@
     Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
+    In Fig.~\ref{fig: all_derived_ones}, all the regions except regions 4 and 7 are surrounded by white colours.
+    This indicates that all the immediate neighbours for neurons occupied with each region have similar properties as the occupied ones, except for regions 4 and 7.
+    These two regions are sitting in very close regions and their smallest dissimilarity causes the changes in distances between their neighbours.
     \import{../image_paper3/text_files/image_texts/}{all.tex}
@@
     Considering the position of these two regions in M31 (both right on the edge of the star forming rings in the galaxy), similarity of these two regions was predictable.
-    The position of region 3 on the SOM is close to the position of regions 4 and 7, but with a darker colour between the nodes. 
+    The position of region 3 on the SOM is relatively close to the position of regions 4 and 7, but with a darker colour between the nodes. 
     In Fig.~\ref{fig: regions in m31} it is clear that this region in M31 is physically closer to regions 4 and 7 than to any other region, but it is on the outer side of the star forming ring.
@@
              \import{../image_paper3/text_files/image_texts/}{PAHS_or_not_PAHs.tex}
-            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of regions in those networks are the same.
+            Comparing the SOM from all data in Fig.~\ref{fig: all_derived_ones} with the SOMs in Fig.~\ref{fig: PAHS_or_not_PAHs} shows that the general position of almost all regions in those networks are the same.
             Region 10 is in one corner of all three networks.
@@
             these data from another region in M31.
-            By comparing the position of the new region with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.
+            By comparing the position of the new region (with the same spatial size of these 10 regions) with respect to our original 10 regions in the network, one would have an estimate for total PAHs in the new region without having any observational data for it.
 

### 2016-08-30 version0.0/paper2.tex
Applying R.A's comments on the ch.4

@@
 
-     In order to create self-organizing maps, we used the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
-     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library, which works in two phases, the ``ordering phase" and ``tuning phase" . 
-     Phase one is the ``ordering phase". 
-     This phase starts with maximum neighbourhood distance, and an initial high learning factor, usually 0.9, which is provided by the user. 
-     The ordering phase continues for the requested number of iterations.
-     At the end of the iterations, the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user. 
-     The second phase is the ``tuning phase".
-     In this phase the neighbourhood distance is at its minimum, but the learning factor decreases very slowly.
-     This minimum neighbourhood distance and slowly decreasing learning factor helps to fine tune the topology results and causes a more stable SOM. 
-     The number of iterations in this tuning phase must be much greater than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
-     We chose the number of epochs in the tuning phase to be 3 times more than the number of epochs in the ordering phase.
-
-     To present our results, we use \textsc{nnt}'s built-in plotting tool.
-     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
-     In the maps, the purple hexagonal shapes show the neurons. 
-     The distances are shown by the grey-scale colours: the darker the colour, the larger the distance between neurons.
-     Neurons with zero hits are left empty.
-     In Section~\ref{sec: mock_sample} we used \textsc{newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.
+     The same as Chapter~\ref{ch: paper3}, we use the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox} to create self-organizing maps.
+     To present our results in this chapter, we use {\sc nnt}'s built-in plotting tool.
+     Specifically, we use two of the plots in this tool: a hits map, which shows the number of times each neuron has became the winner (hits), and a distance map, which shows the distance between those neurons.
+     In the maps, the purple hexagonal shapes represent the neurons. 
+     The distances in a distance map are shown by the grey cycle colours:
+     the darker the colour, the larger the distance between neurons.
+     In the hit maps, neurons with zero hits are left empty.
 
@@
      Users must decide the size of the network based on their data set and their usage of the results.
-     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
+     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are well established. 
      We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$.
@@
 In this sample, the 27 galaxies are clustered in 4 groups, containing 8, 7, 6 and 6 galaxies respectively.}
-%             \label{fig: sample_SOMZ}
+%             \label{fig: sample}
 %         \end{figure}
@@
 
-%  Fig. ~\ref{fig: sample_SOMZ} shows the SOM of this mock sample. 
+%  Fig. ~\ref{fig: sample} shows the SOM of this mock sample. 
 %  The upper panel is the distance map. 
 %  The axes show the position of the neurons in the $10 \times 10$ network.
-%  The lower panel in Fig.~\ref{fig: sample_SOMZ} shows the hit map.
+%  The lower panel in Fig.~\ref{fig: sample} shows the hit map.
 %  On this map, similar to the distance map, the axes show the position of the neurons and the hexagonal shapes are the neurons.
@@
 % Using this method, as expected, we are able to divide the mock sample galaxies into 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
-% The upper panel in the Fig.~\ref{fig: sample_SOMZ} clearly shows this division.
+% The upper panel in the Fig.~\ref{fig: sample} clearly shows this division.
 % In that plot, the upper half belongs to high star forming galaxies, while the lower half belongs to low star forming galaxies.
@@
 % Different shades of gray show the border between regions.
-% The lower panel in Fig.~\ref{fig: sample_SOMZ} shows that only 4 neurons (out of 100) are occupied. 
+% The lower panel in Fig.~\ref{fig: sample} shows that only 4 neurons (out of 100) are occupied. 
 % 8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
@@
             Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
-            The lower left panel shows the average SED of the 80 galaxies that were classified as early type. 
+            The lower left panel shows the median SED of the 80 galaxies that were classified as early type. 
             These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
@@
             The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
-            The average SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
+            The median SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
             \begin{figure}
@@
 In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies.
-Lower panel: Average SED of the galaxies in each group, early-type on the left and starburst on the right.}
+Lower panel: median SED of the galaxies in each group, early-type on the left and starburst on the right.}
                 \label{fig: 1by2V}
@@
                 \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times22$~networks]{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
-In the average SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones.
+In the median SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones.
 The 4000\AA~ break weakens from left to right and the emission line strengths increase.}
@@
 
-            The lower panels present the average SED of the galaxies in each neuron.
+            The lower panels present the median SED of the galaxies in each neuron.
             Since galaxies had more space to separate, some of the neurons are left empty.
-            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.
+            Thus, instead of having 22 median SED plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.
 
@@
             If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
-            Otherwise, we can conclude that the SEDs of galaxies in the cluster are similar to two of the \citetalias{Kinney96} templates.
+            Otherwise, we can conclude that the SEDs of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates.
             For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.
@@
             There are 3 galaxies in the third neuron, similar to the S0 type. 
-            18 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
-            There is one Sb type galaxy and 15 galaxies with SEDs similar to both Sa and Sb type galaxies.
+            19 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 6 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
+            There are 8 Sb type galaxy and 19 galaxies with SEDs similar to both Sa and Sb type galaxies.
             The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
             In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
-            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and the SEDs of the 14 galaxies in the ninth neuron are similar to the SB6 galaxies.
+            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and the SEDs of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
             The far right neurons in the network belong to galaxies with SED comparable to types SB1 and SB2.
@@
 
-        In order to compare our classifications with previous works, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
+        In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
         In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
@@
     As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
-    This quality of the SOMs provides a unique opportunity to analyse 2D networks in two approaches. 
+    This quality of the SOMs provides a unique opportunity to analyse 2D networks using two approaches. 
     At first, as in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 templates in Fig.~\ref{fig: k96}.
@@
     In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
-    This approach can be used to trace and recognize the outliers.
-    To execute the second approach, we used the {\tiny selforgmap} library in {\tiny MATLAB}.
-    Using the {\tiny selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
+    This approach can be used to trace and recognize the outliers, which could include galaxy types that are not presented in the \citetalias{Kinney96} templates.
+    To execute the second approach, we used the {\textsc selforgmap} library in the {\textsc matlab}.
+    Unlike the {\textsc newsom} library which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameters), in the {\textsc selforgmap} we can change this value.
+    Using the {\textsc selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
 
@@
 
+Two-dimensional networks can be used to find the relations of the neurons and classifications in more details.
+The sample galaxies have more freedom to be categorized, and only 23 of them occupies exactly the same neurons as \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
+Additionally, by using two-dimensional networks we showed that we do not have nay outlier in the sample galaxies.
+
 \addcontentsline{toc}{section}{Bibliography}

### 2016-08-30 version0.0/paper3.tex
Applying R.A's comments on the ch.4

@@
 \label{sec: create_som}
-     In order to create SOMs, we use {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
+     In order to create SOMs, we use the {\sc matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
 
-     SOM in {\sc nnt} can be created by {\sc newsom} or {\sc selforgmap} library, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
+     SOM in {\sc nnt} can be created by using the {\sc newsom} or {\sc selforgmap} libraries, both of which work in two phases, an ``ordering phase" and a ``tuning phase". 
      The first phase is called the ``ordering phase" and

### 2016-08-30 version0.0/intro0.01.tex
Applying part of Sarah's comments on ch4

@@
 This is why the H${\alpha}$ emission line strength is greater in optically thick environments.
-The relation between the SFR, the luminosity of the \halpha\ emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
+The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
 \begin{align}
@@
 Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
-The effects of dust must be measured and \halpha\ observations must be corrected for extinction (e.g.
+The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
 by adding lumincity at 24~$\mu$m (L(24~$\mu$m)) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
@@
 Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727~\AA. 
-Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha\ emission. 
-As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha\ luminosity. 
+Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
+As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
 \cite{Gallagher89} calibrated the SFR based on the \oii~luminosity by using a sample of 75 galaxies. 
@@
 Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
-In these galaxies, the \halpha\ emission line is redshifted out of the optical band.
+In these galaxies, the \halpha emission line is redshifted out of the optical band.
 Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.

### 2016-08-30 version0.0/paper1.tex
Applying part of Sarah's comments on ch4

@@
 A second method to calculate the SFR involved using a combination of \halpha\ and 24~$\mu$m emission.
-\citet{Massey06, Massey07} mapped M31 in broad and narrow bands, including \halpha, as part of the Nearby Galaxies Survey using the KPNO 4-m telescope.
+\citet{Massey06, Massey07} mapped M31 in broad and narrow bands, including \halphadot, as part of the Nearby Galaxies Survey using the KPNO 4-m telescope.
 A detailed description of how our \halpha\ map was made can be found in Appendix~\ref{app:halpha}.

### 2016-08-30 version0.0/paper2.tex
Applying part of Sarah's comments on ch4

@@
 %What \citetalias{Hossein12} did
-~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified SEDs of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
-With the supervised method, they could only classify SED of 105 out of the 142 galaxies.
-The SED of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
+~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified spectral types of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
+With the supervised method, they could only classify spectral types of 105 out of the 142 galaxies.
+The spectra of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
 In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
@@
 Our hypothesis was that since a self-organizing map has the freedom to classify objects in between known classes, it could be applied to this data 
-to find the best SED class for the 37 galaxies that could not be classified by the supervised method.
+to find the best spectral class for the 37 galaxies that could not be classified by the supervised method.
 First, we train self-organizing maps using the \citetalias{Kinney96} spectral templates and compare our classification with the \citetalias{Kinney96} classification.
-Then, we use the trained network to classify the SEDs of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
+Then, we use the trained network to classify the spectra of 142 galaxies with $0.5 < z < 1$ from \citetalias{Hossein12}. 
 As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
@@
 We describe the SOM methods in Section $\S$~\ref{sec: method_somz}. 
-The results of the SED classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
+The results of the spectral classifications and a comparison with previous studies are presented in Section $\S$~\ref{sec: result}. 
 In Section $\S$~\ref{sec: summary_SOMZ}, we summarize our results and discuss potential future work in this subject.
@@
 \label{sec: data_highZ}
-We use SED templates from \citetalias{Kinney96} to train neural networks.
+We use spectra templates from \citetalias{Kinney96} to train neural networks.
 To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12}.
-Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in SED clustering, but also to easily compare supervised and unsupervised methods.
+Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in spectra clustering, but also to easily compare supervised and unsupervised methods.
 
@@
 The type of each template is shown in each frame.
-Plots B, E, S0, Sa, Sb and SC show spectra that belong to the early types galaxies.
+Plots B, E, S0, Sa, Sb and SC show spectra that belong to the quiescent galaxies.
 Starburst galaxies spectra are indicated with SB 1 to 6.
@@
 
-    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of SEDs.
+    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of spectra templates.
     These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
-    \citetalias{Kinney96} stated that these templates can also be used to classify the SED of high-redshift galaxies.
+    \citetalias{Kinney96} stated that these templates can also be used to classify the spectra of high-redshift galaxies.
 
-    The 12 templates are divided based on their morphological types for early type galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
+    The 12 templates are divided based on their morphological types for quiescent galaxies or their extinction for starburst galaxies (Fig.~\ref{fig: k96}). 
     The quiescent group of galaxies includes Bulge (B), Elliptical (E), S0, Sa, Sb, and Sc galaxies.
@@
     As Fig.~\ref{fig: k96} shows, SB1 galaxies have lower internal extinctions ($E(B-V) \simeq 0.05$), while SB6 galaxies have the highest amount of extinction ($E(B-V) \simeq 0.65$) among starburst galaxies.
-    In the early type (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
-    SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the early types and show strong emission lines.
+    In the quiescent (B to Sb) templates, the spectrum is redder; strong absorption lines and the 4000~\AA~break are distinguishable.
+    SEDs of starburst galaxies are flatter in the optical and near-infrared region than those of the quiescent ones and show strong emission lines.
     For more details on each spectral type, we encourage readers to see \citetalias{Kinney96} and references therein. 
@@
     These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength in a wide range of wavelengths.
-    Since we have used the \citetalias{Hossein12} SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} templates.
+    Since we have used the \citetalias{Hossein12} SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} spectral templates.
 
@@
             In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
-            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flattter SED compare to other quiescent galaxies.
+            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flattter spectra compare to other quiescent galaxies.
 
@@
             Based on the colours between these two groups, we conclude that they are very similar; both groups are starbursting and have strong emission lines.
-            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the SED to become flatter at shorter wavelengths. 
-            The flatter UV SED makes these two templates more similar to quiescent galaxies than to other starbursts.
-            Therefore, in the networks, SB5 and SB6 types are to be grouped close to the early type galaxy templates.
+            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the spectra to become flatter at shorter wavelengths. 
+            The flatter UV spectra makes these two templates more similar to quiescent galaxies than to other starbursts.
+            Therefore, in the networks, SB5 and SB6 types are to be grouped close to the quiescent galaxy templates.
 
@@
             pays more attention to small differences between groups.
-            If the templates from \citetalias{Kinney96} had completely distinct SEDs, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
+            If the templates from \citetalias{Kinney96} had completely distinct spectral types, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
             However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
@@
             The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
-            This template has the most extinction and its SED has more similarity to early type galaxies than other starburst types.
+            This template has the most extinction and its spectra has more similarity to quiescent galaxies than other starburst types.
 
@@
             The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
-            Eighty of the galaxies have SEDs similar to those of the early type galaxies and the SEDs of the rest are similar to the starburst galaxies.
-            The lower left panel shows the median SED of the 80 galaxies that were classified as early type. 
+            Eighty of the galaxies have spectral types similar to those of the quiescent galaxies and the spectral types of the rest are similar to the starburst galaxies.
+            The lower left panel shows the median spectra of the 80 galaxies that were classified as quiescent. 
             These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
-            the SEDs clearly show the 4000\AA~break, one of the signatures of early type galaxies.
-            The H$\alpha$ emission in the spectrum could be from galaxies with similar SEDs to Sa galaxies, but with stronger emission lines.
-            The median SED in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
+            the spectra clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
+            The H$\alpha$ emission in the spectrum could be from galaxies with similar spectral types to Sa galaxies, but with stronger emission lines.
+            The median spectra in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
             \begin{figure}
@@
 Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group.
-In this case 80 means that 80 of the 142 SEDs are classified into the early type group while the 62 of the 142 SEDs are categorized as starburst galaxies.
-Lower panel: median SED of the galaxies in each group, early-type on the left and starburst on the right.}
+In this case 80 means that 80 of the 142 spectra are classified into the quiescent group while the 62 of the 142 spectra are categorized as starburst galaxies.
+Lower panel: median spectra of the galaxies in each group, early-type on the left and starburst on the right.}
                 \label{fig: 1by2V}
@@
 
-            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's SED predominantly decides which group the galaxy belongs to.
-            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as early type.
+            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectra predominantly decides which group the galaxy belongs to.
+            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
             Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.
 
-            Fig.~\ref{fig: 1by3V} presents the result of classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to the early type group, and 47 belong to the starburst group.
+            Fig.~\ref{fig: 1by3V} presents the result of classifying the spectra of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to the quiescent group, and 47 belong to the starburst group.
             However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
-            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the early type galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).
+            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the quiescent galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).
 
@@
                 \caption[Classification of fitted galaxy SEDs from \citet{Hossein12} using the $1\times22$~networks]{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies.
-In the median SED of each neuron, we can clearly see the changes from early type galaxies to the starburst ones.
+In the median spectra of each neuron, we can clearly see the changes from quiescent galaxies to the starburst ones.
 The 4000\AA~ break weakens from left to right and the emission line strengths increase.}
@@
 
-            The lower panels present the median SED of the galaxies in each neuron.
+            The lower panels present the median spectra of the galaxies in each neuron.
             Since galaxies had more space to separate, some of the neurons are left empty.
-            Thus, instead of having 22 median SED plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.
+            Thus, instead of having 22 median spectral plots in the lower part of Fig.~\ref{fig: 1by22V}, there are only 12.
 
             Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
-            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that SEDs of galaxies in the cluster are very similar to those of the template.
-            Otherwise, we can conclude that the SEDs of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates.
+            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that spectra of galaxies in the cluster are very similar to those of the template.
+            Otherwise, we can conclude that the spectra of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates.
             For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.
@@
             The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
-            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with SEDs similar to that of type B or E.
+            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with spectral type similar to that of type B or E.
             There are 3 galaxies in the third neuron, similar to the S0 type. 
-            19 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 6 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
-            There are 8 Sb type galaxy and 19 galaxies with SEDs similar to both Sa and Sb type galaxies.
-            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
+            19 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 6 galaxies in the fourth neurons have spectral type similar to both S0 and Sa galaxies.
+            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
+            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.
             In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
-            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies, and the SEDs of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
-            The far right neurons in the network belong to galaxies with SED comparable to types SB1 and SB2.
+            Therefore, 24 galaxies in the eighth neurons have similar spectra to Sb type galaxies, and the spectra of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
+            The far right neurons in the network belong to galaxies with spectra comparable to types SB1 and SB2.
 
@@
 
-            With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of SEDs is limited to models and the results are always reported with uncertainties.
+            With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
             However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
-            Therefore, if the SED of galaxies do not match completely with any of the model SEDs in Fig.~\ref{fig: k96}, they can be categorized as a SED with similarity to two or more of the groups.
+            Therefore, if the spectra of galaxies do not match completely with any of the spectra templates in Fig.~\ref{fig: k96}, they can be categorized as a spectra with similarity to two or more of the groups.
 
@@
 %        
-        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from early type galaxies to starburst. 
-       Separating galaxies based on SED types also leads to a separation in properties that derived (via {\em CIGALE}) from the SEDs, as expected since the SED types are also based on {\em CIGALE} fitting.
+        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst. 
+       Separating galaxies based on spectral types also leads to a separation in properties that derived (via {\em CIGALE}) from the spectra, as expected since the spectra types are also based on {\em CIGALE} fitting.
 
@@
 The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies.
-The other colours depend on how much they are close to red or blue show that the galaxies are early type or starburst.}
+The other colours depend on how much they are close to red or blue show that the galaxies are quiescent or starburst.}
         \label{fig: props_vs_props}
@@
         The colours show the galaxy types, where B type galaxies are shown with red and SB1 types are shown with blue.
-        The redder the colour, the more similarity with early type galaxies, while the purple to blue colours show more similarity to starburst galaxies.
+        The redder the colour, the more similarity with quiescent galaxies, while the purple to blue colours show more similarity to starburst galaxies.
         Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
-        The purple point in the middle of the blue points in  Fig.~\ref{fig: props_vs_props} corresponds to galaxies with SEDs similar to type Sc: the shape of their SED indicates that they are old galaxies with high sSFR.
+        The purple point in the middle of the blue points in  Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.
 
@@
         Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
-        From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their SED type.
+        From older to younger galaxies, the colour of the points changes from red to blue, which shows a good correlation with their spectral type.
         %for more details discussion on these correlations, we encourage readers to read \citetalias{Noll09} and \citetalias{Hossein12}.
@@
         They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
-        They found that for early type galaxies (E, S0 and S0/a ), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
+        They found that for quiescent galaxies (E, S0 and S0/a ), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$ ) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
        Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
@@
         Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
-        Whether this dependence is real or not, our results here show that using self-organizing maps can separate SEDs of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
+        Whether this dependence is real or not, our results here show that using self-organizing maps can separate spectra of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
 
@@
     \label{sec: 2D}
-    The one-dimensional networks are great tools to categorize the SEDs and monitor the changes of properties of galaxies with category.
+    The one-dimensional networks are great tools to categorize the spectral types of galaxies and monitor the changes of properties of galaxies with category.
     However, each neuron in these networks is limited to be connected to one other neuron in each direction.
-    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each SED type.
+    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each spectral type.
     As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
     This quality of the SOMs provides a unique opportunity to analyse 2D networks using two approaches. 
-    At first, as in the 1D SOMs, we assumed that all the galaxies must have SEDs similar to any of the 12 templates in Fig.~\ref{fig: k96}.
-    In this case, we can categorize SEDs of other galaxies based on those 12 types.
+    At first, as in the 1D SOMs, we assumed that all the galaxies must have spectra similar to any of the 12 templates in Fig.~\ref{fig: k96}.
+    In this case, we can categorize spectra of other galaxies based on those 12 types.
     In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
@@
     The upper left panel in Fig.~\ref{fig: 12by12} shows the SOM results from the first approach. 
-    Since we considered that SEDs of all galaxies can be categorized using the \citetalias{Kinney96} templates, the galaxies were placed all over the map.
-    Using this network to categorize any set of SEDs forced the SEDs to be either in the same neurons as the \citetalias{Kinney96} templates or in the neurons between them.
+    Since we considered that spectra of all galaxies can be categorized using the \citetalias{Kinney96} templates, the galaxies were placed all over the map.
+    Using this network to categorize any set of spectra forced the spectra to be either in the same neurons as the \citetalias{Kinney96} templates or in the neurons between them.
     In the map shown in the upper right panel in Fig.~\ref{fig: 12by12}, the \citetalias{Kinney96} templates are in a small region.
-This provides enough freedom for the SEDs of galaxies to be placed everywhere in the map, even far away from the templates.
+This provides enough freedom for the spectra of galaxies to be placed everywhere in the map, even far away from the templates.
 
@@
     There is a distinguishable strip of grey, dark grey and in some cases black colour in the map:
-    this strip separates early type galaxies from starburst ones.
+    this strip separates quiescent galaxies from starburst ones.
     The lower map shows that 5 of the neurons on the left side of the strip are full. 
-    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (early type galaxies),
+    These five neurons are the same as the ones on the left hand side of Fig.~\ref{fig: 1by2T} (quiescent galaxies),
     the only difference being that in this map they have more space to be separated from each other.
-    When we use this network to categorize the SED of galaxies, any galaxy placed on the left hand side of the strip is an early type galaxy and any one placed on the right side of the strip is a starburst one.
-    The decision about what sub-type of early type or starburst galaxy is based upon its relative position to each type in the SOM.
+    When we use this network to categorize the spectra of galaxies, any galaxy placed on the left hand side of the strip is a quiescent galaxy and any one placed on the right side of the strip is a starburst one.
+    The decision about what sub-type of quiescent or starburst galaxy is based upon its relative position to each type in the SOM.
 
     As in the other map, in the upper right panel of Fig.~\ref{fig: 12by12}, galaxies are generally divided into two main groups.
-    The border between the early type galaxies and the starburst ones is the black strips in the middle of the map,  ending with the bright grey colour at the bottom of the map in the fifth neuron.
-    In this network, neurons in the right side of the strip represent the early type galaxies and the neurons in the left side represent the starburst ones. 
-    When categorizing a new set of SEDs, if the new SEDs are similar to the \citetalias{Kinney96} template all of them will be placed in the bottom of the map, but if there are different type of galaxies, they would sit in any other neurons in the map.
-    In large datasets, one can easily use this network to figure out whether there is any of new type of SEDs (or any outliers) in the datasets. 
+    The border between the quiescent galaxies and the starburst ones is the black strips in the middle of the map,  ending with the bright grey colour at the bottom of the map in the fifth neuron.
+    In this network, neurons in the right side of the strip represent the quiescent galaxies and the neurons in the left side represent the starburst ones. 
+    When categorizing a new set of spectral types, if the new spectra are similar to the \citetalias{Kinney96} template all of them will be placed in the bottom of the map, but if there are different type of galaxies, they would sit in any other neurons in the map.
+    In large datasets, one can easily use this network to figure out whether there is any of new type of spectra (or any outliers) in the datasets. 
     Since the networks are already available, this procedure should be quick and easy for big datasets.
@@
     We used both 2D networks to categorize the \citetalias{Hossein12} galaxies and the results are shown in the lower panels of Fig.~\ref{fig: 12by12}.
-    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the \citetalias{Hossein12} sample there are no outliers or SEDs very different from  the \citetalias{Kinney96} templates.
+    In the lower right map in Fig.~\ref{fig: 12by12}, all galaxies are placed in the bottom part of the map and we can conclude that in the \citetalias{Hossein12} sample there are no outliers or spectra with very different from the \citetalias{Kinney96} templates.
     The lower left map of Fig.~\ref{fig: 12by12} shows the \citetalias{Hossein12} galaxies categorized based on the network in the upper left of Fig.~\ref{fig: 12by12}. 
@@
     Using 2D maps results in categorizing galaxies into more intermediate type than in 1D maps.
-    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the early type side of the SOM, which was predictable from the results in Sec.\ref{sec: 1Dv}.
-This does not imply that in general there are more early type galaxies at higher red-shifts but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.
+    In both lower maps in Fig.~\ref{fig: 12by12}, most galaxies are in the quiescent side of the SOM, which was predictable from the results in Sec.\ref{sec: 1Dv}.
+This does not imply that in general there are more quiescent galaxies at higher red-shifts but rather is a selection effect from the fact that those galaxies had more reliable redshift estimates.
 
-    Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy SED classification should use 2D networks first.
+    Although for ease of presentation this paper first discusses 1D networks and continues to 2D networks, we suggest that users of SOMs for galaxy spectral classification should use 2D networks first.
 These can be used as a first step with networks similar to the upper left map in Fig.~\ref{fig: 12by12} to identify outliers in the sample.
@@
 %One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
-The test results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.% but not exactly the same as one of them.
+The test results showed that using SOMs can allow identification of galaxies with spectra similar to two or more morphological types.% but not exactly the same as one of them.
 The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
-\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} SED templates and classify the same sample of 142 galaxy spectra;
+\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} spectral templates and classify the same sample of 142 galaxy spectra;
 however, they could not classify 37 out of 142 spectra.

### 2016-08-30 version0.0/paper3.tex
Applying part of Sarah's comments on ch4

@@
 Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein14,Hossein16}.
-ANNs are spiered to work in the same way that the neurons work in a human brain.
+ANNs are inspired to work in the same way that the neurons work in a human brain.
 These are networks of interconnected neurons (nodes), in which all of the connections are weighted.
@@
 
-    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
+    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha (6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
      The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
@@
      Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g.][]{Smith07a,Leitherer99} and it can be used to calculate the stellar mass~\citep{Eskew12}.
-     FUV, \halpha, and TIR emission are indicators of star forming regions.
+     FUV, \halphadot, and TIR emission are indicators of star forming regions.
      In this project, we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24~$\mu$m emission.
@@
         Comparing the correlation coefficient plots for all 10 regions in M31 (Fig.~\ref{fig: cor_all}) and for the clustered data (Fig.~\ref{fig: cor_cluster1}) shows the differences between all 10 regions and clustered data and why regions 3 to 8 become separated from the other regions.
-        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
+        The main features that differentiate these two plots are the anti-correlations between PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.8~$\mu$m~emission.
         Additionally, for the PAH fluxes in Fig.~\ref{fig: cor_cluster1}, there are no significant correlations with PACS~100~$\mu$m, L$_\mathrm{dust}$, L$_\mathrm{TIR}$, SFR, or metallicity.
@@
         Many groups have used PAH features as a tracer of SFR by finding correlations between 
-        PAH emission and SFR derived from extinction-corrected \halpha~\citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
+        PAH emission and SFR derived from extinction-corrected \halpha \citep[e.g.][]{Calzetti07,Khramtsova13,Shipley16}.
         These correlations are seen in Fig.~\ref{fig: cor_all}, when we considered the data from all regions, but not in Fig.~\ref{fig: cor_cluster1} when considering the clustered data.
@@
 
-        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halpha, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
-        Anti-correlations between PAH features and the \halpha, \sii, and \oiii~emission could be the result of one of the following. 
+        Strong anti-correlations between 6.2 to 17.0~$\mu$m~main PAH features and RHI, stellar mass, \halphadot, \sii, \oiii, and IRAC~5.6~$\mu$m~emission in Fig.~\ref{fig: cor_cluster1} were not seen in Fig.~\ref{fig: cor_all} (even if we ignore the outlier values).
+        Anti-correlations between PAH features and the \halphadot, \sii, and \oiii~emission could be the result of one of the following. 
         First, the optical data are not corrected for dust extinction.
-        The PAH features correlate with the amount of dust while \halpha~emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
-        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha~emission, and the same holds for \sii~and \oiii~emission.
+        The PAH features correlate with the amount of dust while \halpha emission anti-correlates with the amount of dust due to extinction as suggested by \cite{Calzetti94}.
+        Therefore, higher PAH fluxes imply higher dust abundance and less \halpha emission, and the same holds for \sii~and \oiii~emission.
         Second is the possible effect of the structure of the observed regions.
-        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha~emission. 
+        If the observed regions are located near the edge of \hii~regions we would expect to see more PAH and less \halpha emission. 
         The anti-correlations between 6.2 to 17.0~$\mu$m~PAH features and RHI have been seen in other studies, as well~\citep[e.g.][]{Wu06, Gordon08,Calzetti10,Dim15}. 
@@
 Hence, simply a harder RHI does not argue for a smaller PDRs being more plausible.
-        The latter reason, which could also describe the anti-correlation between PAH features and \halpha~emission, seems to be the more probable one.
+        The latter reason, which could also describe the anti-correlation between PAH features and \halpha emission, seems to be the more probable one.
 
@@
     Regions 1 and 9 are close to each other and in the same side of the star forming ring. 
-    However, region 1 is in an area of the galaxy with less diffuse \halpha~emission than region 9, which might be the reason for their distances in the SOM.
+    However, region 1 is in an area of the galaxy with less diffuse \halpha emission than region 9, which might be the reason for their distances in the SOM.
     Region 2 is more distant from other regions in the galaxy and located in the star forming ring.
-    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha~emission.
+    However, similar to regions 1 and 4, region 2 is located in an area of the galaxy with less diffuse \halpha emission.
     Therefore, the place of region 2 in the SOM tends towards regions 1 and 4. 
@@
             The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e.
-the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha~emission and \sii~ continuum, and so on.
+the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and \halpha\ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, \halpha emission and \sii~ continuum, and so on.
             \import{../image_paper3/text_files/image_texts/}{col3byall.tex}
@@
 
-            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
+            Comparing Figs.~\ref{fig: col3and11_dist} to~\ref{fig: col3and25_dist} shows that adding \halpha emission data to PAH features causes regions 9 and 10 become isolated. 
             Increasing the dimension of the input data makes region 10 more isolated.
@@
 Six of the regions in M31 create a subgroup with relatively lower mid- and far-infrared emission.
-PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
+PAH fluxes in these regions are highly anti-correlated with \halphadot, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and radiation hardness index.
 These anti-correlations are insignificant when the full dataset is considered.
 The most probable reason for PAHs to anti-correlate with optical emission lines and RHI is a harder radiation field.
-This makes the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha~emission and less PAH emission, respectively.
+This makes the size of \hii~regions bigger and the size of photo-dissociation regions smaller, causing more \halpha emission and less PAH emission, respectively.
 

### 2016-08-30 version0.0/paper1.tex
Applying Sarah's comments on ch2.

--- 2016-08-29 version0.0/paper1.tex
@@
 However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications.
-There are many studies on correlation of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Dib11b, Lilly13}.
+There are many studies of correlations of metallicity with stellar mass and SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Dib11b, Lilly13}.
 These studies suggest that metallicity has a critical role in the formation of H$_2$ gas.
@@
 \citet{Krumholz09} introduced a theoretical SFR law which suggests that the SFR and metallicity of galaxies have a power-law correlation, but the power-law index changes with the amount of total gas.
- Using results obtained from both observations and analytical models, \citet{Mannucci10} and \citet{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a 'fundamental metallicity relation'.
+ Using results obtained from both observations and analytical models, \citet{Mannucci10} and \citet{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a `fundamental metallicity relation'.
 They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation.
@@
 %P6(2*): What we did and why Andromeda
-In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31).
+In this chapter, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31).
 Additionally, we applied these two laws on three different regions in M31 to determine whether there is any dependence on distance from the centre of the galaxy.
@@
 To calculate the mass of H$_2$ from the molecular hydrogen column density, we estimated the volume and volume density of H$_2$ in each pixel.
-Then, using M$_{H_2} = \mu_{H_2}m_H\rho_{H_2}$ where $ \mu_{H_2}$ is the mean molecular mass of H$_2$, m$_H$ is the mass of one hydrogen atom and $\rho_{H_2}$ is the volume density, we calculated M$_{H_2}$.
+Then, using M$_{H_2} = \mu_{H_2}m_H\rho_{H_2}V$ where $ \mu_{H_2}$ is the mean molecular mass of H$_2$, m$_H$ is the mass of one hydrogen atom, $\rho_{H_2}$ is the volume density and $V$ is the volume of each pixel, we calculated M$_{H_2}$.
 

### 2016-08-30 version0.0/paper3.tex
Applying M.D.'s comments on the ch.3

--- 2016-08-30 version0.0/paper3.tex
@@
 % data mining and clustering in general; when we have so many data and we want to map them
-\cite{Ball10} gave an extensive review of data mining and machine learning algorithms and their usage in astronomy.
+\cite{Ball10} gave an extensive review of machine learning/data mining algorithms and their usage in astronomy.
 A data mining algorithm learns about data from training, which can be supervised or unsupervised.
@@
 Unsupervised methods train without any prior knowledge of output results: 
-they work solely based on the underlying structure of the input data.   
+they work solely based on the underlying relation of the input data.   
 The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.
@@
 
-    The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
-    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
+     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
+     Users must decide the size of the network based on their data set and their usage of the results.
+     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are well established. 
+     In order to create maps that we can get the most information from them, we varied the initial values for the maps.
+     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose a suitable size for the maps we generated, and decided that based on the size of our sample, for the 2D SOMs, $10\times10$ gives us the most information.
+     Any map higher than this size, repeats the same results and become very time consuming.
+     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
 
@@
         Each of these subgroups separates for a reason.
-        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
+        This reason can vary from having higher values in some specific properties, as discussed in Section~\ref{Sec: 1d_cluster}, to some unknown non-linear or linear correlations between data that cannot be seen in other groups or in the galaxy as a whole.
         To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

### 2016-08-30 version0.0/paper2.tex
Applying M.D's comments on ch.4

@@
-\chapter[Classifying High-Redshift Galaxies Using Self-Organizing Maps]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
+\chapter[Classifying High-Redshift Galaxies Spectra]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
 \label{ch: paper2}
@@
 %What \citetalias{Hossein12} did
-~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified spectral types of a sample of 142 galaxies using a supervised neural network method, based on the spectral template presented by \citetalias{Kinney96}.
+~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified spectral types of a sample of 142 galaxies using a supervised (Multi-layer feed-forward) neural network method, based on the spectral template presented by \citetalias{Kinney96}.
 With the supervised method, they could only classify spectral types of 105 out of the 142 galaxies.
@@
 
-     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
-     Users must decide the size of the network based on their data set and their usage of the results.
-     There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are well established. 
-     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$.
-     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
+    The sizes of the SOM maps are arbitrary and there are no rules regarding choosing one over the other. 
+    \citet{Vesanto05} suggested that a total number of $5\sqrt{n}$ neurons is a sufficient size, but users usually choose the size of the grids based on their dataset and their application of the results.
 

### 2016-08-31 version0.0/appendixa_3.tex
Adding an appendix about Bayesian fitting

\chapter{Fitting Star Formation Laws Using Hierarchical Bayesian Regression}
\pagestyle{plain}
\label{app:bays_fitting}
\myappendices

In Chapter~\ref{ch: paper1}, we mentioned that we used hierarchical Bayesian linear regression to fit the star formation laws (both the Kennicutt-Schmidt and the extended Schmidt law).
The goal is to find the star formation laws using observational data.
In order to compare our results with previous studies and testing star formation laws, we chose to use linear regression to fit the data.
Hierarchical Bayesian regression fitting method were chosen over the simple linear regions methods (e.g. ordinary least square fitting) due to fact that this method thoroughly accounts for all the measured uncertainties and considers the hierarchical data structure (if there is any).
\cite{Shetty13} described the fitting using hierarchical Bayesian linear regression in detail.
In this section, we first summarize \cite{Shetty13} approach and then we describe how we extended their code to fit multiple hierarchical Bayesian regression in order to investigate the extended Schmidt law.

\cite{Shetty13} assumed Bayes' theorem:
\begin{equation}
  \mathcal{P}({\Theta | \mathcal{D}})  \propto \mathcal{P}({\mathcal{D}|\Theta})\mathcal{P}(\Theta)
\end{equation}
where $\Theta$ is the model parameters and $D$ is the data.
$\mathcal{P}({\Theta | \mathcal{D}})$, which is called posterior, is the result of the Bayesian interface.
Posterior is the probability distribution of the model parameters given data. 
$\mathcal{P}(\Theta)$ is the prior on $\Theta$, and $\Theta$ is a vector of all the parameters that define the model.
In the case of the Kennicutt-Schmidt law, $\Theta$ contains power-law index (which is in the log-log basis is the slop,  {\it N}) and intercept, A, (from Equation~\ref{eq:sfr_law_ks_log}), their mean values and variance for each pixel. 
$\mathcal{P}({\mathcal{D}|\Theta})$ is the probability of the data given model parameter, also known as the likelihood.

Given the measured values of the \sigmagas and \sigmasfr and their uncertainty, the Bayesian analysis performs Markov Chain Monte Carlo simulations (MCMC) to find the true value of \sigmagas and \sigmasfr.
The posterior is a probability distribution function for each parameter of $\Theta$ is the the output of the analysis after a large number of MCMC steps (here we chose 50000 steps).

For finding probability distribution function of parameters of the extended Schmidt law, we followed the similar procedure as \cite{Shetty13}.
Since in the extended Schmidt law, the \sigmasfr depends on two independent variables (\sigmagas and \sigmastar), we used the multiple hierarchical Bayesian linear regression instead on the hierarchical Bayesian linear regression.
We assumed $\Theta$ contains $\eqnprime$, $\beta$, A$^\prime$ from Equation~\ref{eq:sfr_law_es_log}, their mean values and their uncertainties. 
As a result of the analysis we have a distributions of plausible values for the parameters of the star formation laws, which are measured by considering the measured values of the \sigmagas, \sigmasfr, \sigmastar and their uncertainties for each pixel.

\bibliographystyle{apj.bst}
\bibliography{ref_paper1.bib}

### 2016-08-31 version0.0/paper1.tex
Adding an appendix about Bayesian fitting

@@
 We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \citet{Shetty13}.
-Shetty and colleagues used a Bayesian linear regression approach in a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
+Shetty and colleagues used a Bayesian linear regression approach in a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure (for more detail on fitting procedure see Appendix~\ref{app:bays_fitting}).
 We used the same technique as \citet{Shetty13} to estimate the K-S law parameters.
@@
 Solid line shows the best fit (the mean value of the range reported in Table~\ref{table:res}) from a pixel-by-pixel method.
-Equivalent plots for the other SFR and gas tracers are in Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the appendix.}
+Equivalent plots for the other SFR and gas tracers are in Fig.s~\ref{fig:es,all,fir,h2} - ~\ref{fig:es,all,halpha,tot} in the Appendix~\ref{app:es,figs}.}
         \label{fig:es,all,fuv,tot}

### 2016-08-31 version0.0/summary.tex
Applying P.W.'s comments on adding the big picture to the summary

@@
 %future works and add big questions
+In this thesis we first measured star formation rate in a nearby galaxy and tested the the current star formation laws using Bayesian statistic on the galaxy.
+We used data mining methods study  observed or measured quantities of the nearby galaxies and compare them with the SFR.
+We then applied the spectra of high-redshift galaxies to determine the correlation between SFR with properties of galaxies in a distant galaxies and through the time.
 To move forward, we would like to test star formation laws in high-redshift galaxies with the hierarchical Bayesian regression fitting method.

### 2016-08-31 version0.0/intro0.01.tex
Adding about the origin of 21 cm emission.

@@
 The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
-Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state. 
-The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
-The energy of the anti-parallel mode is slightly less than the parallel mode.
-Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
-However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
-The large amount of hydrogen atoms compensates for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
+Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state, which is the state of lowest energy.
+Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of 1420.40~MHz.
+This splitting is referred to as the hyperfine structure. 
+The electron can be in either of the two aforementioned states. 
+These states are very stable and the transition between them is forbidden, with a transition rate of $2.5\times10^{-15}\mathrm{s}^{-1}$.
+This means that one would expect this transition to naturally happen once every ten million years.
+%The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
+%The energy of the anti-parallel mode is slightly less than the parallel mode.
+%Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
+%However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
+However, the large amounts of hydrogen atoms in these atomic clouds compensate for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
 Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.
@@
 \centering
-\includegraphics[width=16cm]{../image_intro/imf.png}
+\includegraphics[width=15.5cm]{../image_intro/imf.png}
 \small
@@
 \begin{equation}
-\m {SFR}(YSO) = N_{yso} <M>/\tau 
+{\m SFR}(YSO) = N_{yso} <M>/\tau 
 \end{equation}

### 2016-08-31 version0.0/asli.tex
Applying R.A's comments on the ch3.
Applying part of Sarah's comments on ch4
Adding an appendix about Bayesian fitting
correct typos in CV

@@
 
-{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future. %TBD: change this if you change the title
+{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.
 
@@
 \newcommand{\halpha}    {H$\alpha\ $}
+\newcommand{\halphadot}    {H$\alpha$}
 \newcommand{\um}    {$\mu$m\ }
@@
  \include{appendixa_2}
+ \include{appendixa_3}
  \include{appendixb}
@@
 % & Winnipeg, MB (Spring, 2016)\\
-&{\sl Scholarship for Utrecht Summer School on Star formation,}\\
+&{\sl Scholarship for Utrecht Summer School on Star Formation,}\\
 &Utrecht, Netherlands (Summer, 2009)\\\\
@@
 \subsubsection*{Publications:}
- \textbf{Rahmani. S}, Lianou. S, Barmby. P, ``{\em Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}'', 2016, MNRAS, 456, 4128\\
-\textbf{Rahmani. S}, Teimoorinia. H, Barmby. P, `` {\em Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}", Submitted to MNRAS, JUNE,2016\\
+ \textbf{Rahmani, S.}, Lianou, S., Barmby, P., ``{\em Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}'', 2016, MNRAS, 456, 4128\\
+\textbf{Rahmani, S.}, Teimoorinia, H., Barmby, P., `` {\em Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}", Submitted to MNRAS, June ,2016\\
 
 \subsubsection*{Work in Preparation}
- \textbf{Rahmani. S}, Teimoorinia. H, Peeters. E, Barmby. P, `` {\em Data Mining in nearby galaxies}", In prep.\\
+ \textbf{Rahmani, S.}, Teimoorinia, H., Peeters, E., Barmby, P., `` {\em Data Mining in nearby galaxies}", in prep.\\
 
-\subsubsection*{Conferences Talks}
+\subsubsection*{Conference Talks}
 
@@
 {\sl International Tusi Conference on Astrophysics, devoted to the Maragha Observatory's 750th year
-anniversary, Maragha, Iran} \hfill(2009)
+Anniversary, Maragha, Iran} \hfill(2009)
 \begin{itemize} 
-\item Rahmani, S., Mashhoon, M., Moghaddam , A., ``Challenges of brightness variations of Planets: From Geocentric to Heliocentric" 
+\item Rahmani, S., Mashhoon, M., Moghaddam, A., ``Challenges of brightness variations of Planets: From Geocentric to Heliocentric" 
 \end{itemize}
-\subsubsection*{Conferences Posters}
-{\sl Statistical challenges in Modern Astronomy {\textsc VI}, Pittsburgh, PA}\hfill(2016)
+\subsubsection*{Conference Posters}
+{\sl Statistical Challenges in Modern Astronomy {\textsc VI}, Pittsburgh, PA}\hfill(2016)
 \begin{itemize} 
@@
 \begin{itemize} 
-\item Rahmani, S., Barmby, P. 2013, ``Which Star formation laws in M31?" 
+\item Rahmani, S., Barmby, P. 2013, ``Which Star Formation Laws in M31?" 
 \end{itemize}
 
-{\sl Canadian Astronomical Society Conference (CASCA), University of British Colombia, BC}\hfill (2013)
+{\sl Canadian Astronomical Society Conference (CASCA), Vancouver, BC}\hfill (2013)
 \begin{itemize} 

### 2016-08-31 version0.0/asli.tex
Update asli.tex
correct name spellings in acknowledgments

@@
 S.
-Lianue, and Dr.
+Lianou, and Dr.
 H.
@@
 
-I would like to thank all my fellow graduate students in Western University: Alex, Aycha, Beth, Boshra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
+I would like to thank all my fellow graduate students in Western University: Alex, Aycha, Beth, Bushra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
 You guys are amazing; you helped me whenever I needed, and I had so much fun hanging out with you.

### 2016-08-31 version0.0/paper2.tex
Adding an appendix about Bayesian fitting
Applying S.G.'s comment on changing Y title of Spectra plots
Update paper2.tex
grammatical corrections to paper2.tex

@@
-\chapter[Classifying High-Redshift Galaxies Spectra]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
+\chapter[Classifying High-Redshift Galaxy Spectra]{Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach}
 \label{ch: paper2}
@@
 We can determine some physical property of a galaxy by properly modeling various features observed in its SED, and the general shape of the SED can be used as an identifier of the morphological type.
-Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical or spiral.
+Considering the main features of SEDs, galaxies can be categorized into two main groups: elliptical or spiral. %PB: quiescent or SB?
 Each group has its own characteristic features and can in turn be divided into many sub-branches.
@@
 To overcome this challenge, many fitting methods have been developed and used to find template matches for SEDs, with $\chi^2$ minimization being the most commonly used. 
-Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies based on their SED \citep[e.g.][]{Allen13,Ordov14,Shi15}.
+Artificial neural networks, K-means clustering, and principal component analysis are some other methods used to cluster and classify spectral types of galaxies \citep[e.g.][]{Allen13,Ordov14,Shi15}.
 
@@
 The latter has been the subject of many other studies \citep[e.g.][]{Kind14a}.
-From classifying quasars' spectra to star/galaxy classifications, from gamma-ray bursts clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.
+From classifying quasars' spectra to star/galaxy classifications, from gamma-ray burst clustering to classification of light curves, this method has proved to be useful in various fields of astronomy \citep[e.g.][]{Maehoenen95, Miller96, Andreon00, Balastegui01, Rajaniemi02, Brett04, Scaringi09}.
 
@@
 \citet{Fustes13} produced a package based on SOM to classify spectra from the GAIA survey that were previously classified as ``unknown'' by the SDSS pipeline.
-This package can recognize an astronomical object from instrumental errors, and then classify the object based on its spectrum.
+This package can distinguish an astronomical object from instrumental errors, and then classify the object based on its spectrum.
 
 %What \citetalias{Hossein12} did
-~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified spectral types of a sample of 142 galaxies using a supervised (Multi-layer feed-forward) neural network method, based on the spectral template presented by \citetalias{Kinney96}.
+~\citet[][hereafter \citetalias{Hossein12}]{Hossein12} classified spectral types of a sample of 142 galaxies using a supervised (Multi-layer feed-forward) neural network method, based on the spectral templates presented by \citetalias{Kinney96}.
 With the supervised method, they could only classify spectral types of 105 out of the 142 galaxies.
 The spectra of the 37 galaxies from their samples could not be matched with any of those in the \citetalias{Kinney96} templates. 
-In order to classify the remaining 37 galaxies, they combined spectrum of the \citetalias{Kinney96} templates.
+In order to classify the remaining 37 galaxies, they combined spectra of the \citetalias{Kinney96} templates.
 \citetalias{Hossein12} also showed that there are tight correlations between physical properties of galaxies, and these correlations might be different for each type of galaxy.
@@
 \label{sec: data_highZ}
-We use spectra templates from \citetalias{Kinney96} to train neural networks.
+We use spectral templates from \citetalias{Kinney96} to train neural networks.
 To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12}.
-Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in spectra clustering, but also to easily compare supervised and unsupervised methods.
+Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in spectral clustering, but also to easily compare supervised and unsupervised methods.
 
@@
         \includegraphics[width=0.9\textwidth]{../image_paper2/k96.jpg}
-        \caption[\citet{Kinney96} spectra template for 12 types of galaxies]{\citet{Kinney96} spectra template for 12 types of galaxies from \citet{Hossein12} paper (Fig.
+        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies from \citet{Hossein12} paper (Fig.
 1 in \citet{Hossein12}).
 The type of each template is shown in each frame.
-Plots B, E, S0, Sa, Sb and SC show spectra that belong to the quiescent galaxies.
-Starburst galaxies spectra are indicated with SB 1 to 6.
-Higher numbers represent more intrinsic colour extinction.}
+Plots B, E, S0, Sa, Sb and SC show spectra that belong to quiescent galaxies.
+Starburst galaxy spectra are indicated with SB 1 to 6.
+Higher numbers represent more intrinsic extinction.}
         \label{fig: k96}
@@
 
-    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of spectra templates.
+    \citetalias{Kinney96} used ultraviolet-optical spectra of 70 star-forming and quiescent nearby galaxies to produce a set of templates that contained 12 types of spectral templates.
     These templates have been widely used in many studies to determine morphological type of galaxies or properties of specific types of galaxies~\citep[e.g.][]{Shakouri16, Paiano16, Laporte16, Holden16}.
@@
 Values for the number of neurons is arbitrary, and for various toolboxes values for one or all of $L_0$,$L(t)$, $R(t)$  and $r^t_{BMU}$ are arbitrary.
-\cite{Geach12} demonstrate the algorithm of the SOM in more detail.
+\cite{Geach12} discussed the SOM algorithm in more detail.
 
@@
             Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.
-            As in to Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
+            As in Fig.~\ref{fig: sample}, the upper part of the figures shows the neurons and their relative distances between weight of neurons.
             As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
@@
             In this method, the Sc template has been categorized as starburst due to the relatively higher disk stellar population relative to that of the bulge. 
-            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have a flattter spectra compare to other quiescent galaxies.
+            According to \citetalias{Kinney96}, Sc galaxies are considered to be late Hubble type galaxies which have  flattter spectra compare to other quiescent galaxies.
 
@@
             On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the spectra to become flatter at shorter wavelengths. 
-            The flatter UV spectra makes these two templates more similar to quiescent galaxies than to other starbursts.
-            Therefore, in the networks, SB5 and SB6 types are to be grouped close to the quiescent galaxy templates.
+            The flatter UV spectra make these two templates more similar to quiescent galaxies than to other starbursts.
+            Therefore, in the networks, SB5 and SB6 types are grouped close to the quiescent galaxy templates.
 
@@
             The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
-            This template has the most extinction and its spectra has more similarity to quiescent galaxies than other starburst types.
+            This template has the most extinction and its spectrum has more similarity to quiescent galaxies than other starburst types.
 
@@
             Eighty of the galaxies have spectral types similar to those of the quiescent galaxies and the spectral types of the rest are similar to the starburst galaxies.
-            The lower left panel shows the median spectra of the 80 galaxies that were classified as quiescent. 
+            The lower left panel shows the median spectrum of the 80 galaxies that were classified as quiescent. 
             These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
@@
             The H$\alpha$ emission in the spectrum could be from galaxies with similar spectral types to Sa galaxies, but with stronger emission lines.
-            The median spectra in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
+            The median spectrum in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
             \begin{figure}
@@
 In this case 80 means that 80 of the 142 spectra are classified into the quiescent group while the 62 of the 142 spectra are categorized as starburst galaxies.
-Lower panel: median spectra of the galaxies in each group, early-type on the left and starburst on the right.}
+Lower panel: median spectra of the galaxies in each group (fluxes are normalized by dividing spectra by flux at 4000\AA), early-type on the left and starburst on the right.}
                 \label{fig: 1by2V}
@@
 
-            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectra predominantly decides which group the galaxy belongs to.
+            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decides which group the galaxy belongs to.
             Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
@@
             Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
-            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that spectra of galaxies in the cluster are very similar to those of the template.
+            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that the spectra of galaxies in the cluster are very similar to those of the template.
             Otherwise, we can conclude that the spectra of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates.
@@
             There are 3 galaxies in the third neuron, similar to the S0 type. 
-            19 of the galaxies are jn the fifth neurons and similar to the Sa type, while the 6 galaxies in the fourth neurons have spectral type similar to both S0 and Sa galaxies.
+            19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
             There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
@@
             In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
-            Therefore, 24 galaxies in the eighth neurons have similar spectra to Sb type galaxies, and the spectra of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
+            Therefore, 24 galaxies in the eighth neuron have similar spectra to Sb type galaxies, and the spectra of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
             The far right neurons in the network belong to galaxies with spectra comparable to types SB1 and SB2.
@@
             However, with SOM, we have the freedom to categorize galaxies in intermediate groups.
-            Therefore, if the spectra of galaxies do not match completely with any of the spectra templates in Fig.~\ref{fig: k96}, they can be categorized as a spectra with similarity to two or more of the groups.
+            Therefore, if the spectra of galaxies do not match completely with any of the spectral templates in Fig.~\ref{fig: k96}, they can be categorized as a spectrum with similarity to two or more of the groups.
 
@@
         As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst. 
-       Separating galaxies based on spectral types also leads to a separation in properties that derived (via {\em CIGALE}) from the spectra, as expected since the spectra types are also based on {\em CIGALE} fitting.
+       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the spectra, as expected since the spectral types are also based on {\em CIGALE} fitting.
 
@@
 Two-dimensional networks can be used to find the relations of the neurons and classifications in more details.
-The sample galaxies have more freedom to be categorized, and only 23 of them occupies exactly the same neurons as \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
-Additionally, by using two-dimensional networks we showed that we do not have nay outlier in the sample galaxies.
+The sample galaxies have more freedom to be categorized, and only 23 of them occupy exactly the same neurons as the \citetalias{Kinney96} template spectra (in one-dimensional networks this number was 56).
+Additionally, by using two-dimensional networks we showed that we do not have any outliers in the sample galaxies.
 

### 2016-08-31 version0.0/paper3.tex

@@
      One feature of the SOM method is that there is no rule or restriction on the number of clusters.
-     Users must decide the size of the network based on their data set and their usage of the results.
+     Users must decide on the size of the network based on their data set and their usage of the results.
      There have been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are well established. 
-     In order to create maps that we can get the most information from them, we varied the initial values for the maps.
+     In order to create maps from which we can get the most information, we varied the initial values for the maps.
      We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose a suitable size for the maps we generated, and decided that based on the size of our sample, for the 2D SOMs, $10\times10$ gives us the most information.
-     Any map higher than this size, repeats the same results and become very time consuming.
-     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
+     Any map larger than this size repeats the same results and becomes very time consuming to generate.
+     We created our final SOMs with initial values for the number of iterations in the ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively.
 
@@
      Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
-     Metallicity for all regions except regions 5 and 8 were adapted from~\citep{Sanders12} and for regions 5 and 8, \cite{Dim15} estimated metallicity from the radial metallicity profile.
-     \cite{Dim15} also measured radiation hardness index (RHI) using calibration of the ratio of two lines, $\left (\log \frac{[Ne~\textsc{iii}]}{[Ne~\textsc{ii}]} + \left [ 0.71 + 1.58\log\frac{[S~\textsc{iV}]}{[S~\textsc{iii}]} \right ] \right )/2$, for these 10 regions.
+     Metallicity for all regions except regions 5 and 8 was adopted from~\citep{Sanders12} and for regions 5 and 8, \cite{Dim15} estimated metallicity from the radial metallicity profile.
+     \cite{Dim15} also calculated the radiation hardness index (RHI) for these 10 regions using $\left (\log \frac{[Ne~\textsc{iii}]}{[Ne~\textsc{ii}]} + \left [ 0.71 + 1.58\log\frac{[S~\textsc{iV}]}{[S~\textsc{iii}]} \right ] \right )/2$ \citep{}.
+%PB: NEED CITATION HERE
      We used the measured PAH feature fluxes, metallicity and RHI of each region as the input for self-organizing maps.
@@
     Therefore, we need data from at least a few regions in the galaxy to use this application of SOMs and cannot use these networks to learn about properties of a single region in other galaxies.
-    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that region 7 and 4 have relatively higher surface brightness than the other regions in M101.
+    As mentioned before, since we know the properties of regions in M31, from Fig.~\ref{fig: subset9}, we can quickly conclude that regions 7 and 4 have relatively higher surface brightness than the other regions in M101.
     Similarly, we can say that regions 6 and 8 in M101 have very faint surface brightness for most of the parameters, and are very different from regions 7 and 4.

### 2016-08-31 version0.0/paper3.tex

@@
 Their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content.
-In Fig.~\refthere ha{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
+In Fig.~\ref{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
 The left part of the plot is where regions with low SFR belong and the right side is for high SFR regions.

### 2016-08-31 version0.0/intro0.01.tex
Changing MHz to J

@@
 This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
-The gas and dust in the ISM are heated by interstellar radiation field and cooled through a variety of line and continuum processes which usually depend on the local physical conditions. 
+The gas and dust in the ISM are heated by the interstellar radiation field and cooled through a variety of line and continuum processes which usually depend on the local physical conditions. 
 The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
@@
 Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state, which is the state of lowest energy.
-Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of 1420.40~MHz.
+Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of 9.4E-25~J.
 This splitting is referred to as the hyperfine structure. 
@@
 Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
-In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically proven that they have a power-law size distribution.
+In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically found to have a power-law size distribution.
 The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
@@
 %Extinction can be defined as a reduction of the original intensity caused by dust:
-Extinction is quantified as the difference in observed and initial magnitudes of an object in a specific wavelength ($\lambda$):
+Extinction is quantified as the difference between observed and intrinsic magnitudes of an object at a specific wavelength ($\lambda$):
 \begin{equation}
@@
 \end{equation}
-where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are observed and initial magnitude, respectively.
-Magnitude is related to intensity (I) as:
+where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are the observed and intrinsic magnitudes, respectively.
+Magnitude is related to intensity ($I$) as:
 \begin{equation}
@@
 \end{equation}
-where $c$ is a constant which depends on photometric system that is being used.
-Optical depth, $\tau_{\lambda}$, is defined by ratio of observed and initial intensity of a source as:
+where $C$ is a constant which depends on the photometric system that is being used.
+Optical depth, $\tau_{\lambda}$, is defined as the ratio of observed and intrinsic intensity for a source as:
 \begin{equation}
@@
 \end{equation}
-where I$(\lambda)$ is observed intensity in wavelength $\lambda$ and I$_0(\lambda)$ is intensity of light before passing through dust.
-Therefore, the optical depth and extinction can be converted to one an other by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
+where I$(\lambda)$ is the observed intensity at wavelength $\lambda$ and I$_0(\lambda)$ is the intensity of light before it passes through the extincting dust.
+Therefore, the optical depth and extinction can be converted to one another by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
 The extinction also depends on the grain size and extinction cross section.
-For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.
+For measuring SFR using various wavebands, the decrease in the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.
 
@@
 From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\cite{McKee07}. 
-From an observational standpoint, star formation is discussed by many authers \citep[e.g.][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.
+From an observational standpoint, star formation is discussed by many authors \citep[e.g.][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.
 
@@
 The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g.
-by adding lumincity at 24~$\mu$m (L(24~$\mu$m)) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
+by adding luminosity at 24~$\mu$m (L(24~$\mu$m)) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.
 
@@
 I cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
-During this process, I find hidden structures in high-dimensional data space.
-In Chapter~\ref{ch: paper2}, I move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
-I train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
+During this process, I find hidden structures in a high-dimensional data space.
+In Chapter~\ref{ch: paper2}, I move to more distant galaxies and apply the SOM algorithm to their spectra.
+I train networks using a set of galaxy spectral templates covering the wavelength range from UV to IR and use them to classify the spectra of a sample of 142 galaxies with $0.5 < z < 1$. 
 Then I study the grouped properties of the classified galaxies.

### 2016-08-31 version0.0/summary.tex
Changing MHz to J

@@
 The dependence of SFR on other properties of galaxies such as morphology and dust mass have been tested as well, but there is no SFR law that considers all of the above quantities together.
-The Kennicutt-Schmidt law ~\citep{Schmidt59, Kennicutt98b} was the first empirical star formation law, suggesting that SFR and molecular gas have a logarithmic correlation with each other. 
+The Kennicutt-Schmidt law~\citep{Schmidt59, Kennicutt98b} was the first empirical star formation law, suggesting that SFR and molecular gas have a logarithmic correlation with each other. 
 However, after many years and studies, there is still an ongoing question of whether it is a universal law or not.
 \citet{Shetty13} showed that, besides the physical and environmental effects, fitting methods also change our perspective of the K-S law.
-Extended version of the K-S law were introduced by adding the effect of stars (extended Schmidt law; introduced by ~\citealt{Shi11}) or metallicity (Krumholz law; introduced by ~\citealt{Krumholz09}).
+Extended version of the K-S law were introduced by adding the effect of stars (extended Schmidt law; introduced by~\citealt{Shi11}) or metallicity (Krumholz law; introduced by~\citealt{Krumholz09}).
 Compared to the K-S law, the extended Schmidt law and Krumholz law are relatively recently introduced and still need to be tested with diverse statistical methods on different scales (local and global), with various morphological types and in both nearby and high-redshift galaxies.

### 2016-08-31 version0.0/paper2.tex
Update paper2.tex
minor grammar change
change line 567 of chapter 4, to include S.G.'s comment on the other type of galaxies that are not in the K96 template

@@
             Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
-            In these plots we force the galaxies to be categorized in a maximum 3 groups. 
+            In these plots we force the galaxies to be categorized in a maximum of 3 groups. 
             If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
@@
     In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
-    This approach can be used to trace and recognize the outliers, which could include galaxy types that are not presented in the \citetalias{Kinney96} templates.
+    This approach can be used to trace and recognize the outliers, which could include galaxy types that are not presented in the \citetalias{Kinney96} templates (e.g.
+dwarf galaxies, luminous infrared galaxies, active galactic nucleus).
     To execute the second approach, we used the {\textsc selforgmap} library in the {\textsc matlab}.

### 2016-08-31 version0.0/paper2.tex
changing testing to classifying in chapter 4

@@
 As in \citetalias{Hossein12}, we examine the averaged properties of the new galaxy groups and compare them with previous work.
-In Section $\S$~\ref{sec: data_highZ}, we present the data that we use to train and test our networks. 
+In Section $\S$~\ref{sec: data_highZ}, we present the data that we used to train our networks and the data classified using the trained networks. 
 We describe the SOM methods in Section $\S$~\ref{sec: method_somz}. 
@@
 We use spectral templates from \citetalias{Kinney96} to train neural networks. 
-To test the trained networks, we use SED and physical properties of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12}.
+We classify the spectra of 142 galaxies at $0.5<z<1$ from \citetalias{Hossein12} using the trained networks, and use their physical properties to test the new classifications.
 Following the \citetalias{Hossein12} work, we chose these two sets of data not only to show the application of SOMs in spectral clustering, but also to easily compare supervised and unsupervised methods.
@@
 
-    For testing the created networks, we use SEDs that were produced by \citetalias{Hossein12}. 
-    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength in a wide range of wavelengths.
-    Since we have used the \citetalias{Hossein12} SEDs to test the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} spectral templates.
-
+    We classify SEDs that were produced by \citetalias{Hossein12} using the created networks.
+    These SEDs are publicly available~\footnote{All the \citetalias{Hossein12} produced SEDs can be found in \href{http://telbib.eso.org/detail.php?bibcode=2012AJ....144..172T}{ESO webpage}} in the form of flux per rest frame wavelength over a wide range of wavelengths.
+    Since we have chosen the \citetalias{Hossein12} SEDs to be classified by the trained network, we only used the part of the SEDs that have the same wavelength range as the \citetalias{Kinney96} spectral templates.
 %----------------------------------------------------------------------------------------
@@
 
-        In order to check whether our conclusions in Section~\ref{sec: 1Dv}~are correct, in this section we test the relations between median properties of the galaxies in each neuron.
+       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is correct, in this section we examine the relations between median properties of the galaxies in each neuron.
 
@@
 
-A sample of 142 high red-shift galaxies from \citetalias{Hossein12} was used to test the trained networks.
-%One of the main criteria to choose a test sample is that the test sample must have fluxes in exactly the same wavelengths of the training sample.
-The test results showed that using SOMs can allow identification of galaxies with spectra similar to two or more morphological types.% but not exactly the same as one of them.
+A sample of 142 high-redshift galaxy SEDs from \citetalias{Hossein12} was classified by the trained networks.
+The classification results showed that using SOMs can allow identification of galaxies with SEDs similar to two or more morphological types.
 The freedom of having in-between types is one of the main differences between supervised and unsupervised artificial neural networks.
-\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} spectral templates and classify the same sample of 142 galaxy spectra;
+\citetalias{Hossein12} used a supervised training method to train networks with \citetalias{Kinney96} SED templates and classify the same sample of 142 galaxy spectra;
 however, they could not classify 37 out of 142 spectra.
@@
 
-The properties of the galaxies in the test sample using the new
-classification were found to more tightly correlate in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies. 
+TThe properties of the galaxies in the \citetalias{Hossein12} sample using the new classification were found to be more tightly correlated in mean values of age, specific star formation rate, stellar mass, and far-UV extinction than in previous studies.
 The properties of the galaxies in each group are in good agreement with their morphological types.

### 2016-08-31 version0.0/intro0.01.tex
Kinda adding why SOM and relative differences.

@@
 Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
-Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
+Planets and black holes without an accretion disc, on the other hand, have much lower luminosities compared to the other aforementioned components, and therefore contribute less to the SED.
 Therefore, by properly modeling of observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.
@@
 Gas and dust in galaxies can be found in the space between stars.
-This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
+This space is called the interstellar medium (ISM), and it is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
 The gas and dust in the ISM are heated by the interstellar radiation field and cooled through a variety of line and continuum processes which usually depend on the local physical conditions. 
@@
 
-In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot}$) in the ISM due to gravitational instabilities. 
+In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $M \sim 10^7$ M$_{\odot}$) in the ISM due to gravitational instabilities. 
 The denser regions within GMCs collapse under their own gravity (self-gravity) and create clumps.
@@
 Since the protostars have a higher mass than their surroundings, more gas from GMCs accretes onto protostars.
-This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).
+This procedure continues until hydrogen burning in the centres of protostars starts (see~\cite{McKee07} for more detail).
 
@@
 Observations show that massive low metallicity stars rotate faster.
-Being more massive at the end of their evolutionary tracks gives massive low metallicity stars have a lower chance to explode and become a supernova.
+Being more massive at the end of their evolutionary tracks gives massive low metallicity stars a lower chance to explode and become a supernova.
 
@@
 Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
-Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
+Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analyses), using the templates.
 One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
@@
 Dust is mostly comprised of silicates, and graphite grains can be seen in dark clouds or galactic cirrus.
-Emission lines from atoms or ions (i.e \hii~regions) in a hot gas, lines from molecules in cold clouds, and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
+Emission lines from atoms or ions (i.e.\ \hii~regions) in a hot gas, lines from molecules in cold clouds, and 21~cm emission of \hi~are the main observational signatures of the gas in the ISM of galaxies.
 Dust can be observed directly through far-infrared and sub-millimeter wavelength emission or indirectly through its extinction and attenuation effects (see Section~\ref{sec: extinction}).
@@
 Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state, which is the state of lowest energy.
-Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of 9.4E-25~J.
+Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of $9.4\times 10^{-25}$~J.
 This splitting is referred to as the hyperfine structure. 
 The electron can be in either of the two aforementioned states. 
-These states are very stable and the transition between them is forbidden, with a transition rate of $2.5\times10^{-15}\mathrm{s}^{-1}$.
+These states are very stable and the transition between them is forbidden, with a transition rate of $2.5\times10^{-15}$~s$^{-1}$.
 This means that one would expect this transition to naturally happen once every ten million years.

### 2016-08-31 version0.0/paper3.tex
Kinda adding why SOM and relative differences.

--- 2016-08-31 version0.0/paper3.tex
@@
 These networks are used to study nonlinear and complex relations between input and output data.
+There are quite a few data mining methods available, and each one of them has its own advantages or disadvantages. 
 One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
@@
 The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
+The main disadvantages of this method are not handling errors in the data points and having relative results.
+However, the one of the main advantages of this method beside the mentioned ones is that this method is well-tested in Astronomy. 
 Since the 1990s, many studies have utilized SOMs for object classification and clustering (e.g.
@@
 In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure.
-Comparing the SOMs, K-means and hierarchical clustering methods shows that in some cases the hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
+There are reports of mis-classifies the data~\citep[][and references therein]{Mangiameli96} by the hierarchical clustering method, when it was compared with SOMs and K-means using the same datasets.
 We chose the SOM method over the K-means method due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
 Therefore, we can cluster our sample data and study the underlying structure simultaneously.
+%The other point is that as long as one of the data mining method works on a dataset, the other method will work on it, too.
 
@@
 Grey to black colours show the border between regions.
+As mentioned in Section~\ref{sec: algorithm_somz}, the grey cycle shows the differences between the weight of each neurons and the initial weight is assigned randomly.
+Therefore, the colours between neurons shows the relative differences not the absolute ones.
 This network is considered to be a trained network, and can be used to cluster any new data set with similar entries.
@@
      Metallicity for all regions except regions 5 and 8 was adopted from~\citep{Sanders12} and for regions 5 and 8, \cite{Dim15} estimated metallicity from the radial metallicity profile.
-     \cite{Dim15} also calculated the radiation hardness index (RHI) for these 10 regions using $\left (\log \frac{[Ne~\textsc{iii}]}{[Ne~\textsc{ii}]} + \left [ 0.71 + 1.58\log\frac{[S~\textsc{iV}]}{[S~\textsc{iii}]} \right ] \right )/2$ \citep{}.
-%PB: NEED CITATION HERE
+     \cite{Dim15} also calculated the radiation hardness index (RHI) for these 10 regions using $\left (\log \frac{[Ne~\textsc{iii}]}{[Ne~\textsc{ii}]} + \left [ 0.71 + 1.58\log\frac{[S~\textsc{iV}]}{[S~\textsc{iii}]} \right ] \right )/2$~\citep{Engelbracht08}.
      We used the measured PAH feature fluxes, metallicity and RHI of each region as the input for self-organizing maps.

### 2016-08-31 version0.0/appendixa_3.tex
Changing plots in ch4. to flux density instead of flux

@@
 \cite{Shetty13} described the fitting using hierarchical Bayesian linear regression in detail.
-In this section, we first summarize \cite{Shetty13} approach and then we describe how we extended their code to fit multiple hierarchical Bayesian regression in order to investigate the extended Schmidt law.
+In this section, we first summarize \cite{Shetty13} approach and show the differences between ordinary least square fitting and the hierarchical Bayesian linear regression and then we describe how we extended their code to fit multiple hierarchical Bayesian regression in order to investigate the extended Schmidt law.
 

### 2016-08-31 version0.0/intro0.01.tex
Changing plots in ch4. to flux density instead of flux

@@
 Forbidden lines are not called so because there is no chance of them occurring, but merely because their probability is much lower than the normal ``allowed'' transitions.
-Optically bright \halpha emission from \hii~regions is correlated with number of new massive stars in regions, and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
+Optically bright \halpha emission from \hii~regions is correlated with the number of new massive stars in regions, and can be used as a star formation tracer~\citep[e.g.][]{Kennicutt98b,Calzetti13}.
 Studying \hii~regions provides valuable insight into star forming regions by providing information such as star formation rate, initial mass function (IMF), and distribution of ionizing stellar masses~\citep[][and references therein]{Azimlu11}.
@@
 The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
-Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
+Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar populations~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
 Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
@@
 It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
+%PB: please check this: I think \int should be omitted, dV should be \Delta V, and $V$ should also be $\Delta V$
 For a uniform cloud with a radius $R$, the CO luminosity is given by:
@@
 \end{equation}
-where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
+where $T_{\mathrm B}$ is the brightness temperature  in Kelvin and $dV$ is in km~s$^{-1}$, with the integral over the line profile. 
 These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi~is detectable in most spiral galaxies and some elliptical galaxies).
@@
 
-Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to low spatial resolution of available observational data.
+Studying the gas clouds in the ISM of distant galaxies by using direct methods is almost impossible and not practical, due to the low spatial resolution of available observational data.
 \cite{Hildebran83} was the first to suggest that one way to estimate the mass of the gas in the ISM might be from the optical depth of the sub-mm continuum emission from the dust; continuum dust emission is generally optically thin.
@@
 Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08}.
-Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
+The peak of emission of young, hot, and massive stars is at UV wavelengths, which makes them an ideal tracer of the current SFR.
 One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer.
@@
 \begin{split}
-    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
-           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
+    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M_{\odot}) \le 0.5)\\                  
+           & \propto M^{-3.3}    \quad    (0.5 \le M(M_{\odot}) \le 100)
 \end{split}
@@
 The mass ranges from 0.1 to 120~M$_\odot$.
-Adopted from~\cite{Baldry03}.}
+Adapted from~\cite{Baldry03}.}
 \label{fig: imf}
@@
 $<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
-$\tau$ is the lifetime of the YSO  $\tau \sim 2$~Myr~\citep{Evans09}. 
+$\tau$ is the lifetime of the YSO,  $\tau \sim 2$~Myr~\citep{Evans09}. 
 Since our current devices cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.
@@
 \end{equation}
-where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g, starburst99][]{Leitherer99}).
+where SFR is in units of M${_\odot}$~yr$^{-1}$, $L(\lambda)$ is the luminosity in erg~s$^{-1}$ at the wavelength $\lambda$, and $C$ is a constant derived from stellar population models~\citep[e.g., Starburst99][]{Leitherer99}).
 The constant $C$ varies for different wavelengths, mass ranges of the stellar IMF, and the timescale $\tau$ over which star formation is assumed to remain constant. 
@@
 \hline
-L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
-L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
-L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
-L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
-L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
-L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
+L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100$ Myr \\
+L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100$ Myr \\
+L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10$ Myr \\
+L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
+L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$Myr \\
+L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
+L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100$ Myr \\
+L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
+L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100$ Myr \\
+L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6$ Myr \\
+L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10$ Myr \\
 \hline
@@
 where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
-Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
+Although SFR(\oii) is not as accurate as the SFR(\halphafot), it is one of major SFR indicators in high-redshift galaxies.
 In these galaxies, the \halpha emission line is redshifted out of the optical band.
@@
 \end{equation}
-where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.
+where SFR(TIR) is in M$_{\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.
 
@@
 \begin{table}
-\caption{SFR calibrations from PAH luminosities; adopted from~\cite{Shipley16}}
+\caption{SFR calibrations from PAH luminosities; adapted from~\cite{Shipley16}}
 \label{table_PAH}
@@
 
-The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used.
+The most common use of combined luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used.
 This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
@@
 \begin{table}
-\caption{Multi-wavelength dust-corrected luminosities, adopted from~\cite{Kennicutt12}}
+\caption{Multi-wavelength dust-corrected luminosities, adapted from~\cite{Kennicutt12}}
 \label{table3}
@@
 Therefore, even though it might have an insignificant part in UV emission from galaxies, a correction for emission from evolved stars should be considered~\citep{Leroy08}.
-After measuring the corrected luminosities for star forming regions in galaxies (global or local), using proper calibrations can give the best estimation of SFR in galaxies.
+After measuring the corrected luminosities for star forming regions in galaxies (global or local), using proper calibrations can give the best estimate of SFR in galaxies.
 
@@
 %In more recent work,~\cite{Laura16} measured stellar mass for a group of galaxies with ($z < 0.035$) using correlation introduced by~\cite{Eskew12} and showed these stellar masses are tightly correlated with stellar masses measured from other calibrations.
-In more recent work,~\cite{Laura16} measured stellar mass for a group of galaxies with $z < 0.035$, using the correlation that was introduced by~\cite{Eskew12}. 
-The study revealed that measured stellar masses in that study are tightly correlated with stellar masses measured from other calibrations.
+In more recent work,~\cite{Laura16} measured stellar masses for galaxies in groups with $z < 0.035$, using the correlation that was introduced by~\cite{Eskew12}. 
+Those authors found that measured stellar masses in that study were tightly correlated with stellar masses measured from other calibrations.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-08-31 version0.0/paper2.tex
Kinda adding why SOM and relative differences.
Changing plots in ch4. to flux density instead of flux

@@
 
-    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra.
+    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra (binned in 10\AA).
     Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
@@
                 \begin{subfigure}[b]{\textwidth}
-                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2.png}
+                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by2_fluxdensity.png}
                      %\caption{$1\times2$ hits map}
@@
 In this case 80 means that 80 of the 142 spectra are classified into the quiescent group while the 62 of the 142 spectra are categorized as starburst galaxies.
-Lower panel: median spectra of the galaxies in each group (fluxes are normalized by dividing spectra by flux at 4000\AA), early-type on the left and starburst on the right.}
+Lower panel: median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), early-type on the left and starburst on the right.}
                 \label{fig: 1by2V}
@@
                 \begin{subfigure}[b]{\textwidth}
-                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by3.png}
+                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by3_fluxdensity.png}
                 \end{subfigure}
@@
                 \centering
-                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by22.png}
+                     \includegraphics[width=\textwidth]{../image_paper2/1d/SED_total1by22_fluxdensity.png}
                 \end{subfigure}

### 2016-08-31 version0.0/appendixa_3.tex
Done with ch4

@@
 
+\begin{figure}
+\centering
+\includegraphics[width=164mm]{../image_paper1/OLS_vs_bayes.png.pdf}
+\caption[]{Mosaic created using the Montage programme from six fields of \halpha\ emission images of M31 from \citet{Massey07}.
+The resulting image from Montage was continuum-subtracted and masked for all point sources.
+The centre of the galaxy was masked out due to saturation of data in the continuum $R$-band image.}
+\label{fig:halpha}
+\end{figure}
+
 For finding probability distribution function of parameters of the extended Schmidt law, we followed the similar procedure as \cite{Shetty13}.

### 2016-08-31 version0.0/intro0.01.tex
Done with ch4

@@
 It can be written as ${\int T_{\mathrm CO} dV}$ where $T_{\mathrm CO}$(K) is the peak brightness temperature in the CO line and $V$ is the line-width in km~s$^{-1}$.
-%PB: please check this: I think \int should be omitted, dV should be \Delta V, and $V$ should also be $\Delta V$
+%PB: please check this: I think \int should be omitted, dV should be \Delta V, and $V$ in text should also be $\Delta V$
 For a uniform cloud with a radius $R$, the CO luminosity is given by:
@@
 The other problem is that there is evidence that the gas to dust ratio depends on the metallicity of the gas~\citep{Lisenfeld98, Draine07}, but even in direct methods the dependence on metallicity must be solved.
-Using dust emission as a tracer of gas is the best alternative for measuring the total gas in galaxies, that there is no observation of CO or \hi~emission.
+Using dust emission as a tracer of gas is the best alternative for measuring the total gas in galaxies where there are no observations of CO or \hi~emission.
 
@@
 Dust in ISM affects stellar emission by attenuating, scattering or absorption.
-Effect of dust clouds with embedded light sources on distribution of the light is called attenuation. 
+The effect of dust clouds with embedded light sources on the distribution of the light is called attenuation. 
 The dust cloud could have any distribution and be clumpy or smooth. 

### 2016-08-31 version0.0/paper2.tex
Done with ch4

@@
         \includegraphics[width=0.9\textwidth]{../image_paper2/k96.jpg}
-        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies from \citet{Hossein12} paper (Fig.
-1 in \citet{Hossein12}).
+        \caption[\citet{Kinney96} spectral templates for 12 types of galaxies]{\citet{Kinney96} spectral templates for 12 types of galaxies from Fig.
+1 in \citet{Hossein12}.
 The type of each template is shown in each frame.
@@
 Starburst galaxy spectra are indicated with SB 1 to 6.
-Higher numbers represent more intrinsic extinction.}
+Higher numbers represent more intrinsic extinction.
+Note that he vertical axis label from \citet{Hossein12} is incorrect: the quantity plotted is flux density, not flux.}
         \label{fig: k96}
